### 2016-01-25 Literature/thirdorder.tex
Uploaded ongoing articles

\documentclass[aps,preprint,amsmath,amssymb]{revtex4-1}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{bm}
\usepackage{color}
\usepackage{float}
\usepackage{dcolumn}
\usepackage{subfigure}
\usepackage{multirow}

\begin{document}

\title{Third order onebody diagrams}

\author{ }

\begin{abstract} 
All diagrams to third order in the interaction for an arbitrary two-body interaction $\hat{v}$.
\end{abstract}

%\pacs{02.70.Ss, 31.15.A-, 31.15.bw, 71.15.-m, 73.21.La}

\maketitle

\section*{Expressions}
The states $pq$ represent outgoing single-particle states. They can be either hole or particle states.
Holes states are labeled as $ijk\dots$ and particle states are $abc\dots$, the standard quantum chemistry notation. 
\subsection*{Diagram 1-5}
\[
\frac{1}{4}\sum_{abcd}\sum_{i}\frac{\langle pi| \hat{v} |ab  \rangle \langle ab| \hat{v} |cd  \rangle \langle cd| \hat{v} |qi  \rangle }{(\varepsilon_q+\varepsilon_i-\varepsilon_c-\varepsilon_d) (\varepsilon_q+\varepsilon_i-\varepsilon_a-\varepsilon_b)}.
\]

\subsection*{Diagram 1-6}
\[
-\frac{1}{4}\sum_{abc}\sum_{ij}\frac{\langle pc| \hat{v} |ab  \rangle \langle ab| \hat{v} |ij  \rangle \langle ij| \hat{v} |cq  \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_b) (\varepsilon_i+\varepsilon_j-\varepsilon_p-\varepsilon_c)}.
\]
\subsection*{Diagram 1-7}
\[
\frac{1}{4}\sum_{abc}\sum_{ij}\frac{\langle pc| \hat{v} |ij  \rangle \langle ij| \hat{v} |ab  \rangle \langle ab| \hat{v} |cq  \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_p-\varepsilon_c) (\varepsilon_i+\varepsilon_j+\varepsilon_q-\varepsilon_a-\varepsilon_p-\varepsilon_b)}.
\]

\subsection*{Diagram 1-8}
\[
-\frac{1}{4}\sum_{a}\sum_{ijkl}\frac{\langle ij| \hat{v} |qa  \rangle \langle kl| \hat{v} |ij  \rangle \langle pa| \hat{v} |kl  \rangle }{(\varepsilon_k+\varepsilon_l-\varepsilon_p-\varepsilon_a) (\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_p)}.
\]

\subsection*{Diagram 1-9}
\[
-\frac{1}{4}\sum_{ab}\sum_{ijk}\frac{\langle jp| \hat{v} |ab  \rangle \langle ab| \hat{v} |ik  \rangle \langle ik| \hat{v} |qj  \rangle }{(\varepsilon_k+\varepsilon_i-\varepsilon_a-\varepsilon_b) (\varepsilon_q+\varepsilon_j-\varepsilon_a-\varepsilon_b)}.
\]

\subsection*{Diagram 1-10}
\[
-\frac{1}{4}\sum_{ab}\sum_{ijk}\frac{\langle ab| \hat{v} |qk  \rangle \langle kp| \hat{v} |ij  \rangle \langle ij| \hat{v} |ab  \rangle }{(\varepsilon_k+\varepsilon_q-\varepsilon_a-\varepsilon_b) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-11}
\[
-\frac{1}{2}\sum_{ab}\sum_{ijk}\frac{\langle ab| \hat{v} |kj  \rangle \langle pk| \hat{v} |qi  \rangle \langle ij| \hat{v} |ab  \rangle }{(\varepsilon_k+\varepsilon_j-\varepsilon_a-\varepsilon_b) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-12}
\[
\frac{1}{2}\sum_{abc}\sum_{ij}\frac{\langle cb| \hat{v} |ij  \rangle \langle ij| \hat{v} |ab  \rangle \langle pa| \hat{v} |qc  \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_c) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-13}
\[
\frac{1}{2}\sum_{abc}\sum_{ij}\frac{\langle ab| \hat{v} |ij  \rangle \langle ic| \hat{v} |ab  \rangle \langle jp| \hat{v} |cq  \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_b) (\varepsilon_j-\varepsilon_c)}.
\]

\subsection*{Diagram 1-14}
\[
\frac{1}{2}\sum_{abc}\sum_{ij}\frac{\langle pc| \hat{v} |qi  \rangle \langle ab| \hat{v} |cj  \rangle \langle ij| \hat{v} |ab  \rangle }{(\varepsilon_i+\varepsilon_q-\varepsilon_p-\varepsilon_c) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-15}
\[
-\frac{1}{2}\sum_{ab}\sum_{ijk}\frac{\langle kp| \hat{v} |bq  \rangle \langle ij| \hat{v} |ak  \rangle \langle ab| \hat{v} |ij  \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_b) (\varepsilon_k-\varepsilon_b)}.
\]

\subsection*{Diagram 1-16}
\[
-\frac{1}{2}\sum_{ab}\sum_{ijk}\frac{\langle pa| \hat{v} |qk  \rangle \langle kb| \hat{v} |ij  \rangle \langle ij| \hat{v} |ab  \rangle }{(\varepsilon_q+\varepsilon_k-\varepsilon_p-\varepsilon_a) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-17}
\[
\sum_{abc}\sum_{ij}\frac{\langle ac| \hat{v} |ij  \rangle \langle jb| \hat{v} |cq  \rangle \langle ip| \hat{v} |ab \rangle }{(\varepsilon_i+\varepsilon_j-\varepsilon_a-\varepsilon_c) (\varepsilon_q+\varepsilon_i-\varepsilon_a-\varepsilon_b)}.
\]

\subsection*{Diagram 1-18}
\[
\sum_{abc}\sum_{ij}\frac{\langle ij| \hat{v}| ab  \rangle \langle bp| \hat{v} |jc  \rangle \langle ac| \hat{v} |iq  \rangle }{(\varepsilon_i+\varepsilon_q-\varepsilon_a-\varepsilon_c) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\subsection*{Diagram 1-19}
\[
\sum_{abc}\sum_{ij}\frac{\langle pi| \hat{v} |ab  \rangle \langle jb| \hat{v} |ci  \rangle \langle ac| \hat{v} |qj  \rangle }{(\varepsilon_q+\varepsilon_j-\varepsilon_a-\varepsilon_c) (\varepsilon_q+\varepsilon_i-\varepsilon_a-\varepsilon_b)}.
\]

\subsection*{Diagram 1-20}
\[
-\sum_{ab}\sum_{ijk}\frac{\langle pb| \hat{v} |ik  \rangle \langle ka| \hat{v} |bj  \rangle \langle ij| \hat{v} |qa  \rangle }{(\varepsilon_i+\varepsilon_k-\varepsilon_p-\varepsilon_b) (\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_p)}.
\]

\subsection*{Diagram 1-21}
\[
-\sum_{ab}\sum_{ijk}\frac{\langle ij| \hat{v} |aq  \rangle \langle kp| \hat{v} |bj  \rangle \langle ab| \hat{v} |ik  \rangle }{(\varepsilon_i+\varepsilon_k-\varepsilon_a-\varepsilon_b) (\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_p)}.
\]

\subsection*{Diagram 1-22}
\[
-\sum_{ab}\sum_{ijk}\frac{\langle ap| \hat{v} |ik  \rangle \langle bk| \hat{v} |jq  \rangle \langle ij| \hat{v} |ab  \rangle }{(\varepsilon_i+\varepsilon_k-\varepsilon_a-\varepsilon_p) (\varepsilon_q+\varepsilon_j+\varepsilon_i-\varepsilon_a-\varepsilon_b-\varepsilon_p)}.
\]

\begin{figure}%[hbtp]
     \begin{center}
            \includegraphics[width=0.38\textwidth]{onebd1.pdf}
            \includegraphics[width=0.38\textwidth]{onebd2.pdf}
            \includegraphics[width=0.38\textwidth]{onebd3.pdf}
    \end{center}
    \caption{One-body diagrams to third order in the interaction.}
\end{figure}

\end{document}

### 2016-01-25 compWithOtherMethods/Testing/fitcurve.f90

@@ -1,0 +1,412 @@
+!
+!     Main program starts here
+!
+      PROGRAM  fitting
+      IMPLICIT NONE
+      CALL vmcfit
+
+      END  PROGRAM fitting
+!
+!     This subroutine fits a data set with  in terms
+!     of a polynomial expansion. Number of terms in the polynomial
+!     expansion is given by the variable number_terms
+!     The number of data ( delta  and corresponding energy
+!     and the standard error) are defined by the variable number_of_data
+!
+      SUBROUTINE  vmcfit
+      IMPLICIT NONE
+      INTEGER :: i, number_of_data, number_terms
+      DOUBLE PRECISION, ALLOCATABLE, DIMENSION(:) :: w, n, e,sig,polynom_terms, variance
+      DOUBLE PRECISION, ALLOCATABLE, DIMENSION(:,:) :: cvm, v, u
+      DOUBLE PRECISION :: chisq, kappa, v_over_c, adiabatic
+      DOUBLE PRECISION :: d, eee, f, g, h, x3, x1, x2
+      EXTERNAL eos_param
+
+      READ (5,*) number_of_data, number_terms                  
+      ALLOCATE (cvm(number_terms,number_terms), &
+                v(number_terms,number_terms) )
+      ALLOCATE ( u(number_of_data,number_terms) )
+      ALLOCATE ( w(number_terms) )
+      ALLOCATE ( variance(number_terms) )
+      ALLOCATE ( polynom_terms(number_terms) )
+      ALLOCATE (n(number_of_data), e(number_of_data), sig(number_of_data) ) 
+      sig = 1.d0
+      DO i=1,number_of_data
+         READ (5,*)n(i) , d, e(i)!, f, g, h, x3, x1, x2
+      ENDDO
+      CALL svdfit(n,e,sig,number_of_data,polynom_terms, &
+                  number_terms, &
+                  u,v,w,number_of_data,number_terms,chisq)
+      CALL svdvar(v,number_terms,number_terms,w,cvm,number_terms)
+!     Compute now the variance for each coefficient using Eq. 15.4.19
+!     of numerical recipes
+      variance = 0.0; w = 1.0/(w*w)
+      DO i = 1, number_terms
+         variance(i) = SUM(v(i,:)*v(i,:)*w(:))
+      ENDDO
[…]

### 2016-01-25 compWithOtherMethods/Testing/per.f90

@@ -1,0 +1,32 @@
+      program yalla
+      implicit none
+      integer :: i, j, n
+      real(kind=8) :: hw, a, b, c, d, dmc
+      real(kind=8) :: elog1, elog2, elog3, corre, hf
+      real(kind=8), allocatable, dimension(:) :: r, x1, x2, x3
+
+      read(5,*)n, hw, dmc
+      allocate(r(n),x1(n),x2(n), x3(n))
+      do i=1,n
+         read(5,*) j, a, b, c,d
+         r(i) = j
+         x1(i) = b*hw
+         x2(i) = c*hw
+         x3(i) = d*hw
+      enddo 
+      hf = a*hw
+      corre = abs(a*hw-dmc)
+!      dmc = x3(n)
+
+      do i=1,n
+         a= (((x1(i)-hf)-corre))/corre
+         b = (((x2(i)-hf)-corre))/corre
+         c = (((x3(i)-hf)-corre))/corre
+         elog1 = 100-abs(a)*100
+         elog2 = 100-(abs( b ))*100
+         elog3 =  100-(abs( c ))*100
+         write(6,'(4E20.10)') r(i), elog1, elog2, elog3
+      enddo 
+
+
+      end

### 2016-01-25 compWithOtherMethods/Testing/plot.f90

@@ -1,0 +1,26 @@
+      program yalla
+      implicit none
+      integer :: i, j, n
+      real(kind=8) :: hw, a, b, c, d, dmc
+      real(kind=8) :: elog1, elog2, elog3
+      real(kind=8), allocatable, dimension(:) :: r, x1, x2, x3
+
+      read(5,*)n , hw, dmc, d
+      allocate(r(n),x1(n),x2(n))
+      do i=1,n
+         read(5,*) j, a, b
+         r(i) = j
+         x1(i) = a
+         x2(i) = b
+      enddo 
+      do i=2,n
+         a= ((x1(i)-dmc))!/dmc
+         b = ((x2(i)-dmc))!/dmc
+!         a = ((x2(i)-x2(i-1)))
+
+         elog2 = log10(abs( b ))
+         write(6,'(3E20.10)') log10(r(i)), elog2, elog2
+      enddo 
+
+
+      end

### 2016-01-25 compWithOtherMethods/Testing/vmcfit.f90

@@ -1,0 +1,420 @@
+!
+!     Main program starts here
+!
+      PROGRAM  fitting
+      IMPLICIT NONE
+      CALL vmcfit
+
+      END  PROGRAM fitting
+!
+!     This subroutine fits a data set with  in terms
+!     of a polynomial expansion. Number of terms in the polynomial
+!     expansion is given by the variable number_terms
+!     The number of data ( delta  and corresponding energy
+!     and the standard error) are defined by the variable number_of_data
+!
+      SUBROUTINE  vmcfit
+      IMPLICIT NONE
+      INTEGER :: i, number_of_data, number_terms, j
+      DOUBLE PRECISION, ALLOCATABLE, DIMENSION(:) :: w, n, e,sig,polynom_terms, variance
+      DOUBLE PRECISION, ALLOCATABLE, DIMENSION(:,:) :: cvm, v, u
+      DOUBLE PRECISION :: chisq, kappa, v_over_c, adiabatic
+      DOUBLE PRECISION :: d, eee, f, g, h, x3, x1, x2
+      EXTERNAL eos_param
+
+      READ (5,*) number_of_data, number_terms                  
+      ALLOCATE (cvm(number_terms,number_terms), &
+                v(number_terms,number_terms) )
+      ALLOCATE ( u(number_of_data,number_terms) )
+      ALLOCATE ( w(number_terms) )
+      ALLOCATE ( variance(number_terms) )
+      ALLOCATE ( polynom_terms(number_terms) )
+      ALLOCATE (n(number_of_data), e(number_of_data), sig(number_of_data) ) 
+      sig = 1.d0
+      DO i=1,number_of_data
+         READ (5,*)n(i) , d, e(i)!, f, g, h, x3, x1, x2
+      ENDDO
+      CALL svdfit(n,e,sig,number_of_data,polynom_terms, &
+                  number_terms, &
+                  u,v,w,number_of_data,number_terms,chisq)
+      CALL svdvar(v,number_terms,number_terms,w,cvm,number_terms)
+!     Compute now the variance for each coefficient using Eq. 15.4.19
+!     of numerical recipes
+      variance = 0.0; w = 1.0/(w*w)
+      DO i = 1, number_terms
+         variance(i) = SUM(v(i,:)*v(i,:)*w(:))
[…]

### 2016-01-25 compWithOtherMethods/fci6.py

@@ -1,0 +1,31 @@
+from pylab import *
+import sys
+import os
+import scipy.special as ss
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x,a,b,c):
+    z=np.zeros(len(x))
+    for i in range (len(x)):
+        res = 0 
+        for j in range (1, int(x[i])+1):
+            res += j**(b)
+        z[i] = c-res*a
+    return z
+
+dataSRG = loadtxt("6part10/FCI6part.dat")
+x = dataSRG[:,0]
+y = dataSRG[:,1]
+
+
+
+popt, pcov = curve_fit(func, x[-4:-1], y[-4:-1], sigma=None, maxfev=200000, gtol=.00001)
+a = popt[2]
+b = popt[0]
+c = -popt[1]
+extrapolated_energy = a-b*ss.zeta(c, 1)
+print extrapolated_energy
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol.py

@@ -1,0 +1,47 @@
+'''
+R^-c extrapolation script
+'''
+
+from scipy.optimize import curve_fit
+import numpy as np
+import scipy.special as ss
+
+def func(x,a,b,c):
+    z=np.zeros(len(x))
+    for i in range (len(x)):
+        res = 0               
+        for j in range (1, int(x[i])+1):
+            res += j**(b)
+        z[i] = c-res*a
+    return z
+
+'''
+example:
+@x shells
+@y energies
+@err error estimates
+'''
+#init arrays
+x = np.array([5, 7, 9, 11, 13, 15, 17, 19, 21, 23]) #shells
+y = np.array([15.016034, 14.990082, 14.978221, 14.971254, 14.967 , 14.963577, 14.961598 ,14.958911 , 14.958189, 14.957]) #energies
+err = np.array([.001, .0005, .0005, .00047, .0009, .0006, .0006, .0008, .00055, .0007])
+
+#fit curve
+maxfev = 10000 #max iterations
+gtol = 0.00001 #tolerance (see scipy manual)
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev=10000, gtol=.00001)
+
+#the slope is
+slope = popt[1]
+#the covariance matrix is
+pcov
+
+#the extrapolated energy is on closed form a-b*zeta(c)
+#where ss.zeta is the Riemann-Zeta function
+a = popt[2]
+b = popt[0]
+c = -popt[1]
+extrapolated_energy = a-b*ss.zeta(c, 1)
+print extrapolated_energy
+print a
+print b

### 2016-01-25 compWithOtherMethods/interpol12hw01.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("12part01/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol12hw028.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("12part028/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol12hw05.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("12part05/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol12hw1.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("12part10/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol2.py

@@ -1,0 +1,35 @@
+import numpy as np
+from scipy.optimize import curve_fit
+import scipy.special as ss
+
+def func(x,a,b,c):
+    z=np.zeros(len(x))
+    for i in range (len(x)):
+        res = 0               
+        for j in range (1, int(x[i])+1):
+            res += j**(b)
+        z[i] = c-res*a
+    return z
+
+#def func(x, a, b, c):
+#     return a*(x**b) + c
+
+x = np.array([10,12,14,16,18,20]) #shells
+y = np.array([12.21380, 12.21819, 12.22080, 12.22152, 12.22196, 12.22229]) #energies
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 10000, gtol=0.01)
+#the slope is
+slope = popt[1]
+#the covariance matrix is
+pcov
+
+#the extrapolated energy is on closed form a-b*zeta(c)
+#where ss.zeta is the Riemann-Zeta function
+a = popt[2]
+b = popt[0]
+c = -popt[1]
+extrapolated_energy = a-b*ss.zeta(c, 1)
+print extrapolated_energy
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol20hw01.py

@@ -1,0 +1,24 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(c))
+#     return a+ b*exp(-x*c)
+
+dataSRG = loadtxt("20part01/20part.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+#popt, pcov = curve_fit(func, x[-4:-1], y[-4:-1], sigma=None, maxfev = 200000, gtol=0.00001)
+
+popt, pcov = curve_fit(func, x,y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol20hw028.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("20part028/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol20hw05.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("20part05/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol20hw1.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("20part10/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol30hw01.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("30part01/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol30hw028.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("30part028/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol30hw05.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("30part05/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol30hw1.py

@@ -1,0 +1,31 @@
+from pylab import *
+import sys
+import os
+import scipy.special as ss
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x,a,b,c):
+    z=np.zeros(len(x))
+    for i in range (len(x)):
+        res = 0 
+        for j in range (1, int(x[i])+1):
+            res += j**(b)
+        z[i] = c-res*a
+    return z
+
+dataSRG = loadtxt("42part01/interpol.dat")
+x = dataSRG[:,0]
+y = dataSRG[:,2]
+
+
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev=200000, gtol=.00001)
+a = popt[2]
+b = popt[0]
+c = -popt[1]
+extrapolated_energy = a-b*ss.zeta(c, 1)
+print extrapolated_energy
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol42hw01.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("42part01/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol42hw028.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("42part028/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol42hw05.py

@@ -1,0 +1,22 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a - b*(x**(-c))
+
+dataSRG = loadtxt("30part01/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol42hw1.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*exp(-x*c)
+
+dataSRG = loadtxt("42part10/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol6hw01.py

@@ -1,0 +1,27 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("6part01/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c
+
+
+
+
+
+

### 2016-01-25 compWithOtherMethods/interpol6hw028.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("6part028/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol6hw05.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("6part05/interpol.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,2]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/interpol6hw1.py

@@ -1,0 +1,21 @@
+from pylab import *
+import sys
+import os
+import numpy as np
+from scipy.optimize import curve_fit
+
+def func(x, a, b, c):
+     return a+ b*(x**(-c))
+
+dataSRG = loadtxt("6part10/FCI6part.dat")
+x = dataSRG[:,0]
+y=dataSRG[:,1]
+
+popt, pcov = curve_fit(func, x, y, sigma=None, maxfev = 200000, gtol=0.00001)
+
+a = popt[0]
+b = popt[1]
+c = popt[2]
+print a
+print b
+print c

### 2016-01-25 compWithOtherMethods/plot12parthw01.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("12part01/12part.dat")
+dataCCSD = loadtxt("12part01/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 12.26984
+
+axis([5,20,12, 14.2])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=12,\;\omega=0.1$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('12parthw01.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot12parthw028.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("12part028/12part.dat")
+dataCCSD = loadtxt("12part028/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 25.63577
+
+axis([5,20,25.46, 27.7])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=12,\;\omega=0.28$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('12parthw028.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot12parthw05.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("12part05/12part.dat")
+dataCCSD = loadtxt("12part05/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 39.1596
+
+axis([5,20,39.0, 41.2])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=12,\;\omega=0.5$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('12parthw05.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot20parthw01.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("20part01/20part.dat")
+dataCCSD = loadtxt("20part01/CCSD.dat")
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 29.9779
+
+axis([8,20,29.6, 33.1])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0]
+, dataCCSD[:,1], 'm:v',  dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=20,\;\omega=0.1$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD', 'DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('20parthw01.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot20parthw028.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("20part028/20part.dat")
+dataCCSD = loadtxt("20part028/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 61.9268
+
+axis([8,20,61.5, 68])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=20,\;\omega=0.28$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('20parthw028.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot20parthw05.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("20part05/20part.dat")
+dataCCSD = loadtxt("20part05/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 93.8752
+
+axis([6,20,93.3, 99.9])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=20,\;\omega=0.5$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('20parthw05.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot20parthw1.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("20part10/20part.dat")
+dataCCSD = loadtxt("20part10/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 155.8822
+
+axis([6,20,155.4, 161.3])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=20,\;\omega=1.0$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('20parthw1.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot30parthw01.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("30part01/30part.dat")
+dataCCSD = loadtxt("30part01/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 60.4205
+
+axis([9,20,59.5, 68])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.',  dataCCSD[:,0], dataCCSD[:,1], 'm:v', dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=30,\;\omega=0.1$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('30parthw01.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot30parthw028.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("30part028/30part.dat")
+dataCCSD = loadtxt("30part028/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 123.9683
+
+axis([7,20,122, 139])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=30,\;\omega=0.28$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('30parthw028.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot30parthw05.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("30part05/30part.dat")
+dataCCSD = loadtxt("30part05/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 187.0426
+
+axis([7,20,185, 202])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=30,\;\omega=0.5$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('30parthw05.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot30parthw1.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("30part10/30part.dat")
+dataCCSD = loadtxt("30part10/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 308.5627
+
+axis([7,20,307, 323])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=30,\;\omega=1.0$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('30parthw1.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot42parthw01.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("42part01/42part.dat")
+dataCCSD = loadtxt("42part01/CCSD.dat")
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 107.6389
+
+axis([14,20,106, 115])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.',  dataCCSD[:,0]
+, dataCCSD[:,1], 'm:v', dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=42,\;\omega=0.1$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD', 'DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('42parthw01.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot42parthw028.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("42part028/42part.dat")
+dataCCSD = loadtxt("42part028/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 219.8426
+
+axis([12,20,218,229.5])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=42,\;\omega=0.28$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('42parthw028.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot42parthw05.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("42part05/42part.dat")
+dataCCSD = loadtxt("42part05/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 330.6306
+
+axis([8,20,327, 364])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=42,\;\omega=0.5$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('42parthw05.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot42parthw1.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("42part10/42part.dat")
+dataCCSD = loadtxt("42part10/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 542.9428
+
+axis([8,20,540, 575])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=42,\;\omega=1.0$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('42parthw1.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot6parthw01.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("6part01/6part.dat")
+dataCCSD = loadtxt("6part01/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 3.555385
+
+axis([4,20,3.4, 4.03])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=6,\;\omega=0.1$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('6parthw01.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot6parthw028.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("6part028/6part.dat")
+dataFCI = loadtxt("6part028/6partFCIStd.dat")
+dataCCSD = loadtxt("6part028/CCSD.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 7.60019
+
+axis([4,20,7.50, 8.16])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', 
+dataFCI[:,0], dataFCI[:,1],'g--x', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=6,\;\omega=0.28$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','FCI','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('6parthw028.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot6parthw05.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("6part05/SRG6part.dat")
+dataFCI = loadtxt("6part05/FCI6part.dat")
+dataCCSD = loadtxt("6part05/CCSD6part.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+data7[:] = 11.78484
+
+axis([4,20,11.70, 12.4])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', 
+dataFCI[:,0], dataFCI[:,1],'g--x', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=6,\;\omega=0.5$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','FCI','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('6parthw05.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plot6parthw1.py

@@ -1,0 +1,39 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['Six electron quantum dot']})
+
+dataSRG = loadtxt("6part10/SRG6part.dat")
+dataFCI = loadtxt("6part10/FCI6part.dat")
+dataCCSD = loadtxt("6part10/CCSD6part.dat")
+
+l = len(dataSRG[:,0])
+data7 = zeros(l)
+# DMC results
+data7[:] = 20.1532
+
+axis([4,20,20.05, 21])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', 
+dataFCI[:,0], dataFCI[:,1],'g--x', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataSRG[:,0], data7[:], 'k--',markersize=7)
+
+#title(r'$N=6,\;\omega=1.0$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','FCI','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('6parthw1.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 compWithOtherMethods/plotfig12.py

@@ -1,0 +1,39 @@
+#!/usr/bin/python
+from numpy import *
+from pylab import *
+from matplotlib import rc, rcParams
+import matplotlib.units as units
+import matplotlib.ticker as ticker
+import sys
+import os
+
+
+rc('text',usetex=True)
+rc('font',**{'family':'serif','serif':['New fits of nuclear forces']})
+
+dataSRG = loadtxt("6part10/6part.dat")
+dataFCI = loadtxt("6part10/6partFCIStd.dat")
+dataCCSD = loadtxt("6part10/CCSD.dat")
+dataCCSDHO = loadtxt("6part10/CCSDHO.dat")
+
+l = len(dataCCSDHO[:,0])
+data7 = zeros(l)
+data7[:] = 20.1598
+
+axis([4,20,20.12, 20.9])
+xlabel(r'$R$',fontsize=20)
+ylabel(r'$E_0\, [E_h^*]$',fontsize=20)
+plot(dataSRG[:,0], dataSRG[:,2],'b-*', dataSRG[:,0], dataSRG[:,1],'r:.', 
+dataFCI[:,0], dataFCI[:,1],'g--x', dataCCSD[:,0], dataCCSD[:,1], 'm:v',dataCCSDHO[:,0], data7[:], 'k--',markersize=7)
+
+title(r'$N=6,\;\omega=1.0$', fontsize=20, horizontalalignment='center')
+legend(('SRG','HF','FCI','CCSD','DMC'),
+           'upper right', shadow=False, fancybox=False,prop={"size":18})
+legend(loc='upper right')
+
+xticks( [4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20])
+# Save the figure in a separate file
+savefig('6parthw1.pdf', format='pdf')
+# Draw the plot to screen
+show()
+    

### 2016-01-25 Manuscript/paper.tex
Update on tex file

\documentclass[amsmath, amssymb, aps, floatfix, nofootinbib, preprintnumbers,showpacs, superscriptaddress, twocolumn]{revtex4-1}
\usepackage{bm}
\usepackage[cmyk]{xcolor}
\usepackage{dcolumn}
\usepackage{epsfig}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{subfigure}
\newcommand{\lb}{\left(}
\newcommand{\rb}{\right)}
\newcommand{\ad}{a^{\dagger}}
\newcommand{\Hd}{\hat{H}^{\rm d}}
\newcommand{\Ho}{\hat{H}^{\rm od}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\T}{\hat{T}_{\rm rel}}
\newcommand{\da}{^\dagger}
\newcommand{\lla}{\left\langle}
\newcommand{\rra}{\right\rangle}
\newcommand{\llb}{\lbrace}
\newcommand{\rrb}{\rbrace}
\newcommand{\rv}{\mathbf{r}}

%Jorgen commands
\newcommand{\OP}[1]{{\hat{#1}}}
\newcommand{\ket}[1]{\left| #1 \right>}
\newcommand{\bra}[1]{\left< #1 \right|}
\newcommand{\braket}[2]{\left\langle #1 | #2\right\rangle}

\begin{document}

\title{Studies of quantum dots}

\author{Fei Yuan}
\affiliation{National Superconducting Cyclotron Laboratory and
  Department of Physics and Astronomy,
  Michigan State University,
  East Lansing, MI 48824, USA}
\author{Sarah Reimann}
\affiliation{Department of Chemistry and Center for Theoretical and Computational Chemistry, University of Oslo, N-0316 Oslo, Norway}
\author{Scott Bogner}
\affiliation{National Superconducting Cyclotron Laboratory and
  Department of Physics and Astronomy,
  Michigan State University,
  East Lansing, MI 48824, USA}
\author{Morten Hjorth-Jensen}
\affiliation{National Superconducting Cyclotron Laboratory and
  Department of Physics and Astronomy,
  Michigan State University,
  East Lansing, MI 48824, USA}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\begin{abstract}
  We present and compare several many-body methods used to study a quantum dot
  system.  We calculate the approximate ground state energy of electrons in a
  circularly symmetric potential well using a harmonic oscillator basis
  optimized via Hartree-Fock.  We further improve the ground state energy
  using in-medium similarity renormalization group (IM-SRG).  Additionally, we
  calculate the addition and removal energies using quasidegenerate
  perturbation theory (QDPT).  Our results are benchmarked against quasi-exact
  diffusion Monte Carlo results from previous works.  Possible explanations
  for the discrepancies are discussed.
\end{abstract}

\pacs{02.70.Ss, 31.15.A-, 31.15.bw, 71.15.-m, 73.21.La}
\maketitle

\section{Introduction}

Understanding the behaviour of strongly confined electrons is of fundamental
interest for solving many-body problems.  Quantum dots, e.g. electrons
confined in semiconducting heterostructures, are of particular interest since
they exhibit, due to their small size, discrete quantum levels. Under these
conditions, typical quantum phenomena like tunnelling, entanglement and
magnetization can all be observed \cite{reimann2002,engel1993}.  Since quantum
dots are manufactured and designed artificially at the laboratory, their
quantum levels can be tuned to one's needs by changing for instance the
external field, or the size and shape of the system. As a consequence, quantum
dots provide a high level of control for the dynamics and correlation of the
electrons, which makes them perfectly suited to study quantum effects in
practice.  Since their ground state shows similar shell structures and magic
numbers as seen for atoms and nuclei \cite{tarucha1996}, these systems give
the opportunity to study electronic systems without the presence of a nucleus
affecting the electrons.  Apart from their relevance for theoretical research
in quantum physics, quantum dots offer a wide variety of applications: In
particular, their electrical and optical properties make them attractive for
the use in laser technology \cite{strauf2010,5075760} and solar cells
\cite{jenks:013111,doi:10.1021/cr900289f}, but they are also used in quantum
computers \cite{PhysRevA.57.120} and medical imaging \cite{Ben-Ari02042003}.

In order to properly understand the properties of quantum dots and make
theoretical predictions to their behaviour in various applications, it is
necessary to study features like ground state energy and correlation
effects. Since apart from quantum dots consisting of only two electrons or
with specific values of the external field, no analytical solutions exist
\cite{PhysRevA.48.3561}, the development of appropriate few- and many-body
methods is required.

Several \textit{ab initio} methods have been applied to these systems, in
particular variational and diffusion Monte Carlo \cite{PhysRevB.68.035304,%
  PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}, large-scale
diagonalization \cite{JJAP.36.3924,PhysRevB.56.6428,Kvaalcode,rontani:124102}
and Coupled Cluster theory \cite{PhysRevB.67.045320,heidari:114708,%
  PhysRevB.84.115302}.

Additionally to those approaches, another very promising first-principle
method has recently evolved. This is the Similarity Renormalization Group
(SRG) method, which drives the Hamiltonian to a band- or block-diagonal form
using a continuous series of unitary transformations.  Especially in nuclear
theory, it has successfully been applied to study systems with different
underlying potentials, and it has been used to analyse their binding energy
and other observables \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}. Apart
from the free-space approach, where the Hamiltonian is set up with respect to
the zero vacuum state, in recent times another interesting alternative has
been worked out: Making use of the technique of normal-ordering, the SRG
evolution is performed in medium, where 3, \ldots, $A$-body operators can be
approximated using only two-body machinery. This in-medium SRG (IM-SRG) allows
considerable simplifications to the problem and makes numerical calculations
much more efficient \cite{IMSRG}.

 This article is organized as follows: Section \ref{sec:formalism}
 introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
 use to model circular quantum dots, and gives afterwards an overview
 over the SRG (\ref{subsec:SRG}) and DMC (\ref{subsec:DMC})
 formalism. Our results are presented in Section \ref{sec:results}. We
 point out the differences arising from the use of two different
 generators, Wegner's and White's one, and give an overview over the
 ground state energies up to 42 particles. In particular, we compare
 the results obtained with five different \textit{ab initio} methods:
 IM-SRG(2), DMC, Hartree-Fock, Full Configuration Interaction and
 Coupled Cluster. Section \ref{sec:conclusions} concludes our work and
 gives perspectives for future work.

The harmonic oscillator (HO) is ubiquitous in quantum physics. It is
the basis for extremely diverse many-body calculations in nuclear
physics,\cite{HjorthJensen1995} quantum chemistry,\cite{Helgaker2002}
and quantum dot calculations in solid state physics.\cite{Reimann2002}
In these calculations, one typically seeks a few of the lowest
eigenenergies $E_k$ of the system Hamiltonian $H$, and their
corresponding eigenvectors $\psi_k$, viz,
\[ H\psi_k = E_k\psi_k, \quad k = 1,\cdots,k_\text{max}. \] In all
cases, the many-body wave function is expanded in a basis of
eigenfunctions of the HO, and then necessarily truncated to give an
approximation. In fact, the so-called curse of dimensionality implies
that the number of degrees of freedom per particle available is
severely limited. It is clear, that an understanding of the properties
of such expansions, giving \emph{a priori} error estimates on
many-body calculations, is very important. Unfortunately, this is a
neglected topic in the physics literature. In this article, we give a
thorough mathematical and numerical analysis and give practical
convergence estimates of HO basis expansions. It generalizes and
refines the findings of a recent study of one-dimensional systems.\cite{Kvaal2007}

The HO eigenfunctions are popular for several reasons. Many quantum
systems, such as the quantum dot model considered here, are perturbed
harmonic oscillators \emph{per se}, so that the true eigenstates
should be perturbations of the HO states. Moreover, the HO has many
beautiful properties, such as separability, invariance under
orthogonal coordinate changes, and easily computed eigenfunctions, so
that computing matrix elements of relevant operators becomes
relatively simple. The HO eigenfunctions are defined on the
\emph{whole} of $\mathbb{R}^d$ in which the particles live, so that
truncation of the domain is unnecessary. Indeed, this is one of the
main problems with methods such as finite difference or finite element
methods.\cite{RamMohan2002}

\section{Formalism}
\label{sec:formalism}

\subsection{The model Hamiltonian}
\label{subsec:modelHamiltonian}

We model the quantum dot as a collection of $N$ electrons trapped in an
external harmonic-oscillator potential.\footnote{In this paper, we use atomic
  units where $\hbar$, $m$, $e$, and $4 \pi \epsilon$ are unity, with
  $\epsilon$ denoting the permittivity and $m$ denoting the mass, which may be
  an effective mass.  In vacuum where $m = m_{\text e}$ and
  $\epsilon = \epsilon_0$, energy would be measured in units of hartrees
  $E_{\text h} \equiv m_{\text e} (\alpha c)^2$.  More generally, the units of
  energy are $m_{\text r \vphantom h}^{} E_{\text h}^{} /
  \epsilon_{\text r \vphantom h}^2$ where
  $\epsilon_{\text r} \equiv \epsilon / \epsilon_0$ and
  $m_{\text r} \equiv m / m_{\text e}$.}  Each electron possesses kinetic
energy $t(\bm p) \equiv \bm p^2 / 2$ and experiences an external potential
\begin{align*}
  u(\bm r) \equiv \frac{1}{2} \omega^2 \bm r^2
\end{align*}
where $\omega$ is the angular frequency of the oscillator, $\bm r$ is the
2-dimensional coordinate of an electron, and $\bm p$ is its momentum.  Each
pair of electrons experience a Coulomb repulsion
\begin{align*}
  v(\bm r, \bm r') \equiv \frac{1}{|\bm r - \bm r'|}
\end{align*}
where $\bm r$ and $\bm r'$ are coordinates of a pair of electrons.  Thus, the
full many-body problem is described by the nonrelativistic Hamiltonian
\begin{align*}
  \hat H \equiv \sum_{p} \bigl(
  t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
  \bigr) + \sum_{\{p, q\}} v(\hat{\bm r}_p, \hat{\bm r}_q)
\end{align*}
where $\hat{\bm p}_p$ is the momentum operator and $\hat{\bm r}_p$ is the
position operator for a particle labeled by $p$.  The first summation is
performed over every particle $p$, while the the second summation is performed
over every unordered pair of particles $\{ p, q \}$ (with $p \ne q$).

The full problem is not a trivial one.  We shall first consider a much simpler
problem: a noninteracting Hamiltonian $\hat H^{\text o}$ in which the Coulomb
interaction $v$ is removed:
\begin{align*}
  \hat H^{\text o} \equiv \sum_{p} \bigl(
  t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
  \bigr)
\end{align*}
In this case, the many-body Hamiltonian reduces to $N$ independent
single-particle Hamiltonians, each of the form:
\begin{align*}
  \hat h^{\text o} \equiv
  \frac{\hat{\bm p}^2 + \omega^2 \hat{\bm x}^2}{2}
\end{align*}
This is a 2-dimensional harmonic oscillator problem for a single particle,
whose solutions are well known.  There are, however, various ways to construct
the set of eigenfunctions: we shall use the Fock-Darwin states that conserve
angular momentum about the axis perpendicular to the plane.  The
eigenfunctions have the following analytic form in polar
coordinates:\citep[Appx.\ A]{lohne2010coupled}
\begin{gather*}
  \phi^{\text{fd}}_{n, m_\ell}(r, \varphi)
  \equiv \sqrt\omega
  \phi^{\text{fdr}}_{n, |m_\ell|}(\sqrt \omega r)
  \phi^{\text{fda}}_{m_\ell}(\varphi)
\end{gather*}
where
\begin{align*}
  \phi^{\text{fdr}}_{n, \mu}(\rho) &\equiv
  \sqrt{\frac{2 \cdot n!}{(n + \mu)!}}
  {\mathrm e}^{- \rho^2 / 2} \rho^\mu L_n^{(\mu)}(\rho^2) \\
  \phi^{\text{fda}}_{m_\ell}(\varphi) &\equiv
  \frac{1}{\sqrt{2 \pi}} {\mathrm e}^{i m_\ell \varphi}
\end{align*}
and $L_n^{(\mu)}$ denotes the generalized Laguerre polynomial of degree $n$
with parameter $\mu$.  The states are labelled by two quantum numbers: the
principal quantum number $n \in \{0, 1, \ldots\}$ and the angular momentum
projection $m_\ell \in \mathbb Z$.

Additionally, since electrons are spin-$1/2$ fermions, they can occupy either
of the two spin states $\chi_{+\frac12}$ or $\chi_{-\frac12}$.  Thus, the
single-particle basis states can be constructed as
\begin{align} \label{eq:singleparticlestate}
  \phi_{n, m_\ell, m_{\text s}}(r, \varphi) \equiv
  \phi^{\text{fd}}_{n, m_\ell}(r, \varphi) \chi_{m_{\text s}}
\end{align}
with the spin projection $m_{\text s} \in \bigl\{-\frac12, +\frac12\bigr\}$.

\begin{figure}
\includegraphics[width=.48\textwidth]{fig-shell-structure}
\caption{Structure of the single-particle states in a noninteracting harmonic
  oscillator.}
\label{fig:shell-structure}
\end{figure}
The eigenvalues of the single-particle Hamiltonian $\hat h^{\text o}$ are
given by
\begin{align*}
  \varepsilon_{n, m_\ell, m_{\text s}} \equiv (2 n + |m_\ell| + 1) \omega
\end{align*}
Note that they are degenerate with respect to the spin projection
$m_{\text s}$ since our Hamiltonian $\hat h^{\text o}$ does not distinguish
between them.  From this equation, we can see that the single-particle basis
states form a shell structure as shown in Figure \ref{fig:shell-structure}.
Every state within a given shell is degenerate and states within a given shell
satisfy $2 n + |m_\ell| = k$ for some nonnegative integer $k$, which we call
the \textit{shell index}.  The shells are equidistant from each other, with a
spacing equal to the frequency $\omega$.

The many-body Hamiltonian $\hat H^{\text o}$ is the sum of the single-particle
Hamiltonians $\hat h^{\text o}_p$ over all particles $p$, where $p$ may now be
treated as a tuple of all three single-particle quantum numbers:
$(n, m_\ell, m_{\text s})$.  From the states $\phi$ in
\eqref{eq:singleparticlestate} we can construct the eigenstates of the
many-body Hamiltonian $\hat H^{\text o}$ in the form of Slater determinants
that automatically satisfy the Pauli exclusion principle:
\begin{align*}
  \Phi_{p_1, \ldots, p_N}(\bm r_1, \ldots, \bm r_N) \equiv
  \frac{1}{\sqrt{N}} \left|
  \begin{matrix}
    \phi_{p_1}(\bm r_1) & \cdots & \phi_{p_N}(\bm r_1) \\
    \vdots & \ddots & \vdots \\
    \phi_{p_1}(\bm r_N) & \cdots & \phi_{p_N}(\bm r_N) \\
  \end{matrix}
  \right|
\end{align*}
The energy of these states is given by the sum of the single-particle
energies:
\begin{align*}
  E^{\text o}_{p_1, \ldots, p_N} \equiv
  \varepsilon_{p_1} + \cdots + \varepsilon_{p_N}
\end{align*}
For ground states, we may have degeneracies due to the shell structure of the
single-particle basis.  However, if $N = k_{\text f} (k_{\text f} + 1)$ for
some nonnegative integer $k_{\text f}$, there are just enough particles to
form a closed-shell system.  In this case, there is a unique, well-isolated
ground state.  The values of $N$ for which this occurs are typically referred
to as \textit{magic numbers} and we call $k_{\text f}$ the \textit{number of
  filled shells}.  This completes the solution of the noninteracting problem.

The difficulty in solving the full Hamiltonian $\hat H$ stems from the fact
that the exact solution cannot be expressed in terms of a single Slater
determinant due to the presence of interactions.  Hence, it is not possible to
reduce the problem to that of a single particle as we had done previously.

However, if we assume that the interaction alters the behavior of the system
only mildly, we can use the Slater determinants of the noninteracting system
as an initial guess for the solution, and then apply iterative methods to
improve the accuracy of the solution.

Since Slater determinants are rather cumbersome to write out in full, we shall
instead work in the more convenient formalism of second quantization:
\begin{align*}
  |\Phi_{p_1, \ldots, p_N}\rangle =
  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger |\varnothing\rangle
\end{align*}
Here, $\hat a_p^\dagger$ is the creation operator for the single-particle
state $p$ and $|\varnothing\rangle$ is the (true) vacuum state that is devoid
of particles.  Analogously, $\hat a_p$ is the annihilation operator for the
state $p$.

Operators can be rewritten in this formalism as well.  The one-body kinetic
energy operator, defined by
\begin{align*}
  \hat T \equiv \sum_p \hat t(\hat{\bm p}_p)
\end{align*}
can be rewritten in second quantization as
\begin{align*}
  \hat T = \sum_{p, q} T_{p, q}^{} \hat a_p^\dagger \hat a_q^{}
\end{align*}
where the operator matrix element
$T_{p, q} \equiv \langle \Phi_p | \hat T | \Phi_q \rangle$.  This can likewise
be extended for both $\hat U$ and $\hat V$,
\begin{align*}
  \hat U &= \sum_{p, q} U_{p, q}^{} \hat a_p^\dagger \hat a_q^{} \\
  \hat V &= \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
  \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
\end{align*}
where $U_{p, q} \equiv \langle \Phi_p | \hat U | \Phi_q \rangle$ and
$V_{p, q, r, s} \equiv \langle \Phi_{p, q} | \hat V | \Phi_{r, s} \rangle$.
Note that due to the antisymmetry present in the Slater determinants, we have
the property that exchanging either $p$ with $q$ or $r$ with $s$ causes
$V_{p, q, r, s}$ to reverse in sign.

\subsection{Hartree-Fock method}
\label{subsec:HartreeFockmethod}

The first correction that we will apply to our solution is that of the
Hartree-Fock method.  Using the variational principle, we compute an
approximate ground state $\Psi^{\text{hf}}$ by minimizing the energy
\begin{align*}
  E^{\text{hf}} \equiv \langle \Psi^{\text{hf}} | \hat H | \Psi^{\text{hf}} \rangle
\end{align*}
with respect to $\Psi^{\text{hf}}$, subject to the restriction that
$\Psi^{\text{hf}}$ is a single Slater determinant constructed from a set of
$N$ orthonormal single-particle states.  We denote each state $\psi_u$, where
$u$ is its label.

To make this computationally feasible, we further assume that the unknown
states $\psi$ are built from a linear combination of known functions,
drawn from a finite set.  This reduces the problem from an abstract
mathematical one to a numerical linear algebra problem, with the caveat that
this set of known functions must be chosen carefully.

Assuming the interaction is not too strong, we can use the single-particle
states $\phi$ of our noninteracting Hamiltonian as a basis for the unknown
states $\psi$.  The two sets of states are then related by a linear
transformation $\bm C$:
\begin{align*}
  \psi_u \equiv \sum_p \phi_p C_{p, u}
\end{align*}
To ensure the orthonormality of the states, we expand the set of unknown
states $\psi$ to have as many elements as the set of $\phi$ and require the
\textit{coefficient matrix} $\bm C$ to be unitary.  While these conditions
are more strict than necessary, they greatly simplify the calculations and the
additional states are essential inputs for methods beyond Hartree-Fock.  The
set of states $\psi$ now consists of $N$ \textit{occupied} states that
participate in the Slater determinant $\Psi^{\text{hf}}$ and the remaining
\textit{unoccupied} states that do not.

Since the coefficient matrix uniquely determines the unknown states, the
variational problem has been reduced to that of solving of the coefficients
$\bm C$ that minimize the energy $E$, which is given by
\begin{align*}
  E^{\text{hf}} = \sum_{\underline u} C_{p, u}^* H_{p, q}^{\text o} C_{q, u}^{}
  + \sum_{\underline u, \underline v}
  C_{p, u}^* C_{q, u}^* V_{p, q, r, s}^{} C_{r, u}^{} C_{s, u}^{}
\end{align*}
where the underlined indices indicate that the summation is over occupied
states only.

Using the method of Lagrange multiplers, the minimization problem can be
reduced to the solving of a nonlinear equation -- the \textit{Hartree-Fock
  equation}:
\begin{align} \label{eq:hartreefock}
  \bm f \bm C = \bm C \bm \epsilon
\end{align}
where the \textit{Fock matrix} $\bm f$ is defined as
\begin{align} \label{eq:fock}
  f_{p, r} \equiv H_{p, r}^{\text o} + \sum_{\underline u q s}
  C_{q, u}^* V_{p, q, r, s}^{} C_{s, u}^{}
\end{align}
and $\bm \epsilon$ is a vector of Lagrange multipliers with each
element $\epsilon_u$ associated with a particular state $u$.  While the Fock
matrix $\bm f$ may appear to be an artificial Hamiltonian derived purely
from the minimization problem, it can be generalized as an operator whose
relevance extends beyond Hartree-Fock.

The Hartree-Fock equation can be solved by an iterative technique: a solution
$\bm C$ can be fed into \eqref{eq:fock} and new solution can then obtained
by solving the eigenvalue problem in \eqref{eq:hartreefock} using the Fock
matrix obtained.  For the initial guess, we use the ground state of our
noninteracting Hamiltonian, thus $\bm C$ is initially the identity matrix.

Since Hartree-Fock method restricts the ground state to a Slater determinant
of single-particle states, it cannot provide an exact solution to a problem
where correlation is present, even if the basis $\phi$ is infinite.  The
energy difference between the best Hartree-Fock energy and the exact ground
state energy is thus by definition known as the \textit{correlation energy}.
There are various methods of recovering (at least parts of) this missing
energy.  The focus of this paper shall be on the IM-SRG method.

\subsection{The IM-SRG method}
\label{subsec:imsrgmethod}

In the similarity renormalization group (SRG) method, one performs a
continuous sequence of unitary transformations on a Hamiltonian operator
$\hat H$ to evolve it into a more ``amenable'' form -- which generally implies
decoupling a small model space of interest from its complement.  The sequence
is parameterized by a continuous variable $s$ known as the \textit{flow
  parameter}, which by convention we define to be $0$ at the beginning of the
sequence.  Upon reaching $s$, the transformed Hamiltonian is given by
\begin{align*}
  \tilde H(s) \equiv \hat U(s) \hat H \hat U(s)
\end{align*}
where $U(s)$ describes the product of all such transformations since $s = 0$.
At every step $s'$, the differential unitary transformation is described by
the exponential of an antihermitian operator $\eta(s)$, known as the
\textit{generator} of the transformation.  When ``integrated'' as a product,
the full transformation $\hat U(s)$ is recovered:\footnote{Alternatively, this
  can also be reinterpreted as an $s'$-ordered integral.  See \cite[\S
  6.1]{reimann2013quantum}.}
\begin{align*}
  \hat U(s) = \lim_{\Delta s' \to 0} \prod_{s' = 0}^{s' = s}
  \mathrm e^{\hat \eta(s') \Delta s'}
\end{align*}
The evolution of the Hamiltonian itself is governed by a differential
equation, commonly referred to as the flow equation:
\begin{gather} \label{eq:imsrgode}
  \frac{d}{d s} \tilde H(s) = [\hat \eta(s), \tilde H(s)]
\end{gather}
which allows $\tilde H(s)$ to be evaluated without explicitly constructing the
full transformation $\hat U(s)$.

 Introducing a flow parameter $s$, there exits a unitary
 transformation $U_s$, such that
\begin{equation}
 \hat{H}_s = U_s^\dagger \hat{H} U_s \equiv \Hd_s + \Ho_s,
\end{equation}
with the relations $U_{s=0} = \mathbf{1}$, and $\hat{H}_{s= 0} =
\hat{H}$.  The transformation $U_s$ is parametrized as
\[
U_s = T_s \exp \left(\int_0^s \! ds'\hat{\eta}_{s'} \right),
\]
where the anti-hermitian operator $\hat{\eta}_s$ serves as generator
of the transformation. With $T_s$ we denote $s$-ordering, which is
defined equivalently to usual time-ordering.  Taking the derivative of
$\hat{H}_s$ with respect to $s$ gives
\begin{equation}
 \frac{d \hat{H}_s}{ds} = \frac{d U_s}{ds}\hat{H} U_s^\dagger + U_s
 \hat{H} \frac{d U_s^\dagger}{ds}.
\label{eq:flow_long}
\end{equation}
Utilizing that for our particular form of $U_s$, we have that \be
\hat{\eta}_s = \frac{d U_s}{ds} U_s^\dagger = - U_s \frac{d
  U_s^\dagger}{ds} = -\hat{\eta}_s,
\label{eq:eta}
\ee we obtain that \be \frac{d \hat{H}_s}{ds} = \hat{\eta}_s \hat{H}_s
- \hat{H}_s \hat{\eta}_s = \left[\hat{\eta}_s, \hat{H}_s \right].
\label{eq:flowEquations}
\ee This is the key expression of the SRG method, describing the flow
of the Hamiltonian.  The specific unitary transformation is determined
by the choice of $\hat{\eta}_s$.  Through different choices of
$\hat{\eta}_s$, the SRG evolution can be adapted to the features of a
particular problem.\\

\paragraph*{In-medium SRG}

One possibility to solve the flow equations is to choose a basis with
respect to the physical vacuum state, set up the Hamiltonian matrix in
this basis and solve Eq.~(\ref{eq:flowEquations}) as a set of coupled
first-order differential equations. However, since the size of the
problem grows enormously with the number of particles and the size of
the model space, the applicability of this free-space SRG method is
restricted to comparatively small systems.

Instead of performing SRG in free space, the evolution can be done at
finite density, i.e.~directly in the A-body system
\cite{kehrein2006flow}. This approach has recently been applied very
successfully in nuclear physics \cite{IMSRG,PhysRevLett.106.222502}
and is called in-medium SRG (IM-SRG). The method allows the evolution
of $3,...,A$-body operators using only two-body machinery, with the
simplifications arising from the use of normal-ordering with respect
to a reference state.

In our case, we assume that the problem can be modelled by a
Hamiltonian containing maximally two-body interactions. In
second-quantized form, this one is given by
\begin{align}
\hat{H} & = \sum\limits_{pq}\left\langle p \right| \hat{h}^{(0)}
\left| q \right\rangle a_p\da a_q + \frac{1}{4}\sum\limits_{pqrs}\lla
pq || r s \rra a_p\da a_q\da a_s a_r,
\label{eq:ourHamiltonian}
\end{align} 
where the operator $\hat{h}^{(0)}$ denotes the single-particle
Hamiltonian, and the elements $\langle pq||rs\rangle$ are the
anti-symmetrized two-body matrix elements.  Normal-ordering with
respect to a reference state $|\Phi_0\rangle$ yields
\begin{align*}
\hat{H} &= E_0 + \sum\limits_{pq}f_{pq}\llb a_p\da a_q\rrb +
\frac{1}{4}\sum\limits_{pqrs}v_{pqrs} \llb a_p\da a_q\da a_s a_r \rrb,
\end{align*}
with Fock matrix elements
\[
f_{pq} = \lla p \right|\hat{h}^{(0)}\left| q \rra + \sum\limits_{i}
\lla pi || qi\rra,
\]
and where $v_{pqrs} = \lla pq || r s \rra$ are the amplitudes of the
two-body operator.  Here and in the following, indices $i,j,k,...$
denote hole states below the Fermi level, indices $a,b,c,...$
particles states above the Fermi level, and indices $ p,q,r,...$ can
be used for both particle and hole states. As reference state
$|\Phi_0\rangle$ we choose the ground state of the non-interacting
system, where all single-particle orbitals below the Fermi level are
occupied.

Integrating the flow equations~(\ref{eq:flowEquations}), we face one
of the major challenges of the SRG method, namely the generation of
higher and higher order interaction terms during the flow. With each
evaluation of the commutator, the Hamiltonian gains terms of higher
order, and these induced contributions will in subsequent integration
steps contribute to terms of lower order. In principle, this continues
to infinity.\\ To make the method computationally possible, we have to
close the IM-SRG flow equations, suggesting that we are forced to
truncate the equations to a certain order. We choose to truncate both
$\hat{H}_s$ and $\hat{\eta}_s$ at the two-body level, an approach
which is referred to as IM-SRG(2).  This normal-ordered two-body
approximation seems to be sufficient in many cases and has yielded
excellent results for several nuclei
\cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.\\ The
commutator in the flow equations (\ref{eq:flowEquations}) guarantees
that the IM-SRG wave function $U_s^\dagger|\Phi\rangle$ can be
expanded in terms of linked diagrams only
\cite{shavitt2009many,ISI:A1981MN73700014}, which suggests that IM-SRG
is size-extensive. Regarding the quality of the SRG results, it means
that the error introduced by truncating the many-body expansions
scales linearly with the number of particles~$N$.\\ With this
truncation, the generator $\hat{\eta}$ can be written as
\[
\hat{\eta} = \sum_{pq} \eta_{pq}^{(1)} \llb a_p\da a_q\rrb +
\frac{1}{4}\sum\limits_{pqrs}\eta_{pqrs}^{(2)} \llb a_p\da a_q\da a_s
a_r \rrb,
\]
where $\eta_{pq}^{(1)}$ and $ \eta_{pqrs}^{(2)}$ are the one- and
two-body elements, respectively. Making use of the permutation
operator $ \hat{P}_{pq}f(p,q) = f(q,p)$, the IM-SRG(2) flow equations
are given by
\begin{widetext}
\begin{align}
\frac{d E_0}{ds} &= \sum_{ia}\left( \eta_{ia}^{(1)}f_{ai} -
\eta_{ai}^{(1)}f_{ia}\right) +
\frac{1}{2}\sum_{ijab}\eta_{ijab}^{(2)}v_{abij},
\label{eq:flow1}\\
\frac{d f_{pq}}{ds}&= \sum_r \lb \eta_{pr}^{(1)}f_{rq} +
\eta_{qr}^{(1)}f_{rp}\right) + \sum_{ia}\lb 1-\hat{P}_{ia}\rb \lb
\eta_{ia}^{(1)}v_{apiq} - f_{ia}\eta_{apiq}^{(2)} \rb \notag \\ &
+\frac{1}{2} \sum_{aij} \lb 1+\hat{P}_{pq}\rb
\eta_{apij}^{(2)}v_{ijaq} + \frac{1}{2}\sum_{abi}\lb 1+\hat{P}_{pq}\rb
\eta_{ipab}^{(2)}v_{abiq},
\label{eq:flow2}
\end{align}
\begin{align}
\frac{d v_{pqrs}}{ds} &= \sum_t \lb 1-\hat{P}_{pq} \rb \lb
\eta_{pt}^{(1)}v_{tqrs}-f_{pt}\eta_{tqrs}^{(2)}\rb -\sum_t \lb
1-\hat{P}_{rs} \rb \lb \eta_{tr}^{(1)} v_{pqts} - f_{tr}
\eta_{pqts}^{(2)}\rb \notag \\ & +\frac{1}{2}\sum_{ab}
\lb\eta_{pqab}^{(2)} v_{abrs} - v_{pqab}\eta_{abrs}^{(2)}\rb -
\frac{1}{2}\sum_{ij} \lb\eta_{pqij}^{(2)} v_{ijrs} -
v_{pqij}\eta_{ijrs}^{(2)}\rb \notag \\ & -\sum_{ia} \lb 1-
\hat{P}_{ia} \rb \lb 1-\hat{P}_{pq}\rb \lb 1-\hat{P}_{rs} \rb
\eta_{aqis}^{(2)}v_{ipar}.
\label{eq:flow3}
\end{align}
\end{widetext}
Note that for brevity, we skip all $s$-dependence in the equations.

\subsubsection*{Choice of generator}
To determine the specific unitary transformation, one needs to specify
the generator~$\hat{\eta}$. Through different choices, the SRG flow
can be adapted to the features of a particular problem.\\

\paragraph*{Wegner's canonical generator}
The original choice, suggested by Wegner \cite{PhysRepWegner0}, reads
\be \hat{\eta} = \left[ \Hd, \Ho \right] = \left[ \Hd, \hat{H}
  \right].
\label{eq:etaWegner}
\ee As commutator between two Hermitian operators, $\hat{\eta}$
fulfils the criterion of antihermiticity and can be shown to suppress
the off-diagonal matrix elements \cite{kehrein2006flow}. In general,
matrix elements far off the diagonal, where the Hamiltonian connects
states with large energy differences, are suppressed much faster than
elements closer to the diagonal. \\ Evaluating the commutator, we get
for the one- and two-body elements
\begin{align*}
\eta_{pq}^{(1)} = & \sum_{r}\lb f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \rb
+ f_{pq} v_{qppq}^d \lb n_q - n_p \rb \\ \eta_{pqrs}^{(2)} = & -
\sum_t \left\lbrace \lb 1-\hat{P}_{pq} \rb f_{pt} v_{tqrs}^d - \lb 1 -
\hat{P}_{rs} \rb f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t
\left\llb \lb 1 - \hat{P}_{pq} \rb f_{pt}^d v_{tqrs} - \lb 1 -
\hat{P}_{rs} \rb f_{tr}^d v_{pqts} \right\rrb \notag \\ & +
\frac{1}{2} \sum_{tu} (1 - n_t - n_u) \lb v_{pqtu}^d v_{turs} -
v_{pqtu} v_{turs}^d \rb \notag \\ & + \sum_{tu} \lb n_t - n_u \rb \lb
1 - \hat{P}_{pq} \rb \lb 1 - \hat{P}_{rs} \rb v_{tpur}^d v_{uqts},
\end{align*}
where we use the standard notation
\[
n_p = \begin{cases} 1, & \mbox{if } p< \epsilon_F \quad(p\;\mbox{is
    hole state})\\ 0, &\mbox{if } p> \epsilon_F \quad(p\;\mbox{is
    particle state})\\
\end{cases}.
\]

\paragraph*{White's generator}
Apart from this canonical generator, there exist several other ones in
literature. One of them is White's choice
\cite{White:cond-mat0201346}, which makes numerical approaches much
more efficient.  The problem with Wegner's generator are the widely
varying decaying speeds of the elements, removing first terms with
large energy differences and then subsequently those ones with smaller
energy separations.  That way the flow equations become a stiff set of
coupled differential equations, which often gets numerically
unstable.\\ White takes an alternative approach, which is especially
suited for problems where one is interested in the ground state of a
system. Instead of driving all off-diagonal elements of the
Hamiltonian to zero, he focuses solely on those ones that are
connected to the reference state $|\Phi_0\rangle$, aiming to decouple
the reference state from the remaining Hamiltonian. With a suitable
transformation, the elements get similar decaying speeds, which solves
the problem of stiffness of the flow equations.  The generator is
explicitly constructed the following way
\cite{PhysRevLett.106.222502,White:cond-mat0201346}
\begin{align}
\hat{\eta} &= \sum_{ai} \frac{f_{ai}}{f_a-f_i-v_{aiai}}\lbrace a_a\da a_i\rbrace -\text{hc} \notag \\ & + \sum_{abij}
\frac{v_{abij}}{f_a+f_b-f_i-f_j+A_{abij}}\lbrace a_a\da a_b\da a_j
a_i\rbrace - \text{hc},
\label{eq:WhiteFull}
\end{align}
with $f_p \equiv f_{pp}$, 'hc' denoting the Hermitian conjugate, and
\[
A_{abij} = v_{abab} + v_{ijij} - v_{aiai} - v_{ajaj} - v_{bibi} -
v_{bjbj}.
\label{eq:White7}
\]
Compared to Wegner's canonical generator, where the final flow
equations involve third order powers of the $f$- and $v$-elements,
these elements contribute only linearly with White's generator, which
results in much better numerical properties.

We may attempt follow the same technique as for Hartree-Fock and reduce the
operator problem into a linear algebra problem by evaluating the operator
using a single-particle basis.  However, since a commutator between two-body
operators can result in a three-body operator, it follows that as $s$
increases, the evolved Hamiltonian $\tilde H(s)$ can gain terms that couple
more and more particles.  It is not practical to keep all such terms,
especially since higher-body operators are much more computationally
expensive.

In-medium SRG follows the same procedure as with ordinary SRG, but the
calculations are performed relative to some reference state rather than the
vacuum state.  This is advantageous for systems with many-particles as the
effect of truncation is not quite as drastic as it would be in SRG
[[true/false?]].

[[need some more content before diving straight into the algebra]]

Normal-ordering is a syntactic operation that reorders a product of operators
so as to eliminate all but the highest-body interaction.  The operation is
must be defined against a fixed many-body state, such as the vacuum state.  We
denote normal ordering using $\mathopen: \ldots \mathclose:$, with with the
state given by context.

\textit{Normal-ordering with respect to the vacuum state} is performed by
rearranging the operator product such that every $\hat a^\dagger$ appear
before $\hat a$, with the caveat that the parity of the permutation must also
be applied to the sign of the result.

For many-body problems involving large number of particles, the vacuum state
is not very convenient as it requires the application of many creation
operators to reach the states of interest.  Therefore, it is preferable to
utilize some reference state $\Phi$ (a Slater determinant) so that any other
state can be readily expressed as some excitation from this state.

Given a reference state $\Phi$, we may define a set of \textit{quasiparticle
  creation and annihilation operators} $\hat b^\dagger$ and $\hat b$ that obey
the same commutation relations as the $\hat a$ operators.  The two sets of
operators are related by:
\begin{align*}
  \hat b_p^\dagger \equiv \begin{cases}
    \hat a_p^\dagger & \text{if $p$ is unoccupied in $\Phi$} \\
    \hat a_p^{} & \text{if $p$ is occupied in $\Phi$}
  \end{cases}
\end{align*}
Analogously, there is a similar notion of normal-ordering with respect to the
reference state: namely, the rearrangement operators such that every
$\hat b^\dagger$ appears before $\hat b$.

The relationship between the $\hat b$ operators and $\Phi$ is completely
analogous to the relationship between the $\hat a$ operators and $0$.  As a
result, theorems governing these operators can be applied to both.  In
particular, \textit{Wick's theorem} -- an algebraic theorem that allows
complicated strings of creation and annihilation operators to be simplified
algorithmically -- plays an important role in simplifying the equations of
IM-SRG.

For conciseness, we introduce the notation $\hat A_{q_1,\dots,q_k}^\dagger$ to
denote the normal-ordered string of creation operators
$\hat a_{p_1}^\dagger \dots \hat a_{p_k}^\dagger$, and similarly for
$\hat B^\dagger$ as well as their annihilation counterparts.  Note that this
implies that the ordering is reversed in the annihilation version of this
notation.

[[...]]

For our purposes, we restrict ourselves to at most two-body operators, and
thus any higher-body operators that emerge from the commutator are neglected.
In this approximation, the method is known as ``IMSRG (2)''.  The loss of
three-body and higher terms one of the two sources of error in this method,
the other being the basis truncation.

The heart of the method lies in the choice of the generator $\eta(s)$.  We
would like to choose the generator such that as $s \to \infty$ the transformed
Hamiltonian $\tilde H(s)$ approaches either a diagonal, block-diagonal, or
band-diagonal form, all of which reduce the amount of effort needed to solve
the problem.  For our problem, we choose to decouple the ground state from all
the excited states in the Hamiltonian matrix using a carefully chosen
generator.  Doing so allows us to readily recover the ground state energy.

There are two commonly used generators: the Wegner generator and the White
generator.  The Wegner generator has been known since the introduction of the
SRG method by Wegner\cite{PhysRepWegner0} and has a particularly simple form:
\begin{align*}
  \hat \eta^{\text{g}}(s) \equiv [\hat H^{\text d}(s), \hat H(s)]
\end{align*}
where $\hat H^{\text d}$ denotes the diagonal component of $\hat H$.  Despite
its apparently simplicity, it does not work particularly well in practice as
the off-diagonal elements vanish at vastly different rates, leading to
differential equations that are typically stiff.

The White generator remedies this problem by introducing denominators for each
term to control and normalize the rate at which off-diagonal elements vanish:
\begin{align*}
  \hat \eta^{\text{h}}(s) \equiv
  \sum_{\substack{a \\ p_1, \ldots, p_a \\ q_1, \ldots, q_a}}
  \frac{
  \langle \Phi_{p_1, \ldots, p_a} | \hat H^{[a]} | \Phi_{q_1, \ldots, q_a} \rangle
  \hat B_{p_1, \ldots, p_a}^\dagger \hat B_{q_1, \ldots, q_a}^{}
  }{E_{p_1, \ldots, p_a} - E_{q_1, \ldots, q_a}}
\end{align*}
where [[note: haven't explained what $\hat b$ means]]
\begin{align*}
  E_{p_1, \ldots, p_a} &\equiv
  \langle \Phi_{p_1, \ldots, p_a} | \hat H | \Phi_{p_1, \ldots, p_a} \rangle \\
  \hat B_{p_1, \ldots, p_a}^\dagger &\equiv
  \hat b_{p_1}^\dagger \cdots \hat b_{p_a}^\dagger
\end{align*}
and $\hat H^{[a]}$ denotes the $a$-body term of the Hamiltonian.  As a result
of this modification, the White generator exhibits better numerical stability
and is computationally less expensive than the Wegner generator.

An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
In particular, the solver must be able to handle the stiffness that can often
arise (even in the case of White generator).  For this, we use an accurate,
high-order ODE solver implementation by Shampine and Gordon that uses the
Adams predictor-corrector formulas [[Ref: Shampine and Gordon book]].

[[...]]

\begin{figure}
\includegraphics[width=.48\textwidth]{fig-diagrams-imsrg}
\caption{Diagrammatic form of $\hat C(\circ, \bullet)$.}
\label{fig:diagrams-imsrg}
\end{figure}
Expanding the commutator leads to the expression
\begin{align*}
  [\hat \eta, \hat H] = \hat C(\hat \eta, \hat H) - \hat C(\hat H, \hat \eta)
\end{align*}
where $\hat C$ is defined diagrammatically in Figure \ref{fig:diagrams-imsrg}.
For IM-SRG(2), we truncate the commutator to a two-body operator, neglecting
the three-body term.

\subsection{The self-energy correction}
\label{subsec:selfenergy}

IM-SRG, in the form described, does not provide a means to obtain ground state
energies of open-shell systems.  While there exists a multi-reference IM-SRG
that can handle the general problem ([[cite Heiko?]]), we opted to use a much
simpler approach to obtain the addition and removal energies: quasidegenerate
perturbation theory (QDPT).  In QDPT, the solutions of the approximate
Hamiltonian $\hat H^{\text o}$ are used as the basis of the model space.  One
then assumes the existence of an operator $\hat \Omega$, known as the
\textit{wave operator}, that maps some set of states $\tilde \Phi_u$ within
the model space to the exact ground state $\Psi_u$:
\begin{align} \label{eq:omega-condition1}
  \Psi_u = \hat \Omega \tilde \Phi_u
\end{align}
The states $\tilde \Phi_u$ consist of some mixture of the eigenstates
$\Phi_{u'}$ of the approximate Hamiltonian $\hat H^{\text o}$.

There is some freedom in the choice of the wave operator $\hat \Omega$.  We
assume it has the following form:
\begin{align} \label{eq:omega-condition2}
  \hat \Omega = \hat P + \hat Q \hat \Omega \hat P
\end{align}
where $\hat P$ projects any state into the model space and $\hat Q$ is the
complement of $\hat P$.  This entails that the exact states $\Psi_u$ is no
longer normalized but instead satisfies the typical intermediate
normalization: $\langle \Psi_u | \tilde \Phi_u \rangle = 1$.

Making use of the assumptions in Eq.\ \eqref{eq:omega-condition1} and
\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation
the generalized Bloch equation, the main equation of QDPT:
\begin{gather*}
  [\hat \Omega, \hat H^{\text o}] =
  (1 - \hat \Omega) \hat V \Omega
\end{gather*}
where $\hat V \equiv \hat H - \hat H^{\text o}$ is the perturbation.  The
commutator on the left may be ``inverted'' using the resolvent approach
[[ShavittBartlett,p.50]], resulting in:
\begin{align*}
  \hat Q \Omega \hat P_u =
  \hat R_u (1 - \hat \Omega) \hat V \Omega \hat P_u
\end{align*}
where
$\hat R_u \equiv \hat Q (E_u - \hat Q \hat H^{\text o} \hat Q)^{-1} \hat Q$ is
the resolvent and $\hat P_u$ projects any state onto $\Phi_u$.  As is typical
in perturbation theory, we assume $\hat \Omega$ can be expanded as a series of
the increasing order as measured by the ``power'' of the perturbation
$\hat V$:
\begin{align*}
  \hat \Omega = \hat P +
  \hat Q\bigl(\hat \Omega_1 + \hat \Omega_2 + \cdots\bigr) \hat P
\end{align*}
This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$
to be calculated up to any order, as least in theory.  Here, we show
$\hat \Omega$ up to third order: [[double-check]]
\begin{align*}
  &\hat \Omega_1 \hat P_u = \hat R_u \hat V \hat P_u \\
  &\hat \Omega_2 \hat P_u =
    \hat R_u \biggl(
    \hat V \hat R_u
    - \sum_v \hat R_v \hat V \hat P_v
    \biggr) \hat V \hat P_u \\
  &\hat \Omega_3 \hat P_u =
    \hat R_u \biggl(
    \hat V \hat R_u \hat V \hat R_u
    - \hat V \hat R_u \sum_v \hat R_v \hat V \hat P_v \\
  &\qquad\qquad
    - \sum_v \hat R_v \hat V \hat P_v \hat V \hat R_u
    - \sum_v \hat R_v \hat V \hat R_v \hat V \hat P_v \\
  &\qquad\qquad
    + \sum_v \hat R_v \sum_w \hat R_w \hat V \hat P_w \hat V \hat P_v
    \biggr) \hat V \hat P_u
\end{align*}

[[Since the systems are all closed-shell, the
diagonal approximation can be used here to simplify the calculations.]]

\begin{figure}
\includegraphics[width=.48\textwidth]{fig-diagrams-sfe}
\caption{Diagrammatic form of the second- and third-order self-energy
  corrections.}
\label{fig:diagrams-sfe}
\end{figure}
[[Discuss how]]
The diagrams for each order of correction can be evaluated using algebraic or
diagrammatic techniques.  The second-order correction is given by
\begin{gather*}
  \epsilon_p = \frac{1}{2} \biggl(
      \sum_{i a b} \frac{|V_{p i a b}|^2}{f_p + f_i - f_a - f_b}
    - \sum_{i j a} \frac{|V_{i j p a}|^2}{f_i + f_j - f_p - f_a}
  \biggr)
\end{gather*}
and depicted in Figure \ref{fig:diagrams-sfe}.  Since there are numerous terms in
the third-order correction, they are simply listed in a diagrammatic form in
Figure \ref{fig:diagrams-sfe}.

[[...]]

\subsection{Diffusion Monte Carlo}

Diffusion Monte Carlo (DMC) is a method for calculating the ground state
properties via a stochastic process akin to classical diffusion, refining an
approximate ground state density towards that of the exact ground state.  The
rules that govern the diffusion process are obtained by evolving the wave
function using what can be formally be thought of as the time-dependent
Schr\"odinger equation along imaginary time $t = \mathrm i \tau$:
\begin{align} \label{eq:itse}
  \frac{\partial}{\partial \tau} |\Phi(\tau)\rangle = \hat H |\Phi(\tau)\rangle
\end{align}
The solutions to this equation are not unlike the ordinary Schr\"odinger
equation with a slight but crucial difference in the exponent:
\begin{align*}
  |\Phi(\tau)\rangle = \mathrm e^{-\hat H \tau} |\Phi(0)\rangle
\end{align*}
where $|\Phi(0)\rangle$ is the initial wave function at $\tau = 0$ -- not to
be confused with the exact ground state of $\hat H$, which we denote
$|\Psi_0\rangle$ here.  If we decompose the wave function into a sum over the
eigenstates $|\Psi_n\rangle$,
\begin{align*}
  |\Psi(\tau)\rangle
  = \mathrm e^{-\hat H \tau} \sum_n c_n |\Psi_n\rangle
  = \sum_n c_n \mathrm e^{-E_n \tau} |\Psi_n\rangle
\end{align*}
we find that components of the wave function that have negative energy will
increase exponentially as $\tau \to \infty$, while those with positive energy
will decrease exponentially.  This property can be exploited to filter out the
undesirable components, leaving only the ground state energy.  To do this, we
require a trial energy $E_{\text{T}}$ -- a guess of the ground state energy --
and replace $\hat H$ in \eqref{eq:itse} with $(\hat H - E_{\text{T}})$ so
that, if our trial energy is good, all states but the ground states will
approximately vanish.

Diffusion Monte-Carlo (DMC) is a method used for refining a crude estimate to the ground state density into a better approximation to the exact ground state. The basic idea is to move multiple random walkers in position space with sampling rules which ensures convergence to a behavior representing a walk guided by the exact ground state density. Once a satisfying level of convergence is reached, expectation values are calculated by accumulating local estimates along the path of the walkers.

The equations representing the DMC algorithm is obtained by applying the projection operator $\OP{P}(\tau)$ on the crude trial state $\ket{\Psi_T}$
\begin{equation}
 \OP{P}(\tau)\ket{\Psi_T} \equiv \exp\left({-(\OP{H} - E_0)\tau}\right)\ket{\Psi_T} 
\end{equation}
\noindent
where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\OP{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\OP{H}$. By expanding the trial state in the eigenfunctions of $\OP{H}$, the ground state is obtained up to a constant factor

\begin{equation}
 \label{eq:DMC_ExactProjection}
 \lim_{\tau\to\infty} \bra{\mathbf{r}}  \OP{P}(\tau) \ket{\Psi_T} = \braket{\Psi_0}{\Psi_T}\Psi_0(\mathbf{r}).
\end{equation}

Defining $\Phi(\mathbf{r}, \tau) \equiv \bra{\mathbf{r}}\OP{P}(\tau)\ket{\Psi_T}$, we obtain the state at a later time $\tau + \delta\tau$ through projection

\begin{align}
 \Phi(\mathbf{r}, \tau + \delta\tau) &= \bra{\mathbf{r}} P(\tau + \delta\tau) \ket{\Psi_T} \notag\\
 &= \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right) \OP{P}(\tau) \ket{\Psi_T} \notag\\
 &= \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
 &= \int \mathrm{d}\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
 &\equiv \int \mathrm{d}\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
\end{align}

In practice, the ground state energy is a priori unknown, hence a trailing averaged value obtained from the converging DMC density is used. This energy is often referred to as the trial energy, and it is believed that with a sufficiently good trial state, the error due to this approximation is small.

The Green's function introduced in Eq.~(\ref{eq:DMC_GreenFuncRevealed}) has singularities due to the the Coulomb interaction term in $\OP{H}$. Due to Pauli exclusion these are not physical, nevertheless, in numerical implementations they are unpredictable and undesirable, hence we want to avoid them.

For evaluation of the local energy, the trial state is designed to cancel the Coulomb singularities by containing so-called correlation factors, however, this cancellation does not apply to the terms in the Green's function. In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\mathbf{r}, \tau) \equiv \Phi(\mathbf{r}, \tau)\Psi_T(\mathbf{r})$. Note that all previous arguments regarding convergence to the true ground state still applies for the new distribution.

Methods exist for transforming the mixed density into the pure density $|\Phi(\mathbf{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.

Additionally, to avoid issues regarding the positive definiteness of the mixed distribution, the nodes of the mixed density is fixed to those of the wave function of the trial state. This is known as the \textit{fixed node approximation} \cite{umrigar:2865, abInitioMC}. Again, given a sufficiently good trial state, the errors should be small.

The Green's function for the mixed density is given as \cite{umrigar:2865}

\begin{align}
  G(\mathbf{r}, \mathbf{r}'; \delta\tau)_f &= \bra{\mathbf{r}} \exp\left({\frac{1}{2}\nabla\cdot \left[\left(\nabla - \mathbf{F}(\mathbf{r})\right)\right] - \left(E_L(\mathbf{r}) - E_T\right)}\right)\ket{\mathbf{r}'} \label{eq:DMC_IS_GF_raw}\\
  &\propto e^{-\left[|\mathbf{r} - \mathbf{r}' - \frac{1}{2}\delta\tau\mathbf{F}(\mathbf{r})|^2/2\delta\tau\right]} \label{eq:DMC_IS_GF}\\
  &\qquad\times e^{-\left[\frac{1}{2}\left[E_L(\mathbf{r'}) + E_L(\mathbf{r})\right] - E_T\right]\delta\tau} + \mathcal{O}(\delta\tau^2), \notag
\end{align}
where 
\begin{equation}
  \mathbf{F}(\mathbf{r}) = 2\Psi_T(\mathbf{r})^{-1} \nabla \Psi_T(\mathbf{r})
\end{equation}

\noindent
is the drift vector commonly referred to as the \textit{quantum force}.

The local energy 
\begin{equation} 
E_L(\mathbf{r}) = \Psi_T(\mathbf{r})^{-1}\OP{H} \Psi_T(\mathbf{r})
\end{equation} 
is necessarily sampled from $|\Psi_T(\mathbf{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_T(\mathbf{r})$.

The Green's function from Eq.~(\ref{DMC_IS_GF_raw}) has been split into two for practical reasons; one part containing the kinetic terms, more specifically this represents a Fokker-Planck diffusion process, and a second part which is commonly referred to as a \textit{branching function}, which is an effective reweighing of a positions contribution to the overall density. Excluding branching we will simply sample from the density of the trial state.

In order dampen the errors introduced by splitting the Green's function, the time step $\delta\tau$ should be small. A value in the range of $10^{-3}$ to $10^{-4}$ is used in this work. High variance in energy samples requires a smaller time step to keep the branching controlled, since the fluctuations of the two are connected by Eq.~(\ref{eq:DMC_IS_GF}).

The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of Eq.~(\ref{eq:DMC_IS_GF}). Let $G_b$ denote the value of the branching function at a given position. Correct weighting is then ensured by guaranteeing $m = \max\left(\mathrm{floor}\left(G_b\right)-1, 0\right)$ branches with a probability $G_b - m$ of getting an additional branch. A branch is an identical copy of the corresponding walker, with an identical past but with a different future. When the number of requested branches is zero, the walker is removed from the simulation.

Initially, $N_w$ walkers are initialized to span $|\Psi_T(\mathbf{r})|^2$. This is ensured by using the Metropolis Algorithm. Moreover, importance sampling is ensured by sampling according to the kinetic term of  Eq.~(\ref{eq:DMC_IS_GF_raw}) \textit{cite solution langevin}

\begin{equation}
x_{i+1} = x_i + \frac{1}{2}\delta\tau F(\mathbf{r})_x + \xi,
\end{equation}
\noindent
where $\xi$ is a uniform distributed random number with variance $\mathrm{Var}(\xi) = 2D\delta\tau$. A typical value of $N_w$ in this work is 250 000.

For each time step, diffusion and branching repeats a given number of blocks $N_b$ for each walker. New branches are not active until the next time step, and if a walker hits zero branches the block repetition stops. During these block loops, the trial energy $E_T$ is sampled for use in the next time step $k+1$

\begin{equation}
 E_T^{k+1} = \frac{1}{M^{(k)}}\sum_{i=1}^{M^{(k)}} G_b(\mathbf{r}^{(k)}_i)E_L(\mathbf{r}^{(k)}_i),
\end{equation}
\noindent
where $M^{(k)}$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_b = 100$ to be sufficient.

Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_c$ trial energies calculated after $N_t$ thermalization cycles 
\begin{equation}
 E_0 = \frac{1}{N_c-N_t}\sum\limits_{k=N_t}^{N_c} E_T^{(k)}.
\end{equation}
This is the relation we use in this work to obtain the DMC energies.

In this work, the trial state has been chosen to consist of a single Slater determinant (cite) 
together with a single variational parameter Padé-Jastrow correlation function (cite).

The Slater determinant contains eigenstates $\phi_n(\mathbf{r})$ of Eq.~(\ref{eq:potential})
with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$ 
such that $\omega\to\alpha\omega$ in all solutions:

\begin{equation}
 \phi_n(\mathbf{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\exp(-\alpha\omega r^2),
\end{equation}

\noindent
where $H_n$ is the $n$'th level Hermite polynomial.

The eigenstates are selected such that the $N$ lowest lying energy eigenstates are selected (counting spin-degeneracy). Due to the Hamiltonian being spin independent we may split the Slater determinant into two equal parts - 
one for each spin level (cite). The overall form of the trial state is as follows:

\begin{equation}
 \Psi_T(\mathbf{r}) = S(\mathbf{r}^\uparrow) S(\mathbf{r}^\downarrow) \prod_{i<j}^{N} J(r_{ij}),
\end{equation}

with

\begin{equation}
 S(\mathbf{r}^s) =  \left| \begin{array}{cccc}
\phi_1(\mathbf{r}^s_1) & \phi_2(\mathbf{r}^s_1)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_1) \\
\phi_1(\mathbf{r}^s_2) & \phi_2(\mathbf{r}^s_2)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_2) \\
\vdots & \vdots& \ddots & \vdots \\
\phi_1(\mathbf{r}^s_\frac{N}{2}) & \phi_2(\mathbf{r}^s_\frac{N}{2})& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_\frac{N}{2}) \\
 \end{array} \right|,
\end{equation}

and

\begin{equation}
 J(r_{ij}) = \exp\left(\frac{r_{ij}}{1 + \beta r_{ij}}\right),
\end{equation}

where $\mathbf{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons. 
Since Metropolis Monte-Carlo only involves ratios of density functions, all normalization factors are skipped.

As a consequence of the variational principle, the optimal numeric values for $\alpha$ and $\beta$ can be found by minimizing the energy in the variational parameter space.
For this we have used the adaptive step gradient descent method (cite ASGD).

Using a single Slater determinant and a single variational parameter in the correlation function might at first glance seem insufficient,
however, the strength and robustness of DMC greatly succeeds at transforming this naive approximation into a very good estimate to the ground
state density. It should be mentioned that for systems where the single-particle Hamiltonian does not have analytical solutions, this approach
will indeed be insufficient due to low overlap between the initial and exact state.

A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the CPU-time of most calculations.
We refer to Refs (cite optimization techniques) for more information. 
Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once
for the entire calculation. This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is 
preserved under differentiation.

\section{Results}
\label{sec:results}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=6$ and $\omega=1.0$ ]{
            \label{fig:N6hw1}
            \includegraphics[width=0.38\textwidth]{figures/6parthw1.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.5$ ]{
           \label{fig:N6hw05}
           \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=6$ and $\omega=0.28$ ]{
            \label{fig:N6hw028}
            \includegraphics[width=0.38\textwidth]{figures/6parthw028.pdf}
        }
        \subfigure[Results for $N=6$ and $\omega=0.1$ ]{
            \label{fig:N6hw01}
            \includegraphics[width=0.38\textwidth]{figures/6parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=6$ and $\omega=1.0$
       The results are compared with diffusion Monte Carlo (DMC),
      coupled cluster at the level of singles and doubles (CCSD), full
      configuration interaction (FCI) and Hartree-Fock calculations
      (HF) as functions of the number of major oscillator shells
      $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N6}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=12$ and $\omega=1.0$ ]{
            \label{fig:N12hw1}
            \includegraphics[width=0.38\textwidth]{figures/12parthw1.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.5$ ]{
           \label{fig:N12hw05}
           \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[Results for $N=12$ and $\omega=0.28$ ]{
            \label{fig:N12hw028}
            \includegraphics[width=0.38\textwidth]{figures/12parthw028.pdf}
        }
        \subfigure[Results for $N=12$ and $\omega=0.1$ ]{
            \label{fig:N12hw01}
            \includegraphics[width=0.38\textwidth]{figures/12parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=12$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N12}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=20$ and $\omega=1.0$ ]{
            \label{fig:N20hw1}
            \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.5$ ]{
           \label{fig:N20hw05}
           \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=20$ and $\omega=0.28$ ]{
            \label{fig:N20hw028}
            \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
        } \subfigure[Results for $N=20$ and $\omega=0.1$ ]{
            \label{fig:N20hw01}
            \includegraphics[width=0.38\textwidth]{figures/20parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=20$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N20}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=30$ and $\omega=1.0$ ]{
            \label{fig:N30hw1}
            \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.5$ ]{
           \label{fig:N30hw05}
           \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=30$ and $\omega=0.28$ ]{
            \label{fig:N30hw028}
            \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
        } \subfigure[Results for $N=30$ and $\omega=0.1$ ]{
            \label{fig:N30hw01}
            \includegraphics[width=0.38\textwidth]{figures/30parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=30$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N30}
\end{figure}

\begin{figure}%[hbtp]
     \begin{center}
        \subfigure[Results for $N=42$ and $\omega=1.0$ ]{
            \label{fig:N42hw1}
            \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.5$ ]{
           \label{fig:N42hw05}
           \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
        }\\ % ------- End of the first row ----------------------%
        \subfigure[Results for $N=42$ and $\omega=0.28$ ]{
            \label{fig:N42hw028}
            \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
        } \subfigure[Results for $N=42$ and $\omega=0.1$ ]{
            \label{fig:N42hw01}
            \includegraphics[width=0.38\textwidth]{figures/42parthw01.pdf}
        }
    \end{center}
    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
      for circular quantum dots for $N=42$ and different values of
      $\omega$. The results are compared with diffusion Monte
      Carlo (DMC), coupled cluster at the level of singles and doubles
      (CCSD), full configuration interaction (FCI) and Hartree-Fock
      calculations (HF) as functions of the number of major oscillator
      shells $R$. A harmonic oscilaltor basis has been used, with an
      unrenormalized Coulomb repulsion and White's generator. All
      energies in atomic units.}
   \label{fig:N42}
\end{figure}

\begin{table}
\begin{center}
\caption{Ground state energy (in atomic units) of a circular quantum
  dot, with $N$ particles and oscillator frequency $\omega$. The
  IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$
  results which are for $R=18$), employing a Hartree-Fock basis, a
  bare Coulomb interaction and White's generator. For $N=42$ and
  $\omega=0.1$ results are presented up to $R=22$ major shells. The
  results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained
  using the extrapolation formula of Eq.().}
\label{tab:SRGDMC-R20}
\begin{tabular}{ccccc}
\hline\hline
$N$ & $\omega$ & IM-SRG(2) &IM-SRG(2)$_{R\rightarrow \infty}$ & DMC \\
\hline
6 & 1.0 & 20.1583 & 20.1468   & 20.1593(1) \\
& 0.5&11.7690  & 11.7631 &11.7848(1) \\
& 0.28& 7.5713 &   7.5695 &7.6002(1) \\
& 0.1& 3.4962  &  3.4977 &3.5539(1)\\
\hline
12&1.0 & 65.7280 & 65.6990  & 65.7001(1) \\
&0.5 &39.1631 &  39.1473 & 39.1596(1)\\
&  0.28&25.6212 &  25.6140& 25.6358(1)\\
&  0.1&12.2223 &  12.2234 & 12.2698(1)\\
\hline
20& 1.0&155.9737 & 155.9130  & 155.8822(1)\\
&  0.5&93.9219 &   93.8853 &93.8752(1)\\
&  0.28&61.94362 & 61.9240 &61.9268(1) \\
&  0.1&29.95263 &29.9565  & 29.9779(1)\\
\hline
30& 1.0& 308.7673 & 308.6053 & 308.5627(2) \\
 & 0.5& 187.1671& 186.8340 &187.0426(2)\\
 & 0.28&124.0410 & 123.7171 & 123.9683(2) \\
 & 0.1& 60.4319& 60.1158 & 60.4205(2)\\
\hline
42& 1.0&543.3398 & 543.3304 & 542.9428(8) \\
 & 0.5&330.8885 & 330.8425 & 330.6306(2)\\
 & 0.28&220.0226 & 219.9534y &219.8426(2) \\
 & 0.1& 107.7851&  106.8074& 107.6389(2)\\
 \hline
56& 1.0& 880.4159 &  & 879.3986(6) \\
 & 0.5& 538.8199 & & 537.353(2)\\
 & 0.28&360.83689  &  & 358.145(2) \\
\hline
\end{tabular}
\end{center}
\end{table}

In Figure \ref{fig:gs} we show the calculated ground state energies from
Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and
IMSRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a
dashed line in systems where it is known \cite{PhysRevB.84.115302}.

Both perturbation theory and IMSRG add corrections in addition to the
Hartree-Fock results to recover the correlation energy and they do quite well
in recovering the correlation energy in the system.  Compared with MPPT, IMSRG
generally converges faster, although does not always converge to the DMC
result.  Generally speaking, IMSRG is closer to the DMC result as the number
of particles increases.

There are a few cases where the IMSRG over-corrects the result, leading to a
ground state energy that is lower than the exact result.  This is not
unexpected given that, unlike Hartree-Fock, IMSRG is non-variational.  These
tend to occur when the number of particles is few, or the frequency is very
low (high correlation).  However, MPPT does not do much better in the high
frequency regimes as it often converges slower than IMSRG.

[[Q: should we discuss the absolute/relative correction plots?]]

For our addition and removal energy calculations, the results are summarized
in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.  The figures
show the the addition/removal energies for Hartree-Fock, combined with IM-SRG
and/or QDPT (Hartree-Fock is always included, as usual) [[better way to
explain this? the figure labels are somewhat misleading too]].  The DMC
results are also shown via dashed lines where they are known.

From these results, we see that the QDPT corrections add a substantial
contribution to the results of both Hartree-Fock with and without IM-SRG.
[[quantify ``substantial'' numerically]]

For the IM-SRG results, there is a small asymmetry between the behavior of our
removal and addition energies: we find that removal energies tend to be more
accurate and its behavior is relatively stable with respect to the number of
shells. [[why]]

Interestingly, the addition energy of Hartree-Fock with second-order QDPT
appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
This is likely coincidental, as the third-order QDPT dramatically worsens the
result.

Both Hartree-Fock and IM-SRG results worsen as the frequency decreases, which
is not unexpected since the correlations become much more dominant.  The
Hartree-Fock appears to perform much worse, however, as the results converge
much more slowly as the number of shells increases.

We also note that IM-SRG with 2 particles and frequency 0.1 generally fail to
give any result as the ODE solver eventually leads to divergence [[Why?]]
This seems to be a particular quirk associated with this specific system and
does not usually occur in other systems except in a few extreme, isolated
cases where there are far too few unoccupied states.

\section{Conclusions}
\label{sec:conclusions}

We demonstrated the use various many-body theories, Hartree-Fock method, M\o
eller-Plesset perturbation theory, IM-SRG, as well as quasidegenerate
perturbation theory to calculate ground state as well as addition and removal
energies of two-dimensional quantum dots.  We showed that these methods, when
combined, can give a good approximate description of the systems at moderate
cost compared to near-exact but much more expensive methods such as FCI and
DMC.

For ground state energy, we showed that the convergence of IM-SRG is generally
faster than that of MPPT, and the results are typically closer to the exact
results.  Similarly, we found that IM-SRG improves the rate of convergence of
the addition and removal energies, both as the order of perturbation theory
increases and as the number of shells increases.

There are several directions in which the calculations may be improved.  One
can attempt to improve the IM-SRG approximation by incorporating some of the
missing higher-body terms in the commutator.  This would also provide some
insight into the rate of convergence with respect to the operator truncation.
While some of the higher-body terms can be rather costly to compute --
rendering a full 3-body IM-SRG quite expensive -- certain additional
approximations may be made to alleviate this without incurring the full cost
of evolving 3-body operators [[Ref?]].

[[As noted earlier [[haven't written that yet]], the application of IM-SRG
removes a large portion of the QDPT diagrams, which is beneficial as it
increases the efficiency of the QDPT calculations.  However, many of these
diagrams can also be eliminated further through an infinite resummation scheme
[[Any good refs for this?]], which would further reduce the number of diagrams
in QDPT, especially those of lower order, whic would likely increase the
accuracy of the result.]]

It would also be useful to investigate how the results obtained with finite
number of shells in the basis are related to those obtained with an infinite
number of shells in the basis.  [[Ref: paper on IR/UV extrapolation]] With a
good theoretical foundation, a model of how the observables converge with
respect to the size of the basis may be used to extrapolate the results to
infinite-basis limit.  This would also enable us to perform cheaper
calculations with fewer shells and optimistically extrapolate results for
large systems that would be otherwise infeasible to compute.

We note that this calculation was done entirely using the traditional approach
of using a high-order ODE solver to solve the flow equation.  A new technique
developed by T. Morris [[Ref?]] uses an alternative approach that obviates the
need for a high-order ODE solver, leading to much more efficient computations
and also allowing operators of other observables to be evolved with greater
ease.  Implementing this approach would be beneficial as it would allows us to
study the accuracy and convergence of other observables beyond energy and
energy differences.

Implementation-wise, our current code constructs the two-particle basis as
simple Slater determinants without any angular momentum coupling.  This
approach is often referred to as \textit{m-scheme} in nuclear physics.  This
method is simple and works well for general systems, but it does not fully
exploit the circular symmetry present in the quantum dot system.  A more
efficient approach is to use angular momentum coupling to generate the
two-particle basis, which is known as \textit{j-scheme} in nuclear physics.
Combined with the symmetries of the Hamiltonian, this can significantly reduce
the amount of computation required in this system, albeit at the cost of
increasing the complexity of the implementation.

A more technical issue is its lack of parallelization: currently, the code
makes very little use of parallelism and therefore does not scale well on
modern clusters.  As the problem is not embarrassingly parallel, implementing
parallelism does introduce additional complications that must be considered.
Distributing the workload across multiple nodes can significantly reduce the
cost of the calculations, allowing larger systems to be studied.

\begin{acknowledgments}
 This work was supported by the 
National Science Foundation Grant No.~PHY-1404159 
(Michigan State University) and by the Research
Council of Norway under contract ISP-Fysikk/216699. 
\end{acknowledgments}

\bibliography{paper}
\bibliographystyle{apsrev4-1}
\end{document}

\documentclass[aps,twocolumn,showpacs,floatfix,nofootinbib,preprintnumbers,superscriptaddress,amsmath,amssymb]{revtex4-1}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{bm}
\usepackage{color}
\usepackage{float}
\usepackage{dcolumn}
\usepackage{subfigure}
\usepackage{multirow}

\section{Results}
\label{sec:results}
In this section, we discuss the IM-SRG results for the ground-state
energies of closed-shell systems. In subsection \ref{subsec:Wegner},
we start with Wegner's canonical generator. Numerical instabilities in
the integration process, as well as a rather slow convergence as
function of the number of oscillator shells, motivate the use of a
Hartree-Fock basis and the Coulomb interaction. Since higher
correlations still lead to stiff equation systems, we change in
subsection \ref{subsec:White} to White's generator. In particular, we
give an overview of the IM-SRG(2) ground state energies for
closed-shell systems up to $N=42$ particles and compare with other
\textit{ab initio} many-body methods.\\ In all our calculations, we
perform the integration of the flow equations using the algorithm
developed by Shampine and Gordon \cite{shampine1975computer}. This
algorithm solves linear systems of differential equations based on the
implicit Adams method, which is a multi-step method of variable
order. Source code is freely available \cite{odesolver}.

\section{Conclusions}
\label{sec:conclusions}
We have used IM-SRG to study the ground state energy of circular,
two-dimensional quantum dots up to $N=42$ particles. We utilized two
different generators, Wegner's and White's one, and realized that
Wegner's generator results in stiff equation systems, whereas White's
generator has much better numerics and is computationally more
efficient. Moreover, we found out that the use of an Hartree-Fock
basis improves numerical stability enormously, whereas analogous to
previous FCI \cite{Kvaalcode} and CCSD \cite{PhysRevB.84.115302}
calculations, the use of an effective interaction improves convergence
of the ground state energy as function of the number of oscillator
shells.  Our IM-SRG(2) results are in excellent agreement with other
many-body methods, in particular DMC, which can be considered as more
or less exact benchmark. For more than six particles, we lie in all
cases closer to the DMC result than corresponding CCSD calculations
do.

Until now, we have applied the SRG flow equations in m-scheme only. A
next step, which we are currently working on, is to perform the
calculations in j-scheme. This allows for further simplifications of
the flow equations, such that numerical calculations get even more
efficient.  Moreover, one aspect of great interest is to extend
IM-SRG(2) to IM-SRG(3), where all operators are truncated one a
three-body instead of a two-body level. A comparison of both results
would give insight into the significance of higher correlations and it
would allow to analyse the convergence behaviour of the IM-SRG
hierarchy of truncation. However, since this is expected to be
computationally highly expensive, a first alternative would be not to
look at the whole IM-SRG(3) evolution, but to restrict oneself just to
certain additional terms, in order to get an impression of how
important excitations beyond the IM-SRG(2) level are. Since we use an
initial two-body Hamiltonian, one particular possibility is not to
save the induced three-body interactions explicitly, but to include
their loop terms in the calculations for lower-body interaction
terms. Work along these lines is in progress.\\ Furthermore, we plan
to apply these improvements not only to quantum dots, but to extend
our studies to nuclear and/or atomic systems, which opens up an even
larger range of applications.

%
\begin{acknowledgments}
  We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for
  several discussions. This work was supported by the Research Council
  of Norway under contract ISP-Fysikk/216699. This research used
  computational resources of the Notur project in Norway.
\end{acknowledgments}

\bibliography{srg}
\bibliographystyle{apsrev4-1}

\end{document}

The Hilbert spaces MR and PR is much closer in dimensionality than MR and PNP R . We
will therefore assume that we can use the same error formula for the spaces MR and PR .
As we will see later, this formula seems to hold very well for the systems we are studying.
We will also assume that ν(R) is negligible and rewrite Eq. (5.7) on the form
∞
∆E ≈ b ∑ (NP + r) r−c , b ∈ R.
(5.10)
r=R+1
This assumption is justified by Kvaal’s [16] results. He has performed FCI calculations on
two dimensional quantum dots in the energy cut basis with 3, 4 and 5 particles, and for these
systems ν(R) is shown to be small. Also, since PR ⊂ MR , we expect ν(R) to decay even
faster in the direct product basis.
5.3
Extrapolation Formulas
We have used Eq. (5.10) to parametrize the energy as a function of the number of shells.
R
E(R) ≈ a − b ∑ (NP + r)r− c ,
(5.11)
r=1
where a, b, c are real constants. This formula has an error ∼ E(R)ν(R), and consequently
it will become more accurate as R increases and ν(R) becomes small. This means that we
ˆ ˆˆ
should avoid extrapolations with energies ⟨PR H PR ⟩ for small R.
We also want to find the extrapolated energy at R → ∞ given that we know the optimal
values of a, b, c. We notice that E(∞) can be written in terms of the Riemann zeta function
ζ(c) such that
lim E(R) ≈ a − b[NP ζ(c) + ζ(c − 1)],
R→∞
where ζ(c) = ∑∞ r−c , which is known to converge for all c > 1.
r=1
34

In this section, we will calculate a set of extrapolated energies and compare these to
Diffusion Monte Carlo (DMC) energies which are not affected by a basis incompleteness
error. We use the extrapolation formula Eq. (5.11)
R
E(R) ≈ a − b ∑ (N + r)r−c ,
(25.1)
r=1
where N is the number of particles, R + 1 is the number of shells and a, b, c ∈ R are
constants. A curve fit of the FCIQMC values to E(R) yields the optimal parameters a, b, c.
The extrapolated energy is taken at the limit R → ∞, and the error is estimated using Eqs.
(13.18) and (13.22) assuming that Eq. (25.1) is exact.
As we discussed earlier, the extrapolation formula has an uncontrolled error ∝ ν(R)
where ν(R) is an unknown function. ν(R) is however assumed to fall off quickly as a
function of R. This is justified by the results of Kvaal [16] together with general consid-
erations about the form of the function. As we will see in this section, this assumption
seems to hold well for the systems that we have threated. To minimize ν(R) and reduce the
extrapolation error, we have only used energies calculated with R ≥ 5.

### 2016-03-25 Manuscript/paper.tex
Changed author list
spEnergiesQD/Manuscript/paper.tex: strip trailing whitespace
spEnergiesQD: Move extrapolation notes from paper.tex to extrapolation.txt

@@
   East Lansing, MI 48824, USA}
+\author{J\o rgen H\o gberget}
+\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}
+\author{Sam Novario}
+\affiliation{National Superconducting Cyclotron Laboratory and
+  Department of Physics and Astronomy,
+  Michigan State University,
+  East Lansing, MI 48824, USA}
+\author{Nathan Parzuchowski}
+\affiliation{National Superconducting Cyclotron Laboratory and
+  Department of Physics and Astronomy,
+  Michigan State University,
+  East Lansing, MI 48824, USA}
 \author{Sarah Reimann}
@@
   perturbation theory (QDPT).  Our results are benchmarked against quasi-exact
-  diffusion Monte Carlo results from previous works.  Possible explanations
-  for the discrepancies are discussed.
+  diffusion Monte Carlo and Coupled Cluster calculations.
 \end{abstract}
@@
 \end{document}
-
-The Hilbert spaces MR and PR is much closer in dimensionality than MR and PNP R . We
-will therefore assume that we can use the same error formula for the spaces MR and PR .
-As we will see later, this formula seems to hold very well for the systems we are studying.
-We will also assume that ν(R) is negligible and rewrite Eq. (5.7) on the form
-∞
-∆E ≈ b ∑ (NP + r) r−c , b ∈ R.
-(5.10)
-r=R+1
-This assumption is justified by Kvaal’s [16] results. He has performed FCI calculations on
-two dimensional quantum dots in the energy cut basis with 3, 4 and 5 particles, and for these
-systems ν(R) is shown to be small. Also, since PR ⊂ MR , we expect ν(R) to decay even
-faster in the direct product basis.
-5.3
-Extrapolation Formulas
-We have used Eq. (5.10) to parametrize the energy as a function of the number of shells.
-R
-E(R) ≈ a − b ∑ (NP + r)r− c ,
-(5.11)
-r=1
-where a, b, c are real constants. This formula has an error ∼ E(R)ν(R), and consequently
-it will become more accurate as R increases and ν(R) becomes small. This means that we
-ˆ ˆˆ
-should avoid extrapolations with energies ⟨PR H PR ⟩ for small R.
-We also want to find the extrapolated energy at R → ∞ given that we know the optimal
-values of a, b, c. We notice that E(∞) can be written in terms of the Riemann zeta function
-ζ(c) such that
-lim E(R) ≈ a − b[NP ζ(c) + ζ(c − 1)],
-R→∞
-where ζ(c) = ∑∞ r−c , which is known to converge for all c > 1.
-r=1
-34
-
-In this section, we will calculate a set of extrapolated energies and compare these to
-Diffusion Monte Carlo (DMC) energies which are not affected by a basis incompleteness
-error. We use the extrapolation formula Eq. (5.11)
-R
-E(R) ≈ a − b ∑ (N + r)r−c ,
-(25.1)
-r=1
-where N is the number of particles, R + 1 is the number of shells and a, b, c ∈ R are
-constants. A curve fit of the FCIQMC values to E(R) yields the optimal parameters a, b, c.
-The extrapolated energy is taken at the limit R → ∞, and the error is estimated using Eqs.
-(13.18) and (13.22) assuming that Eq. (25.1) is exact.
-As we discussed earlier, the extrapolation formula has an uncontrolled error ∝ ν(R)
-where ν(R) is an unknown function. ν(R) is however assumed to fall off quickly as a
-function of R. This is justified by the results of Kvaal [16] together with general consid-
-erations about the form of the function. As we will see in this section, this assumption
-seems to hold well for the systems that we have threated. To minimize ν(R) and reduce the
-extrapolation error, we have only used energies calculated with R ≥ 5.

### 2016-08-01 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 \begin{align*}
-  \hat U(s) = \lim_{\Delta s' \to 0} \prod_{s' = 0}^{s' = s}
-  \mathrm e^{\hat \eta(s') \Delta s'}
-\end{align*}
+  \hat U(s')
+  = \mathcal T_s \left\{ \exp \left(\int_0^{s'} \hat \eta_s \, d s \right)\},
+  := \lim_{\Delta s \to 0} \prod_{s = 0}^{s = s'}
+  \mathrm e^{\hat \eta(s) \Delta s}
+\end{align*}
+where $\mathcal T_s$ denotes $s$-ordering, defined analogously to the usual
+time-ordering from quantum field theory.
+
 The evolution of the Hamiltonian itself is governed by a differential
@@
 \[
-U_s = T_s \exp \left(\int_0^s \! ds'\hat{\eta}_{s'} \right),
+U(s') = \mathcal T_s \left\{ \exp \left(\int_0^{s'} \! ds'\hat{\eta}_s \right)\},
 \]
-where the anti-hermitian operator $\hat{\eta}_s$ serves as generator
-of the transformation. With $T_s$ we denote $s$-ordering, which is
-defined equivalently to usual time-ordering.  Taking the derivative of
-$\hat{H}_s$ with respect to $s$ gives
+Taking the derivative of $\hat{H}_s$ with respect to $s$ gives
 \begin{equation}
- \frac{d \hat{H}_s}{ds} = \frac{d U_s}{ds}\hat{H} U_s^\dagger + U_s
- \hat{H} \frac{d U_s^\dagger}{ds}.
+ \frac{d \hat H(s)}{d s} = \frac{d U(s)}{ds} \hat{H}(0) U^\dagger(s) + U(s)
+ \hat{H} \frac{d U^\dagger(s)}{ds}.
 \label{eq:flow_long}
 \end{equation}
-Utilizing that for our particular form of $U_s$, we have that \be
-\hat{\eta}_s = \frac{d U_s}{ds} U_s^\dagger = - U_s \frac{d
-  U_s^\dagger}{ds} = -\hat{\eta}_s,
+Utilizing that for our particular form of $U(s)$, we have that \be
+\hat{\eta}(s) = \frac{d U_s}{ds} U^\dagger(s) = - U(s) \frac{d U^\dagger(s)}{ds} = -\hat{\eta}(s),
 \label{eq:eta}

### 2016-09-09 Manuscript/paper.tex
Update spEnergiesQD paper

--- 2016-03-25 Manuscript/paper.tex
@@
 \usepackage{subfigure}
-\newcommand{\lb}{\left(}
-\newcommand{\rb}{\right)}
-\newcommand{\ad}{a^{\dagger}}
-\newcommand{\Hd}{\hat{H}^{\rm d}}
-\newcommand{\Ho}{\hat{H}^{\rm od}}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
-\newcommand{\T}{\hat{T}_{\rm rel}}
-\newcommand{\da}{^\dagger}
-\newcommand{\lla}{\left\langle}
-\newcommand{\rra}{\right\rangle}
-\newcommand{\llb}{\lbrace}
-\newcommand{\rrb}{\rbrace}
-\newcommand{\rv}{\mathbf{r}}
-
-%Jorgen commands
-\newcommand{\OP}[1]{{\hat{#1}}}
+
+\newcommand{\D}{\operatorname{d\!}}
 \newcommand{\ket}[1]{\left| #1 \right>}
@@
 \newcommand{\braket}[2]{\left\langle #1 | #2\right\rangle}
+\newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
 
@@
   circularly symmetric potential well using a harmonic oscillator basis
-  optimized via Hartree-Fock.  We further improve the ground state energy
+  optimized via Hartree-Fock (HF).  We further improve the ground state energy
   using in-medium similarity renormalization group (IM-SRG).  Additionally, we
@@
   perturbation theory (QDPT).  Our results are benchmarked against quasi-exact
-  diffusion Monte Carlo and Coupled Cluster calculations.
+  diffusion Monte Carlo (DMC) and coupled cluster (CC) calculations.
 \end{abstract}
@@
 
-Understanding the behaviour of strongly confined electrons is of fundamental
+Understanding the behavior of strongly confined electrons is of fundamental
 interest for solving many-body problems.  Quantum dots, e.g. electrons
@@
 they exhibit, due to their small size, discrete quantum levels.  Under these
-conditions, typical quantum phenomena like tunnelling, entanglement and
+conditions, typical quantum phenomena like tunneling, entanglement and
 magnetization can all be observed \cite{reimann2002,engel1993}.  Since quantum
 dots are manufactured and designed artificially at the laboratory, their
-quantum levels can be tuned to one's needs by changing for instance the
-external field, or the size and shape of the system. As a consequence, quantum
-dots provide a high level of control for the dynamics and correlation of the
-electrons, which makes them perfectly suited to study quantum effects in
-practice.  Since their ground state shows similar shell structures and magic
-numbers as seen for atoms and nuclei \cite{tarucha1996}, these systems give
-the opportunity to study electronic systems without the presence of a nucleus
-affecting the electrons.  Apart from their relevance for theoretical research
-in quantum physics, quantum dots offer a wide variety of applications: In
-particular, their electrical and optical properties make them attractive for
-the use in laser technology \cite{strauf2010,5075760} and solar cells
+quantum levels can be arbitrarily tuned by changing the external field or the
+size and shape of the system.  As a consequence, quantum dots provide a high
+level of control for the dynamics and correlation of the electrons, which
+makes them perfectly suited to study quantum effects in practice.  Since their
+ground state shows similar shell structures and magic numbers as seen for
+atoms and nuclei \cite{tarucha1996}, these systems give the opportunity to
+study electronic systems without the presence of a nucleus affecting the
+electrons.  Apart from their relevance for theoretical research in quantum
+physics, quantum dots offer a wide variety of applications: In particular,
+their electrical and optical properties make them attractive for the use in
+laser technology \cite{strauf2010,5075760} and solar cells
 \cite{jenks:013111,doi:10.1021/cr900289f}, but they are also used in quantum
-computers \cite{PhysRevA.57.120} and medical imaging \cite{Ben-Ari02042003}.
+computers\cite{PhysRevA.57.120} and medical imaging \cite{Ben-Ari02042003}.
 
 In order to properly understand the properties of quantum dots and make
-theoretical predictions to their behaviour in various applications, it is
+theoretical predictions of their behavior in various applications, it is
 necessary to study features like ground state energy and correlation
-effects. Since apart from quantum dots consisting of only two electrons or
-with specific values of the external field, no analytical solutions exist
-\cite{PhysRevA.48.3561}, the development of appropriate few- and many-body
-methods is required.
+effects. Since there generally does not exist an analytical solution for
+quantum dots except for ones containing only two electrons or with specific
+values of the external field \cite{PhysRevA.48.3561}, the development of
+appropriate numerical few- and many-body methods is required to solve the
+problem.
 
 Several \textit{ab initio} methods have been applied to these systems, in
-particular variational and diffusion Monte Carlo \cite{PhysRevB.68.035304,%
+particular variational and diffusion Monte Carlo (VMC and DMC)
+\cite{PhysRevB.68.035304,%
   PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}, large-scale
-diagonalization \cite{JJAP.36.3924,PhysRevB.56.6428,Kvaalcode,rontani:124102}
-and Coupled Cluster theory \cite{PhysRevB.67.045320,heidari:114708,%
+diagonalization/full configuration interaction (FCI)
+\cite{JJAP.36.3924,PhysRevB.56.6428,Kvaalcode,rontani:124102} and coupled
+cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,%
   PhysRevB.84.115302}.
 
-Additionally to those approaches, another very promising first-principle
-method has recently evolved. This is the Similarity Renormalization Group
-(SRG) method, which drives the Hamiltonian to a band- or block-diagonal form
-using a continuous series of unitary transformations.  Especially in nuclear
-theory, it has successfully been applied to study systems with different
-underlying potentials, and it has been used to analyse their binding energy
-and other observables \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}. Apart
-from the free-space approach, where the Hamiltonian is set up with respect to
-the zero vacuum state, in recent times another interesting alternative has
-been worked out: Making use of the technique of normal-ordering, the SRG
-evolution is performed in medium, where 3, \ldots, $A$-body operators can be
-approximated using only two-body machinery. This in-medium SRG (IM-SRG) allows
-considerable simplifications to the problem and makes numerical calculations
-much more efficient \cite{IMSRG}.
-
- This article is organized as follows: Section \ref{sec:formalism}
- introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
- use to model circular quantum dots, and gives afterwards an overview
- over the SRG (\ref{subsec:SRG}) and DMC (\ref{subsec:DMC})
- formalism. Our results are presented in Section \ref{sec:results}. We
- point out the differences arising from the use of two different
- generators, Wegner's and White's one, and give an overview over the
- ground state energies up to 42 particles. In particular, we compare
- the results obtained with five different \textit{ab initio} methods:
- IM-SRG(2), DMC, Hartree-Fock, Full Configuration Interaction and
- Coupled Cluster. Section \ref{sec:conclusions} concludes our work and
- gives perspectives for future work.
-
-The harmonic oscillator (HO) is ubiquitous in quantum physics. It is
-the basis for extremely diverse many-body calculations in nuclear
-physics,\cite{HjorthJensen1995} quantum chemistry,\cite{Helgaker2002}
-and quantum dot calculations in solid state physics.\cite{Reimann2002}
-In these calculations, one typically seeks a few of the lowest
-eigenenergies $E_k$ of the system Hamiltonian $H$, and their
-corresponding eigenvectors $\psi_k$, viz,
-\[ H\psi_k = E_k\psi_k, \quad k = 1,\cdots,k_\text{max}. \] In all
-cases, the many-body wave function is expanded in a basis of
-eigenfunctions of the HO, and then necessarily truncated to give an
-approximation. In fact, the so-called curse of dimensionality implies
-that the number of degrees of freedom per particle available is
-severely limited. It is clear, that an understanding of the properties
-of such expansions, giving \emph{a priori} error estimates on
-many-body calculations, is very important. Unfortunately, this is a
-neglected topic in the physics literature. In this article, we give a
-thorough mathematical and numerical analysis and give practical
-convergence estimates of HO basis expansions. It generalizes and
-refines the findings of a recent study of one-dimensional systems.\cite{Kvaal2007}
-
-The HO eigenfunctions are popular for several reasons. Many quantum
-systems, such as the quantum dot model considered here, are perturbed
-harmonic oscillators \emph{per se}, so that the true eigenstates
-should be perturbations of the HO states. Moreover, the HO has many
-beautiful properties, such as separability, invariance under
-orthogonal coordinate changes, and easily computed eigenfunctions, so
-that computing matrix elements of relevant operators becomes
-relatively simple. The HO eigenfunctions are defined on the
-\emph{whole} of $\mathbb{R}^d$ in which the particles live, so that
-truncation of the domain is unnecessary. Indeed, this is one of the
-main problems with methods such as finite difference or finite element
+Additionally to those approaches, another very promising first-principles
+method has recently been developed.  The similarity renormalization group
+(SRG) is a family of methods that drives the Hamiltonian toward a band- or
+block-diagonal form through a continuous sequence of unitary transformations,
+reducing the coupling between a subspace of interest -- such as the ground
+state -- and the remaining Hilbert space.  It has successfully been applied to
+study systems with different underlying potentials and to analyse their
+binding energy and other observables, especially in nuclear theory
+\cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.  Aside from usual
+\emph{free-space} SRG, where the Hamiltonian is constructed with respect to
+the vacuum state with no physical particles, it is possible to evolve a
+Hamiltonian via SRG \emph{in medium} through the normal-ordering technique,
+which enables the Hamiltonian to be constructed with respect to some reference
+state containing a finite number of particles.  In-medium SRG (IM-SRG) can
+further take advantage of the normal-ordering process to account for 3-body
+forces in an approximate manner without resorting to the full, computationally
+intensive 3-body machinery.  The method allows considerable simplifications to
+the problem and makes numerical calculations much more efficient \cite{IMSRG}.
+
+This article is organized as follows: Section \ref{sec:formalism} introduces
+first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular
+quantum dots, and gives afterwards an overview of the IM-SRG
+(\ref{subsec:SRG}) and DMC (\ref{subsec:DMC}) formalisms.  Our results are
+presented in Section \ref{sec:results}.  We point out the differences arising
+from the use of two different generators (Wegner and White generator), and
+give an overview of the ground state energies up to 42 particles. In
+particular, we compare the results obtained with five different \textit{ab
+  initio} methods: IM-SRG(2), DMC, Hartree-Fock, FCI and CC. Section
+\ref{sec:conclusions} concludes our work and gives perspectives for future
+work.
+
+The harmonic oscillator (HO) is a ubiquitous system in quantum physics. It is
+the basis for an extremely diverse set of many-body calculations -- in nuclear
+physics \cite{HjorthJensen1995}, quantum chemistry \cite{Helgaker2002}, and
+quantum dot calculations of solid state physics \cite{Reimann2002}. In these
+calculations, one typically seeks a few of the lowest eigenvalues $E_k$ and
+eigenvectors of a many-body Hamiltonian $\hat{H}$ that describes the full
+system by solving the Schr\"odinger equation,
+\begin{equation*}
+\hat{H} \ket{\psi_k} = E_k \ket{\psi_k}, \quad k \in \{1, 2, \ldots, k_{\text{max}}\}.
+\end{equation*}
+In all cases, the many-body wave function is expanded in a basis of
+eigenstates of the one-body HO system.  Necessarily, in order to perform
+numerical calculations the basis must be truncated to give an approximation.
+In particular, the so-called ``curse of dimensionality'' implies that for a
+system with many particles the number of available degrees of freedom per
+particle is severely limited by the finiteness of a computer.
+
+[[This paragraph seems to be talking about a different paper]]
+It is clear, that an understanding of the properties of such expansions,
+giving \emph{a priori} error estimates on many-body calculations, is very
+important. Unfortunately, this is a neglected topic in the physics
+literature. In this article, we give a thorough mathematical and numerical
+analysis and give practical convergence estimates of HO basis expansions. It
+generalizes and refines the findings of a recent study of one-dimensional
+systems.\cite{Kvaal2007}
+
+The HO eigenfunctions are popular for several reasons. Many quantum systems,
+such as the quantum dot model considered here, can be considered perturbed
+harmonic oscillators \textit{per se}, thus the true eigenstates should be
+perturbations of the HO eigenstates.  Moreover, the HO has many beautiful
+properties, such as separability, invariance under orthogonal coordinate
+changes, and easily computable eigenfunctions, so that computing matrix
+elements of relevant operators becomes relatively simple.  Since HO
+eigenfunctions are defined on the \emph{entire} space in which particles live,
+a truncation of the spatial domain is unnecessary.  This avoids one of the
+main problems with approaches such as finite difference or finite element
 methods.\cite{RamMohan2002}
@@
 external harmonic-oscillator potential.\footnote{In this paper, we use atomic
-  units where $\hbar$, $m$, $e$, and $4 \pi \epsilon$ are unity, with
-  $\epsilon$ denoting the permittivity and $m$ denoting the mass, which may be
-  an effective mass.  In vacuum where $m = m_{\text e}$ and
-  $\epsilon = \epsilon_0$, energy would be measured in units of hartrees
-  $E_{\text h} \equiv m_{\text e} (\alpha c)^2$.  More generally, the units of
-  energy are $m_{\text r \vphantom h}^{} E_{\text h}^{} /
-  \epsilon_{\text r \vphantom h}^2$ where
-  $\epsilon_{\text r} \equiv \epsilon / \epsilon_0$ and
-  $m_{\text r} \equiv m / m_{\text e}$.}  Each electron possesses kinetic
-energy $t(\bm p) \equiv \bm p^2 / 2$ and experiences an external potential
-\begin{align*}
-  u(\bm r) \equiv \frac{1}{2} \omega^2 \bm r^2
-\end{align*}
+  units where $\hbar$, $m$, $e$, and $4 \pi \epsilon$ are set to 1.  Here,
+  $\epsilon$ denotes the permittivity and $m$ denotes the mass, which could be
+  an effective mass rather than the true electron mass.  In effect, the unit
+  of energy in this article is
+  $E_{\text h} (m / m_{\text e}) / (\epsilon / \epsilon_0)^2$ where
+  $E_{\text h} \equiv m_{\text e} (\alpha c)^2$, the hartree unit of energy.}
+Each electron possesses kinetic energy $t(\bm p) \equiv \bm p^2 / 2$ and
+experiences an external potential $u(\bm r) \equiv \omega^2 \bm r^2 / 2$,
 where $\omega$ is the angular frequency of the oscillator, $\bm r$ is the
-2-dimensional coordinate of an electron, and $\bm p$ is its momentum.  Each
-pair of electrons experience a Coulomb repulsion
-\begin{align*}
-  v(\bm r, \bm r') \equiv \frac{1}{|\bm r - \bm r'|}
-\end{align*}
-where $\bm r$ and $\bm r'$ are coordinates of a pair of electrons.  Thus, the
-full many-body problem is described by the nonrelativistic Hamiltonian
+2-dimensional position vector of an electron, and $\bm p$ is its linear
+momentum.  Each pair of electrons experience a Coulomb repulsion
+$v(\bm r, \bm r') \equiv |\bm r - \bm r'|^{-1}$ where $\bm r$ and $\bm r'$ are
+their positions.  The full many-body problem is described by the
+nonrelativistic Hamiltonian
 \begin{align*}
@@
   t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
-  \bigr) + \sum_{\{p, q\}} v(\hat{\bm r}_p, \hat{\bm r}_q)
-\end{align*}
-where $\hat{\bm p}_p$ is the momentum operator and $\hat{\bm r}_p$ is the
-position operator for a particle labeled by $p$.  The first summation is
-performed over every particle $p$, while the the second summation is performed
-over every unordered pair of particles $\{ p, q \}$ (with $p \ne q$).
+  \bigr) + \sum_{p < q} v(\hat{\bm r}_p, \hat{\bm r}_q)
+\end{align*}
+where $\hat{\bm p}_p$ and $\hat{\bm r}_p$ respectively denote the momentum and
+position operators of a particle $p$.  The first summation is performed over
+every particle, while the the second summation is performed over every
+unordered pair of distinct particles (the ordering of $p$ is arbitrary).
 
@@
 interaction $v$ is removed:
-\begin{align*}
-  \hat H^{\text o} \equiv \sum_{p} \bigl(
+\begin{align} \label{eq:onebodyhamiltonian}
+  \hat H^{\text o} \equiv \sum_p \hat h^{\text o}_p
+  \equiv \sum_{p} \bigl(
   t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
   \bigr)
-\end{align*}
+\end{align}
 In this case, the many-body Hamiltonian reduces to $N$ independent
@@
 This is a 2-dimensional harmonic oscillator problem for a single particle,
-whose solutions are well known.  There are, however, various ways to construct
-the set of eigenfunctions: we shall use the Fock-Darwin states that conserve
-angular momentum about the axis perpendicular to the plane.  The
-eigenfunctions have the following analytic form in polar
+whose solutions are well known.  There are various ways to construct the set
+of eigenfunctions: we shall use the Fock-Darwin states that conserve angular
+momentum $\hat{L}_{\text{z}}$ about the $z$-axis (perpendicular to the 2D
+plane).  The eigenfunctions have the following analytic form in polar
 coordinates:\citep[Appx.\ A]{lohne2010coupled}
 \begin{gather*}
-  \phi^{\text{fd}}_{n, m_\ell}(r, \varphi)
+  \phi^{\text{FD}}_{n, m_\ell}(r, \varphi)
   \equiv \sqrt\omega
-  \phi^{\text{fdr}}_{n, |m_\ell|}(\sqrt \omega r)
-  \phi^{\text{fda}}_{m_\ell}(\varphi)
+  \phi^{\text{FD.R}}_{n, |m_\ell|}(\sqrt \omega r)
+  \phi^{\text{FD.A}}_{m_\ell}(\varphi)
 \end{gather*}
@@
 \begin{align*}
-  \phi^{\text{fdr}}_{n, \mu}(\rho) &\equiv
+  \phi^{\text{FD.R}}_{n, \mu}(\rho) &\equiv
   \sqrt{\frac{2 \cdot n!}{(n + \mu)!}}
   {\mathrm e}^{- \rho^2 / 2} \rho^\mu L_n^{(\mu)}(\rho^2) \\
-  \phi^{\text{fda}}_{m_\ell}(\varphi) &\equiv
+  \phi^{\text{FD.A}}_{m_\ell}(\varphi) &\equiv
   \frac{1}{\sqrt{2 \pi}} {\mathrm e}^{i m_\ell \varphi}
@@
 and $L_n^{(\mu)}$ denotes the generalized Laguerre polynomial of degree $n$
-with parameter $\mu$.  The states are labelled by two quantum numbers: the
+with parameter $\mu$.  The states are labeled by two quantum numbers: the
 principal quantum number $n \in \{0, 1, \ldots\}$ and the angular momentum
@@
 Additionally, since electrons are spin-$1/2$ fermions, they can occupy either
-of the two spin states $\chi_{+\frac12}$ or $\chi_{-\frac12}$.  Thus, the
+of the two spin states $\chi_{-\frac12}$ or $\chi_{+\frac12}$.  Thus, the
 single-particle basis states can be constructed as
@@
   \phi_{n, m_\ell, m_{\text s}}(r, \varphi) \equiv
-  \phi^{\text{fd}}_{n, m_\ell}(r, \varphi) \chi_{m_{\text s}}
+  \phi^{\text{FD}}_{n, m_\ell}(r, \varphi) \chi_{m_{\text s}}
 \end{align}
@@
 \includegraphics[width=.48\textwidth]{fig-shell-structure}
-\caption{Structure of the single-particle states in a noninteracting harmonic
-  oscillator.}
+\caption{Structure of the lowest 12 single-particle states in a noninteracting
+  harmonic oscillator of frequency $\omega = 1$.  Each box represents a
+  single-particle state, and the arrows denote the spin of the states.}
 \label{fig:shell-structure}
@@
 \end{align*}
-Note that they are degenerate with respect to the spin projection
-$m_{\text s}$ since our Hamiltonian $\hat h^{\text o}$ does not distinguish
-between them.  From this equation, we can see that the single-particle basis
-states form a shell structure as shown in Figure \ref{fig:shell-structure}.
-Every state within a given shell is degenerate and states within a given shell
-satisfy $2 n + |m_\ell| = k$ for some nonnegative integer $k$, which we call
-the \textit{shell index}.  The shells are equidistant from each other, with a
-spacing equal to the frequency $\omega$.
+which satisfies
+$\hat{h}^{\text o} \ket{\phi_{n, m_\ell, m_{\text s}}} = \varepsilon_{n,
+  m_\ell, m_{\text s}} \ket{\phi_{n, m_\ell, m_{\text s}}}$.  Note that the
+states are degenerate with respect to the spin projection $m_{\text s}$ since
+our Hamiltonian $\hat h^{\text o}$ does not distinguish between them.  From
+this equation, we can deduce the shell structure as shown in Figure
+\ref{fig:shell-structure}.  It is notable that there are degeneracies beyond
+that of the spin pairs: each shell contains a set of states that satisfy the
+equation $2 n + |m_\ell| = k$ for some nonnegative integer $k$, which we
+conveniently call the \textit{shell index}.  The shells are equidistant from
+each other, with a spacing equal to the frequency $\omega$.
 
@@
 $(n, m_\ell, m_{\text s})$.  From the states $\phi$ in
-\eqref{eq:singleparticlestate} we can construct the eigenstates of the
-many-body Hamiltonian $\hat H^{\text o}$ in the form of Slater determinants
-that automatically satisfy the Pauli exclusion principle:
-\begin{align*}
-  \Phi_{p_1, \ldots, p_N}(\bm r_1, \ldots, \bm r_N) \equiv
+\eqref{eq:singleparticlestate} we can construct the an eigenstate of the
+many-body Hamiltonian $\hat H^{\text o}$ in the form of a Slater determinant
+$\varnothing_{p_1, \ldots, p_N}$:
+\begin{align*}
+  \varnothing_{p_1, \ldots, p_N}(\bm r_1, \ldots, \bm r_N) \equiv
   \frac{1}{\sqrt{N}} \left|
@@
 \end{align*}
-The energy of these states is given by the sum of the single-particle
-energies:
-\begin{align*}
-  E^{\text o}_{p_1, \ldots, p_N} \equiv
-  \varepsilon_{p_1} + \cdots + \varepsilon_{p_N}
-\end{align*}
-For ground states, we may have degeneracies due to the shell structure of the
-single-particle basis.  However, if $N = k_{\text f} (k_{\text f} + 1)$ for
-some nonnegative integer $k_{\text f}$, there are just enough particles to
-form a closed-shell system.  In this case, there is a unique, well-isolated
-ground state.  The values of $N$ for which this occurs are typically referred
-to as \textit{magic numbers} and we call $k_{\text f}$ the \textit{number of
-  filled shells}.  This completes the solution of the noninteracting problem.
+This automatically satisfies the Pauli exclusion principle, ensuring that the
+Fermi statistics are satisfied.  The energy of these states is given by the
+sum of the single-particle energies:
+\begin{align*}
+  E^{\text o}_{p_1, \ldots, p_N} =
+  \varepsilon_{p_1} + \cdots + \varepsilon_{p_N},
+\end{align*}
+which satisfies
+$\hat{H}^{\text o} \ket{\varnothing_{p_1, \ldots, p_N}} = E^{\text o}_{p_1, \ldots,
+  p_N} \ket{\varnothing_{p_1, \ldots, p_N}}$.  For ground states, we may have
+degeneracies due to the shell structure of the single-particle basis.
+However, if $N = k_{\text F} (k_{\text F} + 1)$ for some nonnegative integer
+$k_{\text F}$, there are just enough particles to form a closed-shell system.
+In this case, there is a unique, well-isolated ground state.  The values of
+$N$ for which this occurs are typically referred to as \textit{magic numbers}
+and we call $k_{\text F}$ the \textit{number of filled shells} (or ``Fermi
+level'').  This completes the solution of the noninteracting problem.
 
@@
 determinant due to the presence of interactions.  Hence, it is not possible to
-reduce the problem to that of a single particle as we had done previously.
+trivially reduce the problem to that of a single particle as we had done
+previously.
 
@@
 Since Slater determinants are rather cumbersome to write out in full, we shall
-instead work in the more convenient formalism of second quantization:
-\begin{align*}
-  |\Phi_{p_1, \ldots, p_N}\rangle =
-  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger |\varnothing\rangle
-\end{align*}
-Here, $\hat a_p^\dagger$ is the creation operator for the single-particle
-state $p$ and $|\varnothing\rangle$ is the (true) vacuum state that is devoid
-of particles.  Analogously, $\hat a_p$ is the annihilation operator for the
-state $p$.
-
-Operators can be rewritten in this formalism as well.  The one-body kinetic
-energy operator, defined by
-\begin{align*}
-  \hat T \equiv \sum_p \hat t(\hat{\bm p}_p)
-\end{align*}
-can be rewritten in second quantization as
-\begin{align*}
-  \hat T = \sum_{p, q} T_{p, q}^{} \hat a_p^\dagger \hat a_q^{}
-\end{align*}
-where the operator matrix element
-$T_{p, q} \equiv \langle \Phi_p | \hat T | \Phi_q \rangle$.  This can likewise
-be extended for both $\hat U$ and $\hat V$,
-\begin{align*}
-  \hat U &= \sum_{p, q} U_{p, q}^{} \hat a_p^\dagger \hat a_q^{} \\
-  \hat V &= \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
+instead work in the more convenient formalism of \textit{second quantization}:
+\begin{align*}
+  \ket{\varnothing_{p_1, \ldots, p_N}} =
+  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger \ket{\varnothing}
+\end{align*}
+Here, $\varnothing$ is the vacuum state that is devoid of particles and
+$\hat a_p^\dagger$ is a \textit{creation operator} for the single-particle
+state $p$.  If the state $p$ is not yet occupied by a particle,
+$\hat a_p^\dagger$ creates such a particle.  Otherwise, it collapses the
+entire many-body state to $0$.  The Hermitian conjugate of $\hat a_p^\dagger$
+is $\hat a_p$, which is an \textit{annihilation operator} for the state $p$
+that has the opposite effect.  For fermions, the field operators $\hat a_p$
+and $\hat a_p^\dagger$ satisfy the essential anticommutation relations,
+\begin{align*}
+  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
+  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}.
+\end{align*}
+Operators can be rewritten in this formalism as well.  The one-body
+Hamiltonian $H^{\text o}$ defined by \eqref{eq:onebodyhamiltonian} can be
+rewritten in second quantization as
+\begin{align} \label{eq:second_quantized_one_body_hamiltonian}
+  \hat H^{\text o} = \sum_{p, q} H_{p, q}^{\text o} \hat a_p^\dagger \hat a_q^{}
+\end{align}
+where the \textit{matrix element}
+$H_{p, q}^{\text o} \equiv \bra{\varnothing_p} \hat H^{\text o} \ket{\varnothing_q}$.  This
+can likewise be extended to $\hat V$,
+\begin{align} \label{eq:second_quantized_two_body_hamiltonian}
+  \hat V = \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
   \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
-\end{align*}
-where $U_{p, q} \equiv \langle \Phi_p | \hat U | \Phi_q \rangle$ and
-$V_{p, q, r, s} \equiv \langle \Phi_{p, q} | \hat V | \Phi_{r, s} \rangle$.
+\end{align}
+where $U_{p, q} \equiv \langle \varnothing_p | \hat U | \varnothing_q \rangle$ and
+$V_{p, q, r, s} \equiv \langle \varnothing_{p, q} | \hat V | \varnothing_{r, s} \rangle$.
 Note that due to the antisymmetry present in the Slater determinants, we have
 the property that exchanging either $p$ with $q$ or $r$ with $s$ causes
-$V_{p, q, r, s}$ to reverse in sign.
+$V_{p, q, r, s}$ to reverse in sign, leading to a $4$-fold symmetry that is
+canceled out by the factor of $1/4$.  For this reason, the two-body matrix
+element $V_{p, q, r, s}$ is commonly referred to as the \emph{antisymmetrized}
+matrix element.  This is not to be confused with the non-antisymmetric
+interaction integral defined by:
+\begin{align*}
+  \tilde V_{p, q, r, s} \equiv \int \phi_p(\bm r) \phi_q(\bm r') v(\bm r, \bm r') \phi_r(\bm r) \phi_s(\bm r') \D \bm r \D \bm r'
+\end{align*}
+The antisymmetrized matrix element is computed from the interaction integral
+by $V_{p, q, r, s} = \tilde V_{p, q, r, s} - \tilde V_{p, q, s, r}$.  In our
+work, we compute the interaction numerically via the OpenFCI software, which
+numerical integrates the Coulomb interaction in the center-of-mass frame
+[[cite Kvaal's paper; also, is the description correct?]].
+
+There are significant advantages in the second quantization formalism in
+many-body theory: the operators are written in a way that does not generic
+with respect to the number of particles, and the anticommutative behavior of
+field operators ensures the Pauli exclusion principle holds no matter how the
+operator is manipulated.  Furthermore, it allows the application of a useful
+combinatoric theorem known as Wick's theorem [[cite something]] to simplify
+complicated operator expressions.  Ultimately, the computations themselves do
+not involve operators at all -- rather, they involve the calculation of
+\emph{matrix elements} via equations derived with the aid of Wick's theorem.
 
@@
 The first correction that we will apply to our solution is that of the
-Hartree-Fock method.  Using the variational principle, we compute an
-approximate ground state $\Psi^{\text{hf}}$ by minimizing the energy
-\begin{align*}
-  E^{\text{hf}} \equiv \langle \Psi^{\text{hf}} | \hat H | \Psi^{\text{hf}} \rangle
-\end{align*}
-with respect to $\Psi^{\text{hf}}$, subject to the restriction that
-$\Psi^{\text{hf}}$ is a single Slater determinant constructed from a set of
-$N$ orthonormal single-particle states.  We denote each state $\psi_u$, where
-$u$ is its label.
+Hartree-Fock (HF) method.  Using the variational principle, we compute an
+approximate ground state $\Psi^{\text{HF}}$ by minimizing the energy
+\begin{align*}
+  E^{\text{HF}} \equiv \langle \Psi^{\text{HF}} | \hat H | \Psi^{\text{HF}} \rangle
+\end{align*}
+with respect to $\Psi^{\text{HF}}$, subject to the restriction that
+$\Psi^{\text{HF}}$ is a single Slater determinant constructed from an unknown
+set of $N$ orthonormal single-particle states.  We denote each unknown
+single-particle state $\psi_u$ by some label $u$.
 
 To make this computationally feasible, we further assume that the unknown
-states $\psi$ are built from a linear combination of known functions,
-drawn from a finite set.  This reduces the problem from an abstract
-mathematical one to a numerical linear algebra problem, with the caveat that
-this set of known functions must be chosen carefully.
+states $\{\psi_u\}$ are built from a linear combination of known functions,
+drawn from a finite set $\{\phi_p\}$.  This reduces the problem from an
+abstract mathematical one to a numerical linear algebra problem, with the
+caveat that this set of known functions must be chosen carefully to ensure
+convergence.
 
 Assuming the interaction is not too strong, we can use the single-particle
-states $\phi$ of our noninteracting Hamiltonian as a basis for the unknown
-states $\psi$.  The two sets of states are then related by a linear
-transformation $\bm C$:
+states $\{\phi_p\}$ of our noninteracting Hamiltonian as a basis for the
+unknown states $\{\psi_u\}$.  The two sets of states are then related by a
+linear transformation matrix $\bm C$:
 \begin{align*}
@@
 \end{align*}
-To ensure the orthonormality of the states, we expand the set of unknown
-states $\psi$ to have as many elements as the set of $\phi$ and require the
-\textit{coefficient matrix} $\bm C$ to be unitary.  While these conditions
-are more strict than necessary, they greatly simplify the calculations and the
-additional states are essential inputs for methods beyond Hartree-Fock.  The
-set of states $\psi$ now consists of $N$ \textit{occupied} states that
-participate in the Slater determinant $\Psi^{\text{hf}}$ and the remaining
+To ensure the orthonormality of the states, we assume the set of unknown
+states $\{\psi_u\}$ has as many elements as the set of $\{\phi_pp\}$ and
+require the coefficient matrix $\bm C$ to be unitary.  While these conditions
+are more strict than necessary, they greatly simplify the calculations and
+allow the states $\{\psi_u\}$ to act as inputs for methods beyond HF.  The set
+of states $\psi$ now consists of $N$ \textit{occupied} states that participate
+in the Slater determinant $\Psi^{\text{HF}}$ and the remaining
 \textit{unoccupied} states that do not.
@@
 \begin{align*}
-  E^{\text{hf}} = \sum_{\underline u} C_{p, u}^* H_{p, q}^{\text o} C_{q, u}^{}
+  E^{\text{HF}} = \sum_{\underline u} C_{p, \underline u}^* H_{p, q}^{\text o} C_{q, \underline u}^{}
   + \sum_{\underline u, \underline v}
-  C_{p, u}^* C_{q, u}^* V_{p, q, r, s}^{} C_{r, u}^{} C_{s, u}^{}
+  C_{p, \underline u}^* C_{q, \underline v}^* V_{p, q, r, s}^{} C_{r, \underline u}^{} C_{s, \underline v}^{}
 \end{align*}
@@
 \begin{align} \label{eq:hartreefock}
-  \bm f \bm C = \bm C \bm \epsilon
+  \bm F \bm C = \bm C \bm \epsilon
 \end{align}
-where the \textit{Fock matrix} $\bm f$ is defined as
+where the \textit{Fock matrix} $\bm F$ is defined as
 \begin{align} \label{eq:fock}
-  f_{p, r} \equiv H_{p, r}^{\text o} + \sum_{\underline u q s}
-  C_{q, u}^* V_{p, q, r, s}^{} C_{s, u}^{}
+  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{\underline u r s}
+  C_{r, \underline u}^* V_{p, r, q, s}^{} C_{s, \underline u}^{}
 \end{align}
-and $\bm \epsilon$ is a vector of Lagrange multipliers with each
-element $\epsilon_u$ associated with a particular state $u$.  While the Fock
-matrix $\bm f$ may appear to be an artificial Hamiltonian derived purely
-from the minimization problem, it can be generalized as an operator whose
-relevance extends beyond Hartree-Fock.
-
-The Hartree-Fock equation can be solved by an iterative technique: a solution
-$\bm C$ can be fed into \eqref{eq:fock} and new solution can then obtained
-by solving the eigenvalue problem in \eqref{eq:hartreefock} using the Fock
-matrix obtained.  For the initial guess, we use the ground state of our
+and $\bm \epsilon$ is a vector of Lagrange multipliers with each element
+$\epsilon_u$ associated with a particular state $u$.  [[move this sentence
+later to the intro to normal-ordering: While the Fock matrix $\bm F$ may
+appear to be an artificial Hamiltonian derived purely from the minimization
+problem, it can be considered the normal-ordered operator with respect to a
+non-vacuum state, as explained later.]]
+
+The HF equation can be solved by an iterative technique: a solution $\bm C$
+can be fed into \eqref{eq:fock} and new solution can then obtained by solving
+the eigenvalue problem in \eqref{eq:hartreefock} using the Fock matrix
+obtained.  For the initial guess, we use the ground state of our
 noninteracting Hamiltonian, thus $\bm C$ is initially the identity matrix.
 
-Since Hartree-Fock method restricts the ground state to a Slater determinant
-of single-particle states, it cannot provide an exact solution to a problem
-where correlation is present, even if the basis $\phi$ is infinite.  The
+Since HF restricts the ground state to a Slater determinant of single-particle
+states, it cannot provide an exact solution to a problem where correlations
+are present even if the basis $\{\phi_p\}$ is not truncated (infinite).  The
 energy difference between the best Hartree-Fock energy and the exact ground
 state energy is thus by definition known as the \textit{correlation energy}.
-There are various methods of recovering (at least parts of) this missing
-energy.  The focus of this paper shall be on the IM-SRG method.
-
-\subsection{The IM-SRG method}
+The focus of post-HF methods such as IM-SRG is to improve on the HF results,
+thus recovering parts of this missing energy.
+
+\subsection{The SRG methods}
 \label{subsec:imsrgmethod}
 
-In the similarity renormalization group (SRG) method, one performs a
-continuous sequence of unitary transformations on a Hamiltonian operator
-$\hat H$ to evolve it into a more ``amenable'' form -- which generally implies
-decoupling a small model space of interest from its complement.  The sequence
-is parameterized by a continuous variable $s$ known as the \textit{flow
-  parameter}, which by convention we define to be $0$ at the beginning of the
-sequence.  Upon reaching $s$, the transformed Hamiltonian is given by
-\begin{align*}
-  \tilde H(s) \equiv \hat U(s) \hat H \hat U(s)
-\end{align*}
-where $U(s)$ describes the product of all such transformations since $s = 0$.
-At every step $s'$, the differential unitary transformation is described by
-the exponential of an antihermitian operator $\eta(s)$, known as the
-\textit{generator} of the transformation.  When ``integrated'' as a product,
-the full transformation $\hat U(s)$ is recovered:\footnote{Alternatively, this
-  can also be reinterpreted as an $s'$-ordered integral.  See \cite[\S
-  6.1]{reimann2013quantum}.}
-\begin{align*}
-  \hat U(s) = \lim_{\Delta s' \to 0} \prod_{s' = 0}^{s' = s}
-  \mathrm e^{\hat \eta(s') \Delta s'}
-\end{align*}
-The evolution of the Hamiltonian itself is governed by a differential
-equation, commonly referred to as the flow equation:
-\begin{gather} \label{eq:imsrgode}
-  \frac{d}{d s} \tilde H(s) = [\hat \eta(s), \tilde H(s)]
-\end{gather}
-which allows $\tilde H(s)$ to be evaluated without explicitly constructing the
-full transformation $\hat U(s)$.
-
- Introducing a flow parameter $s$, there exits a unitary
- transformation $U_s$, such that
-\begin{equation}
- \hat{H}_s = U_s^\dagger \hat{H} U_s \equiv \Hd_s + \Ho_s,
-\end{equation}
-with the relations $U_{s=0} = \mathbf{1}$, and $\hat{H}_{s= 0} =
-\hat{H}$.  The transformation $U_s$ is parametrized as
+\subsubsection*{Similarity renormalization group methods}
+
+In similarity renormalization group (SRG) methods, one performs a continuous
+sequence of unitary transformations on a Hamiltonian operator $\hat H$ to
+evolve it into a band- or block-diagonal form, reducing the coupling between a
+small model space of interest from its complementary space.  This allows the
+Hilbert space to be truncated to the small model space without losing
+significant accuracy.
+
+The sequence of transformations is parameterized by a continuous variable $s$
+known as the \textit{flow parameter}.  By convention we define to be $0$ at
+the beginning of the sequence, and thus the evolving Hamiltonian $\hat H(s)$
+at $s = 0$ is set to the original Hamiltonian.  Upon reaching $s$, the
+transformed Hamiltonian is given by
+\begin{align*}
+  \hat H(s) \equiv \hat U(s) \hat H(0) \hat U^\dagger(s)
+\end{align*}
+where $U(s)$ is a unitary operator that describes the product of all such
+transformations since $s = 0$.  Taking the derivative with respect to $s$, we obtain:
+\begin{align*}
+  \frac{\D}{\D s} H(s) =
+  \left(\frac{\D}{\D s} \hat{U}(s)\right) \hat{H}(0) \hat{U}^\dagger(s) +
+  \hat{U}(s) \hat{H}(0) \frac{\D}{\D s} \hat{U}^\dagger(s)
+\end{align*}
+If we define an operator $\eta(s)$ as
+\begin{align*}
+  \eta(s) \equiv \left(\frac{\D}{\D s} \hat{U}(s)\right) \hat{U}^\dagger(s)
+\end{align*}
+we find that it is antihermitian as a result of the unitarity of $\hat{U}(s)$:
+\begin{align*}
+  \eta(s) + \eta^\dagger(s)
+  = \frac{\D}{\D s} \left(\hat{U}(s) \hat{U}^\dagger(s)\right)
+  = 0
+\end{align*}
+From this property we can derive a differential equation known as the
+\textit{SRG flow equation}:
+\begin{align} \label{eq:imsrgode}
+  \frac{\D}{\D s} H(s) = [\eta(s), \hat{H}(s)]
+\end{align}
+The equation allows $\hat{H}(s)$ to be evaluated without explicitly
+constructing the full transformation $\hat U(s)$.  The operator $\hat \eta(s)$
+is known as the \textit{generator} of the transformation.  When ``integrated''
+as a product, the full transformation $\hat U(s)$ is recovered:
+\begin{align*}
+  \hat U(s')
+  = \mathcal T_s \left\{ \mathrm{e}^{\int_0^{s'} \hat{\eta}(s) \D s} \right\}
+  \equiv \lim_{\Delta s \to 0} \prod_{s = 0, \Delta s, \ldots}^{s = s'}
+  \mathrm{e}^{\hat \eta(s) \Delta s}
+\end{align*}
+Here $\mathcal T_s$ is a notational device that denotes $s$-ordering: a
+reordering of the $\eta(s)$ operator products expanded from the exponential
+with respect to $s$ in ascending order \cite[\S 6.1]{reimann2013quantum}.
+This is analogous to the usual time-ordering from quantum field theory.
+
+The operator $\hat{\eta}(s)$ can be chosen to suppress certain undesirable
+parts of the Hamiltonian matrix, which can be considered the ``off-diagonal''
+parts in a loose sense.  The ``off-diagonal'' parts could be elements far away
+from the matrix diagonal, in which case the evolution drives the matrix
+towards a band-diagonal form.  Or, the ``off-diagonal'' parts could be
+elements that couple the ground state from the excited state, in which case
+the evolution drives the matrix towards a block-diagonal form that isolates
+the ground state.  Or, the ``off-diagonal'' could be literally the elements
+that do not lie on the diagonal, in which case the evolution would simply
+diagonalize the Hamiltonian.  Through different choices of $\hat{\eta}_s$, the
+SRG evolution can be controlled and adapted to the features of a particular
+problem.
+
+\subsubsection*{In-medium SRG}
+
+The SRG flow equation \eqref{eq:imsrgode} can be solved in the second
+quantization formalism described in Section \ref{subsec:modelHamiltonian},
+where field operators are defined with respect to the physical vacuum state.
+However, since the size of the problem grows enormously with the number of
+particles and the size of the model space, the applicability of this
+free-space SRG method is restricted to comparatively small systems.
+Alternatively, the evolution can be done at finite density, i.e.\ directly in
+an $N$-particle system defined by a reference state \cite{kehrein2006flow}.
+This gives rise to the IM-SRG method.
+
+The second-quantized operators in
+\eqref{eq:second_quantized_one_body_hamiltonian} and
+\eqref{eq:second_quantized_two_body_hamiltonian} are constructed with respect
+to the vacuum state.  That is, the operator strings
+$\hat{a}_p^\dagger \hat{a}_q$ and
+$\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum
+expectation value of zero:
+\begin{align*}
+&\bra{\varnothing} \hat{a}_p^\dagger \hat{a}_q \ket{\varnothing} = 0 &
+&\bra{\varnothing} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{\varnothing} = 0
+\end{align*}
+They are said to be \emph{normal-ordered} with respect to the vacuum state
+$\varnothing$.  It is possible to be normal-ordered with respect to a
+non-vacuum state, however.  Consider a Slater determinant $\Phi$ with
+$N_{\text F}$ occupied states.  One can define a set of \textit{quasiparticle
+  field operators} $\hat b$ and $\hat b^\dagger$ that obey the same
+anticommutation relations as the $\hat a$ operators.  The field operators are
+defined as:
+\begin{align*}
+  \hat b_p \equiv \hat a_{\overline p} + \hat a_{\underline p}^\dagger = \begin{cases}
+    \hat a_{\overline p} & \text{if $\overline p$ is unoccupied in $\Phi$} \\
+    \hat a_{\underline p}^\dagger & \text{if $\underline p$ is occupied in $\Phi$}
+  \end{cases}
+\end{align*}
+Here we use an underline to indicate that only an occupied state is accepted
+and an overline to indicate only an unoccupied state is accepted.  If the
+state is not acceptable, then that term does not contribute to the overall
+expression.
+
+We can then define normal ordering with respect to the reference state $\Phi$:
+namely, rearrange an operator string such that every creation operator appears
+before an annihilation operator by repeatedly exchanging neighboring
+operators, with each exchange costing a minus sign.  In this form, it is
+guaranteed that the expectation value of the operator string with respect to
+$\Phi$ is zero:
+\begin{align*}
+&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q \ket{\Phi} = 0 &
+&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^\dagger \hat{b}_s \hat{b}_r \ket{\Phi} = 0
+\end{align*}
+We denote normal ordering of an operator string with respect to $\Phi$ by a
+pair of colons:
+\begin{align*}
+  \normord{\hat{b}_p \hat{b}_q^\dagger} =
+  -\hat{b}_q^\dagger \hat{b}_p
+\end{align*}
+It is not particularly interesting to examine normal ordering of the
+quasiparticle field operators, since the result is trivial to compute.  What
+is more interesting is the normal ordering of the physical field operators
+$\hat a$ and $\hat a^\dagger$ with respect to $\Phi$:
+\begin{align*}
+  \normord{\hat{a}_p^\dagger \hat{a}_q} =
+  -\hat{a}_{\underline q} \hat{a}_{\underline p}^\dagger
+  + \hat{a}_{\underline p}^\dagger \hat{a}_{\overline q}
+  + \hat{a}_{\overline p}^\dagger \hat{a}_{\underline q}
+  + \hat{a}_{\overline p}^\dagger \hat{a}_{\overline q} =
+  -\delta_{\underline q \underline p}
+  + \hat{a}_p^\dagger \hat{a}_q
+\end{align*}
+This makes the normal ordering notation a useful and concise way of expressing
+the right-hand side.
+
+Using the normal ordering formalism, we can rewrite the Hamiltonian
+$\hat H = \hat H^{\text o} + \hat V$ as
+\begin{align*}
+  \hat{H} = E + \sum_{p, q} F_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
+\end{align*}
+where
+\begin{align*}
+  E &= \sum_{\underline p} H^{\text o}_{\underline p, \underline p} + \frac{1}{2} \sum_{\underline p, \underline q} V_{\underline p, \underline q, \underline p, \underline q} \\
+  F_{p, q} &= H^{\text o}_{\underline p, \underline q} + \sum_{\underline r} V_{\underline p, \underline r, \underline q, \underline r} \\
+\end{align*}
+Notice that $E$ is in fact the Hartree-Fock energy and $F_{p, q}$ is the Fock matrix.
+
+Integrating the flow equations (\ref{eq:imsrgode}), we face one of the
+major challenges of the SRG method, namely the generation of higher and higher
+order interaction terms during the flow.  With each evaluation of the
+commutator, the Hamiltonian gains terms of higher order, and these induced
+contributions will in subsequent integration steps contribute to terms of
+lower order.  In principle, this continues to infinity.
+
+To make the method computationally possible, we must close the IM-SRG flow
+equations: we are thus forced to truncate the equations to a certain order. We
+choose to truncate both $\hat{H}(s)$ and $\hat{\eta}(s)$ at the two-body
+level, an approach which is referred to as IM-SRG(2).  This normal-ordered
+two-body approximation appears to be sufficient in many cases and has yielded
+excellent results for several nuclei
+\cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+%[[---]]
+
+The commutator in the flow equations (\ref{eq:imsrgode}) guarantees that the
+IM-SRG wave function $U^\dagger(s) \ket{\Phi}$ can be expanded in terms of
+linked diagrams only \cite{shavitt2009many,ISI:A1981MN73700014}, which
+suggests that IM-SRG is size-extensive. Regarding the quality of the SRG
+results, it means that the error introduced by truncating the many-body
+expansions scales linearly with the number of particles $N$.
+
+With this truncation, the generator
+$\hat{\eta}$ can be written as
 \[
-U_s = T_s \exp \left(\int_0^s \! ds'\hat{\eta}_{s'} \right),
-\]
-where the anti-hermitian operator $\hat{\eta}_s$ serves as generator
-of the transformation. With $T_s$ we denote $s$-ordering, which is
-defined equivalently to usual time-ordering.  Taking the derivative of
-$\hat{H}_s$ with respect to $s$ gives
-\begin{equation}
- \frac{d \hat{H}_s}{ds} = \frac{d U_s}{ds}\hat{H} U_s^\dagger + U_s
- \hat{H} \frac{d U_s^\dagger}{ds}.
-\label{eq:flow_long}
-\end{equation}
-Utilizing that for our particular form of $U_s$, we have that \be
-\hat{\eta}_s = \frac{d U_s}{ds} U_s^\dagger = - U_s \frac{d
-  U_s^\dagger}{ds} = -\hat{\eta}_s,
-\label{eq:eta}
-\ee we obtain that \be \frac{d \hat{H}_s}{ds} = \hat{\eta}_s \hat{H}_s
-- \hat{H}_s \hat{\eta}_s = \left[\hat{\eta}_s, \hat{H}_s \right].
-\label{eq:flowEquations}
-\ee This is the key expression of the SRG method, describing the flow
-of the Hamiltonian.  The specific unitary transformation is determined
-by the choice of $\hat{\eta}_s$.  Through different choices of
-$\hat{\eta}_s$, the SRG evolution can be adapted to the features of a
-particular problem.\\
-
-\paragraph*{In-medium SRG}
-
-One possibility to solve the flow equations is to choose a basis with
-respect to the physical vacuum state, set up the Hamiltonian matrix in
-this basis and solve Eq.~(\ref{eq:flowEquations}) as a set of coupled
-first-order differential equations. However, since the size of the
-problem grows enormously with the number of particles and the size of
-the model space, the applicability of this free-space SRG method is
-restricted to comparatively small systems.
-
-Instead of performing SRG in free space, the evolution can be done at
-finite density, i.e.~directly in the A-body system
-\cite{kehrein2006flow}. This approach has recently been applied very
-successfully in nuclear physics \cite{IMSRG,PhysRevLett.106.222502}
-and is called in-medium SRG (IM-SRG). The method allows the evolution
-of $3,...,A$-body operators using only two-body machinery, with the
-simplifications arising from the use of normal-ordering with respect
-to a reference state.
-
-In our case, we assume that the problem can be modelled by a
-Hamiltonian containing maximally two-body interactions. In
-second-quantized form, this one is given by
-\begin{align}
-\hat{H} & = \sum\limits_{pq}\left\langle p \right| \hat{h}^{(0)}
-\left| q \right\rangle a_p\da a_q + \frac{1}{4}\sum\limits_{pqrs}\lla
-pq || r s \rra a_p\da a_q\da a_s a_r,
-\label{eq:ourHamiltonian}
-\end{align}
-where the operator $\hat{h}^{(0)}$ denotes the single-particle
-Hamiltonian, and the elements $\langle pq||rs\rangle$ are the
-anti-symmetrized two-body matrix elements.  Normal-ordering with
-respect to a reference state $|\Phi_0\rangle$ yields
-\begin{align*}
-\hat{H} &= E_0 + \sum\limits_{pq}f_{pq}\llb a_p\da a_q\rrb +
-\frac{1}{4}\sum\limits_{pqrs}v_{pqrs} \llb a_p\da a_q\da a_s a_r \rrb,
-\end{align*}
-with Fock matrix elements
-\[
-f_{pq} = \lla p \right|\hat{h}^{(0)}\left| q \rra + \sum\limits_{i}
-\lla pi || qi\rra,
-\]
-and where $v_{pqrs} = \lla pq || r s \rra$ are the amplitudes of the
-two-body operator.  Here and in the following, indices $i,j,k,...$
-denote hole states below the Fermi level, indices $a,b,c,...$
-particles states above the Fermi level, and indices $ p,q,r,...$ can
-be used for both particle and hole states. As reference state
-$|\Phi_0\rangle$ we choose the ground state of the non-interacting
-system, where all single-particle orbitals below the Fermi level are
-occupied.
-
-Integrating the flow equations~(\ref{eq:flowEquations}), we face one
-of the major challenges of the SRG method, namely the generation of
-higher and higher order interaction terms during the flow. With each
-evaluation of the commutator, the Hamiltonian gains terms of higher
-order, and these induced contributions will in subsequent integration
-steps contribute to terms of lower order. In principle, this continues
-to infinity.\\ To make the method computationally possible, we have to
-close the IM-SRG flow equations, suggesting that we are forced to
-truncate the equations to a certain order. We choose to truncate both
-$\hat{H}_s$ and $\hat{\eta}_s$ at the two-body level, an approach
-which is referred to as IM-SRG(2).  This normal-ordered two-body
-approximation seems to be sufficient in many cases and has yielded
-excellent results for several nuclei
-\cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.\\ The
-commutator in the flow equations (\ref{eq:flowEquations}) guarantees
-that the IM-SRG wave function $U_s^\dagger|\Phi\rangle$ can be
-expanded in terms of linked diagrams only
-\cite{shavitt2009many,ISI:A1981MN73700014}, which suggests that IM-SRG
-is size-extensive. Regarding the quality of the SRG results, it means
-that the error introduced by truncating the many-body expansions
-scales linearly with the number of particles~$N$.\\ With this
-truncation, the generator $\hat{\eta}$ can be written as
-\[
-\hat{\eta} = \sum_{pq} \eta_{pq}^{(1)} \llb a_p\da a_q\rrb +
-\frac{1}{4}\sum\limits_{pqrs}\eta_{pqrs}^{(2)} \llb a_p\da a_q\da a_s
-a_r \rrb,
+\hat{\eta} = \sum_{pq} \eta_{pq}^{(1)} \lbrace a_p^\dagger a_q\rbrace +
+\frac{1}{4}\sum\limits_{pqrs}\eta_{pqrs}^{(2)} \lbrace a_p^\dagger a_q^\dagger a_s
+a_r \rbrace,
 \]
@@
 are given by
+% [[fix the equations to avoid requiring (anti)hermittivity in H]]
 \begin{widetext}
 \begin{align}
-\frac{d E_0}{ds} &= \sum_{ia}\left( \eta_{ia}^{(1)}f_{ai} -
-\eta_{ai}^{(1)}f_{ia}\right) +
-\frac{1}{2}\sum_{ijab}\eta_{ijab}^{(2)}v_{abij},
+\frac{\D E}{\D s} &= \sum_{\underline p, \overline q} \left(\eta_{\underline p, \overline q} F_{a, \underline p} - \eta_{\overline q, \underline p} f_{\underline p, \overline q}\right) + \frac{1}{2} \sum_{\underline p, \underline q, \overline r, \overline s} \eta_{\underline p, \underline q, \overline r, \overline s} V_{\overline r, \overline s, \underline p, \underline q},
 \label{eq:flow1}\\
-\frac{d f_{pq}}{ds}&= \sum_r \lb \eta_{pr}^{(1)}f_{rq} +
-\eta_{qr}^{(1)}f_{rp}\right) + \sum_{ia}\lb 1-\hat{P}_{ia}\rb \lb
-\eta_{ia}^{(1)}v_{apiq} - f_{ia}\eta_{apiq}^{(2)} \rb \notag \\ &
-+\frac{1}{2} \sum_{aij} \lb 1+\hat{P}_{pq}\rb
-\eta_{apij}^{(2)}v_{ijaq} + \frac{1}{2}\sum_{abi}\lb 1+\hat{P}_{pq}\rb
+\frac{\D F_{p, q}}{ds}&= \sum_r \left( \eta_{pr}^{(1)}f_{rq} +
+\eta_{qr}^{(1)}f_{rp}\right) + \sum_{ia}\left( 1-\hat{P}_{ia}\right) \left(
+\eta_{ia}^{(1)}v_{apiq} - f_{ia}\eta_{apiq}^{(2)} \right) \notag \\ &
++\frac{1}{2} \sum_{aij} \left( 1+\hat{P}_{pq}\right)
+\eta_{apij}^{(2)}v_{ijaq} + \frac{1}{2}\sum_{abi}\left( 1+\hat{P}_{pq}\right)
 \eta_{ipab}^{(2)}v_{abiq},
@@
 \begin{align}
-\frac{d v_{pqrs}}{ds} &= \sum_t \lb 1-\hat{P}_{pq} \rb \lb
-\eta_{pt}^{(1)}v_{tqrs}-f_{pt}\eta_{tqrs}^{(2)}\rb -\sum_t \lb
-1-\hat{P}_{rs} \rb \lb \eta_{tr}^{(1)} v_{pqts} - f_{tr}
-\eta_{pqts}^{(2)}\rb \notag \\ & +\frac{1}{2}\sum_{ab}
-\lb\eta_{pqab}^{(2)} v_{abrs} - v_{pqab}\eta_{abrs}^{(2)}\rb -
-\frac{1}{2}\sum_{ij} \lb\eta_{pqij}^{(2)} v_{ijrs} -
-v_{pqij}\eta_{ijrs}^{(2)}\rb \notag \\ & -\sum_{ia} \lb 1-
-\hat{P}_{ia} \rb \lb 1-\hat{P}_{pq}\rb \lb 1-\hat{P}_{rs} \rb
+\frac{\D V_{p, q, r, s}}{ds} &= \sum_t \left( 1-\hat{P}_{pq} \right) \left(
+\eta_{pt}^{(1)}v_{tqrs}-f_{pt}\eta_{tqrs}^{(2)}\right) -\sum_t \left(
+1-\hat{P}_{rs} \right) \left( \eta_{tr}^{(1)} v_{pqts} - f_{tr}
+\eta_{pqts}^{(2)}\right) \notag \\ & +\frac{1}{2}\sum_{ab}
+\left(\eta_{pqab}^{(2)} v_{abrs} - v_{pqab}\eta_{abrs}^{(2)}\right) -
+\frac{1}{2}\sum_{ij} \left(\eta_{pqij}^{(2)} v_{ijrs} -
+v_{pqij}\eta_{ijrs}^{(2)}\right) \notag \\ & -\sum_{ia} \left( 1-
+\hat{P}_{ia} \right) \left( 1-\hat{P}_{pq}\right) \left( 1-\hat{P}_{rs} \right)
 \eta_{aqis}^{(2)}v_{ipar}.
@@
 the generator~$\hat{\eta}$. Through different choices, the SRG flow
-can be adapted to the features of a particular problem.\\
-
-\paragraph*{Wegner's canonical generator}
+can be adapted to the features of a particular problem.
+
+\subsubsection*{Wegner's canonical generator}
+
 The original choice, suggested by Wegner \cite{PhysRepWegner0}, reads
-\be \hat{\eta} = \left[ \Hd, \Ho \right] = \left[ \Hd, \hat{H}
-  \right].
+\begin{equation}
+  \hat{\eta}_{\text{Wegner}}
+  = \left[ \hat{H}_{\text{diagonal}}, \hat{H}_{\text{off-diagonal}} \right]
+  = \left[ \hat{H}_{\text{off-diagonal}}, \hat{H} \right].
   \label{eq:etaWegner}
-\ee As commutator between two Hermitian operators, $\hat{\eta}$
-fulfils the criterion of antihermiticity and can be shown to suppress
-the off-diagonal matrix elements \cite{kehrein2006flow}. In general,
-matrix elements far off the diagonal, where the Hamiltonian connects
-states with large energy differences, are suppressed much faster than
-elements closer to the diagonal. \\ Evaluating the commutator, we get
-for the one- and two-body elements
-\begin{align*}
-\eta_{pq}^{(1)} = & \sum_{r}\lb f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \rb
-+ f_{pq} v_{qppq}^d \lb n_q - n_p \rb \\ \eta_{pqrs}^{(2)} = & -
-\sum_t \left\lbrace \lb 1-\hat{P}_{pq} \rb f_{pt} v_{tqrs}^d - \lb 1 -
-\hat{P}_{rs} \rb f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t
-\left\llb \lb 1 - \hat{P}_{pq} \rb f_{pt}^d v_{tqrs} - \lb 1 -
-\hat{P}_{rs} \rb f_{tr}^d v_{pqts} \right\rrb \notag \\ & +
-\frac{1}{2} \sum_{tu} (1 - n_t - n_u) \lb v_{pqtu}^d v_{turs} -
-v_{pqtu} v_{turs}^d \rb \notag \\ & + \sum_{tu} \lb n_t - n_u \rb \lb
-1 - \hat{P}_{pq} \rb \lb 1 - \hat{P}_{rs} \rb v_{tpur}^d v_{uqts},
+\end{equation}
+The commutator between two Hermitian operators, $\hat{\eta}$ is always
+antihermitian, as required for a generator.  Additionally, it can be shown that the commutator to suppress the off-diagonal matrix elements
+\cite{kehrein2006flow}. In general, matrix elements far off the diagonal,
+where the Hamiltonian connects states with large energy differences, are
+suppressed much faster than elements closer to the diagonal. \\ Evaluating the
+commutator, we get for the one- and two-body elements
+\begin{align*}
+\eta_{pq}^{(1)} = & \sum_{r}\left( f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \right)
++ f_{pq} v_{qppq}^d \left( n_q - n_p \right) \\ \eta_{pqrs}^{(2)} = & -
+\sum_t \left\lbrace \left( 1-\hat{P}_{pq} \right) f_{pt} v_{tqrs}^d - \left( 1 -
+\hat{P}_{rs} \right) f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t
+\left\lbrace \left( 1 - \hat{P}_{pq} \right) f_{pt}^d v_{tqrs} - \left( 1 -
+\hat{P}_{rs} \right) f_{tr}^d v_{pqts} \right\rbrace \notag \\ & +
+\frac{1}{2} \sum_{tu} (1 - n_t - n_u) \left( v_{pqtu}^d v_{turs} -
+v_{pqtu} v_{turs}^d \right) \notag \\ & + \sum_{tu} \left( n_t - n_u \right) \left(
+1 - \hat{P}_{pq} \right) \left( 1 - \hat{P}_{rs} \right) v_{tpur}^d v_{uqts},
 \end{align*}
@@
 
-\paragraph*{White's generator}
+\subsubsection*{White's generator}
 Apart from this canonical generator, there exist several other ones in
-literature. One of them is White's choice
-\cite{White:cond-mat0201346}, which makes numerical approaches much
-more efficient.  The problem with Wegner's generator are the widely
+literature. One choice, proposed by White
+\cite{White:cond-mat0201346}, makes numerical approaches much
+more efficient.  The problem with Wegner's generator is the widely
 varying decaying speeds of the elements, removing first terms with
@@
 coupled differential equations, which often gets numerically
-unstable.\\ White takes an alternative approach, which is especially
+unstable.
+
+White takes an alternative approach, which is especially
 suited for problems where one is interested in the ground state of a
@@
 the reference state from the remaining Hamiltonian. With a suitable
-transformation, the elements get similar decaying speeds, which solves
-the problem of stiffness of the flow equations.  The generator is
+transformation, the elements would decay near the same rate, solving
+the stiffness problem in the flow equations.  The generator is
 explicitly constructed the following way
@@
 \begin{align}
-\hat{\eta} &= \sum_{ai} \frac{f_{ai}}{f_a-f_i-v_{aiai}}\lbrace a_a\da a_i\rbrace -\text{hc} \notag \\ & + \sum_{abij}
-\frac{v_{abij}}{f_a+f_b-f_i-f_j+A_{abij}}\lbrace a_a\da a_b\da a_j
-a_i\rbrace - \text{hc},
+\hat{\eta}_{\text{White}} &\equiv \hat{\eta}'_{\text{White}} - \hat{\eta}'{}^\dagger_{\text{White}} \text{ where} \notag \\
+\hat{\eta}'_{\text{White}} &\equiv \sum_{ai} \frac{f_{ai}}{f_a-f_i-v_{aiai}}\lbrace a_a^\dagger a_i\rbrace \notag \\ & + \sum_{abij}
+\frac{v_{abij}}{f_a+f_b-f_i-f_j+A_{abij}}\lbrace a_a^\dagger a_b^\dagger a_j
+a_i\rbrace,
 \label{eq:WhiteFull}
 \end{align}
-with $f_p \equiv f_{pp}$, 'hc' denoting the Hermitian conjugate, and
+with $f_p \equiv f_{pp}$ and
 \[
@@
 
-The equations representing the DMC algorithm is obtained by applying the projection operator $\OP{P}(\tau)$ on the crude trial state $\ket{\Psi_T}$
+The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_T}$
 \begin{equation}
- \OP{P}(\tau)\ket{\Psi_T} \equiv \exp\left({-(\OP{H} - E_0)\tau}\right)\ket{\Psi_T}
+ \hat{P}(\tau)\ket{\Psi_T} \equiv \exp\left({-(\hat{H} - E_0)\tau}\right)\ket{\Psi_T}
 \end{equation}
 \noindent
-where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\OP{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\OP{H}$.
-By expanding the trial state in the eigenfunctions of $\OP{H}$, the ground state is obtained up to a constant factor
+where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\hat{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\hat{H}$.
+By expanding the trial state in the eigenfunctions of $\hat{H}$, the ground state is obtained up to a constant factor
 
@@
  \label{eq:DMC_ExactProjection}
- \lim_{\tau\to\infty} \bra{\mathbf{r}}  \OP{P}(\tau) \ket{\Psi_T} = \braket{\Psi_0}{\Psi_T}\Psi_0(\mathbf{r}).
+ \lim_{\tau\to\infty} \bra{\mathbf{r}}  \hat{P}(\tau) \ket{\Psi_T} = \braket{\Psi_0}{\Psi_T}\Psi_0(\mathbf{r}).
 \end{equation}
 
-Defining $\Phi(\mathbf{r}, \tau) \equiv \bra{\mathbf{r}}\OP{P}(\tau)\ket{\Psi_T}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
+Defining $\Phi(\mathbf{r}, \tau) \equiv \bra{\mathbf{r}}\hat{P}(\tau)\ket{\Psi_T}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
 
@@
  \Phi(\mathbf{r}, \tau + \delta\tau) &= \bra{\mathbf{r}} P(\tau + \delta\tau) \ket{\Psi_T} \notag\\
- &= \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right) \OP{P}(\tau) \ket{\Psi_T} \notag\\
- &= \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
- &= \int \mathrm{d}\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\OP{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
+ &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \hat{P}(\tau) \ket{\Psi_T} \notag\\
+ &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
+ &= \int \mathrm{d}\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
  &\equiv \int \mathrm{d}\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
@@
 
-The Green's function introduced in Eq.~(\ref{eq:DMC_GreenFuncRevealed}) has singularities due to the the Coulomb interaction term in $\OP{H}$.
+The Green's function introduced in Eq.~(\ref{eq:DMC_GreenFuncRevealed}) has singularities due to the the Coulomb interaction term in $\hat{H}$.
 Due to Pauli exclusion these are not physical, nevertheless, in numerical implementations they are unpredictable and undesirable, hence we want to avoid them.
@@
 \begin{equation}
-E_L(\mathbf{r}) = \Psi_T(\mathbf{r})^{-1}\OP{H} \Psi_T(\mathbf{r})
+E_L(\mathbf{r}) = \Psi_T(\mathbf{r})^{-1}\hat{H} \Psi_T(\mathbf{r})
 \end{equation}
@@
 would give insight into the significance of higher correlations and it
-would allow to analyse the convergence behaviour of the IM-SRG
+would allow to analyse the convergence behavior of the IM-SRG
 hierarchy of truncation. However, since this is expected to be

### 2016-09-14 Manuscript/paper.tex
Update paper

@@
 \newcommand{\D}{\operatorname{d\!}}
-\newcommand{\ket}[1]{\left| #1 \right>}
-\newcommand{\bra}[1]{\left< #1 \right|}
-\newcommand{\braket}[2]{\left\langle #1 | #2\right\rangle}
+\newcommand{\ket}[1]{| #1 \rangle}
+\newcommand{\bra}[1]{\langle #1 |}
+\newcommand{\braket}[2]{\langle #1 | #2\rangle}
 \newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
@@
 \begin{align*}
-  \hat H \equiv \sum_{p} \bigl(
+  \hat H \equiv \hat H^{\text o} + \hat V = \sum_{p} \bigl(
     t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
@@
 
-The full problem is not a trivial one.  We shall first consider a much simpler
-problem: a noninteracting Hamiltonian $\hat H^{\text o}$ in which the Coulomb
-interaction $v$ is removed:
+The full problem is not a trivial one.
+We shall first consider a much simpler problem: the noninteracting part of the Hamiltonian, $\hat H^{\text o}$, which does not contain the Coulomb interaction $v$:
 \begin{align} \label{eq:onebodyhamiltonian}
@@
   &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
-  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}.
-\end{align*}
+  &\{\hat a_p, \hat a_q^\dagger\} = [p = q].
+\end{align*}
+where $[P]$ denotes the Iverson bracket, which returns $1$ if the predicate $P$ is true and $0$ otherwise.
+Here, $[p = q]$ is simply an alternative way to denote the Kronecker delta $\delta_{p, q}$, but this notation will be used later for other kinds of predicates as well.
+
 Operators can be rewritten in this formalism as well.  The one-body
@@
 $V_{p, q, r, s} \equiv \langle \varnothing_{p, q} | \hat V | \varnothing_{r, s} \rangle$.
+The complete Hamiltonian is given by their sum:
+\begin{align}
+  \hat{H} = \sum_{p, q} H^{\text o}_{p, q} \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
+\end{align}
 Note that due to the antisymmetry present in the Slater determinants, we have
@@
 Hartree-Fock (HF) method.  Using the variational principle, we compute an
-approximate ground state $\Psi^{\text{HF}}$ by minimizing the energy
-\begin{align*}
-  E^{\text{HF}} \equiv \langle \Psi^{\text{HF}} | \hat H | \Psi^{\text{HF}} \rangle
-\end{align*}
-with respect to $\Psi^{\text{HF}}$, subject to the restriction that
-$\Psi^{\text{HF}}$ is a single Slater determinant constructed from an unknown
+approximate ground state $\Psi_{\text{HF}}$ by minimizing the energy
+\begin{align*}
+  E_{\Psi_{\text{HF}}} \equiv \langle \Psi_{\text{HF}} | \hat H | \Psi_{\text{HF}} \rangle
+\end{align*}
+with respect to $\Psi_{\text{HF}}$, subject to the restriction that
+$\Psi_{\text{HF}}$ is a single Slater determinant constructed from an unknown
 set of $N$ orthonormal single-particle states.  We denote each unknown
@@
 To ensure the orthonormality of the states, we assume the set of unknown
-states $\{\psi_u\}$ has as many elements as the set of $\{\phi_pp\}$ and
+states $\{\psi_u\}$ has as many elements as the set of $\{\phi_p\}$ and
 require the coefficient matrix $\bm C$ to be unitary.  While these conditions
@@
 of states $\psi$ now consists of $N$ \textit{occupied} states that participate
-in the Slater determinant $\Psi^{\text{HF}}$ and the remaining
+in the Slater determinant $\Psi_{\text{HF}}$ and the remaining
 \textit{unoccupied} states that do not.
@@
 variational problem has been reduced to that of solving of the coefficients
-$\bm C$ that minimize the energy $E$, which is given by
-\begin{align*}
-  E^{\text{HF}} = \sum_{\underline u} C_{p, \underline u}^* H_{p, q}^{\text o} C_{q, \underline u}^{}
-  + \sum_{\underline u, \underline v}
-  C_{p, \underline u}^* C_{q, \underline v}^* V_{p, q, r, s}^{} C_{r, \underline u}^{} C_{s, \underline v}^{}
-\end{align*}
-where the underlined indices indicate that the summation is over occupied
-states only.
+$\bm C$ that minimize the energy $E_{\Psi_{\text{HF}}}$, which is given by
+\begin{align}
+  E_{\Psi_{\text{HF}}} &= \sum_{u \in \text{occ.}} C_{p, u}^* H_{p, q}^{\text o} C_{q, u}^{}
+  \notag \\ &\hphantom{{}=} + \sum_{u, v \in \text{occ.}}
+  C_{p, u}^* C_{q, v}^* V_{p, q, r, s}^{} C_{r, u}^{} C_{s, v}^{} \label{eq:hfenergy}
+\end{align}
 
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{\underline u r s}
-  C_{r, \underline u}^* V_{p, r, q, s}^{} C_{s, \underline u}^{}
+  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{r, s \in \text{any}; u \in \text{occ.}}
+  C_{r, u}^* V_{p, r, q, s}^{} C_{s, u}^{}
 \end{align}
 and $\bm \epsilon$ is a vector of Lagrange multipliers with each element
-$\epsilon_u$ associated with a particular state $u$.  [[move this sentence
+$\epsilon_u$ associated with a particular state $\psi_u$.  [[move this sentence
 later to the intro to normal-ordering: While the Fock matrix $\bm F$ may
@@
 non-vacuum state, however.  Consider a Slater determinant $\Phi$ with
-$N_{\text F}$ occupied states.  One can define a set of \textit{quasiparticle
+$N_{\text F}$ occupied states:
+\begin{align*}
+  \ket{\Phi} \equiv \ket{\varnothing_{i_1, i_2, \ldots, i_{N_{\text F}}}}
+\end{align*}
+Here $\{i_1, i_2, \ldots, i_{N_{\text F}}\}$ is a set of $N_{\text F}$ indices that label the occupied states.
+
+One can define a set of \textit{quasiparticle
   field operators} $\hat b$ and $\hat b^\dagger$ that obey the same
@@
 \begin{align*}
-  \hat b_p \equiv \hat a_{\overline p} + \hat a_{\underline p}^\dagger = \begin{cases}
-    \hat a_{\overline p} & \text{if $\overline p$ is unoccupied in $\Phi$} \\
-    \hat a_{\underline p}^\dagger & \text{if $\underline p$ is occupied in $\Phi$}
+  \hat b_p \equiv \begin{cases}
+    \hat a_{p} & \text{if $p$ is unoccupied in $\Phi$} \\
+    \hat a_{p}^\dagger & \text{if $p$ is occupied in $\Phi$}
   \end{cases}
 \end{align*}
-Here we use an underline to indicate that only an occupied state is accepted
-and an overline to indicate only an unoccupied state is accepted.  If the
-state is not acceptable, then that term does not contribute to the overall
-expression.
-
-We can then define normal ordering with respect to the reference state $\Phi$:
-namely, rearrange an operator string such that every creation operator appears
-before an annihilation operator by repeatedly exchanging neighboring
-operators, with each exchange costing a minus sign.  In this form, it is
-guaranteed that the expectation value of the operator string with respect to
+The quasiparticle field operators consider $\ket{\Phi}$ to be their ``vacuum state'' (sometimes called ``Fermi vaccuum''), even though it is not a true vacuum state.
+Analogously, it is possible to construct any other Slater determinant by applying quasiparticle operators on top of the reference state:
+\begin{align*}
+  \ket{\Phi_{p_1, \ldots, p_k}} \equiv \hat{b}^\dagger_{p_1} \cdots \hat{b}^\dagger_{p_k} \ket{\Phi}
+\end{align*}
+In nonrelativistic many-body theory, it is expected that $\{p_1, \ldots, p_k\}$ contain a balanced number of occupied and unoccupied states to conserve the total number of particles.
+
+We can then define normal ordering with respect to the reference state $\Phi$: namely, rearrange an operator string such that every quasiparticle creation operator appears before a quasiparticle annihilation operator by repeatedly exchanging neighboring operators, with each exchange costing a minus sign.
+In this form, it is guaranteed that the expectation value of the operator string with respect to
 $\Phi$ is zero:
@@
 \begin{align*}
-  \normord{\hat{a}_p^\dagger \hat{a}_q} =
-  -\hat{a}_{\underline q} \hat{a}_{\underline p}^\dagger
-  + \hat{a}_{\underline p}^\dagger \hat{a}_{\overline q}
-  + \hat{a}_{\overline p}^\dagger \hat{a}_{\underline q}
-  + \hat{a}_{\overline p}^\dagger \hat{a}_{\overline q} =
-  -\delta_{\underline q \underline p}
-  + \hat{a}_p^\dagger \hat{a}_q
-\end{align*}
-This makes the normal ordering notation a useful and concise way of expressing
-the right-hand side.
+  \normord{\hat{a}_p^\dagger \hat{a}_q} &=
+  \hat{a}_p^\dagger \hat{a}_q - [p, q \in \text{occ.} \text{ and } p = q]
+\end{align*}
+This makes the normal ordering notation a useful and concise way of expressing the right-hand side.
 
@@
 $\hat H = \hat H^{\text o} + \hat V$ as
-\begin{align*}
-  \hat{H} = E + \sum_{p, q} F_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
-\end{align*}
+\begin{align}
+  \hat{H} = E_\Phi + \sum_{p, q} F_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
+  \label{eq:normordhamiltonian}
+\end{align}
 where
 \begin{align*}
-  E &= \sum_{\underline p} H^{\text o}_{\underline p, \underline p} + \frac{1}{2} \sum_{\underline p, \underline q} V_{\underline p, \underline q, \underline p, \underline q} \\
-  F_{p, q} &= H^{\text o}_{\underline p, \underline q} + \sum_{\underline r} V_{\underline p, \underline r, \underline q, \underline r} \\
-\end{align*}
-Notice that $E$ is in fact the Hartree-Fock energy and $F_{p, q}$ is the Fock matrix.
+  E_\Phi &= \sum_{i \in \text{occ.}} H^{\text o}_{i, i} + \frac{1}{2} \sum_{i, j \in \text{occ.}} V_{i, j, i, j} \\
+  F_{p, q} &= H^{\text o}_{p, q} + \sum_{i \in \text{occ.}} V_{p, i, q, i} \\
+\end{align*}
+Notice that $E_\Phi$ is in fact the Hartree-Fock energy and $F_{p, q}$ is the Fock matrix.
+The representation of $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to that of $\hat H$ in \eqref{eq:vacuumhamiltonian}.
+The only difference is that it shuffles the matrix elements so as to put the reference state $\ket{\Phi}$ into the main focus, as opposed to the vacuum state $\ket{\varnothing}$.
+Where this makes a crucial difference is when the equations become \emph{truncated}.
 
@@
 
-The commutator in the flow equations (\ref{eq:imsrgode}) guarantees that the
-IM-SRG wave function $U^\dagger(s) \ket{\Phi}$ can be expanded in terms of
+The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the
+IM-SRG wave function $\hat U(s) \ket{\Phi}$ can be expanded in terms of
 linked diagrams only \cite{shavitt2009many,ISI:A1981MN73700014}, which
@@
 
-With this truncation, the generator
-$\hat{\eta}$ can be written as
-\[
-\hat{\eta} = \sum_{pq} \eta_{pq}^{(1)} \lbrace a_p^\dagger a_q\rbrace +
-\frac{1}{4}\sum\limits_{pqrs}\eta_{pqrs}^{(2)} \lbrace a_p^\dagger a_q^\dagger a_s
-a_r \rbrace,
-\]
-where $\eta_{pq}^{(1)}$ and $ \eta_{pqrs}^{(2)}$ are the one- and
-two-body elements, respectively. Making use of the permutation
-operator $ \hat{P}_{pq}f(p,q) = f(q,p)$, the IM-SRG(2) flow equations
-are given by
-% [[fix the equations to avoid requiring (anti)hermittivity in H]]
+With this truncation, the generator $\hat{\eta}$ can be written as
+\begin{align*}
+\hat{\eta} = \sum_{p, q} \eta_{p, q}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
+\frac{1}{4} \sum_{p, q, r, s}\eta_{p, q, r, s}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r}
+\end{align*}
+where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ are the one- and two-body elements respectively.
+For consistency, we define $H^{[0]} \equiv E_\Phi$, $H^{[1]}_{p, q} \equiv F_{p, q}$, and $H^{[2]}_{p, q, r, s} \equiv V_{p, q, r, s}$ as well.
+
+By expanding the commutator in \eqref{eq:imsrgode} and dropping the three-body term, we obtain the IM-SRG(2) flow equations:
 \begin{widetext}
   \begin{align}
-\frac{\D E}{\D s} &= \sum_{\underline p, \overline q} \left(\eta_{\underline p, \overline q} F_{a, \underline p} - \eta_{\overline q, \underline p} f_{\underline p, \overline q}\right) + \frac{1}{2} \sum_{\underline p, \underline q, \overline r, \overline s} \eta_{\underline p, \underline q, \overline r, \overline s} V_{\overline r, \overline s, \underline p, \underline q},
-\label{eq:flow1}\\
-\frac{\D F_{p, q}}{ds}&= \sum_r \left( \eta_{pr}^{(1)}f_{rq} +
-\eta_{qr}^{(1)}f_{rp}\right) + \sum_{ia}\left( 1-\hat{P}_{ia}\right) \left(
-\eta_{ia}^{(1)}v_{apiq} - f_{ia}\eta_{apiq}^{(2)} \right) \notag \\ &
-+\frac{1}{2} \sum_{aij} \left( 1+\hat{P}_{pq}\right)
-\eta_{apij}^{(2)}v_{ijaq} + \frac{1}{2}\sum_{abi}\left( 1+\hat{P}_{pq}\right)
-\eta_{ipab}^{(2)}v_{abiq},
-\label{eq:flow2}
-\end{align}
-\begin{align}
-\frac{\D V_{p, q, r, s}}{ds} &= \sum_t \left( 1-\hat{P}_{pq} \right) \left(
-\eta_{pt}^{(1)}v_{tqrs}-f_{pt}\eta_{tqrs}^{(2)}\right) -\sum_t \left(
-1-\hat{P}_{rs} \right) \left( \eta_{tr}^{(1)} v_{pqts} - f_{tr}
-\eta_{pqts}^{(2)}\right) \notag \\ & +\frac{1}{2}\sum_{ab}
-\left(\eta_{pqab}^{(2)} v_{abrs} - v_{pqab}\eta_{abrs}^{(2)}\right) -
-\frac{1}{2}\sum_{ij} \left(\eta_{pqij}^{(2)} v_{ijrs} -
-v_{pqij}\eta_{ijrs}^{(2)}\right) \notag \\ & -\sum_{ia} \left( 1-
-\hat{P}_{ia} \right) \left( 1-\hat{P}_{pq}\right) \left( 1-\hat{P}_{rs} \right)
-\eta_{aqis}^{(2)}v_{ipar}.
-\label{eq:flow3}
+    \frac{\mathrm{d} H^{[0]}}{\mathrm{d} s}
+    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
+      \sum_{i, a} \eta^{[1]}_{i, a} H^{[1]}_{a, i}
+      + \frac{1}{4} \sum_{i, j, a, b} \eta^{[2]}_{i, j, a, b} H^{[2]}_{a, b, i, j}
+    \Biggr) \label{eq:flow0} \\
+    \frac{\mathrm{d} H^{[1]}_{p, q}}{\mathrm{d} s}
+    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
+      \sum_{r} \eta^{[1]}_{p, r} H^{[1]}_{r, q}
+      - \frac{1}{2} \sum_{a, i, j} \eta^{[2]}_{i, j, a, q} H^{[2]}_{a, p, i, j}
+      + \frac{1}{2} \sum_{a, b, i} \eta^{[2]}_{i, p, a, b} H^{[2]}_{a, b, i, q}
+      + \sum_{a, i} \bigl(
+        \eta^{[1]}_{i, a} H^{[2]}_{a, p, i, q}
+        + \eta^{[2]}_{i, p, a, q} H^{[1]}_{a, i}
+      \bigr)
+    \Biggr) \label{eq:flow1} \\
+    \frac{\mathrm{d} H^{[2]}_{p, q, r, s}}{\mathrm{d} s}
+    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
+      \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s}
+        \sum_{a, i} \eta^{[2]}_{i, p, a, r} H^{[2]}_{a, q, i, s}
+      + \frac{1}{2} \sum_{i, j} \eta^{[2]}_{i, j, r, s} H^{[2]}_{p, q, i, j}
+      + \frac{1}{2} \sum_{a, b} \eta^{[2]}_{p, q, a, b} H^{[2]}_{a, b, r, s}
+      \notag \\ &\hphantom{{}=\tilde{\mathcal{A}}_{\eta, H} \Biggl(}
+      + \sum_{t} \bigl(
+        \tilde{\mathcal{A}}_{p, q} \eta^{[1]}_{q, t} H^{[2]}_{p, t, r, s}
+        + \tilde{\mathcal{A}}_{r, s} \eta^{[2]}_{p, q, r, t} H^{[1]}_{t, s}
+      \bigr)
+    \Biggr) \label{eq:flow1}
 \end{align}
 \end{widetext}
-Note that for brevity, we skip all $s$-dependence in the equations.
+Note that for brevity, we skip all the $s$ parameter in the equations and make use of the unnormalized antisymmetrizer $\tilde{\mathcal{A}}_{x, y} f(x, y) \equiv f(x, y) - f(y, x)$.
+We also use the convention that $i, j$ denote indices of occupied states, $a, b$ denote indices of unoccupied states, and $p, q, r, s, t$ denote indices of any state.
 
@@
   = \left[ \hat{H}_{\text{diagonal}}, \hat{H}_{\text{off-diagonal}} \right]
-  = \left[ \hat{H}_{\text{off-diagonal}}, \hat{H} \right].
+  = \left[ \hat{H}_{\text{diagonal}}, \hat{H} \right].
   \label{eq:etaWegner}

### 2016-10-06 Manuscript/paper.tex
spEnergiesQD: reorder indices in \sum
Update spEnergiesQD/Manuscript/paper.tex

@@
 
-The harmonic oscillator (HO) is a ubiquitous system in quantum physics. It is
-the basis for an extremely diverse set of many-body calculations -- in nuclear
-physics \cite{HjorthJensen1995}, quantum chemistry \cite{Helgaker2002}, and
-quantum dot calculations of solid state physics \cite{Reimann2002}. In these
-calculations, one typically seeks a few of the lowest eigenvalues $E_k$ and
-eigenvectors of a many-body Hamiltonian $\hat{H}$ that describes the full
-system by solving the Schr\"odinger equation,
+The harmonic oscillator (HO) is a ubiquitous system in quantum physics.
+It is the basis for an extremely diverse set of many-body calculations -- in nuclear physics \cite{HJORTHJENSEN1995125}, quantum chemistry \cite{Helgaker2002} [[missing ref for Helgaker 2002]], and quantum dot calculations of solid state physics \cite{reimann2002}.
+In these calculations, one typically seeks a few of the lowest eigenvalues $E_k$ and eigenvectors of a many-body Hamiltonian $\hat{H}$ that describes the full system by solving the Schr\"odinger equation,
 \begin{equation*}
@@
 
-The HO eigenfunctions are popular for several reasons. Many quantum systems,
-such as the quantum dot model considered here, can be considered perturbed
-harmonic oscillators \textit{per se}, thus the true eigenstates should be
-perturbations of the HO eigenstates.  Moreover, the HO has many beautiful
-properties, such as separability, invariance under orthogonal coordinate
-changes, and easily computable eigenfunctions, so that computing matrix
-elements of relevant operators becomes relatively simple.  Since HO
-eigenfunctions are defined on the \emph{entire} space in which particles live,
-a truncation of the spatial domain is unnecessary.  This avoids one of the
-main problems with approaches such as finite difference or finite element
-methods.\cite{RamMohan2002}
+The HO eigenfunctions are popular for several reasons.
+Many quantum systems, such as the quantum dot model considered here, can be considered perturbed harmonic oscillators \textit{per se}, thus the true eigenstates should be perturbations of the HO eigenstates.
+Moreover, the HO has many beautiful properties, such as separability, invariance under orthogonal coordinate changes, and easily computable eigenfunctions, so that computing matrix elements of relevant operators becomes relatively simple.
+Since HO eigenfunctions are defined on the \emph{entire} space in which particles live, a truncation of the spatial domain is unnecessary.
+This avoids one of the main problems with approaches such as finite difference or finite element methods.\cite{RamMohan2002} [[Unknown citation]]
 
@@
 \begin{align*}
-  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
-  &\{\hat a_p, \hat a_q^\dagger\} = [p = q].
-\end{align*}
-where $[P]$ denotes the Iverson bracket, which returns $1$ if the predicate $P$ is true and $0$ otherwise.
-Here, $[p = q]$ is simply an alternative way to denote the Kronecker delta $\delta_{p, q}$, but this notation will be used later for other kinds of predicates as well.
+  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0 &
+  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}
+\end{align*}
+where $\delta_{p, q}$ denotes the Kronecker delta.
 
@@
 Hartree-Fock (HF) method.  Using the variational principle, we compute an
-approximate ground state $\Psi_{\text{HF}}$ by minimizing the energy
-\begin{align*}
-  E_{\Psi_{\text{HF}}} \equiv \langle \Psi_{\text{HF}} | \hat H | \Psi_{\text{HF}} \rangle
-\end{align*}
-with respect to $\Psi_{\text{HF}}$, subject to the restriction that
-$\Psi_{\text{HF}}$ is a single Slater determinant constructed from an unknown
+approximate ground state $\Phi$ by minimizing the energy expectation value
+\begin{align*}
+  E_{\Phi} \equiv \langle \Phi | \hat H | \Phi \rangle
+\end{align*}
+with respect to $\Phi$, subject to the restriction that
+$\Phi$ is a single Slater determinant constructed from an unknown
 set of $N$ orthonormal single-particle states.  We denote each unknown
-single-particle state $\psi_u$ by some label $u$.
+single-particle state $\phi_{q}'$ by some label $q$.
 
 To make this computationally feasible, we further assume that the unknown
-states $\{\psi_u\}$ are built from a linear combination of known functions,
+states $\{\phi_q'\}$ are built from a linear combination of known functions,
 drawn from a finite set $\{\phi_p\}$.  This reduces the problem from an
@@
 states $\{\phi_p\}$ of our noninteracting Hamiltonian as a basis for the
-unknown states $\{\psi_u\}$.  The two sets of states are then related by a
+unknown states $\{\phi'_u\}$.  The two sets of states are then related by a
 linear transformation matrix $\bm C$:
 \begin{align*}
-  \psi_u \equiv \sum_p \phi_p C_{p, u}
-\end{align*}
-To ensure the orthonormality of the states, we assume the set of unknown
-states $\{\psi_u\}$ has as many elements as the set of $\{\phi_p\}$ and
-require the coefficient matrix $\bm C$ to be unitary.  While these conditions
-are more strict than necessary, they greatly simplify the calculations and
-allow the states $\{\psi_u\}$ to act as inputs for methods beyond HF.  The set
-of states $\psi$ now consists of $N$ \textit{occupied} states that participate
-in the Slater determinant $\Psi_{\text{HF}}$ and the remaining
-\textit{unoccupied} states that do not.
-
-Since the coefficient matrix uniquely determines the unknown states, the
-variational problem has been reduced to that of solving of the coefficients
-$\bm C$ that minimize the energy $E_{\Psi_{\text{HF}}}$, which is given by
+  \phi_q' \equiv \sum_p \phi_p C_{p, q}
+\end{align*}
+To ensure the orthonormality of the states, we assume the set of unknown states $\{\phi_q'\}$ has as many elements as the set of $\{\phi_p\}$ and require the coefficient matrix $\bm C$ to be unitary.
+While these conditions are more strict than necessary, they greatly simplify the calculations and allow the states $\{\phi_q'\}$ to act as inputs for methods beyond HF.
+The set of states $\{\phi_q'\}$ now consists of $N$ \textit{occupied} states that participate in the Slater determinant $\Phi$ and the remaining \textit{unoccupied} states that do not.
+
+Since the coefficient matrix uniquely determines the unknown states, the variational problem has been reduced to that of solving of the coefficients $\bm C$ that minimize the energy $E_{\Phi}$, which is given by
 \begin{align}
-  E_{\Psi_{\text{HF}}} &= \sum_{u \in \text{occ.}} C_{p, u}^* H_{p, q}^{\text o} C_{q, u}^{}
-  \notag \\ &\hphantom{{}=} + \sum_{u, v \in \text{occ.}}
-  C_{p, u}^* C_{q, v}^* V_{p, q, r, s}^{} C_{r, u}^{} C_{s, v}^{} \label{eq:hfenergy}
-\end{align}
-
-Using the method of Lagrange multiplers, the minimization problem can be
-reduced to the solving of a nonlinear equation -- the \textit{Hartree-Fock
-  equation}:
+  E_{\Phi} &= \sum_{j} n_j H^{\text{o} \prime}_{j, j} + \sum_{j, k} n_j n_k V'_{j, k, j, k} \label{eq:hfenergy}
+\end{align}
+where the transformed operators are defined as
+\begin{align}
+  H^{\text{o} \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* H_{r, s}^{\text o} C_{s, q}^{} \label{eq:hftransform1} \\
+  V'_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* V_{t, u, v, w}^{} C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
+\end{align}
+and the occupancy number $n_p$ is defined as
+\begin{align}
+  n_p \equiv \begin{cases}
+    1 & \text{if $p$ is an occupied state in $\Phi$} \\
+    0 & \text{if $p$ is an unoccupied state in $\Phi$}
+  \end{cases}
+\end{align}
+and further define $\bar n_p \equiv 1 - n_p$ as the complement.
+
+With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree-Fock equation}:
 \begin{align} \label{eq:hartreefock}
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{r, s \in \text{any}; u \in \text{occ.}}
-  C_{r, u}^* V_{p, r, q, s}^{} C_{s, u}^{}
-\end{align}
-and $\bm \epsilon$ is a vector of Lagrange multipliers with each element
-$\epsilon_u$ associated with a particular state $\psi_u$.  [[move this sentence
-later to the intro to normal-ordering: While the Fock matrix $\bm F$ may
-appear to be an artificial Hamiltonian derived purely from the minimization
-problem, it can be considered the normal-ordered operator with respect to a
-non-vacuum state, as explained later.]]
-
-The HF equation can be solved by an iterative technique: a solution $\bm C$
-can be fed into \eqref{eq:fock} and new solution can then obtained by solving
-the eigenvalue problem in \eqref{eq:hartreefock} using the Fock matrix
-obtained.  For the initial guess, we use the ground state of our
-noninteracting Hamiltonian, thus $\bm C$ is initially the identity matrix.
+  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{r, s, j} n_j C_{r, j}^* V_{p, r, q, s}^{} C_{s, j}^{}
+\end{align}
+and $\bm \epsilon$ is a vector of Lagrange multipliers with each element $\epsilon_q$ associated with a particular state $\phi'_q$.
+
+The HF equation can be solved by an iterative technique: a solution $\bm C$ can be fed into \eqref{eq:fock} and new solution can then obtained by solving the eigenvalue problem in \eqref{eq:hartreefock} using the Fock matrix obtained.
+For the initial guess, we use the ground state of our noninteracting Hamiltonian, thus $\bm C$ is initially the identity matrix.
+After dozens of iterations, perhaps with the aid of a convergence acceleration technique (such as DIIS [[cite??] or Broyden's method [[cite?]]), one would usually reach a state of self-consistency where the solution converges to a fixed value.
+This is the Hartree-Fock solution.
 
@@
 
-\subsection{The SRG methods}
+To make use of the HF solution as the reference state for future calculations, we transform the operators via \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
+Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat H^{\text{o} \prime}$ and $\hat V'$ as inputs.
+However, for generality, we omit the prime symbols as the methods do not necessitate a state optimized by HF.
+
+\subsection{The IM-SRG method}
 \label{subsec:imsrgmethod}
 
-\subsubsection*{Similarity renormalization group methods}
+\subsubsection{Similarity renormalization group methods}
+\label{subsubsec:srgmethods}
 
@@
 \end{align*}
-Here $\mathcal T_s$ is a notational device that denotes $s$-ordering: a
-reordering of the $\eta(s)$ operator products expanded from the exponential
-with respect to $s$ in ascending order \cite[\S 6.1]{reimann2013quantum}.
+Here $\mathcal T_s$ is a notational device that denotes $s$-ordering: a reordering of the $\hat{\eta}(s)$ operator products expanded from the exponential with respect to $s$ in ascending order \cite[\S 6.1]{reimann2013quantum}.
 This is analogous to the usual time-ordering from quantum field theory.
 
-The operator $\hat{\eta}(s)$ can be chosen to suppress certain undesirable
-parts of the Hamiltonian matrix, which can be considered the ``off-diagonal''
-parts in a loose sense.  The ``off-diagonal'' parts could be elements far away
-from the matrix diagonal, in which case the evolution drives the matrix
-towards a band-diagonal form.  Or, the ``off-diagonal'' parts could be
-elements that couple the ground state from the excited state, in which case
-the evolution drives the matrix towards a block-diagonal form that isolates
-the ground state.  Or, the ``off-diagonal'' could be literally the elements
-that do not lie on the diagonal, in which case the evolution would simply
-diagonalize the Hamiltonian.  Through different choices of $\hat{\eta}_s$, the
-SRG evolution can be controlled and adapted to the features of a particular
-problem.
-
-\subsubsection*{In-medium SRG}
+The operator $\hat{\eta}$ can be chosen to suppress certain undesirable parts of the Hamiltonian matrix, which can be considered the ``off-diagonal'' parts in a loose sense.
+The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
+Or, the ``off-diagonal'' parts could be elements that couple the ground state from the excited state, in which case the evolution drives the matrix towards a block-diagonal form that isolates the ground state.
+Or, the ``off-diagonal'' could be literally the elements that do not lie on the diagonal, in which case the evolution would simply diagonalize the Hamiltonian.
+Through different choices of $\hat{\eta}$, the SRG evolution can be controlled and adapted to the features of a particular problem.
+
+\subsubsection{Evolving the flow equation in medium}
 
@@
 \end{align*}
-Here $\{i_1, i_2, \ldots, i_{N_{\text F}}\}$ is a set of $N_{\text F}$ indices that label the occupied states.
-
-One can define a set of \textit{quasiparticle
-  field operators} $\hat b$ and $\hat b^\dagger$ that obey the same
-anticommutation relations as the $\hat a$ operators.  The field operators are
-defined as:
-\begin{align*}
-  \hat b_p \equiv \begin{cases}
-    \hat a_{p} & \text{if $p$ is unoccupied in $\Phi$} \\
-    \hat a_{p}^\dagger & \text{if $p$ is occupied in $\Phi$}
-  \end{cases}
-\end{align*}
-The quasiparticle field operators consider $\ket{\Phi}$ to be their ``vacuum state'' (sometimes called ``Fermi vaccuum''), even though it is not a true vacuum state.
-Analogously, it is possible to construct any other Slater determinant by applying quasiparticle operators on top of the reference state:
+where $\{i_1, i_2, \ldots, i_{N_{\text F}}\}$ is a set of $N_{\text F}$ indices that label the occupied states.
+One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators:
+\begin{align*}
+  \hat b_p \equiv \bar n_p \hat a_{p} + n_p \hat a_{p}^\dagger
+\end{align*}
+The quasiparticle field operators treat $\ket{\Phi}$ as their ``vacuum state'' (sometimes called ``Fermi vaccuum'' in an abstract sense), despite not being the physical vacuum state.
+As before, it is possible to construct arbitrary Slater determinants by applying quasiparticle operators to the reference state:
 \begin{align*}
@@
 \end{align*}
-In nonrelativistic many-body theory, it is expected that $\{p_1, \ldots, p_k\}$ contain a balanced number of occupied and unoccupied states to conserve the total number of particles.
-
-We can then define normal ordering with respect to the reference state $\Phi$: namely, rearrange an operator string such that every quasiparticle creation operator appears before a quasiparticle annihilation operator by repeatedly exchanging neighboring operators, with each exchange costing a minus sign.
-In this form, it is guaranteed that the expectation value of the operator string with respect to
-$\Phi$ is zero:
+In nonrelativistic many-body theory, it is expected that $\{p_1, \ldots, p_k\}$ contain a balanced number of occupied and unoccupied states to conserve the total number of particles; otherwise, the Slater determinant would represent a different system.
+
+We may then define \emph{normal ordering with respect to the reference state} $\Phi$, a notational device that rearranges a string of operators such that every quasiparticle creation operator appears before a quasiparticle annihilation operator by repeatedly exchanging neighboring operators, with each exchange incurring a change in sign.
+A simple example would be the normal ordering of a pair of field operators such as:
+\begin{align*}
+  \normord{\hat{b}_p \hat{b}_q^\dagger} =
+  -\hat{b}_q^\dagger \hat{b}_p
+\end{align*}
+Here, we denote normal ordering of an operator string with respect to $\Phi$ by a pair of colons.
+The expectation value of a normal ordered string of operators with respect to $\Phi$ is guaranteed to vanish:
 \begin{align*}
@@
 \end{align*}
-We denote normal ordering of an operator string with respect to $\Phi$ by a
-pair of colons:
-\begin{align*}
-  \normord{\hat{b}_p \hat{b}_q^\dagger} =
-  -\hat{b}_q^\dagger \hat{b}_p
-\end{align*}
-It is not particularly interesting to examine normal ordering of the
-quasiparticle field operators, since the result is trivial to compute.  What
-is more interesting is the normal ordering of the physical field operators
-$\hat a$ and $\hat a^\dagger$ with respect to $\Phi$:
+The normal ordering of the quasiparticle field operators are straightforward to compute, but what is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $\Phi$:
 \begin{align*}
   \normord{\hat{a}_p^\dagger \hat{a}_q} &=
-  \hat{a}_p^\dagger \hat{a}_q - [p, q \in \text{occ.} \text{ and } p = q]
-\end{align*}
-This makes the normal ordering notation a useful and concise way of expressing the right-hand side.
-
-Using the normal ordering formalism, we can rewrite the Hamiltonian
-$\hat H = \hat H^{\text o} + \hat V$ as
+  \hat{a}_p^\dagger \hat{a}_q - n_p \delta_{p, q}
+\end{align*}
+The normal ordering notation thus provides a concise way of expressing the right-hand side.
+In this new notation, we can rewrite the Hamiltonian $\hat H = \hat H^{\text o} + \hat V$ in its \emph{normal-ordered representation}:
 \begin{align}
-  \hat{H} = E_\Phi + \sum_{p, q} F_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
+  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
   \label{eq:normordhamiltonian}
@@
 \begin{align*}
-  E_\Phi &= \sum_{i \in \text{occ.}} H^{\text o}_{i, i} + \frac{1}{2} \sum_{i, j \in \text{occ.}} V_{i, j, i, j} \\
-  F_{p, q} &= H^{\text o}_{p, q} + \sum_{i \in \text{occ.}} V_{p, i, q, i} \\
-\end{align*}
-Notice that $E_\Phi$ is in fact the Hartree-Fock energy and $F_{p, q}$ is the Fock matrix.
-The representation of $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to that of $\hat H$ in \eqref{eq:vacuumhamiltonian}.
-The only difference is that it shuffles the matrix elements so as to put the reference state $\ket{\Phi}$ into the main focus, as opposed to the vacuum state $\ket{\varnothing}$.
-Where this makes a crucial difference is when the equations become \emph{truncated}.
-
-Integrating the flow equations (\ref{eq:imsrgode}), we face one of the
-major challenges of the SRG method, namely the generation of higher and higher
-order interaction terms during the flow.  With each evaluation of the
-commutator, the Hamiltonian gains terms of higher order, and these induced
-contributions will in subsequent integration steps contribute to terms of
-lower order.  In principle, this continues to infinity.
-
-To make the method computationally possible, we must close the IM-SRG flow
-equations: we are thus forced to truncate the equations to a certain order. We
-choose to truncate both $\hat{H}(s)$ and $\hat{\eta}(s)$ at the two-body
-level, an approach which is referred to as IM-SRG(2).  This normal-ordered
-two-body approximation appears to be sufficient in many cases and has yielded
-excellent results for several nuclei
-\cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
-
-%[[---]]
-
-The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the
-IM-SRG wave function $\hat U(s) \ket{\Phi}$ can be expanded in terms of
-linked diagrams only \cite{shavitt2009many,ISI:A1981MN73700014}, which
-suggests that IM-SRG is size-extensive.  Regarding the quality of the SRG
-results, it means that the error introduced by truncating the many-body
-expansions scales linearly with the number of particles $N$.
-
-With this truncation, the generator $\hat{\eta}$ can be written as
+  H^{[0]} &\equiv \sum_{i} n_i H^{\text o}_{i, i} + \frac{1}{2} \sum_{i, j} n_i n_j V_{i, j, i, j} \\
+  H^{[1]}_{p, q} &\equiv H^{\text o}_{p, q} + \sum_{i} n_i V_{p, i, q, i} \\
+  H^{[2]}_{p, q, r, s} &\equiv V_{p, q, r, s} \\
+\end{align*}
+If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p, q}$ is the Fock matrix $F_{p, q}$.
+The normal-ordered representation of $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to that of $\hat H$ in \eqref{eq:vacuumhamiltonian}.
+The only difference is that it rearranges the matrix elements so as to emphasize the reference state $\Phi$ rather than vacuum state $\ket{\varnothing}$.
+This makes a critical difference when the expressions containing 3-body or higher terms are \emph{truncated} to only 2-body.
+If the reference state $\Phi$ is good approximation of the true solution $\Psi$, then the importance of the higher-body parts of the Hamiltonian are greatly reduced.
+
+Higher-body operators arise from integrating the flow equations (\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
+With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
+Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy is of interest.
+
+Computationally, higher-body terms are difficult to handle: the amount of memory required to store an $r$-body operator is grows exponentially with $r$.
+Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
+Thus, to make the method tractable, we must close the IM-SRG flow equations, truncating the equations to a finite order.
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, an approach known as IM-SRG(2).
+This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+With the truncation, the generator $\hat{\eta}$ can be written as a generic antihermitian 2-body operator:
 \begin{align*}
@@
 \end{align*}
-where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ are the one- and two-body elements respectively.
-For consistency, we define $H^{[0]} \equiv E_\Phi$, $H^{[1]}_{p, q} \equiv F_{p, q}$, and $H^{[2]}_{p, q, r, s} \equiv V_{p, q, r, s}$ as well.
-
-By expanding the commutator in \eqref{eq:imsrgode} and dropping the three-body term, we obtain the IM-SRG(2) flow equations:
+where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$.
+
+By expanding the commutator in \eqref{eq:imsrgode} without consideration of the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
+\begin{align}
+    \frac{\D H^{[r]}}{\D s} = C^{[r]}(\eta, H) \label{eq:flowmxe}
+\end{align}
+where
+\begin{align}
+  C^{[r]}(A, B) &\equiv \tilde{\mathcal{A}}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
+  \tilde{\mathcal{A}}_{x, y} f(x, y) &\equiv f(x, y) - f(y, x) \text{ for any $x$, $y$, $f$}
+\end{align}
+and finally
 \begin{widetext}
   \begin{align}
-    \frac{\mathrm{d} H^{[0]}}{\mathrm{d} s}
-    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
-      \sum_{i, a} \eta^{[1]}_{i, a} H^{[1]}_{a, i}
-      + \frac{1}{4} \sum_{i, j, a, b} \eta^{[2]}_{i, j, a, b} H^{[2]}_{a, b, i, j}
-    \Biggr) \label{eq:flow0} \\
-    \frac{\mathrm{d} H^{[1]}_{p, q}}{\mathrm{d} s}
-    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
-      \sum_{r} \eta^{[1]}_{p, r} H^{[1]}_{r, q}
-      - \frac{1}{2} \sum_{a, i, j} \eta^{[2]}_{i, j, a, q} H^{[2]}_{a, p, i, j}
-      + \frac{1}{2} \sum_{a, b, i} \eta^{[2]}_{i, p, a, b} H^{[2]}_{a, b, i, q}
-      + \sum_{a, i} \bigl(
-        \eta^{[1]}_{i, a} H^{[2]}_{a, p, i, q}
-        + \eta^{[2]}_{i, p, a, q} H^{[1]}_{a, i}
-      \bigr)
-    \Biggr) \label{eq:flow1} \\
-    \frac{\mathrm{d} H^{[2]}_{p, q, r, s}}{\mathrm{d} s}
-    &= \tilde{\mathcal{A}}_{\eta, H} \Biggl(
+    D^{[0]}(A, B)
+    &\equiv
+      \sum_{i, a} n_i \bar{n}_a A^{[1]}_{i, a} B^{[1]}_{a, i}
+      + \frac{1}{4} \sum_{i, j, a, b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i, j, a, b} B^{[2]}_{a, b, i, j}
+      \label{eq:flow0} \\
+    D^{[1]}_{p, q}(A, B)
+    &\equiv
+      \sum_{r} A^{[1]}_{p, r} B^{[1]}_{r, q}
+      - \frac{1}{2} \sum_{i, j, a} n_i n_j \bar{n}_a A^{[2]}_{i, j, a, q} B^{[2]}_{a, p, i, j}
+      + \frac{1}{2} \sum_{i, a, b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i, p, a, b} B^{[2]}_{a, b, i, q}
+      \notag \\
+    &\hphantom{=}
+      + \sum_{i, a} n_i \bar{n}_a \left(
+        A^{[1]}_{i, a} B^{[2]}_{a, p, i, q}
+        + A^{[2]}_{i, p, a, q} B^{[1]}_{a, i}
+      \right)
+      \label{eq:flow1} \\
+    D^{[2]}_{p, q, r, s}(A, B)
+    &\equiv
       \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s}
-        \sum_{a, i} \eta^{[2]}_{i, p, a, r} H^{[2]}_{a, q, i, s}
-      + \frac{1}{2} \sum_{i, j} \eta^{[2]}_{i, j, r, s} H^{[2]}_{p, q, i, j}
-      + \frac{1}{2} \sum_{a, b} \eta^{[2]}_{p, q, a, b} H^{[2]}_{a, b, r, s}
-      \notag \\ &\hphantom{{}=\tilde{\mathcal{A}}_{\eta, H} \Biggl(}
-      + \sum_{t} \bigl(
-        \tilde{\mathcal{A}}_{p, q} \eta^{[1]}_{q, t} H^{[2]}_{p, t, r, s}
-        + \tilde{\mathcal{A}}_{r, s} \eta^{[2]}_{p, q, r, t} H^{[1]}_{t, s}
-      \bigr)
-    \Biggr) \label{eq:flow1}
+        \sum_{i, a} n_i \bar{n}_a A^{[2]}_{i, p, a, r} B^{[2]}_{a, q, i, s}
+      + \frac{1}{2} \sum_{i, j} n_i n_j A^{[2]}_{i, j, r, s} B^{[2]}_{p, q, i, j}
+      + \frac{1}{2} \sum_{a, b} \bar{n}_a \bar{n}_b A^{[2]}_{p, q, a, b} B^{[2]}_{a, b, r, s}
+      \notag \\
+    &\hphantom{=}
+      + \sum_{t} \left(
+        \tilde{\mathcal{A}}_{p, q} A^{[1]}_{q, t} B^{[2]}_{p, t, r, s}
+        + \tilde{\mathcal{A}}_{r, s} A^{[2]}_{p, q, r, t} B^{[1]}_{t, s}
+      \right)
+      \label{eq:flow2}
 \end{align}
 \end{widetext}
-Note that for brevity, we skip all the $s$ parameter in the equations and make use of the unnormalized antisymmetrizer $\tilde{\mathcal{A}}_{x, y} f(x, y) \equiv f(x, y) - f(y, x)$.
-We also use the convention that $i, j$ denote indices of occupied states, $a, b$ denote indices of unoccupied states, and $p, q, r, s, t$ denote indices of any state.
-
-\subsubsection*{Choice of generator}
-To determine the specific unitary transformation, one needs to specify
-the generator~$\hat{\eta}$. Through different choices, the SRG flow
-can be adapted to the features of a particular problem.
-
-\subsubsection*{Wegner's canonical generator}
-
-The original choice, suggested by Wegner \cite{PhysRepWegner0}, reads
+\begin{figure}
+\includegraphics[width=.48\textwidth]{fig-diagrams-imsrg}
+\caption{Diagrammatic representation of $C^{[r]}(\circ, \bullet)$ in \eqref{eq:commutmxe} that forms part of the IM-SRG flow equation \eqref{eq:flowmxe}.
+The diagrams are implicitly antisymmetrized (Hugenholtz diagrams \cite{HUGENHOLTZ1957481} as described in \cite{shavitt2009many} \S 4.4.3).}
+\label{fig:diagrams-imsrg}
+\end{figure}
+The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem [[ref]] or, even more efficiently, diagrammatic techniques [[ref]] to arrive at the results.
+In particular, the diagrammatic representation of antisymmetrized matrix elements are shown in Figure \ref{fig:diagrams-imsrg}.
+
+The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the IM-SRG state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which demonstrates that IM-SRG is size-extensive.
+Regarding the quality of the SRG results, it means that the error introduced by truncating the many-body expansions scales linearly with the number of particles $N$.
+
+\subsubsection{Wegner's canonical generator}
+
+To determine the specific unitary transformation, one needs to specify the generator $\hat{\eta}$.  Through different choices, the SRG flow can be adapted to the features of a particular problem.
+
+The original choice suggested by Wegner \cite{PhysRepWegner0} reads
 \begin{equation}
   \hat{\eta}_{\text{Wegner}}
-  = \left[ \hat{H}_{\text{diagonal}}, \hat{H}_{\text{off-diagonal}} \right]
-  = \left[ \hat{H}_{\text{diagonal}}, \hat{H} \right].
+  = [\hat{H}^{\text{d}}, \hat{H} - \hat{H}^{\text{d}}]
+  = [\hat{H}^{\text{d}}, \hat{H}]
   \label{eq:etaWegner}
 \end{equation}
-The commutator between two Hermitian operators, $\hat{\eta}$ is always
-antihermitian, as required for a generator.  Additionally, it can be shown that the commutator to suppress the off-diagonal matrix elements
-\cite{kehrein2006flow}. In general, matrix elements far off the diagonal,
-where the Hamiltonian connects states with large energy differences, are
-suppressed much faster than elements closer to the diagonal. \\ Evaluating the
-commutator, we get for the one- and two-body elements
-\begin{align*}
-\eta_{pq}^{(1)} = & \sum_{r}\left( f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \right)
-+ f_{pq} v_{qppq}^d \left( n_q - n_p \right) \\ \eta_{pqrs}^{(2)} = & -
-\sum_t \left\lbrace \left( 1-\hat{P}_{pq} \right) f_{pt} v_{tqrs}^d - \left( 1 -
-\hat{P}_{rs} \right) f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t
-\left\lbrace \left( 1 - \hat{P}_{pq} \right) f_{pt}^d v_{tqrs} - \left( 1 -
-\hat{P}_{rs} \right) f_{tr}^d v_{pqts} \right\rbrace \notag \\ & +
-\frac{1}{2} \sum_{tu} (1 - n_t - n_u) \left( v_{pqtu}^d v_{turs} -
-v_{pqtu} v_{turs}^d \right) \notag \\ & + \sum_{tu} \left( n_t - n_u \right) \left(
-1 - \hat{P}_{pq} \right) \left( 1 - \hat{P}_{rs} \right) v_{tpur}^d v_{uqts},
-\end{align*}
-where we use the standard notation
-\[
-n_p = \begin{cases} 1, & \mbox{if } p< \epsilon_F \quad(p\;\mbox{is
-    hole state})\\ 0, &\mbox{if } p> \epsilon_F \quad(p\;\mbox{is
-    particle state})\\
-\end{cases}.
-\]
-
-\subsubsection*{White's generator}
-Apart from this canonical generator, there exist several other ones in
-literature. One choice, proposed by White
-\cite{White:cond-mat0201346}, makes numerical approaches much
-more efficient.  The problem with Wegner's generator is the widely
-varying decaying speeds of the elements, removing first terms with
-large energy differences and then subsequently those ones with smaller
-energy separations.  That way the flow equations become a stiff set of
-coupled differential equations, which often gets numerically
-unstable.
-
-White takes an alternative approach, which is especially
-suited for problems where one is interested in the ground state of a
-system. Instead of driving all off-diagonal elements of the
-Hamiltonian to zero, he focuses solely on those ones that are
-connected to the reference state $|\Phi_0\rangle$, aiming to decouple
-the reference state from the remaining Hamiltonian. With a suitable
-transformation, the elements would decay near the same rate, solving
-the stiffness problem in the flow equations.  The generator is
-explicitly constructed the following way
-\cite{PhysRevLett.106.222502,White:cond-mat0201346}
+where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the Hamiltonian (and $\hat{H} - \hat{H}^{\text{d}}$ denotes the ``off-diagonal'' part) in the abstract sense described at the end of section \ref{subsubsec:srgmethods}.
+
+The commutator between two Hermitian operators, $\hat{\eta}$ is always antihermitian, as required for a generator.
+Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
+In particular, matrix elements far off the diagonal, where the Hamiltonian couples states with large energy differences, are suppressed much faster than elements closer to the diagonal.
+
+The matrix elements of the generator can be evaluated using \eqref{eq:commutmxe} to \eqref{eq:flow2}.
+If assume that $\hat{H}^{\text{d}}$ does not couple the ground state to the excited states, the equations can be simplified considerably: [[clean up this equation]]
+\begin{align*}
+\eta_{pq}^{(1)} = & \sum_{r} \left(f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \right) + f_{pq} v_{qppq}^d \left( n_q - n_p \right) \\ \eta_{pqrs}^{(2)} = & - \sum_t \left\lbrace \tilde{\mathcal{A}}_{p, q} f_{pt} v_{tqrs}^d - \tilde{\mathcal{A}}_{r, s} f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t \left\lbrace \tilde{\mathcal{A}}_{p, q} f_{pt}^d v_{tqrs} - \tilde{\mathcal{A}}_{r, s} f_{tr}^d v_{pqts} \right\rbrace \notag \\ & + \frac{1}{2} \sum_{tu} (1 - n_t - n_u) \left( v_{pqtu}^d v_{turs} - v_{pqtu} v_{turs}^d \right) \notag \\ & + \sum_{tu} \left( n_t - n_u \right) \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s} v_{tpur}^d v_{uqts},
+\end{align*}
+
+\subsubsection{White's generator}
+
+Apart from Wegner's choice of the generator, there exist several other ones in literature.
+One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
+The problem with Wegner's generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
+Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
+This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
+
+White takes an alternative approach, which is especially suited for problems where one is interested in the ground state of a system.
+Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, he focuses solely on those ones that are connected to the reference state $\Phi$, aiming to decouple the reference state from the remaining Hamiltonian.
+This reduces the amount of change performed on the Hamiltonian, which can reduce the accuracy loss resulting from the truncated higher-body terms.
+Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
+This reduces the stiffness of the flow equations.
+
+The generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}
 \begin{align}
-\hat{\eta}_{\text{White}} &\equiv \hat{\eta}'_{\text{White}} - \hat{\eta}'{}^\dagger_{\text{White}} \text{ where} \notag \\
-\hat{\eta}'_{\text{White}} &\equiv \sum_{ai} \frac{f_{ai}}{f_a-f_i-v_{aiai}}\lbrace a_a^\dagger a_i\rbrace \notag \\ & + \sum_{abij}
-\frac{v_{abij}}{f_a+f_b-f_i-f_j+A_{abij}}\lbrace a_a^\dagger a_b^\dagger a_j
-a_i\rbrace,
-\label{eq:WhiteFull}
-\end{align}
-with $f_p \equiv f_{pp}$ and
-\[
-A_{abij} = v_{abab} + v_{ijij} - v_{aiai} - v_{ajaj} - v_{bibi} -
-v_{bjbj}.
+\hat{\eta}_{\text{White}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
+\end{align}
+where
+\begin{align}
+\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i}}
+\label{eq:WhiteFull1} \\
+\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{4 \bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j}}
+\label{eq:WhiteFull2} \\
+X_{a, b, i, j}
+  &\equiv v_{a, b, a, b} + v_{i, j, i, j} \notag \\
+  &\hphantom{\equiv} - v_{a, i, a, i} - v_{a, j, a, j} \notag \\
+  &\hphantom{\equiv} - v_{b, i, b, i} - v_{b, j, b, j}
 \label{eq:White7}
-\]
-Compared to Wegner's canonical generator, where the final flow
-equations involve third order powers of the $f$- and $v$-elements,
-these elements contribute only linearly with White's generator, which
-results in much better numerical properties.
-
-We may attempt follow the same technique as for Hartree-Fock and reduce the
-operator problem into a linear algebra problem by evaluating the operator
-using a single-particle basis.  However, since a commutator between two-body
-operators can result in a three-body operator, it follows that as $s$
-increases, the evolved Hamiltonian $\tilde H(s)$ can gain terms that couple
-more and more particles.  It is not practical to keep all such terms,
-especially since higher-body operators are much more computationally
-expensive.
-
-In-medium SRG follows the same procedure as with ordinary SRG, but the
-calculations are performed relative to some reference state rather than the
-vacuum state.  This is advantageous for systems with many-particles as the
-effect of truncation is not quite as drastic as it would be in SRG
-[[true/false?]].
-
-[[need some more content before diving straight into the algebra]]
-
-Normal-ordering is a syntactic operation that reorders a product of operators
-so as to eliminate all but the highest-body interaction.  The operation is
-must be defined against a fixed many-body state, such as the vacuum state.  We
-denote normal ordering using $\mathopen: \ldots \mathclose:$, with with the
-state given by context.
-
-\textit{Normal-ordering with respect to the vacuum state} is performed by
-rearranging the operator product such that every $\hat a^\dagger$ appear
-before $\hat a$, with the caveat that the parity of the permutation must also
-be applied to the sign of the result.
-
-For many-body problems involving large number of particles, the vacuum state
-is not very convenient as it requires the application of many creation
-operators to reach the states of interest.  Therefore, it is preferable to
-utilize some reference state $\Phi$ (a Slater determinant) so that any other
-state can be readily expressed as some excitation from this state.
-
-Given a reference state $\Phi$, we may define a set of \textit{quasiparticle
-  creation and annihilation operators} $\hat b^\dagger$ and $\hat b$ that obey
-the same commutation relations as the $\hat a$ operators.  The two sets of
-operators are related by:
-\begin{align*}
-  \hat b_p^\dagger \equiv \begin{cases}
-    \hat a_p^\dagger & \text{if $p$ is unoccupied in $\Phi$} \\
-    \hat a_p^{} & \text{if $p$ is occupied in $\Phi$}
-  \end{cases}
-\end{align*}
-Analogously, there is a similar notion of normal-ordering with respect to the
-reference state: namely, the rearrangement operators such that every
-$\hat b^\dagger$ appears before $\hat b$.
-
-The relationship between the $\hat b$ operators and $\Phi$ is completely
-analogous to the relationship between the $\hat a$ operators and $0$.  As a
-result, theorems governing these operators can be applied to both.  In
-particular, \textit{Wick's theorem} -- an algebraic theorem that allows
-complicated strings of creation and annihilation operators to be simplified
-algorithmically -- plays an important role in simplifying the equations of
-IM-SRG.
-
-For conciseness, we introduce the notation $\hat A_{q_1,\dots,q_k}^\dagger$ to
-denote the normal-ordered string of creation operators
-$\hat a_{p_1}^\dagger \dots \hat a_{p_k}^\dagger$, and similarly for
-$\hat B^\dagger$ as well as their annihilation counterparts.  Note that this
-implies that the ordering is reversed in the annihilation version of this
-notation.
-
-[[...]]
+\end{align}
+
+Compared to Wegner's canonical generator, where the final flow equations involve cubes of the one-body and two-body Hamiltonian matrix elements, these elements contribute only linearly with White's generator, which results in much better numerical properties.
+[[It is not explained at all what ``final flow equations'' means]]
+
+% [[---]]
 
@@
 
-\begin{figure}
-\includegraphics[width=.48\textwidth]{fig-diagrams-imsrg}
-\caption{Diagrammatic form of $\hat C(\circ, \bullet)$.}
-\label{fig:diagrams-imsrg}
-\end{figure}
 Expanding the commutator leads to the expression
@@
  &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
- &= \int \mathrm{d}\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
- &\equiv \int \mathrm{d}\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
+ &= \int \D\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
+ &\equiv \int \D\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
 \end{align}

### 2016-10-06 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 
-The SRG flow equation \eqref{eq:imsrgode} can be solved in the second
-quantization formalism described in Section \ref{subsec:modelHamiltonian},
-where field operators are defined with respect to the physical vacuum state.
-However, since the size of the problem grows enormously with the number of
-particles and the size of the model space, the applicability of this
-free-space SRG method is restricted to comparatively small systems.
-Alternatively, the evolution can be done at finite density, i.e.\ directly in
-an $N$-particle system defined by a reference state \cite{kehrein2006flow}.
+The SRG flow equation \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
+However, since the size of the problem grows enormously with the number of particles and the size of the model space, the applicability of this free-space SRG method is restricted to comparatively small systems.
+Alternatively, the evolution can be done at finite density, i.e.\ directly in an $N$-particle system defined by a reference state \cite{kehrein2006flow}.
 This gives rise to the IM-SRG method.
 
-The second-quantized operators in
-\eqref{eq:second_quantized_one_body_hamiltonian} and
-\eqref{eq:second_quantized_two_body_hamiltonian} are constructed with respect
-to the vacuum state.  That is, the operator strings
-$\hat{a}_p^\dagger \hat{a}_q$ and
-$\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum
-expectation value of zero:
+The second-quantized operators in \eqref{eq:second_quantized_one_body_hamiltonian} and \eqref{eq:second_quantized_two_body_hamiltonian} are constructed with respect to the vacuum state.
+That is, the operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum expectation value of zero:
 \begin{align*}
@@
 \end{align*}
-They are said to be \emph{normal-ordered} with respect to the vacuum state
-$\varnothing$.  It is possible to be normal-ordered with respect to a
-non-vacuum state, however.  Consider a Slater determinant $\Phi$ with
-$N_{\text F}$ occupied states:
+They are said to be \emph{normal-ordered} with respect to the vacuum state $\varnothing$.
+It is possible to be normal-ordered with respect to a non-vacuum state, however.
+Consider a Slater determinant $\Phi$ with $N_{\text F}$ occupied states:
 \begin{align*}
@@
 As before, it is possible to construct arbitrary Slater determinants by applying quasiparticle operators to the reference state:
-\begin{align*}
+\begin{align}
   \ket{\Phi_{p_1, \ldots, p_k}} \equiv \hat{b}^\dagger_{p_1} \cdots \hat{b}^\dagger_{p_k} \ket{\Phi}
-\end{align*}
+  \label{eq:quasisd}
+\end{align}
 In nonrelativistic many-body theory, it is expected that $\{p_1, \ldots, p_k\}$ contain a balanced number of occupied and unoccupied states to conserve the total number of particles; otherwise, the Slater determinant would represent a different system.
@@
 Thus, to make the method tractable, we must close the IM-SRG flow equations, truncating the equations to a finite order.
+
 In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, an approach known as IM-SRG(2).
@@
 
-With the truncation, the generator $\hat{\eta}$ can be written as a generic antihermitian 2-body operator:
+Note that the loss of three-body and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
+The other source of error is due to the \textit{basis truncation}, as with any method that relies on a finite single-particle basis.
+The latter can be reduced by increasing the size of the basis at the expense of greater computational effort.
+
+With the operator truncation, the generator $\hat{\eta}$ can be written as a generic antihermitian 2-body operator:
 \begin{align*}
@@
 
-The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the IM-SRG state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which demonstrates that IM-SRG is size-extensive.
+An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
+In particular, the solver must be able to handle the stiffness that can often arise (even in the case of White generator).
+For this, we use an accurate, high-order ODE solver implementation by Shampine and Gordon that uses the Adams predictor-corrector formulas [[Ref: Shampine and Gordon book]].
+
+Through the flow equation and with an appropriate choice of the generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will gradually approach a more ``diagonal'' form.
+If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
+In particular, $H^{[0]}$ would approach the true ground state energy.
+
+The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the evolved state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which demonstrates that IM-SRG is size-extensive.
 Regarding the quality of the SRG results, it means that the error introduced by truncating the many-body expansions scales linearly with the number of particles $N$.
@@
 
-% [[---]]
-
-For our purposes, we restrict ourselves to at most two-body operators, and
-thus any higher-body operators that emerge from the commutator are neglected.
-In this approximation, the method is known as ``IMSRG (2)''.  The loss of
-three-body and higher terms one of the two sources of error in this method,
-the other being the basis truncation.
-
-The heart of the method lies in the choice of the generator $\eta(s)$.  We
-would like to choose the generator such that as $s \to \infty$ the transformed
-Hamiltonian $\tilde H(s)$ approaches either a diagonal, block-diagonal, or
-band-diagonal form, all of which reduce the amount of effort needed to solve
-the problem.  For our problem, we choose to decouple the ground state from all
-the excited states in the Hamiltonian matrix using a carefully chosen
-generator.  Doing so allows us to readily recover the ground state energy.
-
-There are two commonly used generators: the Wegner generator and the White
-generator.  The Wegner generator has been known since the introduction of the
-SRG method by Wegner\cite{PhysRepWegner0} and has a particularly simple form:
-\begin{align*}
-  \hat \eta^{\text{g}}(s) \equiv [\hat H^{\text d}(s), \hat H(s)]
-\end{align*}
-where $\hat H^{\text d}$ denotes the diagonal component of $\hat H$.  Despite
-its apparently simplicity, it does not work particularly well in practice as
-the off-diagonal elements vanish at vastly different rates, leading to
-differential equations that are typically stiff.
-
-The White generator remedies this problem by introducing denominators for each
-term to control and normalize the rate at which off-diagonal elements vanish:
-\begin{align*}
-  \hat \eta^{\text{h}}(s) \equiv
-  \sum_{\substack{a \\ p_1, \ldots, p_a \\ q_1, \ldots, q_a}}
-  \frac{
-  \langle \Phi_{p_1, \ldots, p_a} | \hat H^{[a]} | \Phi_{q_1, \ldots, q_a} \rangle
-  \hat B_{p_1, \ldots, p_a}^\dagger \hat B_{q_1, \ldots, q_a}^{}
-  }{E_{p_1, \ldots, p_a} - E_{q_1, \ldots, q_a}}
-\end{align*}
-where [[note: haven't explained what $\hat b$ means]]
-\begin{align*}
-  E_{p_1, \ldots, p_a} &\equiv
-  \langle \Phi_{p_1, \ldots, p_a} | \hat H | \Phi_{p_1, \ldots, p_a} \rangle \\
-  \hat B_{p_1, \ldots, p_a}^\dagger &\equiv
-  \hat b_{p_1}^\dagger \cdots \hat b_{p_a}^\dagger
-\end{align*}
-and $\hat H^{[a]}$ denotes the $a$-body term of the Hamiltonian.  As a result
-of this modification, the White generator exhibits better numerical stability
-and is computationally less expensive than the Wegner generator.
-
-An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
-In particular, the solver must be able to handle the stiffness that can often
-arise (even in the case of White generator).  For this, we use an accurate,
-high-order ODE solver implementation by Shampine and Gordon that uses the
-Adams predictor-corrector formulas [[Ref: Shampine and Gordon book]].
-
-[[...]]
-
-Expanding the commutator leads to the expression
-\begin{align*}
-  [\hat \eta, \hat H] = \hat C(\hat \eta, \hat H) - \hat C(\hat H, \hat \eta)
-\end{align*}
-where $\hat C$ is defined diagrammatically in Figure \ref{fig:diagrams-imsrg}.
-For IM-SRG(2), we truncate the commutator to a two-body operator, neglecting
-the three-body term.
-
-\subsection{The self-energy correction}
+\subsection{Quasigenerate perturbation theory}
 \label{subsec:selfenergy}
 
-IM-SRG, in the form described, does not provide a means to obtain ground state
-energies of open-shell systems.  While there exists a multi-reference IM-SRG
-that can handle the general problem ([[cite Heiko?]]), we opted to use a much
-simpler approach to obtain the addition and removal energies: quasidegenerate
-perturbation theory (QDPT).  In QDPT, the solutions of the approximate
-Hamiltonian $\hat H^{\text o}$ are used as the basis of the model space.  One
-then assumes the existence of an operator $\hat \Omega$, known as the
-\textit{wave operator}, that maps some set of states $\tilde \Phi_u$ within
-the model space to the exact ground state $\Psi_u$:
+IM-SRG, in the approach described, provides a means to calculate the ground state energy of any system that is reasonably approximated by a single Slater determinant.
+This works well for closed-shell systems, but it does not provide a direct means to obtain the ground state energy of open-shell systems.
+While there exists more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use the simpler quasidegenerate perturbation theory (QDPT), which provides us with a simple approach to extract ground state energies of open-shell systems that are only a few particles removed from a closed-shell system.
+In particular, it allows us to calculate \textit{addition energies} $\epsilon_a$ and \textit{removal energies} $\epsilon_i$ of such systems, which we define as:
+\begin{align}
+  \epsilon_a &\equiv E_{\Phi_a} - E_{\Phi} \\
+  \epsilon_i &\equiv E_{\Phi} - E_{\Phi_i}
+\end{align}
+where the meaning of $\Phi_p$ is defined in \eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
+
+In QDPT, the solutions of the approximate Hamiltonian $\hat H^{\text o}$ are used as the basis of the model space.
+One then assumes the existence of an operator $\hat \Omega$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\text o}_u$ within the model space to the exact ground state $\Psi_u$:
 \begin{align} \label{eq:omega-condition1}
-  \Psi_u = \hat \Omega \tilde \Phi_u
-\end{align}
-The states $\tilde \Phi_u$ consist of some mixture of the eigenstates
-$\Phi_{u'}$ of the approximate Hamiltonian $\hat H^{\text o}$.
+  \Psi_u = \hat \Omega \tilde \Psi^{\text o}_u
+\end{align}
+The states $\tilde \Psi^{\text o}_u$ consist of some mixture of the eigenstates
+$\Psi^{\text o}_{u'}$ of the approximate Hamiltonian $\hat H^{\text o}$.
 
@@
 longer normalized but instead satisfies the typical intermediate
-normalization: $\langle \Psi_u | \tilde \Phi_u \rangle = 1$.
-
-Making use of the assumptions in Eq.\ \eqref{eq:omega-condition1} and
-\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation
-the generalized Bloch equation, the main equation of QDPT:
+normalization: $\langle \Psi_u | \tilde \Psi^{\text o}_u \rangle = 1$.
+
+Making use of the assumptions in Eq.\ \eqref{eq:omega-condition1} and \eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
 \begin{gather*}
@@
 commutator on the left may be ``inverted'' using the resolvent approach
-[[ShavittBartlett,p.50]], resulting in:
+(\cite{shavitt2009many}, p.\ 50), resulting in:
 \begin{align*}
@@
 \end{align*}
-where
-$\hat R_u \equiv \hat Q (E_u - \hat Q \hat H^{\text o} \hat Q)^{-1} \hat Q$ is
-the resolvent and $\hat P_u$ projects any state onto $\Phi_u$.  As is typical
-in perturbation theory, we assume $\hat \Omega$ can be expanded as a series of
-the increasing order as measured by the ``power'' of the perturbation
-$\hat V$:
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat H^{\text o} \hat Q)^{-1} \hat Q$ is the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\text o}_u$.
+As is typical in perturbation theory, we assume $\hat \Omega$ can be expanded as a series of the increasing order as measured by the ``power'' of the perturbation $\hat V$:
 \begin{align*}
@@
 \end{align*}
-This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$
-to be calculated up to any order, as least in theory.  Here, we show
-$\hat \Omega$ up to third order: [[double-check]]
+This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$ to be calculated up to any order, as least in principle.  Up to third order, we have: [[double-check]]
 \begin{align*}
@@
 \end{align*}
-
-[[Since the systems are all closed-shell, the
-diagonal approximation can be used here to simplify the calculations.]]
+Until now, the solution is described purely in terms of abstract operators in Hilbert space.
+To make this concrete and relevant for many-body physics, we must make some additional assumptions.
+First, we make use of the single-particle basis as we have for HF and IM-SRG.
+Secondly, we assume the set of reference states $\Psi^{\text o}_u$ are Slater determinants of the single-particle states.
 
@@
 \includegraphics[width=.48\textwidth]{fig-diagrams-sfe}
-\caption{Diagrammatic form of the second- and third-order self-energy
-  corrections.}
+\caption{Diagrammatic form of the second- and third-order QDPT corrections.
+The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.}
 \label{fig:diagrams-sfe}
 \end{figure}
-[[Discuss how]]
-The diagrams for each order of correction can be evaluated using algebraic or
-diagrammatic techniques.  The second-order correction is given by
+
+Since for this paper we are interested in the addition and removal energies, which involve one particle more or one particle less than a closed-shell state, we can take the label $u$ to be simply the label of the state that is added or removed from the closed-shell state $\Phi$.
+With this realization, we can then express the perturbation expansion in terms of summations over matrix elements as we had done before for the IM-SRG flow equation, perhaps with the aid of Wick's theorem or diagrammatic techniques.
+This leads to the following expression for the second-order correction:
 \begin{gather*}
-  \epsilon_p = \frac{1}{2} \biggl(
-      \sum_{i a b} \frac{|V_{p i a b}|^2}{f_p + f_i - f_a - f_b}
-    - \sum_{i j a} \frac{|V_{i j p a}|^2}{f_i + f_j - f_p - f_a}
-  \biggr)
+  \epsilon_p^{(2)} =
+      \frac{1}{2} \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |V_{p i a b}|^2}{H^{[1]}_p + H^{[1]}_i - H^{[1]}_a - H^{[1]}_b}
+    - \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |V_{i j p a}|^2}{H^{[1]}_i + H^{[1]}_j - H^{[1]}_p - H^{[1]}_a}
 \end{gather*}
-and depicted in Figure \ref{fig:diagrams-sfe}.  Since there are numerous terms in
-the third-order correction, they are simply listed in a diagrammatic form in
-Figure \ref{fig:diagrams-sfe}.
-
-[[...]]
+[[write out the full thing using $H^1_{p,p}$]]
+The expression is depicted in Figure \ref{fig:diagrams-sfe}.
+Since there are numerous terms in the third-order correction $\epsilon_p^{(3)}$, they are listed exclusively in a diagrammatic form in Figure \ref{fig:diagrams-sfe}.
+
+Taking into account the perturbation corrections, one can obtain reasonably accurate addition and removal energies for single-particle states near the Fermi level via:
+\begin{align*}
+  \epsilon_p = H^{[1]}_{p, p} + \epsilon_p^{(2)} + \epsilon_p^{(3)}
+\end{align*}
 
@@
 function using what can be formally be thought of as the time-dependent
-Schr\"odinger equation along imaginary time $t = \mathrm i \tau$:
+Schr\"odinger equation along imaginary time $\tau \equiv t / \mathrm{i}$:
 \begin{align} \label{eq:itse}

### 2016-10-17 Manuscript/paper.tex
added EOM section

@@
-\documentclass[amsmath, amssymb, aps, floatfix, nofootinbib, preprintnumbers,showpacs, superscriptaddress, twocolumn]{revtex4-1}
+e\documentclass[amsmath, amssymb, aps, floatfix, nofootinbib, preprintnumbers,showpacs, superscriptaddress, twocolumn]{revtex4-1}
 \usepackage{bm}
@@
 \end{align*}
+
+\subsection{Equations of Motion Methods}
+Particle attached and particle removed equations of motion (EOM) methods can be coupled with either IM-SRG
+or coupled cluster calculations. The principle idea is that one may construct a ladder operator $X$, 
+which promotes the $A$-body ground state to any state in the $A$+$1$ or $A$-$1$ spectrum,
+\begin{equation}\label{eq:ladder_def} 
+  | \Psi^{(A \pm 1)}_\nu \rangle  = X^{(A \pm 1)}_\nu | \Psi^{(A)}_0 \rangle, 
+\end{equation} 
+where $X$ is in principle a linear combination of excitation and de-excitation operators which change particle number by one,
+\begin{align}
+  \label{eq:gen_attached}
+  X^{(A+1)}_\nu &= \sum_p \bar{n}_p x^p  a^\dagger_p + \frac{1}{2} \sum_{pqr} \bar{n}_p \bar{n}_q n_r x^{pq}_r  a^\dagger_p a^\dagger_q a_r + \cdots,  \\
+  \label{eq:gen_removed}
+  X^{(A-1)}_\nu &= \sum_p n_p x_p a_p + \frac{1}{2} \sum_{pqr} n_p n_q \bar{n}_r  x_{pq}^r  a^\dagger_r a_q a_p  + \cdots. 
+\end{align}
+Substitution of equation~\ref{eq:ladder_def} into the energy eigenvalue problem $H | \Psi_\nu^{(A \pm 1)} \rangle = E^{(A\pm1)}_\nu | \Psi_\nu^{(A \pm 1)} \rangle$ gives
+\begin{equation}\label{eq:EOM}
+  [H,X^{(A \pm 1)}_\nu] | \Psi^{(A)}_0 \rangle = \omega_\pm X^{(A \pm 1)}_\nu | \Psi^{(A)}_0 \rangle,
+\end{equation}
+which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\omega_\pm$ are the
+single particle addition and removal energies. The quality of this calculation depends on the ansatz for the $A$-body ground state, as well as the systematically
+improvable truncation on the ladder operators. In this work we include 1p and 2p1h excitations in the $A$+1 ladder operator and likewise 1h and 2h1p operators for
+the $A$-1 ladder operators.
+
+\subsubsection{IM-SRG}
+After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with
+corresponding eigenvalue $E^{(A)}_0$, which is the correlated $A$-body ground state energy. The EOM equation is therefore 
+\begin{equation}\label{eq:EOMIMSRG} 
+  [\bar{H},\bar{X}^{(A \pm 1)}_\nu] | \Phi^{(A)}_0 \rangle = \omega_\pm \bar{X}^{(A \pm 1)}_\nu | \Phi^{(A)}_0 \rangle,
+\end{equation}
+where bars denote rotated operators. Now the reference state is used in place of the bare correlated ground state. The ground state IM-SRG procedure has
+implicitly re-summed contributions from higher order excitations (3p2h, 3h2p, 4p3h,...) into the lower order amplitudes of the ladder operators (1p, 1h, 2p1h, 2h1p).
+
+Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2p1h and 2h1p operators. We expect $A$+1 ($A$-1) states
+to be described appropriately by EOM-IMSRG if their wavefunctions are dominated by 1p (1h) contributions in the rotated frame. We use partial norms of the EOM ladder operators
+to make this determination:
+\begin{align}\label{eq:partial_norms}
+  n(1p) &= \sqrt{ \sum_p \bar{n}_p | \bar{x}^p |^2 },\\
+  n(1h) &= \sqrt{ \sum_p n_p | \bar{x}_p |^2 }.
+\end{align}
+Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
+States with lower single particle norms should be treated by with a higher EOM approximation, which can be accomplished directly or perturbatively.
+{\color{red} My paper talks about this a bit more, and we have some plots.
+Of course it only concerns the A-body stuff}.
 

### 2016-10-18 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

--- 2016-10-06 Manuscript/paper.tex
@@
 \end{align}
-In nonrelativistic many-body theory, it is expected that $\{p_1, \ldots, p_k\}$ contain a balanced number of occupied and unoccupied states to conserve the total number of particles; otherwise, the Slater determinant would represent a different system.
+If $p$ is an unoccupied state, then applying $\hat{b}_p^\dagger$ creates a particle exactly like $\hat{a}_p^\dagger$.
+However, if $p$ is an occupied state, then applying $\hat{b}_p^\dagger$ destroys an existing particle in $\Phi$ or, equivalently, creates a \textit{hole} state.
+The set of labels $\{p_1, \ldots, p_k\}$ may contain up to $N$ hole states and a potentially infinite number of particle states.
+It is typical to classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
+If $N_{\text{p}} = N_{\text{h}}$, the Slater determinant represents a system containing the same number of physical particles.
 
@@
 This leads to the following expression for the second-order correction:
-\begin{gather*}
-  \epsilon_p^{(2)} =
-      \frac{1}{2} \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |V_{p i a b}|^2}{H^{[1]}_p + H^{[1]}_i - H^{[1]}_a - H^{[1]}_b}
-    - \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |V_{i j p a}|^2}{H^{[1]}_i + H^{[1]}_j - H^{[1]}_p - H^{[1]}_a}
-\end{gather*}
+\begin{align*}
+  \epsilon_p^{(2)}
+  &=
+  \frac{1}{2} \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{H^{[1]}_p + H^{[1]}_i - H^{[1]}_a - H^{[1]}_b} \\
+  &{}-
+  \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{H^{[1]}_i + H^{[1]}_j - H^{[1]}_p - H^{[1]}_a}
+\end{align*}
 [[write out the full thing using $H^1_{p,p}$]]
@@
 \end{align*}
+
+\subsection{Equations of Motion Methods}
+
+Particle attached and particle removed equations of motion (EOM) methods can be coupled with either IM-SRG or coupled cluster calculations.
+The principal idea is that one may construct a ladder operator $\hat{X}$ that promotes the $N$-particle ground state to any state in the $N + 1$ or $N - 1$ spectrum,
+\begin{equation}\label{eq:ladder_def}
+  \ket{\Psi^{(N \pm 1)}_u}  = \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
+\end{equation}
+where $\hat{X}$ is in principle a linear combination of excitation and de-excitation operators that change particle number by one,
+\begin{align}
+  \label{eq:gen_attached}
+  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r x_{p, q; r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
+  \label{eq:gen_removed}
+  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  x_{p, q}{}^r \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
+\end{align}
+Substitution of \eqref{eq:ladder_def} into the energy eigenvalue problem $\hat H \ket{\Psi_u^{(N \pm 1)}} = E^{(N\pm1)}_u \ket{\Psi_u^{(N \pm 1)}}$ gives
+\begin{equation}\label{eq:EOM}
+  [\hat{H}, \hat{X}^{(N \pm 1)}_u] \ket{\Psi^{(N)}_0} = \epsilon_\pm \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
+\end{equation}
+which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\epsilon_\pm$ are the single-particle addition ($+$) and removal ($-$) energies.
+The quality of this calculation depends on the ansatz for the $N$-particle ground state, as well as the systematically improvable truncation on the ladder operators.
+In this work we include 1p and 2p1h excitations in the $N + 1$ ladder operator and likewise 1h and 2h1p operators for the $N - 1$ ladder operators.
+
+\subsubsection*{EOM-IM-SRG}
+After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(A)}_0$, which is the correlated $A$-particle ground state energy.
+The EOM equation is therefore
+\begin{equation}\label{eq:EOMIMSRG}
+  [\bar{H},\bar{X}^{(A \pm 1)}_u] \ket{\Phi^{(A)}_0} = \omega_\pm \bar{X}^{(A \pm 1)}_u \ket{\Phi^{(A)}_0},
+\end{equation}
+where bars denote rotated operators. Now the reference state is used in place of the bare correlated ground state. The ground state IM-SRG procedure has
+implicitly re-summed contributions from higher order excitations (3p2h, 3h2p, 4p3h,...) into the lower order amplitudes of the ladder operators (1p, 1h, 2p1h, 2h1p).
+
+Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2p1h and 2h1p operators. We expect $A$+1 ($A$-1) states
+to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1p (1h) contributions in the rotated frame. We use partial norms of the EOM ladder operators
+to make this determination:
+\begin{align}\label{eq:partial_norms}
+  n(1p) &= \sqrt{\sum_p \bar{n}_p | \bar{x}^p |^2},\\
+  n(1h) &= \sqrt{\sum_p n_p | \bar{x}_p |^2}.
+\end{align}
+Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
+States with lower single particle norms should be treated by with a higher EOM approximation, which can be accomplished directly or perturbatively.
+{\color{red} My paper talks about this a bit more, and we have some plots.
+Of course it only concerns the A-body stuff}.
 
@@
 \noindent
-where $\xi$ is a uniform distributed random number with variance $\mathrm{Var}(\xi) = 2D\delta\tau$. A typical value of $N_w$ in this work is 250 000.
+where $\xi$ is a uniform distributed random number with variance $\mathrm{Var}(\xi) = 2D\delta\tau$. A typical value of $N_w$ in this work is 250\,000.
 
@@
 Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and
-IMSRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a
+IM-SRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a
 dashed line in systems where it is known \cite{PhysRevB.84.115302}.
 
-Both perturbation theory and IMSRG add corrections in addition to the
+Both perturbation theory and IM-SRG add corrections in addition to the
 Hartree-Fock results to recover the correlation energy and they do quite well
-in recovering the correlation energy in the system.  Compared with MPPT, IMSRG
+in recovering the correlation energy in the system.  Compared with MPPT, IM-SRG
 generally converges faster, although does not always converge to the DMC
-result.  Generally speaking, IMSRG is closer to the DMC result as the number
+result.  Generally speaking, IM-SRG is closer to the DMC result as the number
 of particles increases.
 
-There are a few cases where the IMSRG over-corrects the result, leading to a
+There are a few cases where the IM-SRG over-corrects the result, leading to a
 ground state energy that is lower than the exact result.  This is not
-unexpected given that, unlike Hartree-Fock, IMSRG is non-variational.  These
+unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational.  These
 tend to occur when the number of particles is few, or the frequency is very
 low (high correlation).  However, MPPT does not do much better in the high
-frequency regimes as it often converges slower than IMSRG.
+frequency regimes as it often converges slower than IM-SRG.
 

### 2016-10-18 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
   \label{eq:gen_attached}
-  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r x_{p, q; r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
+  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum^{[2,1]}_{p, q, r} \bar{n}_p \bar{n}_q n_r x_{p, q, r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  x_{p, q}{}^r \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
+  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  x^{[1,2]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
 \end{align}
@@
 \begin{equation}\label{eq:EOM}
-  [\hat{H}, \hat{X}^{(N \pm 1)}_u] \ket{\Psi^{(N)}_0} = \epsilon_\pm \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
+  [\hat{H}, \hat{X}^{(N \pm 1)}_u] \ket{\Psi^{(N)}_0} = \pm \epsilon^{(\pm)}_u \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
 \end{equation}
-which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\epsilon_\pm$ are the single-particle addition ($+$) and removal ($-$) energies.
+which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\epsilon^{(\pm)}_u$ are the single-particle addition ($+$) and removal ($-$) energies.
 The quality of this calculation depends on the ansatz for the $N$-particle ground state, as well as the systematically improvable truncation on the ladder operators.
@@
 \subsubsection*{EOM-IM-SRG}
-After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(A)}_0$, which is the correlated $A$-particle ground state energy.
+After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the correlated $N$-particle ground state energy.
 The EOM equation is therefore
 \begin{equation}\label{eq:EOMIMSRG}
-  [\bar{H},\bar{X}^{(A \pm 1)}_u] \ket{\Phi^{(A)}_0} = \omega_\pm \bar{X}^{(A \pm 1)}_u \ket{\Phi^{(A)}_0},
+  [\bar{H},\bar{X}^{(N \pm 1)}_u] \ket{\Phi^{(N)}_0} = \pm \epsilon^{(\pm)}_u \bar{X}^{(N \pm 1)}_u \ket{\Phi^{(N)}_0},
 \end{equation}
-where bars denote rotated operators. Now the reference state is used in place of the bare correlated ground state. The ground state IM-SRG procedure has
-implicitly re-summed contributions from higher order excitations (3p2h, 3h2p, 4p3h,...) into the lower order amplitudes of the ladder operators (1p, 1h, 2p1h, 2h1p).
-
-Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2p1h and 2h1p operators. We expect $A$+1 ($A$-1) states
-to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1p (1h) contributions in the rotated frame. We use partial norms of the EOM ladder operators
-to make this determination:
+where bars denote rotated operators.
+Now the reference state is used in place of the bare correlated ground state.
+The ground state IM-SRG procedure has implicitly re-summed contributions from higher order excitations (3-particle-2-hole, 2-particle-3-hole, 2-particle-3-hole, 4-particle-3-hole, \ldots) into the lower order amplitudes of the ladder operators (1-particle-0-hole, 0-particle-1-hole, 2-particle-1-hole, 1-particle-2-hole).
+
+Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2-particle-1-hole and 1-particle-2-hole operators.
+We expect $N + 1$ (or $N - 1$) states to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in the rotated frame.
+We use partial norms of the EOM ladder operators to make this determination:
 \begin{align}\label{eq:partial_norms}
-  n(1p) &= \sqrt{\sum_p \bar{n}_p | \bar{x}^p |^2},\\
-  n(1h) &= \sqrt{\sum_p n_p | \bar{x}_p |^2}.
+  n_{\text{1-particle}} &= \sqrt{\sum_p \bar{n}_p | \bar{x}^{[1,0]}_p |^2},\\
+  n_{\text{1-hole}} &= \sqrt{\sum_p n_p | \bar{x}^{[0,1]}_p |^2}.
 \end{align}

### 2016-10-23 Manuscript/paper.tex
spEnergiesQD/Manuscript/paper.tex: re-write Wegner generator expression

@@
 \begin{align}
-  C^{[r]}(A, B) &\equiv \tilde{\mathcal{A}}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
-  \tilde{\mathcal{A}}_{x, y} f(x, y) &\equiv f(x, y) - f(y, x) \text{ for any $x$, $y$, $f$}
+  C^{[r]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
+  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$}
 \end{align}
@@
 \begin{equation}
-  \hat{\eta}_{\text{Wegner}}
+  \hat{\eta}^{\text{Wg}}
   = [\hat{H}^{\text{d}}, \hat{H} - \hat{H}^{\text{d}}]
@@
 
-The commutator between two Hermitian operators, $\hat{\eta}$ is always antihermitian, as required for a generator.
+Since $\hat{\eta}^{\text{Wg}}$ is the commutator between two Hermitian operators, it is antihermitian as required for a generator.
 Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
@@
 
-The matrix elements of the generator can be evaluated using \eqref{eq:commutmxe} to \eqref{eq:flow2}.
-If assume that $\hat{H}^{\text{d}}$ does not couple the ground state to the excited states, the equations can be simplified considerably: [[clean up this equation]]
-\begin{align*}
-\eta_{pq}^{(1)} = & \sum_{r} \left(f_{pr}^d f_{rq} - f_{pr} f_{rq}^d \right) + f_{pq} v_{qppq}^d \left( n_q - n_p \right) \\ \eta_{pqrs}^{(2)} = & - \sum_t \left\lbrace \tilde{\mathcal{A}}_{p, q} f_{pt} v_{tqrs}^d - \tilde{\mathcal{A}}_{r, s} f_{tr} v_{pqts}^d \right\rbrace \notag \\ & + \sum_t \left\lbrace \tilde{\mathcal{A}}_{p, q} f_{pt}^d v_{tqrs} - \tilde{\mathcal{A}}_{r, s} f_{tr}^d v_{pqts} \right\rbrace \notag \\ & + \frac{1}{2} \sum_{tu} (1 - n_t - n_u) \left( v_{pqtu}^d v_{turs} - v_{pqtu} v_{turs}^d \right) \notag \\ & + \sum_{tu} \left( n_t - n_u \right) \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s} v_{tpur}^d v_{uqts},
-\end{align*}
+The matrix elements of the generator can be evaluated using \eqref{eq:commutmxe} to \eqref{eq:flow2}.  If define $\hat{H}^{\text{d}}$ via
+\begin{align*}
+  H^{\text{d}, [1]}_{p, q} &\equiv \delta_{p, q} H^{[1]}_{p, p} \\
+  H^{\text{d}, [2]}_{p, q, r, s} &\equiv (\delta_{p, r} \delta_{q, s} - \delta_{p, s} \delta_{q, r}) H^{[2]}_{p, q, p, q}
+\end{align*}
+then the expressions for $\hat{\eta}^{\text{Wg}}$ can be simplified considerably:
+\begin{align*}
+  \eta^{\text{Wg},[0]} &= 0 \\
+  \eta^{\text{Wg},[1]}_{p, q} &= 2 H^{[1]}_{p, q} \mathcal{A}_{p, q} \bigl( H^{[1]}_{p, p} + n_p H^{[2]}_{p, q, p, q} \bigr) \\
+  \eta^{\text{Wg},[2]}_{p, q, r, s} &= 2 \mathcal{A}_{p, q} \mathcal{A}_{r, s} \Big( \\
+  &\qquad H^{[2]}_{p, q, r, s} \mathcal{A}_{(p, q), (r, s)} \Bigl(\\
+  &\qquad \qquad 2 H^{[1]}_{p, p} + 4 n_p H^{[2]}_{p, r, p, r} \\
+  &\qquad \qquad + (1 - 2 n_p) H^{[2]}_{p, q, p, q} \Bigr) \\
+  &\qquad + 4 \delta_{p, r} H^{[1]}_{q, s} \mathcal{A}_{(p, q), (r, s)} H^{[2]}_{p, q, p, q}
+  \Bigr)
+\end{align*}
+where for any $x$, $y$, $z$, $w$, $f$ we define the antisymmetrizer
+\begin{align*}
+  \mathcal{A}_{(x, y), (z, w)} f(x, y, z, w) &\equiv \frac{1}{2} \bigl(f(x, y, z, w) - f(z, w, x, y)\bigr)
+\end{align}
 
@@
 \begin{align}
-\hat{\eta}_{\text{White}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
+\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
 \end{align}
@@
 X_{a, b, i, j}
-  &\equiv v_{a, b, a, b} + v_{i, j, i, j} \notag \\
-  &\hphantom{\equiv} - v_{a, i, a, i} - v_{a, j, a, j} \notag \\
-  &\hphantom{\equiv} - v_{b, i, b, i} - v_{b, j, b, j}
+  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
+  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j}
 \label{eq:White7}

### 2016-10-24 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex
See also: last pargraph in §4.4 of Heiko's paper
https://arxiv.org/pdf/1512.06956v1.pdf

@@
 
-Compared to Wegner's canonical generator, where the final flow equations involve cubes of the one-body and two-body Hamiltonian matrix elements, these elements contribute only linearly with White's generator, which results in much better numerical properties.
-[[It is not explained at all what ``final flow equations'' means]]
+Compared to Wegner's canonical generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White's generator contribute only linearly with White's generator.
+This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.
 

### 2016-11-02 Manuscript/paper.tex
Remove incorrect factor of 4 in spEnergiesQD/Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 \begin{align*}
-  \hat H \equiv \hat H^{\text o} + \hat V = \sum_{p} \bigl(
-    t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
-  \bigr) + \sum_{p < q} v(\hat{\bm r}_p, \hat{\bm r}_q)
-\end{align*}
-where $\hat{\bm p}_p$ and $\hat{\bm r}_p$ respectively denote the momentum and
-position operators of a particle $p$.  The first summation is performed over
+  \hat H \equiv \hat H^{\text o} + \hat V = \sum_j \bigl(
+    t(\hat{\bm p}_j) + u(\hat{\bm r}_j)
+  \bigr) + \sum_{j_1 < j_2} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2})
+\end{align*}
+where $\hat{\bm p}_j$ and $\hat{\bm r}_j$ respectively denote the momentum and
+position operators of a particle $j$.  The first summation is performed over
 every particle, while the the second summation is performed over every
-unordered pair of distinct particles (the ordering of $p$ is arbitrary).
+unordered pair of distinct particles (the ordering of the particle labels $j$ is arbitrary).
 
@@
   \hat h^{\text o} \equiv
-  \frac{\hat{\bm p}^2 + \omega^2 \hat{\bm x}^2}{2}
+  \frac{\hat{\bm p}^2 + \omega^2 \hat{\bm r}^2}{2}
 \end{align*}
@@
 \begin{gather*}
-  \phi^{\text{FD}}_{n, m_\ell}(r, \varphi)
+  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi)
   \equiv \sqrt\omega
-  \phi^{\text{FD.R}}_{n, |m_\ell|}(\sqrt \omega r)
-  \phi^{\text{FD.A}}_{m_\ell}(\varphi)
+  \phi^{\text{FDr}}_{n, |m_\ell|}(\sqrt \omega \rho)
+  \phi^{\text{Lz}}_{m_\ell}(\varphi)
 \end{gather*}
-where
-\begin{align*}
-  \phi^{\text{FD.R}}_{n, \mu}(\rho) &\equiv
-  \sqrt{\frac{2 \cdot n!}{(n + \mu)!}}
-  {\mathrm e}^{- \rho^2 / 2} \rho^\mu L_n^{(\mu)}(\rho^2) \\
-  \phi^{\text{FD.A}}_{m_\ell}(\varphi) &\equiv
+where $\rho$ denotes the radial coordinate, $\varphi$ denotes the angular coordinate,
+\begin{align*}
+  \phi^{\text{FDr}}_{n, m}(r) &\equiv
+  \sqrt{\frac{2 \cdot n!}{(n + m)!}}
+  {\mathrm e}^{-r^2 / 2} r^m L_n^{(m)}(r^2) \\
+  \phi^{\text{Lz}}_{m_\ell}(\varphi) &\equiv
   \frac{1}{\sqrt{2 \pi}} {\mathrm e}^{i m_\ell \varphi}
@@
 \begin{align} \label{eq:singleparticlestate}
-  \phi_{n, m_\ell, m_{\text s}}(r, \varphi) \equiv
-  \phi^{\text{FD}}_{n, m_\ell}(r, \varphi) \chi_{m_{\text s}}
+  \phi_{n, m_\ell, m_{\text s}}(\rho, \varphi) \equiv
+  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi) \chi_{m_{\text s}}
 \end{align}
@@
   \mathcal{A}_{(x, y), (z, w)} f(x, y, z, w) &\equiv \frac{1}{2} \bigl(f(x, y, z, w) - f(z, w, x, y)\bigr)
-\end{align}
+\end{align*}
 
@@
 \label{eq:WhiteFull1} \\
-\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{4 \bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j}}
+\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j}}
 \label{eq:WhiteFull2} \\

### 2016-11-11 Manuscript/paper.tex
Fix some references

@@
 quantum dots, and gives afterwards an overview of the IM-SRG
-(\ref{subsec:SRG}) and DMC (\ref{subsec:DMC}) formalisms.  Our results are
+(\ref{subsec:imsrgmethod}) and DMC (\ref{subsec:DMC}) formalisms.  Our results are
 presented in Section \ref{sec:results}.  We point out the differences arising
@@
 \subsubsection{Wegner's canonical generator}
+\label{subsec:Wegner}
 
@@
 \subsubsection{White's generator}
+\label{subsec:White}
 
@@
 
-Making use of the assumptions in Eq.\ \eqref{eq:omega-condition1} and \eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
+Making use of the assumptions in  \eqref{eq:omega-condition1} and \eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
 \begin{gather*}
@@
 \subsection{Diffusion Monte Carlo}
+\label{subsec:DMC}
 
@@
 
-The Green's function introduced in Eq.~(\ref{eq:DMC_GreenFuncRevealed}) has singularities due to the the Coulomb interaction term in $\hat{H}$.
+The Green's function introduced in \eqref{eq:DMC_GreenFuncRevealed} has singularities due to the the Coulomb interaction term in $\hat{H}$.
 Due to Pauli exclusion these are not physical, nevertheless, in numerical implementations they are unpredictable and undesirable, hence we want to avoid them.
@@
 
-The Green's function from Eq.~(\ref{DMC_IS_GF_raw}) has been split into two for practical reasons; one part containing the kinetic terms, more specifically this represents a Fokker-Planck diffusion process, and a second part which is commonly referred to as a \textit{branching function}, which is an effective reweighing of a positions contribution to the overall density.
+The Green's function from \eqref{eq:DMC_IS_GF_raw} has been split into two for practical reasons; one part containing the kinetic terms, more specifically this represents a Fokker-Planck diffusion process, and a second part which is commonly referred to as a \textit{branching function}, which is an effective reweighing of a positions contribution to the overall density.
 Excluding branching we will simply sample from the density of the trial state.
@@
 A value in the range of $10^{-3}$ to $10^{-4}$ is used in this work.
-High variance in energy samples requires a smaller time step to keep the branching controlled, since the fluctuations of the two are connected by Eq.~(\ref{eq:DMC_IS_GF}).
-
-The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of Eq.~(\ref{eq:DMC_IS_GF}).
+High variance in energy samples requires a smaller time step to keep the branching controlled, since the fluctuations of the two are connected by \eqref{eq:DMC_IS_GF}.
+
+The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of \eqref{eq:DMC_IS_GF}.
 Let $G_b$ denote the value of the branching function at a given position.
@@
 This is ensured by using the Metropolis Algorithm.
-Moreover, importance sampling is ensured by sampling according to the kinetic term of  Eq.~(\ref{eq:DMC_IS_GF_raw}) \textit{cite solution langevin}
+Moreover, importance sampling is ensured by sampling according to the kinetic term of \eqref{eq:DMC_IS_GF_raw} [[cite solution langevin]]
 
@@
 
-The Slater determinant contains eigenstates $\phi_n(\mathbf{r})$ of Eq.~(\ref{eq:potential})
+The Slater determinant contains eigenstates $\phi_n(\mathbf{r})$ of the 2-dimensional harmonic oscillator
 with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$
@@
   results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained
-  using the extrapolation formula of Eq.().}
+  using the extrapolation formula of [[equation?]].}
 \label{tab:SRGDMC-R20}
@@
 
-In Figure \ref{fig:gs} we show the calculated ground state energies from
+In Figure [[fig:gs]] we show the calculated ground state energies from
 Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and
@@
 For our addition and removal energy calculations, the results are summarized
-in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.  The figures
+in Figure [[fig:add]] and Figure [[fig:rm]] respectively.  The figures
 show the the addition/removal energies for Hartree-Fock, combined with IM-SRG
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
-
-We demonstrated the use various many-body theories, Hartree-Fock method, M\o
-eller-Plesset perturbation theory, IM-SRG, as well as quasidegenerate
-perturbation theory to calculate ground state as well as addition and removal
-energies of two-dimensional quantum dots.  We showed that these methods, when
-combined, can give a good approximate description of the systems at moderate
-cost compared to near-exact but much more expensive methods such as FCI and
-DMC.
-
-For ground state energy, we showed that the convergence of IM-SRG is generally
-faster than that of MPPT, and the results are typically closer to the exact
-results.  Similarly, we found that IM-SRG improves the rate of convergence of
-the addition and removal energies, both as the order of perturbation theory
-increases and as the number of shells increases.
-
-There are several directions in which the calculations may be improved.  One
-can attempt to improve the IM-SRG approximation by incorporating some of the
-missing higher-body terms in the commutator.  This would also provide some
-insight into the rate of convergence with respect to the operator truncation.
-While some of the higher-body terms can be rather costly to compute --
-rendering a full 3-body IM-SRG quite expensive -- certain additional
-approximations may be made to alleviate this without incurring the full cost
-of evolving 3-body operators [[Ref?]].
-
-[[As noted earlier [[haven't written that yet]], the application of IM-SRG
-removes a large portion of the QDPT diagrams, which is beneficial as it
-increases the efficiency of the QDPT calculations.  However, many of these
-diagrams can also be eliminated further through an infinite resummation scheme
-[[Any good refs for this?]], which would further reduce the number of diagrams
-in QDPT, especially those of lower order, whic would likely increase the
-accuracy of the result.]]
-
-It would also be useful to investigate how the results obtained with finite
-number of shells in the basis are related to those obtained with an infinite
-number of shells in the basis.  [[Ref: paper on IR/UV extrapolation]] With a
-good theoretical foundation, a model of how the observables converge with
-respect to the size of the basis may be used to extrapolate the results to
-infinite-basis limit.  This would also enable us to perform cheaper
-calculations with fewer shells and optimistically extrapolate results for
-large systems that would be otherwise infeasible to compute.
-
-We note that this calculation was done entirely using the traditional approach
-of using a high-order ODE solver to solve the flow equation.  A new technique
-developed by T. Morris [[Ref?]] uses an alternative approach that obviates the
-need for a high-order ODE solver, leading to much more efficient computations
-and also allowing operators of other observables to be evolved with greater
-ease.  Implementing this approach would be beneficial as it would allows us to
-study the accuracy and convergence of other observables beyond energy and
-energy differences.
-
-Implementation-wise, our current code constructs the two-particle basis as
-simple Slater determinants without any angular momentum coupling.  This
-approach is often referred to as \textit{m-scheme} in nuclear physics.  This
-method is simple and works well for general systems, but it does not fully
-exploit the circular symmetry present in the quantum dot system.  A more
-efficient approach is to use angular momentum coupling to generate the
-two-particle basis, which is known as \textit{j-scheme} in nuclear physics.
-Combined with the symmetries of the Hamiltonian, this can significantly reduce
-the amount of computation required in this system, albeit at the cost of
-increasing the complexity of the implementation.
-
-A more technical issue is its lack of parallelization: currently, the code
-makes very little use of parallelism and therefore does not scale well on
-modern clusters.  As the problem is not embarrassingly parallel, implementing
-parallelism does introduce additional complications that must be considered.
-Distributing the workload across multiple nodes can significantly reduce the
-cost of the calculations, allowing larger systems to be studied.
-
-\begin{acknowledgments}
- This work was supported by the
-National Science Foundation Grant No.~PHY-1404159
-(Michigan State University) and by the Research
-Council of Norway under contract ISP-Fysikk/216699.
-\end{acknowledgments}
-
-\bibliography{paper}
-\bibliographystyle{apsrev4-1}
-\end{document}
-
-\documentclass[aps,twocolumn,showpacs,floatfix,nofootinbib,preprintnumbers,superscriptaddress,amsmath,amssymb]{revtex4-1}
-
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{bm}
-\usepackage{color}
-\usepackage{float}
-\usepackage{dcolumn}
-\usepackage{subfigure}
-\usepackage{multirow}
-
-\section{Results}
-\label{sec:results}
+[[begin unmerged]]
+
 In this section, we discuss the IM-SRG results for the ground-state
@@
 
+[[end unmerged]]
+
 \section{Conclusions}
 \label{sec:conclusions}
+
+We demonstrated the use various many-body theories, Hartree-Fock method, M\o
+eller-Plesset perturbation theory, IM-SRG, as well as quasidegenerate
+perturbation theory to calculate ground state as well as addition and removal
+energies of two-dimensional quantum dots.  We showed that these methods, when
+combined, can give a good approximate description of the systems at moderate
+cost compared to near-exact but much more expensive methods such as FCI and
+DMC.
+
+For ground state energy, we showed that the convergence of IM-SRG is generally
+faster than that of MPPT, and the results are typically closer to the exact
+results.  Similarly, we found that IM-SRG improves the rate of convergence of
+the addition and removal energies, both as the order of perturbation theory
+increases and as the number of shells increases.
+
+There are several directions in which the calculations may be improved.  One
+can attempt to improve the IM-SRG approximation by incorporating some of the
+missing higher-body terms in the commutator.  This would also provide some
+insight into the rate of convergence with respect to the operator truncation.
+While some of the higher-body terms can be rather costly to compute --
+rendering a full 3-body IM-SRG quite expensive -- certain additional
+approximations may be made to alleviate this without incurring the full cost
+of evolving 3-body operators [[Ref?]].
+
+[[As noted earlier [[haven't written that yet]], the application of IM-SRG
+removes a large portion of the QDPT diagrams, which is beneficial as it
+increases the efficiency of the QDPT calculations.  However, many of these
+diagrams can also be eliminated further through an infinite resummation scheme
+[[Any good refs for this?]], which would further reduce the number of diagrams
+in QDPT, especially those of lower order, whic would likely increase the
+accuracy of the result.]]
+
+It would also be useful to investigate how the results obtained with finite
+number of shells in the basis are related to those obtained with an infinite
+number of shells in the basis.  [[Ref: paper on IR/UV extrapolation]] With a
+good theoretical foundation, a model of how the observables converge with
+respect to the size of the basis may be used to extrapolate the results to
+infinite-basis limit.  This would also enable us to perform cheaper
+calculations with fewer shells and optimistically extrapolate results for
+large systems that would be otherwise infeasible to compute.
+
+We note that this calculation was done entirely using the traditional approach
+of using a high-order ODE solver to solve the flow equation.  A new technique
+developed by T. Morris [[Ref?]] uses an alternative approach that obviates the
+need for a high-order ODE solver, leading to much more efficient computations
+and also allowing operators of other observables to be evolved with greater
+ease.  Implementing this approach would be beneficial as it would allows us to
+study the accuracy and convergence of other observables beyond energy and
+energy differences.
+
+Implementation-wise, our current code constructs the two-particle basis as
+simple Slater determinants without any angular momentum coupling.  This
+approach is often referred to as \textit{m-scheme} in nuclear physics.  This
+method is simple and works well for general systems, but it does not fully
+exploit the circular symmetry present in the quantum dot system.  A more
+efficient approach is to use angular momentum coupling to generate the
+two-particle basis, which is known as \textit{j-scheme} in nuclear physics.
+Combined with the symmetries of the Hamiltonian, this can significantly reduce
+the amount of computation required in this system, albeit at the cost of
+increasing the complexity of the implementation.
+
+A more technical issue is its lack of parallelization: currently, the code
+makes very little use of parallelism and therefore does not scale well on
+modern clusters.  As the problem is not embarrassingly parallel, implementing
+parallelism does introduce additional complications that must be considered.
+Distributing the workload across multiple nodes can significantly reduce the
+cost of the calculations, allowing larger systems to be studied.
+
+[[begin unmerged]]
+
 We have used IM-SRG to study the ground state energy of circular,
@@
 
-%
+[[end unmerged]]
+
 \begin{acknowledgments}
+  This work was supported by the
+  National Science Foundation Grant No.~PHY-1404159
+  (Michigan State University) and by the Research
+  Council of Norway under contract ISP-Fysikk/216699.
+
+  [[begin unmerged]]
+
   We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for
@@
   computational resources of the Notur project in Norway.
+
+  [[end unmerged]]
 \end{acknowledgments}
 
-\bibliography{srg}
+\bibliography{paper}
 \bibliographystyle{apsrev4-1}
-
 \end{document}

### 2016-11-12 Manuscript/paper.tex
Fix references

@@
 diagonalization/full configuration interaction (FCI)
-\cite{JJAP.36.3924,PhysRevB.56.6428,Kvaalcode,rontani:124102} and coupled
+\cite{JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} and coupled
 cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,%
@@
 The harmonic oscillator (HO) is a ubiquitous system in quantum physics.
-It is the basis for an extremely diverse set of many-body calculations -- in nuclear physics \cite{HJORTHJENSEN1995125}, quantum chemistry \cite{Helgaker2002} [[missing ref for Helgaker 2002]], and quantum dot calculations of solid state physics \cite{reimann2002}.
+It is the basis for an extremely diverse set of many-body calculations -- in nuclear physics \cite{HJORTHJENSEN1995125}, quantum chemistry \cite{helgaker2000molecular}, and quantum dot calculations of solid state physics \cite{reimann2002}.
 In these calculations, one typically seeks a few of the lowest eigenvalues $E_k$ and eigenvectors of a many-body Hamiltonian $\hat{H}$ that describes the full system by solving the Schr\"odinger equation,
@@
 Since HO eigenfunctions are defined on the \emph{entire} space in which particles live, a truncation of the spatial domain is unnecessary.
-This avoids one of the main problems with approaches such as finite difference or finite element methods.\cite{RamMohan2002} [[Unknown citation]]
+This avoids one of the main problems with approaches such as finite difference or finite element methods.\cite{ram2002finite} [[Unknown citation]]
 
@@
 
-The original choice suggested by Wegner \cite{PhysRepWegner0} reads
+The original choice suggested by Wegner \cite{Wegner200177} reads
 \begin{equation}
@@
 basis improves numerical stability enormously, whereas analogous to
-previous FCI \cite{Kvaalcode} and CCSD \cite{PhysRevB.84.115302}
+previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302}
 calculations, the use of an effective interaction improves convergence

### 2016-11-25 Manuscript/paper.tex
spEnergiesQD: clarify White generator denominators

@@
 
-\subsubsection{White's generator}
+\subsubsection{White generator}
 \label{subsec:White}
@@
 One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
-The problem with Wegner's generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
+The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
 Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
@@
 The generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}
-\begin{align}
+\begin{align*}
 \hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
-\end{align}
+\end{align*}
 where
-\begin{align}
-\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i}}
-\label{eq:WhiteFull1} \\
-\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j}}
-\label{eq:WhiteFull2} \\
+\begin{align*}
+\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\Delta^{[1]}_{a, i}} &
+\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\Delta^{[2]}_{a, b, i, j}}
+\end{align*}
+and the denominators $\Delta^{[1]}$ and $\Delta^{[2]}$ are
+\begin{align*}
+\Delta^{[1]}_{a, i} &\equiv H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i} \\
+\Delta^{[2]}_{a, b, i, j} &\equiv H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j} \\
 X_{a, b, i, j}
@@
   &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j}
-\label{eq:White7}
-\end{align}
-
-Compared to Wegner's canonical generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White's generator contribute only linearly with White's generator.
+\end{align*}
+These are the Epstein--Nesbet denominators.
+Some literature use M\o eller--Plesset denominators, which omit the $X_{a, b, i, j}$ term, leading to a slightly different variant of the canonical White generator.
+
+Compared to the Wegner generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.
 This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.
@@
       $R$. A harmonic oscilaltor basis has been used, with an
-      unrenormalized Coulomb repulsion and White's generator. All
+      unrenormalized Coulomb repulsion and the White generator. All
       energies in atomic units.}
@@
       shells $R$. A harmonic oscilaltor basis has been used, with an
-      unrenormalized Coulomb repulsion and White's generator. All
+      unrenormalized Coulomb repulsion and the White generator. All
       energies in atomic units.}
@@
   results which are for $R=18$), employing a Hartree-Fock basis, a
-  bare Coulomb interaction and White's generator. For $N=42$ and
+  bare Coulomb interaction and the White generator. For $N=42$ and
   $\omega=0.1$ results are presented up to $R=22$ major shells. The
@@
 energies of closed-shell systems. In subsection \ref{subsec:Wegner},
-we start with Wegner's canonical generator. Numerical instabilities in
+we start with the Wegner generator. Numerical instabilities in
 the integration process, as well as a rather slow convergence as
@@
 correlations still lead to stiff equation systems, we change in
-subsection \ref{subsec:White} to White's generator. In particular, we
+subsection \ref{subsec:White} to the White generator. In particular, we
 give an overview of the IM-SRG(2) ground state energies for
@@
 two-dimensional quantum dots up to $N=42$ particles. We utilized two
-different generators, Wegner's and White's one, and realized that
-Wegner's generator results in stiff equation systems, whereas White's
+different generators, Wegner and White generators, and realized that
+the Wegner generator results in stiff equation systems, whereas the White
 generator has much better numerics and is computationally more

### 2016-12-12 Manuscript/paper.tex
Add new figures

@@
-\documentclass[amsmath, amssymb, aps, floatfix, nofootinbib, preprintnumbers,showpacs, superscriptaddress, twocolumn]{revtex4-1}
+\input{head_plain}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{bm}
-\usepackage[cmyk]{xcolor}
-\usepackage{dcolumn}
-\usepackage{epsfig}
-\usepackage{float}
+\usepackage{booktabs}
+\usepackage{color}
 \usepackage{graphicx}
-\usepackage{multirow}
+\usepackage{hyperref}
+\usepackage{natbib}
+\usepackage{siunitx}
 \usepackage{subfigure}
@@
 \newcommand{\D}{\operatorname{d\!}}
-\newcommand{\ket}[1]{| #1 \rangle}
 \newcommand{\bra}[1]{\langle #1 |}
 \newcommand{\braket}[2]{\langle #1 | #2\rangle}
+\newcommand{\ket}[1]{| #1 \rangle}
 \newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
@@
 \begin{document}
-
 \title{Studies of quantum dots}
@@
 \author{Fei Yuan}
-\affiliation{National Superconducting Cyclotron Laboratory and
-  Department of Physics and Astronomy,
-  Michigan State University,
-  East Lansing, MI 48824, USA}
+\email{yuan@nscl.msu.edu}
+\homepage{https://people.nscl.msu.edu/~yuan}
+\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
 \author{J\o rgen H\o gberget}
@@
 \author{Sam Novario}
-\affiliation{National Superconducting Cyclotron Laboratory and
-  Department of Physics and Astronomy,
-  Michigan State University,
-  East Lansing, MI 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
 \author{Nathan Parzuchowski}
-\affiliation{National Superconducting Cyclotron Laboratory and
-  Department of Physics and Astronomy,
-  Michigan State University,
-  East Lansing, MI 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
 \author{Sarah Reimann}
@@
 \author{Scott Bogner}
-\affiliation{National Superconducting Cyclotron Laboratory and
-  Department of Physics and Astronomy,
-  Michigan State University,
-  East Lansing, MI 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
 \author{Morten Hjorth-Jensen}
-\affiliation{National Superconducting Cyclotron Laboratory and
-  Department of Physics and Astronomy,
-  Michigan State University,
-  East Lansing, MI 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
 \affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}
@@
 \begin{abstract}
-  We present and compare several many-body methods used to study a quantum dot
-  system.  We calculate the approximate ground state energy of electrons in a
-  circularly symmetric potential well using a harmonic oscillator basis
-  optimized via Hartree-Fock (HF).  We further improve the ground state energy
-  using in-medium similarity renormalization group (IM-SRG).  Additionally, we
-  calculate the addition and removal energies using quasidegenerate
-  perturbation theory (QDPT).  Our results are benchmarked against quasi-exact
-  diffusion Monte Carlo (DMC) and coupled cluster (CC) calculations.
+  We present and compare several many-body methods used to study a quantum dot system.
+We calculate the approximate ground state energy of electrons in a circularly symmetric potential well using a harmonic oscillator basis optimized via Hartree-Fock (HF).
+We further improve the ground state energy using in-medium similarity renormalization group (IM-SRG).
+Additionally, we calculate the addition and removal energies using quasidegenerate perturbation theory (QDPT).
+Our results are benchmarked against quasi-exact diffusion Monte Carlo (DMC) and coupled cluster (CC) calculations.
 \end{abstract}
@@
 and finally
-\begin{widetext}
 \begin{align}
@@
 \end{align}
-\end{widetext}
 \begin{figure}
@@
 \begin{center}
-\caption{Ground state energy (in atomic units) of a circular quantum
-  dot, with $N$ particles and oscillator frequency $\omega$. The
-  IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$
-  results which are for $R=18$), employing a Hartree-Fock basis, a
-  bare Coulomb interaction and the White generator. For $N=42$ and
-  $\omega=0.1$ results are presented up to $R=22$ major shells. The
-  results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained
-  using the extrapolation formula of [[equation?]].}
+  \caption{Ground state energy (in atomic units) of a circular quantum dot, with $N$ particles and oscillator frequency $\omega$.
+The IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$ results which are for $R=18$), employing a Hartree-Fock basis, a bare Coulomb interaction and the White generator.
+For $N=42$ and $\omega=0.1$ results are presented up to $R=22$ major shells.
+The results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained using the extrapolation formula of [[equation?]].}
 \label{tab:SRGDMC-R20}
-\begin{tabular}{ccccc}
-\hline\hline
-$N$ & $\omega$ & IM-SRG(2) &IM-SRG(2)$_{R\rightarrow \infty}$ & DMC \\
-\hline
+\begin{tabular}{SSSSS}
+  \toprule
+  {$N$} & {$\omega$} & {IM-SRG(2)} & {IM-SRG(2)$_{R\rightarrow \infty}$} & {DMC} \\
+  \midrule
   6 & 1.0 & 20.1583 & 20.1468   & 20.1593(1) \\
@@
       & 0.1& 3.4962  &  3.4977 &3.5539(1)\\
-\hline
+  \midrule
   12&1.0 & 65.7280 & 65.6990  & 65.7001(1) \\
@@
       &  0.1&12.2223 &  12.2234 & 12.2698(1)\\
-\hline
+  \midrule
   20& 1.0&155.9737 & 155.9130  & 155.8822(1)\\
@@
       &  0.1&29.95263 &29.9565  & 29.9779(1)\\
-\hline
+  \midrule
   30& 1.0& 308.7673 & 308.6053 & 308.5627(2) \\
@@
       & 0.1& 60.4319& 60.1158 & 60.4205(2)\\
-\hline
+  \midrule
   42& 1.0&543.3398 & 543.3304 & 542.9428(8) \\
@@
       & 0.1& 107.7851&  106.8074& 107.6389(2)\\
- \hline
+  \midrule
   56& 1.0& 880.4159 &  & 879.3986(6) \\
@@
       & 0.28&360.83689  &  & 358.145(2) \\
-\hline
+  \bottomrule
 \end{tabular}
@@
 \end{table}
+
+[[begin unmerged]]
+
+In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems.
+In subsection \ref{subsec:Wegner}, we start with the Wegner generator.
+Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, motivate the use of a Hartree-Fock basis and the Coulomb interaction.
+Since higher correlations still lead to stiff equation systems, we change in subsection \ref{subsec:White} to the White generator.
+In particular, we give an overview of the IM-SRG(2) ground state energies for closed-shell systems up to $N=42$ particles and compare with other \textit{ab initio} many-body methods.
+
+In all our calculations, we perform the integration of the flow equations using the algorithm developed by Shampine and Gordon \cite{shampine1975computer}.
+This algorithm solves linear systems of differential equations based on the implicit Adams method, which is a multi-step method of variable order.
+Source code is freely available \cite{odesolver}.
+
+[[end unmerged]]
 
@@
 
-[[begin unmerged]]
-
-In this section, we discuss the IM-SRG results for the ground-state
-energies of closed-shell systems. In subsection \ref{subsec:Wegner},
-we start with the Wegner generator. Numerical instabilities in
-the integration process, as well as a rather slow convergence as
-function of the number of oscillator shells, motivate the use of a
-Hartree-Fock basis and the Coulomb interaction. Since higher
-correlations still lead to stiff equation systems, we change in
-subsection \ref{subsec:White} to the White generator. In particular, we
-give an overview of the IM-SRG(2) ground state energies for
-closed-shell systems up to $N=42$ particles and compare with other
-\textit{ab initio} many-body methods.\\ In all our calculations, we
-perform the integration of the flow equations using the algorithm
-developed by Shampine and Gordon \cite{shampine1975computer}. This
-algorithm solves linear systems of differential equations based on the
-implicit Adams method, which is a multi-step method of variable
-order. Source code is freely available \cite{odesolver}.
-
-[[end unmerged]]
-
 \section{Conclusions}
@@
 
-We demonstrated the use various many-body theories, Hartree-Fock method, M\o
-eller-Plesset perturbation theory, IM-SRG, as well as quasidegenerate
-perturbation theory to calculate ground state as well as addition and removal
-energies of two-dimensional quantum dots.  We showed that these methods, when
-combined, can give a good approximate description of the systems at moderate
-cost compared to near-exact but much more expensive methods such as FCI and
-DMC.
-
-For ground state energy, we showed that the convergence of IM-SRG is generally
-faster than that of MPPT, and the results are typically closer to the exact
-results.  Similarly, we found that IM-SRG improves the rate of convergence of
-the addition and removal energies, both as the order of perturbation theory
-increases and as the number of shells increases.
-
-There are several directions in which the calculations may be improved.  One
-can attempt to improve the IM-SRG approximation by incorporating some of the
-missing higher-body terms in the commutator.  This would also provide some
-insight into the rate of convergence with respect to the operator truncation.
-While some of the higher-body terms can be rather costly to compute --
-rendering a full 3-body IM-SRG quite expensive -- certain additional
-approximations may be made to alleviate this without incurring the full cost
-of evolving 3-body operators [[Ref?]].
-
-[[As noted earlier [[haven't written that yet]], the application of IM-SRG
-removes a large portion of the QDPT diagrams, which is beneficial as it
-increases the efficiency of the QDPT calculations.  However, many of these
-diagrams can also be eliminated further through an infinite resummation scheme
-[[Any good refs for this?]], which would further reduce the number of diagrams
-in QDPT, especially those of lower order, whic would likely increase the
-accuracy of the result.]]
+We have demonstrated the use of various many-body theories -- Hartree-Fock method, M\o eller-Plesset perturbation theory, in-medium similarity renormalization group, and quasidegenerate perturbation theory -- to calculate ground state as well as addition and removal energies of two-dimensional circular quantum dots up to 56 [[make sure the figure/data for 56 particles stays]] particles.
+We showed that these methods, when combined, can provide a good, approximate description of the systems at moderate cost compared to near-exact but much more expensive methods such as FCI and DMC.
+
+Two different generators, Wegner and White generators, were used [[T/F?]] to perform the calculations.
+It was observed that the Wegner generator results in stiff equation systems, whereas the White generator has much better numerics and is computationally more efficient.[[make sure this is this elaborated in the Results section]] Moreover, we found out that the use of an Hartree-Fock basis improves numerical stability enormously.
+
+For ground state energy, we showed that the convergence of IM-SRG is generally faster than that of MPPT, and the results are typically closer to the the near-exact results.
+Similar to previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302} calculations, the use of an effective interaction improves convergence of the ground state energy as function of the number of oscillator shells.
+[[delete or keep: For more than six particles, we lie in all cases closer to the DMC result than corresponding CCSD calculations do.]]
+
+For addition and removal energies, we found that IM-SRG improves their rate of convergence both as the order of perturbation theory increases and as the number of shells increases.
+
+There are several directions in which the calculations may be improved.
+One can attempt to improve the IM-SRG approximation by incorporating some of the missing higher-body terms in the commutator.
+This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
+While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost [[Ref?]].
+
+As noted earlier [[not yet written]], the application of IM-SRG eliminates a large portion of the QDPT diagrams, which is beneficial as it increases the efficiency of the QDPT calculations.
+However, many of these diagrams can also be eliminated further through an infinite resummation scheme [[Good refs for this?]], which would further reduce the number of diagrams in QDPT, especially those of lower order, whic would likely increase the accuracy of the result.
 
@@
 number of shells in the basis are related to those obtained with an infinite
-number of shells in the basis.  [[Ref: paper on IR/UV extrapolation]] With a
+number of shells in the basis.  [[Ref: IR/UV extrapolation]] With a
 good theoretical foundation, a model of how the observables converge with
@@
 
-We note that this calculation was done entirely using the traditional approach
-of using a high-order ODE solver to solve the flow equation.  A new technique
-developed by T. Morris [[Ref?]] uses an alternative approach that obviates the
-need for a high-order ODE solver, leading to much more efficient computations
-and also allowing operators of other observables to be evolved with greater
-ease.  Implementing this approach would be beneficial as it would allows us to
-study the accuracy and convergence of other observables beyond energy and
-energy differences.
-
-Implementation-wise, our current code constructs the two-particle basis as
-simple Slater determinants without any angular momentum coupling.  This
-approach is often referred to as \textit{m-scheme} in nuclear physics.  This
-method is simple and works well for general systems, but it does not fully
-exploit the circular symmetry present in the quantum dot system.  A more
-efficient approach is to use angular momentum coupling to generate the
-two-particle basis, which is known as \textit{j-scheme} in nuclear physics.
-Combined with the symmetries of the Hamiltonian, this can significantly reduce
-the amount of computation required in this system, albeit at the cost of
-increasing the complexity of the implementation.
-
-A more technical issue is its lack of parallelization: currently, the code
-makes very little use of parallelism and therefore does not scale well on
-modern clusters.  As the problem is not embarrassingly parallel, implementing
-parallelism does introduce additional complications that must be considered.
-Distributing the workload across multiple nodes can significantly reduce the
-cost of the calculations, allowing larger systems to be studied.
-
-[[begin unmerged]]
-
-We have used IM-SRG to study the ground state energy of circular,
-two-dimensional quantum dots up to $N=42$ particles. We utilized two
-different generators, Wegner and White generators, and realized that
-the Wegner generator results in stiff equation systems, whereas the White
-generator has much better numerics and is computationally more
-efficient. Moreover, we found out that the use of an Hartree-Fock
-basis improves numerical stability enormously, whereas analogous to
-previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302}
-calculations, the use of an effective interaction improves convergence
-of the ground state energy as function of the number of oscillator
-shells.  Our IM-SRG(2) results are in excellent agreement with other
-many-body methods, in particular DMC, which can be considered as more
-or less exact benchmark. For more than six particles, we lie in all
-cases closer to the DMC result than corresponding CCSD calculations
-do.
-
-Until now, we have applied the SRG flow equations in m-scheme only. A
-next step, which we are currently working on, is to perform the
-calculations in j-scheme. This allows for further simplifications of
-the flow equations, such that numerical calculations get even more
-efficient.  Moreover, one aspect of great interest is to extend
-IM-SRG(2) to IM-SRG(3), where all operators are truncated one a
-three-body instead of a two-body level. A comparison of both results
-would give insight into the significance of higher correlations and it
-would allow to analyse the convergence behavior of the IM-SRG
-hierarchy of truncation. However, since this is expected to be
-computationally highly expensive, a first alternative would be not to
-look at the whole IM-SRG(3) evolution, but to restrict oneself just to
-certain additional terms, in order to get an impression of how
-important excitations beyond the IM-SRG(2) level are. Since we use an
-initial two-body Hamiltonian, one particular possibility is not to
-save the induced three-body interactions explicitly, but to include
-their loop terms in the calculations for lower-body interaction
-terms. Work along these lines is in progress.\\ Furthermore, we plan
-to apply these improvements not only to quantum dots, but to extend
-our studies to nuclear and/or atomic systems, which opens up an even
-larger range of applications.
-
-[[end unmerged]]
+We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
+A new technique developed by T.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved with greater ease.
+Implementing this approach would be beneficial as it would allows us to study the accuracy and convergence of other observables beyond energy and energy differences.
+
+Implementation-wise, our current code constructs the two-particle states as simple Slater determinants of their one-particle states.
+This approach is often referred to as \textit{m-scheme} in nuclear physics.
+It is a simple approach and works well for general systems, but it does not fully exploit the symmetries in the quantum dot system, since not only is spin projection $\hat S_z$ conserved, but squared spin $\hat S^2$ too.
+A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
+Combining this with the spherical tensor symmetries of the Hamiltonian, this can reduce the amount of computation required in this system via the Eckart-Wigner theoerem, albeit at the cost of increasing the implementation complexity.
+
+A more technical issue is its lack of parallelization: currently, the code makes very little use of parallelism and therefore does not scale well on modern clusters.
+Parallelism would allow the workload and memory resources to be divided over multiple computing nodes, allowing larger systems to be explored, but this must be weighed carefully against the costs of communication, which can be severe if the algorithm is chosen poorly.
+
+Eventually, we plan to apply these theoretical and technical enhancements not only to the study of quantum dots, but to the studies of nuclear and atomic systems, opening up an even larger range of applications.
 
 \begin{acknowledgments}
-  This work was supported by the
-  National Science Foundation Grant No.~PHY-1404159
-  (Michigan State University) and by the Research
-  Council of Norway under contract ISP-Fysikk/216699.
-
-  [[begin unmerged]]
-
-  We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for
-  several discussions. This work was supported by the Research Council
-  of Norway under contract ISP-Fysikk/216699. This research used
-  computational resources of the Notur project in Norway.
-
-  [[end unmerged]]
+  This work was supported by the National Science Foundation Grant No.~PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.
+This research used computational resources of the Notur project in Norway.
+We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for several discussions.
 \end{acknowledgments}
 
+\bibliographystyle{\mybibstyle}
 \bibliography{paper}
-\bibliographystyle{apsrev4-1}
 \end{document}

### 2016-12-12 Datafiles/plot_compare_rel_slopes.py

@@ -14,30 +14,31 @@ d = utils.parse_simple("compare_rel_slopes.txt")
 # so we have to use this awful hack
 x_labels = [
     "'_sigmaA=0.5_sigmaB=4.0', 1.0, 6",
-    "'_sigmaA=0.5_sigmaB=4.0', 1.0, 6",
-    "'_sigmaA=0.5_sigmaB=4.0', 1.0, 12",
     "'_sigmaA=0.5_sigmaB=4.0', 1.0, 12",
     "'_sigmaA=0.5_sigmaB=4.0', 1.0, 20",
-    "'_sigmaA=0.5_sigmaB=4.0', 1.0, 20",
-    "'_sigmaA=0.5_sigmaB=4.0', 0.28, 6",
     "'_sigmaA=0.5_sigmaB=4.0', 0.28, 6",
     "'_sigmaA=0.5_sigmaB=4.0', 0.28, 12",
-    "'_sigmaA=0.5_sigmaB=4.0', 0.28, 12",
     "'_sigmaA=0.5_sigmaB=4.0', 0.28, 20",
-    "'_sigmaA=0.5_sigmaB=4.0', 0.28, 20",
-    "'', 1.0, 6",
+    "'_sigmaA=0.5', 1.0, 6",
+    "'_sigmaA=0.5', 1.0, 12",
+    "'_sigmaA=0.5', 1.0, 20",
+    "'_sigmaA=0.5', 0.28, 6",
+    "'_sigmaA=0.5', 0.28, 12",
+    "'_sigmaA=0.5', 0.28, 20",
+    "'_sigmaB=4.0', 1.0, 6",
+    "'_sigmaB=4.0', 1.0, 12",
+    "'_sigmaB=4.0', 1.0, 20",
+    "'_sigmaB=4.0', 0.28, 6",
+    "'_sigmaB=4.0', 0.28, 12",
+    "'_sigmaB=4.0', 0.28, 20",
     "'', 1.0, 6",
     "'', 1.0, 12",
-    "'', 1.0, 12",
-    "'', 1.0, 20",
     "'', 1.0, 20",
     "'', 0.28, 6",
-    "'', 0.28, 6",
     "'', 0.28, 12",
-    "'', 0.28, 12",
-    "'', 0.28, 20",
     "'', 0.28, 20",
 ]
+x_labels_ = [l.replace("_", " ").replace("sigma", "σ") for l in x_labels]
 x_labels_lookup = dict((x, i) for i, x in enumerate(x_labels))
[…]

### 2016-12-14 Manuscript/paper.tex
Add some results and figures to the manuscript

@@
-\input{head_plain}
+\input{head_plain.tex}
 \usepackage{amsmath}
@@
 \newcommand{\D}{\operatorname{d\!}}
+\newcommand{\E}{\operatorname{e}}
 \newcommand{\bra}[1]{\langle #1 |}
@@
 An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
-In particular, the solver must be able to handle the stiffness that can often arise (even in the case of White generator).
-For this, we use an accurate, high-order ODE solver implementation by Shampine and Gordon that uses the Adams predictor-corrector formulas [[Ref: Shampine and Gordon book]].
+In particular, the solver must be able to handle the stiffness that can often arise (even in the case of White generator, which is designed to avoid some of the stiffness).
+For our numerical experiments, we used a high-order ODE solver algorithm by L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which is a multistep method based on the implicit Adams predictor-corrector formulas.
+Its source code is freely available \cite{odesolver}.
 
@@
 
-The commutator in the flow equations \eqref{eq:imsrgode} guarantees that the evolved state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which demonstrates that IM-SRG is size-extensive.
-Regarding the quality of the SRG results, it means that the error introduced by truncating the many-body expansions scales linearly with the number of particles $N$.
+The commutator in the flow equations \eqref{eq:imsrgode} indicates that the evolved state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which ensures the size-extensive property of IM-SRG by construction.
+This holds even if the commutator is truncated.
+Regarding the quality of the SRG results, this indicates that the error introduced by truncating the many-body expansions scales linearly with the number of particles $N$.
 
@@
 \end{align}
-Substitution of \eqref{eq:ladder_def} into the energy eigenvalue problem $\hat H \ket{\Psi_u^{(N \pm 1)}} = E^{(N\pm1)}_u \ket{\Psi_u^{(N \pm 1)}}$ gives
+Substitution of \eqref{eq:ladder_def} into the energy eigenvalue problem
+\begin{gather*}
+  \hat H \ket{\Psi_u^{(N \pm 1)}} = E^{(N\pm1)}_u \ket{\Psi_u^{(N \pm 1)}}
+\end{gather*}
+gives
 \begin{equation}\label{eq:EOM}
@@
 
-Diffusion Monte Carlo (DMC) is a method for calculating the ground state
-properties via a stochastic process akin to classical diffusion, refining an
-approximate ground state density towards that of the exact ground state.  The
-rules that govern the diffusion process are obtained by evolving the wave
-function using what can be formally be thought of as the time-dependent
-Schr\"odinger equation along imaginary time $\tau \equiv t / \mathrm{i}$:
+Diffusion Monte Carlo (DMC) is a method for calculating the ground state properties via a stochastic process akin to classical diffusion, refining an approximate ground state density towards that of the exact ground state.
+The rules that govern the diffusion process are obtained by evolving the wave function using what can be formally be thought of as the time-dependent Schr\"odinger equation along imaginary time $\tau \equiv t / \mathrm{i}$:
 \begin{align} \label{eq:itse}
@@
 \end{align}
-The solutions to this equation are not unlike the ordinary Schr\"odinger
-equation with a slight but crucial difference in the exponent:
+The solutions to this equation are not unlike the ordinary Schr\"odinger equation with a slight but crucial difference in the exponent:
 \begin{align*}
@@
 \end{align*}
-where $|\Phi(0)\rangle$ is the initial wave function at $\tau = 0$ -- not to
-be confused with the exact ground state of $\hat H$, which we denote
-$|\Psi_0\rangle$ here.  If we decompose the wave function into a sum over the
-eigenstates $|\Psi_n\rangle$,
+where $|\Phi(0)\rangle$ is the initial wave function at $\tau = 0$ -- not to be confused with the exact ground state of $\hat H$, which we denote $|\Psi_0\rangle$ here.
+If we decompose the wave function into a sum over the eigenstates $|\Psi_n\rangle$,
 \begin{align*}
@@
 \end{align*}
-we find that components of the wave function that have negative energy will
-increase exponentially as $\tau \to \infty$, while those with positive energy
-will decrease exponentially.  This property can be exploited to filter out the
-undesirable components, leaving only the ground state energy.  To do this, we
-require a trial energy $E_{\text{T}}$ -- a guess of the ground state energy --
-and replace $\hat H$ in \eqref{eq:itse} with $(\hat H - E_{\text{T}})$ so
-that, if our trial energy is good, all states but the ground states will
-approximately vanish.
+we find that components of the wave function that have negative energy will increase exponentially as $\tau \to \infty$, while those with positive energy will decrease exponentially.
+This property can be exploited to filter out the undesirable components, leaving only the ground state energy.
+To do this, we require a trial energy $E_{\text{T}}$ -- a guess of the ground state energy -- and replace $\hat H$ in \eqref{eq:itse} with $(\hat H - E_{\text{T}})$ so that, if our trial energy is good, all states but the ground states will approximately vanish.
 
@@
 
-[[begin unmerged]]
-
-In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{fig-gs}
+  \caption{Ground state energies.}
+  \label{fig:gs}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{fig-add}
+  \caption{Addition energies.}
+  \label{fig:add}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{fig-rm}
+  \caption{Removal energies.}
+  \label{fig:rm}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{fig-rel-slopes}
+  \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.
+The key observation from this plot is that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
+  \label{fig:rel-slopes}
+\end{figure}
+
+In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems .
 In subsection \ref{subsec:Wegner}, we start with the Wegner generator.
@@
 
-In all our calculations, we perform the integration of the flow equations using the algorithm developed by Shampine and Gordon \cite{shampine1975computer}.
-This algorithm solves linear systems of differential equations based on the implicit Adams method, which is a multi-step method of variable order.
-Source code is freely available \cite{odesolver}.
-
-[[end unmerged]]
-
-In Figure [[fig:gs]] we show the calculated ground state energies from
-Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and
-IM-SRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a
-dashed line in systems where it is known \cite{PhysRevB.84.115302}.
-
-Both perturbation theory and IM-SRG add corrections in addition to the
-Hartree-Fock results to recover the correlation energy and they do quite well
-in recovering the correlation energy in the system.  Compared with MPPT, IM-SRG
-generally converges faster, although does not always converge to the DMC
-result.  Generally speaking, IM-SRG is closer to the DMC result as the number
-of particles increases.
-
-There are a few cases where the IM-SRG over-corrects the result, leading to a
-ground state energy that is lower than the exact result.  This is not
-unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational.  These
-tend to occur when the number of particles is few, or the frequency is very
-low (high correlation).  However, MPPT does not do much better in the high
-frequency regimes as it often converges slower than IM-SRG.
-
-[[Q: should we discuss the absolute/relative correction plots?]]
-
-For our addition and removal energy calculations, the results are summarized
-in Figure [[fig:add]] and Figure [[fig:rm]] respectively.  The figures
-show the the addition/removal energies for Hartree-Fock, combined with IM-SRG
-and/or QDPT (Hartree-Fock is always included, as usual) [[better way to
-explain this? the figure labels are somewhat misleading too]].  The DMC
-results are also shown via dashed lines where they are known.
-
-From these results, we see that the QDPT corrections add a substantial
-contribution to the results of both Hartree-Fock with and without IM-SRG.
-[[quantify ``substantial'' numerically]]
-
-For the IM-SRG results, there is a small asymmetry between the behavior of our
-removal and addition energies: we find that removal energies tend to be more
-accurate and its behavior is relatively stable with respect to the number of
-shells. [[why]]
-
-Interestingly, the addition energy of Hartree-Fock with second-order QDPT
-appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
-This is likely coincidental, as the third-order QDPT dramatically worsens the
-result.
-
-Both Hartree-Fock and IM-SRG results worsen as the frequency decreases, which
-is not unexpected since the correlations become much more dominant.  The
-Hartree-Fock appears to perform much worse, however, as the results converge
-much more slowly as the number of shells increases.
-
-We also note that IM-SRG with 2 particles and frequency 0.1 generally fail to
-give any result as the ODE solver eventually leads to divergence [[Why?]]
-This seems to be a particular quirk associated with this specific system and
-does not usually occur in other systems except in a few extreme, isolated
-cases where there are far too few unoccupied states.
+[[...]]
+
+In Figure \ref{fig:gs} we show the calculated ground state energies from Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.
+The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line in systems where it is known \cite{PhysRevB.84.115302}.
+
+Both perturbation theory and IM-SRG add corrections in addition to the Hartree-Fock results to recover the correlation energy and they do quite well in recovering the correlation energy in the system.
+Compared with MPPT, IM-SRG generally converges faster, although does not always converge to the DMC result.
+Generally speaking, IM-SRG is closer to the DMC result as the number of particles increases.
+
+There are a few cases where the IM-SRG over-corrects the result, leading to a ground state energy that is lower than the exact result.
+This is not unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational in the presence of operator truncations that cause small unitarity violations.
+Such behavior tends to occur when the number of particles is few, or the frequency is very low (high correlation).
+However, MPPT does not do much better in the high frequency regimes as it often converges slower than IM-SRG.
+
+For our addition and removal energy calculations, the results are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.
+The figures show the the addition/removal energies for Hartree-Fock, combined with IM-SRG and/or QDPT (Hartree-Fock is always included, as usual) [[better way to explain this?
+the figure labels are somewhat misleading too]].
+The DMC results are also shown via dashed lines where they are known.
+
+From these results, we see that the QDPT corrections add a substantial contribution to the results of both Hartree-Fock with and without IM-SRG.  [[quantify ``substantial'' numerically]]
+
+Interestingly, the addition energy of Hartree-Fock with second-order QDPT appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
+This is likely coincidental, as the third-order QDPT dramatically worsens the result.
+
+Both Hartree-Fock and IM-SRG results worsen as the frequency decreases, which is not unexpected since the correlations become much more dominant.
+The Hartree-Fock appears to perform much worse, however, as the results converge much more slowly as the number of shells increases.
+
+We also note that IM-SRG with 2 particles and a frequency 0.1 generally fail to give any result as the ODE solver eventually leads to divergence [[Why?]]  This seems to be a quirk isolated to this particular system and does not usually occur in other systems.
+
+[[---]]
+
+To investigate the drifts, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
+\begin{align}
+  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
+\end{align}
+where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.
+The coefficient is defined to ensure the peak of the envelope remains at unity.
+By setting $\sigma_{\mathrm{A}} = 0$ and $\sigma_{\mathrm{B}} = \infty$ one recovers the original Coulomb interaction.
+By increasing $\sigma_{\mathrm{A}}$ one can reduce the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can reduce the long-range part of the interaction.
+For our numerical experiments we consider the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
+
+To analyze the convergence as function of the number of shells $K$, we use a simple but approximate metric, the \textit{relative slope} at $K = 15$:
+\begin{align*}
+  \rho_{15}(\varepsilon) \equiv \frac{\varepsilon_{K = 15} - \varepsilon_{K = 14}}{\varepsilon_{K = 15}}
+\end{align*}
+For the systems we have selected, at $K = 15$ the addition and removal energies have essentially reached the asymptotic behavior (by visual inspection), thus $\rho_{15}$ gives a crude measure of the rate of convergence as a relative quantity independent of the energy unit, allowing it to be meaningfully compared between systems with different interactions and different particle numbers.
+The results are plotted in Figure \ref{fig:rel-slopes}.
+
+Analyzing the figure, we observe that the reducing short-range part of the interaction improves the rate of convergence greatly -- the relative slope has saturated and reached the precision of the ODE solver -- whereas eliminating the long-range part of the interaction had very little effect.
+This demonstrates that the main cause of the slow convergence lies in the highly repulsive, short-ranged part of the interaction, which leads to the presence of nondifferentiable cusps (the so-called \textit{Coulomb cusps}) in the exact wave functions that are difficult to reproduce exactly using linear combinations of the smooth harmonic oscillator wave functions.
+
+The figure also tells us that the convergence is negatively impacted at lower frequencies and, to a lesser extent, by the number of particles.
+Both are expected: lower frequencies increase the correlation in the system, while higher number of particles naturally require more shells to converge.
+
+We also note that the behavior of addition energies versus removal energies tend to be similar, and which one converges faster fluctuates from system to system.
 
@@
 A new technique developed by T.
+D.
 Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved with greater ease.

### 2017-01-05 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 
-The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_T}$
+The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_{\mathrm{T}}}$
 \begin{equation}
- \hat{P}(\tau)\ket{\Psi_T} \equiv \exp\left({-(\hat{H} - E_0)\tau}\right)\ket{\Psi_T}
+ \hat{P}(\tau)\ket{\Psi_{\mathrm{T}}} \equiv \E^{-(\hat{H} - E_0)\tau} \ket{\Psi_{\mathrm{T}}}
 \end{equation}
-\noindent
 where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\hat{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\hat{H}$.
 By expanding the trial state in the eigenfunctions of $\hat{H}$, the ground state is obtained up to a constant factor
-
 \begin{equation}
  \label{eq:DMC_ExactProjection}
- \lim_{\tau\to\infty} \bra{\mathbf{r}}  \hat{P}(\tau) \ket{\Psi_T} = \braket{\Psi_0}{\Psi_T}\Psi_0(\mathbf{r}).
+ \lim_{\tau\to\infty} \bra{\bm{r}}  \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} = \braket{\Psi_0}{\Psi_{\mathrm{T}}}\Psi_0(\bm{r}).
 \end{equation}
 
-Defining $\Phi(\mathbf{r}, \tau) \equiv \bra{\mathbf{r}}\hat{P}(\tau)\ket{\Psi_T}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
-
+Defining $\Phi(\bm{r}, \tau) \equiv \bra{\bm{r}}\hat{P}(\tau)\ket{\Psi_{\mathrm{T}}}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
 \begin{align}
- \Phi(\mathbf{r}, \tau + \delta\tau) &= \bra{\mathbf{r}} P(\tau + \delta\tau) \ket{\Psi_T} \notag\\
- &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \hat{P}(\tau) \ket{\Psi_T} \notag\\
- &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
- &= \int \D\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
- &\equiv \int \D\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
-\end{align}
+ \Phi(\bm{r}, \tau + \delta\tau) &= \bra{\bm{r}} P(\tau + \delta\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
+ &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
+ &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\Phi(\tau)} \notag\\
+ &= \int \D\bm{r}' \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\bm{r}'} \Phi(\bm{r}', \tau)\notag \\
+ &\equiv \int \D\bm{r}' G(\bm{r}, \bm{r}'; \delta\tau) \Phi(\bm{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
+\end{align}
+which defines the Green's function $G$.
 
@@
 For evaluation of the local energy, the trial state is designed to cancel the Coulomb singularities by containing so-called correlation factors, however, this cancellation does not apply to the terms in the Green's function.
-In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\mathbf{r}, \tau) \equiv \Phi(\mathbf{r}, \tau)\Psi_T(\mathbf{r})$.
+In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\bm{r}, \tau) \equiv \Phi(\bm{r}, \tau)\Psi_{\mathrm{T}}(\bm{r})$.
 Note that all previous arguments regarding convergence to the true ground state still applies for the new distribution.
 
-Methods exist for transforming the mixed density into the pure density $|\Phi(\mathbf{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.
+Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.
 
@@
 \begin{align}
-  G(\mathbf{r}, \mathbf{r}'; \delta\tau)_f &= \bra{\mathbf{r}} \exp\left({\frac{1}{2}\nabla\cdot \left[\left(\nabla - \mathbf{F}(\mathbf{r})\right)\right] - \left(E_L(\mathbf{r}) - E_T\right)}\right)\ket{\mathbf{r}'} \label{eq:DMC_IS_GF_raw}\\
-  &\propto e^{-\left[|\mathbf{r} - \mathbf{r}' - \frac{1}{2}\delta\tau\mathbf{F}(\mathbf{r})|^2/2\delta\tau\right]} \label{eq:DMC_IS_GF}\\
-  &\qquad\times e^{-\left[\frac{1}{2}\left[E_L(\mathbf{r'}) + E_L(\mathbf{r})\right] - E_T\right]\delta\tau} + \mathcal{O}(\delta\tau^2), \notag
+  G(\bm{r}, \bm{r}'; \delta\tau)_f &= \bra{\bm{r}} \E^{\frac{1}{2} \hat{\bm{\nabla}} \cdot \left(\hat{\bm{\nabla}} - \bm{F}(\bm{r})\right) - \left(E_{\mathrm{L}}(\bm{r}) - E_{\mathrm{T}}\right)} \ket{\bm{r}'} \label{eq:DMC_IS_GF_raw}\\
+  &\propto \E^{-\left(|\bm{r} - \bm{r}' - \frac{1}{2}\delta\tau\bm{F}(\bm{r})|^2/(2\delta\tau)\right)} \label{eq:DMC_IS_GF}\\
+  &\qquad\times \E^{-\left(\frac{1}{2}\left(E_{\mathrm{L}}(\bm{r'}) + E_{\mathrm{L}}(\bm{r})\right) - E_{\mathrm{T}}\right) \delta\tau} + \mathcal{O}\bigl((\delta\tau)^2\bigr), \notag
 \end{align}
@@
 \begin{equation}
-  \mathbf{F}(\mathbf{r}) = 2\Psi_T(\mathbf{r})^{-1} \nabla \Psi_T(\mathbf{r})
+  \bm{F}(\bm{r}) = \frac{2 \hat{\bm{\nabla}} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
 \end{equation}
-
-\noindent
 is the drift vector commonly referred to as the \textit{quantum force}.
@@
 \begin{equation}
-E_L(\mathbf{r}) = \Psi_T(\mathbf{r})^{-1}\hat{H} \Psi_T(\mathbf{r})
+E_{\mathrm{L}}(\bm{r}) \equiv \frac{\hat{H} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
 \end{equation}
-is necessarily sampled from $|\Psi_T(\mathbf{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_T(\mathbf{r})$.
+is necessarily sampled from $|\Psi_{\mathrm{T}}(\bm{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_{\mathrm{T}}(\bm{r})$.
 
@@
 The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of \eqref{eq:DMC_IS_GF}.
-Let $G_b$ denote the value of the branching function at a given position.
-Correct weighting is then ensured by guaranteeing $m = \max\left(\mathrm{floor}\left(G_b\right)-1, 0\right)$ branches with a probability $G_b - m$ of getting an additional branch.
+Let $G_{\mathrm{b}}$ denote the value of the branching function at a given position.
+Correct weighting is then ensured by guaranteeing $m = \max\{0, \lfloor G_{\mathrm{b}} \rfloor - 1\}$ branches\footnote{$\lfloor x \rfloor$ denotes the floor of $x$, namely the largest integer $n$ such that $n \le x$.} with a probability $G_{\mathrm{b}} - m$ of getting an additional branch.
 A branch is an identical copy of the corresponding walker, with an identical past but with a different future.
@@
 
-Initially, $N_w$ walkers are initialized to span $|\Psi_T(\mathbf{r})|^2$.
+Initially, $N_{\mathrm{w}}$ walkers are initialized to span $|\Psi_{\mathrm{T}}(\bm{r})|^2$.
 This is ensured by using the Metropolis Algorithm.
@@
 \begin{equation}
-x_{i+1} = x_i + \frac{1}{2}\delta\tau F(\mathbf{r})_x + \xi,
+x_{i+1} = x_i + \frac{1}{2} \delta \tau F(\bm{r})_x + \xi,
 \end{equation}
-\noindent
-where $\xi$ is a uniform distributed random number with variance $\mathrm{Var}(\xi) = 2D\delta\tau$. A typical value of $N_w$ in this work is 250\,000.
-
-For each time step, diffusion and branching repeats a given number of blocks $N_b$ for each walker.
+where $\xi$ is a uniform distributed random number with variance $\operatorname{Var}(\xi) = 2D\delta\tau$. A typical value of $N_{\mathrm{w}}$ in this work is \num{250000}.
+
+For each time step, diffusion and branching repeats a given number of blocks $N_{\mathrm{b}}$ for each walker.
 New branches are not active until the next time step, and if a walker hits zero branches the block repetition stops.
-During these block loops, the trial energy $E_T$ is sampled for use in the next time step $k+1$
-
+During these block loops, the trial energy $E_{\mathrm{T}}$ is sampled for use in the next time step $k+1$
 \begin{equation}
- E_T^{k+1} = \frac{1}{M^{(k)}}\sum_{i=1}^{M^{(k)}} G_b(\mathbf{r}^{(k)}_i)E_L(\mathbf{r}^{(k)}_i),
+ E_{\mathrm{T}}^{k+1} = \frac{1}{M_k}\sum_{i=1}^{M_k} G_{\mathrm{b}}(\bm{r}^{(k)}_i)E_{\mathrm{L}}(\bm{r}^{(k)}_i),
 \end{equation}
-\noindent
-where $M^{(k)}$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_b = 100$ to be sufficient.
-
-Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_c$ trial energies calculated after $N_t$ thermalization cycles
+where $M_k$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_{\mathrm{b}} = 100$ to be sufficient.
+
+Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_{\mathrm{c}}$ trial energies calculated after $N_{\mathrm{t}}$ thermalization cycles
 \begin{equation}
- E_0 = \frac{1}{N_c-N_t}\sum\limits_{k=N_t}^{N_c} E_T^{(k)}.
+ E_0 = \frac{1}{N_{\mathrm{c}}-N_{\mathrm{t}}} \sum_{k=N_{\mathrm{t}}}^{N_{\mathrm{c}}} E_{\mathrm{T}}^{(k)}.
 \end{equation}
@@
 
-In this work, the trial state has been chosen to consist of a single Slater determinant (cite)
-together with a single variational parameter Padé-Jastrow correlation function (cite).
-
-The Slater determinant contains eigenstates $\phi_n(\mathbf{r})$ of the 2-dimensional harmonic oscillator
+In this work, the trial state has been chosen to consist of a single Slater determinant [[cite]] together with a single variational parameter Pad\'e-Jastrow correlation function [[cite]].
+
+The Slater determinant contains eigenstates $\phi_n(\bm{r})$ of the 2-dimensional harmonic oscillator
 with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$
 such that $\omega\to\alpha\omega$ in all solutions:
-
 \begin{equation}
- \phi_n(\mathbf{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\exp(-\alpha\omega r^2),
+ \phi_n(\bm{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\E^{-\alpha\omega r^2}.
 \end{equation}
-
-\noindent
-where $H_n$ is the $n$'th level Hermite polynomial.
+where $H_n$ is the $n$th level Hermite polynomial.
 
@@
 Due to the Hamiltonian being spin independent we may split the Slater determinant into two equal parts -
-one for each spin level (cite). The overall form of the trial state is as follows:
-
+one for each spin level [[cite]]. The overall form of the trial state is as follows:
 \begin{equation}
- \Psi_T(\mathbf{r}) = S(\mathbf{r}^\uparrow) S(\mathbf{r}^\downarrow) \prod_{i<j}^{N} J(r_{ij}),
+ \Psi_{\mathrm{T}}(\bm{r}) \equiv S(\bm{r}^\uparrow) S(\bm{r}^\downarrow) \prod_{i<j}^{N} J(r_{i,j}),
 \end{equation}
-
 with
-
 \begin{equation}
- S(\mathbf{r}^s) =  \left| \begin{array}{cccc}
-\phi_1(\mathbf{r}^s_1) & \phi_2(\mathbf{r}^s_1)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_1) \\
-\phi_1(\mathbf{r}^s_2) & \phi_2(\mathbf{r}^s_2)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_2) \\
+ S(\bm{r}^s) \equiv \begin{vmatrix}
+\phi_1(\bm{r}^s_1) & \phi_2(\bm{r}^s_1)& \cdots & \phi_{N/2}(\bm{r}^s_1) \\
+\phi_1(\bm{r}^s_2) & \phi_2(\bm{r}^s_2)& \cdots & \phi_{N/2}(\bm{r}^s_2) \\
 \vdots & \vdots& \ddots & \vdots \\
-\phi_1(\mathbf{r}^s_\frac{N}{2}) & \phi_2(\mathbf{r}^s_\frac{N}{2})& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_\frac{N}{2}) \\
- \end{array} \right|,
+\phi_1(\bm{r}^s_{N/2}) & \phi_2(\bm{r}^s_{N/2})& \cdots & \phi_{N/2}(\bm{r}^s_{N/2}) \\
+ \end{vmatrix},
 \end{equation}
-
 and
-
 \begin{equation}
- J(r_{ij}) = \exp\left(\frac{r_{ij}}{1 + \beta r_{ij}}\right),
+ J(r_{i, j}) \equiv \exp\left(\frac{r_{i, j}}{1 + \beta r_{i, j}}\right),
 \end{equation}
-
-where $\mathbf{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons.
+where $\bm{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons.
 Since Metropolis Monte-Carlo only involves ratios of density functions, all normalization factors are skipped.
@@
 As a consequence of the variational principle, the optimal numeric values for $\alpha$ and $\beta$ can be found by minimizing the energy in the variational parameter space.
-For this we have used the adaptive step gradient descent method (cite ASGD).
+For this we have used the adaptive step gradient descent method [[cite ASGD]].
 
@@
 
-A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the CPU-time of most calculations.
-We refer to Refs (cite optimization techniques) for more information.
-Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once
-for the entire calculation. This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is
-preserved under differentiation.
+A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the computation time of most calculations.
+We refer to Refs [[cite optimization techniques]] for more information.
+Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once for the entire calculation.
+This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is preserved under differentiation.
 
@@
 
-In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems .
-In subsection \ref{subsec:Wegner}, we start with the Wegner generator.
-Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, motivate the use of a Hartree-Fock basis and the Coulomb interaction.
-Since higher correlations still lead to stiff equation systems, we change in subsection \ref{subsec:White} to the White generator.
+[[Sarah's discussions on ground state energy are absent :(]]
+In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems.
+We start with the Wegner generator in subsection [[??]].
+Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, favors the use of a Hartree-Fock basis and the Coulomb interaction.
+Since higher correlations still lead to stiff equation systems, we change in subsection [[??]] to the White generator.
 In particular, we give an overview of the IM-SRG(2) ground state energies for closed-shell systems up to $N=42$ particles and compare with other \textit{ab initio} many-body methods.
@@
 
-In Figure \ref{fig:gs} we show the calculated ground state energies from Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.
-The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line in systems where it is known \cite{PhysRevB.84.115302}.
+\subsection{Extrapolation}
+
+In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.
+The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line \cite{PhysRevB.84.115302}.
 
@@
 
-To investigate the drifts, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
+\subsection{Slow convergence}
+
+When the tail part of the convergence plots are magnified about a factor of ten or so [[double-check this number]], we noticed that the addition and removal energies are still drifting somewhat [[quantify how much]], hinting that the convergence rate is probably not exponential.
+
+To investigate the rate of convergence, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
 \begin{align}
@@
 We also note that the behavior of addition energies versus removal energies tend to be similar, and which one converges faster fluctuates from system to system.
+
+\subsection{Extrapolation}
+
+As suggested by Kvaal in \cite{PhysRevB.80.045321}, the asymptotic convergence of the wave function can be approximately described by a power law model: [[assuming I understood his paper correctly]]
+\begin{align*}
+  \Delta E \propto K^{-\beta}
+\end{align*}
+where $\Delta E$ is the error in the energy, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.
+Essentially, the \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
+
+It is difficult to ascertain what $\beta$ is \textit{a priori}, but based on Kvaal's results $\beta$ is expected to be below $5$ for quantum dot systems.
+To determine this from our numerical calculations, we perform a curve using the following power-law model:
+\begin{align} \label{eq:power_law_model}
+  E = \alpha K^{-\beta} + \gamma
+\end{align}
+As with most nonlinear curve fits, it is often fairly sensitive to the initial parameters.
+To extract the initial parameters, we first do a linear fit on the logarithm of the \emph{derivative} $\partial E / \partial K$ against the logarithm of $K$:
+\begin{align*}
+  \ln \left(\frac{\partial E}{\partial K}\right) = \ln(\alpha) - \beta \ln(K)
+\end{align*}
+The derivative is computed numerically using finite differences of adjacent data points.
+This amplifies the noise but linear fits do have the advantage of being very reliable to fit, hence the results are useful as guesses for the more accurate power-law fit.
+This does not give us a guess for the infinite-basis energy $\gamma$, but we can estimate it by solving \label{eq:power_law_model} given a single data point and the (estimated) model paramters $\alpha$ and $\beta$.
 

### 2017-01-06 Manuscript/paper.tex
More extrapolation experiments

@@
 As with most nonlinear curve fits, it is often fairly sensitive to the initial parameters.
-To extract the initial parameters, we first do a linear fit on the logarithm of the \emph{derivative} $\partial E / \partial K$ against the logarithm of $K$:
+To extract the initial parameters, we first do a linear fit on $\ln (\partial E / \partial K)$ against $\ln (K)$:
 \begin{align*}
@@
 \end{align*}
-The derivative is computed numerically using finite differences of adjacent data points.
-This amplifies the noise but linear fits do have the advantage of being very reliable to fit, hence the results are useful as guesses for the more accurate power-law fit.
-This does not give us a guess for the infinite-basis energy $\gamma$, but we can estimate it by solving \label{eq:power_law_model} given a single data point and the (estimated) model paramters $\alpha$ and $\beta$.
+The derivative is approximated using finite differences of adjacent data points:
+\begin{align*}
+  \frac{\partial E}{\partial K} \approx E\left(K + \frac{1}{2}\right) - E\left(K - \frac{1}{2}\right)
+\end{align*}
+The process of calculating a derivative amplifies the noise, but linear fits do have the strong advantage of being very reliable to fit -- there is little concern about being stuck in a local minimum -- as well as making the results easy to judge by visually.
+Of course, linear fits do not weigh the individual contributions equally, thus a more accurate nonlinear curve fit is required afterward.
+One could in principle do a power-law fit on $\partial E/\partial K$ against $K$, but numerical experiments show that as the noise level becomes large this fitting tends to produce abnormal results.
+
+Instead, we use the results as inputs for a power-law fit of $E$ against $K$, which is not as sensitive to noise.
+We do require a guess for the infinite-basis energy $\gamma$, which we estimate by fitting \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
+Finally, we do a fit with all three parameters free to vary.
+
+There is still one additional tuning knob for this model that is not explicitly shown in \eqref{eq:power_law_model}: the number of data points taken into consideration.
+Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still far from convergence.
+To remedy this, we restrict ourselves to fitting only the last $n_{\mathrm{f}}$ data points.
+If $n_{\mathrm{f}}$ is too high, then the non-asymptotic behavior would perturb the result too much, whereas if $n_{\mathrm{f}}$ is too small, the noise will obscure the result.
+[[Find ideal number]] [[Maybe it's better to use an explicit K range, rather than using the number of points]]
+
+[[Hypothesis for the poor HF fits: either it's decaying so fast that it quickly becomes dominated by the precision of the calculation, or it's exponential.]]
 

### 2017-01-06 Datafiles/plot_change.py

@@ -8,9 +8,6 @@ import utils
 FIT_TYPES = ["loglog", "semilog"]
 
 def plot(interactive, fit_type):
-    if interactive:
-        plt.ion()
-
     suffix = ""
     fit_points = 4
 
@@ -58,7 +55,7 @@ def plot(interactive, fit_type):
                              fit_points=fit_points,
                              **kwargs)
         sys.stdout.write("{}\n\n".format(
-            json.dumps(r["extra"], **utils.JSON_PRETTY)))
+            json.dumps(utils.sanitize_json(r["extra"]), **utils.JSON_PRETTY)))
         sys.stdout.flush()
         return r["x"], r["y"]
 
@@ -91,15 +88,12 @@ def plot(interactive, fit_type):
             sys.stderr.write("// Figure saved to: {}\n\n".format(fn))
             sys.stderr.flush()
 
-    if interactive:
-        plt.show(block=True)
-
 def main():
     p = argparse.ArgumentParser()
     p.add_argument("-i", "--interactive", action="store_true")
     kwargs = vars(p.parse_args())
-    utils.init(__file__)
-    for fit_type in FIT_TYPES:
-        plot(fit_type=fit_type, **kwargs)
+    with utils.plot(__file__, interactive=kwargs["interactive"]):
+        for fit_type in FIT_TYPES:
+            plot(fit_type=fit_type, **kwargs)
 
 main()

### 2017-01-06 Datafiles/plot_gsenergy.py

@@ -1,139 +1,0 @@
-#!/usr/bin/env python3
-import argparse, json, os, scipy, sys
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-import utils
-
-FIT_TYPES = ["loglog", "semilog"]
-
-def plot(interactive):
-    if interactive:
-        plt.ion()
-
-    d = pd.read_csv("imsrg-qdpt/dat_gsenergy.txt",
-                    header=0, index_col=False,
-                    delim_whitespace=True)
-    d = d[d["num_filled"] == 3]
-    d = d[d["freq"] == 1.0]
-    d = d[d["freq"] == 1.0]
-    fit_type = "loglog"
-    fit_points = 7
-
-    for [num_filled, freq], gg in d.groupby(["num_filled", "freq"]):
-        fig, ax = plt.subplots()
-        fig.set_size_inches(8, 10)
-        for method, g in gg.groupby(["method"]):
-            g = g.sort_values(["num_shells"])
-            g["d_num_shells"] = g["num_shells"].diff()
-            g["d_energy"] = g["energy"].diff()
-            g["d_energy_d_num_shells"] = g["energy"].diff()
-            #g = g.dropna()
-
-            def guess_constant(a, b):
-                return g["energy"].iat[-1] - a * g["num_shells"].iat[-1] ** b
-
-            x = g["num_shells"] - g["d_num_shells"] / 2.0
-            y = abs(g["d_energy"] / g["d_num_shells"])
-            fit = utils.fit_change(fit_type=fit_type,
-                                   fit_points=fit_points,
-                                   x=x,
-                                   y=y,
-                                   num_filled=num_filled,
-                                   freq=freq,
-                                   method=method)
-            sys.stdout.write("{}\n\n".format(
-                json.dumps(utils.sanitize_json(fit["extra"]),
-                           **utils.JSON_PRETTY)))
-            sys.stdout.flush()
-            guess_c = guess_constant(fit["extra"]["coefficient"],
-                                     fit["extra"]["exponent"])
-            fit_label = ("{method} deriv fit ("
-                         "E_gnd = ({coefficient:.3g}±{coefficient_err:.2g}) * K ** "
-                         "({exponent:.3g}±{exponent_err:.2g}) + "
-                         "(≈{constant:.5g})"
-                         .format(constant=guess_c, **fit["extra"]))
-
-            def f(x, a, b, c):
[…]

### 2017-01-06 Datafiles/plot_gsenergy2.py

@@ -1,0 +1,214 @@
+#!/usr/bin/env python3
+import argparse, json, os, scipy, sys
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import utils
+
+def do_fit(data, deriv_data):
+    '''Perform a fit using a power law model
+
+        y = a * x ** b + c
+
+    data: DataFrameish{"x", "y"}
+    deriv_data: DataFrameish{"x", "dydx"}
+    '''
+    result = {}
+
+    r = utils.fit_change(
+        fit_type="loglog",
+        fit_points=0,
+        x=deriv_data["x"],
+        y=deriv_data["dydx"],
+    )
+    result["logderiv"] = r["extra0"] # linear fit on log|dy/dx|-log(x)
+    try:
+        result["deriv"] = r["extra"]     # power fit on dy/dx-x
+    except KeyError:
+        pass
+
+    b0 = result["logderiv"]["exponent"]
+    a0 = result["logderiv"]["coefficient"]
+    c0, var_c0 = scipy.optimize.curve_fit(
+        lambda x, c: a0 * x ** b0 + c,
+        data["x"], data["y"], p0=[0.0])
+    result["fixedab"] = {
+        "exponent": b0,
+        "coefficient": a0,
+        "constant": c0[0],
+        "constant_err": var_c0[0] ** 0.5,
+    }
+
+    try:
+        abc, var_abc = scipy.optimize.curve_fit(
+            lambda x, a, b, c: a * x ** b + c,
+            data["x"], data["y"], p0=[a0, b0, c0])
+    except RuntimeError:
+        pass
+    else:
+        result["full"] = {
+            "exponent": abc[1],
+            "exponent_err": var_abc[1, 1] ** 0.5,
+            "coefficient": abc[0],
+            "coefficient_err": var_abc[0, 0] ** 0.5,
+            "constant": abc[2],
+            "constant_err": var_abc[2, 2] ** 0.5,
+            "covariance": var_abc,
+        }
+
+    return result
+
+def plot(interactive):
+
+    d = pd.read_csv("imsrg-qdpt/dat_gsenergy.txt",
+                    header=0, index_col=False,
+                    delim_whitespace=True)
+
+    d_dmc = pd.read_csv("dat-qdsfe.jEYRh-4ptC1Dr5nlBcz0tg/dat-gs-dmc.txt",
+                        header=0, index_col=False,
[…]

### 2017-01-06 Datafiles/utils.py

@@ -1,5 +1,6 @@
-import functools, json, os, sys
+import contextlib, functools, json, os, sys
 import matplotlib
+import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 import scipy.optimize
@@ -34,9 +35,40 @@ def matplotlib_try_enable_deterministic_svgs():
         sys.stderr.flush()
 
 def init(filename):
+    plot(filename, interactive=False).__enter__()
+
+@contextlib.contextmanager
+def plot(filename, interactive):
     os.chdir(os.path.dirname(filename))
     matplotlib_try_enable_deterministic_svgs()
     matplotlib.style.use("ggplot")
+    if interactive:
+        plt.ion()
+    yield
+    if interactive:
+        plt.show(block=True)
+
+def savefig(fig, interactive, name):
+    if not interactive:
+        fn = "../FigureFiles/fig-{name}.svg".format(**locals())
+        fig.savefig(fn)
+        plt.close(fig)
+        sys.stderr.write("// Figure saved to: {}\n\n".format(fn))
+        sys.stderr.flush()
+
+def update_range(r, x):
+    for x in np.array(x).flatten():
+        # make sure NaN gets handled correctly
+        if r[0] == None or not (x >= r[0]):
+            r[0] = x
+        if r[1] == None or not (x <= r[1]):
+            r[1] = x
+
+def expand_range(r, factor):
+    return np.array([
+        r[0] - factor * (r[1] - r[0]),
+        r[1] + factor * (r[1] - r[0]),
+    ])
 
 def skip_comment_char(read_func, filename):
     with open(filename) as f:
@@ -62,6 +94,9 @@ def sanitize_json(j):
         return int(j)
     raise TypeError("can't convert to JSON: {!r} ({})"
                     .format(j, type(j)))
+
+def json_pretty(j):
+    return json.dumps(sanitize_json(j), **JSON_PRETTY)
 
 def parse_simple(fn):
     return skip_comment_char(
@@ -187,51 +222,47 @@ def get_ar_energies_for_v(v):
         yield d
 
 def fit_change(fit_type, fit_points, x, y, **params):
+    # note: y here is the derivative
     x_in = x[-fit_points:]
     y_in = y[-fit_points:]
+    sign = np.sign(np.mean(y_in))
[…]

### 2017-01-08 Manuscript/paper.tex
Add new figures

@@
 Of course, linear fits do not weigh the individual contributions equally, thus a more accurate nonlinear curve fit is required afterward.
-One could in principle do a power-law fit on $\partial E/\partial K$ against $K$, but numerical experiments show that as the noise level becomes large this fitting tends to produce abnormal results.
-
-Instead, we use the results as inputs for a power-law fit of $E$ against $K$, which is not as sensitive to noise.
+
+We use the results as inputs for a power-law fit of $E$ against $K$, which is not as sensitive to noise.
 We do require a guess for the infinite-basis energy $\gamma$, which we estimate by fitting \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
@@
 
-There is still one additional tuning knob for this model that is not explicitly shown in \eqref{eq:power_law_model}: the number of data points taken into consideration.
+There is still one additional tuning knob for this model that is not explicitly shown in \eqref{eq:power_law_model}: the range of data points taken into consideration.
 Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still far from convergence.
-To remedy this, we restrict ourselves to fitting only the last $n_{\mathrm{f}}$ data points.
-If $n_{\mathrm{f}}$ is too high, then the non-asymptotic behavior would perturb the result too much, whereas if $n_{\mathrm{f}}$ is too small, the noise will obscure the result.
-[[Find ideal number]] [[Maybe it's better to use an explicit K range, rather than using the number of points]]
+To remedy this, we restrict ourselves to fitting only the last few data points within some chosen range.
+If range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, the noise will obscure the result.
+This part is tuned by hand based on observations of the log-log plot: we expect the asymptotic region to lie more or less on a straight line.
+
+[[Idea for further exploration: see how much the extrapolation improves the result, and see what happens as we increase the number of shells included in the fit on the right/upper bound.]]
 

### 2017-01-08 Datafiles/plot_fit.py

@@ -1,5 +1,5 @@
 #!/usr/bin/env python3
-import argparse, json, os, scipy, sys
+import argparse, json, os, scipy, sys, traceback
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
@@ -112,6 +112,7 @@ def plot_fits(data,
     x_c = np.linspace(data[x_col].min(), data[x_col].max(), 250) # continuous x
     for title_key, gg in utils.groupby(data, title_cols):
         fig, [ax1, ax2] = plt.subplots(2)
+        fig.set_size_inches(8, 10) # otherwise the text will get obscured
         y_range = np.array([np.nan, np.nan])
         for color_key, g in utils.groupby(gg, color_cols):
             color = get_color(**color_key)
@@ -119,30 +120,33 @@ def plot_fits(data,
             g = g.sort_values([x_col])
             d = g.rename(columns={x_col: "x", y_col: "y"})
             deriv_d = differentiate(d, "x", "y", "dydx")
-            fit = do_fit(
-                d[d["x"].between(*fit_range)],
-                deriv_d[deriv_d["x"].between(*fit_range)])
+            x = deriv_d["x"]
+            dydx = deriv_d["dydx"]
+            ax1.plot(x, abs(dydx), "x", label=label, color=color)
+
+            d_subset = d[d["x"].between(*fit_range)]
+            deriv_subset = deriv_d[deriv_d["x"].between(*fit_range)]
+            if len(deriv_subset) < 2:
+                continue
+            fit = do_fit(d_subset, deriv_subset)
             sys.stdout.write(utils.json_pretty(fit) + "\n\n")
             sys.stdout.flush()
 
-            x = deriv_d["x"]
-            dydx = deriv_d["dydx"]
-            ax1.plot(x, abs(dydx), "o", label=label, color=color)
             for stage, result in fit.items():
                 if stage == "fixedab":
                     continue # fixedab yields the same plot here as logderiv
                 a = result["coefficient"]
                 b = result["exponent"]
                 b_err = result.get("exponent_err", None)
-                dydx = a * b * x ** (b - 1.0)
+                dydx_c = a * b * x_c ** (b - 1.0)
                 ax1.plot(
-                    x, abs(dydx), linestyle=STAGE_TO_LINESTYLE[stage],
[…]

### 2017-01-08 Datafiles/plot_fit.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+set -eu
+dir=`dirname "$0"`
+cd "$dir"
+i=${PLOTFLAGS-} # use -i for interactive
+
+./plot_fit.py $i --num-filled=1 --freq=1.0 --fit-start=6 ground
+./plot_fit.py $i --num-filled=1 --freq=0.28 --fit-start=6 ground
+./plot_fit.py $i --num-filled=2 --freq=1.0 --fit-start=6 ground
+./plot_fit.py $i --num-filled=2 --freq=0.28 --fit-start=6 ground
+./plot_fit.py $i --num-filled=3 --freq=1.0 --fit-start=9 ground
+./plot_fit.py $i --num-filled=3 --freq=0.28 --fit-start=9 ground
+./plot_fit.py $i --num-filled=4 --freq=1.0 --fit-start=10 ground
+#needs more data:
+#./plot_fit.py $i --num-filled=4 --freq=0.28 --fit-start=¿ ground
+./plot_fit.py $i --num-filled=5 --freq=1.0 --fit-start=15 ground
+./plot_fit.py $i --num-filled=5 --freq=0.28 --fit-start=17 ground
+./plot_fit.py $i --num-filled=6 --freq=1.0 --fit-start=16 ground
+
+./plot_fit.py $i --num-filled=1 --freq=1.0 --fit-start=7 add
+./plot_fit.py $i --num-filled=1 --freq=0.28 --fit-start=7 add
+./plot_fit.py $i --num-filled=2 --freq=1.0 --fit-start=10 add
+./plot_fit.py $i --num-filled=2 --freq=0.28 --fit-start=10 add
+./plot_fit.py $i --num-filled=3 --freq=1.0 --fit-start=13 add
+./plot_fit.py $i --num-filled=3 --freq=0.28 --fit-start=13 add
+./plot_fit.py $i --num-filled=4 --freq=1.0 --fit-start=13 add

### 2017-01-08 Datafiles/utils.py

@@ -39,13 +39,13 @@ def init(filename):
     plot(filename).__enter__()
 
 @contextlib.contextmanager
-def plot(filename):
+def plot(filename, block=True):
     os.chdir(os.path.dirname(filename))
     matplotlib_try_enable_deterministic_svgs()
     matplotlib.style.use("ggplot")
     yield
     if matplotlib.rcParams["interactive"]:
-        plt.show(block=True)
+        plt.show(block=block)
 
 def savefig(fig, name):
     if not matplotlib.rcParams["interactive"]:
@@ -93,7 +93,7 @@ def load_json_records(fn):
 def sanitize_json(j):
     if isinstance(j, dict):
         return dict((k, sanitize_json(v)) for k, v in j.items())
-    if isinstance(j, list) or isinstance(j, np.ndarray):
+    if isinstance(j, list) or isinstance(j, tuple) or isinstance(j, np.ndarray):
         return [sanitize_json(x) for x in j]
     if isinstance(j, float) or isinstance(j, int) or isinstance(j, str):
         return j
@@ -106,6 +106,33 @@ def sanitize_json(j):
 
 def json_pretty(j):
     return json.dumps(sanitize_json(j), **JSON_PRETTY)
+
+def load_json(fn, fallback=None):
+    if os.path.exists(fn):
+        with open(fn) as f:
+            return json.load(f)
+    return fallback
+
+def save_json(fn, j):
+    with open(fn + ".tmp", "w") as f:
+        f.write(json_pretty(j))
+    os.rename(fn + ".tmp", fn)
+
+def sync_axes_lims(ax, settings, save):
+    setting = settings.get("xlim")
+    if setting:
+        ax.set_xlim(setting)
+    setting = settings.get("ylim")
+    if setting:
+        ax.set_ylim(setting)
+    def on_xlims_changed(ax):
+        settings["xlim"] = ax.get_xlim()
+        save()
+    def on_ylims_changed(ax):
+        settings["ylim"] = ax.get_ylim()
+        save()
+    ax.callbacks.connect("xlim_changed", on_xlims_changed)
+    ax.callbacks.connect("ylim_changed", on_ylims_changed)
 
 def parse_simple(fn):
     return skip_comment_char(

### 2017-01-11 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 
-\begin{figure}%[hbtp]
-     \begin{center}
-        \subfigure[Results for $N=6$ and $\omega=1.0$ ]{
+\begin{figure}
+  \centering
+  \subfigure[Results for $N=6$ and $\omega=1.0$]{
     \label{fig:N6hw1}
@@
   }
-        \subfigure[Results for $N=6$ and $\omega=0.5$ ]{
+  \subfigure[Results for $N=6$ and $\omega=0.5$]{
     \label{fig:N6hw05}
     \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
-        }\\ %  ------- End of the first row ----------------------%
-        \subfigure[Results for $N=6$ and $\omega=0.28$ ]{
+  } \\
+  \subfigure[Results for $N=6$ and $\omega=0.28$]{
     \label{fig:N6hw028}
@@
   }
-        \subfigure[Results for $N=6$ and $\omega=0.1$ ]{
+  \subfigure[Results for $N=6$ and $\omega=0.1$]{
     \label{fig:N6hw01}
@@
   }
-    \end{center}
-    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
-      for circular quantum dots for $N=6$ and $\omega=1.0$
-       The results are compared with diffusion Monte Carlo (DMC),
-      coupled cluster at the level of singles and doubles (CCSD), full
-      configuration interaction (FCI) and Hartree-Fock calculations
-      (HF) as functions of the number of major oscillator shells
-      $R$. A harmonic oscilaltor basis has been used, with an
-      unrenormalized Coulomb repulsion and the White generator. All
-      energies in atomic units.}
+  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=6$ and $\omega=1.0$ The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
+A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
+All energies in atomic units.}
   \label{fig:N6}
@@
 
-\begin{figure}%[hbtp]
-     \begin{center}
-        \subfigure[Results for $N=12$ and $\omega=1.0$ ]{
+\begin{figure}
+  \centering
+  \subfigure[Results for $N=12$ and $\omega=1.0$]{
     \label{fig:N12hw1}
@@
   }
-        \subfigure[Results for $N=12$ and $\omega=0.5$ ]{
+  \subfigure[Results for $N=12$ and $\omega=0.5$]{
     \label{fig:N12hw05}
     \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
-        }\\ %  ------- End of the first row ----------------------%
-        \subfigure[Results for $N=12$ and $\omega=0.28$ ]{
+  } \\
+  \subfigure[Results for $N=12$ and $\omega=0.28$]{
     \label{fig:N12hw028}
@@
   }
-        \subfigure[Results for $N=12$ and $\omega=0.1$ ]{
+  \subfigure[Results for $N=12$ and $\omega=0.1$]{
     \label{fig:N12hw01}
@@
   }
-    \end{center}
-    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
-      for circular quantum dots for $N=12$ and different values of
-      $\omega$. The results are compared with diffusion Monte
-      Carlo (DMC), coupled cluster at the level of singles and doubles
-      (CCSD), full configuration interaction (FCI) and Hartree-Fock
-      calculations (HF) as functions of the number of major oscillator
-      shells $R$. A harmonic oscilaltor basis has been used, with an
-      unrenormalized Coulomb repulsion and the White generator. All
-      energies in atomic units.}
+  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=12$ and different values of $\omega$.
+The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
+A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
+All energies in atomic units.}
   \label{fig:N12}
@@
 
-\begin{figure}%[hbtp]
-     \begin{center}
-        \subfigure[Results for $N=20$ and $\omega=1.0$ ]{
+\begin{figure}
+  \centering
+  \subfigure[Results for $N=20$ and $\omega=1.0$]{
     \label{fig:N20hw1}
     \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
-        } \subfigure[Results for $N=20$ and $\omega=0.5$ ]{
+  } \subfigure[Results for $N=20$ and $\omega=0.5$]{
     \label{fig:N20hw05}
     \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
-        }\\ % ------- End of the first row ----------------------%
-        \subfigure[Results for $N=20$ and $\omega=0.28$ ]{
+  } \\
+  \subfigure[Results for $N=20$ and $\omega=0.28$]{
     \label{fig:N20hw028}
     \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
-        } \subfigure[Results for $N=20$ and $\omega=0.1$ ]{
+  } \subfigure[Results for $N=20$ and $\omega=0.1$]{
     \label{fig:N20hw01}
@@
   }
-    \end{center}
   \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
@@
 
-\begin{figure}%[hbtp]
-     \begin{center}
-        \subfigure[Results for $N=30$ and $\omega=1.0$ ]{
+\begin{figure}
+  \centering
+  \subfigure[Results for $N=30$ and $\omega=1.0$]{
     \label{fig:N30hw1}
     \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
-        } \subfigure[Results for $N=30$ and $\omega=0.5$ ]{
+  } \subfigure[Results for $N=30$ and $\omega=0.5$]{
     \label{fig:N30hw05}
     \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
-        }\\ % ------- End of the first row ----------------------%
-        \subfigure[Results for $N=30$ and $\omega=0.28$ ]{
+  } \\
+  \subfigure[Results for $N=30$ and $\omega=0.28$]{
     \label{fig:N30hw028}
     \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
-        } \subfigure[Results for $N=30$ and $\omega=0.1$ ]{
+  } \subfigure[Results for $N=30$ and $\omega=0.1$]{
     \label{fig:N30hw01}
@@
 
-\begin{figure}%[hbtp]
-     \begin{center}
-        \subfigure[Results for $N=42$ and $\omega=1.0$ ]{
+\begin{figure}
+  \centering
+  \subfigure[Results for $N=42$ and $\omega=1.0$]{
     \label{fig:N42hw1}
     \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
-        } \subfigure[Results for $N=42$ and $\omega=0.5$ ]{
+  } \subfigure[Results for $N=42$ and $\omega=0.5$]{
     \label{fig:N42hw05}
     \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
-        }\\ % ------- End of the first row ----------------------%
-        \subfigure[Results for $N=42$ and $\omega=0.28$ ]{
+  } \\
+  \subfigure[Results for $N=42$ and $\omega=0.28$]{
     \label{fig:N42hw028}
     \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
-        } \subfigure[Results for $N=42$ and $\omega=0.1$ ]{
+  } \subfigure[Results for $N=42$ and $\omega=0.1$]{
     \label{fig:N42hw01}
@@
   }
-    \end{center}
-    \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
-      for circular quantum dots for $N=42$ and different values of
-      $\omega$. The results are compared with diffusion Monte
-      Carlo (DMC), coupled cluster at the level of singles and doubles
-      (CCSD), full configuration interaction (FCI) and Hartree-Fock
-      calculations (HF) as functions of the number of major oscillator
-      shells $R$. A harmonic oscilaltor basis has been used, with an
-      unrenormalized Coulomb repulsion and the White generator. All
-      energies in atomic units.}
+  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=42$ and different values of $\omega$.
+The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
+A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
+All energies in atomic units.}
   \label{fig:N42}
@@
 \begin{table}
-\begin{center}
+  \centering
   \caption{Ground state energy (in atomic units) of a circular quantum dot, with $N$ particles and oscillator frequency $\omega$.
@@
     6  & 1.0  &  20.1583  &  20.1468 &  20.1593(1) \\
-      & 0.5&11.7690  & 11.7631 &11.7848(1) \\
-      & 0.28& 7.5713 &   7.5695 &7.6002(1) \\
-      & 0.1& 3.4962  &  3.4977 &3.5539(1)\\
+       & 0.5  &  11.7690  &  11.7631 &  11.7848(1) \\
+       & 0.28 &   7.5713  &   7.5695 &   7.6002(1) \\
+       & 0.1  &   3.4962  &   3.4977 &   3.5539(1) \\
     \midrule
-  12&1.0 & 65.7280 & 65.6990  & 65.7001(1) \\
-      &0.5 &39.1631 &  39.1473 & 39.1596(1)\\
-      &  0.28&25.6212 &  25.6140& 25.6358(1)\\
-      &  0.1&12.2223 &  12.2234 & 12.2698(1)\\
+    12 & 1.0  &  65.7280  &  65.6990 &  65.7001(1) \\
+       & 0.5  &  39.1631  &  39.1473 &  39.1596(1) \\
+       & 0.28 &  25.6212  &  25.6140 &  25.6358(1) \\
+       & 0.1  &  12.2223  &  12.2234 &  12.2698(1) \\
     \midrule
-  20& 1.0&155.9737 & 155.9130  & 155.8822(1)\\
-      &  0.5&93.9219 &   93.8853 &93.8752(1)\\
-      &  0.28&61.94362 & 61.9240 &61.9268(1) \\
-      &  0.1&29.95263 &29.9565  & 29.9779(1)\\
+    20 & 1.0  & 155.9737  & 155.9130 & 155.8822(1) \\
+       & 0.5  &  93.9219  &  93.8853 &  93.8752(1) \\
+       & 0.28 &  61.94362 &  61.9240 &  61.9268(1) \\
+       & 0.1  &  29.95263 &  29.9565 &  29.9779(1) \\
     \midrule
-  30& 1.0& 308.7673 & 308.6053 & 308.5627(2) \\
-      & 0.5& 187.1671& 186.8340 &187.0426(2)\\
-      & 0.28&124.0410 & 123.7171 & 123.9683(2) \\
-      & 0.1& 60.4319& 60.1158 & 60.4205(2)\\
+    30 & 1.0  & 308.7673  & 308.6053 & 308.5627(2) \\
+       & 0.5  & 187.1671  & 186.8340 & 187.0426(2) \\
+       & 0.28 & 124.0410  & 123.7171 & 123.9683(2) \\
+       & 0.1  &  60.4319  &  60.1158 &  60.4205(2) \\
     \midrule
-  42& 1.0&543.3398 & 543.3304 & 542.9428(8) \\
-      & 0.5&330.8885 & 330.8425 & 330.6306(2)\\
-      & 0.28&220.0226 & 219.9534y &219.8426(2) \\
-      & 0.1& 107.7851&  106.8074& 107.6389(2)\\
+    42 & 1.0  & 543.3398  & 543.3304 & 542.9428(8) \\
+       & 0.5  & 330.8885  & 330.8425 & 330.6306(2) \\
+       & 0.28 & 220.0226  & 219.9534 & 219.8426(2) \\
+       & 0.1  & 107.7851  & 106.8074 & 107.6389(2) \\
     \midrule
-  56& 1.0& 880.4159 &  & 879.3986(6) \\
-      & 0.5& 538.8199 & & 537.353(2)\\
-      & 0.28&360.83689  &  & 358.145(2) \\
+    56 & 1.0  & 880.4159  &          & 879.3986(6) \\
+       & 0.5  & 538.8199  &          & 537.353(2)  \\
+       & 0.28 & 360.83689 &          & 358.145(2)  \\
     \bottomrule
   \end{tabular}
-\end{center}
 \end{table}
@@
 
-\subsection{Extrapolation}
+The discrepeancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
+The former can be reduced by increasing the number of shells, and can be further alleviated by extrapolation techniques.
+
+Both IM-SRG and MP2 improve the accuracy the result dramatically over the more primitive HF.  (It may help to add plots *without* HF.)
+
+[[TODO: add FCI, CCSD results to GS energy plots]]
+
+\subsection{Comparison between methods}
+
+\subsubsection{Ground state energy}
 
@@
 There are a few cases where the IM-SRG over-corrects the result, leading to a ground state energy that is lower than the exact result.
-This is not unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational in the presence of operator truncations that cause small unitarity violations.
-Such behavior tends to occur when the number of particles is few, or the frequency is very low (high correlation).
+This is not unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
+Overcorrection tends to occur when the number of particles is few, or the frequency is very low (high correlation).
 However, MPPT does not do much better in the high frequency regimes as it often converges slower than IM-SRG.
+
+The operator truncations in the evaluation of the commutator is one of the two sources of discrepancy between IM-SRG and exact results.
+The other source is that of basis truncation, which limits the size of the Hilbert space that can be explored by the method.
+Unlike operator truncation, which is difficult to overcome as it increases the computational cost exponentially, increasing the basis comes a cost of about $O(n^2 N^4)$ for IM-SRG(2) with the White generator,\footnote{This result holds for any generator whose two-body part contains only pphh- and hhpp-type matrix elements.} [[cite Heiko?]] where $N$ is the total number of states in the single-particle basis and $n$ is the number of particles.
+In practice, the scaling cost is usually lower as the conserved symmetries allow the Hamiltonian to be partitioned into blocks.
+
+\subsubsection{Addition and removal energies}
 
@@
 
-\subsection{Slow convergence}
+\subsection{Rate of convergence}
 

### 2017-01-14 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 
-We model the quantum dot as a collection of $N$ electrons trapped in an
-external harmonic-oscillator potential.\footnote{In this paper, we use atomic
-  units where $\hbar$, $m$, $e$, and $4 \pi \epsilon$ are set to 1.  Here,
-  $\epsilon$ denotes the permittivity and $m$ denotes the mass, which could be
-  an effective mass rather than the true electron mass.  In effect, the unit
-  of energy in this article is
-  $E_{\text h} (m / m_{\text e}) / (\epsilon / \epsilon_0)^2$ where
-  $E_{\text h} \equiv m_{\text e} (\alpha c)^2$, the hartree unit of energy.}
-Each electron possesses kinetic energy $t(\bm p) \equiv \bm p^2 / 2$ and
-experiences an external potential $u(\bm r) \equiv \omega^2 \bm r^2 / 2$,
-where $\omega$ is the angular frequency of the oscillator, $\bm r$ is the
-2-dimensional position vector of an electron, and $\bm p$ is its linear
-momentum.  Each pair of electrons experience a Coulomb repulsion
-$v(\bm r, \bm r') \equiv |\bm r - \bm r'|^{-1}$ where $\bm r$ and $\bm r'$ are
-their positions.  The full many-body problem is described by the
-nonrelativistic Hamiltonian
-\begin{align*}
-  \hat H \equiv \hat H^{\text o} + \hat V = \sum_j \bigl(
-    t(\hat{\bm p}_j) + u(\hat{\bm r}_j)
-  \bigr) + \sum_{j_1 < j_2} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2})
-\end{align*}
-where $\hat{\bm p}_j$ and $\hat{\bm r}_j$ respectively denote the momentum and
-position operators of a particle $j$.  The first summation is performed over
-every particle, while the the second summation is performed over every
-unordered pair of distinct particles (the ordering of the particle labels $j$ is arbitrary).
-
-The full problem is not a trivial one.
-We shall first consider a much simpler problem: the noninteracting part of the Hamiltonian, $\hat H^{\text o}$, which does not contain the Coulomb interaction $v$:
-\begin{align} \label{eq:onebodyhamiltonian}
-  \hat H^{\text o} \equiv \sum_p \hat h^{\text o}_p
-  \equiv \sum_{p} \bigl(
-  t(\hat{\bm p}_p) + u(\hat{\bm r}_p)
-  \bigr)
-\end{align}
-In this case, the many-body Hamiltonian reduces to $N$ independent
-single-particle Hamiltonians, each of the form:
-\begin{align*}
-  \hat h^{\text o} \equiv
-  \frac{\hat{\bm p}^2 + \omega^2 \hat{\bm r}^2}{2}
-\end{align*}
-This is a 2-dimensional harmonic oscillator problem for a single particle,
-whose solutions are well known.  There are various ways to construct the set
-of eigenfunctions: we shall use the Fock-Darwin states that conserve angular
-momentum $\hat{L}_{\text{z}}$ about the $z$-axis (perpendicular to the 2D
-plane).  The eigenfunctions have the following analytic form in polar
-coordinates:\citep[Appx.\ A]{lohne2010coupled}
+We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in 2-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2 r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
+The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
+
+Even though the model system contains 5 parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
+With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
+For rest of this paper, we shall use atomic units\footnote{Here, ``atomic unit'' is used in an \emph{abstract} sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$ correspond to true values in vacuum, or some effective value in medium.} where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ all have a value of one.
+This implies that the units of energy are hartrees $E_{\mathrm{h}}$ and the units of length are Bohr radii $a$:
+\begin{align*}
+  E_{\mathrm{h}} &\equiv m \left(\frac{e^2}{4 \pi \epsilon \hbar}\right)^2 &
+  a &\equiv \frac{4 \pi \epsilon \hbar^2}{m e^2}
+\end{align*}
+This leaves us with $(N, \omega)$ as the only necessary parameters to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
+
+The behavior of each electron in isolation is described by its kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
+\begin{align*}
+  t(\bm{p}) &\equiv \frac{1}{2} \bm{p}^2 &
+  u(\bm{r}) &\equiv \frac{1}{2} \omega^2 \bm{r}^2 &
+  h(\bm{p}, \bm{r}) &\equiv t(\bm{p}) + t(\bm{r})
+\end{align*}
+Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is its position relative to the center of the trap.
+The pairwise interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$ is simply the Coulomb interaction:
+\begin{align*}
+  v(\bm{r}, \bm{r}') \equiv \frac{1}{\left|\bm{r} - \bm{r}'\right|}
+\end{align*}
+Then, the full many-body problem is described by the Hamiltonian
+\begin{align*}
+  \hat H \equiv \hat H^{[1]} + \hat H^{[2]}
+\end{align*}
+where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are the one- and two-body parts of the Hamiltonian,
+\begin{align} \label{eq:onetwobodyhamiltonian}
+\hat{H}^{[1]} &\equiv \sum_{j = 1}^N h(\hat{\bm p}_j, \hat{\bm r}_j) &
+\hat{H}^{[2]} &\equiv \sum_{j_1 = 1}^N \sum_{j_2 = 1}^{j_1 - 1} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2})
+\end{align}
+The operators $\hat{\bm p}_j$ and $\hat{\bm r}_j$ respectively denote momentum and position of the $j$-th particle.\footnote{The order in which particles are labeled is unimportant; it is used only for bookkeeping.}
+
+The first step towards a solution is to solve \emph{just} the noninteracting part $\hat{H}^{[1]}$.
+In this case, the many-body Hamiltonian reduces to $N$ independent single-particle Hamiltonians $\hat{h}$, each of the form:
+\begin{align*}
+  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2
+\end{align*}
+This is a 2-dimensional harmonic oscillator problem for a single particle with known analytic solutions.
+There are various ways to construct the set of eigenfunctions: we shall use the Fock-Darwin states, which conserve the angular momentum $\hat{L}_{\mathrm{z}}$.
+In polar coordinates, they are given by\citep[Appx.\ A]{lohne2010coupled}
 \begin{gather*}
@@
 \end{figure}
-The eigenvalues of the single-particle Hamiltonian $\hat h^{\text o}$ are
+The eigenvalues of the single-particle Hamiltonian $\hat{h}$ are
 given by
@@
 which satisfies
-$\hat{h}^{\text o} \ket{\phi_{n, m_\ell, m_{\text s}}} = \varepsilon_{n,
+$\hat{h} \ket{\phi_{n, m_\ell, m_{\text s}}} = \varepsilon_{n,
   m_\ell, m_{\text s}} \ket{\phi_{n, m_\ell, m_{\text s}}}$.  Note that the
 states are degenerate with respect to the spin projection $m_{\text s}$ since
-our Hamiltonian $\hat h^{\text o}$ does not distinguish between them.  From
+our Hamiltonian $\hat{h}$ does not distinguish between them.  From
 this equation, we can deduce the shell structure as shown in Figure
@@
 
-The many-body Hamiltonian $\hat H^{\text o}$ is the sum of the single-particle
-Hamiltonians $\hat h^{\text o}_p$ over all particles $p$, where $p$ may now be
+The many-body Hamiltonian $\hat{H}^{[1]}$ is the sum of the single-particle
+Hamiltonians $\hat{h}_p$ over all particles $p$, where $p$ may now be
 treated as a tuple of all three single-particle quantum numbers:
@@
 \eqref{eq:singleparticlestate} we can construct the an eigenstate of the
-many-body Hamiltonian $\hat H^{\text o}$ in the form of a Slater determinant
+many-body Hamiltonian $\hat{H}^{[1]}$ in the form of a Slater determinant
 $\varnothing_{p_1, \ldots, p_N}$:
@@
 \begin{align*}
-  E^{\text o}_{p_1, \ldots, p_N} =
-  \varepsilon_{p_1} + \cdots + \varepsilon_{p_N},
-\end{align*}
-which satisfies
-$\hat{H}^{\text o} \ket{\varnothing_{p_1, \ldots, p_N}} = E^{\text o}_{p_1, \ldots,
-  p_N} \ket{\varnothing_{p_1, \ldots, p_N}}$.  For ground states, we may have
-degeneracies due to the shell structure of the single-particle basis.
-However, if $N = k_{\text F} (k_{\text F} + 1)$ for some nonnegative integer
-$k_{\text F}$, there are just enough particles to form a closed-shell system.
-In this case, there is a unique, well-isolated ground state.  The values of
-$N$ for which this occurs are typically referred to as \textit{magic numbers}
-and we call $k_{\text F}$ the \textit{number of filled shells} (or ``Fermi
-level'').  This completes the solution of the noninteracting problem.
+  E^{[1]}_{p_1, \ldots, p_N} = \varepsilon_{p_1} + \cdots + \varepsilon_{p_N},
+\end{align*}
+which satisfies $\hat{H}^{[1]} \ket{\varnothing_{p_1, \ldots, p_N}} = E^{[1]}_{p_1, \ldots, p_N} \ket{\varnothing_{p_1, \ldots, p_N}}$.
+For ground states, we may have degeneracies due to the shell structure of the single-particle basis.
+However, if $N = k_{\text F} (k_{\text F} + 1)$ for some nonnegative integer $k_{\text F}$, there are just enough particles to form a closed-shell system.
+In this case, there is a unique, well-isolated ground state.
+The values of $N$ for which this occurs are typically referred to as \textit{magic numbers} and we call $k_{\text F}$ the \textit{number of filled shells} (or ``Fermi level'').
+This completes the solution of the noninteracting problem.
 
@@
 Operators can be rewritten in this formalism as well.  The one-body
-Hamiltonian $H^{\text o}$ defined by \eqref{eq:onebodyhamiltonian} can be
+Hamiltonian $H^{[1]}$ defined by \eqref{eq:onetwobodyhamiltonian} can be
 rewritten in second quantization as
 \begin{align} \label{eq:second_quantized_one_body_hamiltonian}
-  \hat H^{\text o} = \sum_{p, q} H_{p, q}^{\text o} \hat a_p^\dagger \hat a_q^{}
+  \hat H^{[1]} = \sum_{p, q} H_{p, q}^{[1]} \hat a_p^\dagger \hat a_q^{}
 \end{align}
 where the \textit{matrix element}
-$H_{p, q}^{\text o} \equiv \bra{\varnothing_p} \hat H^{\text o} \ket{\varnothing_q}$.  This
-can likewise be extended to $\hat V$,
+$H_{p, q}^{[1]} \equiv \bra{\varnothing_p} \hat{H}^{[1]} \ket{\varnothing_q}$.  This
+can likewise be extended to $\hat{H}^{[2]}$,
 \begin{align} \label{eq:second_quantized_two_body_hamiltonian}
-  \hat V = \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
+  \hat{H}^{[2]} = \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
   \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
@@
 where $U_{p, q} \equiv \langle \varnothing_p | \hat U | \varnothing_q \rangle$ and
-$V_{p, q, r, s} \equiv \langle \varnothing_{p, q} | \hat V | \varnothing_{r, s} \rangle$.
+$V_{p, q, r, s} \equiv \langle \varnothing_{p, q} | \hat{H}^{[2]} | \varnothing_{r, s} \rangle$.
 The complete Hamiltonian is given by their sum:
 \begin{align}
-  \hat{H} = \sum_{p, q} H^{\text o}_{p, q} \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
+  \hat{H} = \sum_{p, q} H^{[1]}_{p, q} \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
 \end{align}
@@
 \begin{align}
-  E_{\Phi} &= \sum_{j} n_j H^{\text{o} \prime}_{j, j} + \sum_{j, k} n_j n_k V'_{j, k, j, k} \label{eq:hfenergy}
+  E_{\Phi} &= \sum_{j} n_j H^{[1] \prime}_{j, j} + \sum_{j, k} n_j n_k V'_{j, k, j, k} \label{eq:hfenergy}
 \end{align}
@@
 \begin{align}
-  H^{\text{o} \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* H_{r, s}^{\text o} C_{s, q}^{} \label{eq:hftransform1} \\
+  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* H_{r, s}^{[1]} C_{s, q}^{} \label{eq:hftransform1} \\
   V'_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* V_{t, u, v, w}^{} C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv H_{p, q}^{\text o} + \sum_{r, s, j} n_j C_{r, j}^* V_{p, r, q, s}^{} C_{s, j}^{}
+  F_{p, q} \equiv H_{p, q}^{[1]} + \sum_{r, s, j} n_j C_{r, j}^* V_{p, r, q, s}^{} C_{s, j}^{}
 \end{align}
@@
 To make use of the HF solution as the reference state for future calculations, we transform the operators via \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
-Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat H^{\text{o} \prime}$ and $\hat V'$ as inputs.
+Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
 However, for generality, we omit the prime symbols as the methods do not necessitate a state optimized by HF.
@@
 The normal ordering notation thus provides a concise way of expressing the right-hand side.
-In this new notation, we can rewrite the Hamiltonian $\hat H = \hat H^{\text o} + \hat V$ in its \emph{normal-ordered representation}:
+In this new notation, we can rewrite the Hamiltonian $\hat H = \hat{H}^{[1]} + \hat{H}^{[2]}$ in its \emph{normal-ordered representation}:
 \begin{align}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_{i} n_i H^{\text o}_{i, i} + \frac{1}{2} \sum_{i, j} n_i n_j V_{i, j, i, j} \\
-  H^{[1]}_{p, q} &\equiv H^{\text o}_{p, q} + \sum_{i} n_i V_{p, i, q, i} \\
+  H^{[0]} &\equiv \sum_{i} n_i H^{[1]}_{i, i} + \frac{1}{2} \sum_{i, j} n_i n_j V_{i, j, i, j} \\
+  H^{[1]}_{p, q} &\equiv H^{[1]}_{p, q} + \sum_{i} n_i V_{p, i, q, i} \\
   H^{[2]}_{p, q, r, s} &\equiv V_{p, q, r, s} \\
@@
 
-In QDPT, the solutions of the approximate Hamiltonian $\hat H^{\text o}$ are used as the basis of the model space.
-One then assumes the existence of an operator $\hat \Omega$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\text o}_u$ within the model space to the exact ground state $\Psi_u$:
+In QDPT, the solutions of the approximate Hamiltonian $\hat{H}^{[1]}$ are used as the basis of the model space.
+One then assumes the existence of an operator $\hat \Omega$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
 \begin{align} \label{eq:omega-condition1}
-  \Psi_u = \hat \Omega \tilde \Psi^{\text o}_u
-\end{align}
-The states $\tilde \Psi^{\text o}_u$ consist of some mixture of the eigenstates
-$\Psi^{\text o}_{u'}$ of the approximate Hamiltonian $\hat H^{\text o}$.
+  \Psi_u = \hat \Omega \tilde \Psi^{\mathrm{o}}_u
+\end{align}
+The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates
+$\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
 
@@
 longer normalized but instead satisfies the typical intermediate
-normalization: $\langle \Psi_u | \tilde \Psi^{\text o}_u \rangle = 1$.
+normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
 
@@
 \begin{gather*}
-  [\hat \Omega, \hat H^{\text o}] =
+  [\hat \Omega, \hat{H}^{[1]}] =
   (1 - \hat \Omega) \hat V \Omega
 \end{gather*}
-where $\hat V \equiv \hat H - \hat H^{\text o}$ is the perturbation.  The
+where $\hat V \equiv \hat H - \hat{H}^{[1]}$ is the perturbation.  The
 commutator on the left may be ``inverted'' using the resolvent approach
@@
 \end{align*}
-where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat H^{\text o} \hat Q)^{-1} \hat Q$ is the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\text o}_u$.
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ is the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
 As is typical in perturbation theory, we assume $\hat \Omega$ can be expanded as a series of the increasing order as measured by the ``power'' of the perturbation $\hat V$:
@@
 First, we make use of the single-particle basis as we have for HF and IM-SRG.
-Secondly, we assume the set of reference states $\Psi^{\text o}_u$ are Slater determinants of the single-particle states.
+Secondly, we assume the set of reference states $\Psi^{\mathrm{o}}_u$ are Slater determinants of the single-particle states.
 

### 2017-01-14 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 For rest of this paper, we shall use atomic units\footnote{Here, ``atomic unit'' is used in an \emph{abstract} sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$ correspond to true values in vacuum, or some effective value in medium.} where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ all have a value of one.
-This implies that the units of energy are hartrees $E_{\mathrm{h}}$ and the units of length are Bohr radii $a$:
+Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
 \begin{align*}
@@
 \end{align*}
-This leaves us with $(N, \omega)$ as the only necessary parameters to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
-
-The behavior of each electron in isolation is described by its kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
+This leaves us with $(N, \omega)$ as the only parameters necessary to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
+
+The behavior of each electron in isolation is described by the kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
 \begin{align*}
@@
 \end{align}
-The operators $\hat{\bm p}_j$ and $\hat{\bm r}_j$ respectively denote momentum and position of the $j$-th particle.\footnote{The order in which particles are labeled is unimportant; it is used only for bookkeeping.}
-
-The first step towards a solution is to solve \emph{just} the noninteracting part $\hat{H}^{[1]}$.
-In this case, the many-body Hamiltonian reduces to $N$ independent single-particle Hamiltonians $\hat{h}$, each of the form:
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The choice and ordering of the particle labels $j$ is unimportant; they only exist for the purposes of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
+
+The first step towards a solution is to solve \emph{just} the noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$, which reduces to $N$ independent single-particle Hamiltonians $\hat{h}$ each of the form:
 \begin{align*}
@@
 \end{align*}
-This is a 2-dimensional harmonic oscillator problem for a single particle with known analytic solutions.
-There are various ways to construct the set of eigenfunctions: we shall use the Fock-Darwin states, which conserve the angular momentum $\hat{L}_{\mathrm{z}}$.
-In polar coordinates, they are given by\citep[Appx.\ A]{lohne2010coupled}
-\begin{gather*}
-  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi)
-  \equiv \sqrt\omega
-  \phi^{\text{FDr}}_{n, |m_\ell|}(\sqrt \omega \rho)
-  \phi^{\text{Lz}}_{m_\ell}(\varphi)
-\end{gather*}
-where $\rho$ denotes the radial coordinate, $\varphi$ denotes the angular coordinate,
-\begin{align*}
-  \phi^{\text{FDr}}_{n, m}(r) &\equiv
-  \sqrt{\frac{2 \cdot n!}{(n + m)!}}
-  {\mathrm e}^{-r^2 / 2} r^m L_n^{(m)}(r^2) \\
-  \phi^{\text{Lz}}_{m_\ell}(\varphi) &\equiv
-  \frac{1}{\sqrt{2 \pi}} {\mathrm e}^{i m_\ell \varphi}
-\end{align*}
-and $L_n^{(\mu)}$ denotes the generalized Laguerre polynomial of degree $n$
-with parameter $\mu$.  The states are labeled by two quantum numbers: the
-principal quantum number $n \in \{0, 1, \ldots\}$ and the angular momentum
-projection $m_\ell \in \mathbb Z$.
-
-Additionally, since electrons are spin-$1/2$ fermions, they can occupy either
-of the two spin states $\chi_{-\frac12}$ or $\chi_{+\frac12}$.  Thus, the
-single-particle basis states can be constructed as
+This is a 2-dimensional harmonic oscillator problem for a single particle, of which analytic solutions are known.
+There are various equivalent ways to construct the solutions.
+For our purposes, we shall use the Fock-Darwin states, which can be conveniently described polar coordinates $(\rho, \varphi)$ and have the elegant property of conserving the orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
+The wave functions can be factorized into radial and angular components,\citep[Appx.\ A]{lohne2010coupled}
+\begin{align}
+  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega \phi^{\text{FDr}}_{n, |m_\ell|}(\sqrt \omega \rho) \phi^{\text{Lz}}_{m_\ell}(\varphi) \label{eq:fockdarwin} \\
+  \phi^{\text{FDr}}_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2) \notag \\
+  \phi^{\text{Lz}}_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi} \notag
+\end{align}
+and $L_n^{(m)}$ denotes the generalized Laguerre polynomial of degree $n$
+with parameter $\mu$,
+\begin{align*}
+  L_n^{(m)}(u) = \frac{1}{n!} u^{-m} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{m + n})
+\end{align*}
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, \ldots\}$ and the orbital angular momentum projection $m_\ell \in \mathbb Z$.
+
+Additionally, since electrons are spin-$1/2$ fermions, they can occupy either of the two spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
+For an electron in isolation, the choice is immaterial, but in a multi-electron system, this becomes crucial.
+Thus for a many-body problem a single-particle basis state must contain both the spatial component \eqref{eq:fockdarwin} and the spin component,
 \begin{align} \label{eq:singleparticlestate}
@@
 \end{align}
-with the spin projection $m_{\text s} \in \bigl\{-\frac12, +\frac12\bigr\}$.
+where we have introduced a third quantum number: the spin projection $m_{\text s} \in \bigl\{-1/2, +1/2\bigr\}$.
 

### 2017-01-15 Manuscript/paper.tex
Update paper

@@
 \begin{align*}
-  v(\bm{r}, \bm{r}') \equiv \frac{1}{\left|\bm{r} - \bm{r}'\right|}
+  v(\bm{r}, \bm{r}') \equiv \frac{1}{|\bm{r} - \bm{r}'|}
 \end{align*}
@@
 \end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The choice and ordering of the particle labels $j$ is unimportant; they only exist for the purposes of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
-
-The first step towards a solution is to solve \emph{just} the noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$, which reduces to $N$ independent single-particle Hamiltonians $\hat{h}$ each of the form:
-\begin{align*}
-  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2
-\end{align*}
-This is a 2-dimensional harmonic oscillator problem for a single particle, of which analytic solutions are known.
-There are various equivalent ways to construct the solutions.
-For our purposes, we shall use the Fock-Darwin states, which can be conveniently described polar coordinates $(\rho, \varphi)$ and have the elegant property of conserving the orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
-The wave functions can be factorized into radial and angular components,\citep[Appx.\ A]{lohne2010coupled}
-\begin{align}
-  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega \phi^{\text{FDr}}_{n, |m_\ell|}(\sqrt \omega \rho) \phi^{\text{Lz}}_{m_\ell}(\varphi) \label{eq:fockdarwin} \\
-  \phi^{\text{FDr}}_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2) \notag \\
-  \phi^{\text{Lz}}_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi} \notag
-\end{align}
-and $L_n^{(m)}$ denotes the generalized Laguerre polynomial of degree $n$
-with parameter $\mu$,
-\begin{align*}
-  L_n^{(m)}(u) = \frac{1}{n!} u^{-m} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{m + n})
-\end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, \ldots\}$ and the orbital angular momentum projection $m_\ell \in \mathbb Z$.
-
-Additionally, since electrons are spin-$1/2$ fermions, they can occupy either of the two spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
-For an electron in isolation, the choice is immaterial, but in a multi-electron system, this becomes crucial.
-Thus for a many-body problem a single-particle basis state must contain both the spatial component \eqref{eq:fockdarwin} and the spin component,
-\begin{align} \label{eq:singleparticlestate}
-  \phi_{n, m_\ell, m_{\text s}}(\rho, \varphi) \equiv
-  \phi^{\text{FD}}_{n, m_\ell}(\rho, \varphi) \chi_{m_{\text s}}
-\end{align}
-where we have introduced a third quantum number: the spin projection $m_{\text s} \in \bigl\{-1/2, +1/2\bigr\}$.
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
 
 \begin{figure}
-\includegraphics[width=.48\textwidth]{fig-shell-structure}
-\caption{Structure of the lowest 12 single-particle states in a noninteracting
-  harmonic oscillator of frequency $\omega = 1$.  Each box represents a
-  single-particle state, and the arrows denote the spin of the states.}
+  % [width=.48\textwidth]
+  \includegraphics[width=\textwidth]{figures/fig-shell-structure-v2}
+  \caption{Visualization of the 20 lowest single-particle states in the 2D harmonic oscillator basis.
+Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
+The $n$ quantum number increases upward vertically, starting at zero for the lowest state within a each column.}
   \label{fig:shell-structure}
 \end{figure}
-The eigenvalues of the single-particle Hamiltonian $\hat{h}$ are
-given by
-\begin{align*}
-  \varepsilon_{n, m_\ell, m_{\text s}} \equiv (2 n + |m_\ell| + 1) \omega
-\end{align*}
-which satisfies
-$\hat{h} \ket{\phi_{n, m_\ell, m_{\text s}}} = \varepsilon_{n,
-  m_\ell, m_{\text s}} \ket{\phi_{n, m_\ell, m_{\text s}}}$.  Note that the
-states are degenerate with respect to the spin projection $m_{\text s}$ since
-our Hamiltonian $\hat{h}$ does not distinguish between them.  From
-this equation, we can deduce the shell structure as shown in Figure
-\ref{fig:shell-structure}.  It is notable that there are degeneracies beyond
-that of the spin pairs: each shell contains a set of states that satisfy the
-equation $2 n + |m_\ell| = k$ for some nonnegative integer $k$, which we
-conveniently call the \textit{shell index}.  The shells are equidistant from
-each other, with a spacing equal to the frequency $\omega$.
-
-The many-body Hamiltonian $\hat{H}^{[1]}$ is the sum of the single-particle
-Hamiltonians $\hat{h}_p$ over all particles $p$, where $p$ may now be
-treated as a tuple of all three single-particle quantum numbers:
-$(n, m_\ell, m_{\text s})$.  From the states $\phi$ in
-\eqref{eq:singleparticlestate} we can construct the an eigenstate of the
-many-body Hamiltonian $\hat{H}^{[1]}$ in the form of a Slater determinant
-$\varnothing_{p_1, \ldots, p_N}$:
-\begin{align*}
-  \varnothing_{p_1, \ldots, p_N}(\bm r_1, \ldots, \bm r_N) \equiv
+
+The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
+\begin{align*}
+  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2
+\end{align*}
+Therefore, solving the noninteracting many-body problem amounts to solving the single-particle Schr\"odinger equation
+\begin{align*}
+  \hat{h} |p\rangle = \varepsilon_p |p\rangle
+\end{align*}
+where $p$ is an unknown tuple of quantum numbers.
+The two-dimensional harmonic oscillator Hamiltonian $\hat{h}$ has well known analytic solutions in Cartesian coordinates, but for our purposes, we prefer to use the Fock-Darwin states, which favor a representation in polar coordinates $\bm{r} = (\rho, \varphi)$ and have the useful property of conserving the orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
+
+The Fock-Darwin wave functions can be decomposed into radial and angular components,\cite[Appx.\ A]{lohne2010coupled}
+\begin{align}
+  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n, |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin} \\
+  R_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2) \notag \\
+  A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi} \notag
+\end{align}
+where $L_n^{(m)}$ denotes the generalized Laguerre polynomial of degree $n$ and parameter $m$,
+\begin{align*}
+  L_n^{(m)}(u) = \frac{1}{n!} u^{-m} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{m + n})
+\end{align*}
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, \ldots\}$ and the orbital angular momentum projection $m_\ell \in \mathbb Z$, which is the eigenvalue of $\hat{L}_{\mathrm{z}}$.
+
+Since electrons are spin-$1/2$ fermions, they can occupy either of the two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
+The complete single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+\begin{align} \label{eq:singleparticlestate}
+  \langle (\rho, \varphi) | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \chi_{m_{\mathrm{s}}}
+\end{align}
+where we have introduced the the spin projection $m_{\mathrm{s}} \in \bigl\{-1/2, +1/2\bigr\}$ as the third quantum number.
+
+The energy of the single-particle state $\phi_{n, m_\ell, m_{\mathrm{s}}}$ is given by
+\begin{align*}
+  \varepsilon_{n, m_\ell, m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega
+\end{align*}
+The energies are degenerate with respect to the spin projection $m_{\mathrm{s}}$ as our Hamiltonian $\hat{h}$ does not distinguish between them.
+Additionally, they are degenerate with respect to the nonnegative integer
+\begin{align} \label{eq:shell_index}
+  k \equiv 2 n + |m_\ell|
+\end{align}
+which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
+
+Going back to the many-body Hamiltonian $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation of the triplet $(n, m_\ell, m_{\mathrm{s}})$.
+It is important to emphasize that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
+\begin{align*}
+  \langle \bm{r}_1, \ldots, \bm{r}_N | p_1, \ldots, p_N \rangle \equiv
   \frac{1}{\sqrt{N}} \left|
   \begin{matrix}
-    \phi_{p_1}(\bm r_1) & \cdots & \phi_{p_N}(\bm r_1) \\
+    \langle \bm{r}_1 | p_1 \rangle & \cdots & \langle \bm{r}_1 | p_N \rangle \\
     \vdots & \ddots & \vdots \\
-    \phi_{p_1}(\bm r_N) & \cdots & \phi_{p_N}(\bm r_N) \\
+    \langle \bm{r}_N | p_1 \rangle & \cdots & \langle \bm{r}_N | p_N \rangle \\
   \end{matrix}
@@
 \end{align*}
-This automatically satisfies the Pauli exclusion principle, ensuring that the
-Fermi statistics are satisfied.  The energy of these states is given by the
-sum of the single-particle energies:
-\begin{align*}
-  E^{[1]}_{p_1, \ldots, p_N} = \varepsilon_{p_1} + \cdots + \varepsilon_{p_N},
-\end{align*}
-which satisfies $\hat{H}^{[1]} \ket{\varnothing_{p_1, \ldots, p_N}} = E^{[1]}_{p_1, \ldots, p_N} \ket{\varnothing_{p_1, \ldots, p_N}}$.
-For ground states, we may have degeneracies due to the shell structure of the single-particle basis.
-However, if $N = k_{\text F} (k_{\text F} + 1)$ for some nonnegative integer $k_{\text F}$, there are just enough particles to form a closed-shell system.
-In this case, there is a unique, well-isolated ground state.
-The values of $N$ for which this occurs are typically referred to as \textit{magic numbers} and we call $k_{\text F}$ the \textit{number of filled shells} (or ``Fermi level'').
-This completes the solution of the noninteracting problem.
-
-The difficulty in solving the full Hamiltonian $\hat H$ stems from the fact
-that the exact solution cannot be expressed in terms of a single Slater
-determinant due to the presence of interactions.  Hence, it is not possible to
-trivially reduce the problem to that of a single particle as we had done
-previously.
-
-However, if we assume that the interaction alters the behavior of the system
-only mildly, we can use the Slater determinants of the noninteracting system
-as an initial guess for the solution, and then apply iterative methods to
-improve the accuracy of the solution.
-
-Since Slater determinants are rather cumbersome to write out in full, we shall
-instead work in the more convenient formalism of \textit{second quantization}:
-\begin{align*}
-  \ket{\varnothing_{p_1, \ldots, p_N}} =
-  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger \ket{\varnothing}
-\end{align*}
-Here, $\varnothing$ is the vacuum state that is devoid of particles and
-$\hat a_p^\dagger$ is a \textit{creation operator} for the single-particle
-state $p$.  If the state $p$ is not yet occupied by a particle,
-$\hat a_p^\dagger$ creates such a particle.  Otherwise, it collapses the
-entire many-body state to $0$.  The Hermitian conjugate of $\hat a_p^\dagger$
-is $\hat a_p$, which is an \textit{annihilation operator} for the state $p$
-that has the opposite effect.  For fermions, the field operators $\hat a_p$
-and $\hat a_p^\dagger$ satisfy the essential anticommutation relations,
+The Slater determinant $|p_1, \ldots, p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
+By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
+
+The energy of a Slater determinant is given by a sum over the occupied single-particle energies,
+\begin{align*}
+  \hat{H}^{[1]} | p_1, \ldots, p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1, \ldots, p_N \rangle
+\end{align*}
+It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
+This is possible even for ground states of $\hat{H}^{[1]}$.
+However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
+The values of $N$ at which this occurs are said to be \textit{magic numbers}.
+We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
+In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
+
+Currently, the Hamiltonian $\hat{H}$ is explicit in the number of particles $N$.
+The many-body machinery can be made agnostic to number of particles through the formalism of second quantization, similar to quantum field theory.
+The many-body Hilbert space is extended from states with only $N$ particles to states with every possible number of particles via the Fock space construction.
+Slater determinants can then rewritten as,
+\begin{align*}
+  |p_1, \ldots, p_N\rangle =
+  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger |\rangle
+\end{align*}
+whre $|\rangle$ is the \textit{vacuum state} -- the unique state that is devoid of particles -- and $\hat{a_p}^\dagger$ denotes a \textit{creation operator} for the single-particle state $p$.
+If the single-particle state $p$ is not yet occupied by a particle, $\hat a_p^\dagger$ adds such a particle to the state.
+Otherwise, it collapses the entire many-body state to the number $0$ (not to be confused with the vacuum state $|\rangle$).
+The Hermitian conjugate of $\hat a_p^\dagger$ is \textit{annihilation operator} $\hat a_p$, which has the opposite effect of removing the particle if it exists, collapsing to zero otherwise.
+For fermions, the field operators $\hat a_p$ and $\hat a_p^\dagger$ satisfy the essential anticommutation relations,
 \begin{align*}
@@
 
-Operators can be rewritten in this formalism as well.  The one-body
-Hamiltonian $H^{[1]}$ defined by \eqref{eq:onetwobodyhamiltonian} can be
-rewritten in second quantization as
-\begin{align} \label{eq:second_quantized_one_body_hamiltonian}
-  \hat H^{[1]} = \sum_{p, q} H_{p, q}^{[1]} \hat a_p^\dagger \hat a_q^{}
-\end{align}
-where the \textit{matrix element}
-$H_{p, q}^{[1]} \equiv \bra{\varnothing_p} \hat{H}^{[1]} \ket{\varnothing_q}$.  This
-can likewise be extended to $\hat{H}^{[2]}$,
-\begin{align} \label{eq:second_quantized_two_body_hamiltonian}
-  \hat{H}^{[2]} = \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s}^{}
-  \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
-\end{align}
-where $U_{p, q} \equiv \langle \varnothing_p | \hat U | \varnothing_q \rangle$ and
-$V_{p, q, r, s} \equiv \langle \varnothing_{p, q} | \hat{H}^{[2]} | \varnothing_{r, s} \rangle$.
-The complete Hamiltonian is given by their sum:
-\begin{align}
-  \hat{H} = \sum_{p, q} H^{[1]}_{p, q} \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} V_{p, q, r, s} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
-\end{align}
-Note that due to the antisymmetry present in the Slater determinants, we have
-the property that exchanging either $p$ with $q$ or $r$ with $s$ causes
-$V_{p, q, r, s}$ to reverse in sign, leading to a $4$-fold symmetry that is
-canceled out by the factor of $1/4$.  For this reason, the two-body matrix
-element $V_{p, q, r, s}$ is commonly referred to as the \emph{antisymmetrized}
-matrix element.  This is not to be confused with the non-antisymmetric
-interaction integral defined by:
-\begin{align*}
-  \tilde V_{p, q, r, s} \equiv \int \phi_p(\bm r) \phi_q(\bm r') v(\bm r, \bm r') \phi_r(\bm r) \phi_s(\bm r') \D \bm r \D \bm r'
-\end{align*}
-The antisymmetrized matrix element is computed from the interaction integral
-by $V_{p, q, r, s} = \tilde V_{p, q, r, s} - \tilde V_{p, q, s, r}$.  In our
-work, we compute the interaction numerically via the OpenFCI software, which
-numerical integrates the Coulomb interaction in the center-of-mass frame
-[[cite Kvaal's paper; also, is the description correct?]].
-
-There are significant advantages in the second quantization formalism in
-many-body theory: the operators are written in a way that does not generic
-with respect to the number of particles, and the anticommutative behavior of
-field operators ensures the Pauli exclusion principle holds no matter how the
-operator is manipulated.  Furthermore, it allows the application of a useful
-combinatoric theorem known as Wick's theorem [[cite something]] to simplify
-complicated operator expressions.  Ultimately, the computations themselves do
-not involve operators at all -- rather, they involve the calculation of
-\emph{matrix elements} via equations derived with the aid of Wick's theorem.
+In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from \eqref{eq:onetwobodyhamiltonian} can be rewritten as\footnote{The reversed ordering of $\hat a_s \hat a_r$ here is completely intentional.}
+\begin{align} \label{eq:second_quantized_hamiltonian}
+  \hat H^{[1]} &= \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{} &
+  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
+\end{align}
+where the numbers $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ are known as \textit{matrix elements}, whose values fully characterize the operators.
+In this paper, we use the letters $p, q, r, s, t, \ldots$ as labels for arbitrary single-particle basis states.
+In the harmonic oscillator basis, the letters can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
+A summation such as $\sum_p$ is to be understood as a summation over every single-particle basis state $p$.
+This is very different from \eqref{eq:onetwobodyhamiltonian}, where summations such as $\sum_j$ are performed over arbitrary particle \emph{labels}.
+We thus see another benefit with second quantization: the Hamiltonian representation does not distinguish particles at all, as it should be for quantum particles.
+
+The complete Hamiltonian is given by the sum
+\begin{align}
+  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
+\end{align}
+Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ causes $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ to reverse in sign, leading to a 4-fold symmetry that is canceled out by the factor of $1/4$.
+For this reason, the two-body matrix element $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
+This is not to be confused with the non-antisymmetric interaction integral,
+\begin{align*}
+  v_{p_1, p_2, p_3, p_4} \equiv \int \langle \bm{r} | p_1 \rangle \langle \bm{r}' | p_2 \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'
+\end{align*}
+This object only has a 2-fold symmetry: $v_{p_1, p_2, p_3, p_4} = v_{p_2, p_1, p_4, p_3}$.  The antisymmetrized matrix element can be computed from the interaction integral via
+\begin{align*}
+  \langle p, q | \hat{H}^{[2]} | r, s \rangle = v_{p, q, r, s} - v_{p, q, s, r}
+\end{align*}
+
+In our work, the interaction integrals $v_{p, q, r, s}$ were computed numerically using the algorithm presented in \cite{2008arXiv0810.2644K}, included as part of the OpenFCI program.
+The algorithm uses numerical quadrature to calculate the integrals exactly in the center-of-mass frame and then performs a transformation to obtain matrix elements in the laboratory frame.
+The numerical quadrature technique is much more numerically robust and efficient than using analytical formulas such as the one in \cite{0953-8984-10-3-013}.
+
+The use of second quantization allows the application of a powerful combinatoric theorem known as Wick's theorem \cite{shavitt2009many}, which provides systematic way to expand complicated expressions involving creation and annihilation operators.
+Ultimately, computations \textit{in silico} do not involve algebraic manipulation of abstract operators at all -- rather, they involve numerical calculations of \emph{matrix elements} via equations derived using Wick's theorem.
+
+With the basic formalism and notation established, we begin discussion of techniques to solve the full many-body Hamiltonian $\hat H$.
+The difficulty stems from the fact that the exact solution cannot be expressed in terms of a single Slater determinant due to the presence of interactions.
+Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
+
+However, if we assume the interaction alters the behavior of the system to only a mild extent, we can use Slater determinants of the noninteracting system as starting points for the full solution, and then apply various many-body methods to improve the accuracy of the solution.
 
@@
 
-The first correction that we will apply to our solution is that of the
-Hartree-Fock (HF) method.  Using the variational principle, we compute an
-approximate ground state $\Phi$ by minimizing the energy expectation value
+One relatively simple correction that we can apply to our solution is that of the Hartree-Fock (HF) method.
+Using the variational principle, we compute an approximate ground state $\Phi$ by minimizing the energy expectation value
 \begin{align*}
@@
 \end{align*}
-with respect to $\Phi$, subject to the restriction that
-$\Phi$ is a single Slater determinant constructed from an unknown
-set of $N$ orthonormal single-particle states.  We denote each unknown
-single-particle state $\phi_{q}'$ by some label $q$.
-
-To make this computationally feasible, we further assume that the unknown
-states $\{\phi_q'\}$ are built from a linear combination of known functions,
-drawn from a finite set $\{\phi_p\}$.  This reduces the problem from an
-abstract mathematical one to a numerical linear algebra problem, with the
-caveat that this set of known functions must be chosen carefully to ensure
-convergence.
-
-Assuming the interaction is not too strong, we can use the single-particle
-states $\{\phi_p\}$ of our noninteracting Hamiltonian as a basis for the
-unknown states $\{\phi'_u\}$.  The two sets of states are then related by a
-linear transformation matrix $\bm C$:
-\begin{align*}
-  \phi_q' \equiv \sum_p \phi_p C_{p, q}
-\end{align*}
-To ensure the orthonormality of the states, we assume the set of unknown states $\{\phi_q'\}$ has as many elements as the set of $\{\phi_p\}$ and require the coefficient matrix $\bm C$ to be unitary.
-While these conditions are more strict than necessary, they greatly simplify the calculations and allow the states $\{\phi_q'\}$ to act as inputs for methods beyond HF.
-The set of states $\{\phi_q'\}$ now consists of $N$ \textit{occupied} states that participate in the Slater determinant $\Phi$ and the remaining \textit{unoccupied} states that do not.
+with respect to $\Phi$, subject to the restriction that $\Phi$ is a single Slater determinant constructed from an unknown set of $N$ orthonormal single-particle states.
+We denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To make this computationally feasible, we further assume that each unknown state $|q'\rangle$ can be built from a linear combination of known states, $|p\rangle$ for all $p$.
+This reduces the problem from an abstract mathematical one to a numerical linear algebra problem, with the caveat that this set of known functions be large enough to ensure convergence.
+
+Assuming the interaction is not too strong, we can use the single-particle states of our noninteracting Hamiltonian as a basis for the unknown states.
+The two sets of states are then related by a linear transformation matrix $\bm C$:
+\begin{align*}
+  |q'\rangle = \sum_p |p\rangle C_{p, q'}
+\end{align*}
+To ensure the orthonormality of the states, we assume the set of unknown states $|q'\rangle$ has as many elements as the set of known states $|p\rangle$ and we require the coefficient matrix $\bm C$ to be unitary.
+While these conditions are more strict than necessary, they greatly simplify the calculations and allow the states $|q'\rangle$ to act as inputs for methods beyond HF.
+The set of states $|q'\rangle$ now consists of $N$ \textit{occupied} states that participate in the Slater determinant $\Phi$ and the remaining \textit{unoccupied} states that do not.
 
@@
 \begin{align}
-  E_{\Phi} &= \sum_{j} n_j H^{[1] \prime}_{j, j} + \sum_{j, k} n_j n_k V'_{j, k, j, k} \label{eq:hfenergy}
+  E_{\Phi} &= \sum_{j} n_j H^{[1] \prime}_{j, j} + \sum_{j, k} n_j n_k H^{[2] \prime}_{j, k, j, k} \label{eq:hfenergy}
 \end{align}
@@
 \begin{align}
-  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* H_{r, s}^{[1]} C_{s, q}^{} \label{eq:hftransform1} \\
-  V'_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* V_{t, u, v, w}^{} C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
+  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* \langle r | H^{[1]} | s \rangle C_{s, q}^{} \label{eq:hftransform1} \\
+  H^{[2] \prime}_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* \langle t, u | H^{[2]} | v, w \rangle C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
 \end{align}
@@
 \end{align}
-and $\bm \epsilon$ is a vector of Lagrange multipliers with each element $\epsilon_q$ associated with a particular state $\phi'_q$.
+and $\bm \epsilon$ is a vector of Lagrange multipliers with each element $\epsilon_q$ associated with a particular state $|q'\rangle$.
 
@@
 states, it cannot provide an exact solution to a problem where correlations
-are present even if the basis $\{\phi_p\}$ is not truncated (infinite).  The
+are present even if the single-particle basis is not truncated (infinite in size).  The
 energy difference between the best Hartree-Fock energy and the exact ground
@@
 
-The second-quantized operators in \eqref{eq:second_quantized_one_body_hamiltonian} and \eqref{eq:second_quantized_two_body_hamiltonian} are constructed with respect to the vacuum state.
+The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state.
 That is, the operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum expectation value of zero:
@@
 It is possible to be normal-ordered with respect to a non-vacuum state, however.
-Consider a Slater determinant $\Phi$ with $N_{\text F}$ occupied states:
-\begin{align*}
-  \ket{\Phi} \equiv \ket{\varnothing_{i_1, i_2, \ldots, i_{N_{\text F}}}}
-\end{align*}
-where $\{i_1, i_2, \ldots, i_{N_{\text F}}\}$ is a set of $N_{\text F}$ indices that label the occupied states.
+Consider a Slater determinant $\Phi$ with $N_{\mathrm{F}}$ occupied states:
+\begin{align*}
+  \ket{\Phi} \equiv \ket{\varnothing_{i_1, i_2, \ldots, i_{N_{\mathrm{F}}}}}
+\end{align*}
+where $\{i_1, i_2, \ldots, i_{N_{\mathrm{F}}}\}$ is a set of $N_{\mathrm{F}}$ indices that label the occupied states.
 One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators:

### 2017-01-15 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

@@
 \begin{align}
-  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* \langle r | H^{[1]} | s \rangle C_{s, q}^{} \label{eq:hftransform1} \\
-  H^{[2] \prime}_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* \langle t, u | H^{[2]} | v, w \rangle C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
+  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s, q}^{} \label{eq:hftransform1} \\
+  H^{[2] \prime}_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* \langle t, u | \hat{H}^{[2]} | v, w \rangle C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
 \end{align}
@@
 \begin{align} \label{eq:hartreefock}
-  \bm F \bm C = \bm C \bm \epsilon
+  \bm{F} \bm{C} = \bm{C} \bm{\varepsilon}
 \end{align}
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv H_{p, q}^{[1]} + \sum_{r, s, j} n_j C_{r, j}^* V_{p, r, q, s}^{} C_{s, j}^{}
-\end{align}
-and $\bm \epsilon$ is a vector of Lagrange multipliers with each element $\epsilon_q$ associated with a particular state $|q'\rangle$.
-
-The HF equation can be solved by an iterative technique: a solution $\bm C$ can be fed into \eqref{eq:fock} and new solution can then obtained by solving the eigenvalue problem in \eqref{eq:hartreefock} using the Fock matrix obtained.
-For the initial guess, we use the ground state of our noninteracting Hamiltonian, thus $\bm C$ is initially the identity matrix.
-After dozens of iterations, perhaps with the aid of a convergence acceleration technique (such as DIIS [[cite??] or Broyden's method [[cite?]]), one would usually reach a state of self-consistency where the solution converges to a fixed value.
-This is the Hartree-Fock solution.
-
-Since HF restricts the ground state to a Slater determinant of single-particle
-states, it cannot provide an exact solution to a problem where correlations
-are present even if the single-particle basis is not truncated (infinite in size).  The
-energy difference between the best Hartree-Fock energy and the exact ground
-state energy is thus by definition known as the \textit{correlation energy}.
-The focus of post-HF methods such as IM-SRG is to improve on the HF results,
-thus recovering parts of this missing energy.
+  F_{p, q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r, s, j} n_j C_{r, j}^* \langle p, r | \hat{H}^{[2]} | q, s \rangle C_{s, j}^{}
+\end{align}
+and $\bm{\varepsilon}$ is a vector of Lagrange multipliers with each element $\varepsilon_{q'}$ associated with a particular state $|q'\rangle$.
+
+The HF equation can be solved iteratively: given a guess for the solution $\bm{C}$, it can be fed into \eqref{eq:fock} and new potential solution may be obtained by solving the eigenvalue problem in \eqref{eq:hartreefock} with the Fock matrix obtained from $\bm{C}$.
+While in theory it is possible for the solution to never reach a fixed point, or that it may require a large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
+In cases where it is insufficient, methods such as DIIS, Broyden's method, or even linear mixing can accelerate convergence greatly to the point where the possibility of nonconvergence is not a practical concern.
+
+For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}$ is initially the identity matrix.
+At each iteration, we calculate the sum of the Lagrange multiplers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration will decrease rapidly.
+
+Since HF restricts the ground state to a Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
+The energy difference between the best Hartree-Fock energy and the exact ground state energy is thus known as the \textit{correlation energy} (by definition).
+The focus of post-HF methods such as IM-SRG or coupled cluster is to improve on the HF results, recovering parts of this missing energy.
 
@@
 \begin{align*}
-  \hat H(s) \equiv \hat U(s) \hat H(0) \hat U^\dagger(s)
+  \hat{H}(s) \equiv \hat{U}(s) \hat{H}(0) \hat{U}^\dagger(s)
 \end{align*}
@@
 \begin{align*}
-  \frac{\D}{\D s} H(s) =
-  \left(\frac{\D}{\D s} \hat{U}(s)\right) \hat{H}(0) \hat{U}^\dagger(s) +
-  \hat{U}(s) \hat{H}(0) \frac{\D}{\D s} \hat{U}^\dagger(s)
-\end{align*}
-If we define an operator $\eta(s)$ as
-\begin{align*}
-  \eta(s) \equiv \left(\frac{\D}{\D s} \hat{U}(s)\right) \hat{U}^\dagger(s)
+  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\D s} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}
+\end{align*}
+If we define an operator $\hat{\eta}(s)$ as
+\begin{align*}
+  \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s)
 \end{align*}
@@
 \begin{align*}
-  \eta(s) + \eta^\dagger(s)
+  \hat{\eta}(s) + \hat{\eta}^\dagger(s)
   = \frac{\D}{\D s} \left(\hat{U}(s) \hat{U}^\dagger(s)\right)
@@
 \begin{align} \label{eq:imsrgode}
-  \frac{\D}{\D s} H(s) = [\eta(s), \hat{H}(s)]
+  \frac{\D \hat{H}(s)}{\D s} = [\hat{\eta}(s), \hat{H}(s)]
 \end{align}
@@
 is known as the \textit{generator} of the transformation.  When ``integrated''
-as a product, the full transformation $\hat U(s)$ is recovered:
+as a product, the full transformation $\hat U(s)$ is recovered.  Formally,
 \begin{align*}
   \hat U(s')
-  = \mathcal T_s \left\{ \mathrm{e}^{\int_0^{s'} \hat{\eta}(s) \D s} \right\}
-  \equiv \lim_{\Delta s \to 0} \prod_{s = 0, \Delta s, \ldots}^{s = s'}
-  \mathrm{e}^{\hat \eta(s) \Delta s}
-\end{align*}
-Here $\mathcal T_s$ is a notational device that denotes $s$-ordering: a reordering of the $\hat{\eta}(s)$ operator products expanded from the exponential with respect to $s$ in ascending order \cite[\S 6.1]{reimann2013quantum}.
-This is analogous to the usual time-ordering from quantum field theory.
+  = \mathcal{T}_s \mathrm{e}^{\int_0^{s'} \hat{\eta}(s) \D s}
+  \equiv \lim_{\Delta s \to 0}\left(\mathrm{e}^{\hat{\eta}(s_n) \Delta s} \mathrm{e}^{\hat{\eta}(s_{n - 1}) \Delta s} \cdots \mathrm{e}^{\hat{\eta}(s_1) \Delta s}\right)
+\end{align*}
+where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
+The symbol $\mathcal{T}_s \mathrm{e}$ is a notational device to indicate \textit{$s$-ordering} of its contents: every product of $\hat{\eta}(s)$ expanded from the exponential are to be reordered in descending order with respect to $s$ \cite[\S 6.1]{reimann2013quantum}.
+This is analogous to the time-ordering notation from quantum field theory.
 
@@
 
-The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state.
-That is, the operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum expectation value of zero:
-\begin{align*}
-&\bra{\varnothing} \hat{a}_p^\dagger \hat{a}_q \ket{\varnothing} = 0 &
-&\bra{\varnothing} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{\varnothing} = 0
-\end{align*}
-They are said to be \emph{normal-ordered} with respect to the vacuum state $\varnothing$.
-It is possible to be normal-ordered with respect to a non-vacuum state, however.
-Consider a Slater determinant $\Phi$ with $N_{\mathrm{F}}$ occupied states:
-\begin{align*}
-  \ket{\Phi} \equiv \ket{\varnothing_{i_1, i_2, \ldots, i_{N_{\mathrm{F}}}}}
-\end{align*}
-where $\{i_1, i_2, \ldots, i_{N_{\mathrm{F}}}\}$ is a set of $N_{\mathrm{F}}$ indices that label the occupied states.
+The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum expectation value of zero:
+\begin{align*}
+&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0 &
+&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0
+\end{align*}
+They are said to be \emph{normal-ordered} with respect to the vacuum state $\ket{}$.
+It is possible to be normal-ordered with respect to a different state, however.
+Suppose we have a Slater determinant $\Phi$ with $N$ occupied states:
+\begin{align*}
+  \ket{\Phi} \equiv \ket{i_1, i_2, \ldots, i_N}
+\end{align*}
+where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label the occupied states.
 One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators:
@@
 \end{align*}
-The quasiparticle field operators treat $\ket{\Phi}$ as their ``vacuum state'' (sometimes called ``Fermi vaccuum'' in an abstract sense), despite not being the physical vacuum state.
+The quasiparticle field operators treat the \textit{reference state} $\ket{\Phi}$ as their ``vacuum'' state (sometimes called a \textit{Fermi vaccuum}), even though it is not the true \emph{physical} vacuum state.
 As before, it is possible to construct arbitrary Slater determinants by applying quasiparticle operators to the reference state:
@@
 However, if $p$ is an occupied state, then applying $\hat{b}_p^\dagger$ destroys an existing particle in $\Phi$ or, equivalently, creates a \textit{hole} state.
-The set of labels $\{p_1, \ldots, p_k\}$ may contain up to $N$ hole states and a potentially infinite number of particle states.
-It is typical to classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
-If $N_{\text{p}} = N_{\text{h}}$, the Slater determinant represents a system containing the same number of physical particles.
-
-We may then define \emph{normal ordering with respect to the reference state} $\Phi$, a notational device that rearranges a string of operators such that every quasiparticle creation operator appears before a quasiparticle annihilation operator by repeatedly exchanging neighboring operators, with each exchange incurring a change in sign.
+The set of labels $\{p_1, \ldots, p_k\}$ may contain up to $N$ hole states and as many particle states as the basis allows for (minus the ones that are already hole states).
+One classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
+If $N_{\text{p}} = N_{\text{h}}$, the Slater determinant contains the same number of physical particles as the reference state.
+The ``$N_{\text{p}}$-particle-$N_{\text{h}}$-hole'' classification gives a crude sense of how distant a state is from the reference state, which can be exploited by many-body theories.
+
+We may then define \emph{normal ordering with respect to the reference state} $\Phi$, a notational device that reorders a string of operators such that every quasiparticle creation operator appears before a quasiparticle annihilation operator, while also accounting for the sign.
+Each exchange of operators must incur a change in sign -- mathematically this is just the \textit{sign} of the permutation that reorders the operators.
 A simple example would be the normal ordering of a pair of field operators such as:
 \begin{align*}
-  \normord{\hat{b}_p \hat{b}_q^\dagger} =
-  -\hat{b}_q^\dagger \hat{b}_p
-\end{align*}
-Here, we denote normal ordering of an operator string with respect to $\Phi$ by a pair of colons.
+  \normord{\hat{b}_p^{} \hat{b}_q^\dagger} =
+  -\hat{b}_q^\dagger \hat{b}_p^{}
+\end{align*}
+Here, we denote normal ordering of an operator string with respect to $\Phi$ by a enclosing pair of colons.
 The expectation value of a normal ordered string of operators with respect to $\Phi$ is guaranteed to vanish:
 \begin{align*}
-&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q \ket{\Phi} = 0 &
-&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^\dagger \hat{b}_s \hat{b}_r \ket{\Phi} = 0
-\end{align*}
-The normal ordering of the quasiparticle field operators are straightforward to compute, but what is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $\Phi$:
-\begin{align*}
-  \normord{\hat{a}_p^\dagger \hat{a}_q} &=
-  \hat{a}_p^\dagger \hat{a}_q - n_p \delta_{p, q}
+&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^{} \ket{\Phi} = 0 &
+&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^\dagger \hat{b}_s^{} \hat{b}_r^{} \ket{\Phi} = 0
+\end{align*}
+The normal ordering of the quasiparticle field operators is straightforward to compute.
+What is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $|\Phi\rangle$:
+\begin{align*}
+  \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &=
+  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p, q}^{}
 \end{align*}
@@
 \begin{align}
-  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s}
+  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r^{} \hat{a}_s^{}}
   \label{eq:normordhamiltonian}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_{i} n_i H^{[1]}_{i, i} + \frac{1}{2} \sum_{i, j} n_i n_j V_{i, j, i, j} \\
-  H^{[1]}_{p, q} &\equiv H^{[1]}_{p, q} + \sum_{i} n_i V_{p, i, q, i} \\
-  H^{[2]}_{p, q, r, s} &\equiv V_{p, q, r, s} \\
+  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i, j} n_i n_j \langle i, j | \hat{H}^{[2]} | i , j \rangle \\
+  H^{[1]}_{p, q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle p, i | \hat{H}^{[2]} | q, i \rangle \\
+  H^{[2]}_{p, q, r, s} &\equiv \langle p, q | \hat{H}^{[2]} | r, s \rangle \\
 \end{align*}
@@
 The normal-ordered representation of $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to that of $\hat H$ in \eqref{eq:vacuumhamiltonian}.
-The only difference is that it rearranges the matrix elements so as to emphasize the reference state $\Phi$ rather than vacuum state $\ket{\varnothing}$.
+The only difference is that it rearranges the matrix elements so as to emphasize the reference state $\Phi$ rather than vacuum state $\ket{}$.
 This makes a critical difference when the expressions containing 3-body or higher terms are \emph{truncated} to only 2-body.
@@
 Let $G_{\mathrm{b}}$ denote the value of the branching function at a given position.
-Correct weighting is then ensured by guaranteeing $m = \max\{0, \lfloor G_{\mathrm{b}} \rfloor - 1\}$ branches\footnote{$\lfloor x \rfloor$ denotes the floor of $x$, namely the largest integer $n$ such that $n \le x$.} with a probability $G_{\mathrm{b}} - m$ of getting an additional branch.
+Correct weighting is then ensured by guaranteeing $m = \max\{0, \lfloor G_{\mathrm{b}} \rfloor - 1\}$ branches with a probability $G_{\mathrm{b}} - m$ of getting an additional branch.
 A branch is an identical copy of the corresponding walker, with an identical past but with a different future.

### 2017-01-16 Datafiles/plot_fit.py
Consolidate data even more

@@ -195,7 +195,7 @@ def plot_fits(data,
         ax2.legend(bbox_to_anchor=(1, 1.0))
 
         fn = get_fn(**title_key)
-        settings_fn = fn + ".settings"
+        settings_fn = os.path.join("plot_settings", fn + ".json")
         settings = utils.load_json(settings_fn) or {"ax1": {}, "ax2": {}}
         def save_settings():
             utils.save_json(settings_fn, settings)
@@ -205,7 +205,7 @@ def plot_fits(data,
         break
 
 def plot_addrm(label, num_filled, freq, fit_start, fit_stop, **kwargs):
-    d_dmc = pd.read_csv("dat-qdsfe.jEYRh-4ptC1Dr5nlBcz0tg/dat-addrm-dmc.txt",
+    d_dmc = pd.read_csv("addrm-dmc-pedersen.txt",
                         float_precision=utils.PRECISION,
                         header=0, index_col=False,
                         delim_whitespace=True, comment="#")
@@ -239,6 +239,7 @@ def plot_addrm(label, num_filled, freq, fit_start, fit_stop, **kwargs):
             (d_dmc["num_filled"] == k["num_filled"]) &
             (d_dmc["freq"] == k["freq"])],
         dmc_label="DMC",
+        dmc_yerr_col="energy_err",
     )
 
 def plot_ground(num_filled, freq, fit_start, fit_stop, **kwargs):

### 2017-01-17 Manuscript/paper.tex
Consolidate data even more
Add fig-methods

@@
 \begin{figure}
-  % [width=.48\textwidth]
-  \includegraphics[width=\textwidth]{figures/fig-shell-structure-v2}
+  \includegraphics[width=\linewidth]{figures/fig-shell-structure-v2}
   \caption{Visualization of the 20 lowest single-particle states in the 2D harmonic oscillator basis.
@@
 \begin{figure}
-\includegraphics[width=.48\textwidth]{fig-diagrams-imsrg}
+\includegraphics[width=.48\linewidth]{fig-diagrams-imsrg}
 \caption{Diagrammatic representation of $C^{[r]}(\circ, \bullet)$ in \eqref{eq:commutmxe} that forms part of the IM-SRG flow equation \eqref{eq:flowmxe}.
@@
 \begin{figure}
-\includegraphics[width=.48\textwidth]{fig-diagrams-sfe}
+\includegraphics[width=.48\linewidth]{fig-diagrams-sfe}
 \caption{Diagrammatic form of the second- and third-order QDPT corrections.
@@
     \label{fig:N6hw1}
-    \includegraphics[width=0.38\textwidth]{figures/6parthw1.pdf}
+    \includegraphics[width=0.38\linewidth]{figures/6parthw1.pdf}
   }
@@
     \label{fig:N6hw05}
-    \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
+    \includegraphics[width=0.38\linewidth]{figures/6parthw05.pdf}
   } \\
@@
     \label{fig:N6hw028}
-    \includegraphics[width=0.38\textwidth]{figures/6parthw028.pdf}
+    \includegraphics[width=0.38\linewidth]{figures/6parthw028.pdf}
   }
@@
     \label{fig:N6hw01}
-    \includegraphics[width=0.38\textwidth]{figures/6parthw01.pdf}
+    \includegraphics[width=0.38\linewidth]{figures/6parthw01.pdf}
   }
@@
   \label{fig:N6}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \subfigure[Results for $N=12$ and $\omega=1.0$]{
-    \label{fig:N12hw1}
-    \includegraphics[width=0.38\textwidth]{figures/12parthw1.pdf}
-  }
-  \subfigure[Results for $N=12$ and $\omega=0.5$]{
-    \label{fig:N12hw05}
-    \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
-  } \\
-  \subfigure[Results for $N=12$ and $\omega=0.28$]{
-    \label{fig:N12hw028}
-    \includegraphics[width=0.38\textwidth]{figures/12parthw028.pdf}
-  }
-  \subfigure[Results for $N=12$ and $\omega=0.1$]{
-    \label{fig:N12hw01}
-    \includegraphics[width=0.38\textwidth]{figures/12parthw01.pdf}
-  }
-  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=12$ and different values of $\omega$.
-The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
-A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
-All energies in atomic units.}
-  \label{fig:N12}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \subfigure[Results for $N=20$ and $\omega=1.0$]{
-    \label{fig:N20hw1}
-    \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
-  } \subfigure[Results for $N=20$ and $\omega=0.5$]{
-    \label{fig:N20hw05}
-    \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
-  } \\
-  \subfigure[Results for $N=20$ and $\omega=0.28$]{
-    \label{fig:N20hw028}
-    \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
-  } \subfigure[Results for $N=20$ and $\omega=0.1$]{
-    \label{fig:N20hw01}
-    \includegraphics[width=0.38\textwidth]{figures/20parthw01.pdf}
-  }
-  \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
-    for circular quantum dots for $N=20$ and different values of
-    $\omega$. The results are compared with diffusion Monte
-    Carlo (DMC), coupled cluster at the level of singles and doubles
-    (CCSD), full configuration interaction (FCI) and Hartree-Fock
-    calculations (HF) as functions of the number of major oscillator
-    shells $R$. A harmonic oscilaltor basis has been used, with an
-    unrenormalized Coulomb repulsion and the White generator. All
-    energies in atomic units.}
-  \label{fig:N20}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \subfigure[Results for $N=30$ and $\omega=1.0$]{
-    \label{fig:N30hw1}
-    \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
-  } \subfigure[Results for $N=30$ and $\omega=0.5$]{
-    \label{fig:N30hw05}
-    \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
-  } \\
-  \subfigure[Results for $N=30$ and $\omega=0.28$]{
-    \label{fig:N30hw028}
-    \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
-  } \subfigure[Results for $N=30$ and $\omega=0.1$]{
-    \label{fig:N30hw01}
-    \includegraphics[width=0.38\textwidth]{figures/30parthw01.pdf}
-  }
-  \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
-    for circular quantum dots for $N=30$ and different values of
-    $\omega$. The results are compared with diffusion Monte
-    Carlo (DMC), coupled cluster at the level of singles and doubles
-    (CCSD), full configuration interaction (FCI) and Hartree-Fock
-    calculations (HF) as functions of the number of major oscillator
-    shells $R$. A harmonic oscilaltor basis has been used, with an
-    unrenormalized Coulomb repulsion and the White generator. All
-    energies in atomic units.}
-  \label{fig:N30}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \subfigure[Results for $N=42$ and $\omega=1.0$]{
-    \label{fig:N42hw1}
-    \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
-  } \subfigure[Results for $N=42$ and $\omega=0.5$]{
-    \label{fig:N42hw05}
-    \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
-  } \\
-  \subfigure[Results for $N=42$ and $\omega=0.28$]{
-    \label{fig:N42hw028}
-    \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
-  } \subfigure[Results for $N=42$ and $\omega=0.1$]{
-    \label{fig:N42hw01}
-    \includegraphics[width=0.38\textwidth]{figures/42parthw01.pdf}
-  }
-  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=42$ and different values of $\omega$.
-The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
-A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
-All energies in atomic units.}
-  \label{fig:N42}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{fig-gs}
+  \includegraphics[width=0.8\linewidth]{fig-gs}
   \caption{Ground state energies.}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{fig-add}
+  \includegraphics[width=0.8\linewidth]{fig-add}
   \caption{Addition energies.}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{fig-rm}
+  \includegraphics[width=0.8\linewidth]{fig-rm}
   \caption{Removal energies.}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{fig-rel-slopes}
+  \includegraphics[width=0.8\linewidth]{fig-rel-slopes}
   \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{figures/fig-methods}
+  \caption{A high-level view of the ways in which many-body methods in this paper can be combined to calculate ground state, addition, and removal energies, shown as a directed acyclic graph.}
+  \label{fig:methods}
+\end{figure}
+
+Figure \ref{fig:methods} shows high-level view of the ways in which many-body methods in this paper can be combined to to compute the energy observables.
+There are many possible paths through which one can walk in this directed graph to obtain the output observables.
+For example, one can do HF to get an initial rough estimate, followed by IM-SRG to refine the ground state, and then EOM to refine the addition and removal energies.
+This is in fact one of the approaches benchmarked in this paper.
+
+It is possible to omit some of the methods, bypassing some of the steps.
+For example, one can do an IM-SRG calculation \emph{without} doing HF.
+There are few good reasons to do so, as it typically worsens the result and increases the numerical cost of IM-SRG, but it can be done.
+Similarly, one can do both HF and IM-SRG, but omit QDPT, yet still obtain \emph{addition and removal} energies.
+The result would be poor, but it may be useful for the purpose of assessing difficulty of the problem.
+For example, if the omission of QDPT leads to a large change, then it may indicate the presence of strong correlations.
+
 \subsection{Comparison between methods}
@@
 [[---]]
+
+[[Cite as source of DMC energies: \cite{PhysRevB.84.115302}]]
 

### 2017-01-17 Datafiles/plot_fit.py

@@ -242,16 +242,9 @@ def plot_addrm(label, num_filled, freq, fit_start, fit_stop, **kwargs):
         dmc_yerr_col="energy_err",
     )
 
-def plot_ground(num_filled, freq, fit_start, fit_stop, **kwargs):
-    d_dmc = pd.read_csv("gs-dmc-joergen.txt",
-                        float_precision=utils.PRECISION,
-                        header=0, index_col=False,
-                        delim_whitespace=True, comment="#")
-    d_dmc["num_filled"] = utils.get_num_filled(d_dmc["num_particles"])
-    d = pd.read_csv("imsrg-qdpt/dat_gsenergy.txt",
-                    float_precision=utils.PRECISION,
-                    header=0, index_col=False,
-                    delim_whitespace=True)
+def plot_ground(num_filled, freq, fit_start, fit_stop, hartree_fock, **kwargs):
+    d_dmc = utils.load_gs_dmc_energies()
+    d = utils.load_gs_energies()
     for data in [d, d_dmc]:
         data["num_particles"] = data["num_filled"] * (data["num_filled"] + 1)
         data["energy_per_particle"] = data["energy"] / data["num_particles"]
@@ -261,7 +254,8 @@ def plot_ground(num_filled, freq, fit_start, fit_stop, **kwargs):
     # filters
     d = d[d["num_filled"] == num_filled]
     d = d[d["freq"] == freq]
-    d = d[d["method"] != "hf"]
+    if not hartree_fock:
+        d = d[d["method"] != "hf"]
 
     plot_fits(
         data=d,
@@ -291,6 +285,7 @@ def main():
     p.add_argument("-kf", "--num-filled", type=int, required=True)
     p.add_argument("-k1", "--fit-start", type=float, required=True)
     p.add_argument("-k2", "--fit-stop", type=float, default=np.inf)
+    p.add_argument("-hf", "--hartree-fock", action="store_true")
     p.add_argument("label", metavar="type", help="ground, add, or rm")
     kwargs = vars(p.parse_args())
     plt.rcParams["interactive"] = kwargs["interactive"]

### 2017-01-17 Datafiles/utils.py

@@ -20,17 +20,31 @@ JSON_PRETTY = {
 }
 
 GS_METHOD_COLOR = {
-    "hf": "#841a0b",
-    "mp2": "#39b237",
-    "imsrg": "#1351c4",
+    "hf": "#d39402",
+    "mp2": "#841a0b",
+    "imsrg": "#39b237",
+    "ccsd": "#1351c4",
 }
 
 METHOD_COLOR = {
-    "qdpt": "#39b237",
-    "eom": "#841a0b",
-    "eom_quads": "#a825bc",
-    "eom_f": "#f4ad42",
-    "cc": "#1351c4",
+    "imsrg_qdpt3": "#39b237",
+    "imsrg_eom": "#841a0b",
+    "imsrg_quads_eom": "#a825bc",
+    "imsrg_f_eom": "#d39402",
+    "ccsd_eom": "#1351c4",
+}
+
+METHOD_LABEL = {
+    "hf": "HF only",
+    "hf_qdpt2": "HF only + QDPT2",
+    "hf_qdpt3": "HF only + QDPT3",
+    "imsrg": "IMSRG(2)",
+    "imsrg_qdpt2": "IMSRG(2) + QDPT2",
+    "imsrg_qdpt3": "IMSRG(2) + QDPT3",
+    "imsrg_eom": "IMSRG(2) + EOM",
+    "imsrg_quads_eom": "Magnus(2*) + EOM",
+    "imsrg_f_eom": "IMSRG(2)[F] + EOM[N]",
+    "ccsd_eom": "CCSD+EOM",
 }
 
 def matplotlib_try_enable_deterministic_svgs():
@@ -242,7 +256,7 @@ SAM_ATTACHED_COLS = ["shells", "filled", "ML", "MS", "omega", "E(N)",
 SAM_REMOVED_COLS = ["shells", "filled", "ML", "MS", "omega", "E(N)",
                     "E(N-1)-E(N)", "E(N+1)", "partialnorm(1p)"]
 
-def load_gs_energies():
+def load_gs_energies(drop_priority=True, toler=6e-4):
     '''["freq", "num_filled", "num_shells", "method", "energy"]'''
     ds = []
 
@@ -305,15 +319,19 @@ def load_gs_energies():
     ds.append(d)
 
     d = pd.concat(ds, ignore_index=True)
+    combiner = lambda x: x
+    if drop_priority:
+        combiner = priority_combiner
     try:
[…]

### 2017-01-18 Manuscript/paper.tex
spEnergiesQD/Manuscript/paper.tex: add placeholders

@@
 
-\subsection{Equations of Motion Methods}
+\subsection{Equations of motion methods}
 
@@
 
+\subsection{Coupled cluster theory}
+
+[[?]]
+
+\subsubsection{EOM-CC}
+
+[[?]]
+
 \subsection{Diffusion Monte Carlo}
@@
 
-Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.
+Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.\ for comparisons with other methods), this is strictly not necessary.
 
@@
 \begin{acknowledgments}
-  This work was supported by the National Science Foundation Grant No.~PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.
+  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.
 This research used computational resources of the Notur project in Norway.

### 2017-01-23 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex
Add new figures

@@
 \usepackage{siunitx}
-\usepackage{subfigure}
+\usepackage{subcaption}
 
@@
   &{}-
-  \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{H^{[1]}_i + H^{[1]}_j - H^{[1]}_p - H^{[1]}_a}
-\end{align*}
-[[write out the full thing using $H^1_{p,p}$]]
+  \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{H^{[1]}_{i, i} + H^{[1]}_{j, j} - H^{[1]}_{p, p} - H^{[1]}_{a, a}}
+\end{align*}
 The expression is depicted in Figure \ref{fig:diagrams-sfe}.
@@
 
+\subsection{Methodology}
+
 \begin{figure}
   \centering
-  \subfigure[Results for $N=6$ and $\omega=1.0$]{
-    \label{fig:N6hw1}
-    \includegraphics[width=0.38\linewidth]{figures/6parthw1.pdf}
-  }
-  \subfigure[Results for $N=6$ and $\omega=0.5$]{
-    \label{fig:N6hw05}
-    \includegraphics[width=0.38\linewidth]{figures/6parthw05.pdf}
-  } \\
-  \subfigure[Results for $N=6$ and $\omega=0.28$]{
-    \label{fig:N6hw028}
-    \includegraphics[width=0.38\linewidth]{figures/6parthw028.pdf}
-  }
-  \subfigure[Results for $N=6$ and $\omega=0.1$]{
-    \label{fig:N6hw01}
-    \includegraphics[width=0.38\linewidth]{figures/6parthw01.pdf}
-  }
-  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=6$ and $\omega=1.0$ The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$.
-A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator.
-All energies in atomic units.}
-  \label{fig:N6}
+  \includegraphics[width=0.8\linewidth]{figures/fig-methods}
+  \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
+  \label{fig:methods}
 \end{figure}
+
+Before we discuss the results, let us briefly outline the concrete methodology used by our numerical experiments.
+There is a some degree of flexibility in which many-body methods can be applied, which is not evident from reading the description of each method alone.
+
+The typical approach is to apply them in the order shown in Figure \ref{fig:methods}.
+Such an ordering maximizes the benefits of each method: Hartree-Fock acts as an initial, crude procedure to \textit{soften} the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+
+The arrows in the diagram designate the flow of numerical data, which are generally matrix elements of some operator.
+For HF and IM-SRG, these are simply (evolved) Hamiltonian matrix elements.
+For CC, they would be elements of the cluster operator $\hat{T}$.
+
+There are several paths through which one can traverse in this diagram to obtain the output observables.
+Among these possibilities, there exist (a) HF + IM-SRG + QDPT, (b) HF + IM-SRG + EOM, and (c) HF + CC + EOM.
+All three paths are explored in this paper.
+There are, of course, other paths, but we will not consider every single possibility here.
+
+Moreover, there is also the possibility of omitting one or more of these steps in the process.
+For example, one can omit HF, but continue with the remaining two steps.
+While this is possible, our experience indicate that the HF plays a strong role in increasing the rate of convergence of the post-HF methods, and thereby increasing the accuracy and efficiency as well.
+Hence, there is very little reason to omit HF.
+
+All results in this paper shall discuss results in which HF is included as the first step of the calculation, and thus we will not explicitly state ``HF'' unless there is no post-HF method used, in which case we write ``HF only''.
+
+Unlike ground state energy, whose systems are characterized only by the number of particles $N$ and the oscillator frequency $\omega$, the addition (or removal) energy depend on an additional quantity: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
+This is because there can be multiple states with $N + 1$ particles with near-degenerate energy.
+For our numerical results, we will study exclusively the addition energies such that $|M_\ell|$ is as small as possible subject to the constraint that the particle added lies within the next shell.
+This means the $N + 1$ states we are interested in are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$, while the $N - 1$ states are those with $|M_\ell| = 1 - K_{\mathrm{F}} \bmod 2$, where $K_{\mathrm{F}}$ is the number of occupied shells.
+
+\subsection{Tables and figures}
 
@@
   \centering
-  \caption{Ground state energy (in atomic units) of a circular quantum dot, with $N$ particles and oscillator frequency $\omega$.
+  \caption{Ground state energy with $N$ particles and oscillator frequency $\omega$.
 The IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$ results which are for $R=18$), employing a Hartree-Fock basis, a bare Coulomb interaction and the White generator.
 For $N=42$ and $\omega=0.1$ results are presented up to $R=22$ major shells.
-The results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained using the extrapolation formula of [[equation?]].}
+The results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained using the extrapolation formula of [[equation?
+TODO: redo the extrapolations]].}
   \label{tab:SRGDMC-R20}
@@
 
+[[TODO: table for addrm]]
+
 \begin{figure}
@@
 
-[[Sarah's discussions on ground state energy are absent :(]]
-In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems.
-We start with the Wegner generator in subsection [[??]].
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-0-normal}
+  \caption{[[...]]}
+  \label{fig:by-num-shells-6-2-ground-0-normal}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{fig-by-freq-10-6-ground-0-normal}
+  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$.
+The energy is normalized with respect to the Hartree-Fock values to make plot easier to see.
+Lower frequency leads to stronger correlations and thereby a more difficult problem.
+[[the fact that CCSD and MP2 are really close may be just a coincidence, since they cross around 12 shells but then diverge again]]}
+  \label{fig:by-freq-10-6-gs-0-normal}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{fig-by-freq-10-6-add-0-normal}
+    \caption{Addition energy}
+    \label{fig:by-freq-10-6-add-0-normal}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{fig-by-freq-10-6-rm-1-normal}
+    \caption{Removal energy}
+    \label{fig:by-freq-10-6-rm-1-normal}
+  \end{subfigure}
+  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$.
+Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree-Fock values.}
+\end{figure}
+
+In this section, we discuss the numerical results for the ground state, addition, and removal energies of closed-shell systems for a selection of methods.
+
+For the IM-SRG results
+
+As foreshadowed, we find the Wegner generator described in subsection [[??]].
 Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, favors the use of a Hartree-Fock basis and the Coulomb interaction.
@@
 [[TODO: add FCI, CCSD results to GS energy plots]]
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth]{figures/fig-methods}
-  \caption{A high-level view of the ways in which many-body methods in this paper can be combined to calculate ground state, addition, and removal energies, shown as a directed acyclic graph.}
-  \label{fig:methods}
-\end{figure}
-
-Figure \ref{fig:methods} shows high-level view of the ways in which many-body methods in this paper can be combined to to compute the energy observables.
-There are many possible paths through which one can walk in this directed graph to obtain the output observables.
-For example, one can do HF to get an initial rough estimate, followed by IM-SRG to refine the ground state, and then EOM to refine the addition and removal energies.
-This is in fact one of the approaches benchmarked in this paper.
 

### 2017-01-23 Datafiles/plot_by_freq.py

@@ -1,64 +1,56 @@
 #!/usr/bin/env python3
 # Generates ../FigureFiles/fig-by-freq-*.svg from the data files.
-import itertools, os, sys
+import argparse, itertools, os, sys
 import matplotlib
 import matplotlib.pyplot as plt
 import pandas as pd
 import utils
 
-utils.init(__file__)
-
-d = pd.concat(utils.get_ar_energies())
-print("Saving ...".format(**locals()), flush=True)
-num_shells = 10.0
-num_filled = 2
-d = d[(d["num_shells"] == num_shells) &
-      (d["num_filled"] == num_filled) &
-      # filter out higher frequencies because they stretch the plot too much
-      (d["freq"] <= 1.0)]
-num_particles = num_filled * (num_filled + 1)
-for interaction, label in itertools.product(
-        [utils.V0, utils.V2],
-        ["add", "rm"]):
-    energy_type = {"add": "addition", "rm": "removal"}[label]
-    ml = (num_filled + (label != "add")) % 2
+p = argparse.ArgumentParser()
+p.add_argument("-i", "--interactive", action="store_true")
+p.add_argument("-t", "--title", action="store_true")
+p.add_argument("-int", "--interaction", default="normal")
+p.add_argument("label", metavar="type", help="ground, add, or rm")
+kwargs = vars(p.parse_args())
+plt.rcParams["interactive"] = kwargs["interactive"]
+with utils.plot(__file__):
+    d = utils.load_all()
+    num_shells = 10
+    num_filled = 2
+    interaction = kwargs["interaction"]
+    label = kwargs["label"]
+    ml = utils.label_num_filled_to_ml(label, num_filled)
+    d = d[(d["method"] != "imsrg[f]+eom[n]") &
+          (d["method"] != "magnus_quads+eom") &
+          (d["interaction"] == interaction) &
+          (d["label"] == label) &
+          (d["num_shells"] == num_shells) &
+          (d["num_filled"] == num_filled) &
+          # filter out higher frequencies because they stretch the plot too much
+          (d["freq"] <= 1.0) &
+          (d["ml"] == ml)]
+    num_particles = num_filled * (num_filled + 1)
+    energy_type = {"ground": "ground state",
+                   "add": "addition", "rm": "removal"}[label]
     fig, ax = plt.subplots()
-    fig.set_size_inches(8, 6)
-    for method in d["method"].unique():
-        case = d[(d["ml"] == ml) &
-                 (d["label"] == label) &
[…]

### 2017-01-23 Datafiles/plot_by_freq.sh

@@ -1,0 +1,8 @@
+#!/bin/sh
+set -eu
+dir=`dirname "$0"`
+cd "$dir"
+
+./plot_by_freq.py ground
+./plot_by_freq.py add
+./plot_by_freq.py rm

### 2017-01-23 Datafiles/plot_by_num_shells.py

@@ -1,0 +1,54 @@
+#!/usr/bin/env python3
+# Generates ../FigureFiles/fig-by-num-shells-*.svg from the data files.
+import argparse, itertools, os, sys
+import matplotlib
+import matplotlib.ticker
+import matplotlib.pyplot as plt
+import pandas as pd
+import utils
+
+def plot(label, num_filled, freq,
+         num_shells_range, interaction="normal"):
+    d = utils.load_all()
+    ml = utils.label_num_filled_to_ml(label, num_filled)
+    d = d[(d["method"] != "imsrg[f]+eom[n]") &
+          (d["method"] != "magnus_quads+eom") &
+          (d["interaction"] == interaction) &
+          (d["label"] == label) &
+          (d["num_filled"] == num_filled) &
+          (d["num_shells"] >= num_shells_range[0]) &
+          (d["num_shells"] <= num_shells_range[1]) &
+          (d["freq"] == 1.0) &
+          (d["ml"] == ml)]
+    num_particles = num_filled * (num_filled + 1)
+    energy_type = {"ground": "ground state",
+                   "add": "addition",
+                   "rm": "removal"}[label]
+    fig, ax = plt.subplots()
+    fig.set_size_inches((4, 3))
+    for method, case in d.groupby("method"):
+        case = case.sort_values("num_shells")
+        xs = case["num_shells"].astype(int)
+        ys = case["energy"]
+        ax.plot(xs, ys, "-x", label=utils.METHOD_LABEL[method],
+                color=utils.METHOD_COLOR[method])
+        ax.get_xaxis().set_major_locator(
+            matplotlib.ticker.MaxNLocator(integer=True))
+    ax.set_xlabel("K (number of shells)")
+    ax.set_ylabel("E (energy)")
+    ax.legend()
+    fig.tight_layout()
+    utils.savefig(fig,
+                  "by-num-shells-{num_particles}-{num_filled}-"
+                  "{label}-{ml}-{interaction}"
+                  .format(**locals()))
+
+p = argparse.ArgumentParser()
+p.add_argument("-i", "--interactive")
+args = p.parse_args()
+plt.rcParams["interactive"] = args.interactive is not None
+with utils.plot(__file__):
+    if args.interactive is not None:
+        eval("plot({})".format(args.interactive))
+    else:
+        plot("ground", freq=1.0, num_filled=2, num_shells_range=[4, 15])

### 2017-01-23 Datafiles/plot_fit.py

@@ -250,8 +250,6 @@ def plot_ground(interaction, freq, num_filled,
     if not hartree_fock:
         d = d[d["method"] != "hf"]
 
-    print(d)
-
     plot_fits(
         data=d,
         fit_range=[fit_start, fit_stop],
@@ -264,7 +262,7 @@ def plot_ground(interaction, freq, num_filled,
         get_title="ground, N={num_particles}, ω={freq}".format,
         get_fn="fit-ground-{num_filled}-{freq}".format,
         color_cols=["method"],
-        get_color=lambda method: utils.GROUND_METHOD_COLOR[method],
+        get_color=lambda method: utils.METHOD_COLOR[method],
         get_color_label=lambda method: method,
         get_dmc=utils.filter_eq(["num_filled", "freq"],
                                 check_unused_kwargs=False),

### 2017-01-23 Datafiles/utils.py

@@ -24,36 +24,34 @@ JSON_PRETTY = {
     "sort_keys": True,
 }
 
-GROUND_METHOD_COLOR = {
-    "hf": "#e07b1d",
-    "mp2": "#a81e4c",
-    "imsrg": "#21a54f",
-    "ccsd": "#1c5aa5",
-    "fci": "#2e2360",
-}
-
 METHOD_COLOR = {
+    "ccsd": "#1c5aa5",
+    "ccsd+eom": "#1351c4",
+    "fci": "#2e2360",
     "hf": "#e0cc18",
     "hf+qdpt3": "#e28522",
     "imsrg": "#92e057",
-    "imsrg+qdpt3": "#39b237",
     "imsrg+eom": "#841a0b",
+    "imsrg+qdpt3": "#39b237",
     "imsrg[f]+eom[n]": "#8e2544",
     "magnus_quads+eom": "#a825bc",
-    "ccsd+eom": "#1351c4",
+    "mp2": "#a81e4c",
 }
 
 METHOD_LABEL = {
+    "ccsd": "CCSD",
+    "ccsd+eom": "CCSD+EOM",
+    "fci": "FCI",
     "hf": "HF only",
     "hf+qdpt2": "HF only + QDPT2",
     "hf+qdpt3": "HF only + QDPT3",
     "imsrg": "IMSRG(2)",
+    "imsrg+eom": "IMSRG(2) + EOM",
     "imsrg+qdpt2": "IMSRG(2) + QDPT2",
     "imsrg+qdpt3": "IMSRG(2) + QDPT3",
-    "imsrg+eom": "IMSRG(2) + EOM",
     "imsrg[f]+eom[f]": "IMSRG(2)[F] + EOM[N]",
     "magnus_quads+eom": "Magnus(2*) + EOM",
-    "ccsd+eom": "CCSD+EOM",
+    "mp2": "MP2",
 }
 
 def matplotlib_try_enable_deterministic_svgs():
@@ -276,10 +274,6 @@ def parse_nathan_like_data(d, label):
     d["label"] = label
     return d
 
-# interactions
-V0 = ""                                 # normal Coulomb
-V2 = "_sigmaA=0.5_sigmaB=4.0"           # softened Coulomb (see figures.md)
-
 @np.vectorize
 def get_num_filled(num_particles, max_shells=100):
     for k in range(max_shells):
@@ -370,6 +364,9 @@ def p_num_filled_to_label(p, num_filled):
     else:
[…]

### 2017-02-23 Manuscript/paper.tex
Add tables and table generator script
Also added some new MP2 results.  The remaining IM-SRG(2)+QDPT results
will be added later.

@@
   \caption{Ground state energy with $N$ particles and oscillator frequency $\omega$.
-The IM-SRG(2) results are given for $R=20$ shells (except for the $N=56$ results which are for $R=18$), employing a Hartree-Fock basis, a bare Coulomb interaction and the White generator.
-For $N=42$ and $\omega=0.1$ results are presented up to $R=22$ major shells.
-The results labelled IM-SRG(2)$_{R\rightarrow \infty}$ are obtained using the extrapolation formula of [[equation?
-TODO: redo the extrapolations]].}
+The IM-SRG(2) results are given for $K=20$ shells (except for the $N=56$ results which are for $K=18$), employing a Hartree-Fock basis, the ordinary Coulomb interaction and the White generator.}
   \label{tab:SRGDMC-R20}
-  \begin{tabular}{SSSSS}
-    \toprule
-    {$N$} & {$\omega$} & {IM-SRG(2)} & {IM-SRG(2)$_{R\rightarrow \infty}$} & {DMC} \\
-    \midrule
-    6  & 1.0  &  20.1583  &  20.1468 &  20.1593(1) \\
-       & 0.5  &  11.7690  &  11.7631 &  11.7848(1) \\
-       & 0.28 &   7.5713  &   7.5695 &   7.6002(1) \\
-       & 0.1  &   3.4962  &   3.4977 &   3.5539(1) \\
-    \midrule
-    12 & 1.0  &  65.7280  &  65.6990 &  65.7001(1) \\
-       & 0.5  &  39.1631  &  39.1473 &  39.1596(1) \\
-       & 0.28 &  25.6212  &  25.6140 &  25.6358(1) \\
-       & 0.1  &  12.2223  &  12.2234 &  12.2698(1) \\
-    \midrule
-    20 & 1.0  & 155.9737  & 155.9130 & 155.8822(1) \\
-       & 0.5  &  93.9219  &  93.8853 &  93.8752(1) \\
-       & 0.28 &  61.94362 &  61.9240 &  61.9268(1) \\
-       & 0.1  &  29.95263 &  29.9565 &  29.9779(1) \\
-    \midrule
-    30 & 1.0  & 308.7673  & 308.6053 & 308.5627(2) \\
-       & 0.5  & 187.1671  & 186.8340 & 187.0426(2) \\
-       & 0.28 & 124.0410  & 123.7171 & 123.9683(2) \\
-       & 0.1  &  60.4319  &  60.1158 &  60.4205(2) \\
-    \midrule
-    42 & 1.0  & 543.3398  & 543.3304 & 542.9428(8) \\
-       & 0.5  & 330.8885  & 330.8425 & 330.6306(2) \\
-       & 0.28 & 220.0226  & 219.9534 & 219.8426(2) \\
-       & 0.1  & 107.7851  & 106.8074 & 107.6389(2) \\
-    \midrule
-    56 & 1.0  & 880.4159  &          & 879.3986(6) \\
-       & 0.5  & 538.8199  &          & 537.353(2)  \\
-       & 0.28 & 360.83689 &          & 358.145(2)  \\
-    \bottomrule
-  \end{tabular}
+  \input{tab-ground}
 \end{table}
 
-[[TODO: table for addrm]]
+\begin{table}
+  \centering
+  \caption{[[Addition energy]]}
+  \input{tab-add}
+\end{table}
+
+\begin{table}
+  \centering
+  \caption{[[Removal energy]]}
+  \input{tab-rm}
+\end{table}
 

### 2017-02-23 Datafiles/tabulate.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python3
+import itertools, os, sys
+import numpy as np
+import pandas as pd
+import utils
+
+def save_table(path, label,
+               num_shells=[15, 15, 15, 15, 15, 20],
+               num_particles=[6, 12, 20, 30, 42, 56],
+               freqs=[0.1, 0.28, 1.0]):
+    d = utils.load_all()
+    d = utils.filter_preferred_ml(d)
+    print(d["method"].unique())
+    del d["ml"]
+    d = d[d["interaction"] == "normal"]
+    del d["interaction"]
+    d = d[d["label"] == label]
+    del d["label"]
+    del d["num_filled"]
+    d = d.set_index(["num_shells", "num_particles", "freq", "method"])
+    d = d.unstack("method")
+
+    if label == "ground":
+        methods = ["hf", "mp2", "imsrg", "ccsd"]
+        header = r"""
+        \begin{tabular}{SSSSSSS}%
+        \toprule
+        {$N$} & {$\omega$} & {$K$} & {HF} & {MP2} & {IM-SRG(2)} & {CCSD} \\
+        """
+    else:
+        methods = ["hf+qdpt3", "imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
+        header = r"""
+        \begin{tabular}{SSSSSSS}%
+        \toprule
+        {$N$} & {$\omega$} & {$K$} & {HF} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
+        {} & {} & {} & {+QDPT3} & {+QDPT3} & {+EOM} & {+EOM} \\
+        """
+    d = d.reindex_axis(methods, level=-1, axis=1)
+    d.columns = d.columns.droplevel(level=0)
+
+    out_file = open(path, "w")
+    out_file.write(header)
+    for num_shells, num_particles in zip(num_shells, num_particles):
+        out_file.write("\\midrule\n")
+        for freq in freqs:
+            row = []
+            row.extend([num_particles, freq, num_shells])
+            for method in methods:
+                value = d.loc[(num_shells, num_particles, freq), method]
+                row.append("" if np.isnan(value) else
+                           "{:.4f}".format(value))
+            out_file.write(" & ".join(map(str, row)) + " \\\\\n")
+    out_file.write(r"""\bottomrule\end{tabular}""")
+
+    return d
+
+os.chdir(os.path.dirname(__file__))
[…]

### 2017-02-23 Datafiles/utils.py

@@ -242,6 +242,15 @@ def expand_range(r, factor):
         r[1] + factor * (r[1] - r[0]),
     ])
 
+def intersperse(sep, xs):
+    first = True
+    for x in xs:
+        if first:
+            first = False
+        else:
+            yield sep
+        yield x
+
 def load_json_records(fn):
     with open(fn) as f:
         return pd.DataFrame.from_records([

### 2017-02-26 Manuscript/paper.tex
Add more tables

@@
   \centering
-  \caption{Ground state energy with $N$ particles and oscillator frequency $\omega$.
-The IM-SRG(2) results are given for $K=20$ shells (except for the $N=56$ results which are for $K=18$), employing a Hartree-Fock basis, the ordinary Coulomb interaction and the White generator.}
-  \label{tab:SRGDMC-R20}
+  \caption{Ground state energy of quantum dots with $N$ particles and an oscillator frequency of $\omega$.
+For every row, the calculations performed in a harmonic oscillator basis size with $K$ shells.}
+  \label{tab:ground}
   \input{tab-ground}
@@
   \centering
-  \caption{[[Addition energy]]}
+  \caption{Addition energy of a selection of quantum dot systems.  See Table \ref{tab:ground} for details.}
+  \label{tab:add}
   \input{tab-add}
@@
   \centering
-  \caption{[[Removal energy]]}
+  \caption{Removal energy of a selection of quantum dot systems.  See Table \ref{tab:add} for details.}
+  \label{tab:rm}
   \input{tab-rm}
+\end{table}
+
+\begin{table}
+  \centering
+  % The siunitx package somehow makes the columns unnecessarily wide so we have to compensate by shrinking the text size :/
+  \footnotesize
+  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
+The uncertainties are computed from the approximate Hessian used in Levenberg-Marquardt fitting procedure.
+Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
+  \label{tab:ground-extrapolated}
+  \input{tab-ground-extrapolated}
+\end{table}
+
+\begin{table}
+  \centering
+  \footnotesize
+  \caption{Extrapolated addition energies for quantum dots with fit uncertainties.  See Table \ref{tab:ground-extrapolated} for details.}
+  \label{tab:add-extrapolated}
+  \input{tab-add-extrapolated}
+\end{table}
+
+\begin{table}
+  \centering
+  \footnotesize
+  \caption{Extrapolated removal energies for quantum dots with fit uncertainties.  See Table \ref{tab:add-extrapolated} for details.}
+  \label{tab:rm-extrapolated}
+  \input{tab-rm-extrapolated}
 \end{table}
@@
   \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-0-normal}
-  \caption{[[...]]}
+  \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.  [[TODO: Results for FCI are from who?]] [[TODO: Add DMC results]]}
   \label{fig:by-num-shells-6-2-ground-0-normal}
@@
   \includegraphics[width=\linewidth]{fig-by-freq-10-6-ground-0-normal}
-  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$.
-The energy is normalized with respect to the Hartree-Fock values to make plot easier to see.
+  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
+The energy is normalized with respect to the Hartree-Fock values to magnify the differences.
 Lower frequency leads to stronger correlations and thereby a more difficult problem.
-[[the fact that CCSD and MP2 are really close may be just a coincidence, since they cross around 12 shells but then diverge again]]}
+The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).
+[[TODO: Add DMC results if available]]}
   \label{fig:by-freq-10-6-gs-0-normal}
@@
   \end{subfigure}
-  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$.
+  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
 Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree-Fock values.}
@@
 For the IM-SRG results
+
+All calculations in this paper are performed with a relative numerical precision of about $10^{-5}$ or lower (sometimes \emph{much} lower).
+This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate at every step of the calculation, thus the precision of the final results may be an order of magnitude larger.
 
@@
 
-The discrepeancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
+The discrepancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
 The former can be reduced by increasing the number of shells, and can be further alleviated by extrapolation techniques.
@@
 Both IM-SRG and MP2 improve the accuracy the result dramatically over the more primitive HF.  (It may help to add plots *without* HF.)
-
-[[TODO: add FCI, CCSD results to GS energy plots]]
 
@@
 In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.
-The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line \cite{PhysRevB.84.115302}.
+Results from diffusion Monte Carlo (DMC) \cite{hoegberget2013thesis} are shown as a dashed line for comparison.
 
@@
 the figure labels are somewhat misleading too]].
-The DMC results are also shown via dashed lines where they are known.
+Results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line, where available.
 

### 2017-02-26 Datafiles/plot_predictiveness.py

@@ -179,6 +179,14 @@ def parse_bin(s):
 def parse_binned_groups(stream):
     return ((parse_bin(k), v) for k, v in stream)
 
+def is_good(d_good, r):
+    key = r["interaction"], r["label"], r["freq"], r["num_filled"], r["method"]
+    try:
+        return d_good.loc[key]["good"]
+    except KeyError:
+        # unknown: default to False
+        return False
+
 def plot(fit_count=5, log=False, maxfev=0, plot_type="scatter",
          stat="err", hf=False):
     dorig = utils.filter_preferred_ml(utils.load_all())
@@ -203,9 +211,7 @@ def plot(fit_count=5, log=False, maxfev=0, plot_type="scatter",
     d["rel_constant_err"] = d["constant_err"] / d["constant"]
     d["rel_best_constant_err"] = d["best_constant_err"] / d["best_constant"]
     d["label_is_ground"] = d["label"] == "ground"
-    d["good"] = d.apply(lambda r: d_good.loc[
-        (r["interaction"], r["label"], r["freq"],
-         r["num_filled"], r["method"])]["good"], axis=1)
+    d["good"] = d.apply(functools.partial(is_good, d_good), axis=1)
     d["rel_chi"] = d["chisq"]**.5 / d["constant"]
     d["rel_reduced_chi"] = d["rel_chi"] / (fit_count - 3)
     d["rel_best_chisq"] = d["best_chisq"]**.5 / d["best_constant"]

### 2017-02-26 Datafiles/tabulate.py

@@ -1,16 +1,33 @@
 #!/usr/bin/env python3
-import itertools, os, sys
+import itertools, math, os, sys
 import numpy as np
 import pandas as pd
 import utils
 
+NUM_SHELLS = [12, 15, 15, 15, 20, 20]
+
+# known cases of IM-SRG that don't converge
+KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [
+    (20, 7, 0.1),
+])
+
+def render_entry(value, err=None, default_precision=5):
+    if isinstance(value, str):
+        return "{" + value + "}"
+    if np.isnan(value):
+        return ""
+    if err is None:
+        return "{{:.{}f}}".format(default_precision).format(value)
+    if np.isnan(err):
+        return "{{:.{}f}}{{{{(?)}}}}".format(default_precision).format(value)
+    return utils.render_with_err(value, err)
+
 def save_table(path, label,
-               num_shells=[15, 15, 15, 15, 15, 20],
+               num_shells=NUM_SHELLS,
                num_particles=[6, 12, 20, 30, 42, 56],
                freqs=[0.1, 0.28, 1.0]):
     d = utils.load_all()
     d = utils.filter_preferred_ml(d)
-    print(d["method"].unique())
     del d["ml"]
     d = d[d["interaction"] == "normal"]
     del d["interaction"]
@@ -18,7 +35,6 @@ def save_table(path, label,
     del d["label"]
     del d["num_filled"]
     d = d.set_index(["num_shells", "num_particles", "freq", "method"])
-    d = d.unstack("method")
 
     if label == "ground":
         methods = ["hf", "mp2", "imsrg", "ccsd"]
@@ -35,26 +51,132 @@ def save_table(path, label,
         {$N$} & {$\omega$} & {$K$} & {HF} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
         {} & {} & {} & {+QDPT3} & {+QDPT3} & {+EOM} & {+EOM} \\
         """
-    d = d.reindex_axis(methods, level=-1, axis=1)
-    d.columns = d.columns.droplevel(level=0)
+    c = d["energy"]
 
-    out_file = open(path, "w")
-    out_file.write(header)
+    s = []
+    s.append(header)
     for num_shells, num_particles in zip(num_shells, num_particles):
-        out_file.write("\\midrule\n")
+        s.append("\\midrule\n")
         for freq in freqs:
-            row = []
-            row.extend([num_particles, freq, num_shells])
[…]

### 2017-02-26 Datafiles/utils.py

@@ -1,5 +1,5 @@
 import argparse, base64, collections, contextlib, decimal
-import functools, hashlib, io, json, logging, os, pickle, re, sys
+import functools, hashlib, io, json, logging, math, os, pickle, re, sys
 import matplotlib
 import matplotlib.pyplot as plt
 import numpy as np
@@ -251,6 +251,38 @@ def intersperse(sep, xs):
             yield sep
         yield x
 
+
+def num_dec_digits(x):
+    x = abs(x)
+    e = int(math.log10(x))
+    if 10 ** e > x: # prevent overshooting due to round off errors
+        e -= 1
+    assert 10 ** e <= x < 10 ** (e + 1)
+    return e
+
+def render_with_err(value, err, digits=1):
+    if err <= 0.0:
+        raise Exception("uncertainty must be positive")
+    if not (math.isfinite(value) and math.isfinite(err)):
+        raise Exception("value and err must be finite")
+    e_err = num_dec_digits(err)
+    modified_err = int(round(err * 10.0 ** -e_err))
+    if modified_err == 10:
+        modified_err = 1
+        e_err -= 1
+    if e_err > 0:
+        e_value = num_dec_digits(value)
+        e_diff = e_value - e_err
+        if e_diff >= 0:
+            s = "{{:.{}e}}".format(e_diff).format(value)
+            return s.replace("e", "({})e".format(modified_err))
+        else:
+            return "{}0({})e{}".format("" if value >= 0.0 else "-",
+                                       modified_err, e_err)
+    else:
+        s = "{{:.{}f}}({{}})".format(-e_err)
+        return s.format(value, modified_err)
+
 def load_json_records(fn):
     with open(fn) as f:
         return pd.DataFrame.from_records([
@@ -389,7 +421,7 @@ def load_table(f, sep=r"\s+", names=None, skiprows=0):
     return pd.read_csv(f, **kwargs)
 
 def save_table(f, df):
-    df.to_csv(f, sep=" ", index=False)
+    df.to_csv(f, sep=" ", index=False, na_rep="nan")
 
 def parse_nathan_like_data(d, label):
     if label == "add":

### 2017-04-06 Manuscript/paper.tex
Update paper and figures

@@
-\input{head_plain.tex}
+\input{head_revtex.tex}
 \usepackage{amsmath}
@@
 \begin{document}
-\title{Studies of quantum dots}
+\title{Addition and removal energies of circular quantum dots}
 
@@
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
-\author{J\o rgen H\o gberget}
-\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}
 \author{Sam Novario}
@@
 \begin{abstract}
-  We present and compare several many-body methods used to study a quantum dot system.
-We calculate the approximate ground state energy of electrons in a circularly symmetric potential well using a harmonic oscillator basis optimized via Hartree-Fock (HF).
-We further improve the ground state energy using in-medium similarity renormalization group (IM-SRG).
-Additionally, we calculate the addition and removal energies using quasidegenerate perturbation theory (QDPT).
-Our results are benchmarked against quasi-exact diffusion Monte Carlo (DMC) and coupled cluster (CC) calculations.
+  We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
+We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using one of two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
+With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
+Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
+We examine the rate of convergence and perform extrapolations to the infinite basis limit using a power-law model.
 \end{abstract}
@@
 
-Understanding the behavior of strongly confined electrons is of fundamental
-interest for solving many-body problems.  Quantum dots, e.g. electrons
-confined in semiconducting heterostructures, are of particular interest since
-they exhibit, due to their small size, discrete quantum levels.  Under these
-conditions, typical quantum phenomena like tunneling, entanglement and
-magnetization can all be observed \cite{reimann2002,engel1993}.  Since quantum
-dots are manufactured and designed artificially at the laboratory, their
-quantum levels can be arbitrarily tuned by changing the external field or the
-size and shape of the system.  As a consequence, quantum dots provide a high
-level of control for the dynamics and correlation of the electrons, which
-makes them perfectly suited to study quantum effects in practice.  Since their
-ground state shows similar shell structures and magic numbers as seen for
-atoms and nuclei \cite{tarucha1996}, these systems give the opportunity to
-study electronic systems without the presence of a nucleus affecting the
-electrons.  Apart from their relevance for theoretical research in quantum
-physics, quantum dots offer a wide variety of applications: In particular,
-their electrical and optical properties make them attractive for the use in
-laser technology \cite{strauf2010,5075760} and solar cells
-\cite{jenks:013111,doi:10.1021/cr900289f}, but they are also used in quantum
-computers\cite{PhysRevA.57.120} and medical imaging \cite{Ben-Ari02042003}.
-
-In order to properly understand the properties of quantum dots and make
-theoretical predictions of their behavior in various applications, it is
-necessary to study features like ground state energy and correlation
-effects. Since there generally does not exist an analytical solution for
-quantum dots except for ones containing only two electrons or with specific
-values of the external field \cite{PhysRevA.48.3561}, the development of
-appropriate numerical few- and many-body methods is required to solve the
-problem.
-
-Several \textit{ab initio} methods have been applied to these systems, in
-particular variational and diffusion Monte Carlo (VMC and DMC)
-\cite{PhysRevB.68.035304,%
-  PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}, large-scale
-diagonalization/full configuration interaction (FCI)
-\cite{JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} and coupled
-cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,%
-  PhysRevB.84.115302}.
-
-Additionally to those approaches, another very promising first-principles
-method has recently been developed.  The similarity renormalization group
-(SRG) is a family of methods that drives the Hamiltonian toward a band- or
-block-diagonal form through a continuous sequence of unitary transformations,
-reducing the coupling between a subspace of interest -- such as the ground
-state -- and the remaining Hilbert space.  It has successfully been applied to
-study systems with different underlying potentials and to analyse their
-binding energy and other observables, especially in nuclear theory
-\cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.  Aside from usual
-\emph{free-space} SRG, where the Hamiltonian is constructed with respect to
-the vacuum state with no physical particles, it is possible to evolve a
-Hamiltonian via SRG \emph{in medium} through the normal-ordering technique,
-which enables the Hamiltonian to be constructed with respect to some reference
-state containing a finite number of particles.  In-medium SRG (IM-SRG) can
-further take advantage of the normal-ordering process to account for 3-body
-forces in an approximate manner without resorting to the full, computationally
-intensive 3-body machinery.  The method allows considerable simplifications to
-the problem and makes numerical calculations much more efficient \cite{IMSRG}.
-
-This article is organized as follows: Section \ref{sec:formalism} introduces
-first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular
-quantum dots, and gives afterwards an overview of the IM-SRG
-(\ref{subsec:imsrgmethod}) and DMC (\ref{subsec:DMC}) formalisms.  Our results are
-presented in Section \ref{sec:results}.  We point out the differences arising
-from the use of two different generators (Wegner and White generator), and
-give an overview of the ground state energies up to 42 particles. In
-particular, we compare the results obtained with five different \textit{ab
-  initio} methods: IM-SRG(2), DMC, Hartree-Fock, FCI and CC. Section
-\ref{sec:conclusions} concludes our work and gives perspectives for future
-work.
-
-The harmonic oscillator (HO) is a ubiquitous system in quantum physics.
-It is the basis for an extremely diverse set of many-body calculations -- in nuclear physics \cite{HJORTHJENSEN1995125}, quantum chemistry \cite{helgaker2000molecular}, and quantum dot calculations of solid state physics \cite{reimann2002}.
-In these calculations, one typically seeks a few of the lowest eigenvalues $E_k$ and eigenvectors of a many-body Hamiltonian $\hat{H}$ that describes the full system by solving the Schr\"odinger equation,
-\begin{equation*}
-\hat{H} \ket{\psi_k} = E_k \ket{\psi_k}, \quad k \in \{1, 2, \ldots, k_{\text{max}}\}.
-\end{equation*}
-In all cases, the many-body wave function is expanded in a basis of
-eigenstates of the one-body HO system.  Necessarily, in order to perform
-numerical calculations the basis must be truncated to give an approximation.
-In particular, the so-called ``curse of dimensionality'' implies that for a
-system with many particles the number of available degrees of freedom per
-particle is severely limited by the finiteness of a computer.
-
-[[This paragraph seems to be talking about a different paper]]
-It is clear, that an understanding of the properties of such expansions,
-giving \emph{a priori} error estimates on many-body calculations, is very
-important. Unfortunately, this is a neglected topic in the physics
-literature. In this article, we give a thorough mathematical and numerical
-analysis and give practical convergence estimates of HO basis expansions. It
-generalizes and refines the findings of a recent study of one-dimensional
-systems.\cite{Kvaal2007}
-
-The HO eigenfunctions are popular for several reasons.
-Many quantum systems, such as the quantum dot model considered here, can be considered perturbed harmonic oscillators \textit{per se}, thus the true eigenstates should be perturbations of the HO eigenstates.
-Moreover, the HO has many beautiful properties, such as separability, invariance under orthogonal coordinate changes, and easily computable eigenfunctions, so that computing matrix elements of relevant operators becomes relatively simple.
-Since HO eigenfunctions are defined on the \emph{entire} space in which particles live, a truncation of the spatial domain is unnecessary.
-This avoids one of the main problems with approaches such as finite difference or finite element methods.\cite{ram2002finite} [[Unknown citation]]
+The behavior of strongly confined electrons is of fundamental concern to many-body theory.
+The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificial constructed semiconducting heterostructures.
+Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
+Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
+This allows experiments to quantify the impact of quantum effects at different levels of correlation.
+
+The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
+Thus, this provides a rare opportunity to study electronic systems without the influence of the atomic nuclei.
+They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops.
+
+Beyond their theoretical relevance, there are numerous potential applications quantum dots.
+The electrical and optical properties of quantum dots are particularly useful for solar cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser technology \cite{strauf2010,5075760}.
+They are have potential medical applications in diagnosis and treatment \cite{Ben-Ari02042003}.
+And of course, quantum dots are also promising candidates for the physical realization of quantum computing\cite{PhysRevA.57.120}.
+
+In general, quantum dot systems are not analytically solvable, with the exception of 2-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
+Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
+
+One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuation interaction method.
+Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increases to infinity (the so-called \textit{infinite-basis limit}).
+Despite this significant advantage, it is often infeasible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
+This led to the development of more cost-effective methods that trade varying amounts of accuracy for varying amounts of speed.
+
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MPPT), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
+We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results from existing literature.
+
+Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
+Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
+The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
+It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
+The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
+The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
+
+The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
+Our results are presented in Section \ref{sec:results}.
+We analyze and compare the differences between the various methods and also between different quantum dot systems.
+We examine the usefulness extrapolation techniques in improving the precision of the results.
+Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
 
@@
 With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
-For rest of this paper, we shall use atomic units\footnote{Here, ``atomic unit'' is used in an \emph{abstract} sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$ correspond to true values in vacuum, or some effective value in medium.} where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ all have a value of one.
+For rest of this paper, we shall use atomic units\footnote{Here, ``atomic unit'' is used in an \emph{abstract} sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$ correspond to true values in vacuum, or some effective value in medium.} where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
 Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
@@
 
-The behavior of each electron in isolation is described by the kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
+The behavior of each electron in isolation is described by the nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
 \begin{align*}
@@
 Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
-The $n$ quantum number increases upward vertically, starting at zero for the lowest state within a each column.}
+The $n$ quantum number increases upward vertically, starting at zero for the lowest state within each column.}
   \label{fig:shell-structure}
@@
 where $p$ is an unknown tuple of quantum numbers.
-The two-dimensional harmonic oscillator Hamiltonian $\hat{h}$ has well known analytic solutions in Cartesian coordinates, but for our purposes, we prefer to use the Fock-Darwin states, which favor a representation in polar coordinates $\bm{r} = (\rho, \varphi)$ and have the useful property of conserving the orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
+In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
+However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
 
@@
 \end{align}
-where $L_n^{(m)}$ denotes the generalized Laguerre polynomial of degree $n$ and parameter $m$,
-\begin{align*}
-  L_n^{(m)}(u) = \frac{1}{n!} u^{-m} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{m + n})
-\end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, \ldots\}$ and the orbital angular momentum projection $m_\ell \in \mathbb Z$, which is the eigenvalue of $\hat{L}_{\mathrm{z}}$.
+where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre polynomial \cite[\S 18.3]{NIST:DLMF} of degree $n$ and parameter $\alpha$,
+\begin{align*}
+  L_n^{(\alpha)}(u) = \frac{1}{n!} u^{-\alpha} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{\alpha + n})
+\end{align*}
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
+For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
 
 Since electrons are spin-$1/2$ fermions, they can occupy either of the two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
-The complete single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+Thus, every single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
 \begin{align} \label{eq:singleparticlestate}
-  \langle (\rho, \varphi) | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \chi_{m_{\mathrm{s}}}
-\end{align}
-where we have introduced the the spin projection $m_{\mathrm{s}} \in \bigl\{-1/2, +1/2\bigr\}$ as the third quantum number.
-
-The energy of the single-particle state $\phi_{n, m_\ell, m_{\mathrm{s}}}$ is given by
-\begin{align*}
+  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}
+\end{align}
+Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-1/2, +1/2\bigr\}$ as the third quantum number and $\delta_{p, q}$ to denote the Kronecker delta..
+
+The energy of the single-particle state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ is given by
+\begin{align} \label{eq:energysingleparticlestate}
   \varepsilon_{n, m_\ell, m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega
-\end{align*}
+\end{align}
 The energies are degenerate with respect to the spin projection $m_{\mathrm{s}}$ as our Hamiltonian $\hat{h}$ does not distinguish between them.
@@
 
-Going back to the many-body Hamiltonian $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation of the triplet $(n, m_\ell, m_{\mathrm{s}})$.
-It is important to emphasize that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
+Returning to the many-body Hamiltonian $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
+Note that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
 \begin{align*}
@@
 
-Currently, the Hamiltonian $\hat{H}$ is explicit in the number of particles $N$.
-The many-body machinery can be made agnostic to number of particles through the formalism of second quantization, similar to quantum field theory.
-The many-body Hilbert space is extended from states with only $N$ particles to states with every possible number of particles via the Fock space construction.
-Slater determinants can then rewritten as,
+Currently, the Hamiltonian $\hat{H}$ is defined for a fixed number of particles $N$.
+Through the formalism of second quantization, the many-body machinery can be made agnostic to number of particles, in analogy to quantum field theory.
+Instead of considering the Hilbert space for exactly $N$ particles, we combine every space with $N = 0, 1, 2, \ldots$ particles into a combined Hilbert space called the Fock space.
+To establish relationships between states with differing number of particles, we introduce the \textit{field operators} $\hat{a}_p^\dagger$ and $\hat{a}_p$ to increment and decrement the number of particles in a state, respectively.
+The linear operator $\hat{a}_p^\dagger$ is known as \textit{creation operator} for the single-particle state $p$.
+Its action on an arbitrary Slater determinant is defined as:
+\begin{align*}
+  \hat a_p^\dagger |p'_1, \ldots, p'_N\rangle =
+  |p, p'_1, \ldots, p'_N\rangle
+\end{align*}
+Informally, it is said to \textit{create} a particle in the state $p$.
+If $p$ coincides with any of the existing $p'_1, \ldots, p'_N$, then antisymmetrization would collapse the state to the number $0$, an invalid state.
+The Hermitian conjugate of $\hat{a}_p^\dagger$ is $\hat{a}_p$, which known as the \textit{annihilation operator} for the state $p$.
+By analogy, its action is to remove the state $p$ from a Slater determinant, or collapse it to the number $0$ if the state $p$ was not occupied in the Slater determinant.
+
+From here, one can show that Slater determinants themselves can be built directly from the the unique \textit{vacuum state} $|\rangle$ with no particles ($N = 0$):
 \begin{align*}
@@
 \end{align*}
-whre $|\rangle$ is the \textit{vacuum state} -- the unique state that is devoid of particles -- and $\hat{a_p}^\dagger$ denotes a \textit{creation operator} for the single-particle state $p$.
-If the single-particle state $p$ is not yet occupied by a particle, $\hat a_p^\dagger$ adds such a particle to the state.
-Otherwise, it collapses the entire many-body state to the number $0$ (not to be confused with the vacuum state $|\rangle$).
-The Hermitian conjugate of $\hat a_p^\dagger$ is \textit{annihilation operator} $\hat a_p$, which has the opposite effect of removing the particle if it exists, collapsing to zero otherwise.
-For fermions, the field operators $\hat a_p$ and $\hat a_p^\dagger$ satisfy the essential anticommutation relations,
+To properly describe fermions, the field operators $\hat a_p$ and $\hat a_p^\dagger$ must satisfy the anticommutation relations that encode the Pauli principle,
 \begin{align*}
@@
 \end{align*}
-where $\delta_{p, q}$ denotes the Kronecker delta.
-
-In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from \eqref{eq:onetwobodyhamiltonian} can be rewritten as\footnote{The reversed ordering of $\hat a_s \hat a_r$ here is completely intentional.}
+
+In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from \eqref{eq:onetwobodyhamiltonian} can be rewritten as\footnote{The peculiar ordering of $\hat a_s \hat a_r$ here is not a typographical error.}
 \begin{align} \label{eq:second_quantized_hamiltonian}
@@
 \end{align}
-where the numbers $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ are known as \textit{matrix elements}, whose values fully characterize the operators.
-In this paper, we use the letters $p, q, r, s, t, \ldots$ as labels for arbitrary single-particle basis states.
-In the harmonic oscillator basis, the letters can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
-A summation such as $\sum_p$ is to be understood as a summation over every single-particle basis state $p$.
-This is very different from \eqref{eq:onetwobodyhamiltonian}, where summations such as $\sum_j$ are performed over arbitrary particle \emph{labels}.
-We thus see another benefit with second quantization: the Hamiltonian representation does not distinguish particles at all, as it should be for quantum particles.
+where the numeric coefficients $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
+In this paper, we use the letters $p, q, r, s, t, \ldots$ to label arbitrary single-particle \textit{states} in the basis.
+For the harmonic oscillator basis, labels such as $p$ can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
+A summation such as $\sum_p$ is then understood as a summation over every single-particle basis state $p$.
+This is not to be confused with summations such as $\sum_j$ from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$ denoting an arbitrary \textit{particle}.
+We thus see another benefit with second quantization: the Hamiltonian representation makes no attempt to distinguish particles at all, as expected for particles with quantum statistics.
 
@@
 \begin{align}
-  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r \hat{a}_s  \label{eq:vacuumhamiltonian}
-\end{align}
-Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ causes $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ to reverse in sign, leading to a 4-fold symmetry that is canceled out by the factor of $1/4$.
+  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r  \label{eq:vacuumhamiltonian}
+\end{align}
+Due to antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p, q | \hat{H}^{[2]} | r, s \rangle$, leading to a 4-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
 For this reason, the two-body matrix element $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the non-antisymmetric interaction integral,
-\begin{align*}
-  v_{p_1, p_2, p_3, p_4} \equiv \int \langle \bm{r} | p_1 \rangle \langle \bm{r}' | p_2 \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'
-\end{align*}
-This object only has a 2-fold symmetry: $v_{p_1, p_2, p_3, p_4} = v_{p_2, p_1, p_4, p_3}$.  The antisymmetrized matrix element can be computed from the interaction integral via
-\begin{align*}
+This is not to be confused with the (non-antisymmetric) interaction integral,
+\begin{align} \label{eq:interactionintegral}
+  v_{p_1, p_2, p_3, p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'
+\end{align}
+This object only has a 2-fold symmetry: $v_{p_1, p_2, p_3, p_4} = v_{p_2, p_1, p_4, p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
+\begin{align} \label{eq:antisymmetricmatrixelement}
   \langle p, q | \hat{H}^{[2]} | r, s \rangle = v_{p, q, r, s} - v_{p, q, s, r}
-\end{align*}
-
-In our work, the interaction integrals $v_{p, q, r, s}$ were computed numerically using the algorithm presented in \cite{2008arXiv0810.2644K}, included as part of the OpenFCI program.
-The algorithm uses numerical quadrature to calculate the integrals exactly in the center-of-mass frame and then performs a transformation to obtain matrix elements in the laboratory frame.
-The numerical quadrature technique is much more numerically robust and efficient than using analytical formulas such as the one in \cite{0953-8984-10-3-013}.
-
-The use of second quantization allows the application of a powerful combinatoric theorem known as Wick's theorem \cite{shavitt2009many}, which provides systematic way to expand complicated expressions involving creation and annihilation operators.
-Ultimately, computations \textit{in silico} do not involve algebraic manipulation of abstract operators at all -- rather, they involve numerical calculations of \emph{matrix elements} via equations derived using Wick's theorem.
-
-With the basic formalism and notation established, we begin discussion of techniques to solve the full many-body Hamiltonian $\hat H$.
-The difficulty stems from the fact that the exact solution cannot be expressed in terms of a single Slater determinant due to the presence of interactions.
+\end{align}
+
+With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
+The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
 Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
 
-However, if we assume the interaction alters the behavior of the system to only a mild extent, we can use Slater determinants of the noninteracting system as starting points for the full solution, and then apply various many-body methods to improve the accuracy of the solution.
-
-\subsection{Hartree-Fock method}
+However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
+This is a general strategy for many of the many-body methods that we shall describe.
+
+\subsection{Hartree--Fock method}
 \label{subsec:HartreeFockmethod}
 
-One relatively simple correction that we can apply to our solution is that of the Hartree-Fock (HF) method.
-Using the variational principle, we compute an approximate ground state $\Phi$ by minimizing the energy expectation value
-\begin{align*}
+One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
+Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value
+\begin{align} \label{eq:hfexpectation}
   E_{\Phi} \equiv \langle \Phi | \hat H | \Phi \rangle
-\end{align*}
-with respect to $\Phi$, subject to the restriction that $\Phi$ is a single Slater determinant constructed from an unknown set of $N$ orthonormal single-particle states.
-We denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To make this computationally feasible, we further assume that each unknown state $|q'\rangle$ can be built from a linear combination of known states, $|p\rangle$ for all $p$.
-This reduces the problem from an abstract mathematical one to a numerical linear algebra problem, with the caveat that this set of known functions be large enough to ensure convergence.
-
-Assuming the interaction is not too strong, we can use the single-particle states of our noninteracting Hamiltonian as a basis for the unknown states.
-The two sets of states are then related by a linear transformation matrix $\bm C$:
-\begin{align*}
-  |q'\rangle = \sum_p |p\rangle C_{p, q'}
-\end{align*}
-To ensure the orthonormality of the states, we assume the set of unknown states $|q'\rangle$ has as many elements as the set of known states $|p\rangle$ and we require the coefficient matrix $\bm C$ to be unitary.
-While these conditions are more strict than necessary, they greatly simplify the calculations and allow the states $|q'\rangle$ to act as inputs for methods beyond HF.
-The set of states $|q'\rangle$ now consists of $N$ \textit{occupied} states that participate in the Slater determinant $\Phi$ and the remaining \textit{unoccupied} states that do not.
-
-Since the coefficient matrix uniquely determines the unknown states, the variational problem has been reduced to that of solving of the coefficients $\bm C$ that minimize the energy $E_{\Phi}$, which is given by
-\begin{align}
-  E_{\Phi} &= \sum_{j} n_j H^{[1] \prime}_{j, j} + \sum_{j, k} n_j n_k H^{[2] \prime}_{j, k, j, k} \label{eq:hfenergy}
+\end{align}
+with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
+The restriction is what enables the simplicity and efficiency of this method.
+We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
+\begin{align*}
+  |q'\rangle \equiv \sum_p |p\rangle C_{p, q'}
+\end{align*}
+The allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
+The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
+
+If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
+
+To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
+These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
+At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
+The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
+
+The goal then is to find the coefficients $\bm C$ that minimize the energy $E_{\Phi}$, now given by
+\begin{align}
+  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{i, i} + \sum_{i, j} n_i n_j H^{[2] \prime}_{i, j, i, j} \label{eq:hfenergy}
 \end{align}
@@
 \end{align}
-and the occupancy number $n_p$ is defined as
+and $n_p$ is the \textit{occupancy}, defined as
 \begin{align}
@@
 \end{align}
-and further define $\bar n_p \equiv 1 - n_p$ as the complement.
-
-With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree-Fock equation}:
+We will also use $\bar n_p \equiv 1 - n_p$ as a shorthand for the complement.
+
+With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree--Fock equation}:
 \begin{align} \label{eq:hartreefock}
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r, s, j} n_j C_{r, j}^* \langle p, r | \hat{H}^{[2]} | q, s \rangle C_{s, j}^{}
-\end{align}
-and $\bm{\varepsilon}$ is a vector of Lagrange multipliers with each element $\varepsilon_{q'}$ associated with a particular state $|q'\rangle$.
-
-The HF equation can be solved iteratively: given a guess for the solution $\bm{C}$, it can be fed into \eqref{eq:fock} and new potential solution may be obtained by solving the eigenvalue problem in \eqref{eq:hartreefock} with the Fock matrix obtained from $\bm{C}$.
-While in theory it is possible for the solution to never reach a fixed point, or that it may require a large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
-In cases where it is insufficient, methods such as DIIS, Broyden's method, or even linear mixing can accelerate convergence greatly to the point where the possibility of nonconvergence is not a practical concern.
-
-For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}$ is initially the identity matrix.
-At each iteration, we calculate the sum of the Lagrange multiplers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration will decrease rapidly.
-
-Since HF restricts the ground state to a Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
-The energy difference between the best Hartree-Fock energy and the exact ground state energy is thus known as the \textit{correlation energy} (by definition).
-The focus of post-HF methods such as IM-SRG or coupled cluster is to improve on the HF results, recovering parts of this missing energy.
+  F_{p, q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r, s, i} n_i C_{r, i}^* \langle p, r | \hat{H}^{[2]} | q, s \rangle C_{s, i}^{}
+\end{align}
+and $\bm{\varepsilon}$ is a vector of Lagrange multipliers: each element $\varepsilon_{q'}$ is associated with a specific single-particle state $|q'\rangle$.
+
+Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
+We begin with an initial guess $\bm{C}^{(i)}$, which is fed into \eqref{eq:fock} to produce the Fock matrix.
+This is then used in \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
+This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
+While in theory it is possible for the solution to never reach a fixed point, or that it may require a unfeasibly large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
+In other cases where it is insufficient, methods such as DIIS, Broyden's method, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
+Therefore, the possibility of slow or non-convergence is generally not a concern in practice.
+
+For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity matrix.
+At each iteration, we calculate the sum of the Lagrange multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration should decrease rapidly.
+
+Since HF restricts the ground state to merely a single Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
+The discrepancy between the Hartree--Fock energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
+The focus of post-HF methods such as IM-SRG or coupled cluster is to add corrections beyond mean-field approximations such as HF.
 
@@
 Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
-However, for generality, we omit the prime symbols as the methods do not necessitate a state optimized by HF.
+However, we will not annotate them with the prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
 
@@
 
-\subsubsection{Similarity renormalization group methods}
+\subsubsection{Similarity renormalization group in free space}
 \label{subsubsec:srgmethods}
 
-In similarity renormalization group (SRG) methods, one performs a continuous
-sequence of unitary transformations on a Hamiltonian operator $\hat H$ to
-evolve it into a band- or block-diagonal form, reducing the coupling between a
-small model space of interest from its complementary space.  This allows the
-Hilbert space to be truncated to the small model space without losing
-significant accuracy.
-
-The sequence of transformations is parameterized by a continuous variable $s$
-known as the \textit{flow parameter}.  By convention we define to be $0$ at
-the beginning of the sequence, and thus the evolving Hamiltonian $\hat H(s)$
-at $s = 0$ is set to the original Hamiltonian.  Upon reaching $s$, the
-transformed Hamiltonian is given by
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form.
+This allows the decoupling of a small, designated \textit{model space} from its larger complementary space.
+The problem can thus be truncated to the small model space while preserving a large amount of information about the system.
+
+The sequence of transformations is parameterized by a continuous variable $s$ known as the \textit{flow parameter}.
+Without loss of generality, we can define $s = 0$ to be the beginning of this sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.
+At any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to the original Hamiltonian by
 \begin{align*}
@@
 If we define an operator $\hat{\eta}(s)$ as
-\begin{align*}
+\begin{align} \label{eq:etadefinition}
   \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s)
-\end{align*}
+\end{align}
 we find that it is antihermitian as a result of the unitarity of $\hat{U}(s)$:
@@
 \end{align*}
-From this property we can derive a differential equation known as the
-\textit{SRG flow equation}:
+From this property we can derive a differential equation known as the \textit{SRG flow equation}:
 \begin{align} \label{eq:imsrgode}
@@
 \end{align}
-The equation allows $\hat{H}(s)$ to be evaluated without explicitly
-constructing the full transformation $\hat U(s)$.  The operator $\hat \eta(s)$
-is known as the \textit{generator} of the transformation.  When ``integrated''
-as a product, the full transformation $\hat U(s)$ is recovered.  Formally,
-\begin{align*}
+The equation allows $\hat{H}(s)$ to be evaluated without explicitly constructing the full transformation $\hat U(s)$.
+The focus is instead shifted to the operator $\hat \eta(s)$, the \textit{generator} of the transformation.
+When $\hat \eta(s)$ is \emph{multiplicatively} integrated (\textit{product integral}), the full unitary transformation $\hat U(s)$ is recovered:
+\begin{align} \label{eq:etaintegral}
   \hat U(s')
-  = \mathcal{T}_s \mathrm{e}^{\int_0^{s'} \hat{\eta}(s) \D s}
-  \equiv \lim_{\Delta s \to 0}\left(\mathrm{e}^{\hat{\eta}(s_n) \Delta s} \mathrm{e}^{\hat{\eta}(s_{n - 1}) \Delta s} \cdots \mathrm{e}^{\hat{\eta}(s_1) \Delta s}\right)
-\end{align*}
+  = \lim_{\Delta s \to 0} \prod_{i = 1}^n \mathrm{e}^{\hat{\eta}(s_i) \Delta s}
+\end{align}
 where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
-The symbol $\mathcal{T}_s \mathrm{e}$ is a notational device to indicate \textit{$s$-ordering} of its contents: every product of $\hat{\eta}(s)$ expanded from the exponential are to be reordered in descending order with respect to $s$ \cite[\S 6.1]{reimann2013quantum}.
-This is analogous to the time-ordering notation from quantum field theory.
-
-The operator $\hat{\eta}$ can be chosen to suppress certain undesirable parts of the Hamiltonian matrix, which can be considered the ``off-diagonal'' parts in a loose sense.
+This is the formal solution to the linear differential equation \ref{eq:etadefinition}.
+The product integral in \ref{eq:etaintegral} may also be reinterpreted as \textit{$s$-ordering} \cite[\S 6.1]{reimann2013quantum} in analogy to time-ordering from quantum field theory.
+
+The power of SRG methods lies in the flexibility of the generator $\hat{\eta}$, which is usually chosen in an $s$-dependent manner.
+In particular, it is often dependent on the evolving Hamiltonian $\hat{H}(s)$.
+The operator $\hat{\eta}$ determines which parts of the Hamiltonian matrix would become suppressed by the evolution, which are usually considered ``off-diagonal'' in an abstract sense.
 The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
@@
 The SRG flow equation \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
-However, since the size of the problem grows enormously with the number of particles and the size of the model space, the applicability of this free-space SRG method is restricted to comparatively small systems.
-Alternatively, the evolution can be done at finite density, i.e.\ directly in an $N$-particle system defined by a reference state \cite{kehrein2006flow}.
+However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
+A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
 This gives rise to the IM-SRG method.
 
-The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have a vacuum expectation value of zero:
+The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
 \begin{align*}
@@
 \end{align*}
-The quasiparticle field operators treat the \textit{reference state} $\ket{\Phi}$ as their ``vacuum'' state (sometimes called a \textit{Fermi vaccuum}), even though it is not the true \emph{physical} vacuum state.
+The quasiparticle field operators treat the \textit{reference state} $\ket{\Phi}$ as their ``vacuum'' state (\textit{Fermi vaccuum}), even though it is not the true \emph{physical} vacuum state.
 As before, it is possible to construct arbitrary Slater determinants by applying quasiparticle operators to the reference state:
@@
 The set of labels $\{p_1, \ldots, p_k\}$ may contain up to $N$ hole states and as many particle states as the basis allows for (minus the ones that are already hole states).
-One classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
+One can classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
 If $N_{\text{p}} = N_{\text{h}}$, the Slater determinant contains the same number of physical particles as the reference state.
@@
 \begin{align}
-  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_r^{} \hat{a}_s^{}}
+  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}}
   \label{eq:normordhamiltonian}
@@
 If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p, q}$ is the Fock matrix $F_{p, q}$.
-The normal-ordered representation of $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to that of $\hat H$ in \eqref{eq:vacuumhamiltonian}.
-The only difference is that it rearranges the matrix elements so as to emphasize the reference state $\Phi$ rather than vacuum state $\ket{}$.
-This makes a critical difference when the expressions containing 3-body or higher terms are \emph{truncated} to only 2-body.
-If the reference state $\Phi$ is good approximation of the true solution $\Psi$, then the importance of the higher-body parts of the Hamiltonian are greatly reduced.
+The operator $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in \eqref{eq:vacuumhamiltonian}.
+The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
+Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
+Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
 
@@
 With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
-Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy is of interest.
-
-Computationally, higher-body terms are difficult to handle: the amount of memory required to store an $r$-body operator is grows exponentially with $r$.
+Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy (zero-body component) is of interest.
+
+Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
 Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
-Thus, to make the method tractable, we must close the IM-SRG flow equations, truncating the equations to a finite order.
-
-In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, an approach known as IM-SRG(2).
+Thus, to make the method tractable, the IM-SRG flow equations must be closed by truncating the equations to a finite order.
+
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
 This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
 
-Note that the loss of three-body and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
-The other source of error is due to the \textit{basis truncation}, as with any method that relies on a finite single-particle basis.
-The latter can be reduced by increasing the size of the basis at the expense of greater computational effort.
-
-With the operator truncation, the generator $\hat{\eta}$ can be written as a generic antihermitian 2-body operator:
+Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
+The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
+The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
+In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
+For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
+
+With the operator truncation, the generator $\hat{\eta}$ can be written as a generic 2-body operator:
 \begin{align*}
@@
 \end{align*}
-where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$.
-
-By expanding the commutator in \eqref{eq:imsrgode} without consideration of the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
-\begin{align}
-    \frac{\D H^{[r]}}{\D s} = C^{[r]}(\eta, H) \label{eq:flowmxe}
+where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$, subject to the antihermittivity constraint.
+
+By expanding the commutator in \eqref{eq:imsrgode} and discarding the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
+\begin{align}
+    \frac{\D H^{[k]}}{\D s} = C^{[k]}(\eta, H) \label{eq:flowmxe}
 \end{align}
@@
 \begin{align}
-  C^{[r]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
+  C^{[k]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[k]}(A, B) \text{ for any $k$, $A$, $B$} \label{eq:commutmxe} \\
   \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$}
 \end{align}
-and finally
 \begin{align}
@@
     \sum_{i, a} n_i \bar{n}_a A^{[2]}_{i, p, a, r} B^{[2]}_{a, q, i, s}
+    \notag \\
+  &\hphantom{=}
     + \frac{1}{2} \sum_{i, j} n_i n_j A^{[2]}_{i, j, r, s} B^{[2]}_{p, q, i, j}
@@
 \end{align}
+
 \begin{figure}
 \includegraphics[width=.48\linewidth]{fig-diagrams-imsrg}
-\caption{Diagrammatic representation of $C^{[r]}(\circ, \bullet)$ in \eqref{eq:commutmxe} that forms part of the IM-SRG flow equation \eqref{eq:flowmxe}.
-The diagrams are implicitly antisymmetrized (Hugenholtz diagrams \cite{HUGENHOLTZ1957481} as described in \cite{shavitt2009many} \S 4.4.3).}
+\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
+The two-body vertices are implicitly antisymmetric (i.e.\ \textit{Hugenholtz diagrams} \cite{HUGENHOLTZ1957481}, as described in \cite{shavitt2009many} \S 4.4.3).
+Internal directed lines (bound/dummy indices) that point upward denote summations over unoccupied states, whereas lines that point downward denote summations over occupied states.
+External undirected lines denote unconstrained free indices.}
 \label{fig:diagrams-imsrg}
 \end{figure}
-The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem [[ref]] or, even more efficiently, diagrammatic techniques [[ref]] to arrive at the results.
-In particular, the diagrammatic representation of antisymmetrized matrix elements are shown in Figure \ref{fig:diagrams-imsrg}.
+
+The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
+In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}.
+
+The commutator in the flow equations \eqref{eq:imsrgode} ensures that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked diagrams} only \cite{shavitt2009many}.
+This indicates that IM-SRG is a size-extensive \cite{ISI:A1981MN73700014} method by construction, even if the operators are truncated.
 
 An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
-In particular, the solver must be able to handle the stiffness that can often arise (even in the case of White generator, which is designed to avoid some of the stiffness).
+In particular, the solver must be capable of handling the stiffness that often arises in such problems.
 For our numerical experiments, we used a high-order ODE solver algorithm by L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which is a multistep method based on the implicit Adams predictor-corrector formulas.
@@
 If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
-In particular, $H^{[0]}$ would approach the true ground state energy.
-
-The commutator in the flow equations \eqref{eq:imsrgode} indicates that the evolved state $\hat U(s) \ket{\Phi}$ can be expanded in terms of \emph{linked diagrams} only \cite{shavitt2009many,ISI:A1981MN73700014}, which ensures the size-extensive property of IM-SRG by construction.
-This holds even if the commutator is truncated.
-Regarding the quality of the SRG results, this indicates that the error introduced by truncating the many-body expansions scales linearly with the number of particles $N$.
-
-\subsubsection{Wegner's canonical generator}
-\label{subsec:Wegner}
-
-To determine the specific unitary transformation, one needs to specify the generator $\hat{\eta}$.  Through different choices, the SRG flow can be adapted to the features of a particular problem.
-
-The original choice suggested by Wegner \cite{Wegner200177} reads
-\begin{equation}
+In particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
+
+The original choice of generator suggested by Wegner \cite{Wegner200177} reads
+\begin{align*}
   \hat{\eta}^{\text{Wg}}
@@
   = [\hat{H}^{\text{d}}, \hat{H}]
-  \label{eq:etaWegner}
-\end{equation}
-where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the Hamiltonian (and $\hat{H} - \hat{H}^{\text{d}}$ denotes the ``off-diagonal'' part) in the abstract sense described at the end of section \ref{subsubsec:srgmethods}.
-
-Since $\hat{\eta}^{\text{Wg}}$ is the commutator between two Hermitian operators, it is antihermitian as required for a generator.
+\end{align*}
+where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the Hamiltonian and $\hat{H} - \hat{H}^{\text{d}}$ denotes the ``off-diagonal'' part.
+This is in the abstract sense described at the end of Section \ref{subsubsec:srgmethods}.
+
+Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian operators, it is antihermitian as required for a generator.
 Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
-In particular, matrix elements far off the diagonal, where the Hamiltonian couples states with large energy differences, are suppressed much faster than elements closer to the diagonal.
-
-The matrix elements of the generator can be evaluated using \eqref{eq:commutmxe} to \eqref{eq:flow2}.  If define $\hat{H}^{\text{d}}$ via
-\begin{align*}
-  H^{\text{d}, [1]}_{p, q} &\equiv \delta_{p, q} H^{[1]}_{p, p} \\
-  H^{\text{d}, [2]}_{p, q, r, s} &\equiv (\delta_{p, r} \delta_{q, s} - \delta_{p, s} \delta_{q, r}) H^{[2]}_{p, q, p, q}
-\end{align*}
-then the expressions for $\hat{\eta}^{\text{Wg}}$ can be simplified considerably:
-\begin{align*}
-  \eta^{\text{Wg},[0]} &= 0 \\
-  \eta^{\text{Wg},[1]}_{p, q} &= 2 H^{[1]}_{p, q} \mathcal{A}_{p, q} \bigl( H^{[1]}_{p, p} + n_p H^{[2]}_{p, q, p, q} \bigr) \\
-  \eta^{\text{Wg},[2]}_{p, q, r, s} &= 2 \mathcal{A}_{p, q} \mathcal{A}_{r, s} \Big( \\
-  &\qquad H^{[2]}_{p, q, r, s} \mathcal{A}_{(p, q), (r, s)} \Bigl(\\
-  &\qquad \qquad 2 H^{[1]}_{p, p} + 4 n_p H^{[2]}_{p, r, p, r} \\
-  &\qquad \qquad + (1 - 2 n_p) H^{[2]}_{p, q, p, q} \Bigr) \\
-  &\qquad + 4 \delta_{p, r} H^{[1]}_{q, s} \mathcal{A}_{(p, q), (r, s)} H^{[2]}_{p, q, p, q}
-  \Bigr)
-\end{align*}
-where for any $x$, $y$, $z$, $w$, $f$ we define the antisymmetrizer
-\begin{align*}
-  \mathcal{A}_{(x, y), (z, w)} f(x, y, z, w) &\equiv \frac{1}{2} \bigl(f(x, y, z, w) - f(z, w, x, y)\bigr)
-\end{align*}
-
-\subsubsection{White generator}
-\label{subsec:White}
-
-Apart from Wegner's choice of the generator, there exist several other ones in literature.
+Matrix elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian couples states with large energy differences -- are suppressed much faster than those ``close'' to the diagonal.
+
+Apart from Wegner's generator, there exist several other ones in literature.
 One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
@@
 
-White takes an alternative approach, which is especially suited for problems where one is interested in the ground state of a system.
-Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, he focuses solely on those ones that are connected to the reference state $\Phi$, aiming to decouple the reference state from the remaining Hamiltonian.
-This reduces the amount of change performed on the Hamiltonian, which can reduce the accuracy loss resulting from the truncated higher-body terms.
+The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
+Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
+This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
 Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
-This reduces the stiffness of the flow equations.
-
-The generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}
+This ensures that the affected elements decay at approximately the same rate, reducing the stiffness of the flow equations.
+
+The White generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}.  Let
 \begin{align*}
@@
 \begin{align*}
-\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\Delta^{[1]}_{a, i}} &
-\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\Delta^{[2]}_{a, b, i, j}}
-\end{align*}
-and the denominators $\Delta^{[1]}$ and $\Delta^{[2]}$ are
-\begin{align*}
-\Delta^{[1]}_{a, i} &\equiv H^{[1]}_{a, a} - H^{[1]}_{i, i} - H^{[2]}_{a, i, a, i} \\
-\Delta^{[2]}_{a, b, i, j} &\equiv H^{[1]}_{a, a} + H^{[1]}_{b, b} - H^{[1]}_{i, i} - H^{[1]}_{j, j} + X_{a, b, i, j} \\
-X_{a, b, i, j}
+\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\tilde{\Delta}^{[1]}_{a, i}} &
+\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\tilde{\Delta}^{[2]}_{a, b, i, j}}
+\end{align*}
+and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as
+\begin{align}
+\tilde{\Delta}^{[1]}_{a, i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a, i, a, i} \notag \\
+\tilde{\Delta}^{[2]}_{a, b, i, j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a, b, i, j} \notag \\
+\Delta^{[2]}_{P_1, P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1, p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2, p_2} \label{eq:moellerplessetdenominator} \\
+w_{a, b, i, j}
   &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
-  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j}
-\end{align*}
-These are the Epstein--Nesbet denominators.
-Some literature use M\o eller--Plesset denominators, which omit the $X_{a, b, i, j}$ term, leading to a slightly different variant of the canonical White generator.
-
-Compared to the Wegner generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.
-This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.
+  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j} \notag
+\end{align}
+Some literature use the M\o eller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.
+
+Compared to the Wegner generator, where the derivatives of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.
+This reduces the stiffness in the differential equation, providing a net increase in computational efficiency as stiff ODE solvers tend to be slower and consume more memory.
 
@@
 This works well for closed-shell systems, but it does not provide a direct means to obtain the ground state energy of open-shell systems.
-While there exists more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use the simpler quasidegenerate perturbation theory (QDPT), which provides us with a simple approach to extract ground state energies of open-shell systems that are only a few particles removed from a closed-shell system.
-In particular, it allows us to calculate \textit{addition energies} $\epsilon_a$ and \textit{removal energies} $\epsilon_i$ of such systems, which we define as:
-\begin{align}
-  \epsilon_a &\equiv E_{\Phi_a} - E_{\Phi} \\
-  \epsilon_i &\equiv E_{\Phi} - E_{\Phi_i}
+While there exist more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use a perturbative approach, which is simple, inexpensive, and as we shall see in the results, quite effective for many problems.
+
+Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.
+This provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.
+In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
+\begin{align}
+  \varepsilon_a &\equiv E_{\Phi_a} - E_{\Phi} \\
+  \varepsilon_i &\equiv E_{\Phi} - E_{\Phi_i}
 \end{align}
@@
 
-In QDPT, the solutions of the approximate Hamiltonian $\hat{H}^{[1]}$ are used as the basis of the model space.
-One then assumes the existence of an operator $\hat \Omega$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
+In QDPT, solutions of an approximate one-body Hamiltonian $\hat{H}^{[1]}$ form the basis of the model space.
+One begins by assuming the existence of an operator $\hat{\Omega}$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
 \begin{align} \label{eq:omega-condition1}
@@
 \end{align}
-The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates
-$\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
-
-There is some freedom in the choice of the wave operator $\hat \Omega$.  We
-assume it has the following form:
+The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
+
+There is some freedom in the choice of the wave operator $\hat \Omega$.  We assume it has the following form:
 \begin{align} \label{eq:omega-condition2}
@@
 \end{align}
-where $\hat P$ projects any state into the model space and $\hat Q$ is the
-complement of $\hat P$.  This entails that the exact states $\Psi_u$ is no
-longer normalized but instead satisfies the typical intermediate
-normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
+where $\hat P$ projects any state into the model space and $\hat Q$ is the complement of $\hat P$.
+This entails that the exact states $\Psi_u$ is no longer normalized but instead satisfies the so-called intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
 
@@
 \end{align*}
-where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ is the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
-As is typical in perturbation theory, we assume $\hat \Omega$ can be expanded as a series of the increasing order as measured by the ``power'' of the perturbation $\hat V$:
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
+As is standard in perturbation theory, we now assume $\hat \Omega$ can be expanded as a series of terms of increasing order, as quantified by the power of the perturbation $\hat V$:
 \begin{align*}
   \hat \Omega = \hat P +
-  \hat Q\bigl(\hat \Omega_1 + \hat \Omega_2 + \cdots\bigr) \hat P
-\end{align*}
-This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$ to be calculated up to any order, as least in principle.  Up to third order, we have: [[double-check]]
-\begin{align*}
-  &\hat \Omega_1 \hat P_u = \hat R_u \hat V \hat P_u \\
-  &\hat \Omega_2 \hat P_u =
+  \hat Q\bigl(\hat \Omega^{(1)} + \hat \Omega^{(2)} + \cdots\bigr) \hat P
+\end{align*}
+This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$ to be calculated up to any order, as least in principle.  Up to third order, we have:
+\begin{align*}
+  &\hat \Omega^{(1)} \hat P_u = \hat R_u \hat V \hat P_u \\
+  &\hat \Omega^{(2)} \hat P_u =
     \hat R_u \biggl(
@@
     \biggr) \hat V \hat P_u \\
-  &\hat \Omega_3 \hat P_u =
+  &\hat \Omega^{(3)} \hat P_u =
     \hat R_u \biggl(
@@
 \end{align*}
-Until now, the solution is described purely in terms of abstract operators in Hilbert space.
-To make this concrete and relevant for many-body physics, we must make some additional assumptions.
-First, we make use of the single-particle basis as we have for HF and IM-SRG.
-Secondly, we assume the set of reference states $\Psi^{\mathrm{o}}_u$ are Slater determinants of the single-particle states.
 
@@
 
-Since for this paper we are interested in the addition and removal energies, which involve one particle more or one particle less than a closed-shell state, we can take the label $u$ to be simply the label of the state that is added or removed from the closed-shell state $\Phi$.
-With this realization, we can then express the perturbation expansion in terms of summations over matrix elements as we had done before for the IM-SRG flow equation, perhaps with the aid of Wick's theorem or diagrammatic techniques.
+To make the equations more concrete, we further assume that each reference state $\ket{\Psi^{\mathrm{o}}_u} \equiv \ket{\Phi_u}$, i.e.\ each reference state is simply a Slater determinant constructed by adding or removing a single particle $u$ to a closed-shell reference state $\Phi$, which itself may have been obtained earlier from HF and/or IM-SRG.
+Thus, the number of reference states for QDPT is equal to the number of particles in either the lowest unfilled shell or the highest filled shell of $\ket{\Phi}$, depending on whether we are considering addition or removal energies.
+
+We can then express the perturbation expansion in terms of summations over matrix elements as we had done before for the IM-SRG flow equation, again with the aid of Wick's theorem or diagrammatic techniques.
 This leads to the following expression for the second-order correction:
 \begin{align*}
-  \epsilon_p^{(2)}
+  \varepsilon_p^{(2)}
   &=
-  \frac{1}{2} \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{H^{[1]}_p + H^{[1]}_i - H^{[1]}_a - H^{[1]}_b} \\
-  &{}-
-  \frac{1}{2} \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{H^{[1]}_{i, i} + H^{[1]}_{j, j} - H^{[1]}_{p, p} - H^{[1]}_{a, a}}
-\end{align*}
-The expression is depicted in Figure \ref{fig:diagrams-sfe}.
-Since there are numerous terms in the third-order correction $\epsilon_p^{(3)}$, they are listed exclusively in a diagrammatic form in Figure \ref{fig:diagrams-sfe}.
+    \sum_{i, a, b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p, i, a, b}|^2}{2 \Delta_{\{p, i\}, \{a, b\}}}
+    - \sum_{i, j, a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i, j, p, a}|^2}{2 \Delta_{\{i, j\}, \{p, a\}}}
+\end{align*}
+where the M\o ller--Plesset denominators $\Delta$ are defined in \eqref{eq:moellerplessetdenominator}.
+The above expression is depicted in Figure \ref{fig:diagrams-sfe}.
+Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.
 
@@
 \begin{align*}
-  \epsilon_p = H^{[1]}_{p, p} + \epsilon_p^{(2)} + \epsilon_p^{(3)}
+  \varepsilon_p = H^{[1]}_{p, p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}
 \end{align*}
@@
 \begin{equation}\label{eq:EOM}
-  [\hat{H}, \hat{X}^{(N \pm 1)}_u] \ket{\Psi^{(N)}_0} = \pm \epsilon^{(\pm)}_u \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
+  [\hat{H}, \hat{X}^{(N \pm 1)}_u] \ket{\Psi^{(N)}_0} = \pm \varepsilon^{(\pm)}_u \hat{X}^{(N \pm 1)}_u \ket{\Psi^{(N)}_0},
 \end{equation}
-which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\epsilon^{(\pm)}_u$ are the single-particle addition ($+$) and removal ($-$) energies.
+which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\varepsilon^{(\pm)}_u$ are the single-particle addition ($+$) and removal ($-$) energies.
 The quality of this calculation depends on the ansatz for the $N$-particle ground state, as well as the systematically improvable truncation on the ladder operators.
@@
 \begin{equation}\label{eq:EOMIMSRG}
-  [\bar{H},\bar{X}^{(N \pm 1)}_u] \ket{\Phi^{(N)}_0} = \pm \epsilon^{(\pm)}_u \bar{X}^{(N \pm 1)}_u \ket{\Phi^{(N)}_0},
+  [\bar{H},\bar{X}^{(N \pm 1)}_u] \ket{\Phi^{(N)}_0} = \pm \varepsilon^{(\pm)}_u \bar{X}^{(N \pm 1)}_u \ket{\Phi^{(N)}_0},
 \end{equation}
@@
 Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
-States with lower single particle norms should be treated by with a higher EOM approximation, which can be accomplished directly or perturbatively.
-{\color{red} My paper talks about this a bit more, and we have some plots.
-Of course it only concerns the A-body stuff}.
+States with lower single particle norms should be treated by with a higher EOM approximation, which can be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
 
@@
 [[?]]
-
-\subsection{Diffusion Monte Carlo}
-\label{subsec:DMC}
-
-Diffusion Monte Carlo (DMC) is a method for calculating the ground state properties via a stochastic process akin to classical diffusion, refining an approximate ground state density towards that of the exact ground state.
-The rules that govern the diffusion process are obtained by evolving the wave function using what can be formally be thought of as the time-dependent Schr\"odinger equation along imaginary time $\tau \equiv t / \mathrm{i}$:
-\begin{align} \label{eq:itse}
-  \frac{\partial}{\partial \tau} |\Phi(\tau)\rangle = \hat H |\Phi(\tau)\rangle
-\end{align}
-The solutions to this equation are not unlike the ordinary Schr\"odinger equation with a slight but crucial difference in the exponent:
-\begin{align*}
-  |\Phi(\tau)\rangle = \mathrm e^{-\hat H \tau} |\Phi(0)\rangle
-\end{align*}
-where $|\Phi(0)\rangle$ is the initial wave function at $\tau = 0$ -- not to be confused with the exact ground state of $\hat H$, which we denote $|\Psi_0\rangle$ here.
-If we decompose the wave function into a sum over the eigenstates $|\Psi_n\rangle$,
-\begin{align*}
-  |\Psi(\tau)\rangle
-  = \mathrm e^{-\hat H \tau} \sum_n c_n |\Psi_n\rangle
-  = \sum_n c_n \mathrm e^{-E_n \tau} |\Psi_n\rangle
-\end{align*}
-we find that components of the wave function that have negative energy will increase exponentially as $\tau \to \infty$, while those with positive energy will decrease exponentially.
-This property can be exploited to filter out the undesirable components, leaving only the ground state energy.
-To do this, we require a trial energy $E_{\text{T}}$ -- a guess of the ground state energy -- and replace $\hat H$ in \eqref{eq:itse} with $(\hat H - E_{\text{T}})$ so that, if our trial energy is good, all states but the ground states will approximately vanish.
-
-Diffusion Monte-Carlo (DMC) is a method used for refining a crude estimate to the ground state density into a better approximation to the exact ground state.
-The basic idea is to move multiple random walkers in position space with sampling rules which ensures convergence to a behavior representing a walk guided by the exact ground state density.
-Once a satisfying level of convergence is reached, expectation values are calculated by accumulating local estimates along the path of the walkers.
-
-The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_{\mathrm{T}}}$
-\begin{equation}
- \hat{P}(\tau)\ket{\Psi_{\mathrm{T}}} \equiv \E^{-(\hat{H} - E_0)\tau} \ket{\Psi_{\mathrm{T}}}
-\end{equation}
-where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\hat{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\hat{H}$.
-By expanding the trial state in the eigenfunctions of $\hat{H}$, the ground state is obtained up to a constant factor
-\begin{equation}
- \label{eq:DMC_ExactProjection}
- \lim_{\tau\to\infty} \bra{\bm{r}}  \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} = \braket{\Psi_0}{\Psi_{\mathrm{T}}}\Psi_0(\bm{r}).
-\end{equation}
-
-Defining $\Phi(\bm{r}, \tau) \equiv \bra{\bm{r}}\hat{P}(\tau)\ket{\Psi_{\mathrm{T}}}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
-\begin{align}
- \Phi(\bm{r}, \tau + \delta\tau) &= \bra{\bm{r}} P(\tau + \delta\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
- &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
- &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\Phi(\tau)} \notag\\
- &= \int \D\bm{r}' \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\bm{r}'} \Phi(\bm{r}', \tau)\notag \\
- &\equiv \int \D\bm{r}' G(\bm{r}, \bm{r}'; \delta\tau) \Phi(\bm{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
-\end{align}
-which defines the Green's function $G$.
-
-In practice, the ground state energy is a priori unknown, hence a trailing averaged value obtained from the converging DMC density is used.
-This energy is often referred to as the trial energy, and it is believed that with a sufficiently good trial state, the error due to this approximation is small.
-
-The Green's function introduced in \eqref{eq:DMC_GreenFuncRevealed} has singularities due to the the Coulomb interaction term in $\hat{H}$.
-Due to Pauli exclusion these are not physical, nevertheless, in numerical implementations they are unpredictable and undesirable, hence we want to avoid them.
-
-For evaluation of the local energy, the trial state is designed to cancel the Coulomb singularities by containing so-called correlation factors, however, this cancellation does not apply to the terms in the Green's function.
-In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\bm{r}, \tau) \equiv \Phi(\bm{r}, \tau)\Psi_{\mathrm{T}}(\bm{r})$.
-Note that all previous arguments regarding convergence to the true ground state still applies for the new distribution.
-
-Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.\ for comparisons with other methods), this is strictly not necessary.
-
-Additionally, to avoid issues regarding the positive definiteness of the mixed distribution, the nodes of the mixed density is fixed to those of the wave function of the trial state.
-This is known as the \textit{fixed node approximation} \cite{umrigar:2865, abInitioMC}.
-Again, given a sufficiently good trial state, the errors should be small.
-
-The Green's function for the mixed density is given as \cite{umrigar:2865}
-
-\begin{align}
-  G(\bm{r}, \bm{r}'; \delta\tau)_f &= \bra{\bm{r}} \E^{\frac{1}{2} \hat{\bm{\nabla}} \cdot \left(\hat{\bm{\nabla}} - \bm{F}(\bm{r})\right) - \left(E_{\mathrm{L}}(\bm{r}) - E_{\mathrm{T}}\right)} \ket{\bm{r}'} \label{eq:DMC_IS_GF_raw}\\
-  &\propto \E^{-\left(|\bm{r} - \bm{r}' - \frac{1}{2}\delta\tau\bm{F}(\bm{r})|^2/(2\delta\tau)\right)} \label{eq:DMC_IS_GF}\\
-  &\qquad\times \E^{-\left(\frac{1}{2}\left(E_{\mathrm{L}}(\bm{r'}) + E_{\mathrm{L}}(\bm{r})\right) - E_{\mathrm{T}}\right) \delta\tau} + \mathcal{O}\bigl((\delta\tau)^2\bigr), \notag
-\end{align}
-where
-\begin{equation}
-  \bm{F}(\bm{r}) = \frac{2 \hat{\bm{\nabla}} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
-\end{equation}
-is the drift vector commonly referred to as the \textit{quantum force}.
-
-The local energy
-\begin{equation}
-E_{\mathrm{L}}(\bm{r}) \equiv \frac{\hat{H} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
-\end{equation}
-is necessarily sampled from $|\Psi_{\mathrm{T}}(\bm{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_{\mathrm{T}}(\bm{r})$.
-
-The Green's function from \eqref{eq:DMC_IS_GF_raw} has been split into two for practical reasons; one part containing the kinetic terms, more specifically this represents a Fokker-Planck diffusion process, and a second part which is commonly referred to as a \textit{branching function}, which is an effective reweighing of a positions contribution to the overall density.
-Excluding branching we will simply sample from the density of the trial state.
-
-In order dampen the errors introduced by splitting the Green's function, the time step $\delta\tau$ should be small.
-A value in the range of $10^{-3}$ to $10^{-4}$ is used in this work.
-High variance in energy samples requires a smaller time step to keep the branching controlled, since the fluctuations of the two are connected by \eqref{eq:DMC_IS_GF}.
-
-The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of \eqref{eq:DMC_IS_GF}.
-Let $G_{\mathrm{b}}$ denote the value of the branching function at a given position.
-Correct weighting is then ensured by guaranteeing $m = \max\{0, \lfloor G_{\mathrm{b}} \rfloor - 1\}$ branches with a probability $G_{\mathrm{b}} - m$ of getting an additional branch.
-A branch is an identical copy of the corresponding walker, with an identical past but with a different future.
-When the number of requested branches is zero, the walker is removed from the simulation.
-
-Initially, $N_{\mathrm{w}}$ walkers are initialized to span $|\Psi_{\mathrm{T}}(\bm{r})|^2$.
-This is ensured by using the Metropolis Algorithm.
-Moreover, importance sampling is ensured by sampling according to the kinetic term of \eqref{eq:DMC_IS_GF_raw} [[cite solution langevin]]
-
-\begin{equation}
-x_{i+1} = x_i + \frac{1}{2} \delta \tau F(\bm{r})_x + \xi,
-\end{equation}
-where $\xi$ is a uniform distributed random number with variance $\operatorname{Var}(\xi) = 2D\delta\tau$. A typical value of $N_{\mathrm{w}}$ in this work is \num{250000}.
-
-For each time step, diffusion and branching repeats a given number of blocks $N_{\mathrm{b}}$ for each walker.
-New branches are not active until the next time step, and if a walker hits zero branches the block repetition stops.
-During these block loops, the trial energy $E_{\mathrm{T}}$ is sampled for use in the next time step $k+1$
-\begin{equation}
- E_{\mathrm{T}}^{k+1} = \frac{1}{M_k}\sum_{i=1}^{M_k} G_{\mathrm{b}}(\bm{r}^{(k)}_i)E_{\mathrm{L}}(\bm{r}^{(k)}_i),
-\end{equation}
-where $M_k$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_{\mathrm{b}} = 100$ to be sufficient.
-
-Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_{\mathrm{c}}$ trial energies calculated after $N_{\mathrm{t}}$ thermalization cycles
-\begin{equation}
- E_0 = \frac{1}{N_{\mathrm{c}}-N_{\mathrm{t}}} \sum_{k=N_{\mathrm{t}}}^{N_{\mathrm{c}}} E_{\mathrm{T}}^{(k)}.
-\end{equation}
-This is the relation we use in this work to obtain the DMC energies.
-
-In this work, the trial state has been chosen to consist of a single Slater determinant [[cite]] together with a single variational parameter Pad\'e-Jastrow correlation function [[cite]].
-
-The Slater determinant contains eigenstates $\phi_n(\bm{r})$ of the 2-dimensional harmonic oscillator
-with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$
-such that $\omega\to\alpha\omega$ in all solutions:
-\begin{equation}
- \phi_n(\bm{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\E^{-\alpha\omega r^2}.
-\end{equation}
-where $H_n$ is the $n$th level Hermite polynomial.
-
-The eigenstates are selected such that the $N$ lowest lying energy eigenstates are selected (counting spin-degeneracy).
-Due to the Hamiltonian being spin independent we may split the Slater determinant into two equal parts -
-one for each spin level [[cite]]. The overall form of the trial state is as follows:
-\begin{equation}
- \Psi_{\mathrm{T}}(\bm{r}) \equiv S(\bm{r}^\uparrow) S(\bm{r}^\downarrow) \prod_{i<j}^{N} J(r_{i,j}),
-\end{equation}
-with
-\begin{equation}
- S(\bm{r}^s) \equiv \begin{vmatrix}
-\phi_1(\bm{r}^s_1) & \phi_2(\bm{r}^s_1)& \cdots & \phi_{N/2}(\bm{r}^s_1) \\
-\phi_1(\bm{r}^s_2) & \phi_2(\bm{r}^s_2)& \cdots & \phi_{N/2}(\bm{r}^s_2) \\
-\vdots & \vdots& \ddots & \vdots \\
-\phi_1(\bm{r}^s_{N/2}) & \phi_2(\bm{r}^s_{N/2})& \cdots & \phi_{N/2}(\bm{r}^s_{N/2}) \\
- \end{vmatrix},
-\end{equation}
-and
-\begin{equation}
- J(r_{i, j}) \equiv \exp\left(\frac{r_{i, j}}{1 + \beta r_{i, j}}\right),
-\end{equation}
-where $\bm{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons.
-Since Metropolis Monte-Carlo only involves ratios of density functions, all normalization factors are skipped.
-
-As a consequence of the variational principle, the optimal numeric values for $\alpha$ and $\beta$ can be found by minimizing the energy in the variational parameter space.
-For this we have used the adaptive step gradient descent method [[cite ASGD]].
-
-Using a single Slater determinant and a single variational parameter in the correlation function might at first glance seem insufficient,
-however, the strength and robustness of DMC greatly succeeds at transforming this naive approximation into a very good estimate to the ground
-state density. It should be mentioned that for systems where the single-particle Hamiltonian does not have analytical solutions, this approach
-will indeed be insufficient due to low overlap between the initial and exact state.
-
-A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the computation time of most calculations.
-We refer to Refs [[cite optimization techniques]] for more information.
-Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once for the entire calculation.
-This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is preserved under differentiation.
 
@@
 \subsection{Methodology}
+\label{subsec:methodology}
 
@@
 \end{figure}
-
-Before we discuss the results, let us briefly outline the concrete methodology used by our numerical experiments.
-There is a some degree of flexibility in which many-body methods can be applied, which is not evident from reading the description of each method alone.
-
-The typical approach is to apply them in the order shown in Figure \ref{fig:methods}.
-Such an ordering maximizes the benefits of each method: Hartree-Fock acts as an initial, crude procedure to \textit{soften} the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
-
-The arrows in the diagram designate the flow of numerical data, which are generally matrix elements of some operator.
-For HF and IM-SRG, these are simply (evolved) Hamiltonian matrix elements.
-For CC, they would be elements of the cluster operator $\hat{T}$.
-
-There are several paths through which one can traverse in this diagram to obtain the output observables.
-Among these possibilities, there exist (a) HF + IM-SRG + QDPT, (b) HF + IM-SRG + EOM, and (c) HF + CC + EOM.
-All three paths are explored in this paper.
-There are, of course, other paths, but we will not consider every single possibility here.
-
-Moreover, there is also the possibility of omitting one or more of these steps in the process.
-For example, one can omit HF, but continue with the remaining two steps.
-While this is possible, our experience indicate that the HF plays a strong role in increasing the rate of convergence of the post-HF methods, and thereby increasing the accuracy and efficiency as well.
-Hence, there is very little reason to omit HF.
-
-All results in this paper shall discuss results in which HF is included as the first step of the calculation, and thus we will not explicitly state ``HF'' unless there is no post-HF method used, in which case we write ``HF only''.
-
-Unlike ground state energy, whose systems are characterized only by the number of particles $N$ and the oscillator frequency $\omega$, the addition (or removal) energy depend on an additional quantity: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
-This is because there can be multiple states with $N + 1$ particles with near-degenerate energy.
-For our numerical results, we will study exclusively the addition energies such that $|M_\ell|$ is as small as possible subject to the constraint that the particle added lies within the next shell.
-This means the $N + 1$ states we are interested in are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$, while the $N - 1$ states are those with $|M_\ell| = 1 - K_{\mathrm{F}} \bmod 2$, where $K_{\mathrm{F}}$ is the number of occupied shells.
-
-\subsection{Tables and figures}
 
@@
   \centering
-  \caption{Addition energy of a selection of quantum dot systems.  See Table \ref{tab:ground} for details.}
+  \caption{Addition energy of quantum dot systems.  See Table \ref{tab:ground} for details.}
   \label{tab:add}
@@
   \centering
-  \caption{Removal energy of a selection of quantum dot systems.  See Table \ref{tab:add} for details.}
+  \caption{Removal energy of quantum dot systems.  See Table \ref{tab:add} for details.}
   \label{tab:rm}
@@
   \centering
-  % The siunitx package somehow makes the columns unnecessarily wide so we have to compensate by shrinking the text size :/
+  % [[LAYOUT]] The siunitx package somehow makes the columns unnecessarily wide so we have to compensate by shrinking the text size :/
   \footnotesize
   \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
-The uncertainties are computed from the approximate Hessian used in Levenberg-Marquardt fitting procedure.
+The uncertainties are computed from the approximate Hessian constructed by Levenberg-Marquardt fitting algorithm.
 Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{fig-gs}
+  \includegraphics[width=\linewidth]{fig-gs2}
   \caption{Ground state energies.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{fig-add}
+  \includegraphics[width=\linewidth]{fig-add2}
   \caption{Addition energies.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{fig-rm}
-  \caption{Removal energies.}
+  \includegraphics[width=\linewidth]{fig-rm2}
+  \caption{Removal energies.  See Figure \ref{fig:add} for details.}
   \label{fig:rm}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{fig-rel-slopes}
+  \includegraphics[width=\linewidth]{fig-rel-slopes}
   \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.
-The key observation from this plot is that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
+The trends suggest that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
   \label{fig:rel-slopes}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-0-normal}
-  \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.  [[TODO: Results for FCI are from who?]] [[TODO: Add DMC results]]}
+  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-normal}
+  \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.}
   \label{fig:by-num-shells-6-2-ground-0-normal}
@@
   \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
-The energy is normalized with respect to the Hartree-Fock values to magnify the differences.
+The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
 Lower frequency leads to stronger correlations and thereby a more difficult problem.
-The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).
-[[TODO: Add DMC results if available]]}
+The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).}
   \label{fig:by-freq-10-6-gs-0-normal}
@@
   \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
-Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree-Fock values.}
+Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree--Fock values.}
 \end{figure}
 
-In this section, we discuss the numerical results for the ground state, addition, and removal energies of closed-shell systems for a selection of methods.
-
-For the IM-SRG results
-
-All calculations in this paper are performed with a relative numerical precision of about $10^{-5}$ or lower (sometimes \emph{much} lower).
-This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate at every step of the calculation, thus the precision of the final results may be an order of magnitude larger.
-
-As foreshadowed, we find the Wegner generator described in subsection [[??]].
-Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, favors the use of a Hartree-Fock basis and the Coulomb interaction.
-Since higher correlations still lead to stiff equation systems, we change in subsection [[??]] to the White generator.
-In particular, we give an overview of the IM-SRG(2) ground state energies for closed-shell systems up to $N=42$ particles and compare with other \textit{ab initio} many-body methods.
-
-[[...]]
-
-The discrepancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
-The former can be reduced by increasing the number of shells, and can be further alleviated by extrapolation techniques.
-
-Both IM-SRG and MP2 improve the accuracy the result dramatically over the more primitive HF.  (It may help to add plots *without* HF.)
-
-It is possible to omit some of the methods, bypassing some of the steps.
-For example, one can do an IM-SRG calculation \emph{without} doing HF.
-There are few good reasons to do so, as it typically worsens the result and increases the numerical cost of IM-SRG, but it can be done.
-Similarly, one can do both HF and IM-SRG, but omit QDPT, yet still obtain \emph{addition and removal} energies.
-The result would be poor, but it may be useful for the purpose of assessing difficulty of the problem.
-For example, if the omission of QDPT leads to a large change, then it may indicate the presence of strong correlations.
+There is large amount of flexibility in the application of many-body methods.
+The approach we use is shown in Figure \ref{fig:methods}.
+Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+
+The arrows in the diagram indicate the flow of numerical data, which are usually matrix elements of some many-body operator.
+For HF and IM-SRG, they are simply (evolved) Hamiltonian matrix elements.
+For CC, they would be elements of the cluster operator $\hat{T}$.
+
+There are several paths in this diagram through which one can traverse to obtain the output observables.
+Among these possibilities, we shall primarily focus on the three combinations: (a) HF + IM-SRG + QDPT, (b) HF + IM-SRG + EOM, and (c) HF + CC + EOM.
+
+Moreover, one may also omit some steps of the process.
+For example, one can omit HF, but continue with the remaining two steps.
+While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
+Therefore, in practice there is little reason to omit HF.
+We will however investigate the effects of removing one or more of the post-HF methods.
+
+Since every calculation in this paper is begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
+
+All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
+This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
+Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
+\begin{align*}
+  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N \\
+  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}
+\end{align*}
+
+Ideally, ground state energy should be characterized entirely by the two system parameters $(N, \omega)$, where $N$ is number of particles and $\omega$ is the oscillator frequency.
+However, the methods that we study are limited to a \emph{finite} (truncated) basis and therefore their results are dependent on the level of truncation.
+This is characterized by $K$, the total number of shells in the single-particle basis.
+Thus, results are generally presented as a graph plotted against $K$.
+In Section \ref{subsec:extrapolation} discuss how to estimate results as $K \to \infty$ (infinite-basis limit) through \textit{extrapolations}.
+
+The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
+This is due to the presence of multiple states with near-degenerate energies.
+For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
+In particular, this means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+
+Not all cases are solvable with our selection many-body methods.
+Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
+Cases where the methods required more than our allocated times to arrive at a result are marked ``n.c.'' (``no convergence'').
+For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').
+Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
+
+All calculations in this paper are performed with a relative numerical precision of about $10^{-5}$ or lower (sometimes \emph{much} lower, as is for CC).
+This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate at every step of the calculation, thus the precision of the final results is more like $10^{-4}$.
 
@@
 
-In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.
-Results from diffusion Monte Carlo (DMC) \cite{hoegberget2013thesis} are shown as a dashed line for comparison.
-
-Both perturbation theory and IM-SRG add corrections in addition to the Hartree-Fock results to recover the correlation energy and they do quite well in recovering the correlation energy in the system.
+In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the three approaches described in Section \ref{subsec:methodology}.
+We also include results from DMC \cite{hoegberget2013thesis} and FCI \cite{olsen2013thesis} for comparison.
+
+Both perturbation theory and IM-SRG add significant corrections to the Hartree--Fock results.
 Compared with MPPT, IM-SRG generally converges faster, although does not always converge to the DMC result.
@@
 There are a few cases where the IM-SRG over-corrects the result, leading to a ground state energy that is lower than the exact result.
-This is not unexpected given that, unlike Hartree-Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
+This is not unexpected given that, unlike Hartree--Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
 Overcorrection tends to occur when the number of particles is few, or the frequency is very low (high correlation).
@@
 The other source is that of basis truncation, which limits the size of the Hilbert space that can be explored by the method.
-Unlike operator truncation, which is difficult to overcome as it increases the computational cost exponentially, increasing the basis comes a cost of about $O(n^2 N^4)$ for IM-SRG(2) with the White generator,\footnote{This result holds for any generator whose two-body part contains only pphh- and hhpp-type matrix elements.} [[cite Heiko?]] where $N$ is the total number of states in the single-particle basis and $n$ is the number of particles.
+Unlike operator truncation, which is difficult to overcome due to its exponentially increasing computational cost, the cost of increasing the basis is ``only'' polynomial with respect to the number of basis elements: roughly $O(N_{\mathrm{b}}^6)$ where $N_{\mathrm{b}}$ is the total number of states in the single-particle basis.
 In practice, the scaling cost is usually lower as the conserved symmetries allow the Hamiltonian to be partitioned into blocks.
@@
 For our addition and removal energy calculations, the results are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.
-The figures show the the addition/removal energies for Hartree-Fock, combined with IM-SRG and/or QDPT (Hartree-Fock is always included, as usual) [[better way to explain this?
-the figure labels are somewhat misleading too]].
-Results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line, where available.
-
-From these results, we see that the QDPT corrections add a substantial contribution to the results of both Hartree-Fock with and without IM-SRG.  [[quantify ``substantial'' numerically]]
-
-Interestingly, the addition energy of Hartree-Fock with second-order QDPT appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
+The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
+Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
+
+From these results, we see that the QDPT corrections add a substantial contribution to the results of both Hartree--Fock with and without IM-SRG.  [[quantify ``substantial'' numerically]]
+
+Interestingly, the addition energy of Hartree--Fock with second-order QDPT appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
 This is likely coincidental, as the third-order QDPT dramatically worsens the result.
 
-Both Hartree-Fock and IM-SRG results worsen as the frequency decreases, which is not unexpected since the correlations become much more dominant.
-The Hartree-Fock appears to perform much worse, however, as the results converge much more slowly as the number of shells increases.
+Both Hartree--Fock and IM-SRG results worsen as the frequency decreases, which is not unexpected since the correlations become much more dominant.
+The Hartree--Fock appears to perform much worse, however, as the results converge much more slowly as the number of shells increases.
 
@@
 
+For addition and removal energies, we found that IM-SRG improves their rate of convergence both as the order of perturbation theory increases and as the number of shells increases.
+
 [[---]]
-
-[[Cite as source of DMC energies: \cite{PhysRevB.84.115302}]]
 
@@
 \subsection{Extrapolation}
-
-As suggested by Kvaal in \cite{PhysRevB.80.045321}, the asymptotic convergence of the wave function can be approximately described by a power law model: [[assuming I understood his paper correctly]]
+\label{subsec:extrapolation}
+
+As suggested by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the wave function can be approximately described by a power law model: [[assuming I understood his paper correctly]]
 \begin{align*}
@@
 
-[[Hypothesis for the poor HF fits: either it's decaying so fast that it quickly becomes dominated by the precision of the calculation, or it's exponential.]]
+Unlike all of the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not fit to well to the power-law model.
+In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
+Based on the results with artificial softened interactions as well as past experiences, we believe this is an artifact of the insensitivity of Hartree--Fock theory to the Coulomb cusp.
+
+Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
+This is likely due to its rapid convergence, which leaves very little degree of freedom even for a badly chosen model.
+Moreover, we find that the fit uncertainties of energy are also roughly within the right order of magnitude, surprisingly.
 
@@
 
-We have demonstrated the use of various many-body theories -- Hartree-Fock method, M\o eller-Plesset perturbation theory, in-medium similarity renormalization group, and quasidegenerate perturbation theory -- to calculate ground state as well as addition and removal energies of two-dimensional circular quantum dots up to 56 [[make sure the figure/data for 56 particles stays]] particles.
-We showed that these methods, when combined, can provide a good, approximate description of the systems at moderate cost compared to near-exact but much more expensive methods such as FCI and DMC.
-
-Two different generators, Wegner and White generators, were used [[T/F?]] to perform the calculations.
-It was observed that the Wegner generator results in stiff equation systems, whereas the White generator has much better numerics and is computationally more efficient.[[make sure this is this elaborated in the Results section]] Moreover, we found out that the use of an Hartree-Fock basis improves numerical stability enormously.
-
-For ground state energy, we showed that the convergence of IM-SRG is generally faster than that of MPPT, and the results are typically closer to the the near-exact results.
-Similar to previous FCI \cite{2008arXiv0810.2644K} and CCSD \cite{PhysRevB.84.115302} calculations, the use of an effective interaction improves convergence of the ground state energy as function of the number of oscillator shells.
-[[delete or keep: For more than six particles, we lie in all cases closer to the DMC result than corresponding CCSD calculations do.]]
-
-For addition and removal energies, we found that IM-SRG improves their rate of convergence both as the order of perturbation theory increases and as the number of shells increases.
+We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
+Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
+All such results show good agreement with one another.
+We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the slightly more expensive EOM calculations.
+Moreover, IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost methods such as FCI, allowing exploration of much higher number of particles than would otherwise be possible.
 
@@
 This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
-While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost [[Ref?]].
-
-As noted earlier [[not yet written]], the application of IM-SRG eliminates a large portion of the QDPT diagrams, which is beneficial as it increases the efficiency of the QDPT calculations.
-However, many of these diagrams can also be eliminated further through an infinite resummation scheme [[Good refs for this?]], which would further reduce the number of diagrams in QDPT, especially those of lower order, whic would likely increase the accuracy of the result.
-
-It would also be useful to investigate how the results obtained with finite
-number of shells in the basis are related to those obtained with an infinite
-number of shells in the basis.  [[Ref: IR/UV extrapolation]] With a
-good theoretical foundation, a model of how the observables converge with
-respect to the size of the basis may be used to extrapolate the results to
-infinite-basis limit.  This would also enable us to perform cheaper
-calculations with fewer shells and optimistically extrapolate results for
-large systems that would be otherwise infeasible to compute.
+While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
+
+The application of IM-SRG eliminates a large number of the QDPT diagrams \ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
+Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
+Moreover, the remaining diagrams at third order can be eliminated through infinite resummation techniques, which would incorporate higher order terms and therefore further increase the accuracy of the result.
 
@@
 D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved with greater ease.
-Implementing this approach would be beneficial as it would allows us to study the accuracy and convergence of other observables beyond energy and energy differences.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at much lower cost.
+Implementing this approach would be beneficial as it would allows us to study the accuracy and convergence of other possibly more sensitive observables.
 
@@
 This approach is often referred to as \textit{m-scheme} in nuclear physics.
-It is a simple approach and works well for general systems, but it does not fully exploit the symmetries in the quantum dot system, since not only is spin projection $\hat S_z$ conserved, but squared spin $\hat S^2$ too.
+It is straightforward to implement and works well for general systems, but it fails to exploit all the symmetries in the quantum dot system: not only is spin projection $\hat S_z$ conserved, the Casimir operator $\hat S^2$ is as well.
 A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
-Combining this with the spherical tensor symmetries of the Hamiltonian, this can reduce the amount of computation required in this system via the Eckart-Wigner theoerem, albeit at the cost of increasing the implementation complexity.
-
-A more technical issue is its lack of parallelization: currently, the code makes very little use of parallelism and therefore does not scale well on modern clusters.
-Parallelism would allow the workload and memory resources to be divided over multiple computing nodes, allowing larger systems to be explored, but this must be weighed carefully against the costs of communication, which can be severe if the algorithm is chosen poorly.
-
-Eventually, we plan to apply these theoretical and technical enhancements not only to the study of quantum dots, but to the studies of nuclear and atomic systems, opening up an even larger range of applications.
+A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
+
+Currently, parallelism within the code is limited to a thread level, i.e.\ shared memory parallelism: the program does cannot take advantage of more than a single compute node, thus it would not scale well on modern high-performance computing facilities.
+Rewriting the algorithm to take advantage of distributed memory parallelism would allow the workload and memory resources to be divided over many computing nodes, allowing larger systems to be explored.
+As with any parallelization, the algorithm must be designed carefully to minimize the communication, which are significantly more costly in parallel platforms.
+
+Eventually, we hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
 

### 2017-04-06 ___removed.tex
Update paper and figures

% [[last here]]

[[concrete method]]

The first step of any basis-dependent many-body method is to compute the matrix elements of the one-body and two-body Hamiltonian operators.  In a harmonic oscillator basis, the one-body Hamiltonian is diagonal.  Its diagonal matrix elements are computed directly using \label{eq:energysingleparticlestate}.

The more difficult part is the computation of two-body matrix elements, which requires first the calculating the integration integrals through \label{eq:interactionintegral} and then antisymmetrizing them with \label{eq:antisymmetricmatrixelement}.  One possibility is to use a analytic formula involving iterated summations and products as described in \cite{0953-8984-10-3-013}.  However, the formula has a rapidly growing asymptotic computational cost and also becomes increasingly sensitive to numerical losses due to oscillations as the shell number increases.  Therefore, we opted to use an alternative approach where integrals are calculated exactly in the center-of-mass frame using numerical quadrature and then transformed into the laboratory frame.  This part was done using OpenFCI software, which describes the technique in detail \cite{2008arXiv0810.2644K}.

With the Hamiltonian

The use of second quantization enables the application of an extremely useful combinatoric theorem known as Wick's theorem \cite{shavitt2009many}, which provides systematic way to expand complicated expressions involving creation and annihilation operators.  Ultimately, after simplification, computations \textit{in silico} do not involve algebraic manipulation of abstract operators at all -- rather, they involve numerical calculations of the \emph{matrix elements} via equations derived using Wick's theorem.

### 2017-04-06 Datafiles/plot_by_num_shells.py

@@ -9,6 +9,12 @@ import utils
 
 def plot(label, num_filled, freq,
          num_shells_range, interaction="normal"):
+    d_dmc = utils.load_all_dmc()
+    d_dmc = d_dmc[(d_dmc["interaction"] == interaction) &
+                  (d_dmc["label"] == label) &
+                  (d_dmc["num_filled"] == num_filled) &
+                  (d_dmc["freq"] == freq)]
+    d_dmc = d_dmc.set_index(["num_particles", "freq"])
     d = utils.load_all()
     d = utils.filter_preferred_ml(d)
     d = d[(d["method"] != "imsrg[f]+eom[n]") &
@@ -18,7 +24,7 @@ def plot(label, num_filled, freq,
           (d["num_filled"] == num_filled) &
           (d["num_shells"] >= num_shells_range[0]) &
           (d["num_shells"] <= num_shells_range[1]) &
-          (d["freq"] == 1.0)]
+          (d["freq"] == freq)]
     num_particles = num_filled * (num_filled + 1)
     energy_type = {"ground": "ground state",
                    "add": "addition",
@@ -33,13 +39,19 @@ def plot(label, num_filled, freq,
                 color=utils.METHOD_COLOR[method])
         ax.get_xaxis().set_major_locator(
             matplotlib.ticker.MaxNLocator(integer=True))
+    if len(d_dmc["energy"]):
+        assert len(d_dmc["energy"]) == 1
+        ax.axhline(d_dmc["energy"][0],
+                   label=utils.METHOD_LABEL["dmc"],
+                   color=utils.METHOD_COLOR["dmc"],
+                   linestyle=utils.DMC_LINESTYLE)
     ax.set_xlabel("K (number of shells)")
     ax.set_ylabel("E (energy)")
     ax.legend()
     fig.tight_layout()
     utils.savefig(fig,
                   "by-num-shells-{num_particles}-{num_filled}-"
-                  "{label}-{ml}-{interaction}"
+                  "{label}-{interaction}"
                   .format(**locals()))
 
 with utils.plot(__file__, call=plot) as interactive:

### 2017-04-06 Datafiles/utils.py

@@ -28,6 +28,7 @@ JSON_PRETTY = {
 METHOD_COLOR = {
     "ccsd": "#1c5aa5",
     "ccsd+eom": "#1351c4",
+    "dmc": "#666666",
     "fci": "#2e2360",
     "hf": "#b7ac12",
     "hf+qdpt3": "#e28522",
@@ -42,6 +43,7 @@ METHOD_COLOR = {
 METHOD_LABEL = {
     "ccsd": "CCSD",
     "ccsd+eom": "CCSD+EOM",
+    "dmc": "DMC",
     "fci": "FCI",
     "hf": "HF only",
     "hf+qdpt2": "HF only + QDPT2",
@@ -54,6 +56,24 @@ METHOD_LABEL = {
     "magnus_quads+eom": "Magnus(2*) + EOM",
     "mp2": "MP2",
 }
+
+METHOD_MARKER = {
+    "ccsd": "*",
+    "ccsd+eom": "*",
+    "fci": "D",
+    "hf": "^",
+    "hf+qdpt3": "^",
+    "imsrg": "x",
+    "imsrg+eom": "+",
+    "imsrg+qdpt3": "x",
+    "mp2": "+",
+}
+
+MARKERSIZE_CORRECTION = {
+    "D": 0.7,
+}
+
+DMC_LINESTYLE = "--"
 
 def parse_color(color):
     '''Accepts either (r, g, b[, a]) or "#rrggbb[aa]".'''
@@ -196,9 +216,12 @@ def plot_main(filename, call, main):
         if not interactive:
             main()
 
-def savefig(fig, name):
+def savefig(fig, name=None, fn=None):
+    if (name is None) == (fn is None):
+        raise TypeError("either name or fn must be given, but not both")
     if not matplotlib.rcParams["interactive"]:
-        fn = "../FigureFiles/fig-{name}.svg".format(**locals())
+        if fn is None:
+            fn = "../FigureFiles/fig-{name}.svg".format(**locals())
         fig.savefig(fn)
         plt.close(fig)
         sys.stderr.write("Figure saved to: {}\n".format(fn))

### 2017-04-06 Manuscript/paper.tex
Update paper

@@
 All such results show good agreement with one another.
-We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the slightly more expensive EOM calculations.
-Moreover, IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost methods such as FCI, allowing exploration of much higher number of particles than would otherwise be possible.
+
+We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.
+Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
+EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
 
@@
 D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at much lower cost.
-Implementing this approach would be beneficial as it would allows us to study the accuracy and convergence of other possibly more sensitive observables.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
+Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
+
+The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).
+This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.
+
+By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.
+Such interactions can be used to lower the cost of other methods such as configuration interaction (CI), also known as \textit{shell model} in nuclear physics.
 
@@
 
-Eventually, we hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
+We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
 

### 2017-04-17 Datafiles/plot_grid.py
Tweak theme

@@ -14,13 +14,15 @@ def main(label):
         42: [11.5, 20.5],
         56: [14.5, 20.5],
     }
-    num_particles_ticks = [6, 12, 20, 30, 42, 56]
-    freq_ticks = [0.1, 0.28, 1.0]
+    num_particles_ticks = [6, 30, 56]
+    LEGEND_FACET_IDX = 2
 
     if label == "ground":
+        freq_ticks = [0.1, 1.0]
         methods = ["mp2", "imsrg", "ccsd", "fci"]
         fn = "../Manuscript/fig-gs2.pdf"
     else:
+        freq_ticks = [0.1, 0.28]        # 0.28 needed to show DMC results
         fn = "../Manuscript/fig-{}2.pdf".format(label)
         methods = ["imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
 
@@ -36,6 +38,7 @@ def main(label):
     del d_dmc["label"]
     del d["num_filled"]
     d_dmc = d_dmc.set_index(["num_particles", "freq"])
+    print(d_dmc)
 
     facet_x = {
         "col": "num_particles",
@@ -49,13 +52,14 @@ def main(label):
     }
     facet_to_num_particles_freq = lambda x, y: (x, y)
 
-    base_markersize = 3.0
+    has_dmc = False
+    width = 7
+    height = 3
+    base_markersize = 5.0
     linewidth = 1.0
-    fig = plt.figure(figsize=(9, 4))
+    fig = plt.figure(figsize=(width, height))
     gs = matplotlib.gridspec.GridSpec(len(facet_y["ticks"]),
                                       len(facet_x["ticks"]))
-    #d = d.set_index(["num_shells", "num_particles", "freq", "method"])
-    LEGEND_FACET_IDX = 5
     for (fct_x, fct_y), d in d.groupby([facet_x["col"], facet_y["col"]]):
         num_particles, freq = facet_to_num_particles_freq(fct_x, fct_y)
         try:
@@ -72,6 +76,7 @@ def main(label):
         except KeyError:
             pass
         else:
+            has_dmc = True
             ax.axhline(sel_dmc["energy"],
                        color=utils.METHOD_COLOR["dmc"],
                        linestyle=utils.DMC_LINESTYLE,
@@ -92,40 +97,57 @@ def main(label):
                                 base_markersize),
                     color=utils.METHOD_COLOR[method])
 
-            title = ("${}={}$\n${}={}$"
-                     .format(facet_x["symbol"], fct_x,
[…]

### 2017-04-17 Datafiles/utils.py

@@ -184,8 +184,9 @@ def plot(filename, call=None, block=True, main_name="main"):
         cmd_args = []
     os.chdir(os.path.dirname(filename))
     matplotlib_try_enable_deterministic_svgs()
-    matplotlib.style.use("ggplot")
-    matplotlib.rcParams["font.sans-serif"] = ["Roboto"]
+    matplotlib.style.use("seaborn-deep")
+    matplotlib.rcParams["font.family"] = "sans-serif"
+    matplotlib.rcParams["mathtext.fontset"] = "stixsans"
     if cmd_args:
         args = []
         kwargs = {}

### 2017-04-20 Manuscript/paper.tex
Tweak theme
Add updated rel-slopes figure

@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MPPT), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results from existing literature.
@@
 
+We will refer to QDPT to third order as ``QDPT3''.
+
 \subsection{Equations of motion methods}
@@
   \includegraphics[width=\linewidth]{fig-gs2}
-  \caption{Ground state energies.}
+  \caption{Ground state energies for a selection of quantum dot parameters, plotted against the number of shells.}
   \label{fig:gs}
@@
   \includegraphics[width=\linewidth]{fig-add2}
-  \caption{Addition energies.}
+  \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
   \label{fig:add}
@@
   \includegraphics[width=\linewidth]{fig-rm2}
-  \caption{Removal energies.  See Figure \ref{fig:add} for details.}
+  \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
   \label{fig:rm}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-rel-slopes}
-  \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.
-The trends suggest that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
+  \includegraphics[width=\linewidth]{fig-rel-slopes2}
+  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG + QDPT3.
+For clarity, the plot does not distinguish between addition and removal energies.
+The horizontal axis shows quantum system parameters, where $N$ is the number of particles and $\omega$ is the oscillator frequency.
+The vertical axis shows $|\rho_{15}|$ (``relative slope''), which estimates the rate of convergence at 15 total shells.
+The lower the value of $|\rho_{15}|$, the faster the convergence.
+The data points are categorized by the interactions.
+The trends suggest that the singular short-range part of the interaction has a much stronger impact on the convergence than the long-range tail.}
   \label{fig:rel-slopes}
@@
 There are several paths in this diagram through which one can traverse to obtain the output observables.
-Among these possibilities, we shall primarily focus on the three combinations: (a) HF + IM-SRG + QDPT, (b) HF + IM-SRG + EOM, and (c) HF + CC + EOM.
+Among these possibilities, we shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM, and (c) HF + CCSD + EOM.
 
@@
 In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the three approaches described in Section \ref{subsec:methodology}.
-We also include results from DMC \cite{hoegberget2013thesis} and FCI \cite{olsen2013thesis} for comparison.
+We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison.
 
 Both perturbation theory and IM-SRG add significant corrections to the Hartree--Fock results.
-Compared with MPPT, IM-SRG generally converges faster, although does not always converge to the DMC result.
+Compared with MP2, IM-SRG generally converges faster, although does not always converge to the DMC result.
 Generally speaking, IM-SRG is closer to the DMC result as the number of particles increases.
@@
 Overcorrection tends to occur when the number of particles is few, or the frequency is very low (high correlation).
-However, MPPT does not do much better in the high frequency regimes as it often converges slower than IM-SRG.
+However, MP2 does not do much better in the high frequency regimes as it often converges slower than IM-SRG.
 

### 2017-04-20 Datafiles/plot_compare_rel_slopes.py

@@ -1,67 +1,68 @@
 #!/usr/bin/env python3
-import functools, os, sys
-import pandas as pd
+import itertools, sys
 import matplotlib
 import matplotlib.pyplot as plt
+import numpy as np
 import utils
 
-utils.init(__file__)
+with utils.plot(__file__):
+    d = utils.load_table("compare_rel_slopes.txt", na_filter=False)
 
-d = utils.load_table("compare_rel_slopes.txt")
+    # we want to use (num_particles, freq) as an axis
+    # but matplotlib doesn't let us do that
+    # so we have to use this awful hack
+    interactions = [
+        ("", r"$(\sigma_{\mathrm{A}} = 0, \sigma_{\mathrm{B}} = \infty)$"),
+        ("_sigmaB=4.0", r"$(\sigma_{\mathrm{A}} = 0, \sigma_{\mathrm{B}} = 4)$"),
+        ("_sigmaA=0.5", r"$(\sigma_{\mathrm{A}} = \frac{1}{2}, \sigma_{\mathrm{B}} = \infty)$"),
+        ("_sigmaA=0.5_sigmaB=4.0", r"$(\sigma_{\mathrm{A}} = \frac{1}{2}, \sigma_{\mathrm{B}} = 4)$"),
+    ]
+    interaction_colors = {
+        "": "#a883e4",
+        "_sigmaB=4.0": "#951c16",
+        "_sigmaA=0.5": "#005e93",
+        "_sigmaA=0.5_sigmaB=4.0": "#1e1e1e",
+    }
+    interaction_markers = {
+        "": "o",
+        "_sigmaB=4.0": "X",
+        "_sigmaA=0.5": "o",
+        "_sigmaA=0.5_sigmaB=4.0": "x",
+    }
+    interaction_markerfacecolors = {
+        "": None,
+        "_sigmaB=4.0": None,
+        "_sigmaA=0.5": "none",
+        "_sigmaA=0.5_sigmaB=4.0": "none",
+    }
+    interaction_label = dict(interactions)
+    interaction_pos = dict((x, i) for i, (x, _) in enumerate(interactions))
+    systems = [(num_particles, freq) for freq, num_particles in
+               itertools.product([1.0, 0.28], [6, 12, 20])]
+    system_pos = dict((x, i) for i, x in enumerate(systems))
+    d["system_pos"] = d.apply(
[…]

### 2017-04-20 Datafiles/plot_grid.py

@@ -38,7 +38,6 @@ def main(label):
     del d_dmc["label"]
     del d["num_filled"]
     d_dmc = d_dmc.set_index(["num_particles", "freq"])
-    print(d_dmc)
 
     facet_x = {
         "col": "num_particles",
@@ -93,6 +92,7 @@ def main(label):
             ax.plot(d["num_shells"], d["energy"],
                     linewidth=linewidth,
                     marker=marker,
+                    markerfacecolor="none",
                     markersize=(utils.MARKERSIZE_CORRECTION.get(marker, 1.0) *
                                 base_markersize),
                     color=utils.METHOD_COLOR[method])

### 2017-04-20 Datafiles/utils.py

@@ -32,9 +32,9 @@ METHOD_COLOR = {
     "fci": "#2e2360",
     "hf": "#b7ac12",
     "hf+qdpt3": "#e28522",
-    "imsrg": "#92e057",
+    "imsrg": "#3ec61b",
     "imsrg+eom": "#841a0b",
-    "imsrg+qdpt3": "#39b237",
+    "imsrg+qdpt3": "#286d17",
     "imsrg[f]+eom[n]": "#8e2544",
     "magnus_quads+eom": "#a825bc",
     "mp2": "#a81e4c",
@@ -58,8 +58,8 @@ METHOD_LABEL = {
 }
 
 METHOD_MARKER = {
-    "ccsd": "*",
-    "ccsd+eom": "*",
+    "ccsd": "o",
+    "ccsd+eom": "o",
     "fci": "D",
     "hf": "^",
     "hf+qdpt3": "^",
@@ -275,6 +275,11 @@ def intersperse(sep, xs):
             yield sep
         yield x
 
+def merge_dicts(d, *ds):
+    d = dict(d)
+    for di in ds:
+        d.update(di)
+    return d
 
 def num_dec_digits(x):
     x = abs(x)
@@ -431,7 +436,7 @@ def parse_uncertainty(s):
     uncertainty =  decimal.Decimal((0, list(map(int, uncertainty)), exponent))
     return value, uncertainty
 
-def load_table(f, sep=r"\s+", names=None, skiprows=0):
+def load_table(f, sep=r"\s+", names=None, skiprows=0, na_filter=None):
     kwargs = {
         "sep": sep,
         "names": names,
@@ -439,6 +444,7 @@ def load_table(f, sep=r"\s+", names=None, skiprows=0):
         "comment": "#",
         "float_precision": PRECISION,
         "skiprows": skiprows,
+        "na_filter": na_filter,
     }
     if names is not None:
         kwargs["header"] = None

### 2017-04-20 Manuscript/paper.tex
Improve figures

@@
 The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, this provides a rare opportunity to study electronic systems without the influence of the atomic nuclei.
+Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
 They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops.
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{figures/fig-shell-structure-v2}
-  \caption{Visualization of the 20 lowest single-particle states in the 2D harmonic oscillator basis.
+  \includegraphics{figures/fig-shell-structure-v2}
+  \caption{The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
 Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
-The $n$ quantum number increases upward vertically, starting at zero for the lowest state within each column.}
+Within each column, the principal quantum number $n$ increases as one traverses upward.}
   \label{fig:shell-structure}
@@
 \begin{figure}
-\includegraphics[width=.48\linewidth]{fig-diagrams-imsrg}
+\includegraphics{fig-diagrams-imsrg}
 \caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
@@
 Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.
-This provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.
+It provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.
 In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
@@
 \begin{figure}
-\includegraphics[width=.48\linewidth]{fig-diagrams-sfe}
+\includegraphics{fig-diagrams-sfe}
 \caption{Diagrammatic form of the second- and third-order QDPT corrections.
-The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.}
+The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.
+When QDPT is performed on IM-SRG-evolved Hamiltonians, many of the diagrams vanish.
+The remaining nonvanishing diagrams for addition energy are highlighted in blue and for removal energy are highlighted in red.}
 \label{fig:diagrams-sfe}
@@
 Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.
-
-Taking into account the perturbation corrections, one can obtain reasonably accurate addition and removal energies for single-particle states near the Fermi level via:
+We will refer to QDPT to third order as ``QDPT3''.
+
+Taking into account the perturbation corrections, one can extract reasonably accurate addition and removal energies for single-particle states near the Fermi level via:
 \begin{align*}
@@
 
-We will refer to QDPT to third order as ``QDPT3''.
+There is some degree of synergy between IM-SRG and QDPT: a generator that decouples the ground state energy will necessarily drive certain classes of matrix elements to zero.
+This means certain kinds of vertices in the diagrams become forbidden, reducing the number of nonzero diagrams at third order from 18 to only 4.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{figures/fig-methods}
+  \includegraphics{figures/fig-methods}
   \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
@@
   \centering
-  % [[LAYOUT]] The siunitx package somehow makes the columns unnecessarily wide so we have to compensate by shrinking the text size :/
-  \footnotesize
   \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
@@
   \centering
-  \footnotesize
   \caption{Extrapolated addition energies for quantum dots with fit uncertainties.  See Table \ref{tab:ground-extrapolated} for details.}
@@
   \centering
-  \footnotesize
   \caption{Extrapolated removal energies for quantum dots with fit uncertainties.  See Table \ref{tab:add-extrapolated} for details.}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-gs2}
+  \includegraphics{fig-gs2}
   \caption{Ground state energies for a selection of quantum dot parameters, plotted against the number of shells.}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-add2}
+  \includegraphics{fig-add2}
   \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-rm2}
+  \includegraphics{fig-rm2}
   \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-rel-slopes2}
+  \includegraphics{fig-rel-slopes2}
   \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG + QDPT3.
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-normal}
+  \includegraphics{fig-by-num-shells-6-2-ground-normal}
   \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.}
@@
   \centering
-  \includegraphics[width=\linewidth]{fig-by-freq-10-6-ground-0-normal}
-  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
+  \includegraphics{fig-by-freq-10-6-normal}
+  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
 The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
@@
 The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).}
-  \label{fig:by-freq-10-6-gs-0-normal}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \begin{subfigure}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{fig-by-freq-10-6-add-0-normal}
-    \caption{Addition energy}
-    \label{fig:by-freq-10-6-add-0-normal}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{fig-by-freq-10-6-rm-1-normal}
-    \caption{Removal energy}
-    \label{fig:by-freq-10-6-rm-1-normal}
-  \end{subfigure}
-  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
-Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree--Fock values.}
+  \label{fig:by-freq-10-6-normal}
 \end{figure}

### 2017-04-20 Datafiles/plot_by_freq.py

@@ -6,51 +6,78 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import utils
 
-p = argparse.ArgumentParser()
-p.add_argument("-i", "--interactive", action="store_true")
-p.add_argument("-t", "--title", action="store_true")
-p.add_argument("-int", "--interaction", default="normal")
-p.add_argument("label", metavar="type", help="ground, add, or rm")
-kwargs = vars(p.parse_args())
-plt.rcParams["interactive"] = kwargs["interactive"]
-with utils.plot(__file__):
-    d = utils.load_all()
-    num_shells = 10
-    num_filled = 2
-    interaction = kwargs["interaction"]
-    label = kwargs["label"]
-    ml = utils.label_num_filled_to_ml(label, num_filled)
+def plot(ax, label, interaction, num_shells, num_filled, title=False):
+    d = utils.filter_preferred_ml(utils.load_all())
     d = d[(d["method"] != "imsrg[f]+eom[n]") &
           (d["method"] != "magnus_quads+eom") &
           (d["interaction"] == interaction) &
           (d["label"] == label) &
           (d["num_shells"] == num_shells) &
           (d["num_filled"] == num_filled) &
-          # filter out higher frequencies because they stretch the plot too much
-          (d["freq"] <= 1.0) &
-          (d["ml"] == ml)]
-    num_particles = num_filled * (num_filled + 1)
-    energy_type = {"ground": "ground state",
-                   "add": "addition", "rm": "removal"}[label]
-    fig, ax = plt.subplots()
-    fig.set_size_inches((4, 3))
+          # filter out higher frequencies because they stretch horizontal axis
+          # of plot too much
+          (d["freq"] <= 1.0)]
+    base_markersize = 5.0
     for method, case in d.groupby("method"):
         case = case.sort_values("freq").drop_duplicates()
         xs = case["freq"]
         ys_ref = xs.map(lambda freq: d[(d["method"] == "hf") &
                                        (d["freq"] == freq)]["energy"])
         ys = case["energy"] / ys_ref
-        ax.plot(xs, ys, "-x", label=utils.METHOD_LABEL[method],
-                color=utils.METHOD_COLOR[method])
-    if kwargs["title"]:
+        marker = utils.METHOD_MARKER[method]
+        style = {
+            "marker": marker,
+            "markerfacecolor": "none",
[…]

### 2017-04-20 Datafiles/plot_by_freq.sh

@@ -1,8 +1,0 @@
-#!/bin/sh
-set -eu
-dir=`dirname "$0"`
-cd "$dir"
-
-./plot_by_freq.py ground
-./plot_by_freq.py add
-./plot_by_freq.py rm

### 2017-04-20 Datafiles/plot_by_num_shells.py

@@ -30,13 +30,22 @@ def plot(label, num_filled, freq,
                    "add": "addition",
                    "rm": "removal"}[label]
     fig, ax = plt.subplots()
-    fig.set_size_inches((4, 3))
+    fig.set_size_inches((3.2, 2.7))
+    base_markersize = 5 
     for method, case in d.groupby("method"):
         case = case.sort_values("num_shells")
         xs = case["num_shells"].astype(int)
         ys = case["energy"]
-        ax.plot(xs, ys, "-x", label=utils.METHOD_LABEL[method],
-                color=utils.METHOD_COLOR[method])
+        marker = utils.METHOD_MARKER[method]
+        style = {
+            "marker": marker,
+            "markerfacecolor": "none",
+            "markersize": (utils.MARKERSIZE_CORRECTION.get(marker, 1.0) *
+                           base_markersize),
+            "color": utils.METHOD_COLOR[method],
+            "label": utils.METHOD_LABEL[method],
+        }
+        ax.plot(xs, ys, **style)
         ax.get_xaxis().set_major_locator(
             matplotlib.ticker.MaxNLocator(integer=True))
     if len(d_dmc["energy"]):
@@ -45,9 +54,9 @@ def plot(label, num_filled, freq,
                    label=utils.METHOD_LABEL["dmc"],
                    color=utils.METHOD_COLOR["dmc"],
                    linestyle=utils.DMC_LINESTYLE)
-    ax.set_xlabel("K (number of shells)")
-    ax.set_ylabel("E (energy)")
-    ax.legend()
+    ax.set_xlabel("$K$ (number of shells)")
+    ax.set_ylabel("$E$ (energy)")
+    ax.legend(frameon=False)
     fig.tight_layout()
     utils.savefig(fig,
                   "by-num-shells-{num_particles}-{num_filled}-"

### 2017-04-20 Datafiles/plot_compare_rel_slopes.py

@@ -12,10 +12,10 @@ with utils.plot(__file__):
     # but matplotlib doesn't let us do that
     # so we have to use this awful hack
     interactions = [
-        ("", r"$(\sigma_{\mathrm{A}} = 0, \sigma_{\mathrm{B}} = \infty)$"),
-        ("_sigmaB=4.0", r"$(\sigma_{\mathrm{A}} = 0, \sigma_{\mathrm{B}} = 4)$"),
-        ("_sigmaA=0.5", r"$(\sigma_{\mathrm{A}} = \frac{1}{2}, \sigma_{\mathrm{B}} = \infty)$"),
-        ("_sigmaA=0.5_sigmaB=4.0", r"$(\sigma_{\mathrm{A}} = \frac{1}{2}, \sigma_{\mathrm{B}} = 4)$"),
+        ("", r"$(0, \infty)$"),
+        ("_sigmaB=4.0", r"$(0, 4)$"),
+        ("_sigmaA=0.5", r"$(\frac{1}{2}, \infty)$"),
+        ("_sigmaA=0.5_sigmaB=4.0", r"$(\frac{1}{2}, 4)$"),
     ]
     interaction_colors = {
         "": "#a883e4",
@@ -43,7 +43,9 @@ with utils.plot(__file__):
     d["system_pos"] = d.apply(
         lambda r: system_pos[(r["num_particles"], r["freq"])], axis=1)
 
-    fig, ax = plt.subplots(figsize=(5, 3.5))
+    width = 3.2
+    height = 3.0
+    fig, ax = plt.subplots(figsize=(width, height))
     for inter, g in sorted(d.groupby("interaction"),
                            key=lambda x: interaction_pos[x[0]]):
         g.sort_values(["freq", "num_particles"], inplace=True,
@@ -62,7 +64,9 @@ with utils.plot(__file__):
     ax.set_xlabel(r"$(N, \omega)$")
     ax.set_ylabel(r"$|\rho_{15}|$")
     ax.set_yscale("log")
-    ax.legend(loc="center left", bbox_to_anchor=(1.0, 0.5), frameon=False)
+    ax.legend(loc="center left", frameon=False,
+              title="$(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$",
+              bbox_to_anchor=(1.0 - 0.3 / width, 0.5))
     fig.tight_layout()
-    fig.subplots_adjust(right=0.65)
[…]

### 2017-04-20 Datafiles/plot_grid.py

@@ -52,10 +52,9 @@ def main(label):
     facet_to_num_particles_freq = lambda x, y: (x, y)
 
     has_dmc = False
-    width = 7
+    width = 6.5
     height = 3
     base_markersize = 5.0
-    linewidth = 1.0
     fig = plt.figure(figsize=(width, height))
     gs = matplotlib.gridspec.GridSpec(len(facet_y["ticks"]),
                                       len(facet_x["ticks"]))
@@ -78,8 +77,7 @@ def main(label):
             has_dmc = True
             ax.axhline(sel_dmc["energy"],
                        color=utils.METHOD_COLOR["dmc"],
-                       linestyle=utils.DMC_LINESTYLE,
-                       linewidth=linewidth)
+                       linestyle=utils.DMC_LINESTYLE)
 
         for method, d in d.groupby("method"):
             if method not in methods:
@@ -90,7 +88,6 @@ def main(label):
             d = d.sort_values(["num_shells"])
             marker = utils.METHOD_MARKER[method]
             ax.plot(d["num_shells"], d["energy"],
-                    linewidth=linewidth,
                     marker=marker,
                     markerfacecolor="none",
                     markersize=(utils.MARKERSIZE_CORRECTION.get(marker, 1.0) *
@@ -120,7 +117,6 @@ def main(label):
     markersize = (utils.MARKERSIZE_CORRECTION.get(marker, 1.0) *
                   base_markersize)
     lines = [matplotlib.lines.Line2D([], [],
-                                     linewidth=linewidth,
                                      marker=utils.METHOD_MARKER[method],
                                      markersize=markersize,
                                      color=utils.METHOD_COLOR[method],
@@ -128,7 +124,6 @@ def main(label):
              for method in methods]
     if has_dmc:
         lines.append(matplotlib.lines.Line2D([], [],
-                                             linewidth=linewidth,
                                              linestyle=utils.DMC_LINESTYLE,
                                              color=utils.METHOD_COLOR["dmc"],
                                              label=utils.METHOD_LABEL["dmc"]))

### 2017-04-20 Datafiles/tabulate.py

@@ -39,14 +39,14 @@ def save_table(path, label,
     if label == "ground":
         methods = ["hf", "mp2", "imsrg", "ccsd"]
         header = r"""
-        \begin{tabular}{SSSSSSS}%
+        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
         \toprule
         {$N$} & {$\omega$} & {$K$} & {HF} & {MP2} & {IM-SRG(2)} & {CCSD} \\
         """
     else:
         methods = ["hf+qdpt3", "imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
         header = r"""
-        \begin{tabular}{SSSSSSS}%
+        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
         \toprule
         {$N$} & {$\omega$} & {$K$} & {HF} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
         {} & {} & {} & {+QDPT3} & {+QDPT3} & {+EOM} & {+EOM} \\
@@ -106,14 +106,14 @@ def save_extrapolated_table(path, label,
     if label == "ground":
         methods = ["mp2", "imsrg", "ccsd"]
         header = r"""
-        \begin{tabular}{SSSSSS}%
+        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=4.6]S[table-format=4.6]S[table-format=4.6]}%
         \toprule
         {$N$} & {$\omega$} & {$K_{\text{stop}}$} & {MP2} & {IM-SRG(2)} & {CCSD} \\
         """
     else:
         methods = ["imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
         header = r"""
-        \begin{tabular}{SSSSSS}%
+        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.6]S[table-format=3.6]S[table-format=3.6]}%
         \toprule
         {$N$} & {$\omega$} & {$K_{\text{stop}}$} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
         {} & {} & {} & {+QDPT3} & {+EOM} & {+EOM} \\

### 2017-04-20 Datafiles/utils.py

@@ -26,7 +26,7 @@ JSON_PRETTY = {
 }
 
 METHOD_COLOR = {
-    "ccsd": "#1c5aa5",
+    "ccsd": "#428ff4",
     "ccsd+eom": "#1351c4",
     "dmc": "#666666",
     "fci": "#2e2360",
@@ -59,18 +59,25 @@ METHOD_LABEL = {
 
 METHOD_MARKER = {
     "ccsd": "o",
-    "ccsd+eom": "o",
+    "ccsd+eom": ".",
     "fci": "D",
     "hf": "^",
-    "hf+qdpt3": "^",
+    "hf+qdpt3": "s",
     "imsrg": "x",
-    "imsrg+eom": "+",
-    "imsrg+qdpt3": "x",
-    "mp2": "+",
+    "imsrg+eom": "*",
+    "imsrg+qdpt3": "+",
+    "mp2": "p",
 }
 
 MARKERSIZE_CORRECTION = {
     "D": 0.7,
+    "2": 1.5,
+}
+
+ENERGY_SYMBOL = {
+    "ground": r"E",
+    "add": r"\varepsilon^{(+)}",
+    "rm": r"\varepsilon^{(-)}",
 }
 
 DMC_LINESTYLE = "--"

### 2017-04-23 Manuscript/paper.tex
Add extrapolation fit

@@
 
+\begin{figure}
+  \centering
+  \includegraphics{fig-fit-2-1p0-add}
+  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system.
+The grey shaded region contains the masked data points, which are ignored by the fitting procedure.
+The left figure plots the central difference of the addition energies $\varepsilon^{(+)}$ with respect to the number of shells $K$.
+On such a plot, the power law model should appear as a straight line.
+The fits are optimized using the procedure described in Section \ref{subsec:extrapolation}.
+Note that the lines do not evenly pass through the points in the left plot as the fitting weights are tuned for the energy on a linear scale, not the energy differences on a logarithmic scale.}
+  \label{fig:by-fit-2-1p0-add}
+\end{figure}
+
 There is large amount of flexibility in the application of many-body methods.

### 2017-04-23 Datafiles/plot_specific_fit.py

@@ -28,8 +28,8 @@ def plot(label, num_filled, freq,
     energy_type = {"ground": "ground state",
                    "add": "addition",
                    "rm": "removal"}[label]
-    fig, ax = plt.subplots()
-    fig.set_size_inches((3.2, 2.7))
+    fig, ax = plt.subplots(1, 2)
+    fig.set_size_inches((6.5, 2.3))
     base_markersize = 5
     xc = np.linspace(num_shells_range[0] - 0.5, num_shells_range[1] + 0.5, 200)
     for method, case in d.groupby("method"):
@@ -45,24 +45,36 @@ def plot(label, num_filled, freq,
             "color": utils.METHOD_COLOR[method],
             "label": utils.METHOD_LABEL[method],
         }
-        ax.plot(xs, ys, linestyle="none", **style)
+        xms = 0.5 * (xs[1:] + xs[:-1])
+        yps = abs(ys.diff() / xs.diff())
+        ax[0].plot(xms, yps, linestyle="none", **style)
+        ax[1].plot(xs, ys, linestyle="none", **style)
         p = fits.get_fit_params(fit_data, np.max(xs), num_particles,
                                 freq, method)
-        ax.plot(xc, p["coefficient"] * xc ** p["exponent"] + p["constant"],
-                **utils.merge_dicts(style, {"marker": ""}))
-    ax.axvspan(np.min(xc), np.max(xs) - fits.DEFAULT_FIT_COUNT + 0.5,
-               color="#cccccc")
-    ax.set_xlim(np.min(xc), np.max(xc))
-    ax.get_xaxis().set_major_locator(
-        matplotlib.ticker.MaxNLocator(integer=True))
-    ax.set_xlabel("$K$ (number of shells)")
-    ax.set_ylabel("$E$ (energy)")
-    ax.legend(frameon=False)
+        ax[0].plot(xc, (abs(p["coefficient"] * p["exponent"]) *
+                        xc ** (p["exponent"] - 1)),
+                   **utils.merge_dicts(style, {"marker": ""}))
+        ax[1].plot(xc, p["coefficient"] * xc ** p["exponent"] + p["constant"],
+                   **utils.merge_dicts(style, {"marker": ""}))
+    for axi in ax:
+        axi.set_xlim(np.min(xc), np.max(xc))
+        axi.axvspan(np.min(xc), np.max(xs) - fits.DEFAULT_FIT_COUNT + 0.5,
[…]

### 2017-04-23 Datafiles/utils.py

@@ -9,8 +9,9 @@ import scipy.optimize
 # used for the 'float_precision' argument in pandas.read_csv
 # "round_trip" is preferable but it segfaults on some versions of Pandas:
 # https://github.com/pandas-dev/pandas/issues/15140
-if ("+" in pd.__version__ or
-        tuple(map(int, pd.__version__.split("."))) >= (0, 20, 0)):
+pd_ver = tuple(map(int, re.match("(\d+)\.(\d+)\.(\d+)",
+                                 pd.__version__).groups()))
+if "+" in pd.__version__ or pd_ver >= (0, 20, 0):
     PRECISION = "round_trip"
 else:
     PRECISION = "high"
@@ -42,18 +43,18 @@ METHOD_COLOR = {
 
 METHOD_LABEL = {
     "ccsd": "CCSD",
-    "ccsd+eom": "CCSD+EOM",
+    "ccsd+eom": "CCSD + EOM2",
     "dmc": "DMC",
     "fci": "FCI",
     "hf": "HF only",
     "hf+qdpt2": "HF only + QDPT2",
     "hf+qdpt3": "HF only + QDPT3",
     "imsrg": "IMSRG(2)",
-    "imsrg+eom": "IMSRG(2) + EOM",
+    "imsrg+eom": "IMSRG(2) + EOM2",
     "imsrg+qdpt2": "IMSRG(2) + QDPT2",
     "imsrg+qdpt3": "IMSRG(2) + QDPT3",
-    "imsrg[f]+eom[f]": "IMSRG(2)[F] + EOM[N]",
-    "magnus_quads+eom": "Magnus(2*) + EOM",
+    "imsrg[f]+eom[f]": "IMSRG(2)[F] + EOM2[N]",
+    "magnus_quads+eom": "Magnus(2*) + EOM2",
     "mp2": "MP2",
 }
 

### 2017-04-24 Manuscript/paper.tex
Update paper

@@
 
+There is great amount of flexibility in the application of many-body methods.
+The approaches we use is depicted in Figure \ref{fig:methods}.
+Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+
+The general process begins with the input matrix elements \eqref{eq:interactionintegral}, computed exactly using the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
+Internally, \texttt{OpenFCI} calculates the interaction integrals in the center-of-mass frame using Gauss--Hermite quadrature and transforms them back into the laboratory frame to produce matrix elements suitable for use in our many-body methods.
+
+Afterward, there are several paths through which one can traverse Figure \ref{fig:methods} to obtain output observables.
+We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
+
+It is possible to omit some steps of the process.
+For example, one can omit HF, but continue with the remaining two steps.
+While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
+Therefore, in practice there is little reason to omit HF.
+We will however investigate the effects of removing one or more of the post-HF methods.
+
+Since every calculation in this paper is begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
+
+All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
+This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
+Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
+\begin{align*}
+  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N \\
+  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}
+\end{align*}
+
+Ideally, ground state energy should be characterized entirely by the two system parameters $(N, \omega)$, where $N$ is number of particles and $\omega$ is the oscillator frequency.
+However, the methods that we study are limited to a \emph{finite} (truncated) basis and therefore their results are dependent on the level of truncation.
+This is characterized by $K$, the total number of shells in the single-particle basis.
+Thus, results are generally presented as a graph plotted against $K$.
+In Section \ref{subsec:extrapolation} discuss how to estimate results as $K \to \infty$ (infinite-basis limit) through \textit{extrapolations}.
+
+The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
+This is due to the presence of multiple states with near-degenerate energies.
+For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
+This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+
+Not all cases are solvable with our selection many-body methods.
+Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
+Cases where the methods required more than our allocated times to arrive at a result are marked ``n.c.'' (``no convergence'').
+For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').
+Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
+
+Numerical calculations in this paper are performed with a relative precision of about $10^{-5}$ or lower.
+This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate over the multiple steps of the calculation, thus the precision of the final results is expected to be roughly $10^{-4}$.
+
+\subsection{Comparison between methods}
+
+\subsubsection{Ground state energy}
+
 \begin{table}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics{fig-gs2}
+  \caption{Plots of ground state energy of quantum dots with $N$ particles and an oscillatory frequency of $\omega$ against the number of shells $K$.
+Since DMC does not utilize a finite basis, the horizontal axis is irrelevant and DMC results are plotted as horizontal lines.}
+  \label{fig:gs}
+\end{figure}
+
+In Figure \ref{fig:gs} we display a selection of ground state energies calculated using HF + CC and HF + CCSD as described in Section \ref{subsec:methodology}.
+We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.
+
+We do not include results from ``HF only'' to avoid overshadowing the comparatively smaller differences between the non-HF results in the plots.
+Some HF results can be found Figure \ref{fig:by-freq-10-6-normal} instead.
+Generally, HF ground state energies differ from the non-HF ones by a few to several percent, whereas non-HF energies tend to differ from each other by less than a percent.
+
+With respect to the number of shells, both IM-SRG(2) and CCSD appear to converge slightly faster than second order perturbation theory (MP2), likely due to the presence of higher order corrections in IM-SRG(2) and CCSD.
+
+There are a few cases where the IM-SRG over-corrects the result, leading to an energy lower than the quasi-exact DMC results.
+This is not unexpected given that, unlike Hartree--Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
+This over-correction tends to occur when the frequency is low (high correlation), or somewhat counterintuitvely, when \emph{few} particles are involved.
+
+\subsubsection{Addition and removal energies}
+
 \begin{table}
@@
 \end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig-add2}
+  \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
+  \label{fig:add}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig-rm2}
+  \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
+  \label{fig:rm}
+\end{figure}
+
+The results of our addition and removal energy calculations are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.
+The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
+Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
+
+As before, we do not include results from ``HF only'' in these plots as they are significantly further from the rest.
+Analogously, we also exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure CCSD, as QDPT or EOM both add significant contributions to addition and removal energies.
+Some HF only and pure IM-SRG results can be seen in Figure \ref{fig:by-freq-10-6-normal}.
+
+There is strong agreement between IM-SRG(2) + QDPT3 and IM-SRG(2) + EOM2 in many cases, and slightly weaker agreement between the IM-SRG and CCSD families.
+This suggests that the EOM2 corrections are largely accounted for by the inexpensive QDPT3 method.
+However, in some cases, most notably with few particles and high correlations (low frequency), the IM-SRG(2) + QDPT3 result differs significantly from both IM-SRG(2) + EOM2 and CCSD + EOM2.
+
+\subsection{Rate of convergence}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig-by-freq-10-6-normal}
+  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
+The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
+Lower frequency leads to stronger correlations and thereby a more difficult problem.
+The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).}
+  \label{fig:by-freq-10-6-normal}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig-rel-slopes2}
+  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
+For clarity, the plot does not distinguish between addition and removal energies.
+The horizontal axis shows the system parameters, where $N$ is the number of particles and $\omega$ is the oscillator frequency.
+The vertical axis shows $|\rho_{15}|$ (``relative slope''), which estimates the rate of convergence at 15 total shells.
+The lower the value of $|\rho_{15}|$, the faster the convergence.
+The data points are categorized by the interactions.
+The trends suggest that the singular short-range part of the interaction has a much stronger impact on the convergence than the long-range tail.}
+  \label{fig:rel-slopes}
+\end{figure}
+
+To analyze the rate of convergence more quantitatively, we shall define $\rho_K$ as the relative backward difference of the energy (\textit{relative slope}):
+\begin{align*}
+  \rho_K = \frac{\varepsilon_{K} - \varepsilon_{K - 1}}{\varepsilon_K}
+\end{align*}
+The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge.
+
+In Figure \ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) + QDPT3.
+The many-body methods were tested against a \emph{modified} Coulomb-like interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
+\begin{align}
+  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
+\end{align}
+where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.
+The coefficient is chosen to ensure the peak of the envelope remains at unity.
+With $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}) = (0, \infty)$ one recovers the original Coulomb interaction.
+By increasing $\sigma_{\mathrm{A}}$ one can truncate the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can truncate the long-range part of the interaction.
+For our numerical experiments we considered the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
+
+Reducing short-range part of the interaction appears improves the rate of convergence substantially.
+Many of the cases have reached the precision of the ODE solver ($10^{-5}$ to $10^{-6}$).
+In contrast, eliminating the long-range part of the interaction had very little effect.
+This suggests that the main cause of the slow convergence lies in the highly repulsive, short-ranged part of the interaction, which leads to the presence of nondifferentiable cusps (the so-called \textit{Coulomb cusps}) in the exact wave functions that are difficult to reproduce exactly using linear combinations of the smooth harmonic oscillator wave functions.
+
+The convergence is negatively impacted at lower frequencies and, to a lesser extent, by the increased number of particles.
+Both are expected: lower frequencies increase the correlation in the system, while higher number of particles naturally require more shells to converge.
+
+In general, there does not appear to be any difference between the convergence behavior of addition energies as compared to that of removal energies.
+
+\subsection{Extrapolation}
+\label{subsec:extrapolation}
 
@@
   \centering
-  \includegraphics{fig-gs2}
-  \caption{Ground state energies for a selection of quantum dot parameters, plotted against the number of shells.}
-  \label{fig:gs}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{fig-add2}
-  \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
-  \label{fig:add}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{fig-rm2}
-  \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
-  \label{fig:rm}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{fig-rel-slopes2}
-  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG + QDPT3.
-For clarity, the plot does not distinguish between addition and removal energies.
-The horizontal axis shows quantum system parameters, where $N$ is the number of particles and $\omega$ is the oscillator frequency.
-The vertical axis shows $|\rho_{15}|$ (``relative slope''), which estimates the rate of convergence at 15 total shells.
-The lower the value of $|\rho_{15}|$, the faster the convergence.
-The data points are categorized by the interactions.
-The trends suggest that the singular short-range part of the interaction has a much stronger impact on the convergence than the long-range tail.}
-  \label{fig:rel-slopes}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{fig-by-num-shells-6-2-ground-normal}
-  \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.}
-  \label{fig:by-num-shells-6-2-ground-0-normal}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics{fig-by-freq-10-6-normal}
-  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with 10 shells in the basis.
-The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
-Lower frequency leads to stronger correlations and thereby a more difficult problem.
-The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).}
-  \label{fig:by-freq-10-6-normal}
-\end{figure}
-
-\begin{figure}
-  \centering
   \includegraphics{fig-fit-2-1p0-add}
-  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system.
+  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.
 The grey shaded region contains the masked data points, which are ignored by the fitting procedure.
@@
 
-There is large amount of flexibility in the application of many-body methods.
-The approach we use is shown in Figure \ref{fig:methods}.
-Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
-
-The arrows in the diagram indicate the flow of numerical data, which are usually matrix elements of some many-body operator.
-For HF and IM-SRG, they are simply (evolved) Hamiltonian matrix elements.
-For CC, they would be elements of the cluster operator $\hat{T}$.
-
-There are several paths in this diagram through which one can traverse to obtain the output observables.
-Among these possibilities, we shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM, and (c) HF + CCSD + EOM.
-
-Moreover, one may also omit some steps of the process.
-For example, one can omit HF, but continue with the remaining two steps.
-While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
-Therefore, in practice there is little reason to omit HF.
-We will however investigate the effects of removing one or more of the post-HF methods.
-
-Since every calculation in this paper is begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
-
-All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
-This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
-Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
-\begin{align*}
-  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N \\
-  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}
-\end{align*}
-
-Ideally, ground state energy should be characterized entirely by the two system parameters $(N, \omega)$, where $N$ is number of particles and $\omega$ is the oscillator frequency.
-However, the methods that we study are limited to a \emph{finite} (truncated) basis and therefore their results are dependent on the level of truncation.
-This is characterized by $K$, the total number of shells in the single-particle basis.
-Thus, results are generally presented as a graph plotted against $K$.
-In Section \ref{subsec:extrapolation} discuss how to estimate results as $K \to \infty$ (infinite-basis limit) through \textit{extrapolations}.
-
-The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
-This is due to the presence of multiple states with near-degenerate energies.
-For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
-In particular, this means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
-
-Not all cases are solvable with our selection many-body methods.
-Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-Cases where the methods required more than our allocated times to arrive at a result are marked ``n.c.'' (``no convergence'').
-For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').
-Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
-
-All calculations in this paper are performed with a relative numerical precision of about $10^{-5}$ or lower (sometimes \emph{much} lower, as is for CC).
-This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate at every step of the calculation, thus the precision of the final results is more like $10^{-4}$.
-
-\subsection{Comparison between methods}
-
-\subsubsection{Ground state energy}
-
-In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the three approaches described in Section \ref{subsec:methodology}.
-We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison.
-
-Both perturbation theory and IM-SRG add significant corrections to the Hartree--Fock results.
-Compared with MP2, IM-SRG generally converges faster, although does not always converge to the DMC result.
-Generally speaking, IM-SRG is closer to the DMC result as the number of particles increases.
-
-There are a few cases where the IM-SRG over-corrects the result, leading to a ground state energy that is lower than the exact result.
-This is not unexpected given that, unlike Hartree--Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
-Overcorrection tends to occur when the number of particles is few, or the frequency is very low (high correlation).
-However, MP2 does not do much better in the high frequency regimes as it often converges slower than IM-SRG.
-
-The operator truncations in the evaluation of the commutator is one of the two sources of discrepancy between IM-SRG and exact results.
-The other source is that of basis truncation, which limits the size of the Hilbert space that can be explored by the method.
-Unlike operator truncation, which is difficult to overcome due to its exponentially increasing computational cost, the cost of increasing the basis is ``only'' polynomial with respect to the number of basis elements: roughly $O(N_{\mathrm{b}}^6)$ where $N_{\mathrm{b}}$ is the total number of states in the single-particle basis.
-In practice, the scaling cost is usually lower as the conserved symmetries allow the Hamiltonian to be partitioned into blocks.
-
-\subsubsection{Addition and removal energies}
-
-For our addition and removal energy calculations, the results are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.
-The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
-Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
-
-From these results, we see that the QDPT corrections add a substantial contribution to the results of both Hartree--Fock with and without IM-SRG.  [[quantify ``substantial'' numerically]]
-
-Interestingly, the addition energy of Hartree--Fock with second-order QDPT appears to surpass the accuracy of that of IM-SRG with second-order QDPT.
-This is likely coincidental, as the third-order QDPT dramatically worsens the result.
-
-Both Hartree--Fock and IM-SRG results worsen as the frequency decreases, which is not unexpected since the correlations become much more dominant.
-The Hartree--Fock appears to perform much worse, however, as the results converge much more slowly as the number of shells increases.
-
-We also note that IM-SRG with 2 particles and a frequency 0.1 generally fail to give any result as the ODE solver eventually leads to divergence [[Why?]]  This seems to be a quirk isolated to this particular system and does not usually occur in other systems.
-
-For addition and removal energies, we found that IM-SRG improves their rate of convergence both as the order of perturbation theory increases and as the number of shells increases.
-
-[[---]]
-
-\subsection{Rate of convergence}
-
-When the tail part of the convergence plots are magnified about a factor of ten or so [[double-check this number]], we noticed that the addition and removal energies are still drifting somewhat [[quantify how much]], hinting that the convergence rate is probably not exponential.
-
-To investigate the rate of convergence, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
-\begin{align}
-  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
-\end{align}
-where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.
-The coefficient is defined to ensure the peak of the envelope remains at unity.
-By setting $\sigma_{\mathrm{A}} = 0$ and $\sigma_{\mathrm{B}} = \infty$ one recovers the original Coulomb interaction.
-By increasing $\sigma_{\mathrm{A}}$ one can reduce the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can reduce the long-range part of the interaction.
-For our numerical experiments we consider the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
-
-To analyze the convergence as function of the number of shells $K$, we use a simple but approximate metric, the \textit{relative slope} at $K = 15$:
-\begin{align*}
-  \rho_{15}(\varepsilon) \equiv \frac{\varepsilon_{K = 15} - \varepsilon_{K = 14}}{\varepsilon_{K = 15}}
-\end{align*}
-For the systems we have selected, at $K = 15$ the addition and removal energies have essentially reached the asymptotic behavior (by visual inspection), thus $\rho_{15}$ gives a crude measure of the rate of convergence as a relative quantity independent of the energy unit, allowing it to be meaningfully compared between systems with different interactions and different particle numbers.
-The results are plotted in Figure \ref{fig:rel-slopes}.
-
-Analyzing the figure, we observe that the reducing short-range part of the interaction improves the rate of convergence greatly -- the relative slope has saturated and reached the precision of the ODE solver -- whereas eliminating the long-range part of the interaction had very little effect.
-This demonstrates that the main cause of the slow convergence lies in the highly repulsive, short-ranged part of the interaction, which leads to the presence of nondifferentiable cusps (the so-called \textit{Coulomb cusps}) in the exact wave functions that are difficult to reproduce exactly using linear combinations of the smooth harmonic oscillator wave functions.
-
-The figure also tells us that the convergence is negatively impacted at lower frequencies and, to a lesser extent, by the number of particles.
-Both are expected: lower frequencies increase the correlation in the system, while higher number of particles naturally require more shells to converge.
-
-We also note that the behavior of addition energies versus removal energies tend to be similar, and which one converges faster fluctuates from system to system.
-
-\subsection{Extrapolation}
-\label{subsec:extrapolation}
-
-As suggested by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the wave function can be approximately described by a power law model: [[assuming I understood his paper correctly]]
+As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
 \begin{align*}
@@
 \end{align*}
-where $\Delta E$ is the error in the energy, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.
-Essentially, the \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
-
-It is difficult to ascertain what $\beta$ is \textit{a priori}, but based on Kvaal's results $\beta$ is expected to be below $5$ for quantum dot systems.
-To determine this from our numerical calculations, we perform a curve using the following power-law model:
+where $\Delta E$ is the difference between the finite-basis result and the infinite-basis result, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.
+The \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
+
+It is difficult to ascertain what $\beta$ is \textit{a priori}, thus we will empirically compute $\beta$ by fitting the following model through our data:
 \begin{align} \label{eq:power_law_model}
@@
 \end{align}
-As with most nonlinear curve fits, it is often fairly sensitive to the initial parameters.
-To extract the initial parameters, we first do a linear fit on $\ln (\partial E / \partial K)$ against $\ln (K)$:
-\begin{align*}
-  \ln \left(\frac{\partial E}{\partial K}\right) = \ln(\alpha) - \beta \ln(K)
-\end{align*}
-The derivative is approximated using finite differences of adjacent data points:
+As a nonlinear curve fit, it can be quite sensitive to the initial parameters.
+Therefore, good guesses of the parameters are necessary to obtain a sensible result.
+For this, we first fit a linear model of $\log |\partial E / \partial K|$ against $\log K$:
+\begin{align*}
+  \log \left|\frac{\partial E}{\partial K}\right| = - (\beta + 1) \log K + \log|\alpha \beta|
+\end{align*}
+This is useful because linear fits are very robust and will often converge even if the initial parameters are complete nonsense.
+It also provides a means to visually judge quality of the fit.
+The derivative is approximated using the central difference:
 \begin{align*}
@@
 \end{align*}
-The process of calculating a derivative amplifies the noise, but linear fits do have the strong advantage of being very reliable to fit -- there is little concern about being stuck in a local minimum -- as well as making the results easy to judge by visually.
-Of course, linear fits do not weigh the individual contributions equally, thus a more accurate nonlinear curve fit is required afterward.
-
-We use the results as inputs for a power-law fit of $E$ against $K$, which is not as sensitive to noise.
-We do require a guess for the infinite-basis energy $\gamma$, which we estimate by fitting \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
-Finally, we do a fit with all three parameters free to vary.
-
-There is still one additional tuning knob for this model that is not explicitly shown in \eqref{eq:power_law_model}: the range of data points taken into consideration.
-Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still far from convergence.
-To remedy this, we restrict ourselves to fitting only the last few data points within some chosen range.
-If range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, the noise will obscure the result.
-This part is tuned by hand based on observations of the log-log plot: we expect the asymptotic region to lie more or less on a straight line.
-
-[[Idea for further exploration: see how much the extrapolation improves the result, and see what happens as we increase the number of shells included in the fit on the right/upper bound.]]
-
-Unlike all of the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not fit to well to the power-law model.
+The process of calculating a numericaly derivative can amplify the noise in the data and distorts the weights of the data points.
+Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
+Thus a second accurate nonlinear curve fit is necessary.
+
+The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
+It necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
+The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
+Afterward, we do a final fit with all three parameters free to vary.
+All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm as implemented in \texttt{Minpack}, with equal weighting of all data points.
+
+There is still one additional tuning knob for this model that is not explicitly part of \eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
+Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
+To account for this, we only fit the last few data points within some chosen range.
+If range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, there would be more noise and less confidence in whether the trend is legitimate rather than accidental.
+Empirically, we chose to fit the last 5 points of our available data.
+The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
+A specific example of the fit is shown in Figure \ref{fig:by-fit-2-1p0-add}
+
+The LM fitting procedure also computes uncertainties for the parameters from an approximate Hessian of the model function.
+It is therefore tempting to use the uncertainty of the fit to quantify the uncertainty of the extrapolated energy.
+We certainly would not expect this to account for the error due to the operator truncation, but how accurately does it quantify the discrepancy of our extrapolated result from the true infinite-basis energy?
+
+We investigated this idea by performing a fit over \emph{all possible} 5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.
+By comparing the extrapolated results at varying values of $K_{\text{stop}}$ with the extrapolated result at the highest possible $K_{\text{stop}}$ and treating the latter as the ``true'' infinite-basis result, we can statistically assess whether the fit uncertainties are a good measure of the discrepancy from the true infinite-basis result.
+Our results show a somewhat bimodal distribution: when the relative fit uncertainty is higher than $10^{-3.5}$, the fit uncertainty quantifies the discrepancy well; otherwise, the fit uncertainty underestimates the discrepancy by a factor of 10 or less.
+
+Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
 In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
-Based on the results with artificial softened interactions as well as past experiences, we believe this is an artifact of the insensitivity of Hartree--Fock theory to the Coulomb cusp.
+It is likely that HF is insensitive to the Coulomb cusp.
 
 Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
-This is likely due to its rapid convergence, which leaves very little degree of freedom even for a badly chosen model.
-Moreover, we find that the fit uncertainties of energy are also roughly within the right order of magnitude, surprisingly.
+This is likely due to its rapid convergence, which leaves very little degree of freedom even for a poorly chosen model.
+Moreover, we found that the fit uncertainties of energy are fairly good measures of the true discrepancy.
+
+Not all fits yield a positive value of $\beta$ for addition and removal energies, which suggests that the data points do not converge, or require a very high number of shells to converge.
+These cases are marked ``n.f.'' in the tables.
+This affects exclusively IM-SRG(2) + QDPT3 for systems with few particles and low frequencies, indicating that perturbation theory is inadequate for such systems.
 

### 2017-04-24 Datafiles/plot_grid.py

@@ -107,7 +107,7 @@ def main(label):
              horizontalalignment="center",
              verticalalignment="bottom",
              transform=ax.transAxes)
-    fig.text(0.05 / width, 0.5, "$E$ (energy)",
+    fig.text(0.05 / width, 0.5, "${}$".format(utils.ENERGY_SYMBOL[label]),
              horizontalalignment="left",
              verticalalignment="center",
              transform=ax.transAxes,

### 2017-04-24 Datafiles/tabulate.py

@@ -11,7 +11,7 @@ KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [
     (20, 7, 0.1),
 ])
 
-def render_entry(value, err=None, default_precision=5):
+def render_entry(value, err=None, default_precision=4):
     if isinstance(value, str):
         return "{" + value + "}"
     if np.isnan(value):
@@ -133,8 +133,9 @@ def save_extrapolated_table(path, label,
                         p = fits.get_fit_params(d, num_shells, num_particles,
                                                 freq, method)
                     except fits.NoMatchButBestExistsError as e:
-                        sys.stderr.write("warning: {!r}\n".format(e))
-                        sys.stderr.flush()
+                        if "--verbose" in sys.argv:
+                            sys.stderr.write("warning: {!r}\n".format(e))
+                            sys.stderr.flush()
                         return np.nan,
                     except KeyError:
                         return np.nan,

### 2017-04-24 Datafiles/utils.py

@@ -6,17 +6,26 @@ import numpy as np
 import pandas as pd
 import scipy.optimize
 
+def parse_version_digits(ver):
+    return tuple(map(int, re.match("(\d+)\.(\d+)\.(\d+)", ver).groups()))
+
 # used for the 'float_precision' argument in pandas.read_csv
 # "round_trip" is preferable but it segfaults on some versions of Pandas:
 # https://github.com/pandas-dev/pandas/issues/15140
-pd_ver = tuple(map(int, re.match("(\d+)\.(\d+)\.(\d+)",
-                                 pd.__version__).groups()))
-if "+" in pd.__version__ or pd_ver >= (0, 20, 0):
+if "+" in pd.__version__ or parse_version_digits(pd.__version__) >= (0, 20, 0):
     PRECISION = "round_trip"
 else:
     PRECISION = "high"
     sys.stderr.write("Warning: Your Pandas is too old. "
                      "Data read from files may lose accuracy.\n")
+    sys.stderr.flush()
+
+# we want deterministic PDFs, but this isn't supported until matplotlib 2.1+
+os.environ["SOURCE_DATE_EPOCH"] = "0"
+if not ("+" in matplotlib.__version__ or
+        parse_version_digits(matplotlib.__version__) > (2, 1, 0)):
+    sys.stderr.write("Warning: Your Matplotlib is too old. "
+                     "PDF output may be nondeterministic.\n")
     sys.stderr.flush()
 
 JSON_PRETTY = {
@@ -49,11 +58,11 @@ METHOD_LABEL = {
     "hf": "HF only",
     "hf+qdpt2": "HF only + QDPT2",
     "hf+qdpt3": "HF only + QDPT3",
-    "imsrg": "IMSRG(2)",
-    "imsrg+eom": "IMSRG(2) + EOM2",
-    "imsrg+qdpt2": "IMSRG(2) + QDPT2",
-    "imsrg+qdpt3": "IMSRG(2) + QDPT3",
-    "imsrg[f]+eom[f]": "IMSRG(2)[F] + EOM2[N]",
+    "imsrg": "IM-SRG(2)",
+    "imsrg+eom": "IM-SRG(2) + EOM2",
+    "imsrg+qdpt2": "IM-SRG(2) + QDPT2",
+    "imsrg+qdpt3": "IM-SRG(2) + QDPT3",
[…]

### 2017-04-27 Manuscript/paper.tex
Update Manuscript/paper.tex
Update fit data for fit_count=5

@@
 \end{align}
-Some literature use the M\o eller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.
+Some literature use the M\o ller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.
 
@@
 Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-Cases where the methods required more than our allocated times to arrive at a result are marked ``n.c.'' (``no convergence'').
+Cases where the methods required more than our allocated time to arrive at a result are marked ``n.c.'' (``no convergence'').
 For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').

### 2017-04-30 Manuscript/paper.tex
Add more data and fits
Fit data is now at Datafiles/fit_data.*.txt which has a simpler format
(without all the "best_*" columns, which actually caused a few cases to
be missing whenever there's only 1 data point for a particular system).

@@
 Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-Cases where the methods required more than our allocated time to arrive at a result are marked ``n.c.'' (``no convergence'').
-For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').
-Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
+Cases where IM-SRG converged too slowly to be feasible or diverged are marked ``n.c.(I)''.
+For the extrapolations in Section \ref{subsec:extrapolation}, some fits could not be done due to missing data caused by IM-SRG(2) or CCSD nonconvergence (``n.c.''); others converged but resulted in unphysical $\beta \le 0$ (``n.f.'').
+Cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
 

### 2017-04-30 Datafiles/fits.py

@@ -23,17 +23,21 @@ FIT_PARAM_KEYS = [
     "constant_err",
 ]
 
-class NoMatchButBestExistsError(KeyError):
-    pass
-
 def gather_fit_data(group, fit_count, maxfev):
     badness_threshold = plot_fit.LOGDERIV_BADNESS_THRESHOLD
     (label, interaction, num_filled, freq, method), gg = group
+    context = collections.OrderedDict([
+        ("label", label),
+        ("interaction", interaction),
+        ("num_filled", num_filled),
+        ("freq", freq),
+        ("method", method),
+    ])
     gg = gg.rename(columns={"num_shells": "x", "energy": "y"})
     gg = gg.sort_values(["x"])
     deriv_gg = plot_fit.differentiate(gg, "x", "y", "dydx")
+    results = []
     missing_num_shells = set()
-    subresults = []
     for fit_start in range(max(MIN_FIT_START, num_filled), MAX_FIT_START + 1):
         fit_stop = fit_start + fit_count - 1
         g = gg[gg["x"].between(fit_start, fit_stop)]
@@ -44,31 +48,99 @@ def gather_fit_data(group, fit_count, maxfev):
         deriv_g = deriv_gg[deriv_gg["x"].between(fit_start, fit_stop)]
         fit = plot_fit.do_fit(g, deriv_g, badness_threshold=badness_threshold,
                               maxfev=maxfev)
-        if fit is None:
-            continue
-        main_fit = fit.get("full", fit["fixedab"])
-        exponent = main_fit["exponent"]
-        if exponent > 0:
-            continue
-        constant = main_fit["constant"]
-        constant_err = main_fit["constant_err"]
-        subresults.append({
-            "fit_method": "full" if "full" in fit else "fixedab",
-            "fit_stop": fit_stop,
-            "chisq": np.linalg.norm(
-                g["y"]
-                - (main_fit["coefficient"] * g["x"] ** main_fit["exponent"]
-                   + main_fit["constant"])) ** 2,
-            "coefficient": main_fit["coefficient"],
-            "coefficient_err": main_fit.get("coefficient_err", float("nan")),
-            "exponent": exponent,
-            "exponent_err": main_fit.get("exponent_err", float("nan")),
-            "constant": constant,
-            "constant_err": constant_err,
-            "fixedab_constant_err": fit["fixedab"]["constant_err"],
-            "dist": g["y"].tail(1).iloc[0] - constant,
-            "dist_err": constant_err,
-        })
[…]

### 2017-04-30 Datafiles/plot_fit.py

@@ -1,4 +1,14 @@
 #!/usr/bin/env python3
+# This is the "main" script for doing fits one-by-one interactively.
+# (Non-interactive fitting is done by fits.py instead.)
+#
+# The script can be run interactively like this:
+#
+#     Datafiles/plot_fit.py rm num_filled=1 freq=1.0 fit_start=7
+#
+# All arguments to the 'plot' function in this script are accepted as
+# command-line arguments in the syntax above.
+#
 import argparse, itertools, json, logging, os, sys, traceback, warnings
 import matplotlib.pyplot as plt
 import matplotlib.ticker
@@ -189,7 +199,8 @@ def plot_fits(plot,
               get_color_label,
               get_dmc,
               dmc_label,
-              dmc_yerr_col=None):
+              dmc_yerr_col=None,
+              maxfev=0):
     # continuous x range for plotting continuous functions
     x_c = np.linspace(data[x_col].min() - 1, data[x_col].max() + 1, 250)
     [(title_key, gg)] = utils.groupby(data, title_cols)
@@ -225,7 +236,7 @@ def plot_fits(plot,
             continue
 
         fit = do_fit(d_subset, deriv_subset,
-                     badness_threshold=badness_threshold)
+                     badness_threshold=badness_threshold, maxfev=maxfev)
         if fit is None:
             continue
         fit_result = {
@@ -265,7 +276,8 @@ def plot_fits(plot,
             if b < 0:
                 ax[1].axhline(c, linestyle=":", color=color)
             else:
-                logging.warn(f"plot_fits: {stage}.b >= 0: no asymptotic result")
+                logging.warn(f"plot_fits: {label}: {stage}.b >= 0: "
+                             "no asymptotic result")
             utils.update_range(y_range, c)
 
     g = get_dmc(**title_key)
@@ -313,7 +325,7 @@ def plot_fits(plot,
 
 def plot(label, freq, num_filled, fit_start, fit_stop=np.inf,
          fit_ranges={}, interaction="normal", methods=None,
-         badness_threshold=LOGDERIV_BADNESS_THRESHOLD, plot=True):
+         badness_threshold=LOGDERIV_BADNESS_THRESHOLD, plot=True, maxfev=0):
     '''label: ground, add, or rm.
 
     fit_ranges: {method: (start, stop)}
@@ -364,6 +376,7 @@ def plot(label, freq, num_filled, fit_start, fit_stop=np.inf,
[…]

### 2017-04-30 Datafiles/plot_predictiveness.py

@@ -48,7 +48,7 @@ def plot(fit_count=fits.DEFAULT_FIT_COUNT, log=False,
         ["interaction", "label", "freq", "num_filled", "method"]
     ).first()
 
-    d = fits.load_full_fit_data(fit_count=fit_count, maxfev=maxfev)
+    d = fits.load_predictive_data(fit_count=fit_count, maxfev=maxfev)
 
     d = d[d["interaction"] == "normal"]
     # d = d[d["label"] == "add"]

### 2017-04-30 Datafiles/tabulate.py

@@ -4,19 +4,19 @@ import numpy as np
 import pandas as pd
 import fits, utils
 
-NUM_SHELLS = [12, 15, 15, 15, 20, 20]
+NUM_SHELLS = [12, 16, 16, 16, 20, 20]
 
-# known cases of IM-SRG that don't converge
+# known cases of IM-SRG(2) that don't converge
 KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [
     # diverged (no hope of convergence)
     (8, 3, 0.1),
     (11, 4, 0.1),
 
-    # took more than 500 steps to go from s = 0 to 2.0
+    # took more than 500 steps to reach s = 2.0
     (7, 4, 0.1),
     (7, 4, 0.28),
     (9, 4, 0.1),
-    (12, 5, 0.1),
+    (12, 5, 0.1),               # took more than 2000 steps to reach s = 0.001
     (12, 6, 0.1),
     (13, 6, 0.1),
     (15, 6, 0.1),
@@ -24,11 +24,18 @@ KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [
     (20, 7, 0.1),
 ])
 
+# known cases of CCSD that don't converge
+KNOWN_NC_CCSD = set((k, kf * (kf + 1), f) for (k, kf, f) in [
+    (20, 7, 0.1),
+])
+
 def render_entry(value, err=None, default_precision=4):
     if isinstance(value, str):
         return "{" + value + "}"
-    if np.isnan(value):
+    if value is None:
         return ""
+    if np.isnan(value):
+        return "NaN"
     if err is None:
         return "{{:.{}f}}".format(default_precision).format(value)
     if np.isnan(err):
@@ -74,16 +81,20 @@ def save_table(path, label,
             row = [num_particles, freq, num_shells]
             for method in methods:
                 def get(): # to allow early returns
-                    if ("imsrg" in method and
-                            (num_shells, num_particles, freq)
-                                in KNOWN_NC_IMSRG):
-                        return "n.c."
                     try:
                         r = d.loc[(num_shells, num_particles, freq, method)]
                     except KeyError:
-                        return np.nan
+                        return None
                     return r["energy"]
-                row.append(render_entry(get()))
+                value = get()
+                if value is None:
+                    if ("imsrg" in method and
+                        (num_shells, num_particles, freq) in KNOWN_NC_IMSRG):
+                        value = "n.c."
[…]

### 2017-04-30 Datafiles/utils.py

@@ -1,5 +1,5 @@
-import argparse, base64, collections, contextlib, decimal
-import functools, hashlib, io, json, logging, math, os, pickle, re, sys
+import argparse, base64, collections, contextlib, decimal, functools
+import hashlib, inspect, io, json, logging, math, os, pickle, re, sys
 import matplotlib
 import matplotlib.pyplot as plt
 import numpy as np
@@ -293,7 +293,7 @@ def intersperse(sep, xs):
         yield x
 
 def merge_dicts(d, *ds):
-    d = dict(d)
+    d = type(d)(d)
     for di in ds:
         d.update(di)
     return d
@@ -397,24 +397,24 @@ class FileDeps:
         '''The hash is computed on demand so that the file is only checked in
         the correct context (e.g. if the working directory needs to be changed
         before calling a function)..'''
-        return sha1_json([(path, os.path.getmtime(path))
-                          for path in sorted(paths)])
+        return [(path, os.path.getmtime(path))
+                for path in sorted(self._paths)]
 
 sanitize_json_handlers.append((FileDeps, lambda self: self._hash()))
 
-def cached(filenames=[], dir=".cache", hash=hashlib.sha1,
+def cached(dir=".cache", hash=hashlib.sha1,
            to_bytes=to_json_bytes, dump=pickle.dump, load=pickle.load):
-    filenames = tuple(filenames)
     def make_cached(func):
         h0_in = [func.__qualname__]
-        for filename in filenames:
-            with open(filename, "rb") as f:
-                h0_in.append(hash(f.read()).hexdigest())
         h0 = hash(to_bytes(h0_in)).hexdigest()
         name = "".join(re.findall(r"[-_.a-zA-Z0-9]+", func.__qualname__))
+        signature = inspect.signature(func)
         @functools.wraps(func)
         def wrapper(*args, **kwargs):
-            h_in = to_bytes((h0, args, kwargs))
+            # inspect.Signature is needed to obtain the default arguments
+            bound_arguments = signature.bind(*args, **kwargs)
+            bound_arguments.apply_defaults()
+            h_in = to_bytes((h0, dict(bound_arguments.arguments)))
             h = base64.urlsafe_b64encode(hash(h_in).digest()).decode("ascii")
             path = os.path.join(dir, "{}_{}.cache~".format(name, h.strip("=")))
             try:

### 2017-05-08 Manuscript/paper.tex
Added CCSD sections, refs, and diagrams

@@
 \newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
+\newcommand{\overbar}[1]{\mkern 3.0mu\overline{\mkern-3.0mu #1 \mkern-0.8mu}\mkern 0.8mu}
 
@@
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
-\author{Sam Novario}
+\author{Samuel J. Novario}
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
@@
 One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuation interaction method.
-Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increases to infinity (the so-called \textit{infinite-basis limit}).
+Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increased to infinity (the so-called \textit{infinite-basis limit}).
 Despite this significant advantage, it is often infeasible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
@@
 \end{align*}
-The allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
+This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
 The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
@@
 We use partial norms of the EOM ladder operators to make this determination:
-\begin{align}\label{eq:partial_norms}
+\begin{align}
+  \label{eq:partial_norms_p}
   n_{\text{1-particle}} &= \sqrt{\sum_p \bar{n}_p | \bar{x}^{[1,0]}_p |^2},\\
+  \label{eq:partial_norms_h}
   n_{\text{1-hole}} &= \sqrt{\sum_p n_p | \bar{x}^{[0,1]}_p |^2}.
@@
 
-\subsection{Coupled cluster theory}
-
-[[?]]
+\subsection{Coupled-cluster theory}
+\label{subsec:cctheory}
+
+Coupled-cluster theory is based on expressing the A-particle correlated wave function using the exponential ansatz, $\ket{\Psi} = e^{\hat{T}}\ket{\Phi}$.
+The cluster operator $\hat{T} = \hat{T}_{1} + \hat{T}_{2} + ...
++ \hat{T}_{A}$, is composed of $N$-particle $N$-hole excitation operators, $\hat{T}_{N}$,
+\begin{equation}\label{eq:cc_amps}
+\hat{T}_{N} = \left( \frac{1}{N!} \right)^{2}\sum\limits_{\substack{a_{1} \cdots a_{N} \\ i_{1} \cdots i_{N}}} \bar{n}_{a_{1}} \cdots \bar{n}_{a_{N}} n_{i_{1}} \cdots n_{i_{N}}\ t_{a_{1} \cdots a_{N}, i_{1} \cdots i_{N}}^{[N]}\ \normord{\hat a_{a_{1}}^\dagger \cdots \hat a_{a_{N}}^\dagger \hat a_{i_{N}} \cdots \hat a_{i_{1}}}
+\end{equation}
+which include unknown scalars, $t_{a_{1} \cdots a_{N}, i_{1} \cdots i_{N}}^{[N]}$, known as cluster amplitudes.
+
+Using the coupled cluster wave function, the Schr{\"o}dinger equation,
+\begin{equation}\label{eq:cc_schrodeq}
+\hat{H}e^{\hat{T}}\ket{\Phi} = Ee^{\hat{T}}\ket{\Phi},
+\end{equation}
+can be rewritten by left-multiplying by $\bra{\Phi}e^{-T}$ as,
+\begin{equation}\label{eq:ccsd0}
+\bra{\Phi}\overbar{H}_{CC}\ket{\Phi} = E,
+\end{equation}
+where we define an coupled cluster effective Hamiltonian,
+\begin{equation}\label{eq:cc_heff0}
+\overbar{H}_{CC} \equiv e^{-\hat{T}}\hat{H}e^{\hat{T}},
+\end{equation}
+in which the wave operator, $e^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.
+An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\overbar{H}$ is not Hermitian.
+
+The effective Hamiltonian in \eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker-Campbell-Hausdorff expansion as,
+\begin{equation*}\label{eq:cc_bch}
+\overbar{H}_{CC} = \hat{H} + [ \hat{H},\hat{T} ] + \frac{1}{2} [[ \hat{H},\hat{T} ],\hat{T} ] + \frac{1}{3!} [[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ] + \frac{1}{4!} [[[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ],\hat{T} ],
+\end{equation*}
+which terminates at four-nested commutators due to the two-body nature of the interaction.
+Like with IM-SRG, this commutator expression ensures that coupled cluster is size-extensive and contains only connected terms.
+In addition, because $\hat{T}$ is an excitation operator, terms of the form $\hat{T}\hat{H}$ are disconnected and thus vanish \cite{shavitt2009many}.
+Therefore the coupled cluster effective Hamiltonian can be further reduced to
+\begin{equation}\label{eq:cc_heff1}
+\overbar{H}_{CC} = \left( \hat{H}e^{\hat{T}} \right)_{c},
+\end{equation}
+where the label ``$c$'' indicates that only connected terms are used.
+
+In practice, $\hat{T}$ must be truncated to be computationally feasible.
+In this paper, we make the truncation that includes single and double excitations, $\hat{T} = \hat{T}_{1} + \hat{T}_{2}$, known as CCSD, which scales equivilently to IM-SRG(2).
+This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
+In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
+Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of \eqref{eq:cc_heff1} in CCSD.
+
+\begin{figure}
+\includegraphics{fig-diagrams-ccsd}
+\caption{Diagrammatic representation of $\overbar{H}$ of \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+The diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
+Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}^{[2]}$ are unconstrained.}
+\label{fig:diagrams-ccsd}
+\end{figure}
+
+The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying \eqref{eq:cc_schrodeq} by $\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{a}}e^{-\hat{T}}$ and $\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}e^{-\hat{T}}$, respectively.
+\begin{gather}\label{eq:ccsd1}
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{a}}\overbar{H}_{CC}\ket{\Phi} = 0 \\
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\overbar{H}_{CC}\ket{\Phi} = 0 \notag
+\end{gather}
+After the Fock matrix has been diagonalized, the diagonal components of \eqref{eq:ccsd1} can be separated and, after expanding the exponent in \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
+\begin{gather}\label{eq:ccsd2}
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{a}} \hat{H}^{[2]}( \hat{T}_{1} + \hat{T}_{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{1}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} )_{c} \ket{\Phi} = (H_{i,i}^{[1]} - H_{a,a}^{[1]})t_{a, i}^{[1]} \\
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \hat{H}^{[2]}( 1 + \hat{T}_{1} + \hat{T}_{2} + \frac{1}{2}\hat{T}_{1}^{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{2}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} + \frac{1}{2}\hat{T}_{1}^{2}\hat{T}_{2} + \frac{1}{4!}\hat{T}_{1}^{4} )_{c} \ket{\Phi} \notag \\
+\hspace{10cm} = (H_{i,i}^{[1]} + H_{j,j}^{[1]} - H_{a,a}^{[1]} - H_{b,b}^{[1]})t_{a, b, i, j}^{[2]} \notag
+\end{gather}
+These non-linear equations are solved using an iterative procedure that begins with an initial guess for the cluster amplitudes which are used to calculate the left-hand side of \eqref{eq:ccsd2}.
+Dividing by the denominator on the right-hand side gives updated amplitudes which are used to reevaluate the left-hand side.
+This proccess is repeated until the amplitudes reach a fixed point.
+Like the Hartree-Fock iterative procedure, employing similar convergence acceleration techniques can help improve the coupled cluster iterations.
 
 \subsubsection{EOM-CC}
-
-[[?]]
+\label{subsec:eomcc}
+Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
+Here, the non-Hermitian nature of $\overbar{H}_{CC}$ becomes apparent.
+In this case, in addition to constructing excitation ladder operators \eqref{eq:gen_attached} and \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
+\begin{align}
+  \label{eq:left_attached}
+    \hat{L}^{(N+1)}_w &= \sum_p \bar{n}_p l^{[1,0]}_p  \hat{a}_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r l^{[2,1]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p + \cdots,  \\
+  \label{eq:left_removed}
+    \hat{L}^{(N-1)}_w &= \sum_p n_p l_p^{[0,1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  l^{[1,2]}_{p, q, r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r + \cdots.
+\end{align}
+These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to \eqref{eq:EOMIMSRG},
+\begin{equation}\label{eq:left_EOM}
+  \bra{\Phi^{(N)}_0} [\overbar{H},\bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \overbar{L}^{(N \pm 1)}_w,
+\end{equation}
+and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_w}{\bar{X}^{(N \pm 1)}_u} = \delta_{w,u}$.
+
+In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
+In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle \eqref{eq:partial_norms_p} or single-hole \eqref{eq:partial_norms_h} natures are, in practice, not significant.
+Therefore, only the right-eigenvectors are used in this paper.
 
@@
 
-In Figure \ref{fig:gs} we display a selection of ground state energies calculated using HF + CC and HF + CCSD as described in Section \ref{subsec:methodology}.
+In Figure \ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
 We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.

### 2017-05-10 Manuscript/paper.tex
Fixups

@@
 \newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
-\newcommand{\overbar}[1]{\mkern 3.0mu\overline{\mkern-3.0mu #1 \mkern-0.8mu}\mkern 0.8mu}
 
@@
 Internal directed lines (bound/dummy indices) that point upward denote summations over unoccupied states, whereas lines that point downward denote summations over occupied states.
-External undirected lines denote unconstrained free indices.}
+External undirected lines denote unconstrained free indices.
+In IM-SRG(2), the three-body diagrams are not included.}
 \label{fig:diagrams-imsrg}
@@
 \begin{equation}\label{eq:ccsd0}
-\bra{\Phi}\overbar{H}_{CC}\ket{\Phi} = E,
+\bra{\Phi}\bar{H}_{\mathrm{CC}}\ket{\Phi} = E,
 \end{equation}
@@
 \begin{equation}\label{eq:cc_heff0}
-\overbar{H}_{CC} \equiv e^{-\hat{T}}\hat{H}e^{\hat{T}},
+\bar{H}_{\mathrm{CC}} \equiv e^{-\hat{T}}\hat{H}e^{\hat{T}},
 \end{equation}
 in which the wave operator, $e^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.
-An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\overbar{H}$ is not Hermitian.
+An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\bar{H}$ is not Hermitian.
 
@@
 \begin{equation*}\label{eq:cc_bch}
-\overbar{H}_{CC} = \hat{H} + [ \hat{H},\hat{T} ] + \frac{1}{2} [[ \hat{H},\hat{T} ],\hat{T} ] + \frac{1}{3!} [[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ] + \frac{1}{4!} [[[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ],\hat{T} ],
+\bar{H}_{\mathrm{CC}} = \hat{H} + [ \hat{H},\hat{T} ] + \frac{1}{2} [[ \hat{H},\hat{T} ],\hat{T} ] + \frac{1}{3!} [[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ] + \frac{1}{4!} [[[[ \hat{H},\hat{T} ],\hat{T} ],\hat{T} ],\hat{T} ],
 \end{equation*}
@@
 \begin{equation}\label{eq:cc_heff1}
-\overbar{H}_{CC} = \left( \hat{H}e^{\hat{T}} \right)_{c},
+\bar{H}_{\mathrm{CC}} = \left( \hat{H}e^{\hat{T}} \right)_{\mathrm{c}},
 \end{equation}
-where the label ``$c$'' indicates that only connected terms are used.
+where the subscript ``$\mathrm{c}$'' indicates that only connected terms are used.
 
@@
 \includegraphics{fig-diagrams-ccsd}
-\caption{Diagrammatic representation of $\overbar{H}$ of \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+\caption{Diagrammatic representation of $\bar{H}$ of \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
 The diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
@@
 \begin{gather}\label{eq:ccsd1}
-\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{a}}\overbar{H}_{CC}\ket{\Phi} = 0 \\
-\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\overbar{H}_{CC}\ket{\Phi} = 0 \notag
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{a}}\bar{H}_{\mathrm{CC}}\ket{\Phi} = 0 \\
+\bra{\Phi}\normord{ \hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\bar{H}_{\mathrm{CC}}\ket{\Phi} = 0 \notag
 \end{gather}
@@
 Dividing by the denominator on the right-hand side gives updated amplitudes which are used to reevaluate the left-hand side.
-This proccess is repeated until the amplitudes reach a fixed point.
+This process is repeated until the amplitudes reach a fixed point.
 Like the Hartree-Fock iterative procedure, employing similar convergence acceleration techniques can help improve the coupled cluster iterations.
@@
 Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
-Here, the non-Hermitian nature of $\overbar{H}_{CC}$ becomes apparent.
+Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
 In this case, in addition to constructing excitation ladder operators \eqref{eq:gen_attached} and \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
@@
 \begin{equation}\label{eq:left_EOM}
-  \bra{\Phi^{(N)}_0} [\overbar{H},\bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \overbar{L}^{(N \pm 1)}_w,
+  \bra{\Phi^{(N)}_0} [\bar{H},\bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_w,
 \end{equation}

### 2017-05-10 Datafiles/utils.py
Add new EOM data from Nathan

@@ -770,6 +770,7 @@ def load_addrm(toler=3e-7,
                    "EOM_IMSRG_FEI_HAM_particle_removed.dat",
                    "EOMIMSRG_up_to_16_attached.dat",
                    "EOMIMSRG_up_to_16_removed.dat",
+                   "EOM_particle_removed.dat",
                    "EOM_magnus_quads_attached.dat",
                    "EOM_magnus_quads_removed.dat",
                    "EOM_CCSD_qd_attached.dat",
@@ -795,56 +796,41 @@ def load_addrm(toler=3e-7,
     ds.append(d)
 
     # Nathan's EOM on Nathan's IMSRG matrix elements
-    d = load_table(files["EOM_IMSRG_qd_attached.dat"])
-    d = parse_nathan_like_data(d, "add")
+    d = pd.concat([
+        parse_nathan_like_data(
+            load_table(files["EOM_IMSRG_qd_attached.dat"]), "add"),
+        parse_nathan_like_data(
+            load_table(files["EOM_IMSRG_qd_removed.dat"]), "rm"),
+        parse_nathan_like_data(
+            load_table(files["freq_sweep_N6_R10_attached.dat"]), "add"),
+        parse_nathan_like_data(
+            load_table(files["freq_sweep_N6_R10_removed.dat"]), "rm"),
+        parse_nathan_like_data(
+            load_table(files["EOM-IMSRG_freq_sweep_6part_ml1_attached.dat"],
+                       names=NATHAN_ATTACHED_COLS), "add"),
+        parse_nathan_like_data(
+            load_table(files["EOM-IMSRG_freq_sweep_6part_ml1_removed.dat"],
+                       names=NATHAN_REMOVED_COLS), "rm"),
+        parse_nathan_like_data(
+            load_table(files["EOMIMSRG_up_to_16_attached.dat"],
+                       names=NATHAN_ATTACHED_COLS), "add"),
+        parse_nathan_like_data(
+            load_table(files["EOMIMSRG_up_to_16_removed.dat"],
+                       names=NATHAN_REMOVED_COLS), "rm"),
+        parse_nathan_like_data(
+            load_table(files["EOM_particle_removed.dat"],
+                       names=NATHAN_REMOVED_COLS), "rm"),
+    ], ignore_index=True)
     d["method"] = "imsrg+eom"
[…]

### 2017-05-10 Datafiles/plot_grid.py
Change which data is shown in figures and tables

@@ -7,10 +7,10 @@ import utils
 
 def main(label):
     num_shells_range = {
-        6: [3.5, 15.5],
-        12: [4.5, 15.5],
-        20: [6.5, 15.5],
-        30: [9.5, 20.5],
+        6: [3.5, 14.5],
+        12: [4.5, 16.5],
+        20: [6.5, 16.5],
+        30: [9.5, 16.5],
         42: [11.5, 20.5],
         56: [14.5, 20.5],
     }
@@ -18,11 +18,11 @@ def main(label):
     LEGEND_FACET_IDX = 2
 
     if label == "ground":
-        freq_ticks = [0.1, 1.0]
+        freq_ticks = [0.28, 1.0]
         methods = ["mp2", "imsrg", "ccsd", "fci"]
         fn = "../Manuscript/fig-gs2.pdf"
     else:
-        freq_ticks = [0.1, 0.28]        # 0.28 needed to show DMC results
+        freq_ticks = [0.28, 1.0]        # 0.28 needed to show DMC results
         fn = "../Manuscript/fig-{}2.pdf".format(label)
         methods = ["imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
 

### 2017-05-10 Datafiles/tabulate.py

@@ -4,7 +4,7 @@ import numpy as np
 import pandas as pd
 import fits, utils
 
-NUM_SHELLS = [12, 16, 16, 16, 20, 20]
+NUM_SHELLS = [14, 16, 16, 16, 20, 20]
 
 # known cases of IM-SRG(2) that don't converge
 KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [

### 2017-05-11 Manuscript/paper.tex
Add new EOM data from Nathan
More paper fixups + improve build system

--- 2017-04-30 Manuscript/paper.tex
@@
 \usepackage{siunitx}
-\usepackage{subcaption}
 
@@
 \begin{figure}
-  \includegraphics{figures/fig-shell-structure-v2}
+  \includegraphics{figures/fig-shell-structure-v2.pdf}
   \caption{The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
@@
 \begin{figure}
-\includegraphics{fig-diagrams-imsrg}
+\includegraphics{fig-diagrams-imsrg.pdf}
 \caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
@@
 This reduces the stiffness in the differential equation, providing a net increase in computational efficiency as stiff ODE solvers tend to be slower and consume more memory.
+
+\subsection{Coupled-cluster theory}
+\label{subsec:cctheory}
+
+Coupled-cluster theory is based on expressing the $N$-particle correlated wave function $\ket{\Psi}$ using the exponential ansatz,
+\begin{align*}
+  \ket{\Psi} = e^{\hat{T}}\ket{\Phi}
+\end{align*}
+where $\ket{\Phi}$ is the reference state as before.
+The cluster operator $\hat{T} \equiv \hat{T}_{1} + \hat{T}_{2} + ...
++ \hat{T}_{N}$, is composed of $k$-particle $k$-hole excitation operators, $\hat{T}_{k}$,
+\begin{align} \label{eq:cc_amps}
+  \hat{T}_{k} \equiv \left(\frac{1}{k!}\right)^{2}\sum\limits_{\substack{a_{1}, \dots, a_{k}, \\ i_{1}, \dots, i_{k}}} \bar{n}_{a_{1}} \cdots \bar{n}_{a_{k}} n_{i_{1}} \cdots n_{i_{k}} t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}} \normord{\hat a_{a_{1}}^\dagger \cdots \hat a_{a_{k}}^\dagger \hat a_{i_{k}} \cdots \hat a_{i_{1}}}
+\end{align}
+where the unknown matrix elements, $t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}}$, known as \textit{cluster amplitudes}.
+
+Using the coupled cluster wave function, the Schr\"odinger equation,
+\begin{align} \label{eq:cc_schrodeq}
+  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}}\ket{\Phi}
+\end{align}
+can be rewritten by left-multiplying by $\bra{\Phi}e^{-T}$ as,
+\begin{align*}
+  \bra{\Phi} \bar{H}_{\mathrm{CC}} \ket{\Phi} = E
+\end{align*}
+where we define a coupled-cluster effective Hamiltonian,
+\begin{align} \label{eq:cc_heff0}
+  \bar{H}_{\mathrm{CC}} \equiv \E^{-\hat{T}} \hat{H} \E^{\hat{T}}
+\end{align}
+in which the wave operator, $\E^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.
+An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\bar{H}$ is not Hermitian.
+
+The effective Hamiltonian in \eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker--Campbell--Hausdorff expansion as,
+\begin{align*}
+  \bar{H}_{\mathrm{CC}} = \hat{H} + [\hat{H}, \hat{T}] + \frac{1}{2} [[\hat{H}, \hat{T} ], \hat{T}] + \frac{1}{3!} [[[\hat{H}, \hat{T}], \hat{T}], \hat{T}] + \frac{1}{4!} [[[[\hat{H}, \hat{T}], \hat{T}], \hat{T}], \hat{T}]
+\end{align*}
+which terminates at four-nested commutators due to the two-body nature of the interaction.
+Like with IM-SRG, this commutator expression ensures that coupled cluster is size-extensive and contains only connected terms.
+In addition, because $\hat{T}$ is an excitation operator, terms of the form $\hat{T} \hat{H}$ are disconnected and thus vanish \cite{shavitt2009many}.
+Therefore the coupled cluster effective Hamiltonian can be further reduced to
+\begin{align} \label{eq:cc_heff1}
+  \bar{H}_{\mathrm{CC}} = \bigl(\hat{H}e^{\hat{T}}\bigr)_{\mathrm{c}}
+\end{align}
+where the subscript ``$\mathrm{c}$'' indicates that only connected terms are used.
+
+In practice, the cluster operator $\hat{T}$ must be truncated to be computationally feasible.  In this paper, we truncate it to only single and double excitations,
+\begin{align*}
+  \hat{T} = \hat{T}_{1} + \hat{T}_{2}
+\end{align*}
+This is known as coupled cluster singles and doubles (CCSD), with a asymptotic computational cost that scales like IM-SRG(2).
+This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
+In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
+Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of \eqref{eq:cc_heff1} in CCSD.
+
+\begin{figure}
+  \includegraphics{fig-diagrams-ccsd.pdf}
+  \caption{Diagrammatic representation of $\bar{H}$ of \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
+Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}^{[2]}$ are unconstrained.}
+  \label{fig:diagrams-ccsd}
+\end{figure}
+
+The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively.
+\begin{align} \label{eq:ccsd1}
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0 \\
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0 \notag
+\end{align}
+After the Fock matrix has been diagonalized, the diagonal components of \eqref{eq:ccsd1} can be separated and, after expanding the exponent in \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
+\begin{gather} \label{eq:ccsd2}
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \hat{H}^{[2]}(\hat{T}_{1} + \hat{T}_{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{1}^{2} + \frac{1}{3!}\hat{T}_{1}^{3})_{c} \ket{\Phi} = (H_{i, i}^{[1]} - H_{a, a}^{[1]}) t_{a, i}^{[1]} \\
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \hat{H}^{[2]} (1 + \hat{T}_{1} + \hat{T}_{2} + \frac{1}{2} \hat{T}_{1}^{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{2}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} + \frac{1}{2}\hat{T}_{1}^{2}\hat{T}_{2} + \frac{1}{4!}\hat{T}_{1}^{4} )_{c} \ket{\Phi} \notag \\
+= \Delta_{\{i, j\}, \{a, b\}} t_{a, b, i, j}^{[2]} \notag
+\end{gather}
+where $\Delta$ are the M\o ller--Plesset denominators from \eqref{eq:moellerplessetdenominator}.
+As usual, these non-linear equations are solved using an iterative procedure.
+One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of \eqref{eq:ccsd2}.
+Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side.
+This process is repeated until the amplitudes reach a fixed point.
+Like the Hartree--Fock iterative procedure, employing convergence acceleration techniques can reduce the number of coupled cluster iterations required.
 
@@
 \begin{figure}
-\includegraphics{fig-diagrams-sfe}
+\includegraphics{fig-diagrams-sfe.pdf}
 \caption{Diagrammatic form of the second- and third-order QDPT corrections.
@@
 \subsubsection*{EOM-IM-SRG}
+
 After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the correlated $N$-particle ground state energy.
 The EOM equation is therefore
-\begin{equation}\label{eq:EOMIMSRG}
+\begin{align} \label{eq:EOMIMSRG}
   [\bar{H},\bar{X}^{(N \pm 1)}_u] \ket{\Phi^{(N)}_0} = \pm \varepsilon^{(\pm)}_u \bar{X}^{(N \pm 1)}_u \ket{\Phi^{(N)}_0},
-\end{equation}
+\end{align}
 where bars denote rotated operators.
@@
 
-\subsection{Coupled cluster theory}
-
-[[?]]
-
-\subsubsection{EOM-CC}
-
-[[?]]
+\subsubsection*{EOM-CC}
+
+Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
+Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
+In this case, in addition to constructing excitation ladder operators \eqref{eq:gen_attached} and \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
+\begin{align*}
+    \hat{L}^{(N+1)}_w &= \sum_p \bar{n}_p l^{[1,0]}_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r l^{[2,1]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p + \cdots \\
+    \hat{L}^{(N-1)}_w &= \sum_p n_p l_p^{[0,1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  l^{[1,2]}_{p, q, r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r + \cdots
+\end{align*}
+These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to \eqref{eq:EOMIMSRG},
+\begin{align*}
+  \bra{\Phi^{(N)}_0} [\bar{H},\bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_w
+\end{align*}
+and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_w}{\bar{X}^{(N \pm 1)}_u} = \delta_{w,u}$.
+
+In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
+In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle \eqref{eq:partial_norms_p} or single-hole \eqref{eq:partial_norms_h} natures are, in practice, not significant.
+Therefore, only the right-eigenvectors are used in this paper.
 
@@
   \centering
-  \includegraphics{figures/fig-methods}
+  \includegraphics{figures/fig-methods.pdf}
   \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
@@
   \centering
-  \includegraphics{fig-gs2}
+  \includegraphics{fig-gs2.pdf}
   \caption{Plots of ground state energy of quantum dots with $N$ particles and an oscillatory frequency of $\omega$ against the number of shells $K$.
@@
   \centering
-  \includegraphics{fig-add2}
+  \includegraphics{fig-add2.pdf}
   \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
@@
   \centering
-  \includegraphics{fig-rm2}
+  \includegraphics{fig-rm2.pdf}
   \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
@@
   \centering
-  \includegraphics{fig-by-freq-10-6-normal}
+  \includegraphics{fig-by-freq-10-6-normal.pdf}
   \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
@@
   \centering
-  \includegraphics{fig-rel-slopes2}
+  \includegraphics{fig-rel-slopes2.pdf}
   \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
@@
   \centering
-  \includegraphics{fig-fit-2-1p0-add}
+  \includegraphics{fig-fit-2-1p0-add.pdf}
   \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.

### 2017-05-13 Datafiles/utils.py
Add new results from Nathan

@@ -770,6 +770,7 @@ def load_addrm(toler=3e-7,
                    "EOM_IMSRG_FEI_HAM_particle_removed.dat",
                    "EOMIMSRG_up_to_16_attached.dat",
                    "EOMIMSRG_up_to_16_removed.dat",
+                   "EOM_particle_attached.dat",
                    "EOM_particle_removed.dat",
                    "EOM_magnus_quads_attached.dat",
                    "EOM_magnus_quads_removed.dat",
@@ -817,6 +818,9 @@ def load_addrm(toler=3e-7,
         parse_nathan_like_data(
             load_table(files["EOMIMSRG_up_to_16_removed.dat"],
                        names=NATHAN_REMOVED_COLS), "rm"),
+        parse_nathan_like_data(
+            load_table(files["EOM_particle_attached.dat"],
+                       names=NATHAN_ATTACHED_COLS), "add"),
         parse_nathan_like_data(
             load_table(files["EOM_particle_removed.dat"],
                        names=NATHAN_REMOVED_COLS), "rm"),

### 2017-05-16 Datafiles/utils.py
Add Datafiles/missing_EOM_particle_attached.dat from Nathan

@@ -772,6 +772,7 @@ def load_addrm(toler=3e-7,
                    "EOMIMSRG_up_to_16_removed.dat",
                    "EOM_particle_attached.dat",
                    "EOM_particle_removed.dat",
+                   "missing_EOM_particle_attached.dat",
                    "EOM_magnus_quads_attached.dat",
                    "EOM_magnus_quads_removed.dat",
                    "EOM_CCSD_qd_attached.dat",
@@ -824,6 +825,9 @@ def load_addrm(toler=3e-7,
         parse_nathan_like_data(
             load_table(files["EOM_particle_removed.dat"],
                        names=NATHAN_REMOVED_COLS), "rm"),
+        parse_nathan_like_data(
+            load_table(files["missing_EOM_particle_attached.dat"],
+                       names=NATHAN_ATTACHED_COLS), "add"),
     ], ignore_index=True)
     d["method"] = "imsrg+eom"
     d["interaction"] = "normal"

### 2017-06-13 Manuscript/paper.tex
changed paper.tex

@@
 \begin{abstract}
-  We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
-We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using one of two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
-With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
-Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
-We examine the rate of convergence and perform extrapolations to the infinite basis limit using a power-law model.
+  We present and compare several many-body methods as applied to
+  two-dimensional quantum dots with circular symmetry.  We calculate
+  the approximate ground state energy using a harmonic oscillator
+  basis optimized by Hartree--Fock (HF) theory and further improve the
+  ground state energy using two post-HF methods: in-medium
+  similarity renormalization group (IM-SRG) and coupled cluster
+  singles-and-doubles (CCSD).  With the application of quasidegenerate
+  perturbation theory (QDPT) or the equation-of-motion (EOM) method,
+  we obtain addition and removal energies as well.  Our results are
+  benchmarked against full configuration interaction (FCI) and
+  diffusion Monte Carlo (DMC) where available.  We examine the rate of
+  convergence and perform extrapolations to the infinite basis limit
+  using a power-law model.
 \end{abstract}
@@
 
-The behavior of strongly confined electrons is of fundamental concern to many-body theory.
-The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificial constructed semiconducting heterostructures.
-Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
-Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
-This allows experiments to quantify the impact of quantum effects at different levels of correlation.
-
-The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
-They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops.
-
-Beyond their theoretical relevance, there are numerous potential applications quantum dots.
-The electrical and optical properties of quantum dots are particularly useful for solar cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser technology \cite{strauf2010,5075760}.
-They are have potential medical applications in diagnosis and treatment \cite{Ben-Ari02042003}.
-And of course, quantum dots are also promising candidates for the physical realization of quantum computing\cite{PhysRevA.57.120}.
-
-In general, quantum dot systems are not analytically solvable, with the exception of 2-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
-Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
-
-One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuation interaction method.
-Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increased to infinity (the so-called \textit{infinite-basis limit}).
-Despite this significant advantage, it is often infeasible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
-This led to the development of more cost-effective methods that trade varying amounts of accuracy for varying amounts of speed.
-
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
-We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results from existing literature.
-
-Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
-Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
-The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
-It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
-The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
-The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
-
-The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
-Our results are presented in Section \ref{sec:results}.
-We analyze and compare the differences between the various methods and also between different quantum dot systems.
-We examine the usefulness extrapolation techniques in improving the precision of the results.
-Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
+The behavior of strongly confined electrons is of fundamental concern
+to many-body theory.  The prototypical system is that of quantum dots,
+also known as ``artificial atoms'', in which electrons are confined
+within artificially constructed semiconducting heterostructures.  Such
+nanoscale systems are highly relevant as they lie at a critical point
+where both theoretical models and experimental observations can
+readily probe quantum phenomena such as tunneling, entanglement, and
+magnetization \cite{reimann2002,engel1993}.  Moreover, unlike many
+physical systems, quantum dots enjoy the benefit of being highly
+tunable through changes in the external field or the structure of the
+confining material.  This allows experiments to quantify the impact of
+quantum effects at different levels of correlation.
+
+The ground states of quantum dots exhibit shell structures and magic
+numbers similar to those of atoms and nuclei \cite{tarucha1996}.
+Thus, they provide a rare opportunity to study electronic systems
+without the influence of the atomic nuclei.  They also provide a
+testbed for the development of many-body methods for other systems
+with similar geometry, such as nuclei or neutrons drops \cite{bogner2010}.
+
+Beyond their theoretical relevance, there are numerous potential
+applications of quantum dots.  The electrical and optical properties of
+quantum dots are particularly useful for solar
+cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser
+technology \cite{strauf2010,5075760}.  They have potential medical
+applications in diagnosis and treatment \cite{Ben-Ari02042003}.  And
+of course, quantum dots are also promising candidates for the physical
+realization of quantum computing \cite{PhysRevA.57.120}.
+
+In general, quantum dot systems are not analytically solvable, with
+the exception of two-electron systems or systems with specific strengths
+of the external field \cite{PhysRevA.48.3561}.  Hence, in practical
+applications one can only hope for a numerical solution through
+some \textit{many-body method} or a combination thereof.
+
+One of the most accurate techniques for solving many-body systems is
+that of exact diagonalization, also known as the full configuration
+interaction method.  Unlike most methods, it is assured to converge to
+the exact answer as the size of the finite basis is increased to
+infinity (the so-called \textit{infinite-basis limit}).  Despite this
+significant advantage, it is often not possible  to perform exact
+diagonalization due to its factorially increasing cost with respect to
+the basis size and the number of particles.  This led to the
+development of more cost-effective methods that trade varying amounts
+of accuracy for varying amounts of speed.
+
+In this paper, we analyze the application of several methods to the
+quantum dot systems, including the Hartree--Fock (HF) method, M\o
+ller-Plesset perturbation theory (MP), the in-medium similarity
+renormalization group (IM-SRG) method, coupled cluster (CC)
+theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302},
+quasidegenerate perturbation theory (QDPT), and equation-of-motion
+(EOM) methods.  We compare them against variational and diffusion
+Monte Carlo (VMC and
+DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}
+and full configuration interaction 
+(FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102}
+results, where available,  from the existing literature.
+
+Of these methods, IM-SRG is a recently developed technique that has
+shown significant promises.  Similarity renormalization group (SRG)
+methods are a family of methods that transform the Hamiltonian into a
+band- or block-diagonal form through a continuous sequence of unitary
+transformations.  The goal of such a transformation is to reduce the
+coupling between a subspace of interest -- such as the ground state or
+a set of low-lying states -- and the remaining Hilbert space.  It has
+successfully been applied to systems with various underlying
+potentials to calculate their binding energy and other observables,
+especially in nuclear
+theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
+The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method
+to evolve Hamiltonians in a truncated Fock space, which avoids the
+prohibitive cost of constructing a full many-body Hamiltonian.  The
+effect of the truncation is minimized through the normal-ordering
+technique, which re-expands the operators with respect to a nearby
+many-body reference state rather than the far-away vacuum state.
+
+The article is organized as follows: Section \ref{sec:formalism}
+introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
+use to model circular quantum dots, and gives afterwards an overview
+of the \textit{ab initio} many-body methods used in this paper:
+Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.  Our results are presented in
+Section \ref{sec:results}.  We analyze and compare the differences
+between the various methods and also between different quantum dot
+systems.  We examine the usefulness of extrapolation techniques in
+improving the precision of the results.  Section \ref{sec:conclusions}
+concludes our work and gives perspectives for future work.
 
@@
 
-We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in 2-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2 r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
-The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
-
-Even though the model system contains 5 parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
-With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
-For rest of this paper, we shall use atomic units\footnote{Here, ``atomic unit'' is used in an \emph{abstract} sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$ correspond to true values in vacuum, or some effective value in medium.} where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
-Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
+We shall model the circular quantum dot system as a collection of $N$
+nonrelativistic electrons of mass $m$ in two-dimensional space, trapped
+by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, 
+where $\omega$ is the angular frequency of the oscillator
+trap and $r$ is the distance from the center of the trap.  The
+electrons interact with each other through the standard Coulomb
+interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of
+each electron, $\epsilon$ is the permittivity of the medium, and $R$
+is the distance between the two interacting electrons.
+
+Even though the model system contains five  parameters $(N, m, \omega,
+e, \epsilon)$, many of them are redundant.  With an appropriate choice
+of units, the number of parameters in the system can be reduced to
+just two.  For rest of this paper, we shall use atomic
+units
+%\footnote{Here, ``atomic unit'' is used in an \emph{abstract}
+%sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$
+%correspond to true values in vacuum, or some effective value in
+%medium.} 
+where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to
+one.  The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr
+radius $a$ becomes the unit of length:
 \begin{align*}
   E_{\mathrm{h}} &\equiv m \left(\frac{e^2}{4 \pi \epsilon \hbar}\right)^2 &
-  a &\equiv \frac{4 \pi \epsilon \hbar^2}{m e^2}
-\end{align*}
-This leaves us with $(N, \omega)$ as the only parameters necessary to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
-
-The behavior of each electron in isolation is described by the nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
-\begin{align*}
-  t(\bm{p}) &\equiv \frac{1}{2} \bm{p}^2 &
-  u(\bm{r}) &\equiv \frac{1}{2} \omega^2 \bm{r}^2 &
-  h(\bm{p}, \bm{r}) &\equiv t(\bm{p}) + t(\bm{r})
-\end{align*}
-Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is its position relative to the center of the trap.
-The pairwise interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$ is simply the Coulomb interaction:
-\begin{align*}
-  v(\bm{r}, \bm{r}') \equiv \frac{1}{|\bm{r} - \bm{r}'|}
+  a &\equiv \frac{4 \pi \epsilon \hbar^2}{m e^2}.
+\end{align*}
+This leaves us with $(N, \omega)$ as the only parameters necessary to
+specify the quantum dot system, with $\omega$ in units of
+$E_{\mathrm{h}} / \hbar$.
+
+The behavior of each electron in isolation is described by the
+nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy
+due to the trap $u(\bm{r})$, which combine to form the standard
+harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
+\begin{align*}
+  t(\bm{p}) &\equiv \frac{1}{2} \bm{p}^2, &
+  u(\bm{r}) &\equiv \frac{1}{2} \omega^2 \bm{r}^2, &
+  h(\bm{p}, \bm{r}) &\equiv t(\bm{p}) + t(\bm{r}).
+\end{align*}
+Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is
+its position relative to the center of the trap.  The pairwise
+interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$
+is simply the Coulomb interaction:
+\begin{align*}
+  v(\bm{r}, \bm{r}') \equiv \frac{1}{|\bm{r} - \bm{r}'|}.
 \end{align*}
@@
 \begin{align*}
-  \hat H \equiv \hat H^{[1]} + \hat H^{[2]}
-\end{align*}
-where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are the one- and two-body parts of the Hamiltonian,
+  \hat H \equiv \hat H^{[1]} + \hat H^{[2]},
+\end{align*}
+where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are the one- and two-body parts of the Hamiltonian, respectively, and given 
 \begin{align} \label{eq:onetwobodyhamiltonian}
-\hat{H}^{[1]} &\equiv \sum_{j = 1}^N h(\hat{\bm p}_j, \hat{\bm r}_j) &
-\hat{H}^{[2]} &\equiv \sum_{j_1 = 1}^N \sum_{j_2 = 1}^{j_1 - 1} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2})
-\end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
+\hat{H}^{[1]} &\equiv \sum_{j = 1}^N h(\hat{\bm p}_j, \hat{\bm r}_j), &
+\hat{H}^{[2]} &\equiv \sum_{j_1 = 1}^N \sum_{j_2 = 1}^{j_1 - 1} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2}).
+\end{align}
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th
+particle,\footnote{The ordering of the particle labels $j$ is
+unimportant as they exist only for the purpose of bookkeeping.} and
+$\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its
+momentum operator.
 
 \begin{figure}
-  \includegraphics{figures/fig-shell-structure-v2.pdf}
-  \caption{The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
-Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
-Within each column, the principal quantum number $n$ increases as one traverses upward.}
-  \label{fig:shell-structure}
+  \includegraphics{figures/fig-shell-structure-v2.pdf} \caption{The 42
+  lowest single-particle states (the first 5 shells) in the 2D
+  harmonic oscillator basis.  Each box represents a single-particle
+  state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the
+  up/down arrows indicate the spin of the states.  Within each column,
+  the principal quantum number $n$ increases as one traverses
+  upward.}  \label{fig:shell-structure}
 \end{figure}
@@
 \begin{align*}
-  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2
+  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2.
 \end{align*}
@@
 \begin{align*}
-  \hat{h} |p\rangle = \varepsilon_p |p\rangle
-\end{align*}
-where $p$ is an unknown tuple of quantum numbers.
-In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
-However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
-
-The Fock-Darwin wave functions can be decomposed into radial and angular components,\cite[Appx.\ A]{lohne2010coupled}
+  \hat{h} |p\rangle = \varepsilon_p |p\rangle,
+\end{align*}
+where $p$ is an unknown tuple of quantum numbers.  In Cartesian
+coordinates, the two-dimensional harmonic oscillator is trivially
+reducible to the well-known one-dimensional problem.  However, to
+exploit the circular symmetry, we prefer to use Fock-Darwin states,
+which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+Such states have the computationally useful property of conserving
+orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv
+-\mathrm{i} \partial / (\partial \varphi)$.
+
+The Fock-Darwin wave functions can be decomposed into radial and
+angular components,\cite{lohne2010coupled}
 \begin{align}
-  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n, |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin} \\
-  R_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2) \notag \\
-  A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi} \notag
-\end{align}
-where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre polynomial \cite[\S 18.3]{NIST:DLMF} of degree $n$ and parameter $\alpha$,
-\begin{align*}
-  L_n^{(\alpha)}(u) = \frac{1}{n!} u^{-\alpha} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{\alpha + n})
-\end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
-For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
-
-Since electrons are spin-$1/2$ fermions, they can occupy either of the two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
-Thus, every single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n,
+  |m_\ell|}(\sqrt \omega \rho)
+  A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\ R_{n, m}(\varrho)
+  &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 /
+  2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\ A_{m_\ell}(\varphi)
+  &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i}
+  m_\ell \varphi}, \notag
+\end{align}
+where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre
+polynomial \cite{NIST:DLMF} of degree $n$ and parameter $\alpha$,
+\begin{align*}
+  L_n^{(\alpha)}(u) = \frac{1}{n!} u^{-\alpha} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{\alpha + n}).
+\end{align*}
+The states are labeled by two quantum numbers: the principal quantum
+number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum
+projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
+For a wave function, $n$ indicates the degree of the Laguerre
+polynomial, whereas $m_\ell$ is simply the eigenvalue of
+$\hat{L}_{\mathrm{z}}$.
+
+Since electrons are spin-$1/2$ fermions, they can occupy either of the
+two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.  Thus, every
+single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$
+contains both a spatial component \eqref{eq:fockdarwin} and a spin
+component,
 \begin{align} \label{eq:singleparticlestate}
-  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}
+  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell,
+  m_{\mathrm{s}}) \rangle \equiv F_{n,
+  m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}.
 \end{align}
@@
 \begin{align} \label{eq:energysingleparticlestate}
-  \varepsilon_{n, m_\ell, m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega
+  \varepsilon_{n, m_\ell, m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega.
 \end{align}
@@
 \begin{align} \label{eq:shell_index}
-  k \equiv 2 n + |m_\ell|
-\end{align}
-which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
-
-Returning to the many-body Hamiltonian $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
-Note that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
+  k \equiv 2 n + |m_\ell|,
+\end{align}
+which we conveniently call the \textit{shell index} as it labels each
+shell starting from zero.  The shells are equidistant with an energy
+spacing equal to the frequency $\omega$.
+
+Returning to the one-body part of the many-body Hamiltonian,
+$\hat{H}^{[1]}$, we can use the Slater determinant construction to
+build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the
+many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$
+single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$
+from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for
+the triplet $(n, m_\ell, m_{\mathrm{s}})$.  Note that a Slater
+determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the
+single-particle states, but an antisymmetrized sum over all possible
+products,
 \begin{align*}
@@
   \end{matrix}
-  \right|
-\end{align*}
-The Slater determinant $|p_1, \ldots, p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
-By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
+  \right|.
+\end{align*}
+The Slater determinant $|p_1, \ldots, p_N\rangle$ is said
+to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.  By
+construction, Slater determinants satisfy the Pauli exclusion
+principle, ensuring that the exchange of any two particles is
+equivalent to a reversal in the sign of the many-body wave function.
 
@@
 \end{align*}
-It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
-This is possible even for ground states of $\hat{H}^{[1]}$.
-However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
-The values of $N$ at which this occurs are said to be \textit{magic numbers}.
-We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
-In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
-
-Currently, the Hamiltonian $\hat{H}$ is defined for a fixed number of particles $N$.
-Through the formalism of second quantization, the many-body machinery can be made agnostic to number of particles, in analogy to quantum field theory.
-Instead of considering the Hilbert space for exactly $N$ particles, we combine every space with $N = 0, 1, 2, \ldots$ particles into a combined Hilbert space called the Fock space.
-To establish relationships between states with differing number of particles, we introduce the \textit{field operators} $\hat{a}_p^\dagger$ and $\hat{a}_p$ to increment and decrement the number of particles in a state, respectively.
-The linear operator $\hat{a}_p^\dagger$ is known as \textit{creation operator} for the single-particle state $p$.
-Its action on an arbitrary Slater determinant is defined as:
-\begin{align*}
-  \hat a_p^\dagger |p'_1, \ldots, p'_N\rangle =
-  |p, p'_1, \ldots, p'_N\rangle
-\end{align*}
-Informally, it is said to \textit{create} a particle in the state $p$.
-If $p$ coincides with any of the existing $p'_1, \ldots, p'_N$, then antisymmetrization would collapse the state to the number $0$, an invalid state.
-The Hermitian conjugate of $\hat{a}_p^\dagger$ is $\hat{a}_p$, which known as the \textit{annihilation operator} for the state $p$.
-By analogy, its action is to remove the state $p$ from a Slater determinant, or collapse it to the number $0$ if the state $p$ was not occupied in the Slater determinant.
-
-From here, one can show that Slater determinants themselves can be built directly from the the unique \textit{vacuum state} $|\rangle$ with no particles ($N = 0$):
-\begin{align*}
-  |p_1, \ldots, p_N\rangle =
-  \hat a_{p_1}^\dagger \cdots \hat a_{p_N}^\dagger |\rangle
-\end{align*}
-To properly describe fermions, the field operators $\hat a_p$ and $\hat a_p^\dagger$ must satisfy the anticommutation relations that encode the Pauli principle,
-\begin{align*}
-  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0 &
-  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}
-\end{align*}
-
-In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from \eqref{eq:onetwobodyhamiltonian} can be rewritten as\footnote{The peculiar ordering of $\hat a_s \hat a_r$ here is not a typographical error.}
+It is possible for Slater determinants occupying different sets of
+single-particle states to be degenerate in energy.  This is possible
+even for ground states of $\hat{H}^{[1]}$.  However, if the number of
+particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for
+some nonnegative integer $K_{\mathrm{F}}$, there would be just enough
+particles to form a closed-shell Slater determinant, leading to a
+unique, well-isolated ground state.  The values of $N$ at which this
+occurs are said to be \textit{magic numbers}.  We call
+$K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi
+level'').  In particular, a single-particle state is occupied in the
+ground state Slater determinant if and only $k < K_{\mathrm{F}}$,
+where $k$ is the shell index of the single-particle state as defined
+in \eqref{eq:shell_index}.
+
+In this work we will mainly work with the formalism of second quantization, see for example Ref.~\cite{shavitt2009many}.
+To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
+These operators must satisfy the anticommutation relations that encode the Pauli principle, namely
+\begin{align*}
+  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
+  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}.
+\end{align*}
+
+In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from Eq.~\eqref{eq:onetwobodyhamiltonian} can be rewritten as
 \begin{align} \label{eq:second_quantized_hamiltonian}
-  \hat H^{[1]} &= \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{} &
-  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}
-\end{align}
-where the numeric coefficients $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
-In this paper, we use the letters $p, q, r, s, t, \ldots$ to label arbitrary single-particle \textit{states} in the basis.
-For the harmonic oscillator basis, labels such as $p$ can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
-A summation such as $\sum_p$ is then understood as a summation over every single-particle basis state $p$.
-This is not to be confused with summations such as $\sum_j$ from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$ denoting an arbitrary \textit{particle}.
-We thus see another benefit with second quantization: the Hamiltonian representation makes no attempt to distinguish particles at all, as expected for particles with quantum statistics.
+  \hat H^{[1]} &= \sum_{pq} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{}, &
+  \hat{H}^{[2]} &= \frac{1}{4} \sum_{pqrs} \langle pq | \hat{H}^{[2]} | rs \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}.
+\end{align}
+where the quantities $\langle p | \hat{H}^{[1]} | q \rangle$
+and $\langle pq | \hat{H}^{[2]} | rs \rangle$ are known
+as \textit{matrix elements} and fully characterize the two operators
+in the basis.  In this paper, we use the letters $p, q, r, s,
+t, \ldots$ to label arbitrary single-particle \textit{states} in the
+basis.  For the harmonic oscillator basis, labels such as $p$ can be
+considered abbreviations for triplets of the form $(n, m_\ell,
+m_{\mathrm{s}})$.  A summation such as $\sum_p$ is then understood as
+a summation over every single-particle basis state $p$.  This is not
+to be confused with summations such as $\sum_j$
+from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$
+denoting an arbitrary \textit{particle}.  We thus see another benefit
+with second quantization: the Hamiltonian representation makes no
+attempt to distinguish particles at all, as expected for particles
+with quantum statistics.
 
@@
 \begin{align}
-  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p, q, r, s} \langle p, q | \hat{H}^{[2]} | r, s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r  \label{eq:vacuumhamiltonian}
-\end{align}
-Due to antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p, q | \hat{H}^{[2]} | r, s \rangle$, leading to a 4-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
-For this reason, the two-body matrix element $\langle p, q | \hat{H}^{[2]} | r, s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the (non-antisymmetric) interaction integral,
+  \hat{H} = \sum_{p,q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{pqrs} \langle pq | \hat{H}^{[2]} | rs \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r .
+\label{eq:vacuumhamiltonian}
+\end{align}
+Due to the antisymmetry of Slater determinants, we have the property
+that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign
+of $\langle pq | \hat{H}^{[2]} | rs \rangle$, leading to a 4-fold
+symmetry that must be canceled out by the $1/4$ factor in front of the
+summation in \eqref{eq:vacuumhamiltonian}.  For this reason, the
+two-body matrix element $\langle pq | \hat{H}^{[2]} | rs \rangle$
+is commonly referred to as the \emph{antisymmetrized} matrix element.
+This is not to be confused with the (non-antisymmetric) interaction
+integral,
 \begin{align} \label{eq:interactionintegral}
-  v_{p_1, p_2, p_3, p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'
-\end{align}
-This object only has a 2-fold symmetry: $v_{p_1, p_2, p_3, p_4} = v_{p_2, p_1, p_4, p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
+  v_{p_1p_2p_3p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'.
+\end{align}
+This object only has a two-fold symmetry: $v_{p_1p_2p_3p_4} = v_{p_2p_1p_4p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
 \begin{align} \label{eq:antisymmetricmatrixelement}
-  \langle p, q | \hat{H}^{[2]} | r, s \rangle = v_{p, q, r, s} - v_{p, q, s, r}
-\end{align}
-
-With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
-The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
-Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
-
-However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
-This is a general strategy for many of the many-body methods that we shall describe.
+  \langle pq | \hat{H}^{[2]} | rs \rangle = v_{pqrs} - v_{pqsr}
+\end{align}
+
+With the basic formalism and notation established along with the
+system of interest, we may begin to discuss the various techniques to
+solve the full many-body problem.  The principal difficulty stems from
+the fact that, due to the presence of interactions, the exact solution
+is in general \emph{not} a single Slater determinant built from the
+single-particle states.  Hence, it is not possible to trivially reduce
+the problem to that of a single particle as we had done previously.
+
+However, if we assume the interaction alters the behavior of the
+system only mildly, we can use a Slater determinant of the
+noninteracting system as a starting point and then apply various
+methods to improve the accuracy of the solution.  This is a general
+strategy for many of the many-body methods that we shall describe.
 
@@
 
-One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
-Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value
+One of the simplest numerical corrections that could be applied to the
+initial guess is that of the Hartree--Fock (HF) method.  Using the
+variational principle, one can compute an approximate ground state
+$\Phi$ by minimizing the energy expectation value
 \begin{align} \label{eq:hfexpectation}
@@
 \end{align}
-with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
-The restriction is what enables the simplicity and efficiency of this method.
-We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
-\begin{align*}
-  |q'\rangle \equiv \sum_p |p\rangle C_{p, q'}
-\end{align*}
-This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
-The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
-
-If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
-
-To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
-These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
-At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
+with respect to $|\Phi\rangle$, subject to the restriction that
+$|\Phi\rangle$ remains a single Slater determinant constructed from an
+unknown single-particle basis.  The restriction is what enables the
+simplicity and efficiency of this method.  We shall denote each
+unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To perform numerical calculations, we further assume that each unknown
+state $|q'\rangle$ is built from a linear combination of known states
+$|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined
+via the transformation equation
+\begin{align*}
+  |q'\rangle \equiv \sum_p |p\rangle C_{pq'}.
+\end{align*}
+This allows the problem to be reduced from an abstract minimization
+problem \eqref{eq:hfexpectation} to a concrete numerical problem.  The
+caveat is that the set of known functions be large enough to capture
+the relevant behavior of the system.
+
+If the interaction is not too strong, it is common to use the
+single-particle states of the noninteracting Hamiltonian
+$\hat{H}^{[1]}$ as the set of known states.
+
+To ensure orthonormality of the states, we require there to be as many
+unknown states $|q'\rangle$ as known states $|p\rangle$, and the
+coefficient matrix $\bm C$ must be unitary.  These conditions are more
+strict than necessary, but they greatly simplify the calculations and
+allow the states $|q'\rangle$ to act as \textit{optimized} inputs for
+methods beyond HF.  At the end of the calculation, of the set of
+states $|q'\rangle$ there would exactly $N$ \textit{occupied} states
+that participate in the optimized Slater determinant $|\Phi\rangle$.
+The remaining \textit{unoccupied} states serve as the complementary
+space into which particles can be excited by the interaction
+$\hat{H}^{[2]}$ during the post-HF calculation.
 
@@
 \begin{align}
-  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{i, i} + \sum_{i, j} n_i n_j H^{[2] \prime}_{i, j, i, j} \label{eq:hfenergy}
+  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{ii} + \sum_{ij} n_i n_j H^{[2] \prime}_{ijij} \label{eq:hfenergy},
 \end{align}
@@
 \begin{align}
-  H^{[1] \prime}_{p, q} &\equiv \sum_{r, s} C_{r, p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s, q}^{} \label{eq:hftransform1} \\
-  H^{[2] \prime}_{p, q, r, s} &\equiv \sum_{t, u, v, w} C_{t, p}^* C_{u, q}^* \langle t, u | \hat{H}^{[2]} | v, w \rangle C_{v, r}^{} C_{w, s}^{} \label{eq:hftransform2}
+  H^{[1] \prime}_{pq} &\equiv \sum_{rs} C_{rp}^* \langle r | \hat{H}^{[1]} | s \rangle C_{sq}^{} \label{eq:hftransform1} \\
+  H^{[2] \prime}_{pqrs} &\equiv \sum_{tuvw} C_{tp}^* C_{uq}^* \langle tu | \hat{H}^{[2]} | vw \rangle C_{vr}^{} C_{ws}^{}, \label{eq:hftransform2}
 \end{align}
@@
   n_p \equiv \begin{cases}
-    1 & \text{if $p$ is an occupied state in $\Phi$} \\
-    0 & \text{if $p$ is an unoccupied state in $\Phi$}
+    1 & \text{if $p$ is an occupied state in $\Phi$}, \\
+    0 & \text{if $p$ is an unoccupied state in $\Phi$}.
   \end{cases}
@@
 
-With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree--Fock equation}:
+With the method of Lagrange multipliers, the minimization problem can
+be reduced to the solving of a nonlinear equation --
+the \textit{Hartree--Fock equation}:
 \begin{align} \label{eq:hartreefock}
-  \bm{F} \bm{C} = \bm{C} \bm{\varepsilon}
+  \bm{F} \bm{C} = \bm{C} \bm{\varepsilon},
 \end{align}
@@
 \begin{align} \label{eq:fock}
-  F_{p, q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r, s, i} n_i C_{r, i}^* \langle p, r | \hat{H}^{[2]} | q, s \rangle C_{s, i}^{}
+  F_{pq} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{rsi} n_i C_{ri}^* \langle pr | \hat{H}^{[2]} | qs \rangle C_{si}^{},
 \end{align}
@@
 
-Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
-We begin with an initial guess $\bm{C}^{(i)}$, which is fed into \eqref{eq:fock} to produce the Fock matrix.
-This is then used in \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
-This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
-While in theory it is possible for the solution to never reach a fixed point, or that it may require a unfeasibly large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
-In other cases where it is insufficient, methods such as DIIS, Broyden's method, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
-Therefore, the possibility of slow or non-convergence is generally not a concern in practice.
-
-For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity matrix.
-At each iteration, we calculate the sum of the Lagrange multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration should decrease rapidly.
-
-Since HF restricts the ground state to merely a single Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
-The discrepancy between the Hartree--Fock energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
-The focus of post-HF methods such as IM-SRG or coupled cluster is to add corrections beyond mean-field approximations such as HF.
-
-To make use of the HF solution as the reference state for future calculations, we transform the operators via \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
-Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
-However, we will not annotate them with the prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
+Aside from trivial cases, the HF equation is generally solved using an
+iterative algorithm.  We begin with an initial guess $\bm{C}^{(i)}$,
+which is fed into Eq.~\eqref{eq:fock} to produce the Fock matrix.  This is
+then used in Eq.~\eqref{eq:hartreefock}, which leads to a standard
+eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix
+of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of
+eigenvalues.  This process can be repeated indefinitely until $\bm{C}$
+approaches a fixed point.  While in theory it is possible for the
+solution to never reach a fixed point, or that it may require a
+unfeasibly large number of iterations, in practice this naive approach
+can adequately provide solutions for many cases.  In other cases where
+it is insufficient, methods such as DIIS, Broyden's method, or
+even \textit{ad hoc} linear mixing can improve and accelerate
+convergence greatly.  Therefore, the possibility of slow or
+non-convergence is generally not a concern in practice.
+
+For the initial guess, we simply use the ground state of our
+noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity
+matrix.  At each iteration, we calculate the sum of the Lagrange
+multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the
+iteration approaches convergence, the change in the sum per iteration
+should decrease rapidly.
+
+Since HF restricts the ground state to merely a single Slater
+determinant of single-particle states, it cannot provide an exact
+solution to a problem where multi-particle correlations are present
+even if the single-particle basis is not truncated (infinite in size).
+The discrepancy between the Hartree--Fock energy and the exact ground
+state energy is often referred to as the \textit{correlation energy},
+by definition.  The focus of post-HF methods such as IM-SRG or coupled
+cluster is to add corrections beyond mean-field approximations such as
+HF.
+
+To make use of the HF solution as the reference state for future
+calculations, we transform the operators via Eqs.~\eqref{eq:hftransform1}
+and \eqref{eq:hftransform2}.  Therefore, the post-HF methods described
+in the next few sections generally use the transformed operators
+$\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.  However,
+we will not annotate them with the prime symbols as the methods are
+generic and can be applied to any reference state, whether optimized
+by HF or not.
 
@@
 
-The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form.
-This allows the decoupling of a small, designated \textit{model space} from its larger complementary space.
-The problem can thus be truncated to the small model space while preserving a large amount of information about the system.
-
-The sequence of transformations is parameterized by a continuous variable $s$ known as the \textit{flow parameter}.
-Without loss of generality, we can define $s = 0$ to be the beginning of this sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.
-At any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to the original Hamiltonian by
-\begin{align*}
-  \hat{H}(s) \equiv \hat{U}(s) \hat{H}(0) \hat{U}^\dagger(s)
+The central theme of similarity renormalization group (SRG) methods is
+the application of a continuous sequence of unitary transformations on
+the Hamiltonian to evolve it into a band- or block-diagonal form, see
+for examples Refs.~\cite{kehreinflow2006,heikophysrep2016,lnp936} for
+derivations and calculational details.
+
+This allows the decoupling of
+a small, designated \textit{model space} from its larger complementary
+space.  The problem can thus be truncated to the small model space
+while preserving a large amount of information about the system.
+
+The sequence of transformations is parameterized by a continuous
+variable $s$ known as the \textit{flow parameter}.  Without loss of
+generality, we can define $s = 0$ to be the beginning of this
+sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.  At
+any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to
+the original Hamiltonian by
+\begin{align*}
+  \hat{H}(s) \equiv \hat{U}(s) \hat{H}(0) \hat{U}^\dagger(s),
 \end{align*}
@@
 \begin{align*}
-  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\D s} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}
+  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\Ds} \hat{H}(0) \hat{U}^\dagger(s)
+  + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
 \end{align*}
@@
 \begin{align} \label{eq:etadefinition}
-  \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s)
+  \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s),
 \end{align}
@@
   = \frac{\D}{\D s} \left(\hat{U}(s) \hat{U}^\dagger(s)\right)
-  = 0
+  = 0,
 \end{align*}
@@
 \begin{align} \label{eq:imsrgode}
-  \frac{\D \hat{H}(s)}{\D s} = [\hat{\eta}(s), \hat{H}(s)]
-\end{align}
-The equation allows $\hat{H}(s)$ to be evaluated without explicitly constructing the full transformation $\hat U(s)$.
-The focus is instead shifted to the operator $\hat \eta(s)$, the \textit{generator} of the transformation.
-When $\hat \eta(s)$ is \emph{multiplicatively} integrated (\textit{product integral}), the full unitary transformation $\hat U(s)$ is recovered:
+  \frac{\D \hat{H}(s)}{\D s} = [\hat{\eta}(s), \hat{H}(s)].
+\end{align}
+This equation allows $\hat{H}(s)$ to be evaluated without explicitly
+constructing the full transformation $\hat U(s)$.  The focus is
+instead shifted to the operator $\hat \eta(s)$, the \textit{generator}
+of the transformation.  When $\hat \eta(s)$ is \emph{multiplicatively}
+integrated (\textit{product integral}), the full unitary
+transformation $\hat U(s)$ is recovered:
 \begin{align} \label{eq:etaintegral}
   \hat U(s')
-  = \lim_{\Delta s \to 0} \prod_{i = 1}^n \mathrm{e}^{\hat{\eta}(s_i) \Delta s}
-\end{align}
-where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
-This is the formal solution to the linear differential equation \ref{eq:etadefinition}.
-The product integral in \ref{eq:etaintegral} may also be reinterpreted as \textit{$s$-ordering} \cite[\S 6.1]{reimann2013quantum} in analogy to time-ordering from quantum field theory.
-
-The power of SRG methods lies in the flexibility of the generator $\hat{\eta}$, which is usually chosen in an $s$-dependent manner.
-In particular, it is often dependent on the evolving Hamiltonian $\hat{H}(s)$.
-The operator $\hat{\eta}$ determines which parts of the Hamiltonian matrix would become suppressed by the evolution, which are usually considered ``off-diagonal'' in an abstract sense.
-The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
-Or, the ``off-diagonal'' parts could be elements that couple the ground state from the excited state, in which case the evolution drives the matrix towards a block-diagonal form that isolates the ground state.
-Or, the ``off-diagonal'' could be literally the elements that do not lie on the diagonal, in which case the evolution would simply diagonalize the Hamiltonian.
-Through different choices of $\hat{\eta}$, the SRG evolution can be controlled and adapted to the features of a particular problem.
+  = \lim_{\Delta s \to 0} \prod_{i = 1}^n \mathrm{e}^{\hat{\eta}(s_i) \Delta s},
+\end{align}
+where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta
+s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
+This is the formal solution to the linear differential
+equation Eq.~(\ref{eq:etadefinition}).  The product integral
+in Eq.~(\ref{eq:etaintegral}) may also be reinterpreted
+as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy
+to time-ordering from quantum field theory.
+
+The power of SRG methods lies in the flexibility of the generator
+$\hat{\eta}$, which is usually chosen in an $s$-dependent manner.  In
+particular, it is often dependent on the evolving Hamiltonian
+$\hat{H}(s)$.  The operator $\hat{\eta}$ determines which parts of the
+Hamiltonian matrix would become suppressed by the evolution, which are
+usually considered ``off-diagonal'' in an abstract sense.  The
+``off-diagonal'' parts could be elements far away from the matrix
+diagonal, in which case the evolution drives the matrix towards a
+band-diagonal form.  Or, the ``off-diagonal'' parts could be elements
+that couple the ground state from the excited state, in which case the
+evolution drives the matrix towards a block-diagonal form that
+isolates the ground state.  Or, the ``off-diagonal'' could be
+literally the elements that do not lie on the diagonal, in which case
+the evolution would simply diagonalize the Hamiltonian.  Through
+different choices of $\hat{\eta}$, the SRG evolution can be controlled
+and adapted to the features of a particular problem.
 
@@
 
-The SRG flow equation \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
-However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
-A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
-This gives rise to the IM-SRG method.
-
-The second-quantized operators in \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
-\begin{align*}
-&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0 &
-&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0
+The SRG flow equation Eq.~\eqref{eq:imsrgode} can be solved in the
+second quantization formalism described in
+Section \ref{subsec:modelHamiltonian}, where field operators are
+defined with respect to the physical vacuum state.  However, since the
+basis of a many-body problem grows factorially with the number of
+particles and the size of the model space, the applicability of the
+naive (free-space) SRG method is restricted to comparatively small
+systems.  A more practical approach is to perform the
+evolution \textit{in medium}, i.e.\ using a many-body Slater
+determinant as a reference \cite{kehrein2006flow}.  This gives rise to
+the IM-SRG method \cite{bogner2012,heikophysrep2016,lnp936}.
+
+The second-quantized operators in
+Eq.~\eqref{eq:second_quantized_hamiltonian} are constructed with
+respect to the vacuum state in the sense that their operator strings
+$\hat{a}_p^\dagger \hat{a}_q$ and
+$\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have
+expectation values of zero in vacuum:
+\begin{align*}
+&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0, &
+&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0.
 \end{align*}
@@
 \end{align*}
-where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label the occupied states.
-One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators:
-\begin{align*}
-  \hat b_p \equiv \bar n_p \hat a_{p} + n_p \hat a_{p}^\dagger
-\end{align*}
-The quasiparticle field operators treat the \textit{reference state} $\ket{\Phi}$ as their ``vacuum'' state (\textit{Fermi vaccuum}), even though it is not the true \emph{physical} vacuum state.
-As before, it is possible to construct arbitrary Slater determinants by applying quasiparticle operators to the reference state:
-\begin{align}
-  \ket{\Phi_{p_1, \ldots, p_k}} \equiv \hat{b}^\dagger_{p_1} \cdots \hat{b}^\dagger_{p_k} \ket{\Phi}
-  \label{eq:quasisd}
-\end{align}
-If $p$ is an unoccupied state, then applying $\hat{b}_p^\dagger$ creates a particle exactly like $\hat{a}_p^\dagger$.
-However, if $p$ is an occupied state, then applying $\hat{b}_p^\dagger$ destroys an existing particle in $\Phi$ or, equivalently, creates a \textit{hole} state.
-The set of labels $\{p_1, \ldots, p_k\}$ may contain up to $N$ hole states and as many particle states as the basis allows for (minus the ones that are already hole states).
-One can classify the state $\Phi_{p_1, \ldots, p_k}$ as an $N_{\text{p}}$-particle-$N_{\text{h}}$-hole state, meaning that it contains $N_{\text{p}}$ labels that denote unoccupied states and $N_{\text{h}}$ labels that denote occupied states.
-If $N_{\text{p}} = N_{\text{h}}$, the Slater determinant contains the same number of physical particles as the reference state.
-The ``$N_{\text{p}}$-particle-$N_{\text{h}}$-hole'' classification gives a crude sense of how distant a state is from the reference state, which can be exploited by many-body theories.
-
-We may then define \emph{normal ordering with respect to the reference state} $\Phi$, a notational device that reorders a string of operators such that every quasiparticle creation operator appears before a quasiparticle annihilation operator, while also accounting for the sign.
-Each exchange of operators must incur a change in sign -- mathematically this is just the \textit{sign} of the permutation that reorders the operators.
-A simple example would be the normal ordering of a pair of field operators such as:
-\begin{align*}
-  \normord{\hat{b}_p^{} \hat{b}_q^\dagger} =
-  -\hat{b}_q^\dagger \hat{b}_p^{}
-\end{align*}
-Here, we denote normal ordering of an operator string with respect to $\Phi$ by a enclosing pair of colons.
-The expectation value of a normal ordered string of operators with respect to $\Phi$ is guaranteed to vanish:
-\begin{align*}
-&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^{} \ket{\Phi} = 0 &
-&\bra{\Phi} \hat{b}_p^\dagger \hat{b}_q^\dagger \hat{b}_s^{} \hat{b}_r^{} \ket{\Phi} = 0
-\end{align*}
-The normal ordering of the quasiparticle field operators is straightforward to compute.
-What is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $|\Phi\rangle$:
+where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label
+the occupied states.  One can define a set of \textit{quasiparticle
+field operators} $\hat b$ and $\hat b^\dagger$ that obey the same
+anticommutation relations as the $\hat a$ operators.  The normal
+ordering of the quasiparticle field operators is straightforward to
+compute.  What is more interesting is the normal ordering of the
+physical field operators $\hat a$ and $\hat a^\dagger$ with respect to
+$|\Phi\rangle$:
 \begin{align*}
   \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &=
-  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p, q}^{}
+  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p, q}^{}.
 \end{align*}
@@
 \begin{align}
-  \hat{H} = H^{[0]} + \sum_{p, q} H^{[1]}_{p, q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p, q, r, s} H^{[2]}_{p, q, r, s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}}
+  \hat{H} = H^{[0]} + \sum_{pq} H^{[1]}_{pq} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{pqrs} H^{[2]}_{pqrs} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}},
   \label{eq:normordhamiltonian}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i, j} n_i n_j \langle i, j | \hat{H}^{[2]} | i , j \rangle \\
-  H^{[1]}_{p, q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle p, i | \hat{H}^{[2]} | q, i \rangle \\
-  H^{[2]}_{p, q, r, s} &\equiv \langle p, q | \hat{H}^{[2]} | r, s \rangle \\
-\end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p, q}$ is the Fock matrix $F_{p, q}$.
-The operator $\hat H$ in \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in \eqref{eq:vacuumhamiltonian}.
-The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
-Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
-Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
-
-Higher-body operators arise from integrating the flow equations (\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
-With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
-Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy (zero-body component) is of interest.
-
-Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
-Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
-Thus, to make the method tractable, the IM-SRG flow equations must be closed by truncating the equations to a finite order.
-
-In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
-This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
-
-Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
-The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
-The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
-In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
-For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
+  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{ij} n_i n_j \langle ij | \hat{H}^{[2]} | ij \rangle, \\
+  H^{[1]}_{pq} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle pi | \hat{H}^{[2]} | qi \rangle, \\
+  H^{[2]}_{pqrs} &\equiv \langle pq | \hat{H}^{[2]} | rs \rangle. \\
+\end{align*}
+If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is
+simply the HF energy $E_\Phi$ and $H^{[1]}_{pq}$ is the Fock matrix
+$F_{pq}$.  The operator $\hat H$ in
+Eq.~\eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$
+in Eq.~\eqref{eq:vacuumhamiltonian}.  The only difference is that the
+meaning of a ``$k$-body operator'' has been redefined with respect to
+the reference state $\Phi$ rather than vacuum state $\ket{}$, causing
+matrix elements to be reshuffled among the $k$-body operators.  Where
+this makes a critical difference is when the operator expressions
+are \emph{truncated}, i.e.\ some $k$-body operators may be discarded
+from the computation for efficiency reasons.  Normal-ordering can
+drastically alter the importance of the $k$-body operators with
+respect to each other.
+
+Higher-body operators arise from integrating the flow equations
+(\ref{eq:imsrgode}), which is one of the major challenges of the SRG
+method.  With each evaluation of the commutator, the Hamiltonian gains
+terms of higher order, and these induced contributions will in
+subsequent integration steps feed back into terms of lower order.
+Thus, the higher-body contributions are not irrelevant to the final
+solution even if only the ground state energy (zero-body component) is
+of interest.
+
+Computationally, higher-body terms rapidly become unfeasible to
+handle: the amount of memory required to store a $k$-body operator is
+grows exponentially with $k$.  Moreover, the flow equations are
+capable of generating an infinite number of higher-body terms as the
+Hamiltonian evolves.  Thus, to make the method tractable, the IM-SRG
+flow equations must be closed by truncating the equations to a finite
+order.
+
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the
+two-body level, leading to an approach known as IM-SRG(2).  This
+normal-ordered two-body approximation appears to be sufficient in many
+cases and has yielded excellent results for several
+nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+Note that the loss of three- and higher-body terms (\textit{operator
+truncation}) is only one out of the two sources of error in this
+method.  The other source of error is due to the \textit{basis
+truncation}, a concern for any method that relies on a finite
+single-particle basis such as IM-SRG.  The latter can be reduced by
+increasing the size of the basis at the expense of greater
+computational effort, albeit the cost increases much less rapidly in
+this direction.  In IM-SRG the CPU cost is polynomial with respect to
+$N_{\mathrm{b}}$, the number of states in the single-particle basis.
+For IM-SRG(2) in particular, the CPU cost scales roughly as
+$\mathcal{O}(N_{\mathrm{b}}^6)$.
 
@@
 \begin{align*}
-\hat{\eta} = \sum_{p, q} \eta_{p, q}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
-\frac{1}{4} \sum_{p, q, r, s}\eta_{p, q, r, s}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r}
-\end{align*}
-where $\eta_{p, q}^{[1]}$ and $ \eta_{p, q, r, s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$, subject to the antihermittivity constraint.
-
-By expanding the commutator in \eqref{eq:imsrgode} and discarding the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
+\hat{\eta} = \sum_{pq} \eta_{pq}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
+\frac{1}{4} \sum_{pqrs}\eta_{pqrs}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r},
+\end{align*}
+where $\eta_{pq}^{[1]}$ and $ \eta_{pqrs}^{[2]}$ respectively are its
+one- and two-body matrix elements normal ordered with respect to
+$\Phi$, subject to the antihermittivity constraint.
+
+By expanding the commutator in Eq.~\eqref{eq:imsrgode} and discarding
+the three-body term, we obtain the matrix-element form of the
+IM-SRG(2) flow equation:
 \begin{align}
@@
 \begin{align}
-  C^{[k]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[k]}(A, B) \text{ for any $k$, $A$, $B$} \label{eq:commutmxe} \\
-  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$}
+  C^{[k]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[k]}(A, B) \text{ for any $k$, $A$, $B$}, \label{eq:commutmxe} \\
+  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$},
 \end{align}
@@
   &\equiv
-    \sum_{i, a} n_i \bar{n}_a A^{[1]}_{i, a} B^{[1]}_{a, i}
-    + \frac{1}{4} \sum_{i, j, a, b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i, j, a, b} B^{[2]}_{a, b, i, j}
+    \sum_{ia} n_i \bar{n}_a A^{[1]}_{ia} B^{[1]}_{ai}
+    + \frac{1}{4} \sum_{ijab} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{ijab} B^{[2]}_{abij},
     \label{eq:flow0} \\
@@
   &\equiv
-    \sum_{r} A^{[1]}_{p, r} B^{[1]}_{r, q}
-    - \frac{1}{2} \sum_{i, j, a} n_i n_j \bar{n}_a A^{[2]}_{i, j, a, q} B^{[2]}_{a, p, i, j}
-    + \frac{1}{2} \sum_{i, a, b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i, p, a, b} B^{[2]}_{a, b, i, q}
+    \sum_{r} A^{[1]}_{pr} B^{[1]}_{rq}
+    - \frac{1}{2} \sum_{ija} n_i n_j \bar{n}_a A^{[2]}_{ijaq} B^{[2]}_{apij}
+    + \frac{1}{2} \sum_{iab} n_i \bar{n}_a \bar{n}_b A^{[2]}_{ipab} B^{[2]}_{abiq}
     \notag \\
   &\hphantom{=}
-    + \sum_{i, a} n_i \bar{n}_a \left(
-    A^{[1]}_{i, a} B^{[2]}_{a, p, i, q}
-    + A^{[2]}_{i, p, a, q} B^{[1]}_{a, i}
+    + \sum_{ia} n_i \bar{n}_a \left(
+    A^{[1]}_{ia} B^{[2]}_{apiq}
+    + A^{[2]}_{ipaq} B^{[1]}_{ai}
     \right)
     \label{eq:flow1} \\
-  D^{[2]}_{p, q, r, s}(A, B)
+  D^{[2]}_{pqrs}(A, B)
   &\equiv
-    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s}
-    \sum_{i, a} n_i \bar{n}_a A^{[2]}_{i, p, a, r} B^{[2]}_{a, q, i, s}
+    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{rs}
+    \sum_{ia} n_i \bar{n}_a A^{[2]}_{ipar} B^{[2]}_{aqis}
     \notag \\
   &\hphantom{=}
-    + \frac{1}{2} \sum_{i, j} n_i n_j A^{[2]}_{i, j, r, s} B^{[2]}_{p, q, i, j}
-    + \frac{1}{2} \sum_{a, b} \bar{n}_a \bar{n}_b A^{[2]}_{p, q, a, b} B^{[2]}_{a, b, r, s}
+    + \frac{1}{2} \sum_{ij} n_i n_j A^{[2]}_{ijrs} B^{[2]}_{pqij}
+    + \frac{1}{2} \sum_{ab} \bar{n}_a \bar{n}_b A^{[2]}_{pqab} B^{[2]}_{abrs}
     \notag \\
@@
     + \sum_{t} \left(
-    \tilde{\mathcal{A}}_{p, q} A^{[1]}_{q, t} B^{[2]}_{p, t, r, s}
-    + \tilde{\mathcal{A}}_{r, s} A^{[2]}_{p, q, r, t} B^{[1]}_{t, s}
+    \tilde{\mathcal{A}}_{pq} A^{[1]}_{qt} B^{[2]}_{ptrs}
+    + \tilde{\mathcal{A}}_{rs} A^{[2]}_{pqrt} B^{[1]}_{ts}.
     \right)
@@
 \includegraphics{fig-diagrams-imsrg.pdf}
-\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
+\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and Eq.~\eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
 The two-body vertices are implicitly antisymmetric (i.e.\ \textit{Hugenholtz diagrams} \cite{HUGENHOLTZ1957481}, as described in \cite{shavitt2009many} \S 4.4.3).
@@
 
-The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
-In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of \eqref{eq:flow0}, \eqref{eq:flow1}, and \eqref{eq:flow2}.
-
-The commutator in the flow equations \eqref{eq:imsrgode} ensures that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked diagrams} only \cite{shavitt2009many}.
-This indicates that IM-SRG is a size-extensive \cite{ISI:A1981MN73700014} method by construction, even if the operators are truncated.
-
-An accurate and robust ODE solver is required to solve \eqref{eq:imsrgode}.
-In particular, the solver must be capable of handling the stiffness that often arises in such problems.
-For our numerical experiments, we used a high-order ODE solver algorithm by L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which is a multistep method based on the implicit Adams predictor-corrector formulas.
-Its source code is freely available \cite{odesolver}.
-
-Through the flow equation and with an appropriate choice of the generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will gradually approach a more ``diagonal'' form.
-If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
-In particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
+The equations can be derived directly from the anticommutation
+relations of the field operators, but it is more convenient to use
+Wick's theorem \cite{PhysRev.80.268} or, even more efficiently,
+diagrammatic techniques \cite{shavitt2009many} to arrive at the
+results.  In particular, Figure \ref{fig:diagrams-imsrg} shows the
+diagrammatic form of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and
+Eq.~\eqref{eq:flow2}.
+
+The commutator in the flow equations Eq.~\eqref{eq:imsrgode} ensures
+that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked
+diagrams} only \cite{shavitt2009many}.  This indicates that IM-SRG is
+a size-extensive \cite{ISI:A1981MN73700014} method by construction,
+even if the operators are truncated.
+
+An accurate and robust ODE solver is required to solve
+Eq.~\eqref{eq:imsrgode}.  In particular, the solver must be capable of
+handling the stiffness that often arises in such problems.  For our
+numerical experiments, we used a high-order ODE solver algorithm by
+L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which
+is a multistep method based on the implicit Adams predictor-corrector
+formulas.  Its source code is freely available \cite{odesolver}.
+
+Through the flow equation and with an appropriate choice of the
+generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will
+gradually approach a more ``diagonal'' form.  If the ``diagonal'' form
+decouples the ground state from the excited states, then $\hat
+U(\infty) \ket{\Phi}$ would yield the exact ground state solution of
+the problem if no operator or basis truncations are made.  In
+particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
 
@@
   = [\hat{H}^{\text{d}}, \hat{H} - \hat{H}^{\text{d}}]
-  = [\hat{H}^{\text{d}}, \hat{H}]
-\end{align*}
-where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the Hamiltonian and $\hat{H} - \hat{H}^{\text{d}}$ denotes the ``off-diagonal'' part.
-This is in the abstract sense described at the end of Section \ref{subsubsec:srgmethods}.
-
-Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian operators, it is antihermitian as required for a generator.
-Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
-Matrix elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian couples states with large energy differences -- are suppressed much faster than those ``close'' to the diagonal.
-
-Apart from Wegner's generator, there exist several other ones in literature.
-One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
-The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
-Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
-This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
-
-The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
-Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
-This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
-Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
-This ensures that the affected elements decay at approximately the same rate, reducing the stiffness of the flow equations.
+  = [\hat{H}^{\text{d}}, \hat{H}],
+\end{align*}
+where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the
+Hamiltonian and $\hat{H} - \hat{H}^{\text{d}}$ denotes the
+``off-diagonal'' part.  This is in the abstract sense described at the
+end of Section \ref{subsubsec:srgmethods}.
+
+Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian
+operators, it is antihermitian as required for a generator.
+Additionally, it can be shown that the commutator has the property of
+suppressing off-diagonal matrix elements as the state evolves via the
+flow equation \cite{kehrein2006flow}, as we would like.  Matrix
+elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian
+couples states with large energy differences -- are suppressed much
+faster than those ``close'' to the diagonal.
+
+Apart from Wegner's generator, there exist several other ones in
+literature. One choice, proposed by
+White \cite{White:cond-mat0201346}, makes numerical approaches much
+more efficient.  The problem with the Wegner generator is the widely
+varying decaying speeds of the Hamiltonian matrix elements.  Terms
+with large energy separations from the ground state are suppressed
+initially, followed by those with smaller energy separations.  This
+leads to stiffness in the flow equation, leading to numerical
+difficulties in solving the set of coupled differential equations.
+
+The White generator takes an alternative approach, which is well
+suited for problems where one is mainly interested in the ground state
+of a system.  Firstly, instead of driving all off-diagonal elements of
+the Hamiltonian to zero, the generator focuses exclusively on those
+ones that are coupled to the reference state $\Phi$ so as to decouple
+the reference state from the remaining Hamiltonian.  This reduces the
+amount of change done to the Hamiltonian, reducing the accuracy lost
+from the operator truncation.  Secondly, the rate of decay in
+Hamiltonian matrix elements are approximately normalized by dividing
+the generator matrix elements by an appropriate factor.  This ensures
+that the affected elements decay at approximately the same rate,
+reducing the stiffness of the flow equations.
 
@@
 \begin{align*}
-\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
+\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger,
 \end{align*}
@@
 \begin{align*}
-\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\tilde{\Delta}^{[1]}_{a, i}} &
-\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\tilde{\Delta}^{[2]}_{a, b, i, j}}
-\end{align*}
-and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as
+\eta^{\prime [1]}_{ai} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{ai}}{\tilde{\Delta}^{[1]}_{ai}} &
+\eta^{\prime [2]}_{abij} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{abij}}{\tilde{\Delta}^{[2]}_{abij}}
+\end{align*}
+and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as {\bf ref to epstein-nesbet deno, insert later}
 \begin{align}
-\tilde{\Delta}^{[1]}_{a, i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a, i, a, i} \notag \\
-\tilde{\Delta}^{[2]}_{a, b, i, j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a, b, i, j} \notag \\
-\Delta^{[2]}_{P_1, P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1, p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2, p_2} \label{eq:moellerplessetdenominator} \\
-w_{a, b, i, j}
-  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
-  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j} \notag
-\end{align}
-Some literature use the M\o ller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.
-
-Compared to the Wegner generator, where the derivatives of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.
-This reduces the stiffness in the differential equation, providing a net increase in computational efficiency as stiff ODE solvers tend to be slower and consume more memory.
+\tilde{\Delta}^{[1]}_{ai} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{aiai}, \notag \\
+\tilde{\Delta}^{[2]}_{abij} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{abij}, \notag \\
+\Delta^{[2]}_{P_1P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2p_2}, \label{eq:moellerplessetdenominator} \\
+w_{abij}
+  &\equiv H^{[2]}_{abab} - H^{[2]}_{aiai} - H^{[2]}_{bibi} \notag \\
+  &\qquad + H^{[2]}_{ijij} - H^{[2]}_{ajaj} - H^{[2]}_{bjbj}. \notag
+\end{align}
+Some authors {\bf ref}  use the M\o ller--Plesset denominators $\Delta$
+instead, leading to a slightly different variant of the White
+generator.
+{\bf define Moller plesset denos and give reference}.
+
+Compared to the Wegner generator, where the derivatives of the final
+flow equations contain cubes of the Hamiltonian matrix elements (i.e.\
+each term contains a product of 3 one-body and/or two-body matrix
+elements), the elements in White generators contribute only linearly.
+This reduces the stiffness in the differential equation, providing a
+net increase in computational efficiency as stiff ODE solvers tend to
+be slower and consume more memory.
 
@@
 \begin{align*}
-  \ket{\Psi} = e^{\hat{T}}\ket{\Phi}
+  \ket{\Psi} = e^{\hat{T}}\ket{\Phi},
 \end{align*}
@@
 \begin{align} \label{eq:cc_amps}
-  \hat{T}_{k} \equiv \left(\frac{1}{k!}\right)^{2}\sum\limits_{\substack{a_{1}, \dots, a_{k}, \\ i_{1}, \dots, i_{k}}} \bar{n}_{a_{1}} \cdots \bar{n}_{a_{k}} n_{i_{1}} \cdots n_{i_{k}} t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}} \normord{\hat a_{a_{1}}^\dagger \cdots \hat a_{a_{k}}^\dagger \hat a_{i_{k}} \cdots \hat a_{i_{1}}}
-\end{align}
-where the unknown matrix elements, $t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}}$, known as \textit{cluster amplitudes}.
+  \hat{T}_{k} \equiv \left(\frac{1}{k!}\right)^{2}\sum\limits_{\substack{a_{1}, \dots, a_{k}, \\ i_{1}, \dots, i_{k}}} \bar{n}_{a_{1}} \cdots \bar{n}_{a_{k}} n_{i_{1}} \cdots n_{i_{k}} t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}} \normord{\hat a_{a_{1}}^\dagger \cdots \hat a_{a_{k}}^\dagger \hat a_{i_{k}} \cdots \hat a_{i_{1}}},
+\end{align}
+where the unknown matrix elements, $t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}}$, are known as \textit{cluster amplitudes} \cite{shavitt2009many}.
 
@@
 \begin{align} \label{eq:cc_schrodeq}
-  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}}\ket{\Phi}
+  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}}\ket{\Phi},
 \end{align}
@@
 \begin{align*}
-  \bra{\Phi} \bar{H}_{\mathrm{CC}} \ket{\Phi} = E
+  \bra{\Phi} \bar{H}_{\mathrm{CC}} \ket{\Phi} = E,
 \end{align*}
@@
 \begin{align} \label{eq:cc_heff0}
-  \bar{H}_{\mathrm{CC}} \equiv \E^{-\hat{T}} \hat{H} \E^{\hat{T}}
+  \bar{H}_{\mathrm{CC}} \equiv \E^{-\hat{T}} \hat{H} \E^{\hat{T}},
 \end{align}
@@
 
-The effective Hamiltonian in \eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker--Campbell--Hausdorff expansion as,
-\begin{align*}
-  \bar{H}_{\mathrm{CC}} = \hat{H} + [\hat{H}, \hat{T}] + \frac{1}{2} [[\hat{H}, \hat{T} ], \hat{T}] + \frac{1}{3!} [[[\hat{H}, \hat{T}], \hat{T}], \hat{T}] + \frac{1}{4!} [[[[\hat{H}, \hat{T}], \hat{T}], \hat{T}], \hat{T}]
+The effective Hamiltonian in Eq.~\eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker--Campbell--Hausdorff expansion as,
+\begin{align*}
+  \bar{H}_{\mathrm{CC}} = \hat{H} + [\hat{H}, \hat{T}] + \frac{1}{2} [[\hat{H}, \hat{T} ], \hat{T}] + \frac{1}{3!} [[[\hat{H}, \hat{T}], \hat{T}], \hat{T}] + \frac{1}{4!} [[[[\hat{H}, \hat{T}], \hat{T}], \hat{T}], \hat{T}],
 \end{align*}
@@
 \begin{align} \label{eq:cc_heff1}
-  \bar{H}_{\mathrm{CC}} = \bigl(\hat{H}e^{\hat{T}}\bigr)_{\mathrm{c}}
+  \bar{H}_{\mathrm{CC}} = \bigl(\hat{H}e^{\hat{T}}\bigr)_{\mathrm{c}},
 \end{align}
@@
 \begin{align*}
-  \hat{T} = \hat{T}_{1} + \hat{T}_{2}
-\end{align*}
-This is known as coupled cluster singles and doubles (CCSD), with a asymptotic computational cost that scales like IM-SRG(2).
-This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
-In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
-Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of \eqref{eq:cc_heff1} in CCSD.
+  \hat{T} = \hat{T}_{1} + \hat{T}_{2}.
+\end{align*}
+This is known as coupled cluster singles and doubles (CCSD), with an
+asymptotic computational cost that scales like IM-SRG(2).  This
+truncation has been successfully applied to many problems in quantum
+chemistry \cite{RevModPhys.79.291} and nuclear
+physics \cite{0034-4885-77-9-096302}.  In addition, we also truncate
+the three-body effective Hamiltonian terms that are induced by the
+similarity transformation.  Figure \ref{fig:diagrams-ccsd} shows the
+diagrammatic representation of Eq.~\eqref{eq:cc_heff1} in CCSD.
 
 \begin{figure}
-  \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{Diagrammatic representation of $\bar{H}$ of \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
-As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
-Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}^{[2]}$ are unconstrained.}
-  \label{fig:diagrams-ccsd}
+  \includegraphics{fig-diagrams-ccsd.pdf} \caption{Diagrammatic
+  representation of $\bar{H}$ of Eq.~\eqref{eq:cc_heff1}, where open
+  circles represent the excitation cluster operators $\hat{T}_{1}$ and
+  $\hat{T}_{2}$, and filled circles represent the two-body interaction
+  $\hat{H}^{[2]}$.  As before, the diagrams are implicitly
+  antisymmetrized (Hugenholtz diagrams).  Lines connected to $\hat{T}$
+  are always directed upward because they represent an excitation
+  operator while the directions of external lines connected to
+  $\hat{H}^{[2]}$ are unconstrained.}  \label{fig:diagrams-ccsd}
 \end{figure}
 
-The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively.
+The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b,
+i, j}^{[2]}$, are calculated by left-multiplying
+Eq.~\eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat
+a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat
+a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat
+a_{a}} \E^{-\hat{T}}$, respectively,
 \begin{align} \label{eq:ccsd1}
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0 \\
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0 \notag
-\end{align}
-After the Fock matrix has been diagonalized, the diagonal components of \eqref{eq:ccsd1} can be separated and, after expanding the exponent in \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0, \\
+  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0. \notag
+\end{align}
+After the Fock matrix has been diagonalized, the diagonal components
+of Eq.~\eqref{eq:ccsd1} can be separated and, after expanding the
+exponent in Eq.~\eqref{eq:cc_heff1}, the non-vanishing terms of the
+CCSD amplitude equations become,
 \begin{gather} \label{eq:ccsd2}
@@
   \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \hat{H}^{[2]} (1 + \hat{T}_{1} + \hat{T}_{2} + \frac{1}{2} \hat{T}_{1}^{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{2}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} + \frac{1}{2}\hat{T}_{1}^{2}\hat{T}_{2} + \frac{1}{4!}\hat{T}_{1}^{4} )_{c} \ket{\Phi} \notag \\
-= \Delta_{\{i, j\}, \{a, b\}} t_{a, b, i, j}^{[2]} \notag
+= \Delta_{\{ij\}, \{ab\}} t_{abij}^{[2]} \notag
 \end{gather}
-where $\Delta$ are the M\o ller--Plesset denominators from \eqref{eq:moellerplessetdenominator}.
-As usual, these non-linear equations are solved using an iterative procedure.
-One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of \eqref{eq:ccsd2}.
-Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side.
-This process is repeated until the amplitudes reach a fixed point.
-Like the Hartree--Fock iterative procedure, employing convergence acceleration techniques can reduce the number of coupled cluster iterations required.
+where $\Delta$ are the M\o ller--Plesset denominators from
+Eq.~\eqref{eq:moellerplessetdenominator}.  As usual, these non-linear
+equations are solved using an iterative procedure.  One begins with an
+initial guess for the cluster amplitudes, which are used to calculate
+the left-hand side of Eq.~\eqref{eq:ccsd2}.  Dividing by the
+denominator on the right-hand side gives updated amplitudes which are
+used to re-evaluate the left-hand side. This process is repeated until
+the amplitudes reach a fixed point.  Like the Hartree--Fock iterative
+procedure, employing convergence acceleration techniques can reduce
+the number of coupled cluster iterations required.
 
@@
 
-IM-SRG, in the approach described, provides a means to calculate the ground state energy of any system that is reasonably approximated by a single Slater determinant.
-This works well for closed-shell systems, but it does not provide a direct means to obtain the ground state energy of open-shell systems.
-While there exist more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use a perturbative approach, which is simple, inexpensive, and as we shall see in the results, quite effective for many problems.
-
-Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.
-It provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.
-In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
+The in-medium SRG, in the approach described, provides a means to
+calculate the ground state energy of any system that is reasonably
+approximated by a single Slater determinant.  This works well for
+closed-shell systems, but it does not provide a direct means to obtain
+the ground state energy of open-shell systems.  While there exist more
+complicated multi-reference approaches to IM-SRG that can tackle the
+general problem \cite{Hergert2016165}, we opted to use a perturbative
+approach, which is simple, inexpensive, and as we shall see in the
+results, quite effective for many problems.
+
+Quasidegenerate perturbation theory (QDPT) is an extension to the
+traditional perturbation theory framework that incorporates multiple
+reference states.  It provides us with a simple means to extract
+ground state energies of open-shell systems that are only a few
+particles away from a closed-shell system.  In particular, it allows
+us to calculate \textit{addition energies} $\varepsilon_a$
+and \textit{removal energies} $\varepsilon_i$ of such systems, which
+we define as:
 \begin{align}
-  \varepsilon_a &\equiv E_{\Phi_a} - E_{\Phi} \\
-  \varepsilon_i &\equiv E_{\Phi} - E_{\Phi_i}
-\end{align}
-where the meaning of $\Phi_p$ is defined in \eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
-
-In QDPT, solutions of an approximate one-body Hamiltonian $\hat{H}^{[1]}$ form the basis of the model space.
-One begins by assuming the existence of an operator $\hat{\Omega}$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
+  \varepsilon_a &\equiv E_{\Phi_a} - E_{\Phi}, \\
+  \varepsilon_i &\equiv E_{\Phi} - E_{\Phi_i},
+\end{align}
+where the meaning of $\Phi_p$ is defined in Eq.~\eqref{eq:quasisd},
+$i$ is restricted to labels of occupied states, and $a$ is restricted
+to labels of unoccupied states.
+
+In QDPT, solutions of an approximate one-body Hamiltonian
+$\hat{H}^{[1]}$ form the basis of the model space.  One begins by
+assuming the existence of an operator $\hat{\Omega}$, known as
+the \textit{wave operator}, that maps some set of states
+$\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact
+ground state $\Psi_u$:
 \begin{align} \label{eq:omega-condition1}
-  \Psi_u = \hat \Omega \tilde \Psi^{\mathrm{o}}_u
-\end{align}
-The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
+  \Psi_u = \hat \Omega \tilde \Psi^{\mathrm{o}}_u.
+\end{align}
+The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the
+eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian
+$\hat{H}^{[1]}$.
 
@@
 \begin{align} \label{eq:omega-condition2}
-  \hat \Omega = \hat P + \hat Q \hat \Omega \hat P
-\end{align}
-where $\hat P$ projects any state into the model space and $\hat Q$ is the complement of $\hat P$.
-This entails that the exact states $\Psi_u$ is no longer normalized but instead satisfies the so-called intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
-
-Making use of the assumptions in  \eqref{eq:omega-condition1} and \eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
+  \hat \Omega = \hat P + \hat Q \hat \Omega \hat P,
+\end{align}
+where $\hat P$ projects any state into the model space and $\hat Q$ is
+the complement of $\hat P$.  This entails that the exact states
+$\Psi_u$ is no longer normalized but instead satisfies the so-called
+intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
+
+Making use of the assumptions in Eq.~\eqref{eq:omega-condition1} and
+Eq.~\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger
+equation the generalized Bloch equation, the principal equation of
+QDPT:
 \begin{gather*}
   [\hat \Omega, \hat{H}^{[1]}] =
-  (1 - \hat \Omega) \hat V \Omega
+  (1 - \hat \Omega) \hat V \Omega,
 \end{gather*}
@@
   \hat Q \Omega \hat P_u =
-  \hat R_u (1 - \hat \Omega) \hat V \Omega \hat P_u
-\end{align*}
-where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
-As is standard in perturbation theory, we now assume $\hat \Omega$ can be expanded as a series of terms of increasing order, as quantified by the power of the perturbation $\hat V$:
+  \hat R_u (1 - \hat \Omega) \hat V \Omega \hat P_u,
+\end{align*}
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat
+Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection
+operator that projects any state onto $\Psi^{\mathrm{o}}_u$.  As is
+standard in perturbation theory, we now assume $\hat \Omega$ can be
+expanded as a series of terms of increasing order, as quantified by
+the power of the perturbation $\hat V$:
 \begin{align*}
   \hat \Omega = \hat P +
-  \hat Q\bigl(\hat \Omega^{(1)} + \hat \Omega^{(2)} + \cdots\bigr) \hat P
-\end{align*}
-This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$ to be calculated up to any order, as least in principle.  Up to third order, we have:
-\begin{align*}
-  &\hat \Omega^{(1)} \hat P_u = \hat R_u \hat V \hat P_u \\
+  \hat Q\bigl(\hat \Omega^{(1)} + \hat \Omega^{(2)} + \cdots\bigr) \hat P.
+\end{align*}
+This leads to a recursion relation of $\hat \Omega$ that enables
+$\hat \Omega$ to be calculated up to any order, at least in principle.
+Up to third order, we have:
+\begin{align*}
+  &\hat \Omega^{(1)} \hat P_u = \hat R_u \hat V \hat P_u, \\
   &\hat \Omega^{(2)} \hat P_u =
@@
     - \sum_v \hat R_v \hat V \hat P_v
-    \biggr) \hat V \hat P_u \\
+    \biggr) \hat V \hat P_u, \\
   &\hat \Omega^{(3)} \hat P_u =
@@
     + \sum_v \hat R_v \sum_w \hat R_w \hat V \hat P_w \hat V \hat P_v
-    \biggr) \hat V \hat P_u
+    \biggr) \hat V \hat P_u.
 \end{align*}
@@
 
-To make the equations more concrete, we further assume that each reference state $\ket{\Psi^{\mathrm{o}}_u} \equiv \ket{\Phi_u}$, i.e.\ each reference state is simply a Slater determinant constructed by adding or removing a single particle $u$ to a closed-shell reference state $\Phi$, which itself may have been obtained earlier from HF and/or IM-SRG.
-Thus, the number of reference states for QDPT is equal to the number of particles in either the lowest unfilled shell or the highest filled shell of $\ket{\Phi}$, depending on whether we are considering addition or removal energies.
-
-We can then express the perturbation expansion in terms of summations over matrix elements as we had done before for the IM-SRG flow equation, again with the aid of Wick's theorem or diagrammatic techniques.
-This leads to the following expression for the second-order correction:
+To make the equations more concrete, we further assume that each
+reference state $\ket{\Psi^{\mathrm{o}}_u} \equiv \ket{\Phi_u}$, i.e.\
+each reference state is simply a Slater determinant constructed by
+adding or removing a single particle $u$ to a closed-shell reference
+state $\Phi$, which itself may have been obtained earlier from HF
+and/or IM-SRG.  Thus, the number of reference states for QDPT is equal
+to the number of particles in either the lowest unfilled shell or the
+highest filled shell of $\ket{\Phi}$, depending on whether we are
+considering addition or removal energies.
+
+We can then express the perturbation expansion in terms of summations
+over matrix elements as we did for the IM-SRG flow
+equation, again with the aid of Wick's theorem or diagrammatic
+techniques.  This leads to the following expression for the
+second-order correction:
 \begin{align*}
@@
   &=
-    \sum_{i, a, b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p, i, a, b}|^2}{2 \Delta_{\{p, i\}, \{a, b\}}}
-    - \sum_{i, j, a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i, j, p, a}|^2}{2 \Delta_{\{i, j\}, \{p, a\}}}
-\end{align*}
-where the M\o ller--Plesset denominators $\Delta$ are defined in \eqref{eq:moellerplessetdenominator}.
-The above expression is depicted in Figure \ref{fig:diagrams-sfe}.
-Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.
-We will refer to QDPT to third order as ``QDPT3''.
-
-Taking into account the perturbation corrections, one can extract reasonably accurate addition and removal energies for single-particle states near the Fermi level via:
-\begin{align*}
-  \varepsilon_p = H^{[1]}_{p, p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}
-\end{align*}
-
-There is some degree of synergy between IM-SRG and QDPT: a generator that decouples the ground state energy will necessarily drive certain classes of matrix elements to zero.
-This means certain kinds of vertices in the diagrams become forbidden, reducing the number of nonzero diagrams at third order from 18 to only 4.
+    \sum_{iab} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{piab}|^2}{2 \Delta_{\{pi\}, \{ab\}}}
+    - \sum_{ija} \frac{n_i n_j \bar{n}_a |H^{[2]}_{ijpa}|^2}{2 \Delta_{\{ij\}, \{pa\}}},
+\end{align*}
+where the M\o ller--Plesset denominators $\Delta$ are defined in
+Eq.~\eqref{eq:moellerplessetdenominator}.  The above expression is
+depicted in Figure \ref{fig:diagrams-sfe}.  Since there are numerous
+terms in the third-order correction $\varepsilon_p^{(3)}$, they are
+listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.  We will
+refer to QDPT to third order as ``QDPT3''.
+
+Taking into account the perturbation corrections, one can extract
+reasonably accurate addition and removal energies for single-particle
+states near the Fermi level via:
+\begin{align*}
+  \varepsilon_p = H^{[1]}_{p, p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}.
+\end{align*}
+
+There is some degree of synergy between IM-SRG and QDPT: a generator
+that decouples the ground state energy will necessarily drive certain
+classes of matrix elements to zero.  This means certain kinds of
+vertices in the diagrams become forbidden, reducing the number of
+nonzero diagrams at third order from 18 to only four.
 
@@
 
-Particle attached and particle removed equations of motion (EOM) methods can be coupled with either IM-SRG or coupled cluster calculations.
-The principal idea is that one may construct a ladder operator $\hat{X}$ that promotes the $N$-particle ground state to any state in the $N + 1$ or $N - 1$ spectrum,
+Particle attached and particle removed equations of motion (EOM)
+methods can be coupled with either IM-SRG or coupled cluster
+calculations. The principal idea is that one may construct a ladder
+operator $\hat{X}$ that promotes the $N$-particle ground state to any
+state in the $N + 1$ or $N - 1$ spectrum,
 \begin{equation}\label{eq:ladder_def}
@@
 \end{equation}
-where $\hat{X}$ is in principle a linear combination of excitation and de-excitation operators that change particle number by one,
+where $\hat{X}$ is in principle a linear combination of excitation and
+de-excitation operators that change particle number by one,
 \begin{align}
   \label{eq:gen_attached}
-  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum^{[2,1]}_{p, q, r} \bar{n}_p \bar{n}_q n_r x_{p, q, r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
+  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{pqr} \bar{n}_p \bar{n}_q n_r x^{[2,1]}_{pqr} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  x^{[1,2]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
-\end{align}
-Substitution of \eqref{eq:ladder_def} into the energy eigenvalue problem
+  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{pqr} n_p n_q \bar{n}_r  x^{[1,2]}_{pqr} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
+\end{align}
+Substitution of Eq.~\eqref{eq:ladder_def} into the energy eigenvalue problem
 \begin{gather*}
-  \hat H \ket{\Psi_u^{(N \pm 1)}} = E^{(N\pm1)}_u \ket{\Psi_u^{(N \pm 1)}}
+  \hat H \ket{\Psi_u^{(N \pm 1)}} = E^{(N\pm1)}_u \ket{\Psi_u^{(N \pm 1)}},
 \end{gather*}
@@
 \end{equation}
-which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\varepsilon^{(\pm)}_u$ are the single-particle addition ($+$) and removal ($-$) energies.
-The quality of this calculation depends on the ansatz for the $N$-particle ground state, as well as the systematically improvable truncation on the ladder operators.
-In this work we include 1p and 2p1h excitations in the $N + 1$ ladder operator and likewise 1h and 2h1p operators for the $N - 1$ ladder operators.
-
-\subsubsection*{EOM-IM-SRG}
-
-After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the correlated $N$-particle ground state energy.
-The EOM equation is therefore
+which constitutes a generalized eigenvalue problem for the amplitudes
+$x$, where $\varepsilon^{(\pm)}_u$ are the single-particle addition
+($+$) and removal ($-$) energies. The quality of this calculation
+depends on the ansatz for the $N$-particle ground state, as well as
+the systematically improvable truncation on the ladder operators. In
+this work we include 1p and 2p1h excitations in the $N + 1$ ladder
+operator and likewise 1h and 2h1p operators for the $N - 1$ ladder
+operators.
+
+\subsubsection*{Equation of motion IM-SRG}
+
+After a single-reference ground state IM-SRG calculation, the
+Hamiltonian has been rotated such that the reference state is an
+eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the
+correlated $N$-particle ground state energy. The EOM equation is
+therefore
 \begin{align} \label{eq:EOMIMSRG}
@@
 \end{align}
-where bars denote rotated operators.
-Now the reference state is used in place of the bare correlated ground state.
-The ground state IM-SRG procedure has implicitly re-summed contributions from higher order excitations (3-particle-2-hole, 2-particle-3-hole, 2-particle-3-hole, 4-particle-3-hole, \ldots) into the lower order amplitudes of the ladder operators (1-particle-0-hole, 0-particle-1-hole, 2-particle-1-hole, 1-particle-2-hole).
-
-Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2-particle-1-hole and 1-particle-2-hole operators.
-We expect $N + 1$ (or $N - 1$) states to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in the rotated frame.
-We use partial norms of the EOM ladder operators to make this determination:
+where bars denote rotated operators. Now the reference state is used
+in place of the bare correlated ground state. The ground state IM-SRG
+procedure has implicitly re-summed contributions from higher order
+excitations (3-particle-2-hole, 2-particle-3-hole, 2-particle-3-hole,
+4-particle-3-hole, \ldots) into the lower order amplitudes of the
+ladder operators (1-particle-0-hole, 0-particle-1-hole,
+2-particle-1-hole, 1-particle-2-hole).
+
+Despite these gains, the EOM calculation is still a partial
+diagonalization method, limited by the truncation to 2-particle-1-hole
+and 1-particle-2-hole operators. We expect $N + 1$ (or $N - 1$) states
+to be described appropriately by EOM-IM-SRG if their wavefunctions are
+dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in
+the rotated frame. We use partial norms of the EOM ladder operators to
+make this determination:
 \begin{align}
@@
 \end{align}
-Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
-States with lower single particle norms should be treated by with a higher EOM approximation, which can be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
-
-\subsubsection*{EOM-CC}
-
-Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
-Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
-In this case, in addition to constructing excitation ladder operators \eqref{eq:gen_attached} and \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
-\begin{align*}
-    \hat{L}^{(N+1)}_w &= \sum_p \bar{n}_p l^{[1,0]}_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r l^{[2,1]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p + \cdots \\
+Large single particle partial norms indicate that the EOM truncation
+is valid for the relevant state. States with lower single particle
+norms should be treated with a higher EOM approximation, which can
+be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
+
+\subsubsection*{Equation of motion coupled-cluster theory}
+
+Like EOM-IM-SRG, the equation-of-motion technique can be applied after
+a coupled-cluster ground-state calculation, by using the
+coupled-cluster effective Hamiltonian.  Here, the non-Hermitian nature
+of $\bar{H}_{\mathrm{CC}}$ becomes apparent.  In this case, in
+addition to constructing excitation ladder operators
+Eq.~\eqref{eq:gen_attached} and Eq.~\eqref{eq:gen_removed} that
+correspond to the right-eigenvectors of the generalized eigenvalue
+problem Eq.~\eqref{eq:EOMIMSRG}, there exist analogous de-excitation
+ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that
+correspond to the left-eigenvectors,
+\begin{align*}
+    \hat{L}^{(N+1)}_w &= \sum_p \bar{n}_p l^{[1,0]}_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r l^{[2,1]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p + \cdots, \\
     \hat{L}^{(N-1)}_w &= \sum_p n_p l_p^{[0,1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  l^{[1,2]}_{p, q, r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r + \cdots
 \end{align*}
-These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to \eqref{eq:EOMIMSRG},
+These left-eigenvectors satisfy the left-eigenvalue problem, with
+left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to
+Eq.~\eqref{eq:EOMIMSRG},
 \begin{align*}
@@
 
-In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
-In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle \eqref{eq:partial_norms_p} or single-hole \eqref{eq:partial_norms_h} natures are, in practice, not significant.
-Therefore, only the right-eigenvectors are used in this paper.
+In this paper, because the interaction is real and thus the effective
+Hamiltonian is real, the left- and right-eigenvalues are
+equivalent. In addition, while the the left- and right-eigenvectors
+are generally not equal, the differences in their single-particle
+Eq.~\eqref{eq:partial_norms_p} or single-hole
+Eq.~\eqref{eq:partial_norms_h} natures are, in practice, not
+significant.  Therefore, only the right-eigenvectors are used in this
+paper.
 
@@
   \includegraphics{figures/fig-methods.pdf} 
-  \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
-  \label{fig:methods}
+  \caption{A schematic view of the various ways in which many-body methods in
+  this paper could be combined to calculate ground state, addition,
+  and removal energies.}  \label{fig:methods}
 \end{figure}
 
-There is great amount of flexibility in the application of many-body methods.
-The approaches we use is depicted in Figure \ref{fig:methods}.
-Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
-
-The general process begins with the input matrix elements \eqref{eq:interactionintegral}, computed exactly using the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
-Internally, \texttt{OpenFCI} calculates the interaction integrals in the center-of-mass frame using Gauss--Hermite quadrature and transforms them back into the laboratory frame to produce matrix elements suitable for use in our many-body methods.
-
-Afterward, there are several paths through which one can traverse Figure \ref{fig:methods} to obtain output observables.
-We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
-
-It is possible to omit some steps of the process.
-For example, one can omit HF, but continue with the remaining two steps.
-While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
-Therefore, in practice there is little reason to omit HF.
-We will however investigate the effects of removing one or more of the post-HF methods.
-
-Since every calculation in this paper is begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
-
-All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
-This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
-Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
-\begin{align*}
-  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N \\
-  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}
-\end{align*}
-
-Ideally, ground state energy should be characterized entirely by the two system parameters $(N, \omega)$, where $N$ is number of particles and $\omega$ is the oscillator frequency.
-However, the methods that we study are limited to a \emph{finite} (truncated) basis and therefore their results are dependent on the level of truncation.
-This is characterized by $K$, the total number of shells in the single-particle basis.
-Thus, results are generally presented as a graph plotted against $K$.
-In Section \ref{subsec:extrapolation} discuss how to estimate results as $K \to \infty$ (infinite-basis limit) through \textit{extrapolations}.
-
-The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
-This is due to the presence of multiple states with near-degenerate energies.
-For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
-This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
-
-Not all cases are solvable with our selection many-body methods.
-Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-Cases where IM-SRG converged too slowly to be feasible or diverged are marked ``n.c.(I)''.
-For the extrapolations in Section \ref{subsec:extrapolation}, some fits could not be done due to missing data caused by IM-SRG(2) or CCSD nonconvergence (``n.c.''); others converged but resulted in unphysical $\beta \le 0$ (``n.f.'').
-Cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
-
-Numerical calculations in this paper are performed with a relative precision of about $10^{-5}$ or lower.
-This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate over the multiple steps of the calculation, thus the precision of the final results is expected to be roughly $10^{-4}$.
+There is great amount of flexibility in the application of many-body
+methods.  The approaches we use is shown in
+Fig.~\ref{fig:methods}.  Such an ordering maximizes the benefits of
+each method: Hartree--Fock acts as an initial, crude procedure to
+``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the
+ground state energy, and then finally QDPT or EOM to refine the
+addition and removal energies.
+
+The general process begins with the input matrix elements
+Eq.~\eqref{eq:interactionintegral}, computed exactly using
+the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
+Internally, \texttt{OpenFCI} calculates the interaction integrals in
+the center-of-mass frame using Gauss--Hermite quadrature and
+transforms them back into the laboratory frame to produce matrix
+elements suitable for use in our many-body methods.
+
+Afterward, there are several paths through which one can traverse
+Figure \ref{fig:methods} to obtain output observables.  We shall
+primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3,
+(b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
+
+It is possible to omit some steps of the process.  For example, one
+can omit HF, but continue with the remaining two steps.  While this is
+doable, from our experience Hartree--Fock significantly improves the
+results of the later post-HF methods at very low cost compared to the
+post-HF methods.  Therefore, in practice there is little reason to
+omit HF.  We will however investigate the effects of removing one or
+more of the post-HF methods.
+
+Since every calculation in this paper begins with the Hartree--Fock
+stage, we will not explicitly state ``HF'' unless there is no post-HF
+method used at all, in which case we write ``HF only''.
+
+All calculations of ground state energy $E_N$ in this paper are
+restricted to cases where the number of particles $N$ is a magic
+number, i.e.\ a \textit{closed shell} system (see
+Figure \ref{fig:shell-structure} for an illustration of the shell
+structure).  This is a limitation of the many-body methods used in
+this paper and while there are ways to overcome this limit they are
+beyond the scope of this paper (see Section \ref{sec:conclusions} for
+some ideas).  Addition/removal energies $\varepsilon^{(\pm)}$ are
+similarly restricted in that we only calculate the energy difference
+between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same
+system but with one particle added/removed:
+\begin{align*}
+  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N, \\
+  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}.
+\end{align*}
+
+Ideally, ground state energies should be characterized entirely by the
+two system parameters $(N, \omega)$, where $N$ is number of particles
+and $\omega$ is the oscillator frequency.  However, the methods that
+we study are limited to a \emph{finite} (truncated) basis and
+the results depend on the level of truncation.
+This is characterized by $K$, the total number of shells in the
+single-particle basis.  Thus, results are generally presented as a
+graph plotted against $K$.  In Section \ref{subsec:extrapolation}
+we discuss how to estimate results as $K \to \infty$ (infinite-basis
+limit) through \textit{extrapolations}.
+
+The addition and removal energies are similar, but they require an
+additional parameter: the total orbital angular momentum $M_\ell$,
+defined as the sum of the $m_\ell$ of each particle.  This is due to
+the presence of multiple states with near-degenerate energies.  For
+this paper, we will consider exclusively the addition/removal energies
+with the lowest $|M_\ell|$ subject to the constraint that the particle
+added/removed lies within the next/last shell.  This means the $N + 1$
+states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for modulus division)
+where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N
+- 1$ states of interest are those with $|M_\ell| = 1 -
+(K_{\mathrm{F}} \bmod 2)$.
+
+Not all cases are solvable with our selection many-body methods.  Low
+frequency systems are particularly strenuous for these many-body
+methods due to their strong correlations, leading to equations that
+are difficult and expensive to solve numerically.  Cases where IM-SRG
+converged too slowly to be feasible or diverged are marked
+``n.c.(I)''.  For the extrapolations in
+Section \ref{subsec:extrapolation}, some fits could not be done due to
+missing data caused by lack of convergence for either the IM-SRG(2) calculations or the CCSD calculations.
+
+Numerical calculations in this paper are performed with a relative
+precision of about $10^{-5}$ or lower.  This does not necessarily mean
+the results are as precise as $10^{-5}$, since numerical errors tend
+to accumulate over the multiple steps of the calculation, thus the
+precision of the final results is expected to be roughly $10^{-4}$.
 
@@
 
-In Figure \ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
-We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.
-
-We do not include results from ``HF only'' to avoid overshadowing the comparatively smaller differences between the non-HF results in the plots.
-Some HF results can be found Figure \ref{fig:by-freq-10-6-normal} instead.
-Generally, HF ground state energies differ from the non-HF ones by a few to several percent, whereas non-HF energies tend to differ from each other by less than a percent.
-
-With respect to the number of shells, both IM-SRG(2) and CCSD appear to converge slightly faster than second order perturbation theory (MP2), likely due to the presence of higher order corrections in IM-SRG(2) and CCSD.
-
-There are a few cases where the IM-SRG over-corrects the result, leading to an energy lower than the quasi-exact DMC results.
-This is not unexpected given that, unlike Hartree--Fock, IM-SRG is non-variational in the presence of operator truncations, which cause small unitarity violations.
-This over-correction tends to occur when the frequency is low (high correlation), or somewhat counterintuitvely, when \emph{few} particles are involved.
+In Fig.~\ref{fig:gs} we display a selection of ground state energies
+calculated using HF + IM-SRG(2) and HF + CCSD as described in
+Section \ref{subsec:methodology}.  We also include results from M\o ller--Plesset perturbation theory to second order (MP2),
+DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for
+comparison where available.
+
+We do not include results from ``HF only'' to avoid overshadowing the
+comparatively smaller differences between the non-HF results in the
+plots.  Some HF results can be found in 
+Fig.~\ref{fig:by-freq-10-6-normal} instead.  Generally, the HF ground
+state energies differ from the non-HF ones by a few to several
+percent, whereas non-HF energies tend to differ from each other by
+less than a percent.
+
+With respect to the number of shells, both IM-SRG(2) and CCSD appear
+to converge slightly faster than second order perturbation theory
+(MP2), mainly due to the presence of higher order corrections in
+IM-SRG(2) and CCSD.
+
+There are a few cases where the IM-SRG over-corrects the result,
+leading to an energy lower than the quasi-exact DMC results.  This is
+not unexpected given that, unlike the Hartree--Fock results, the IM-SRG method is
+non-variational in the presence of operator truncations, which in turn results in 
+small unitarity violations.  This over-correction tends to occur when
+the frequency is low (high correlation), or when \emph{few} particles are involved.
 
@@
   \includegraphics{fig-add2.pdf}
-  \caption{Addition energies for a selection of quantum dot parameters.  See Figure \ref{fig:gs} for details.}
+  \caption{Addition energies for a selection of quantum dot parameters.  See Fig.~\ref{fig:gs} for details.}
   \label{fig:add}
@@
   \includegraphics{fig-rm2.pdf}
-  \caption{Removal energies for a selection of quantum dot parameters.  See Figure \ref{fig:add} for details.}
+  \caption{Removal energies for a selection of quantum dot parameters.  See Fig.~\ref{fig:add} for details.}
   \label{fig:rm}
@@
 
-The results of our addition and removal energy calculations are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.
-The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
-Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
-
-As before, we do not include results from ``HF only'' in these plots as they are significantly further from the rest.
-Analogously, we also exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure CCSD, as QDPT or EOM both add significant contributions to addition and removal energies.
-Some HF only and pure IM-SRG results can be seen in Figure \ref{fig:by-freq-10-6-normal}.
-
-There is strong agreement between IM-SRG(2) + QDPT3 and IM-SRG(2) + EOM2 in many cases, and slightly weaker agreement between the IM-SRG and CCSD families.
-This suggests that the EOM2 corrections are largely accounted for by the inexpensive QDPT3 method.
-However, in some cases, most notably with few particles and high correlations (low frequency), the IM-SRG(2) + QDPT3 result differs significantly from both IM-SRG(2) + EOM2 and CCSD + EOM2.
+The results of our addition and removal energy calculations are
+summarized in Fig.~\ref{fig:add} and Fig.~\ref{fig:rm}
+respectively.  The figures show the the addition/removal energies for
+using the approaches mentioned in Section \ref{subsec:methodology}.
+Where available, results from diffusion Monte Carlo
+(DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
+
+As before, we do not include results from ``HF only'' in these plots
+as they are significantly further from the rest.  Analogously, we also
+exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure
+CCSD, as QDPT or EOM both add significant contributions to addition
+and removal energies.  Some HF only and pure IM-SRG results can be
+seen in Fig.~\ref{fig:by-freq-10-6-normal}.
+
+There is strong agreement between IM-SRG(2) + QDPT3 and IM-SRG(2) +
+EOM2 in many cases, and slightly weaker agreement between the IM-SRG
+and CCSD families.  This suggests that the EOM2 corrections are
+largely accounted for by the inexpensive QDPT3 method.  However, in
+some cases, most notably with few particles and high correlations (low
+frequency), the IM-SRG(2) + QDPT3 result differs significantly from
+both IM-SRG(2) + EOM2 and CCSD + EOM2.
 
@@
 \begin{figure}
-  \centering
-  \includegraphics{fig-by-freq-10-6-normal.pdf}
-  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
-The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
-Lower frequency leads to stronger correlations and thereby a more difficult problem.
-The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot).}
+  \centering \includegraphics{fig-by-freq-10-6-normal.pdf} \caption{The
+  behavior of ground state, addition, and removal energies as a
+  function of the oscillator frequency $\omega$, with $K = 10$ shells
+  in the basis.  The energy is normalized with respect to the
+  Hartree--Fock values to magnify the differences.  Lower frequency
+  leads to stronger correlations and thereby a more difficult problem.}
   \label{fig:by-freq-10-6-normal}
@@
 \begin{figure}
-  \centering
-  \includegraphics{fig-rel-slopes2.pdf}
-  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
-For clarity, the plot does not distinguish between addition and removal energies.
-The horizontal axis shows the system parameters, where $N$ is the number of particles and $\omega$ is the oscillator frequency.
-The vertical axis shows $|\rho_{15}|$ (``relative slope''), which estimates the rate of convergence at 15 total shells.
-The lower the value of $|\rho_{15}|$, the faster the convergence.
-The data points are categorized by the interactions.
-The trends suggest that the singular short-range part of the interaction has a much stronger impact on the convergence than the long-range tail.}
-  \label{fig:rel-slopes}
+  \centering \includegraphics{fig-rel-slopes2.pdf} \caption{The impact
+  of the interaction on convergence of addition and removal energies
+  using IM-SRG(2) + QDPT3.  For clarity, the plot does not distinguish
+  between addition and removal energies.  The horizontal axis shows
+  the system parameters, where $N$ is the number of particles and
+  $\omega$ is the oscillator frequency.  The vertical axis shows
+  $|\rho_{15}|$ (``relative slope''), which estimates the rate of
+  convergence at 15 total shells.  The lower the value of
+  $|\rho_{15}|$, the faster the convergence.  The data points are
+  categorized by the interactions.  The trends suggest that the
+  singular short-range part of the interaction has a much stronger
+  impact on the convergence than the long-range
+  tail.}  \label{fig:rel-slopes}
 \end{figure}
 
-To analyze the rate of convergence more quantitatively, we shall define $\rho_K$ as the relative backward difference of the energy (\textit{relative slope}):
-\begin{align*}
-  \rho_K = \frac{\varepsilon_{K} - \varepsilon_{K - 1}}{\varepsilon_K}
-\end{align*}
-The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge.
-
-In Figure \ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) + QDPT3.
-The many-body methods were tested against a \emph{modified} Coulomb-like interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
+To analyze the rate of convergence more quantitatively, we 
+define $\rho_K$ as the relative backward difference of the energy
+(\textit{relative slope}):
+\begin{align*}
+  \rho_K = \frac{\varepsilon_{K} - \varepsilon_{K - 1}}{\varepsilon_K}.
+\end{align*}
+The denominator allows the quantity to be meaningfully compared
+between different systems.  We expect this quantity to become
+increasingly small as the calculations converge.
+
+In Fig.~\ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) +
+QDPT3.  The many-body methods were tested against a \emph{modified}
+Coulomb-like interaction, parametrized by two lengths
+$\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the
+range of the interaction:
 \begin{align}
-  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
+  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r},
 \end{align}
 where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.
-The coefficient is chosen to ensure the peak of the envelope remains at unity.
-With $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}) = (0, \infty)$ one recovers the original Coulomb interaction.
-By increasing $\sigma_{\mathrm{A}}$ one can truncate the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can truncate the long-range part of the interaction.
-For our numerical experiments we considered the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
-
-Reducing short-range part of the interaction appears improves the rate of convergence substantially.
-Many of the cases have reached the precision of the ODE solver ($10^{-5}$ to $10^{-6}$).
-In contrast, eliminating the long-range part of the interaction had very little effect.
-This suggests that the main cause of the slow convergence lies in the highly repulsive, short-ranged part of the interaction, which leads to the presence of nondifferentiable cusps (the so-called \textit{Coulomb cusps}) in the exact wave functions that are difficult to reproduce exactly using linear combinations of the smooth harmonic oscillator wave functions.
-
-The convergence is negatively impacted at lower frequencies and, to a lesser extent, by the increased number of particles.
-Both are expected: lower frequencies increase the correlation in the system, while higher number of particles naturally require more shells to converge.
-
-In general, there does not appear to be any difference between the convergence behavior of addition energies as compared to that of removal energies.
+The coefficient is chosen to ensure the peak of the envelope remains
+at unity.  With $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}) =
+(0, \infty)$ one recovers the original Coulomb interaction.  By
+increasing $\sigma_{\mathrm{A}}$ one can truncate the short-range part
+of the interaction, and analogously by increasing
+$\sigma_{\mathrm{B}}$ one can truncate the long-range part of the
+interaction.  For our numerical experiments we considered the
+following four combinations of
+$(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$,
+$(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
+
+Reducing the short-range part of the interaction appears improves the rate
+of convergence substantially.  Many of the cases have reached the
+precision of the ODE solver ($10^{-5}$ to $10^{-6}$).  In contrast,
+eliminating the long-range part of the interaction had very little
+effect.  This suggests that the main cause of the slow convergence
+lies in the highly repulsive, short-ranged part of the interaction,
+which leads to the presence of nondifferentiable cusps (the
+so-called \textit{Coulomb cusps}) in the exact wave functions that are
+difficult to reproduce exactly using linear combinations of the smooth
+harmonic oscillator wave functions.
+
+The convergence is negatively impacted at lower frequencies and, to a
+lesser extent, by the increased number of particles.  Both are
+expected: lower frequencies increase the correlation in the system,
+while higher number of particles naturally require more shells to
+converge.
+
+In general, there does not appear to be any difference between the
+convergence behavior of addition energies as compared to that of
+removal energies.
 
@@
 \begin{table}
-  \centering
-  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
-The uncertainties are computed from the approximate Hessian constructed by Levenberg-Marquardt fitting algorithm.
-Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
-  \label{tab:ground-extrapolated}
-  \input{tab-ground-extrapolated}
+  \centering \caption{Extrapolated ground state energies for quantum
+  dots with fit uncertainties.  The uncertainties are computed from
+  the approximate Hessian constructed by Levenberg-Marquardt fitting
+  algorithm.  Extrapolations are done using 5-point fits where the
+  number of shells $K$ ranges between $K_{\text{stop}} - 4$ and
+  $K_{\text{stop}}$
+  (inclusive).}  \label{tab:ground-extrapolated} \input{tab-ground-extrapolated}
 \end{table}
@@
 \begin{figure}
-  \centering
-  \includegraphics{fig-fit-2-1p0-add.pdf}
-  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.
-The grey shaded region contains the masked data points, which are ignored by the fitting procedure.
-The left figure plots the central difference of the addition energies $\varepsilon^{(+)}$ with respect to the number of shells $K$.
-On such a plot, the power law model should appear as a straight line.
-The fits are optimized using the procedure described in Section \ref{subsec:extrapolation}.
-Note that the lines do not evenly pass through the points in the left plot as the fitting weights are tuned for the energy on a linear scale, not the energy differences on a logarithmic scale.}
-  \label{fig:by-fit-2-1p0-add}
+  \centering \includegraphics{fig-fit-2-1p0-add.pdf} \caption{A
+  five-point fit of the addition energies of the $(N, \omega) = (6,
+  1.0)$ system with $K_{\text{stop}} = 15$.  The grey shaded region
+  contains the masked data points, which are ignored by the fitting
+  procedure.  The left figure plots the central difference of the
+  addition energies $\varepsilon^{(+)}$ with respect to the number of
+  shells $K$.  On such a plot, the power law model should appear as a
+  straight line.  The fits are optimized using the procedure described
+  in Section \ref{subsec:extrapolation}.  Note that the lines do not
+  evenly pass through the points in the left plot as the fitting
+  weights are tuned for the energy on a linear scale, not the energy
+  differences on a logarithmic scale.}  \label{fig:by-fit-2-1p0-add}
 \end{figure}
 
-As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
+As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the
+asymptotic convergence of the quantum dot observables in a finite
+harmonic oscillator basis can be approximately described by a power
+law model:
 \begin{align*}
@@
 \end{align*}
-where $\Delta E$ is the difference between the finite-basis result and the infinite-basis result, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.
-The \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
-
-It is difficult to ascertain what $\beta$ is \textit{a priori}, thus we will empirically compute $\beta$ by fitting the following model through our data:
+where $\Delta E$ is the difference between the finite-basis result and
+the infinite-basis result, $K$ is the number of shells in the
+single-particle basis, and $\beta$ is some positive real exponent.
+The \textit{smoothness} of the exact wave function determines the rate
+of the convergence: the more times the exact wave function can be
+differentiated, the higher the exponent $\beta$.
+
+It is difficult to ascertain what $\beta$ is \textit{a priori}, thus
+we will empirically compute $\beta$ by fitting the following model
+through our data:
 \begin{align} \label{eq:power_law_model}
@@
 \end{align}
-As a nonlinear curve fit, it can be quite sensitive to the initial parameters.
-Therefore, good guesses of the parameters are necessary to obtain a sensible result.
-For this, we first fit a linear model of $\log |\partial E / \partial K|$ against $\log K$:
+As a nonlinear curve fit, it can be quite sensitive to the initial
+parameters.  Therefore, good guesses of the parameters are necessary
+to obtain a sensible result.  For this, we first fit a linear model of
+$\log |\partial E / \partial K|$ against $\log K$:
 \begin{align*}
@@
 \end{align*}
-This is useful because linear fits are very robust and will often converge even if the initial parameters are complete nonsense.
-It also provides a means to visually judge quality of the fit.
-The derivative is approximated using the central difference:
-\begin{align*}
-  \frac{\partial E}{\partial K} \approx E\left(K + \frac{1}{2}\right) - E\left(K - \frac{1}{2}\right)
-\end{align*}
-The process of calculating a numericaly derivative can amplify the noise in the data and distorts the weights of the data points.
-Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
-Thus a second accurate nonlinear curve fit is necessary.
-
-The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
-It necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
-The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
-Afterward, we do a final fit with all three parameters free to vary.
-All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm as implemented in \texttt{Minpack}, with equal weighting of all data points.
-
-There is still one additional tuning knob for this model that is not explicitly part of \eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
-Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
-To account for this, we only fit the last few data points within some chosen range.
-If range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, there would be more noise and less confidence in whether the trend is legitimate rather than accidental.
+This is useful because linear fits are very robust and will often
+converge even if the initial parameters are far from their final values.  It
+also provides a means to visually assess the quality of the fit.  The
+derivative is approximated using the central difference:
+\begin{align*}
+  \frac{\partial E}{\partial K} \approx E\left(K + \frac{1}{2}\right) - E\left(K - \frac{1}{2}\right).
+\end{align*}
+The process of calculating numerically the derivative can amplify the
+noise in the data and distorts the weights of the data points.
+Moreover, it does not provide a means to compute $\gamma$, the
+extrapolated energy.  Thus a second accurate nonlinear curve fit is
+necessary.
+
+The parameters $\alpha$ and $\beta$ are extracted from the linear fit
+and used as inputs for a power-law fit of $E$ against $K$.  It
+is necessary to estimate the infinite-basis energy $\gamma$ as well,
+which is done by fitting Eq.~\eqref{eq:power_law_model} while the
+parameters $\alpha$ and $\beta$ are fixed to the initial guesses.  The
+fixing ensures that the fit is still linear in nature and thus highly
+likely to converge.  Afterward, we do a final fit with all three
+parameters free to vary.  All fits are done using the traditional
+Levenberg--Marquardt (LM) optimization algorithm as implemented
+in \texttt{Minpack}, with equal weighting of all data points.  {\bf Ref to this}.
+
+There is still one additional tuning knob for this model that is not
+explicitly part of Eq.~\eqref{eq:power_law_model}: the range of data
+points taken into consideration (\textit{fit range}).  Since the model
+describes the \emph{asymptotic} behavior, we do not expect the fit to
+produce good results when the energy is still very far from
+convergence.  To account for this, we only fit the last few data
+points within some chosen range.  If the range is too large, then the
+non-asymptotic behavior would perturb the result too much, whereas if
+the range is too small, there would be more noise and less confidence
+in whether the trend is legitimate rather than accidental.
 Empirically, we chose to fit the last 5 points of our available data.
-The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
-A specific example of the fit is shown in Figure \ref{fig:by-fit-2-1p0-add}
-
-The LM fitting procedure also computes uncertainties for the parameters from an approximate Hessian of the model function.
-It is therefore tempting to use the uncertainty of the fit to quantify the uncertainty of the extrapolated energy.
-We certainly would not expect this to account for the error due to the operator truncation, but how accurately does it quantify the discrepancy of our extrapolated result from the true infinite-basis energy?
-
-We investigated this idea by performing a fit over \emph{all possible} 5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.
-By comparing the extrapolated results at varying values of $K_{\text{stop}}$ with the extrapolated result at the highest possible $K_{\text{stop}}$ and treating the latter as the ``true'' infinite-basis result, we can statistically assess whether the fit uncertainties are a good measure of the discrepancy from the true infinite-basis result.
-Our results show a somewhat bimodal distribution: when the relative fit uncertainty is higher than $10^{-3.5}$, the fit uncertainty quantifies the discrepancy well; otherwise, the fit uncertainty underestimates the discrepancy by a factor of 10 or less.
-
-Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
-In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
-It is likely that HF is insensitive to the Coulomb cusp.
-
-Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
-This is likely due to its rapid convergence, which leaves very little degree of freedom even for a poorly chosen model.
-Moreover, we found that the fit uncertainties of energy are fairly good measures of the true discrepancy.
-
-Not all fits yield a positive value of $\beta$ for addition and removal energies, which suggests that the data points do not converge, or require a very high number of shells to converge.
-These cases are marked ``n.f.'' in the tables.
-This affects exclusively IM-SRG(2) + QDPT3 for systems with few particles and low frequencies, indicating that perturbation theory is inadequate for such systems.
+The results are shown in
+Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated},
+and \ref{tab:rm-extrapolated}.  A specific example of the fit is shown
+in Fig.~\ref{fig:by-fit-2-1p0-add}
+
+The LM fitting procedure also computes uncertainties for the
+parameters from an approximate Hessian of the model function.  It is
+therefore tempting to use the uncertainty of the fit to quantify the
+uncertainty of the extrapolated energy.  We certainly would not expect
+this to account for the error due to the operator truncation, but how
+accurately does it quantify the discrepancy of our extrapolated result
+from the true infinite-basis energy?
+
+We investigated this idea by performing a fit over \emph{all possible}
+5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.  By
+comparing the extrapolated results at varying values of
+$K_{\text{stop}}$ with the extrapolated result at the highest possible
+$K_{\text{stop}}$ and treating the latter as the ``true''
+infinite-basis result, we can statistically assess whether the fit
+uncertainties are a good measure of the discrepancy from the true
+infinite-basis result.  Our results show a somewhat bimodal
+distribution: when the relative fit uncertainty is higher than
+$10^{-3.5}$, the fit uncertainty quantifies the discrepancy well;
+otherwise, the fit uncertainty underestimates the discrepancy by a
+factor of 10 or less.
+
+Unlike the other methods, Hartree--Fock energies are somewhat unusual
+in that they generally do not conform to the power-law model.  In
+fact, the results and plots seem to indicate an \emph{exponential}
+convergence with respect to the number of shells.  It is likely that
+HF is insensitive to the Coulomb cusp.
+
+Nonetheless, despite the poor fits that often arise, the extrapolated
+energies are often quite good for HF.  This is likely due to its rapid
+convergence, which leaves very little degree of freedom even for a
+poorly chosen model.  Moreover, we found that the fit uncertainties of
+the energy are fairly good measures of the true discrepancy.
+
+Not all fits yield a positive value of $\beta$ for addition and
+removal energies, which suggests that the data points do not converge,
+or require a very high number of shells to converge.  These cases are
+marked ``n.f.'' in the tables.  This affects exclusively IM-SRG(2) +
+QDPT3 for systems with few particles and low frequencies, indicating
+that perturbation theory is inadequate for such systems.
 
@@
 
-We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
-Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
+We have demonstrated calculations of ground state, addition, and
+removal energies of two-dimensional circular quantum dots using a
+variety of many-body methods: ranging from the basic Hartree-Fock
+method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or
+EOM.  Many closed-shell quantum dot systems have been explored,
+ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
 All such results show good agreement with one another.
 
-We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.
-Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
-EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
-
-There are several directions in which the calculations may be improved.
-One can attempt to improve the IM-SRG approximation by incorporating some of the missing higher-body terms in the commutator.
-This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
-While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
-
-The application of IM-SRG eliminates a large number of the QDPT diagrams \ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
-Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
-Moreover, the remaining diagrams at third order can be eliminated through infinite resummation techniques, which would incorporate higher order terms and therefore further increase the accuracy of the result.
-
-We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by T.
-D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
-Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
-
-The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).
-This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.
-
-By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.
-Such interactions can be used to lower the cost of other methods such as configuration interaction (CI), also known as \textit{shell model} in nuclear physics.
-
-Implementation-wise, our current code constructs the two-particle states as simple Slater determinants of their one-particle states.
-This approach is often referred to as \textit{m-scheme} in nuclear physics.
-It is straightforward to implement and works well for general systems, but it fails to exploit all the symmetries in the quantum dot system: not only is spin projection $\hat S_z$ conserved, the Casimir operator $\hat S^2$ is as well.
-A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
-A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
-
-Currently, parallelism within the code is limited to a thread level, i.e.\ shared memory parallelism: the program does cannot take advantage of more than a single compute node, thus it would not scale well on modern high-performance computing facilities.
-Rewriting the algorithm to take advantage of distributed memory parallelism would allow the workload and memory resources to be divided over many computing nodes, allowing larger systems to be explored.
-As with any parallelization, the algorithm must be designed carefully to minimize the communication, which are significantly more costly in parallel platforms.
-
-We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
+We note that the HF + IM-SRG + QDPT combination provides a reasonable
+moderate-cost approach to the calculation of addition and removal
+energies for many systems in comparison to the somewhat more expensive
+and complicated EOM calculations.  Both IM-SRG and CC are reasonably
+accurate compared to the near-exact but factorial-cost FCI method,
+allowing exploration of much higher number of particles than would
+otherwise be possible.  EOM-IM-SRG does have more flexibility over
+perturbative approaches: in particular, it could be more readily used
+to construct excited states \cite{2016arXiv161100661P}, which is more
+difficult for methods such as DMC.
+
+There are several directions in which the calculations may be
+improved.  One can attempt to improve the IM-SRG approximation by
+incorporating some of the missing higher-body terms in the commutator.
+This would also provide some insight into the rate of convergence with
+respect to the operator truncation, providing a sense of how large the
+truncation error is.  While a full 3-body treatment of IM-SRG would be
+extremely costly, it is possible implicitly track for a portion of the
+induced 3-body forces by computing certain diagrams that are either
+lower cost or could be approximated at lower cost \cite{IMSRG}.
+
+The application of IM-SRG eliminates a large number of the QDPT
+diagrams of Fig.~\ref{fig:diagrams-sfe}, which is beneficial as it increases
+the efficiency of the QDPT calculations.  Thus it may be more feasible
+to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
+Moreover, the remaining diagrams at third order can be eliminated
+through infinite resummation techniques, which would incorporate
+higher order terms and therefore further increase the accuracy of the
+result.
+
+We note that this calculation was done entirely using the traditional
+approach of using a high-order ODE solver to solve the flow equation.
+A new technique developed by T. D. Morris \cite{PhysRevC.92.034331}
+uses an alternative approach that obviates the need for a high-order
+ODE solver, leading to much more efficient computations and also
+allowing operators of other observables to be evolved at lower cost,
+which poses a significant advantage over coupled cluster methods.
+Implementing this approach would allows us to study the accuracy and
+convergence of other possibly more sensitive observables.
+
+The IM-SRG method can be extended to support multiple reference states
+(multi-reference IM-SRG or simply
+MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through
+the generalized normal ordering
+formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of
+calculating quantum systems that are far from the magic numbers
+(open-shell systems).  This is a territory that few many-body methods
+can tackle and is one of the major strengths of the IM-SRG approach.
+
+By transforming of the operator-SRG rather than the wave function,
+IM-SRG is more amenable to the construction of
+softened \textit{effective interactions} than
+CC \cite{Hergert2016165}.  Such interactions can be used to lower the
+cost of other methods such as full configuration interaction theory.
+
+Implementation-wise, our current code constructs the two-particle
+states as simple Slater determinants of their one-particle states.
+This approach is often referred to as \textit{m-scheme} in nuclear
+physics.  It is straightforward to implement and works well for
+general systems, but it fails to exploit all the symmetries in the
+quantum dot system: not only is spin projection $\hat S_z$ conserved,
+the Casimir operator $\hat S^2$ is as well.  A more efficient approach
+is to couple the spins of the single-particle states to form
+two-particle states with good $\hat S^2$, an approach analogous
+to \textit{j-scheme} in nuclear physics.  A combination of this with
+the Eckart-Wigner theorem could reduce the computational cost
+significantly, albeit at the cost of increased implementation
+complexity.
+
+We hope to apply these theoretical and technical enhancements not only
+to the study of quantum dots, but to studies of nuclear and atomic
+systems, opening up an even greater range of applications.
 
 \begin{acknowledgments}
-  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.
-This research used computational resources of the Notur project in Norway.
-We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for several discussions.
+  This work was supported by the National Science Foundation Grant
+  No.\ PHY-1404159 (Michigan State University).
 \end{acknowledgments}

### 2017-06-13 Manuscript/paper.tex
Reflow paragraphs and clean up whitespace

@@
 \begin{abstract}
-  We present and compare several many-body methods as applied to
-  two-dimensional quantum dots with circular symmetry.  We calculate
-  the approximate ground state energy using a harmonic oscillator
-  basis optimized by Hartree--Fock (HF) theory and further improve the
-  ground state energy using two post-HF methods: in-medium
-  similarity renormalization group (IM-SRG) and coupled cluster
-  singles-and-doubles (CCSD).  With the application of quasidegenerate
-  perturbation theory (QDPT) or the equation-of-motion (EOM) method,
-  we obtain addition and removal energies as well.  Our results are
-  benchmarked against full configuration interaction (FCI) and
-  diffusion Monte Carlo (DMC) where available.  We examine the rate of
-  convergence and perform extrapolations to the infinite basis limit
-  using a power-law model.
+  We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
+We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
+With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
+Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
+We examine the rate of convergence and perform extrapolations to the infinite basis limit using a power-law model.
 \end{abstract}
@@
 
-The behavior of strongly confined electrons is of fundamental concern
-to many-body theory.  The prototypical system is that of quantum dots,
-also known as ``artificial atoms'', in which electrons are confined
-within artificially constructed semiconducting heterostructures.  Such
-nanoscale systems are highly relevant as they lie at a critical point
-where both theoretical models and experimental observations can
-readily probe quantum phenomena such as tunneling, entanglement, and
-magnetization \cite{reimann2002,engel1993}.  Moreover, unlike many
-physical systems, quantum dots enjoy the benefit of being highly
-tunable through changes in the external field or the structure of the
-confining material.  This allows experiments to quantify the impact of
-quantum effects at different levels of correlation.
-
-The ground states of quantum dots exhibit shell structures and magic
-numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, they provide a rare opportunity to study electronic systems
-without the influence of the atomic nuclei.  They also provide a
-testbed for the development of many-body methods for other systems
-with similar geometry, such as nuclei or neutrons drops \cite{bogner2010}.
-
-Beyond their theoretical relevance, there are numerous potential
-applications of quantum dots.  The electrical and optical properties of
-quantum dots are particularly useful for solar
-cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser
-technology \cite{strauf2010,5075760}.  They have potential medical
-applications in diagnosis and treatment \cite{Ben-Ari02042003}.  And
-of course, quantum dots are also promising candidates for the physical
-realization of quantum computing \cite{PhysRevA.57.120}.
-
-In general, quantum dot systems are not analytically solvable, with
-the exception of two-electron systems or systems with specific strengths
-of the external field \cite{PhysRevA.48.3561}.  Hence, in practical
-applications one can only hope for a numerical solution through
-some \textit{many-body method} or a combination thereof.
-
-One of the most accurate techniques for solving many-body systems is
-that of exact diagonalization, also known as the full configuration
-interaction method.  Unlike most methods, it is assured to converge to
-the exact answer as the size of the finite basis is increased to
-infinity (the so-called \textit{infinite-basis limit}).  Despite this
-significant advantage, it is often not possible  to perform exact
-diagonalization due to its factorially increasing cost with respect to
-the basis size and the number of particles.  This led to the
-development of more cost-effective methods that trade varying amounts
-of accuracy for varying amounts of speed.
-
-In this paper, we analyze the application of several methods to the
-quantum dot systems, including the Hartree--Fock (HF) method, M\o
-ller-Plesset perturbation theory (MP), the in-medium similarity
-renormalization group (IM-SRG) method, coupled cluster (CC)
-theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302},
-quasidegenerate perturbation theory (QDPT), and equation-of-motion
-(EOM) methods.  We compare them against variational and diffusion
-Monte Carlo (VMC and
-DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}
-and full configuration interaction 
-(FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102}
-results, where available,  from the existing literature.
-
-Of these methods, IM-SRG is a recently developed technique that has
-shown significant promises.  Similarity renormalization group (SRG)
-methods are a family of methods that transform the Hamiltonian into a
-band- or block-diagonal form through a continuous sequence of unitary
-transformations.  The goal of such a transformation is to reduce the
-coupling between a subspace of interest -- such as the ground state or
-a set of low-lying states -- and the remaining Hilbert space.  It has
-successfully been applied to systems with various underlying
-potentials to calculate their binding energy and other observables,
-especially in nuclear
-theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
-The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method
-to evolve Hamiltonians in a truncated Fock space, which avoids the
-prohibitive cost of constructing a full many-body Hamiltonian.  The
-effect of the truncation is minimized through the normal-ordering
-technique, which re-expands the operators with respect to a nearby
-many-body reference state rather than the far-away vacuum state.
-
-The article is organized as follows: Section \ref{sec:formalism}
-introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
-use to model circular quantum dots, and gives afterwards an overview
-of the \textit{ab initio} many-body methods used in this paper:
-Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.  Our results are presented in
-Section \ref{sec:results}.  We analyze and compare the differences
-between the various methods and also between different quantum dot
-systems.  We examine the usefulness of extrapolation techniques in
-improving the precision of the results.  Section \ref{sec:conclusions}
-concludes our work and gives perspectives for future work.
+The behavior of strongly confined electrons is of fundamental concern to many-body theory.
+The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
+Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
+Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
+This allows experiments to quantify the impact of quantum effects at different levels of correlation.
+
+The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
+Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
+They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{bogner2010}.
+
+Beyond their theoretical relevance, there are numerous potential applications of quantum dots.
+The electrical and optical properties of quantum dots are particularly useful for solar cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser technology \cite{strauf2010,5075760}.
+They have potential medical applications in diagnosis and treatment \cite{Ben-Ari02042003}.
+And of course, quantum dots are also promising candidates for the physical realization of quantum computing \cite{PhysRevA.57.120}.
+
+In general, quantum dot systems are not analytically solvable, with the exception of two-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
+Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
+
+One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuration interaction method.
+Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increased to infinity (the so-called \textit{infinite-basis limit}).
+Despite this significant advantage, it is often not possible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
+This led to the development of more cost-effective methods that trade varying amounts of accuracy for varying amounts of speed.
+
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
+We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
+
+Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
+Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
+The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
+It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
+The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
+The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
+
+The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
+Our results are presented in Section \ref{sec:results}.
+We analyze and compare the differences between the various methods and also between different quantum dot systems.
+We examine the usefulness of extrapolation techniques in improving the precision of the results.
+Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
 
@@
 
-We shall model the circular quantum dot system as a collection of $N$
-nonrelativistic electrons of mass $m$ in two-dimensional space, trapped
-by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, 
-where $\omega$ is the angular frequency of the oscillator
-trap and $r$ is the distance from the center of the trap.  The
-electrons interact with each other through the standard Coulomb
-interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of
-each electron, $\epsilon$ is the permittivity of the medium, and $R$
-is the distance between the two interacting electrons.
-
-Even though the model system contains five  parameters $(N, m, \omega,
-e, \epsilon)$, many of them are redundant.  With an appropriate choice
-of units, the number of parameters in the system can be reduced to
-just two.  For rest of this paper, we shall use atomic
-units
-%\footnote{Here, ``atomic unit'' is used in an \emph{abstract}
-%sense: we do not assume (nor care) whether $m$, $e$, $\epsilon$
-%correspond to true values in vacuum, or some effective value in
-%medium.} 
-where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to
-one.  The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr
-radius $a$ becomes the unit of length:
+We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
+The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
+
+Even though the model system contains five parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
+With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
+For rest of this paper, we shall use atomic units where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
+The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
 \begin{align*}
@@
 \end{align*}
-This leaves us with $(N, \omega)$ as the only parameters necessary to
-specify the quantum dot system, with $\omega$ in units of
-$E_{\mathrm{h}} / \hbar$.
-
-The behavior of each electron in isolation is described by the
-nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy
-due to the trap $u(\bm{r})$, which combine to form the standard
-harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
+This leaves us with $(N, \omega)$ as the only parameters necessary to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
+
+The behavior of each electron in isolation is described by the nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
 \begin{align*}
@@
 \end{align*}
-Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is
-its position relative to the center of the trap.  The pairwise
-interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$
-is simply the Coulomb interaction:
+Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is its position relative to the center of the trap.
+The pairwise interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$ is simply the Coulomb interaction:
 \begin{align*}
@@
 \end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th
-particle,\footnote{The ordering of the particle labels $j$ is
-unimportant as they exist only for the purpose of bookkeeping.} and
-$\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its
-momentum operator.
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
 
 \begin{figure}
-  \includegraphics{figures/fig-shell-structure-v2.pdf} \caption{The 42
-  lowest single-particle states (the first 5 shells) in the 2D
-  harmonic oscillator basis.  Each box represents a single-particle
-  state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the
-  up/down arrows indicate the spin of the states.  Within each column,
-  the principal quantum number $n$ increases as one traverses
-  upward.}  \label{fig:shell-structure}
+  \includegraphics{figures/fig-shell-structure-v2.pdf}
+  \caption{The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
+Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
+Within each column, the principal quantum number $n$ increases as one traverses upward.}
+  \label{fig:shell-structure}
 \end{figure}
@@
 \end{align*}
-where $p$ is an unknown tuple of quantum numbers.  In Cartesian
-coordinates, the two-dimensional harmonic oscillator is trivially
-reducible to the well-known one-dimensional problem.  However, to
-exploit the circular symmetry, we prefer to use Fock-Darwin states,
-which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving
-orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv
--\mathrm{i} \partial / (\partial \varphi)$.
-
-The Fock-Darwin wave functions can be decomposed into radial and
-angular components,\cite{lohne2010coupled}
-\begin{align}
-  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n,
-  |m_\ell|}(\sqrt \omega \rho)
-  A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\ R_{n, m}(\varrho)
-  &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 /
-  2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\ A_{m_\ell}(\varphi)
-  &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i}
-  m_\ell \varphi}, \notag
-\end{align}
-where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre
-polynomial \cite{NIST:DLMF} of degree $n$ and parameter $\alpha$,
+where $p$ is an unknown tuple of quantum numbers.
+In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
+However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
+
+The Fock-Darwin wave functions can be decomposed into radial and angular components,\cite{lohne2010coupled}
+\begin{align}
+  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n, |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\
+  R_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
+  A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi}, \notag
+\end{align}
+where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre polynomial \cite{NIST:DLMF} of degree $n$ and parameter $\alpha$,
 \begin{align*}
@@
 \end{align*}
-The states are labeled by two quantum numbers: the principal quantum
-number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum
-projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
-For a wave function, $n$ indicates the degree of the Laguerre
-polynomial, whereas $m_\ell$ is simply the eigenvalue of
-$\hat{L}_{\mathrm{z}}$.
-
-Since electrons are spin-$1/2$ fermions, they can occupy either of the
-two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.  Thus, every
-single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$
-contains both a spatial component \eqref{eq:fockdarwin} and a spin
-component,
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
+For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
+
+Since electrons are spin-$1/2$ fermions, they can occupy either of the two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
+Thus, every single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
 \begin{align} \label{eq:singleparticlestate}
-  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell,
-  m_{\mathrm{s}}) \rangle \equiv F_{n,
-  m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}.
+  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}.
 \end{align}
@@
 \end{align}
-which we conveniently call the \textit{shell index} as it labels each
-shell starting from zero.  The shells are equidistant with an energy
-spacing equal to the frequency $\omega$.
-
-Returning to the one-body part of the many-body Hamiltonian,
-$\hat{H}^{[1]}$, we can use the Slater determinant construction to
-build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the
-many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$
-single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$
-from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for
-the triplet $(n, m_\ell, m_{\mathrm{s}})$.  Note that a Slater
-determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the
-single-particle states, but an antisymmetrized sum over all possible
-products,
+which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
+
+Returning to the one-body part of the many-body Hamiltonian, $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
+Note that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
 \begin{align*}
@@
 \end{align*}
-The Slater determinant $|p_1, \ldots, p_N\rangle$ is said
-to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.  By
-construction, Slater determinants satisfy the Pauli exclusion
-principle, ensuring that the exchange of any two particles is
-equivalent to a reversal in the sign of the many-body wave function.
+The Slater determinant $|p_1, \ldots, p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
+By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
 
@@
 \end{align*}
-It is possible for Slater determinants occupying different sets of
-single-particle states to be degenerate in energy.  This is possible
-even for ground states of $\hat{H}^{[1]}$.  However, if the number of
-particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for
-some nonnegative integer $K_{\mathrm{F}}$, there would be just enough
-particles to form a closed-shell Slater determinant, leading to a
-unique, well-isolated ground state.  The values of $N$ at which this
-occurs are said to be \textit{magic numbers}.  We call
-$K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi
-level'').  In particular, a single-particle state is occupied in the
-ground state Slater determinant if and only $k < K_{\mathrm{F}}$,
-where $k$ is the shell index of the single-particle state as defined
-in \eqref{eq:shell_index}.
+It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
+This is possible even for ground states of $\hat{H}^{[1]}$.
+However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
+The values of $N$ at which this occurs are said to be \textit{magic numbers}.
+We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
+In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
 
@@
 \begin{align} \label{eq:second_quantized_hamiltonian}
-  \hat H^{[1]} &= \sum_{pq} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{}, &
-  \hat{H}^{[2]} &= \frac{1}{4} \sum_{pqrs} \langle pq | \hat{H}^{[2]} | rs \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}.
-\end{align}
-where the quantities $\langle p | \hat{H}^{[1]} | q \rangle$
-and $\langle pq | \hat{H}^{[2]} | rs \rangle$ are known
-as \textit{matrix elements} and fully characterize the two operators
-in the basis.  In this paper, we use the letters $p, q, r, s,
-t, \ldots$ to label arbitrary single-particle \textit{states} in the
-basis.  For the harmonic oscillator basis, labels such as $p$ can be
-considered abbreviations for triplets of the form $(n, m_\ell,
-m_{\mathrm{s}})$.  A summation such as $\sum_p$ is then understood as
-a summation over every single-particle basis state $p$.  This is not
-to be confused with summations such as $\sum_j$
-from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$
-denoting an arbitrary \textit{particle}.  We thus see another benefit
-with second quantization: the Hamiltonian representation makes no
-attempt to distinguish particles at all, as expected for particles
-with quantum statistics.
+  \hat H^{[1]} &= \sum_{p q} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{}, &
+  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}.
+\end{align}
+where the quantities $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p q | \hat{H}^{[2]} | r s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
+In this paper, we use the letters $p, q, r, s, t, \ldots$ to label arbitrary single-particle \textit{states} in the basis.
+For the harmonic oscillator basis, labels such as $p$ can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
+A summation such as $\sum_p$ is then understood as a summation over every single-particle basis state $p$.
+This is not to be confused with summations such as $\sum_j$ from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$ denoting an arbitrary \textit{particle}.
+We thus see another benefit with second quantization: the Hamiltonian representation makes no attempt to distinguish particles at all, as expected for particles with quantum statistics.
 
@@
 \begin{align}
-  \hat{H} = \sum_{p,q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{pqrs} \langle pq | \hat{H}^{[2]} | rs \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r .
+  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
 \label{eq:vacuumhamiltonian}
 \end{align}
-Due to the antisymmetry of Slater determinants, we have the property
-that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign
-of $\langle pq | \hat{H}^{[2]} | rs \rangle$, leading to a 4-fold
-symmetry that must be canceled out by the $1/4$ factor in front of the
-summation in \eqref{eq:vacuumhamiltonian}.  For this reason, the
-two-body matrix element $\langle pq | \hat{H}^{[2]} | rs \rangle$
-is commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the (non-antisymmetric) interaction
-integral,
+Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a 4-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
+For this reason, the two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
+This is not to be confused with the (non-antisymmetric) interaction integral,
 \begin{align} \label{eq:interactionintegral}
-  v_{p_1p_2p_3p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'.
-\end{align}
-This object only has a two-fold symmetry: $v_{p_1p_2p_3p_4} = v_{p_2p_1p_4p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
+  v_{p_1 p_2 p_3 p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'.
+\end{align}
+This object only has a two-fold symmetry: $v_{p_1 p_2 p_3 p_4} = v_{p_2 p_1 p_4 p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
 \begin{align} \label{eq:antisymmetricmatrixelement}
-  \langle pq | \hat{H}^{[2]} | rs \rangle = v_{pqrs} - v_{pqsr}
-\end{align}
-
-With the basic formalism and notation established along with the
-system of interest, we may begin to discuss the various techniques to
-solve the full many-body problem.  The principal difficulty stems from
-the fact that, due to the presence of interactions, the exact solution
-is in general \emph{not} a single Slater determinant built from the
-single-particle states.  Hence, it is not possible to trivially reduce
-the problem to that of a single particle as we had done previously.
-
-However, if we assume the interaction alters the behavior of the
-system only mildly, we can use a Slater determinant of the
-noninteracting system as a starting point and then apply various
-methods to improve the accuracy of the solution.  This is a general
-strategy for many of the many-body methods that we shall describe.
+  \langle p q | \hat{H}^{[2]} | r s \rangle = v_{p q r s} - v_{p q s r}
+\end{align}
+
+With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
+The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
+Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
+
+However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
+This is a general strategy for many of the many-body methods that we shall describe.
 
@@
 
-One of the simplest numerical corrections that could be applied to the
-initial guess is that of the Hartree--Fock (HF) method.  Using the
-variational principle, one can compute an approximate ground state
-$\Phi$ by minimizing the energy expectation value
+One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
+Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value
 \begin{align} \label{eq:hfexpectation}
@@
 \end{align}
-with respect to $|\Phi\rangle$, subject to the restriction that
-$|\Phi\rangle$ remains a single Slater determinant constructed from an
-unknown single-particle basis.  The restriction is what enables the
-simplicity and efficiency of this method.  We shall denote each
-unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To perform numerical calculations, we further assume that each unknown
-state $|q'\rangle$ is built from a linear combination of known states
-$|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined
-via the transformation equation
-\begin{align*}
-  |q'\rangle \equiv \sum_p |p\rangle C_{pq'}.
-\end{align*}
-This allows the problem to be reduced from an abstract minimization
-problem \eqref{eq:hfexpectation} to a concrete numerical problem.  The
-caveat is that the set of known functions be large enough to capture
-the relevant behavior of the system.
-
-If the interaction is not too strong, it is common to use the
-single-particle states of the noninteracting Hamiltonian
-$\hat{H}^{[1]}$ as the set of known states.
-
-To ensure orthonormality of the states, we require there to be as many
-unknown states $|q'\rangle$ as known states $|p\rangle$, and the
-coefficient matrix $\bm C$ must be unitary.  These conditions are more
-strict than necessary, but they greatly simplify the calculations and
-allow the states $|q'\rangle$ to act as \textit{optimized} inputs for
-methods beyond HF.  At the end of the calculation, of the set of
-states $|q'\rangle$ there would exactly $N$ \textit{occupied} states
-that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary
-space into which particles can be excited by the interaction
-$\hat{H}^{[2]}$ during the post-HF calculation.
+with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
+The restriction is what enables the simplicity and efficiency of this method.
+We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
+\begin{align*}
+  |q'\rangle \equiv \sum_p |p\rangle C_{p q'}.
+\end{align*}
+This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
+The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
+
+If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
+
+To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
+These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
+At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
+The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
 
@@
 \begin{align}
-  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{ii} + \sum_{ij} n_i n_j H^{[2] \prime}_{ijij} \label{eq:hfenergy},
+  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{i i} + \sum_{i j} n_i n_j H^{[2] \prime}_{i j i j} \label{eq:hfenergy},
 \end{align}
@@
 \begin{align}
-  H^{[1] \prime}_{pq} &\equiv \sum_{rs} C_{rp}^* \langle r | \hat{H}^{[1]} | s \rangle C_{sq}^{} \label{eq:hftransform1} \\
-  H^{[2] \prime}_{pqrs} &\equiv \sum_{tuvw} C_{tp}^* C_{uq}^* \langle tu | \hat{H}^{[2]} | vw \rangle C_{vr}^{} C_{ws}^{}, \label{eq:hftransform2}
+  H^{[1] \prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s q}^{} \label{eq:hftransform1} \\
+  H^{[2] \prime}_{p q r s} &\equiv \sum_{t u v w} C_{t p}^* C_{u q}^* \langle t u | \hat{H}^{[2]} | v w \rangle C_{v r}^{} C_{w s}^{}, \label{eq:hftransform2}
 \end{align}
@@
 
-With the method of Lagrange multipliers, the minimization problem can
-be reduced to the solving of a nonlinear equation --
-the \textit{Hartree--Fock equation}:
+With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree--Fock equation}:
 \begin{align} \label{eq:hartreefock}
@@
 \begin{align} \label{eq:fock}
-  F_{pq} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{rsi} n_i C_{ri}^* \langle pr | \hat{H}^{[2]} | qs \rangle C_{si}^{},
+  F_{p q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r s i} n_i C_{r i}^* \langle p r | \hat{H}^{[2]} | q s \rangle C_{s i}^{},
 \end{align}
@@
 
-Aside from trivial cases, the HF equation is generally solved using an
-iterative algorithm.  We begin with an initial guess $\bm{C}^{(i)}$,
-which is fed into Eq.~\eqref{eq:fock} to produce the Fock matrix.  This is
-then used in Eq.~\eqref{eq:hartreefock}, which leads to a standard
-eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix
-of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of
-eigenvalues.  This process can be repeated indefinitely until $\bm{C}$
-approaches a fixed point.  While in theory it is possible for the
-solution to never reach a fixed point, or that it may require a
-unfeasibly large number of iterations, in practice this naive approach
-can adequately provide solutions for many cases.  In other cases where
-it is insufficient, methods such as DIIS, Broyden's method, or
-even \textit{ad hoc} linear mixing can improve and accelerate
-convergence greatly.  Therefore, the possibility of slow or
-non-convergence is generally not a concern in practice.
-
-For the initial guess, we simply use the ground state of our
-noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity
-matrix.  At each iteration, we calculate the sum of the Lagrange
-multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the
-iteration approaches convergence, the change in the sum per iteration
-should decrease rapidly.
-
-Since HF restricts the ground state to merely a single Slater
-determinant of single-particle states, it cannot provide an exact
-solution to a problem where multi-particle correlations are present
-even if the single-particle basis is not truncated (infinite in size).
-The discrepancy between the Hartree--Fock energy and the exact ground
-state energy is often referred to as the \textit{correlation energy},
-by definition.  The focus of post-HF methods such as IM-SRG or coupled
-cluster is to add corrections beyond mean-field approximations such as
-HF.
-
-To make use of the HF solution as the reference state for future
-calculations, we transform the operators via Eqs.~\eqref{eq:hftransform1}
-and \eqref{eq:hftransform2}.  Therefore, the post-HF methods described
-in the next few sections generally use the transformed operators
-$\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.  However,
-we will not annotate them with the prime symbols as the methods are
-generic and can be applied to any reference state, whether optimized
-by HF or not.
+Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
+We begin with an initial guess $\bm{C}^{(i)}$, which is fed into Eq.~\eqref{eq:fock} to produce the Fock matrix.
+This is then used in Eq.~\eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
+This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
+While in theory it is possible for the solution to never reach a fixed point, or that it may require a unfeasibly large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
+In other cases where it is insufficient, methods such as DIIS, Broyden's method, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
+Therefore, the possibility of slow or non-convergence is generally not a concern in practice.
+
+For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity matrix.
+At each iteration, we calculate the sum of the Lagrange multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration should decrease rapidly.
+
+Since HF restricts the ground state to merely a single Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
+The discrepancy between the Hartree--Fock energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
+The focus of post-HF methods such as IM-SRG or coupled cluster is to add corrections beyond mean-field approximations such as HF.
+
+To make use of the HF solution as the reference state for future calculations, we transform the operators via Eqs.~\eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
+Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
+However, we will not annotate them with the prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
 
@@
 
-The central theme of similarity renormalization group (SRG) methods is
-the application of a continuous sequence of unitary transformations on
-the Hamiltonian to evolve it into a band- or block-diagonal form, see
-for examples Refs.~\cite{kehreinflow2006,heikophysrep2016,lnp936} for
-derivations and calculational details.
-
-This allows the decoupling of
-a small, designated \textit{model space} from its larger complementary
-space.  The problem can thus be truncated to the small model space
-while preserving a large amount of information about the system.
-
-The sequence of transformations is parameterized by a continuous
-variable $s$ known as the \textit{flow parameter}.  Without loss of
-generality, we can define $s = 0$ to be the beginning of this
-sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.  At
-any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to
-the original Hamiltonian by
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.~\cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.
+
+This allows the decoupling of a small, designated \textit{model space} from its larger complementary space.
+The problem can thus be truncated to the small model space while preserving a large amount of information about the system.
+
+The sequence of transformations is parameterized by a continuous variable $s$ known as the \textit{flow parameter}.
+Without loss of generality, we can define $s = 0$ to be the beginning of this sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.
+At any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to the original Hamiltonian by
 \begin{align*}
@@
 \end{align*}
-where $U(s)$ is a unitary operator that describes the product of all such
-transformations since $s = 0$.  Taking the derivative with respect to $s$, we obtain:
-\begin{align*}
-  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\Ds} \hat{H}(0) \hat{U}^\dagger(s)
-  + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
+where $U(s)$ is a unitary operator that describes the product of all such transformations since $s = 0$.  Taking the derivative with respect to $s$, we obtain:
+\begin{align*}
+  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\Ds} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
 \end{align*}
@@
 \end{align}
-This equation allows $\hat{H}(s)$ to be evaluated without explicitly
-constructing the full transformation $\hat U(s)$.  The focus is
-instead shifted to the operator $\hat \eta(s)$, the \textit{generator}
-of the transformation.  When $\hat \eta(s)$ is \emph{multiplicatively}
-integrated (\textit{product integral}), the full unitary
-transformation $\hat U(s)$ is recovered:
+This equation allows $\hat{H}(s)$ to be evaluated without explicitly constructing the full transformation $\hat U(s)$.
+The focus is instead shifted to the operator $\hat \eta(s)$, the \textit{generator} of the transformation.
+When $\hat \eta(s)$ is \emph{multiplicatively} integrated (\textit{product integral}), the full unitary transformation $\hat U(s)$ is recovered:
 \begin{align} \label{eq:etaintegral}
@@
 \end{align}
-where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta
-s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
-This is the formal solution to the linear differential
-equation Eq.~(\ref{eq:etadefinition}).  The product integral
-in Eq.~(\ref{eq:etaintegral}) may also be reinterpreted
-as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy
-to time-ordering from quantum field theory.
-
-The power of SRG methods lies in the flexibility of the generator
-$\hat{\eta}$, which is usually chosen in an $s$-dependent manner.  In
-particular, it is often dependent on the evolving Hamiltonian
-$\hat{H}(s)$.  The operator $\hat{\eta}$ determines which parts of the
-Hamiltonian matrix would become suppressed by the evolution, which are
-usually considered ``off-diagonal'' in an abstract sense.  The
-``off-diagonal'' parts could be elements far away from the matrix
-diagonal, in which case the evolution drives the matrix towards a
-band-diagonal form.  Or, the ``off-diagonal'' parts could be elements
-that couple the ground state from the excited state, in which case the
-evolution drives the matrix towards a block-diagonal form that
-isolates the ground state.  Or, the ``off-diagonal'' could be
-literally the elements that do not lie on the diagonal, in which case
-the evolution would simply diagonalize the Hamiltonian.  Through
-different choices of $\hat{\eta}$, the SRG evolution can be controlled
-and adapted to the features of a particular problem.
+where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
+This is the formal solution to the linear differential equation Eq.~(\ref{eq:etadefinition}).
+The product integral in Eq.~(\ref{eq:etaintegral}) may also be reinterpreted as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy to time-ordering from quantum field theory.
+
+The power of SRG methods lies in the flexibility of the generator $\hat{\eta}$, which is usually chosen in an $s$-dependent manner.
+In particular, it is often dependent on the evolving Hamiltonian $\hat{H}(s)$.
+The operator $\hat{\eta}$ determines which parts of the Hamiltonian matrix would become suppressed by the evolution, which are usually considered ``off-diagonal'' in an abstract sense.
+The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
+Or, the ``off-diagonal'' parts could be elements that couple the ground state from the excited state, in which case the evolution drives the matrix towards a block-diagonal form that isolates the ground state.
+Or, the ``off-diagonal'' could be literally the elements that do not lie on the diagonal, in which case the evolution would simply diagonalize the Hamiltonian.
+Through different choices of $\hat{\eta}$, the SRG evolution can be controlled and adapted to the features of a particular problem.
 
@@
 
-The SRG flow equation Eq.~\eqref{eq:imsrgode} can be solved in the
-second quantization formalism described in
-Section \ref{subsec:modelHamiltonian}, where field operators are
-defined with respect to the physical vacuum state.  However, since the
-basis of a many-body problem grows factorially with the number of
-particles and the size of the model space, the applicability of the
-naive (free-space) SRG method is restricted to comparatively small
-systems.  A more practical approach is to perform the
-evolution \textit{in medium}, i.e.\ using a many-body Slater
-determinant as a reference \cite{kehrein2006flow}.  This gives rise to
-the IM-SRG method \cite{bogner2012,heikophysrep2016,lnp936}.
-
-The second-quantized operators in
-Eq.~\eqref{eq:second_quantized_hamiltonian} are constructed with
-respect to the vacuum state in the sense that their operator strings
-$\hat{a}_p^\dagger \hat{a}_q$ and
-$\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have
-expectation values of zero in vacuum:
+The SRG flow equation Eq.~\eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
+However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
+A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
+This gives rise to the IM-SRG method \cite{bogner2012,heikophysrep2016,lnp936}.
+
+The second-quantized operators in Eq.~\eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
 \begin{align*}
@@
 \end{align*}
-where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label
-the occupied states.  One can define a set of \textit{quasiparticle
-field operators} $\hat b$ and $\hat b^\dagger$ that obey the same
-anticommutation relations as the $\hat a$ operators.  The normal
-ordering of the quasiparticle field operators is straightforward to
-compute.  What is more interesting is the normal ordering of the
-physical field operators $\hat a$ and $\hat a^\dagger$ with respect to
-$|\Phi\rangle$:
+where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label the occupied states.
+One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators.
+The normal ordering of the quasiparticle field operators is straightforward to compute.
+What is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $|\Phi\rangle$:
 \begin{align*}
@@
 \begin{align}
-  \hat{H} = H^{[0]} + \sum_{pq} H^{[1]}_{pq} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{pqrs} H^{[2]}_{pqrs} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}},
+  \hat{H} = H^{[0]} + \sum_{p q} H^{[1]}_{p q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p q r s} H^{[2]}_{p q r s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}},
   \label{eq:normordhamiltonian}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{ij} n_i n_j \langle ij | \hat{H}^{[2]} | ij \rangle, \\
-  H^{[1]}_{pq} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle pi | \hat{H}^{[2]} | qi \rangle, \\
-  H^{[2]}_{pqrs} &\equiv \langle pq | \hat{H}^{[2]} | rs \rangle. \\
-\end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is
-simply the HF energy $E_\Phi$ and $H^{[1]}_{pq}$ is the Fock matrix
-$F_{pq}$.  The operator $\hat H$ in
-Eq.~\eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$
-in Eq.~\eqref{eq:vacuumhamiltonian}.  The only difference is that the
-meaning of a ``$k$-body operator'' has been redefined with respect to
-the reference state $\Phi$ rather than vacuum state $\ket{}$, causing
-matrix elements to be reshuffled among the $k$-body operators.  Where
-this makes a critical difference is when the operator expressions
-are \emph{truncated}, i.e.\ some $k$-body operators may be discarded
-from the computation for efficiency reasons.  Normal-ordering can
-drastically alter the importance of the $k$-body operators with
-respect to each other.
-
-Higher-body operators arise from integrating the flow equations
-(\ref{eq:imsrgode}), which is one of the major challenges of the SRG
-method.  With each evaluation of the commutator, the Hamiltonian gains
-terms of higher order, and these induced contributions will in
-subsequent integration steps feed back into terms of lower order.
-Thus, the higher-body contributions are not irrelevant to the final
-solution even if only the ground state energy (zero-body component) is
-of interest.
-
-Computationally, higher-body terms rapidly become unfeasible to
-handle: the amount of memory required to store a $k$-body operator is
-grows exponentially with $k$.  Moreover, the flow equations are
-capable of generating an infinite number of higher-body terms as the
-Hamiltonian evolves.  Thus, to make the method tractable, the IM-SRG
-flow equations must be closed by truncating the equations to a finite
-order.
-
-In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the
-two-body level, leading to an approach known as IM-SRG(2).  This
-normal-ordered two-body approximation appears to be sufficient in many
-cases and has yielded excellent results for several
-nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
-
-Note that the loss of three- and higher-body terms (\textit{operator
-truncation}) is only one out of the two sources of error in this
-method.  The other source of error is due to the \textit{basis
-truncation}, a concern for any method that relies on a finite
-single-particle basis such as IM-SRG.  The latter can be reduced by
-increasing the size of the basis at the expense of greater
-computational effort, albeit the cost increases much less rapidly in
-this direction.  In IM-SRG the CPU cost is polynomial with respect to
-$N_{\mathrm{b}}$, the number of states in the single-particle basis.
-For IM-SRG(2) in particular, the CPU cost scales roughly as
-$\mathcal{O}(N_{\mathrm{b}}^6)$.
+  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} n_i n_j \langle i j | \hat{H}^{[2]} | i j \rangle, \\
+  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
+  H^{[2]}_{p q r s} &\equiv \langle p q | \hat{H}^{[2]} | r s \rangle. \\
+\end{align*}
+If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix $F_{p q}$.
+The operator $\hat H$ in Eq.~\eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.~\eqref{eq:vacuumhamiltonian}.
+The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
+Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
+Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
+
+Higher-body operators arise from integrating the flow equations (\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
+With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
+Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy (zero-body component) is of interest.
+
+Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
+Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
+Thus, to make the method tractable, the IM-SRG flow equations must be closed by truncating the equations to a finite order.
+
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
+This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
+The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
+The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
+In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
+For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
 
@@
 \begin{align*}
-\hat{\eta} = \sum_{pq} \eta_{pq}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
-\frac{1}{4} \sum_{pqrs}\eta_{pqrs}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r},
-\end{align*}
-where $\eta_{pq}^{[1]}$ and $ \eta_{pqrs}^{[2]}$ respectively are its
-one- and two-body matrix elements normal ordered with respect to
-$\Phi$, subject to the antihermittivity constraint.
-
-By expanding the commutator in Eq.~\eqref{eq:imsrgode} and discarding
-the three-body term, we obtain the matrix-element form of the
-IM-SRG(2) flow equation:
+\hat{\eta} = \sum_{p q} \eta_{p q}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
+\frac{1}{4} \sum_{p q r s}\eta_{p q r s}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r},
+\end{align*}
+where $\eta_{p q}^{[1]}$ and $ \eta_{p q r s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$, subject to the antihermittivity constraint.
+
+By expanding the commutator in Eq.~\eqref{eq:imsrgode} and discarding the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
 \begin{align}
@@
   &\equiv
-    \sum_{ia} n_i \bar{n}_a A^{[1]}_{ia} B^{[1]}_{ai}
-    + \frac{1}{4} \sum_{ijab} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{ijab} B^{[2]}_{abij},
+    \sum_{i a} n_i \bar{n}_a A^{[1]}_{i a} B^{[1]}_{a i}
+    + \frac{1}{4} \sum_{i j a b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i j a b} B^{[2]}_{a b i j},
     \label{eq:flow0} \\
@@
   &\equiv
-    \sum_{r} A^{[1]}_{pr} B^{[1]}_{rq}
-    - \frac{1}{2} \sum_{ija} n_i n_j \bar{n}_a A^{[2]}_{ijaq} B^{[2]}_{apij}
-    + \frac{1}{2} \sum_{iab} n_i \bar{n}_a \bar{n}_b A^{[2]}_{ipab} B^{[2]}_{abiq}
+    \sum_{r} A^{[1]}_{p r} B^{[1]}_{r q}
+    - \frac{1}{2} \sum_{i j a} n_i n_j \bar{n}_a A^{[2]}_{i j a q} B^{[2]}_{a p i j}
+    + \frac{1}{2} \sum_{i a b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i p a b} B^{[2]}_{a b i q}
     \notag \\
   &\hphantom{=}
-    + \sum_{ia} n_i \bar{n}_a \left(
-    A^{[1]}_{ia} B^{[2]}_{apiq}
-    + A^{[2]}_{ipaq} B^{[1]}_{ai}
+    + \sum_{i a} n_i \bar{n}_a \left(
+    A^{[1]}_{i a} B^{[2]}_{a p i q}
+    + A^{[2]}_{i p a q} B^{[1]}_{a i}
     \right)
     \label{eq:flow1} \\
-  D^{[2]}_{pqrs}(A, B)
+  D^{[2]}_{p q r s}(A, B)
   &\equiv
-    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{rs}
-    \sum_{ia} n_i \bar{n}_a A^{[2]}_{ipar} B^{[2]}_{aqis}
+    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r s}
+    \sum_{i a} n_i \bar{n}_a A^{[2]}_{i p a r} B^{[2]}_{a q i s}
     \notag \\
   &\hphantom{=}
-    + \frac{1}{2} \sum_{ij} n_i n_j A^{[2]}_{ijrs} B^{[2]}_{pqij}
-    + \frac{1}{2} \sum_{ab} \bar{n}_a \bar{n}_b A^{[2]}_{pqab} B^{[2]}_{abrs}
+    + \frac{1}{2} \sum_{i j} n_i n_j A^{[2]}_{i j r s} B^{[2]}_{p q i j}
+    + \frac{1}{2} \sum_{a b} \bar{n}_a \bar{n}_b A^{[2]}_{p q a b} B^{[2]}_{a b r s}
     \notag \\
@@
     + \sum_{t} \left(
-    \tilde{\mathcal{A}}_{pq} A^{[1]}_{qt} B^{[2]}_{ptrs}
-    + \tilde{\mathcal{A}}_{rs} A^{[2]}_{pqrt} B^{[1]}_{ts}.
+    \tilde{\mathcal{A}}_{p q} A^{[1]}_{q t} B^{[2]}_{p t r s}
+    + \tilde{\mathcal{A}}_{r s} A^{[2]}_{p q r t} B^{[1]}_{t s}.
     \right)
@@
 
-The equations can be derived directly from the anticommutation
-relations of the field operators, but it is more convenient to use
-Wick's theorem \cite{PhysRev.80.268} or, even more efficiently,
-diagrammatic techniques \cite{shavitt2009many} to arrive at the
-results.  In particular, Figure \ref{fig:diagrams-imsrg} shows the
-diagrammatic form of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and
-Eq.~\eqref{eq:flow2}.
-
-The commutator in the flow equations Eq.~\eqref{eq:imsrgode} ensures
-that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked
-diagrams} only \cite{shavitt2009many}.  This indicates that IM-SRG is
-a size-extensive \cite{ISI:A1981MN73700014} method by construction,
-even if the operators are truncated.
-
-An accurate and robust ODE solver is required to solve
-Eq.~\eqref{eq:imsrgode}.  In particular, the solver must be capable of
-handling the stiffness that often arises in such problems.  For our
-numerical experiments, we used a high-order ODE solver algorithm by
-L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which
-is a multistep method based on the implicit Adams predictor-corrector
-formulas.  Its source code is freely available \cite{odesolver}.
-
-Through the flow equation and with an appropriate choice of the
-generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will
-gradually approach a more ``diagonal'' form.  If the ``diagonal'' form
-decouples the ground state from the excited states, then $\hat
-U(\infty) \ket{\Phi}$ would yield the exact ground state solution of
-the problem if no operator or basis truncations are made.  In
-particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
+The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
+In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and Eq.~\eqref{eq:flow2}.
+
+The commutator in the flow equations Eq.~\eqref{eq:imsrgode} ensures that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked diagrams} only \cite{shavitt2009many}.
+This indicates that IM-SRG is a size-extensive \cite{ISI:A1981MN73700014} method by construction, even if the operators are truncated.
+
+An accurate and robust ODE solver is required to solve Eq.~\eqref{eq:imsrgode}.
+In particular, the solver must be capable of handling the stiffness that often arises in such problems.
+For our numerical experiments, we used a high-order ODE solver algorithm by L.\ F.\ Shampine and M.\ K.\ Gordon \cite{shampine1975computer}, which is a multistep method based on the implicit Adams predictor-corrector formulas.
+Its source code is freely available \cite{odesolver}.
+
+Through the flow equation and with an appropriate choice of the generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will gradually approach a more ``diagonal'' form.
+If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
+In particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
 
@@
 \end{align*}
-where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the
-Hamiltonian and $\hat{H} - \hat{H}^{\text{d}}$ denotes the
-``off-diagonal'' part.  This is in the abstract sense described at the
-end of Section \ref{subsubsec:srgmethods}.
-
-Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian
-operators, it is antihermitian as required for a generator.
-Additionally, it can be shown that the commutator has the property of
-suppressing off-diagonal matrix elements as the state evolves via the
-flow equation \cite{kehrein2006flow}, as we would like.  Matrix
-elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian
-couples states with large energy differences -- are suppressed much
-faster than those ``close'' to the diagonal.
-
-Apart from Wegner's generator, there exist several other ones in
-literature. One choice, proposed by
-White \cite{White:cond-mat0201346}, makes numerical approaches much
-more efficient.  The problem with the Wegner generator is the widely
-varying decaying speeds of the Hamiltonian matrix elements.  Terms
-with large energy separations from the ground state are suppressed
-initially, followed by those with smaller energy separations.  This
-leads to stiffness in the flow equation, leading to numerical
-difficulties in solving the set of coupled differential equations.
-
-The White generator takes an alternative approach, which is well
-suited for problems where one is mainly interested in the ground state
-of a system.  Firstly, instead of driving all off-diagonal elements of
-the Hamiltonian to zero, the generator focuses exclusively on those
-ones that are coupled to the reference state $\Phi$ so as to decouple
-the reference state from the remaining Hamiltonian.  This reduces the
-amount of change done to the Hamiltonian, reducing the accuracy lost
-from the operator truncation.  Secondly, the rate of decay in
-Hamiltonian matrix elements are approximately normalized by dividing
-the generator matrix elements by an appropriate factor.  This ensures
-that the affected elements decay at approximately the same rate,
-reducing the stiffness of the flow equations.
+where $\hat{H}^{\text{d}}$ denotes the ``diagonal'' part of the Hamiltonian and $\hat{H} - \hat{H}^{\text{d}}$ denotes the ``off-diagonal'' part.
+This is in the abstract sense described at the end of Section \ref{subsubsec:srgmethods}.
+
+Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian operators, it is antihermitian as required for a generator.
+Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
+Matrix elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian couples states with large energy differences -- are suppressed much faster than those ``close'' to the diagonal.
+
+Apart from Wegner's generator, there exist several other ones in literature.
+One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
+The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
+Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
+This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
+
+The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
+Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
+This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
+Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
+This ensures that the affected elements decay at approximately the same rate, reducing the stiffness of the flow equations.
 
@@
 \begin{align*}
-\eta^{\prime [1]}_{ai} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{ai}}{\tilde{\Delta}^{[1]}_{ai}} &
-\eta^{\prime [2]}_{abij} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{abij}}{\tilde{\Delta}^{[2]}_{abij}}
+\eta^{\prime [1]}_{a i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}} &
+\eta^{\prime [2]}_{a b i j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}}
 \end{align*}
@@
 \begin{align}
-\tilde{\Delta}^{[1]}_{ai} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{aiai}, \notag \\
-\tilde{\Delta}^{[2]}_{abij} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{abij}, \notag \\
-\Delta^{[2]}_{P_1P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2p_2}, \label{eq:moellerplessetdenominator} \\
-w_{abij}
-  &\equiv H^{[2]}_{abab} - H^{[2]}_{aiai} - H^{[2]}_{bibi} \notag \\
-  &\qquad + H^{[2]}_{ijij} - H^{[2]}_{ajaj} - H^{[2]}_{bjbj}. \notag
-\end{align}
-Some authors {\bf ref}  use the M\o ller--Plesset denominators $\Delta$
-instead, leading to a slightly different variant of the White
-generator.
-{\bf define Moller plesset denos and give reference}.
-
-Compared to the Wegner generator, where the derivatives of the final
-flow equations contain cubes of the Hamiltonian matrix elements (i.e.\
-each term contains a product of 3 one-body and/or two-body matrix
-elements), the elements in White generators contribute only linearly.
-This reduces the stiffness in the differential equation, providing a
-net increase in computational efficiency as stiff ODE solvers tend to
-be slower and consume more memory.
+\tilde{\Delta}^{[1]}_{a i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a i a i}, \notag \\
+\tilde{\Delta}^{[2]}_{a b i j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a b i j}, \notag \\
+\Delta^{[2]}_{P_1 P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1 p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2 p_2}, \label{eq:moellerplessetdenominator} \\
+w_{a b i j}
+  &\equiv H^{[2]}_{a b a b} - H^{[2]}_{a i a i} - H^{[2]}_{b i b i} \notag \\
+  &\qquad + H^{[2]}_{i j i j} - H^{[2]}_{a j a j} - H^{[2]}_{b j b j}. \notag
+\end{align}
+Some authors {\bf ref} use the M\o ller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.  {\bf define Moller plesset denos and give reference}.
+
+Compared to the Wegner generator, where the derivatives of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White generators contribute only linearly.
+This reduces the stiffness in the differential equation, providing a net increase in computational efficiency as stiff ODE solvers tend to be slower and consume more memory.
 
@@
 \end{align*}
-This is known as coupled cluster singles and doubles (CCSD), with an
-asymptotic computational cost that scales like IM-SRG(2).  This
-truncation has been successfully applied to many problems in quantum
-chemistry \cite{RevModPhys.79.291} and nuclear
-physics \cite{0034-4885-77-9-096302}.  In addition, we also truncate
-the three-body effective Hamiltonian terms that are induced by the
-similarity transformation.  Figure \ref{fig:diagrams-ccsd} shows the
-diagrammatic representation of Eq.~\eqref{eq:cc_heff1} in CCSD.
+This is known as coupled cluster singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).
+This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
+In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
+Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.~\eqref{eq:cc_heff1} in CCSD.
 
 \begin{figure}
-  \includegraphics{fig-diagrams-ccsd.pdf} \caption{Diagrammatic
-  representation of $\bar{H}$ of Eq.~\eqref{eq:cc_heff1}, where open
-  circles represent the excitation cluster operators $\hat{T}_{1}$ and
-  $\hat{T}_{2}$, and filled circles represent the two-body interaction
-  $\hat{H}^{[2]}$.  As before, the diagrams are implicitly
-  antisymmetrized (Hugenholtz diagrams).  Lines connected to $\hat{T}$
-  are always directed upward because they represent an excitation
-  operator while the directions of external lines connected to
-  $\hat{H}^{[2]}$ are unconstrained.}  \label{fig:diagrams-ccsd}
+  \includegraphics{fig-diagrams-ccsd.pdf}
+  \caption{Diagrammatic representation of $\bar{H}$ of Eq.~\eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
+Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}^{[2]}$ are unconstrained.}
+  \label{fig:diagrams-ccsd}
 \end{figure}
 
-The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b,
-i, j}^{[2]}$, are calculated by left-multiplying
-Eq.~\eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat
-a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat
-a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat
-a_{a}} \E^{-\hat{T}}$, respectively,
+The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying Eq.~\eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively,
 \begin{align} \label{eq:ccsd1}
@@
 \end{align}
-After the Fock matrix has been diagonalized, the diagonal components
-of Eq.~\eqref{eq:ccsd1} can be separated and, after expanding the
-exponent in Eq.~\eqref{eq:cc_heff1}, the non-vanishing terms of the
-CCSD amplitude equations become,
+After the Fock matrix has been diagonalized, the diagonal components of Eq.~\eqref{eq:ccsd1} can be separated and, after expanding the exponent in Eq.~\eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
 \begin{gather} \label{eq:ccsd2}
@@
   \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \hat{H}^{[2]} (1 + \hat{T}_{1} + \hat{T}_{2} + \frac{1}{2} \hat{T}_{1}^{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{2}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} + \frac{1}{2}\hat{T}_{1}^{2}\hat{T}_{2} + \frac{1}{4!}\hat{T}_{1}^{4} )_{c} \ket{\Phi} \notag \\
-= \Delta_{\{ij\}, \{ab\}} t_{abij}^{[2]} \notag
+= \Delta_{\{i j\}, \{a b\}} t_{a b i j}^{[2]} \notag
 \end{gather}
-where $\Delta$ are the M\o ller--Plesset denominators from
-Eq.~\eqref{eq:moellerplessetdenominator}.  As usual, these non-linear
-equations are solved using an iterative procedure.  One begins with an
-initial guess for the cluster amplitudes, which are used to calculate
-the left-hand side of Eq.~\eqref{eq:ccsd2}.  Dividing by the
-denominator on the right-hand side gives updated amplitudes which are
-used to re-evaluate the left-hand side. This process is repeated until
-the amplitudes reach a fixed point.  Like the Hartree--Fock iterative
-procedure, employing convergence acceleration techniques can reduce
-the number of coupled cluster iterations required.
+where $\Delta$ are the M\o ller--Plesset denominators from Eq.~\eqref{eq:moellerplessetdenominator}.
+As usual, these non-linear equations are solved using an iterative procedure.
+One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of Eq.~\eqref{eq:ccsd2}.
+Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side.
+This process is repeated until the amplitudes reach a fixed point.
+Like the Hartree--Fock iterative procedure, employing convergence acceleration techniques can reduce the number of coupled cluster iterations required.
 
@@
 
-The in-medium SRG, in the approach described, provides a means to
-calculate the ground state energy of any system that is reasonably
-approximated by a single Slater determinant.  This works well for
-closed-shell systems, but it does not provide a direct means to obtain
-the ground state energy of open-shell systems.  While there exist more
-complicated multi-reference approaches to IM-SRG that can tackle the
-general problem \cite{Hergert2016165}, we opted to use a perturbative
-approach, which is simple, inexpensive, and as we shall see in the
-results, quite effective for many problems.
-
-Quasidegenerate perturbation theory (QDPT) is an extension to the
-traditional perturbation theory framework that incorporates multiple
-reference states.  It provides us with a simple means to extract
-ground state energies of open-shell systems that are only a few
-particles away from a closed-shell system.  In particular, it allows
-us to calculate \textit{addition energies} $\varepsilon_a$
-and \textit{removal energies} $\varepsilon_i$ of such systems, which
-we define as:
+The in-medium SRG, in the approach described, provides a means to calculate the ground state energy of any system that is reasonably approximated by a single Slater determinant.
+This works well for closed-shell systems, but it does not provide a direct means to obtain the ground state energy of open-shell systems.
+While there exist more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use a perturbative approach, which is simple, inexpensive, and as we shall see in the results, quite effective for many problems.
+
+Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.
+It provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.
+In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
 \begin{align}
@@
 \end{align}
-where the meaning of $\Phi_p$ is defined in Eq.~\eqref{eq:quasisd},
-$i$ is restricted to labels of occupied states, and $a$ is restricted
-to labels of unoccupied states.
-
-In QDPT, solutions of an approximate one-body Hamiltonian
-$\hat{H}^{[1]}$ form the basis of the model space.  One begins by
-assuming the existence of an operator $\hat{\Omega}$, known as
-the \textit{wave operator}, that maps some set of states
-$\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact
-ground state $\Psi_u$:
+where the meaning of $\Phi_p$ is defined in Eq.~\eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
+
+In QDPT, solutions of an approximate one-body Hamiltonian $\hat{H}^{[1]}$ form the basis of the model space.
+One begins by assuming the existence of an operator $\hat{\Omega}$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
 \begin{align} \label{eq:omega-condition1}
@@
 \end{align}
-The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the
-eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian
-$\hat{H}^{[1]}$.
+The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
 
@@
 \end{align}
-where $\hat P$ projects any state into the model space and $\hat Q$ is
-the complement of $\hat P$.  This entails that the exact states
-$\Psi_u$ is no longer normalized but instead satisfies the so-called
-intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
-
-Making use of the assumptions in Eq.~\eqref{eq:omega-condition1} and
-Eq.~\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger
-equation the generalized Bloch equation, the principal equation of
-QDPT:
+where $\hat P$ projects any state into the model space and $\hat Q$ is the complement of $\hat P$.
+This entails that the exact states $\Psi_u$ is no longer normalized but instead satisfies the so-called intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
+
+Making use of the assumptions in Eq.~\eqref{eq:omega-condition1} and Eq.~\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
 \begin{gather*}
@@
 \end{gather*}
-where $\hat V \equiv \hat H - \hat{H}^{[1]}$ is the perturbation.  The
-commutator on the left may be ``inverted'' using the resolvent approach
-(\cite{shavitt2009many}, p.\ 50), resulting in:
+where $\hat V \equiv \hat H - \hat{H}^{[1]}$ is the perturbation.  The commutator on the left may be ``inverted'' using the resolvent approach (\cite{shavitt2009many}, p.\ 50), resulting in:
 \begin{align*}
@@
 \end{align*}
-where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat
-Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection
-operator that projects any state onto $\Psi^{\mathrm{o}}_u$.  As is
-standard in perturbation theory, we now assume $\hat \Omega$ can be
-expanded as a series of terms of increasing order, as quantified by
-the power of the perturbation $\hat V$:
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
+As is standard in perturbation theory, we now assume $\hat \Omega$ can be expanded as a series of terms of increasing order, as quantified by the power of the perturbation $\hat V$:
 \begin{align*}
@@
 \end{align*}
-This leads to a recursion relation of $\hat \Omega$ that enables
-$\hat \Omega$ to be calculated up to any order, at least in principle.
-Up to third order, we have:
+This leads to a recursion relation of $\hat \Omega$ that enables $\hat \Omega$ to be calculated up to any order, at least in principle.  Up to third order, we have:
 \begin{align*}
@@
 
-To make the equations more concrete, we further assume that each
-reference state $\ket{\Psi^{\mathrm{o}}_u} \equiv \ket{\Phi_u}$, i.e.\
-each reference state is simply a Slater determinant constructed by
-adding or removing a single particle $u$ to a closed-shell reference
-state $\Phi$, which itself may have been obtained earlier from HF
-and/or IM-SRG.  Thus, the number of reference states for QDPT is equal
-to the number of particles in either the lowest unfilled shell or the
-highest filled shell of $\ket{\Phi}$, depending on whether we are
-considering addition or removal energies.
-
-We can then express the perturbation expansion in terms of summations
-over matrix elements as we did for the IM-SRG flow
-equation, again with the aid of Wick's theorem or diagrammatic
-techniques.  This leads to the following expression for the
-second-order correction:
+To make the equations more concrete, we further assume that each reference state $\ket{\Psi^{\mathrm{o}}_u} \equiv \ket{\Phi_u}$, i.e.\ each reference state is simply a Slater determinant constructed by adding or removing a single particle $u$ to a closed-shell reference state $\Phi$, which itself may have been obtained earlier from HF and/or IM-SRG.
+Thus, the number of reference states for QDPT is equal to the number of particles in either the lowest unfilled shell or the highest filled shell of $\ket{\Phi}$, depending on whether we are considering addition or removal energies.
+
+We can then express the perturbation expansion in terms of summations over matrix elements as we did for the IM-SRG flow equation, again with the aid of Wick's theorem or diagrammatic techniques.
+This leads to the following expression for the second-order correction:
 \begin{align*}
@@
   &=
-    \sum_{iab} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{piab}|^2}{2 \Delta_{\{pi\}, \{ab\}}}
-    - \sum_{ija} \frac{n_i n_j \bar{n}_a |H^{[2]}_{ijpa}|^2}{2 \Delta_{\{ij\}, \{pa\}}},
-\end{align*}
-where the M\o ller--Plesset denominators $\Delta$ are defined in
-Eq.~\eqref{eq:moellerplessetdenominator}.  The above expression is
-depicted in Figure \ref{fig:diagrams-sfe}.  Since there are numerous
-terms in the third-order correction $\varepsilon_p^{(3)}$, they are
-listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.  We will
-refer to QDPT to third order as ``QDPT3''.
-
-Taking into account the perturbation corrections, one can extract
-reasonably accurate addition and removal energies for single-particle
-states near the Fermi level via:
+    \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{2 \Delta_{\{p i\}, \{a b\}}}
+    - \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{2 \Delta_{\{i j\}, \{p a\}}},
+\end{align*}
+where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.~\eqref{eq:moellerplessetdenominator}.
+The above expression is depicted in Figure \ref{fig:diagrams-sfe}.
+Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.
+We will refer to QDPT to third order as ``QDPT3''.
+
+Taking into account the perturbation corrections, one can extract reasonably accurate addition and removal energies for single-particle states near the Fermi level via:
 \begin{align*}
@@
 
-There is some degree of synergy between IM-SRG and QDPT: a generator
-that decouples the ground state energy will necessarily drive certain
-classes of matrix elements to zero.  This means certain kinds of
-vertices in the diagrams become forbidden, reducing the number of
-nonzero diagrams at third order from 18 to only four.
+There is some degree of synergy between IM-SRG and QDPT: a generator that decouples the ground state energy will necessarily drive certain classes of matrix elements to zero.
+This means certain kinds of vertices in the diagrams become forbidden, reducing the number of nonzero diagrams at third order from 18 to only four.
 
@@
 
-Particle attached and particle removed equations of motion (EOM)
-methods can be coupled with either IM-SRG or coupled cluster
-calculations. The principal idea is that one may construct a ladder
-operator $\hat{X}$ that promotes the $N$-particle ground state to any
-state in the $N + 1$ or $N - 1$ spectrum,
+Particle attached and particle removed equations of motion (EOM) methods can be coupled with either IM-SRG or coupled cluster calculations.
+The principal idea is that one may construct a ladder operator $\hat{X}$ that promotes the $N$-particle ground state to any state in the $N + 1$ or $N - 1$ spectrum,
 \begin{equation}\label{eq:ladder_def}
@@
 \end{equation}
-where $\hat{X}$ is in principle a linear combination of excitation and
-de-excitation operators that change particle number by one,
+where $\hat{X}$ is in principle a linear combination of excitation and de-excitation operators that change particle number by one,
 \begin{align}
   \label{eq:gen_attached}
-  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{pqr} \bar{n}_p \bar{n}_q n_r x^{[2,1]}_{pqr} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
+  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r x^{[2,1]}_{p q r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{pqr} n_p n_q \bar{n}_r  x^{[1,2]}_{pqr} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
+  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  x^{[1,2]}_{p q r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
 \end{align}
@@
 \end{equation}
-which constitutes a generalized eigenvalue problem for the amplitudes
-$x$, where $\varepsilon^{(\pm)}_u$ are the single-particle addition
-($+$) and removal ($-$) energies. The quality of this calculation
-depends on the ansatz for the $N$-particle ground state, as well as
-the systematically improvable truncation on the ladder operators. In
-this work we include 1p and 2p1h excitations in the $N + 1$ ladder
-operator and likewise 1h and 2h1p operators for the $N - 1$ ladder
-operators.
+which constitutes a generalized eigenvalue problem for the amplitudes $x$, where $\varepsilon^{(\pm)}_u$ are the single-particle addition ($+$) and removal ($-$) energies.
+The quality of this calculation depends on the ansatz for the $N$-particle ground state, as well as the systematically improvable truncation on the ladder operators.
+In this work we include 1p and 2p1h excitations in the $N + 1$ ladder operator and likewise 1h and 2h1p operators for the $N - 1$ ladder operators.
 
@@
 
-After a single-reference ground state IM-SRG calculation, the
-Hamiltonian has been rotated such that the reference state is an
-eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the
-correlated $N$-particle ground state energy. The EOM equation is
-therefore
+After a single-reference ground state IM-SRG calculation, the Hamiltonian has been rotated such that the reference state is an eigenfunction with corresponding eigenvalue $E^{(N)}_0$, which is the correlated $N$-particle ground state energy.
+The EOM equation is therefore
 \begin{align} \label{eq:EOMIMSRG}
@@
 \end{align}
-where bars denote rotated operators. Now the reference state is used
-in place of the bare correlated ground state. The ground state IM-SRG
-procedure has implicitly re-summed contributions from higher order
-excitations (3-particle-2-hole, 2-particle-3-hole, 2-particle-3-hole,
-4-particle-3-hole, \ldots) into the lower order amplitudes of the
-ladder operators (1-particle-0-hole, 0-particle-1-hole,
-2-particle-1-hole, 1-particle-2-hole).
-
-Despite these gains, the EOM calculation is still a partial
-diagonalization method, limited by the truncation to 2-particle-1-hole
-and 1-particle-2-hole operators. We expect $N + 1$ (or $N - 1$) states
-to be described appropriately by EOM-IM-SRG if their wavefunctions are
-dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in
-the rotated frame. We use partial norms of the EOM ladder operators to
-make this determination:
+where bars denote rotated operators.
+Now the reference state is used in place of the bare correlated ground state.
+The ground state IM-SRG procedure has implicitly re-summed contributions from higher order excitations (3-particle-2-hole, 2-particle-3-hole, 2-particle-3-hole, 4-particle-3-hole, \ldots) into the lower order amplitudes of the ladder operators (1-particle-0-hole, 0-particle-1-hole, 2-particle-1-hole, 1-particle-2-hole).
+
+Despite these gains, the EOM calculation is still a partial diagonalization method, limited by the truncation to 2-particle-1-hole and 1-particle-2-hole operators.
+We expect $N + 1$ (or $N - 1$) states to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in the rotated frame.
+We use partial norms of the EOM ladder operators to make this determination:
 \begin{align}
@@
 \end{align}
-Large single particle partial norms indicate that the EOM truncation
-is valid for the relevant state. States with lower single particle
-norms should be treated with a higher EOM approximation, which can
-be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
+Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
+States with lower single particle norms should be treated with a higher EOM approximation, which can be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
 
@@
 
-Like EOM-IM-SRG, the equation-of-motion technique can be applied after
-a coupled-cluster ground-state calculation, by using the
-coupled-cluster effective Hamiltonian.  Here, the non-Hermitian nature
-of $\bar{H}_{\mathrm{CC}}$ becomes apparent.  In this case, in
-addition to constructing excitation ladder operators
-Eq.~\eqref{eq:gen_attached} and Eq.~\eqref{eq:gen_removed} that
-correspond to the right-eigenvectors of the generalized eigenvalue
-problem Eq.~\eqref{eq:EOMIMSRG}, there exist analogous de-excitation
-ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that
-correspond to the left-eigenvectors,
+Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
+Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
+In this case, in addition to constructing excitation ladder operators Eq.~\eqref{eq:gen_attached} and Eq.~\eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem Eq.~\eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
 \begin{align*}
@@
 \end{align*}
-These left-eigenvectors satisfy the left-eigenvalue problem, with
-left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to
-Eq.~\eqref{eq:EOMIMSRG},
+These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to Eq.~\eqref{eq:EOMIMSRG},
 \begin{align*}
@@
 
-In this paper, because the interaction is real and thus the effective
-Hamiltonian is real, the left- and right-eigenvalues are
-equivalent. In addition, while the the left- and right-eigenvectors
-are generally not equal, the differences in their single-particle
-Eq.~\eqref{eq:partial_norms_p} or single-hole
-Eq.~\eqref{eq:partial_norms_h} natures are, in practice, not
-significant.  Therefore, only the right-eigenvectors are used in this
-paper.
+In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
+In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle Eq.~\eqref{eq:partial_norms_p} or single-hole Eq.~\eqref{eq:partial_norms_h} natures are, in practice, not significant.
+Therefore, only the right-eigenvectors are used in this paper.
 
@@
   \includegraphics{figures/fig-methods.pdf}
-  \caption{A schematic view of the various ways in which many-body methods in
-  this paper could be combined to calculate ground state, addition,
-  and removal energies.}  \label{fig:methods}
+  \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
+  \label{fig:methods}
 \end{figure}
 
-There is great amount of flexibility in the application of many-body
-methods.  The approaches we use is shown in
-Fig.~\ref{fig:methods}.  Such an ordering maximizes the benefits of
-each method: Hartree--Fock acts as an initial, crude procedure to
-``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the
-ground state energy, and then finally QDPT or EOM to refine the
-addition and removal energies.
-
-The general process begins with the input matrix elements
-Eq.~\eqref{eq:interactionintegral}, computed exactly using
-the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
-Internally, \texttt{OpenFCI} calculates the interaction integrals in
-the center-of-mass frame using Gauss--Hermite quadrature and
-transforms them back into the laboratory frame to produce matrix
-elements suitable for use in our many-body methods.
-
-Afterward, there are several paths through which one can traverse
-Figure \ref{fig:methods} to obtain output observables.  We shall
-primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3,
-(b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
-
-It is possible to omit some steps of the process.  For example, one
-can omit HF, but continue with the remaining two steps.  While this is
-doable, from our experience Hartree--Fock significantly improves the
-results of the later post-HF methods at very low cost compared to the
-post-HF methods.  Therefore, in practice there is little reason to
-omit HF.  We will however investigate the effects of removing one or
-more of the post-HF methods.
-
-Since every calculation in this paper begins with the Hartree--Fock
-stage, we will not explicitly state ``HF'' unless there is no post-HF
-method used at all, in which case we write ``HF only''.
-
-All calculations of ground state energy $E_N$ in this paper are
-restricted to cases where the number of particles $N$ is a magic
-number, i.e.\ a \textit{closed shell} system (see
-Figure \ref{fig:shell-structure} for an illustration of the shell
-structure).  This is a limitation of the many-body methods used in
-this paper and while there are ways to overcome this limit they are
-beyond the scope of this paper (see Section \ref{sec:conclusions} for
-some ideas).  Addition/removal energies $\varepsilon^{(\pm)}$ are
-similarly restricted in that we only calculate the energy difference
-between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same
-system but with one particle added/removed:
+There is great amount of flexibility in the application of many-body methods.
+The approaches we use is shown in Fig.~\ref{fig:methods}.
+Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+
+The general process begins with the input matrix elements Eq.~\eqref{eq:interactionintegral}, computed exactly using the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
+Internally, \texttt{OpenFCI} calculates the interaction integrals in the center-of-mass frame using Gauss--Hermite quadrature and transforms them back into the laboratory frame to produce matrix elements suitable for use in our many-body methods.
+
+Afterward, there are several paths through which one can traverse Figure \ref{fig:methods} to obtain output observables.
+We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
+
+It is possible to omit some steps of the process.
+For example, one can omit HF, but continue with the remaining two steps.
+While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
+Therefore, in practice there is little reason to omit HF.
+We will however investigate the effects of removing one or more of the post-HF methods.
+
+Since every calculation in this paper begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
+
+All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
+This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
+Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
 \begin{align*}
@@
 
-Ideally, ground state energies should be characterized entirely by the
-two system parameters $(N, \omega)$, where $N$ is number of particles
-and $\omega$ is the oscillator frequency.  However, the methods that
-we study are limited to a \emph{finite} (truncated) basis and
-the results depend on the level of truncation.
-This is characterized by $K$, the total number of shells in the
-single-particle basis.  Thus, results are generally presented as a
-graph plotted against $K$.  In Section \ref{subsec:extrapolation}
-we discuss how to estimate results as $K \to \infty$ (infinite-basis
-limit) through \textit{extrapolations}.
-
-The addition and removal energies are similar, but they require an
-additional parameter: the total orbital angular momentum $M_\ell$,
-defined as the sum of the $m_\ell$ of each particle.  This is due to
-the presence of multiple states with near-degenerate energies.  For
-this paper, we will consider exclusively the addition/removal energies
-with the lowest $|M_\ell|$ subject to the constraint that the particle
-added/removed lies within the next/last shell.  This means the $N + 1$
-states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for modulus division)
-where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N
-- 1$ states of interest are those with $|M_\ell| = 1 -
-(K_{\mathrm{F}} \bmod 2)$.
-
-Not all cases are solvable with our selection many-body methods.  Low
-frequency systems are particularly strenuous for these many-body
-methods due to their strong correlations, leading to equations that
-are difficult and expensive to solve numerically.  Cases where IM-SRG
-converged too slowly to be feasible or diverged are marked
-``n.c.(I)''.  For the extrapolations in
-Section \ref{subsec:extrapolation}, some fits could not be done due to
-missing data caused by lack of convergence for either the IM-SRG(2) calculations or the CCSD calculations.
-
-Numerical calculations in this paper are performed with a relative
-precision of about $10^{-5}$ or lower.  This does not necessarily mean
-the results are as precise as $10^{-5}$, since numerical errors tend
-to accumulate over the multiple steps of the calculation, thus the
-precision of the final results is expected to be roughly $10^{-4}$.
+Ideally, ground state energies should be characterized entirely by the two system parameters $(N, \omega)$, where $N$ is number of particles and $\omega$ is the oscillator frequency.
+However, the methods that we study are limited to a \emph{finite} (truncated) basis and the results depend on the level of truncation.
+This is characterized by $K$, the total number of shells in the single-particle basis.
+Thus, results are generally presented as a graph plotted against $K$.
+In Section \ref{subsec:extrapolation} we discuss how to estimate results as $K \to \infty$ (infinite-basis limit) through \textit{extrapolations}.
+
+The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
+This is due to the presence of multiple states with near-degenerate energies.
+For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
+This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for modulus division) where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+
+Not all cases are solvable with our selection many-body methods.
+Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
+Cases where IM-SRG converged too slowly to be feasible or diverged are marked ``n.c.(I)''.
+For the extrapolations in Section \ref{subsec:extrapolation}, some fits could not be done due to missing data caused by lack of convergence for either the IM-SRG(2) calculations or the CCSD calculations.
+
+Numerical calculations in this paper are performed with a relative precision of about $10^{-5}$ or lower.
+This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate over the multiple steps of the calculation, thus the precision of the final results is expected to be roughly $10^{-4}$.
 
@@
 
-In Fig.~\ref{fig:gs} we display a selection of ground state energies
-calculated using HF + IM-SRG(2) and HF + CCSD as described in
-Section \ref{subsec:methodology}.  We also include results from M\o ller--Plesset perturbation theory to second order (MP2),
-DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for
-comparison where available.
-
-We do not include results from ``HF only'' to avoid overshadowing the
-comparatively smaller differences between the non-HF results in the
-plots.  Some HF results can be found in 
-Fig.~\ref{fig:by-freq-10-6-normal} instead.  Generally, the HF ground
-state energies differ from the non-HF ones by a few to several
-percent, whereas non-HF energies tend to differ from each other by
-less than a percent.
-
-With respect to the number of shells, both IM-SRG(2) and CCSD appear
-to converge slightly faster than second order perturbation theory
-(MP2), mainly due to the presence of higher order corrections in
-IM-SRG(2) and CCSD.
-
-There are a few cases where the IM-SRG over-corrects the result,
-leading to an energy lower than the quasi-exact DMC results.  This is
-not unexpected given that, unlike the Hartree--Fock results, the IM-SRG method is
-non-variational in the presence of operator truncations, which in turn results in 
-small unitarity violations.  This over-correction tends to occur when
-the frequency is low (high correlation), or when \emph{few} particles are involved.
+In Fig.~\ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
+We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.
+
+We do not include results from ``HF only'' to avoid overshadowing the comparatively smaller differences between the non-HF results in the plots.
+Some HF results can be found in Fig.~\ref{fig:by-freq-10-6-normal} instead.
+Generally, the HF ground state energies differ from the non-HF ones by a few to several percent, whereas non-HF energies tend to differ from each other by less than a percent.
+
+With respect to the number of shells, both IM-SRG(2) and CCSD appear to converge slightly faster than second order perturbation theory (MP2), mainly due to the presence of higher order corrections in IM-SRG(2) and CCSD.
+
+There are a few cases where the IM-SRG over-corrects the result, leading to an energy lower than the quasi-exact DMC results.
+This is not unexpected given that, unlike the Hartree--Fock results, the IM-SRG method is non-variational in the presence of operator truncations, which in turn results in small unitarity violations.
+This over-correction tends to occur when the frequency is low (high correlation), or when \emph{few} particles are involved.
 
@@
 
-The results of our addition and removal energy calculations are
-summarized in Fig.~\ref{fig:add} and Fig.~\ref{fig:rm}
-respectively.  The figures show the the addition/removal energies for
-using the approaches mentioned in Section \ref{subsec:methodology}.
-Where available, results from diffusion Monte Carlo
-(DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
-
-As before, we do not include results from ``HF only'' in these plots
-as they are significantly further from the rest.  Analogously, we also
-exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure
-CCSD, as QDPT or EOM both add significant contributions to addition
-and removal energies.  Some HF only and pure IM-SRG results can be
-seen in Fig.~\ref{fig:by-freq-10-6-normal}.
-
-There is strong agreement between IM-SRG(2) + QDPT3 and IM-SRG(2) +
-EOM2 in many cases, and slightly weaker agreement between the IM-SRG
-and CCSD families.  This suggests that the EOM2 corrections are
-largely accounted for by the inexpensive QDPT3 method.  However, in
-some cases, most notably with few particles and high correlations (low
-frequency), the IM-SRG(2) + QDPT3 result differs significantly from
-both IM-SRG(2) + EOM2 and CCSD + EOM2.
+The results of our addition and removal energy calculations are summarized in Fig.~\ref{fig:add} and Fig.~\ref{fig:rm} respectively.
+The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
+Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
+
+As before, we do not include results from ``HF only'' in these plots as they are significantly further from the rest.
+Analogously, we also exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure CCSD, as QDPT or EOM both add significant contributions to addition and removal energies.
+Some HF only and pure IM-SRG results can be seen in Fig.~\ref{fig:by-freq-10-6-normal}.
+
+There is strong agreement between IM-SRG(2) + QDPT3 and IM-SRG(2) + EOM2 in many cases, and slightly weaker agreement between the IM-SRG and CCSD families.
+This suggests that the EOM2 corrections are largely accounted for by the inexpensive QDPT3 method.
+However, in some cases, most notably with few particles and high correlations (low frequency), the IM-SRG(2) + QDPT3 result differs significantly from both IM-SRG(2) + EOM2 and CCSD + EOM2.
 
@@
 \begin{figure}
-  \centering \includegraphics{fig-by-freq-10-6-normal.pdf} \caption{The
-  behavior of ground state, addition, and removal energies as a
-  function of the oscillator frequency $\omega$, with $K = 10$ shells
-  in the basis.  The energy is normalized with respect to the
-  Hartree--Fock values to magnify the differences.  Lower frequency
-  leads to stronger correlations and thereby a more difficult problem.}
+  \centering
+  \includegraphics{fig-by-freq-10-6-normal.pdf}
+  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
+The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
+Lower frequency leads to stronger correlations and thereby a more difficult problem.}
   \label{fig:by-freq-10-6-normal}
@@
 \begin{figure}
-  \centering \includegraphics{fig-rel-slopes2.pdf} \caption{The impact
-  of the interaction on convergence of addition and removal energies
-  using IM-SRG(2) + QDPT3.  For clarity, the plot does not distinguish
-  between addition and removal energies.  The horizontal axis shows
-  the system parameters, where $N$ is the number of particles and
-  $\omega$ is the oscillator frequency.  The vertical axis shows
-  $|\rho_{15}|$ (``relative slope''), which estimates the rate of
-  convergence at 15 total shells.  The lower the value of
-  $|\rho_{15}|$, the faster the convergence.  The data points are
-  categorized by the interactions.  The trends suggest that the
-  singular short-range part of the interaction has a much stronger
-  impact on the convergence than the long-range
-  tail.}  \label{fig:rel-slopes}
+  \centering
+  \includegraphics{fig-rel-slopes2.pdf}
+  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
+For clarity, the plot does not distinguish between addition and removal energies.
+The horizontal axis shows the system parameters, where $N$ is the number of particles and $\omega$ is the oscillator frequency.
+The vertical axis shows $|\rho_{15}|$ (``relative slope''), which estimates the rate of convergence at 15 total shells.
+The lower the value of $|\rho_{15}|$, the faster the convergence.
+The data points are categorized by the interactions.
+The trends suggest that the singular short-range part of the interaction has a much stronger impact on the convergence than the long-range tail.}
+  \label{fig:rel-slopes}
 \end{figure}
 
-To analyze the rate of convergence more quantitatively, we 
-define $\rho_K$ as the relative backward difference of the energy
-(\textit{relative slope}):
+To analyze the rate of convergence more quantitatively, we define $\rho_K$ as the relative backward difference of the energy (\textit{relative slope}):
 \begin{align*}
@@
 \end{align*}
-The denominator allows the quantity to be meaningfully compared
-between different systems.  We expect this quantity to become
-increasingly small as the calculations converge.
-
-In Fig.~\ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) +
-QDPT3.  The many-body methods were tested against a \emph{modified}
-Coulomb-like interaction, parametrized by two lengths
-$\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the
-range of the interaction:
+The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge.
+
+In Fig.~\ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) + QDPT3.
+The many-body methods were tested against a \emph{modified} Coulomb-like interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
 \begin{align}
@@
 where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.
-The coefficient is chosen to ensure the peak of the envelope remains
-at unity.  With $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}) =
-(0, \infty)$ one recovers the original Coulomb interaction.  By
-increasing $\sigma_{\mathrm{A}}$ one can truncate the short-range part
-of the interaction, and analogously by increasing
-$\sigma_{\mathrm{B}}$ one can truncate the long-range part of the
-interaction.  For our numerical experiments we considered the
-following four combinations of
-$(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$,
-$(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
-
-Reducing the short-range part of the interaction appears improves the rate
-of convergence substantially.  Many of the cases have reached the
-precision of the ODE solver ($10^{-5}$ to $10^{-6}$).  In contrast,
-eliminating the long-range part of the interaction had very little
-effect.  This suggests that the main cause of the slow convergence
-lies in the highly repulsive, short-ranged part of the interaction,
-which leads to the presence of nondifferentiable cusps (the
-so-called \textit{Coulomb cusps}) in the exact wave functions that are
-difficult to reproduce exactly using linear combinations of the smooth
-harmonic oscillator wave functions.
-
-The convergence is negatively impacted at lower frequencies and, to a
-lesser extent, by the increased number of particles.  Both are
-expected: lower frequencies increase the correlation in the system,
-while higher number of particles naturally require more shells to
-converge.
-
-In general, there does not appear to be any difference between the
-convergence behavior of addition energies as compared to that of
-removal energies.
+The coefficient is chosen to ensure the peak of the envelope remains at unity.
+With $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}) = (0, \infty)$ one recovers the original Coulomb interaction.
+By increasing $\sigma_{\mathrm{A}}$ one can truncate the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can truncate the long-range part of the interaction.
+For our numerical experiments we considered the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.
+
+Reducing the short-range part of the interaction appears improves the rate of convergence substantially.
+Many of the cases have reached the precision of the ODE solver ($10^{-5}$ to $10^{-6}$).
+In contrast, eliminating the long-range part of the interaction had very little effect.
+This suggests that the main cause of the slow convergence lies in the highly repulsive, short-ranged part of the interaction, which leads to the presence of nondifferentiable cusps (the so-called \textit{Coulomb cusps}) in the exact wave functions that are difficult to reproduce exactly using linear combinations of the smooth harmonic oscillator wave functions.
+
+The convergence is negatively impacted at lower frequencies and, to a lesser extent, by the increased number of particles.
+Both are expected: lower frequencies increase the correlation in the system, while higher number of particles naturally require more shells to converge.
+
+In general, there does not appear to be any difference between the convergence behavior of addition energies as compared to that of removal energies.
 
@@
 \begin{table}
-  \centering \caption{Extrapolated ground state energies for quantum
-  dots with fit uncertainties.  The uncertainties are computed from
-  the approximate Hessian constructed by Levenberg-Marquardt fitting
-  algorithm.  Extrapolations are done using 5-point fits where the
-  number of shells $K$ ranges between $K_{\text{stop}} - 4$ and
-  $K_{\text{stop}}$
-  (inclusive).}  \label{tab:ground-extrapolated} \input{tab-ground-extrapolated}
+  \centering
+  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
+The uncertainties are computed from the approximate Hessian constructed by Levenberg-Marquardt fitting algorithm.
+Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
+  \label{tab:ground-extrapolated}
+  \input{tab-ground-extrapolated}
 \end{table}
@@
 \begin{figure}
-  \centering \includegraphics{fig-fit-2-1p0-add.pdf} \caption{A
-  five-point fit of the addition energies of the $(N, \omega) = (6,
-  1.0)$ system with $K_{\text{stop}} = 15$.  The grey shaded region
-  contains the masked data points, which are ignored by the fitting
-  procedure.  The left figure plots the central difference of the
-  addition energies $\varepsilon^{(+)}$ with respect to the number of
-  shells $K$.  On such a plot, the power law model should appear as a
-  straight line.  The fits are optimized using the procedure described
-  in Section \ref{subsec:extrapolation}.  Note that the lines do not
-  evenly pass through the points in the left plot as the fitting
-  weights are tuned for the energy on a linear scale, not the energy
-  differences on a logarithmic scale.}  \label{fig:by-fit-2-1p0-add}
+  \centering
+  \includegraphics{fig-fit-2-1p0-add.pdf}
+  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.
+The grey shaded region contains the masked data points, which are ignored by the fitting procedure.
+The left figure plots the central difference of the addition energies $\varepsilon^{(+)}$ with respect to the number of shells $K$.
+On such a plot, the power law model should appear as a straight line.
+The fits are optimized using the procedure described in Section \ref{subsec:extrapolation}.
+Note that the lines do not evenly pass through the points in the left plot as the fitting weights are tuned for the energy on a linear scale, not the energy differences on a logarithmic scale.}
+  \label{fig:by-fit-2-1p0-add}
 \end{figure}
 
-As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the
-asymptotic convergence of the quantum dot observables in a finite
-harmonic oscillator basis can be approximately described by a power
-law model:
+As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
 \begin{align*}
@@
 \end{align*}
-where $\Delta E$ is the difference between the finite-basis result and
-the infinite-basis result, $K$ is the number of shells in the
-single-particle basis, and $\beta$ is some positive real exponent.
-The \textit{smoothness} of the exact wave function determines the rate
-of the convergence: the more times the exact wave function can be
-differentiated, the higher the exponent $\beta$.
-
-It is difficult to ascertain what $\beta$ is \textit{a priori}, thus
-we will empirically compute $\beta$ by fitting the following model
-through our data:
+where $\Delta E$ is the difference between the finite-basis result and the infinite-basis result, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.
+The \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
+
+It is difficult to ascertain what $\beta$ is \textit{a priori}, thus we will empirically compute $\beta$ by fitting the following model through our data:
 \begin{align} \label{eq:power_law_model}
@@
 \end{align}
-As a nonlinear curve fit, it can be quite sensitive to the initial
-parameters.  Therefore, good guesses of the parameters are necessary
-to obtain a sensible result.  For this, we first fit a linear model of
-$\log |\partial E / \partial K|$ against $\log K$:
+As a nonlinear curve fit, it can be quite sensitive to the initial parameters.
+Therefore, good guesses of the parameters are necessary to obtain a sensible result.
+For this, we first fit a linear model of $\log |\partial E / \partial K|$ against $\log K$:
 \begin{align*}
@@
 \end{align*}
-This is useful because linear fits are very robust and will often
-converge even if the initial parameters are far from their final values.  It
-also provides a means to visually assess the quality of the fit.  The
-derivative is approximated using the central difference:
+This is useful because linear fits are very robust and will often converge even if the initial parameters are far from their final values.
+It also provides a means to visually assess the quality of the fit.
+The derivative is approximated using the central difference:
 \begin{align*}
@@
 \end{align*}
-The process of calculating numerically the derivative can amplify the
-noise in the data and distorts the weights of the data points.
-Moreover, it does not provide a means to compute $\gamma$, the
-extrapolated energy.  Thus a second accurate nonlinear curve fit is
-necessary.
-
-The parameters $\alpha$ and $\beta$ are extracted from the linear fit
-and used as inputs for a power-law fit of $E$ against $K$.  It
-is necessary to estimate the infinite-basis energy $\gamma$ as well,
-which is done by fitting Eq.~\eqref{eq:power_law_model} while the
-parameters $\alpha$ and $\beta$ are fixed to the initial guesses.  The
-fixing ensures that the fit is still linear in nature and thus highly
-likely to converge.  Afterward, we do a final fit with all three
-parameters free to vary.  All fits are done using the traditional
-Levenberg--Marquardt (LM) optimization algorithm as implemented
-in \texttt{Minpack}, with equal weighting of all data points.  {\bf Ref to this}.
-
-There is still one additional tuning knob for this model that is not
-explicitly part of Eq.~\eqref{eq:power_law_model}: the range of data
-points taken into consideration (\textit{fit range}).  Since the model
-describes the \emph{asymptotic} behavior, we do not expect the fit to
-produce good results when the energy is still very far from
-convergence.  To account for this, we only fit the last few data
-points within some chosen range.  If the range is too large, then the
-non-asymptotic behavior would perturb the result too much, whereas if
-the range is too small, there would be more noise and less confidence
-in whether the trend is legitimate rather than accidental.
+The process of calculating numerically the derivative can amplify the noise in the data and distorts the weights of the data points.
+Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
+Thus a second accurate nonlinear curve fit is necessary.
+
+The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
+It is necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting Eq.~\eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
+The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
+Afterward, we do a final fit with all three parameters free to vary.
+All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm as implemented in \texttt{Minpack}, with equal weighting of all data points.
+{\bf Ref to this}.
+
+There is still one additional tuning knob for this model that is not explicitly part of Eq.~\eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
+Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
+To account for this, we only fit the last few data points within some chosen range.
+If the range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, there would be more noise and less confidence in whether the trend is legitimate rather than accidental.
 Empirically, we chose to fit the last 5 points of our available data.
-The results are shown in
-Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated},
-and \ref{tab:rm-extrapolated}.  A specific example of the fit is shown
-in Fig.~\ref{fig:by-fit-2-1p0-add}
-
-The LM fitting procedure also computes uncertainties for the
-parameters from an approximate Hessian of the model function.  It is
-therefore tempting to use the uncertainty of the fit to quantify the
-uncertainty of the extrapolated energy.  We certainly would not expect
-this to account for the error due to the operator truncation, but how
-accurately does it quantify the discrepancy of our extrapolated result
-from the true infinite-basis energy?
-
-We investigated this idea by performing a fit over \emph{all possible}
-5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.  By
-comparing the extrapolated results at varying values of
-$K_{\text{stop}}$ with the extrapolated result at the highest possible
-$K_{\text{stop}}$ and treating the latter as the ``true''
-infinite-basis result, we can statistically assess whether the fit
-uncertainties are a good measure of the discrepancy from the true
-infinite-basis result.  Our results show a somewhat bimodal
-distribution: when the relative fit uncertainty is higher than
-$10^{-3.5}$, the fit uncertainty quantifies the discrepancy well;
-otherwise, the fit uncertainty underestimates the discrepancy by a
-factor of 10 or less.
-
-Unlike the other methods, Hartree--Fock energies are somewhat unusual
-in that they generally do not conform to the power-law model.  In
-fact, the results and plots seem to indicate an \emph{exponential}
-convergence with respect to the number of shells.  It is likely that
-HF is insensitive to the Coulomb cusp.
-
-Nonetheless, despite the poor fits that often arise, the extrapolated
-energies are often quite good for HF.  This is likely due to its rapid
-convergence, which leaves very little degree of freedom even for a
-poorly chosen model.  Moreover, we found that the fit uncertainties of
-the energy are fairly good measures of the true discrepancy.
-
-Not all fits yield a positive value of $\beta$ for addition and
-removal energies, which suggests that the data points do not converge,
-or require a very high number of shells to converge.  These cases are
-marked ``n.f.'' in the tables.  This affects exclusively IM-SRG(2) +
-QDPT3 for systems with few particles and low frequencies, indicating
-that perturbation theory is inadequate for such systems.
+The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
+A specific example of the fit is shown in Fig.~\ref{fig:by-fit-2-1p0-add}
+
+The LM fitting procedure also computes uncertainties for the parameters from an approximate Hessian of the model function.
+It is therefore tempting to use the uncertainty of the fit to quantify the uncertainty of the extrapolated energy.
+We certainly would not expect this to account for the error due to the operator truncation, but how accurately does it quantify the discrepancy of our extrapolated result from the true infinite-basis energy?
+
+We investigated this idea by performing a fit over \emph{all possible} 5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.
+By comparing the extrapolated results at varying values of $K_{\text{stop}}$ with the extrapolated result at the highest possible $K_{\text{stop}}$ and treating the latter as the ``true'' infinite-basis result, we can statistically assess whether the fit uncertainties are a good measure of the discrepancy from the true infinite-basis result.
+Our results show a somewhat bimodal distribution: when the relative fit uncertainty is higher than $10^{-3.5}$, the fit uncertainty quantifies the discrepancy well; otherwise, the fit uncertainty underestimates the discrepancy by a factor of 10 or less.
+
+Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
+In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
+It is likely that HF is insensitive to the Coulomb cusp.
+
+Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
+This is likely due to its rapid convergence, which leaves very little degree of freedom even for a poorly chosen model.
+Moreover, we found that the fit uncertainties of the energy are fairly good measures of the true discrepancy.
+
+Not all fits yield a positive value of $\beta$ for addition and removal energies, which suggests that the data points do not converge, or require a very high number of shells to converge.
+These cases are marked ``n.f.'' in the tables.
+This affects exclusively IM-SRG(2) + QDPT3 for systems with few particles and low frequencies, indicating that perturbation theory is inadequate for such systems.
 
@@
 
-We have demonstrated calculations of ground state, addition, and
-removal energies of two-dimensional circular quantum dots using a
-variety of many-body methods: ranging from the basic Hartree-Fock
-method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or
-EOM.  Many closed-shell quantum dot systems have been explored,
-ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
+We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
+Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
 All such results show good agreement with one another.
 
-We note that the HF + IM-SRG + QDPT combination provides a reasonable
-moderate-cost approach to the calculation of addition and removal
-energies for many systems in comparison to the somewhat more expensive
-and complicated EOM calculations.  Both IM-SRG and CC are reasonably
-accurate compared to the near-exact but factorial-cost FCI method,
-allowing exploration of much higher number of particles than would
-otherwise be possible.  EOM-IM-SRG does have more flexibility over
-perturbative approaches: in particular, it could be more readily used
-to construct excited states \cite{2016arXiv161100661P}, which is more
-difficult for methods such as DMC.
-
-There are several directions in which the calculations may be
-improved.  One can attempt to improve the IM-SRG approximation by
-incorporating some of the missing higher-body terms in the commutator.
-This would also provide some insight into the rate of convergence with
-respect to the operator truncation, providing a sense of how large the
-truncation error is.  While a full 3-body treatment of IM-SRG would be
-extremely costly, it is possible implicitly track for a portion of the
-induced 3-body forces by computing certain diagrams that are either
-lower cost or could be approximated at lower cost \cite{IMSRG}.
-
-The application of IM-SRG eliminates a large number of the QDPT
-diagrams of Fig.~\ref{fig:diagrams-sfe}, which is beneficial as it increases
-the efficiency of the QDPT calculations.  Thus it may be more feasible
-to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
-Moreover, the remaining diagrams at third order can be eliminated
-through infinite resummation techniques, which would incorporate
-higher order terms and therefore further increase the accuracy of the
-result.
-
-We note that this calculation was done entirely using the traditional
-approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by T. D. Morris \cite{PhysRevC.92.034331}
-uses an alternative approach that obviates the need for a high-order
-ODE solver, leading to much more efficient computations and also
-allowing operators of other observables to be evolved at lower cost,
-which poses a significant advantage over coupled cluster methods.
-Implementing this approach would allows us to study the accuracy and
-convergence of other possibly more sensitive observables.
-
-The IM-SRG method can be extended to support multiple reference states
-(multi-reference IM-SRG or simply
-MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through
-the generalized normal ordering
-formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of
-calculating quantum systems that are far from the magic numbers
-(open-shell systems).  This is a territory that few many-body methods
-can tackle and is one of the major strengths of the IM-SRG approach.
-
-By transforming of the operator-SRG rather than the wave function,
-IM-SRG is more amenable to the construction of
-softened \textit{effective interactions} than
-CC \cite{Hergert2016165}.  Such interactions can be used to lower the
-cost of other methods such as full configuration interaction theory.
-
-Implementation-wise, our current code constructs the two-particle
-states as simple Slater determinants of their one-particle states.
-This approach is often referred to as \textit{m-scheme} in nuclear
-physics.  It is straightforward to implement and works well for
-general systems, but it fails to exploit all the symmetries in the
-quantum dot system: not only is spin projection $\hat S_z$ conserved,
-the Casimir operator $\hat S^2$ is as well.  A more efficient approach
-is to couple the spins of the single-particle states to form
-two-particle states with good $\hat S^2$, an approach analogous
-to \textit{j-scheme} in nuclear physics.  A combination of this with
-the Eckart-Wigner theorem could reduce the computational cost
-significantly, albeit at the cost of increased implementation
-complexity.
-
-We hope to apply these theoretical and technical enhancements not only
-to the study of quantum dots, but to studies of nuclear and atomic
-systems, opening up an even greater range of applications.
+We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.
+Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
+EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
+
+There are several directions in which the calculations may be improved.
+One can attempt to improve the IM-SRG approximation by incorporating some of the missing higher-body terms in the commutator.
+This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
+While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
+
+The application of IM-SRG eliminates a large number of the QDPT diagrams of Fig.~\ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
+Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
+Moreover, the remaining diagrams at third order can be eliminated through infinite resummation techniques, which would incorporate higher order terms and therefore further increase the accuracy of the result.
+
+We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
+A new technique developed by T.
+D.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
+Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
+
+The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).
+This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.
+
+By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.
+Such interactions can be used to lower the cost of other methods such as full configuration interaction theory.
+
+Implementation-wise, our current code constructs the two-particle states as simple Slater determinants of their one-particle states.
+This approach is often referred to as \textit{m-scheme} in nuclear physics.
+It is straightforward to implement and works well for general systems, but it fails to exploit all the symmetries in the quantum dot system: not only is spin projection $\hat S_z$ conserved, the Casimir operator $\hat S^2$ is as well.
+A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
+A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
+
+We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
 
 \begin{acknowledgments}
-  This work was supported by the National Science Foundation Grant
-  No.\ PHY-1404159 (Michigan State University).
+  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University).
 \end{acknowledgments}

### 2017-06-13 Manuscript/paper.tex
Replace ~ with \<space>

@@
 
-In this work we will mainly work with the formalism of second quantization, see for example Ref.~\cite{shavitt2009many}.
+In this work we will mainly work with the formalism of second quantization, see for example Ref.\ \cite{shavitt2009many}.
 To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
@@
 
-In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from Eq.~\eqref{eq:onetwobodyhamiltonian} can be rewritten as
+In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from Eq.\ \eqref{eq:onetwobodyhamiltonian} can be rewritten as
 \begin{align} \label{eq:second_quantized_hamiltonian}
@@
 Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
-We begin with an initial guess $\bm{C}^{(i)}$, which is fed into Eq.~\eqref{eq:fock} to produce the Fock matrix.
-This is then used in Eq.~\eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
+We begin with an initial guess $\bm{C}^{(i)}$, which is fed into Eq.\ \eqref{eq:fock} to produce the Fock matrix.
+This is then used in Eq.\ \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
 This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
@@
 
-To make use of the HF solution as the reference state for future calculations, we transform the operators via Eqs.~\eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
+To make use of the HF solution as the reference state for future calculations, we transform the operators via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
 Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
@@
 
-The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.~\cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.
 
@@
 where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.
-This is the formal solution to the linear differential equation Eq.~(\ref{eq:etadefinition}).
-The product integral in Eq.~(\ref{eq:etaintegral}) may also be reinterpreted as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy to time-ordering from quantum field theory.
+This is the formal solution to the linear differential equation Eq.\ (\ref{eq:etadefinition}).
+The product integral in Eq.\ (\ref{eq:etaintegral}) may also be reinterpreted as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy to time-ordering from quantum field theory.
 
@@
 
-The SRG flow equation Eq.~\eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
+The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
 However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
@@
 
-The second-quantized operators in Eq.~\eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
+The second-quantized operators in Eq.\ \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
 \begin{align*}
@@
 If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix $F_{p q}$.
-The operator $\hat H$ in Eq.~\eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.~\eqref{eq:vacuumhamiltonian}.
+The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
 The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
@@
 
-By expanding the commutator in Eq.~\eqref{eq:imsrgode} and discarding the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
+By expanding the commutator in Eq.\ \eqref{eq:imsrgode} and discarding the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
 \begin{align}
@@
 \includegraphics{fig-diagrams-imsrg.pdf}
-\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and Eq.~\eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
+\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
 The two-body vertices are implicitly antisymmetric (i.e.\ \textit{Hugenholtz diagrams} \cite{HUGENHOLTZ1957481}, as described in \cite{shavitt2009many} \S 4.4.3).
@@
 The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
-In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.~\eqref{eq:flow0}, Eq.~\eqref{eq:flow1}, and Eq.~\eqref{eq:flow2}.
-
-The commutator in the flow equations Eq.~\eqref{eq:imsrgode} ensures that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked diagrams} only \cite{shavitt2009many}.
+In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.
+
+The commutator in the flow equations Eq.\ \eqref{eq:imsrgode} ensures that the evolved state $\hat U(s) \ket{\Phi}$ consists of \emph{linked diagrams} only \cite{shavitt2009many}.
 This indicates that IM-SRG is a size-extensive \cite{ISI:A1981MN73700014} method by construction, even if the operators are truncated.
 
-An accurate and robust ODE solver is required to solve Eq.~\eqref{eq:imsrgode}.
+An accurate and robust ODE solver is required to solve Eq.\ \eqref{eq:imsrgode}.
 In particular, the solver must be capable of handling the stiffness that often arises in such problems.
@@
 
-The effective Hamiltonian in Eq.~\eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker--Campbell--Hausdorff expansion as,
+The effective Hamiltonian in Eq.\ \eqref{eq:cc_heff0} can be rewritten with commutators according to the Baker--Campbell--Hausdorff expansion as,
 \begin{align*}
@@
 In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
-Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.~\eqref{eq:cc_heff1} in CCSD.
+Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.
 
@@
   \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{Diagrammatic representation of $\bar{H}$ of Eq.~\eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+  \caption{Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
 As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
@@
 
-The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying Eq.~\eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively,
+The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively,
 \begin{align} \label{eq:ccsd1}
@@
 \end{align}
-After the Fock matrix has been diagonalized, the diagonal components of Eq.~\eqref{eq:ccsd1} can be separated and, after expanding the exponent in Eq.~\eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
+After the Fock matrix has been diagonalized, the diagonal components of Eq.\ \eqref{eq:ccsd1} can be separated and, after expanding the exponent in Eq.\ \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
 \begin{gather} \label{eq:ccsd2}
@@
 \end{gather}
-where $\Delta$ are the M\o ller--Plesset denominators from Eq.~\eqref{eq:moellerplessetdenominator}.
+where $\Delta$ are the M\o ller--Plesset denominators from Eq.\ \eqref{eq:moellerplessetdenominator}.
 As usual, these non-linear equations are solved using an iterative procedure.
-One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of Eq.~\eqref{eq:ccsd2}.
+One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of Eq.\ \eqref{eq:ccsd2}.
 Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side.
@@
 \end{align}
-where the meaning of $\Phi_p$ is defined in Eq.~\eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
+where the meaning of $\Phi_p$ is defined in Eq.\ \eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
 
@@
 
-Making use of the assumptions in Eq.~\eqref{eq:omega-condition1} and Eq.~\eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
+Making use of the assumptions in Eq.\ \eqref{eq:omega-condition1} and Eq.\ \eqref{eq:omega-condition2}, one can derive from the Schr\"odinger equation the generalized Bloch equation, the principal equation of QDPT:
 \begin{gather*}
@@
 \end{align*}
-where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.~\eqref{eq:moellerplessetdenominator}.
+where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.\ \eqref{eq:moellerplessetdenominator}.
 The above expression is depicted in Figure \ref{fig:diagrams-sfe}.
@@
 \end{align}
-Substitution of Eq.~\eqref{eq:ladder_def} into the energy eigenvalue problem
+Substitution of Eq.\ \eqref{eq:ladder_def} into the energy eigenvalue problem
 \begin{gather*}
@@
 Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
-In this case, in addition to constructing excitation ladder operators Eq.~\eqref{eq:gen_attached} and Eq.~\eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem Eq.~\eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
+In this case, in addition to constructing excitation ladder operators Eq.\ \eqref{eq:gen_attached} and Eq.\ \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem Eq.\ \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
 \begin{align*}
@@
 \end{align*}
-These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to Eq.~\eqref{eq:EOMIMSRG},
+These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to Eq.\ \eqref{eq:EOMIMSRG},
 \begin{align*}
@@
 In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
-In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle Eq.~\eqref{eq:partial_norms_p} or single-hole Eq.~\eqref{eq:partial_norms_h} natures are, in practice, not significant.
+In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle Eq.\ \eqref{eq:partial_norms_p} or single-hole Eq.\ \eqref{eq:partial_norms_h} natures are, in practice, not significant.
 Therefore, only the right-eigenvectors are used in this paper.
@@
 There is great amount of flexibility in the application of many-body methods.
-The approaches we use is shown in Fig.~\ref{fig:methods}.
+The approaches we use is shown in Fig.\ \ref{fig:methods}.
 Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
 
-The general process begins with the input matrix elements Eq.~\eqref{eq:interactionintegral}, computed exactly using the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
+The general process begins with the input matrix elements Eq.\ \eqref{eq:interactionintegral}, computed exactly using the \texttt{OpenFCI} software library \cite{2008arXiv0810.2644K}.
 Internally, \texttt{OpenFCI} calculates the interaction integrals in the center-of-mass frame using Gauss--Hermite quadrature and transforms them back into the laboratory frame to produce matrix elements suitable for use in our many-body methods.
@@
 
-In Fig.~\ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
+In Fig.\ \ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
 We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.
@@
 We do not include results from ``HF only'' to avoid overshadowing the comparatively smaller differences between the non-HF results in the plots.
-Some HF results can be found in Fig.~\ref{fig:by-freq-10-6-normal} instead.
+Some HF results can be found in Fig.\ \ref{fig:by-freq-10-6-normal} instead.
 Generally, the HF ground state energies differ from the non-HF ones by a few to several percent, whereas non-HF energies tend to differ from each other by less than a percent.
@@
   \includegraphics{fig-add2.pdf}
-  \caption{Addition energies for a selection of quantum dot parameters.  See Fig.~\ref{fig:gs} for details.}
+  \caption{Addition energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:gs} for details.}
   \label{fig:add}
@@
   \includegraphics{fig-rm2.pdf}
-  \caption{Removal energies for a selection of quantum dot parameters.  See Fig.~\ref{fig:add} for details.}
+  \caption{Removal energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:add} for details.}
   \label{fig:rm}
@@
 
-The results of our addition and removal energy calculations are summarized in Fig.~\ref{fig:add} and Fig.~\ref{fig:rm} respectively.
+The results of our addition and removal energy calculations are summarized in Fig.\ \ref{fig:add} and Fig.\ \ref{fig:rm} respectively.
 The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
@@
 Analogously, we also exclude results from pure IM-SRG (i.e.\ without QDPT nor EOM) or pure CCSD, as QDPT or EOM both add significant contributions to addition and removal energies.
-Some HF only and pure IM-SRG results can be seen in Fig.~\ref{fig:by-freq-10-6-normal}.
+Some HF only and pure IM-SRG results can be seen in Fig.\ \ref{fig:by-freq-10-6-normal}.
 
@@
 
-In Fig.~\ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) + QDPT3.
+In Fig.\ \ref{fig:rel-slopes}, we plot the $\rho_{15}$ for IM-SRG(2) + QDPT3.
 The many-body methods were tested against a \emph{modified} Coulomb-like interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
@@
 The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
-It is necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting Eq.~\eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
+It is necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting Eq.\ \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
 The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
@@
 
-There is still one additional tuning knob for this model that is not explicitly part of Eq.~\eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
+There is still one additional tuning knob for this model that is not explicitly part of Eq.\ \eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
 Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
@@
 The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
-A specific example of the fit is shown in Fig.~\ref{fig:by-fit-2-1p0-add}
+A specific example of the fit is shown in Fig.\ \ref{fig:by-fit-2-1p0-add}
 
@@
 
-The application of IM-SRG eliminates a large number of the QDPT diagrams of Fig.~\ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
+The application of IM-SRG eliminates a large number of the QDPT diagrams of Fig.\ \ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
 Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.

### 2017-06-13 Manuscript/paper.tex
Minor changes to the text

@@
 \end{align*}
-where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are the one- and two-body parts of the Hamiltonian, respectively, and given
+where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are respectively the one- and two-body parts of the Hamiltonian, namely
 \begin{align} \label{eq:onetwobodyhamiltonian}
@@
 
-The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.
-
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form.
 This allows the decoupling of a small, designated \textit{model space} from its larger complementary space.
 The problem can thus be truncated to the small model space while preserving a large amount of information about the system.
+See for examples Refs.\ \cite{kehrein2006flow,Hergert2016165,lnp936} for derivations and calculational details.
 
@@
 \begin{align*}
-  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\Ds} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
+  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\D s} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
 \end{align*}
@@
 A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
-This gives rise to the IM-SRG method \cite{bogner2012,heikophysrep2016,lnp936}.
+This gives rise to the IM-SRG method \cite{bogner2012,Hergert2016165,lnp936}.
 
@@
 \end{align*}
-and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as {\bf ref to epstein-nesbet deno, insert later}
+and the Epstein--Nesbet energy denominators $\tilde{\Delta}$ \cite{shavitt2009many} are defined as
 \begin{align}
@@
 \end{align}
-Some authors {\bf ref} use the M\o ller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.  {\bf define Moller plesset denos and give reference}.
+It is also possible \cite{IMSRG} to use $\Delta$ (also defined above), the same energy denominators from M\o ller--Plesset perturbation theory, which leads to a slightly different variant of the White generator.
+For our calculations, we use exclusively Epstein--Nesbet denominators.
 
@@
 \end{align}
-where the meaning of $\Phi_p$ is defined in Eq.\ \eqref{eq:quasisd}, $i$ is restricted to labels of occupied states, and $a$ is restricted to labels of unoccupied states.
+where $i$ is restricted to labels of occupied states, $a$ is restricted to labels of unoccupied states, and $|\Phi_p\rangle \equiv \hat b_p |\Phi\rangle$.
 
@@
 For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
-This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for modulus division) where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for the modulo operation) where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
 
@@
 Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-Cases where IM-SRG converged too slowly to be feasible or diverged are marked ``n.c.(I)''.
-For the extrapolations in Section \ref{subsec:extrapolation}, some fits could not be done due to missing data caused by lack of convergence for either the IM-SRG(2) calculations or the CCSD calculations.
+In the tables, ``n.c.'' marks the cases where IM-SRG or CCSD either diverged or converged extremely slowly.
+This also affects the extrapolation results in Section \ref{subsec:extrapolation}, as for consistency reasons we chose to extrapolate only when all five points were available.
+Some extrapolations resulted in unphysical parameters ($\beta \le 0$); these are marked ``n.f.''.
 
@@
 \end{align*}
-The process of calculating numerically the derivative can amplify the noise in the data and distorts the weights of the data points.
+The process of numerically calculating the derivative can amplify the noise in the data and distorts the weights of the data points.
 Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
@@
 Afterward, we do a final fit with all three parameters free to vary.
-All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm as implemented in \texttt{Minpack}, with equal weighting of all data points.
-{\bf Ref to this}.
+All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm \cite{10.2307/43633451,doi:10.1137/0111030} as implemented in \texttt{Minpack} \cite{More1978,More:126569}, with equal weighting of all data points.
 

### 2017-06-13 Manuscript/paper.tex
Fix some missing refs + split \Ds

--- 2017-06-13 Manuscript/paper.tex
@@
 
-The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehrein2006flow,Hergert2016165,lnp936} for derivations and calculational details.
 

### 2017-06-13 Manuscript/paper.tex
Strip commas from subscripts

--- 2017-06-13 Manuscript/paper.tex
@@
 \usepackage{natbib}
+\usepackage{scalerel}
 \usepackage{siunitx}
@@
 \newcommand{\normord}[1]{\mathopen: #1 \mathclose:}
+\newcommand{\antisymm}{\mathop{\scalerel*{\mathcal{A}}{\textstyle\sum}}\displaylimits}
 
@@
 However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \partial / (\partial \varphi)$.
+Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
 
@@
 \begin{align}
-  F_{n, m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n, |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\
-  R_{n, m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
+  F_{n m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\
+  R_{n m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
   A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi}, \notag
@@
 \end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, 2, -1, 0, 1, 2, \ldots\}$.
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
 For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
 
-Since electrons are spin-$1/2$ fermions, they can occupy either of the two possible spin states $\chi_{-1/2}$ or $\chi_{+1/2}$.
-Thus, every single-particle basis state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy either of the two possible spin states $\chi_{-\frac{1}{2}}$ or $\chi_{+\frac{1}{2}}$.
+Thus, every single-particle basis state $|n m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
 \begin{align} \label{eq:singleparticlestate}
-  \langle (\rho, \varphi), m_{\mathrm{s}}' | (n, m_\ell, m_{\mathrm{s}}) \rangle \equiv F_{n, m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{}, m_{\mathrm{s}}'}.
-\end{align}
-Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-1/2, +1/2\bigr\}$ as the third quantum number and $\delta_{p, q}$ to denote the Kronecker delta..
-
-The energy of the single-particle state $| (n, m_\ell, m_{\mathrm{s}}) \rangle$ is given by
+  \langle \rho \varphi m_{\mathrm{s}}' |n m_\ell m_{\mathrm{s}}\rangle \equiv F_{n m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{} m_{\mathrm{s}}'}.
+\end{align}
+Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the third quantum number and $\delta_{p q}$ to denote the Kronecker delta..
+
+The energy of the single-particle state $|n m_\ell m_{\mathrm{s}}\rangle$ is given by
 \begin{align} \label{eq:energysingleparticlestate}
-  \varepsilon_{n, m_\ell, m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega.
+  \varepsilon_{n m_\ell m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega.
 \end{align}
@@
 Returning to the one-body part of the many-body Hamiltonian, $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
-Note that a Slater determinant $|p_1, \ldots, p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
-\begin{align*}
-  \langle \bm{r}_1, \ldots, \bm{r}_N | p_1, \ldots, p_N \rangle \equiv
+Note that a Slater determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
+\begin{align*}
+  \langle \bm{r}_1 \ldots \bm{r}_N | p_1 \ldots p_N \rangle \equiv
   \frac{1}{\sqrt{N}} \left|
@@
 \end{align*}
-The Slater determinant $|p_1, \ldots, p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
+The Slater determinant $|p_1 \ldots p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
 By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
@@
 \begin{align*}
-  \hat{H}^{[1]} | p_1, \ldots, p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1, \ldots, p_N \rangle
+  \hat{H}^{[1]} | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle
 \end{align*}
@@
   &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
-  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p, q}.
+  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p q}.
 \end{align*}
@@
 In this paper, we use the letters $p, q, r, s, t, \ldots$ to label arbitrary single-particle \textit{states} in the basis.
-For the harmonic oscillator basis, labels such as $p$ can be considered abbreviations for triplets of the form $(n, m_\ell, m_{\mathrm{s}})$.
 A summation such as $\sum_p$ is then understood as a summation over every single-particle basis state $p$.
@@
 \begin{align}
-  \hat{H} = \sum_{p, q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
+  \hat{H} = \sum_{p q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
 \label{eq:vacuumhamiltonian}
@@
 \begin{align*}
-  \ket{\Phi} \equiv \ket{i_1, i_2, \ldots, i_N}
+  \ket{\Phi} \equiv \ket{i_1 i_2 \ldots i_N}
 \end{align*}
@@
   \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &=
-  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p, q}^{}.
+  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p q}^{}.
 \end{align*}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_{i} n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} n_i n_j \langle i j | \hat{H}^{[2]} | i j \rangle, \\
-  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{i} n_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
+  H^{[0]} &\equiv \sum_i n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} n_i n_j \langle i j | \hat{H}^{[2]} | i j \rangle, \\
+  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_i n_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
   H^{[2]}_{p q r s} &\equiv \langle p q | \hat{H}^{[2]} | r s \rangle. \\
@@
 \begin{align}
-  C^{[k]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[k]}(A, B) \text{ for any $k$, $A$, $B$}, \label{eq:commutmxe} \\
-  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$},
+  C^{[k]}(A, B) &\equiv 2 \antisymm_{A B} D^{[k]}(A, B), \label{eq:commutmxe} \\
+  \antisymm_{x y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr),
 \end{align}
@@
     \label{eq:flow0} \\
-  D^{[1]}_{p, q}(A, B)
+  D^{[1]}_{p q}(A, B)
   &\equiv
-    \sum_{r} A^{[1]}_{p r} B^{[1]}_{r q}
+    \sum_r A^{[1]}_{p r} B^{[1]}_{r q}
     - \frac{1}{2} \sum_{i j a} n_i n_j \bar{n}_a A^{[2]}_{i j a q} B^{[2]}_{a p i j}
@@
     + A^{[2]}_{i p a q} B^{[1]}_{a i}
-    \right)
+    \right),
     \label{eq:flow1} \\
@@
   &\equiv
-    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r s}
+    4 \antisymm_{p q} \antisymm_{r s}
     \sum_{i a} n_i \bar{n}_a A^{[2]}_{i p a r} B^{[2]}_{a q i s}
@@
   &\hphantom{=}
-    + \sum_{t} \left(
-    \tilde{\mathcal{A}}_{p q} A^{[1]}_{q t} B^{[2]}_{p t r s}
-    + \tilde{\mathcal{A}}_{r s} A^{[2]}_{p q r t} B^{[1]}_{t s}.
-    \right)
+    + 2 \sum_t \left(
+    \antisymm_{p q} A^{[1]}_{q t} B^{[2]}_{p t r s}
+    + \antisymm_{r s} A^{[2]}_{p q r t} B^{[1]}_{t s}
+    \right).
     \label{eq:flow2}
@@
 \begin{align}
-\tilde{\Delta}^{[1]}_{a i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a i a i}, \notag \\
-\tilde{\Delta}^{[2]}_{a b i j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a b i j}, \notag \\
-\Delta^{[2]}_{P_1 P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1 p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2 p_2}, \label{eq:moellerplessetdenominator} \\
+\tilde{\Delta}^{[1]}_{a i} &\equiv \Delta_{a i} - H^{[2]}_{a i a i}, \notag \\
+\tilde{\Delta}^{[2]}_{a b i j} &\equiv \Delta_{a b i j} + w_{a b i j}, \notag \\
+\Delta_{p_1 \ldots p_k q_1 \ldots q_k} &\equiv \sum_{i = 1}^k (H^{[1]}_{p_i p_i} -  H^{[1]}_{q_i q_i}), \label{eq:moellerplessetdenominator} \\
 w_{a b i j}
@@
 \begin{align*}
-  \ket{\Psi} = e^{\hat{T}}\ket{\Phi},
+  \ket{\Psi} = e^{\hat{T}} \ket{\Phi},
 \end{align*}
 where $\ket{\Phi}$ is the reference state as before.
-The cluster operator $\hat{T} \equiv \hat{T}_{1} + \hat{T}_{2} + ...
-+ \hat{T}_{N}$, is composed of $k$-particle $k$-hole excitation operators, $\hat{T}_{k}$,
+The cluster operator $\hat{T} \equiv \hat{T}_1 + \hat{T}_2 + \cdots + \hat{T}_N$, is composed of $k$-particle $k$-hole excitation operators, $\hat{T}_k$,
 \begin{align} \label{eq:cc_amps}
-  \hat{T}_{k} \equiv \left(\frac{1}{k!}\right)^{2}\sum\limits_{\substack{a_{1}, \dots, a_{k}, \\ i_{1}, \dots, i_{k}}} \bar{n}_{a_{1}} \cdots \bar{n}_{a_{k}} n_{i_{1}} \cdots n_{i_{k}} t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}} \normord{\hat a_{a_{1}}^\dagger \cdots \hat a_{a_{k}}^\dagger \hat a_{i_{k}} \cdots \hat a_{i_{1}}},
-\end{align}
-where the unknown matrix elements, $t^{[k]}_{a_{1}, \dots, a_{k}, i_{1}, \dots, i_{k}}$, are known as \textit{cluster amplitudes} \cite{shavitt2009many}.
+  \hat{T}_k \equiv \left(\frac{1}{k!}\right)^2 \sum_{\substack{a_1 \ldots a_k \\ i_1 \ldots i_k}} \bar{n}_{a_1} \ldots \bar{n}_{a_k} n_{i_1} \ldots n_{i_k} t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k} \normord{\hat{a}_{a_1}^\dagger \ldots \hat{a}_{a_k}^\dagger \hat a_{i_k}^{} \ldots \hat{a}_{i_1}^{}},
+\end{align}
+where the unknown matrix elements, $t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k}$, are known as \textit{cluster amplitudes} \cite{shavitt2009many}.
 
@@
 \begin{align} \label{eq:cc_schrodeq}
-  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}}\ket{\Phi},
+  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}} \ket{\Phi},
 \end{align}
@@
 \begin{align*}
-  \bar{H}_{\mathrm{CC}} = \hat{H} + [\hat{H}, \hat{T}] + \frac{1}{2} [[\hat{H}, \hat{T} ], \hat{T}] + \frac{1}{3!} [[[\hat{H}, \hat{T}], \hat{T}], \hat{T}] + \frac{1}{4!} [[[[\hat{H}, \hat{T}], \hat{T}], \hat{T}], \hat{T}],
+  \bar{H}_{\mathrm{CC}} = \hat{H} + [\hat{H}, \hat{T}] + \frac{1}{2!} [[\hat{H}, \hat{T} ], \hat{T}] + \frac{1}{3!} [[[\hat{H}, \hat{T}], \hat{T}], \hat{T}] + \frac{1}{4!} [[[[\hat{H}, \hat{T}], \hat{T}], \hat{T}], \hat{T}],
 \end{align*}
@@
 \begin{align} \label{eq:cc_heff1}
-  \bar{H}_{\mathrm{CC}} = \bigl(\hat{H}e^{\hat{T}}\bigr)_{\mathrm{c}},
+  \bar{H}_{\mathrm{CC}} = \bigl\{\hat{H}e^{\hat{T}}\bigr\}_{\mathrm{c}},
 \end{align}
@@
 \begin{align*}
-  \hat{T} = \hat{T}_{1} + \hat{T}_{2}.
+  \hat{T} = \hat{T}_1 + \hat{T}_2.
 \end{align*}
@@
   \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_{1}$ and $\hat{T}_{2}$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+  \caption{Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
 As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
@@
 
-The unknown cluster amplitudes in CCSD, $t_{a, i}^{[1]}$ and $t_{a, b, i, j}^{[2]}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \E^{-\hat{T}}$, respectively,
+The unknown cluster amplitudes in CCSD, $t_{a i}^{[1]}$ and $t_{a b i j}^{[2]}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \E^{-\hat{T}}$, respectively,
 \begin{align} \label{eq:ccsd1}
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0, \\
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0. \notag
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0, \\
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0. \notag
 \end{align}
@@
 \begin{gather} \label{eq:ccsd2}
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{a}} \hat{H}^{[2]}(\hat{T}_{1} + \hat{T}_{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{1}^{2} + \frac{1}{3!}\hat{T}_{1}^{3})_{c} \ket{\Phi} = (H_{i, i}^{[1]} - H_{a, a}^{[1]}) t_{a, i}^{[1]} \\
-  \bra{\Phi} \normord{\hat a_{i}^\dagger \hat a_{j}^\dagger \hat a_{b} \hat a_{a}} \hat{H}^{[2]} (1 + \hat{T}_{1} + \hat{T}_{2} + \frac{1}{2} \hat{T}_{1}^{2} + \hat{T}_{1}\hat{T}_{2} + \frac{1}{2}\hat{T}_{2}^{2} + \frac{1}{3!}\hat{T}_{1}^{3} + \frac{1}{2}\hat{T}_{1}^{2}\hat{T}_{2} + \frac{1}{4!}\hat{T}_{1}^{4} )_{c} \ket{\Phi} \notag \\
-= \Delta_{\{i j\}, \{a b\}} t_{a b i j}^{[2]} \notag
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \hat{H}^{[2]} \bigl\{\hat{T}_1 + \hat{T}_2 + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_1^{2} + \frac{1}{3!} \hat{T}_1^{3}\}_{\mathrm{c}} \ket{\Phi} = \Delta_{i a} t_{a i}^{[1]} \\
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \hat{H}^{[2]} \bigl\{1 + \hat{T}_1 + \hat{T}_2 + \frac{1}{2} \hat{T}_1^{2} + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_2^{2} + \frac{1}{3!} \hat{T}_1^{3} + \frac{1}{2!} \hat{T}_1^{2} \hat{T}_2 + \frac{1}{4!} \hat{T}_1^{4}\bigr\}_{\mathrm{c}} \ket{\Phi} \notag \\
+= \Delta_{i j a b} t_{a b i j}^{[2]} \notag
 \end{gather}
@@
   &=
-    \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{2 \Delta_{\{p i\}, \{a b\}}}
-    - \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{2 \Delta_{\{i j\}, \{p a\}}},
+    \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{2 \Delta_{p i a b}}
+    - \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{2 \Delta_{i j p a}},
 \end{align*}
@@
 \begin{align*}
-  \varepsilon_p = H^{[1]}_{p, p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}.
+  \varepsilon_p = H^{[1]}_{p p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}.
 \end{align*}
@@
   \label{eq:gen_attached}
-  \hat{X}^{(N+1)}_u &= \sum_p \bar{n}_p x^{[1,0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r x^{[2,1]}_{p q r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r + \cdots,  \\
+  \hat{X}^{(N + 1)}_u &= \sum_p \bar{n}_p x^{[1, 0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r x^{[2, 1]}_{p q r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r^{} + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N-1)}_u &= \sum_p n_p x_p^{[0,1]} \hat{a}_p + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  x^{[1,2]}_{p q r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p  + \cdots.
+  \hat{X}^{(N - 1)}_u &= \sum_p n_p x_p^{[0, 1]} \hat{a}_p^{} + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  x^{[1, 2]}_{p q r} \hat{a}^\dagger_r \hat{a}_q^{} \hat{a}_p^{}  + \cdots.
 \end{align}
@@
 Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
-In this case, in addition to constructing excitation ladder operators Eq.\ \eqref{eq:gen_attached} and Eq.\ \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem Eq.\ \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N+1)}$ and $\hat{L}^{(N-1)}$, that correspond to the left-eigenvectors,
-\begin{align*}
-    \hat{L}^{(N+1)}_w &= \sum_p \bar{n}_p l^{[1,0]}_p \hat{a}_p + \frac{1}{2} \sum_{p, q, r} \bar{n}_p \bar{n}_q n_r l^{[2,1]}_{p, q, r} \hat{a}^\dagger_r \hat{a}_q \hat{a}_p + \cdots, \\
-    \hat{L}^{(N-1)}_w &= \sum_p n_p l_p^{[0,1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p, q, r} n_p n_q \bar{n}_r  l^{[1,2]}_{p, q, r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r + \cdots
+In this case, in addition to constructing excitation ladder operators Eq.\ \eqref{eq:gen_attached} and Eq.\ \eqref{eq:gen_removed} that correspond to the right-eigenvectors of the generalized eigenvalue problem Eq.\ \eqref{eq:EOMIMSRG}, there exist analogous de-excitation ladder operators, $\hat{L}^{(N + 1)}$ and $\hat{L}^{(N - 1)}$, that correspond to the left-eigenvectors,
+\begin{align*}
+    \hat{L}^{(N + 1)}_w &= \sum_p \bar{n}_p l^{[1, 0]}_p \hat{a}_p^{} + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r l^{[2, 1]}_{p q r} \hat{a}^\dagger_r \hat{a}_q^{} \hat{a}_p^{} + \cdots, \\
+    \hat{L}^{(N - 1)}_w &= \sum_p n_p l_p^{[0, 1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  l^{[1, 2]}_{p q r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r^{} + \cdots
 \end{align*}
@@
 \begin{align*}
-  \bra{\Phi^{(N)}_0} [\bar{H},\bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_w
-\end{align*}
-and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_w}{\bar{X}^{(N \pm 1)}_u} = \delta_{w,u}$.
+  \bra{\Phi^{(N)}_0} [\bar{H}, \bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_w
+\end{align*}
+and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_w}{\bar{X}^{(N \pm 1)}_u} = \delta_{w u}$.
 
@@
 \begin{align*}
-  \varepsilon^{(+)} &\equiv E_{N + 1} - E_N, \\
-  \varepsilon^{(-)} &\equiv E_N - E_{N - 1}.
+  \varepsilon^{(+)} &\equiv E_{(N + 1)} - E_N, \\
+  \varepsilon^{(-)} &\equiv E_N - E_{(N - 1)}.
 \end{align*}
@@
 \begin{align*}
-  \rho_K = \frac{\varepsilon_{K} - \varepsilon_{K - 1}}{\varepsilon_K}.
+  \rho_K = \frac{\varepsilon_K - \varepsilon_{(K - 1)}}{\varepsilon_K}.
 \end{align*}

### 2017-06-13 Manuscript/paper.tex
Minor edits

@@
 
-In this work we will mainly work with the formalism of second quantization, see for example Ref.\ \cite{shavitt2009many}.
+In this work we will mainly work within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
 To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
@@
 \end{align}
-This object only has a two-fold symmetry: $v_{p_1 p_2 p_3 p_4} = v_{p_2 p_1 p_4 p_3}$.  The antisymmetrized matrix element are related to the interaction integral via
+This object only has a two-fold symmetry: $v_{p_1 p_2 p_3 p_4} = v_{p_2 p_1 p_4 p_3}$.  The antisymmetrized matrix elements are related to the interaction integral via
 \begin{align} \label{eq:antisymmetricmatrixelement}
@@
 
-The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehrein2006flow,Hergert2016165,lnp936} for derivations and calculational details.
-
+The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form.
 This allows the decoupling of a small, designated \textit{model space} from its larger complementary space.
 The problem can thus be truncated to the small model space while preserving a large amount of information about the system.
+See for examples Refs.\ \cite{kehrein2006flow,Hergert2016165,lnp936} for derivations and calculational details.
 

### 2017-06-13 Manuscript/paper.tex

@@
 
-In this work we will mainly work within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
+In this paper, we use the letters $p, q, r, s, \ldots$ to label arbitrary \textit{single-particle states} in the basis.
+In the discussion of many-body methods that rely a single, distinguished Slater determinant $\Phi$, known as the \textit{reference state}, we use the letters $i, j, k, l, \ldots$ as placeholders for the occupied states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
+A summation such as $\sum_p$ is understood as a summation over every single-particle basis state $p$.
+In contrast, $\sum_i$ only sums over those that are occupied and $\sum_a$ only sums over those that are unoccupied.
+
+We will describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
 To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
@@
 where the quantities $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p q | \hat{H}^{[2]} | r s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
-In this paper, we use the letters $p, q, r, s, t, \ldots$ to label arbitrary single-particle \textit{states} in the basis.
-A summation such as $\sum_p$ is then understood as a summation over every single-particle basis state $p$.
-This is not to be confused with summations such as $\sum_j$ from \eqref{eq:onetwobodyhamiltonian}, which contains a label $j$ denoting an arbitrary \textit{particle}.
-We thus see another benefit with second quantization: the Hamiltonian representation makes no attempt to distinguish particles at all, as expected for particles with quantum statistics.
 
@@
 \begin{align}
-  E_{\Phi} &= \sum_i n_i H^{[1] \prime}_{i i} + \sum_{i j} n_i n_j H^{[2] \prime}_{i j i j} \label{eq:hfenergy},
+  E_{\Phi} &= \sum_i H^{[1] \prime}_{i i} + \sum_{i j} H^{[2] \prime}_{i j i j} \label{eq:hfenergy},
 \end{align}
@@
 \end{align}
-and $n_p$ is the \textit{occupancy}, defined as
-\begin{align}
-  n_p \equiv \begin{cases}
-    1 & \text{if $p$ is an occupied state in $\Phi$}, \\
-    0 & \text{if $p$ is an unoccupied state in $\Phi$}.
-  \end{cases}
-\end{align}
-We will also use $\bar n_p \equiv 1 - n_p$ as a shorthand for the complement.
 
@@
 \begin{align} \label{eq:fock}
-  F_{p q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r s i} n_i C_{r i}^* \langle p r | \hat{H}^{[2]} | q s \rangle C_{s i}^{},
+  F_{p q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r s i} C_{r i}^* \langle p r | \hat{H}^{[2]} | q s \rangle C_{s i}^{},
 \end{align}
@@
 \begin{align*}
-  \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &=
-  \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p q}^{}.
-\end{align*}
+  \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &= \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p q}^{}.
+\end{align*}
+and $n_p$ is the \textit{occupancy} of the single-particle state $p$, defined as
+\begin{align}
+  n_p \equiv \begin{cases}
+    1 & \text{if $p$ is an occupied state of $\Phi$}, \\
+    0 & \text{if $p$ is an unoccupied state of $\Phi$}.
+  \end{cases}
+\end{align}
+
 The normal ordering notation thus provides a concise way of expressing the right-hand side.
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_i n_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} n_i n_j \langle i j | \hat{H}^{[2]} | i j \rangle, \\
-  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_i n_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
+  H^{[0]} &\equiv \sum_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} \langle i j | \hat{H}^{[2]} | i j \rangle, \\
+  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
   H^{[2]}_{p q r s} &\equiv \langle p q | \hat{H}^{[2]} | r s \rangle. \\
@@
   &\equiv
-    \sum_{i a} n_i \bar{n}_a A^{[1]}_{i a} B^{[1]}_{a i}
-    + \frac{1}{4} \sum_{i j a b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i j a b} B^{[2]}_{a b i j},
+    \sum_{i a} A^{[1]}_{i a} B^{[1]}_{a i}
+    + \frac{1}{4} \sum_{i j a b} A^{[2]}_{i j a b} B^{[2]}_{a b i j},
     \label{eq:flow0} \\
@@
     \sum_r A^{[1]}_{p r} B^{[1]}_{r q}
-    - \frac{1}{2} \sum_{i j a} n_i n_j \bar{n}_a A^{[2]}_{i j a q} B^{[2]}_{a p i j}
-    + \frac{1}{2} \sum_{i a b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i p a b} B^{[2]}_{a b i q}
+    - \frac{1}{2} \sum_{i j a} A^{[2]}_{i j a q} B^{[2]}_{a p i j}
+    + \frac{1}{2} \sum_{i a b} A^{[2]}_{i p a b} B^{[2]}_{a b i q}
     \notag \\
   &\hphantom{=}
-    + \sum_{i a} n_i \bar{n}_a \left(
+    + \sum_{i a} \left(
     A^{[1]}_{i a} B^{[2]}_{a p i q}
@@
   &\equiv
-    4 \antisymm_{p q} \antisymm_{r s}
-    \sum_{i a} n_i \bar{n}_a A^{[2]}_{i p a r} B^{[2]}_{a q i s}
-    \notag \\
-  &\hphantom{=}
-    + \frac{1}{2} \sum_{i j} n_i n_j A^{[2]}_{i j r s} B^{[2]}_{p q i j}
-    + \frac{1}{2} \sum_{a b} \bar{n}_a \bar{n}_b A^{[2]}_{p q a b} B^{[2]}_{a b r s}
+    4 \antisymm_{p q} \antisymm_{r s} \sum_{i a} A^{[2]}_{i p a r} B^{[2]}_{a q i s}
+    + \frac{1}{2} \sum_{i j} A^{[2]}_{i j r s} B^{[2]}_{p q i j}
+    + \frac{1}{2} \sum_{a b} A^{[2]}_{p q a b} B^{[2]}_{a b r s}
     \notag \\
@@
 \begin{align*}
-\eta^{\prime [1]}_{a i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}} &
-\eta^{\prime [2]}_{a b i j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}}
+\eta^{\prime [1]}_{a i} &\equiv \frac{H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}} &
+\eta^{\prime [2]}_{a b i j} &\equiv \frac{H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}}
 \end{align*}
@@
 \begin{align} \label{eq:cc_amps}
-  \hat{T}_k \equiv \left(\frac{1}{k!}\right)^2 \sum_{\substack{a_1 \ldots a_k \\ i_1 \ldots i_k}} \bar{n}_{a_1} \ldots \bar{n}_{a_k} n_{i_1} \ldots n_{i_k} t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k} \normord{\hat{a}_{a_1}^\dagger \ldots \hat{a}_{a_k}^\dagger \hat a_{i_k}^{} \ldots \hat{a}_{i_1}^{}},
+  \hat{T}_k \equiv \left(\frac{1}{k!}\right)^2 \sum_{\substack{a_1 \ldots a_k \\ i_1 \ldots i_k}} t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k} \normord{\hat{a}_{a_1}^\dagger \ldots \hat{a}_{a_k}^\dagger \hat a_{i_k}^{} \ldots \hat{a}_{i_1}^{}},
 \end{align}
@@
   &=
-    \sum_{i a b} \frac{n_i \bar{n}_a \bar{n}_b |H^{[2]}_{p i a b}|^2}{2 \Delta_{p i a b}}
-    - \sum_{i j a} \frac{n_i n_j \bar{n}_a |H^{[2]}_{i j p a}|^2}{2 \Delta_{i j p a}},
+    \sum_{i a b} \frac{|H^{[2]}_{p i a b}|^2}{2 \Delta_{p i a b}}
+    - \sum_{i j a} \frac{|H^{[2]}_{i j p a}|^2}{2 \Delta_{i j p a}},
 \end{align*}
@@
   \label{eq:gen_attached}
-  \hat{X}^{(N + 1)}_u &= \sum_p \bar{n}_p x^{[1, 0]}_p  \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r x^{[2, 1]}_{p q r} \hat{a}^\dagger_p \hat{a}^\dagger_q \hat{a}_r^{} + \cdots,  \\
+  \hat{X}^{(N + 1)}_u &= \sum_a x^{[1, 0]}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{[2, 1]}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N - 1)}_u &= \sum_p n_p x_p^{[0, 1]} \hat{a}_p^{} + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  x^{[1, 2]}_{p q r} \hat{a}^\dagger_r \hat{a}_q^{} \hat{a}_p^{}  + \cdots.
+  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{[0, 1]} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{[1, 2]}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
 \end{align}
@@
   \label{eq:partial_norms_p}
-  n_{\text{1-particle}} &= \sqrt{\sum_p \bar{n}_p | \bar{x}^{[1,0]}_p |^2},\\
+  n_{\text{1-particle}} &= \sqrt{\sum_a | \bar{x}^{[1,0]}_a |^2},\\
   \label{eq:partial_norms_h}
-  n_{\text{1-hole}} &= \sqrt{\sum_p n_p | \bar{x}^{[0,1]}_p |^2}.
+  n_{\text{1-hole}} &= \sqrt{\sum_i | \bar{x}^{[0,1]}_i |^2}.
 \end{align}
@@
 \begin{align*}
-    \hat{L}^{(N + 1)}_w &= \sum_p \bar{n}_p l^{[1, 0]}_p \hat{a}_p^{} + \frac{1}{2} \sum_{p q r} \bar{n}_p \bar{n}_q n_r l^{[2, 1]}_{p q r} \hat{a}^\dagger_r \hat{a}_q^{} \hat{a}_p^{} + \cdots, \\
-    \hat{L}^{(N - 1)}_w &= \sum_p n_p l_p^{[0, 1]} \hat{a}^\dagger_p + \frac{1}{2} \sum_{p q r} n_p n_q \bar{n}_r  l^{[1, 2]}_{p q r} \hat{a}^\dagger_p  \hat{a}^\dagger_q \hat{a}_r^{} + \cdots
+    \hat{L}^{(N + 1)}_w &= \sum_a l^{[1, 0]}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{[2, 1]}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
+    \hat{L}^{(N - 1)}_w &= \sum_i l_i^{[0, 1]} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{[1, 2]}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
 \end{align*}

### 2017-06-13 Manuscript/paper.tex
bibtex and paper.tex update

@@
 Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
-They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{bogner2010}.
+They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{PhysRevC.84.044306}.
 
@@
 A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
-This gives rise to the IM-SRG method \cite{bogner2012,Hergert2016165,lnp936}.
+This gives rise to the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
 

### 2017-06-13 Manuscript/paper.tex
small revisions

@@
 \begin{abstract}
-  We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
-We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
-With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
-Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
-We examine the rate of convergence and perform extrapolations to the infinite basis limit using a power-law model.
+  We present and compare several many-body methods as applied to
+  two-dimensional quantum dots with circular symmetry.  We calculate
+  the approximate ground state energy using a harmonic oscillator
+  basis optimized by Hartree--Fock (HF) theory and further improve the
+  ground state energy using two post-HF methods: in-medium similarity
+  renormalization group (IM-SRG) and coupled cluster
+  singles-and-doubles (CCSD).  With the application of quasidegenerate
+  perturbation theory (QDPT) or the equation-of-motion (EOM) method,
+  we obtain addition and removal energies as well.  Our results are
+  benchmarked against full configuration interaction (FCI) and
+  diffusion Monte Carlo (DMC) where available.  We examine the rate of
+  convergence and perform extrapolations to the infinite basis limit
+  using a power-law model.
 \end{abstract}
@@
 
-The behavior of strongly confined electrons is of fundamental concern to many-body theory.
-The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
-Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
-Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
-This allows experiments to quantify the impact of quantum effects at different levels of correlation.
-
-The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
-They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{PhysRevC.84.044306}.
-
-Beyond their theoretical relevance, there are numerous potential applications of quantum dots.
-The electrical and optical properties of quantum dots are particularly useful for solar cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser technology \cite{strauf2010,5075760}.
-They have potential medical applications in diagnosis and treatment \cite{Ben-Ari02042003}.
-And of course, quantum dots are also promising candidates for the physical realization of quantum computing \cite{PhysRevA.57.120}.
-
-In general, quantum dot systems are not analytically solvable, with the exception of two-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
-Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
-
-One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuration interaction method.
-Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increased to infinity (the so-called \textit{infinite-basis limit}).
-Despite this significant advantage, it is often not possible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
-This led to the development of more cost-effective methods that trade varying amounts of accuracy for varying amounts of speed.
-
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
-We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
-
-Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
-Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
-The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
-It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
-The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
-The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
-
-The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
-Our results are presented in Section \ref{sec:results}.
-We analyze and compare the differences between the various methods and also between different quantum dot systems.
-We examine the usefulness of extrapolation techniques in improving the precision of the results.
-Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
+The behavior of strongly confined electrons is of fundamental concern
+to many-body theory.  The prototypical system is that of quantum dots,
+also known as ``artificial atoms'', in which electrons are confined
+within artificially constructed semiconducting heterostructures.  Such
+nanoscale systems are highly relevant as they lie at a critical point
+where both theoretical models and experimental observations can
+readily probe quantum phenomena such as tunneling, entanglement, and
+magnetization \cite{reimann2002,engel1993}.  Moreover, unlike many
+physical systems, quantum dots enjoy the benefit of being highly
+tunable through changes in the external field or the structure of the
+confining material.  This allows experiments to quantify the impact of
+quantum effects at different levels of correlation.
+
+The ground states of quantum dots exhibit shell structures and magic
+numbers similar to those of atoms and nuclei \cite{tarucha1996}.
+Thus, they provide a rare opportunity to study electronic systems
+without the influence of the atomic nuclei.  They also provide a
+testbed for the development of many-body methods for other systems
+with similar geometry, such as nuclei or neutrons
+drops \cite{PhysRevC.84.044306}.
+
+Beyond their theoretical relevance, there are numerous potential
+applications of quantum dots.  The electrical and optical properties
+of quantum dots are particularly useful for solar
+cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser
+technology \cite{strauf2010,5075760}.  They have potential medical
+applications in diagnosis and treatment \cite{Ben-Ari02042003}.  And
+of course, quantum dots are also promising candidates for the physical
+realization of quantum computing \cite{PhysRevA.57.120}.
+
+In general, quantum dot systems are not analytically solvable, with
+the exception of two-electron systems or systems with specific
+strengths of the external field \cite{PhysRevA.48.3561}.  Hence, in
+practical applications one can only hope for a numerical solution
+through some \textit{many-body method} or a combination thereof.
+
+One of the most accurate techniques for solving many-body systems is
+that of exact diagonalization, also known as the full configuration
+interaction method.  Unlike most methods, it is assured to converge to
+the exact answer as the size of the finite basis is increased to
+infinity (the so-called \textit{infinite-basis limit}).  Despite this
+significant advantage, it is often not possible to perform exact
+diagonalization due to its factorially increasing cost with respect to
+the basis size and the number of particles.  This led to the
+development of more cost-effective methods that trade varying amounts
+of accuracy for varying amounts of speed.
+
+In this paper, we analyze the application of several methods to the
+quantum dot systems, including the Hartree--Fock (HF) method, M\o
+ller-Plesset perturbation theory (MP), the in-medium similarity
+renormalization group (IM-SRG) method, coupled cluster (CC)
+theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302},
+quasidegenerate perturbation theory (QDPT), and equation-of-motion
+(EOM) methods.  We compare them against variational and diffusion
+Monte Carlo (VMC and
+DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}
+and full configuration interaction (FCI)
+theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102}
+results, where available, from the existing literature.
+
+Of these methods, IM-SRG is a recently developed technique that has
+shown significant promises.  Similarity renormalization group (SRG)
+methods are a family of methods that transform the Hamiltonian into a
+band- or block-diagonal form through a continuous sequence of unitary
+transformations.  The goal of such a transformation is to reduce the
+coupling between a subspace of interest -- such as the ground state or
+a set of low-lying states -- and the remaining Hilbert space.  It has
+successfully been applied to systems with various underlying
+potentials to calculate their binding energy and other observables,
+especially in nuclear
+theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
+The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method
+to evolve Hamiltonians in a truncated Fock space, which avoids the
+prohibitive cost of constructing a full many-body Hamiltonian.  The
+effect of the truncation is minimized through the normal-ordering
+technique, which re-expands the operators with respect to a nearby
+many-body reference state rather than the far-away vacuum state.
+
+The article is organized as follows: Section \ref{sec:formalism}
+introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
+use to model circular quantum dots, and gives afterwards an overview
+of the \textit{ab initio} many-body methods used in this paper:
+Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.  Our results are presented in
+Section \ref{sec:results}.  We analyze and compare the differences
+between the various methods and also between different quantum dot
+systems.  We examine the usefulness of extrapolation techniques in
+improving the precision of the results.  Section \ref{sec:conclusions}
+concludes our work and gives perspectives for future work.
 
@@
 
-We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
-The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
-
-Even though the model system contains five parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
-With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
-For rest of this paper, we shall use atomic units where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
-The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
-\begin{align*}
-  E_{\mathrm{h}} &\equiv m \left(\frac{e^2}{4 \pi \epsilon \hbar}\right)^2 &
+We shall model the circular quantum dot system as a collection of $N$
+nonrelativistic electrons of mass $m$ in two-dimensional space,
+trapped by an external harmonic-oscillator potential of the form
+$m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the
+oscillator trap and $r$ is the distance from the center of the trap.
+The electrons interact with each other through the standard Coulomb
+interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of
+each electron, $\epsilon$ is the permittivity of the medium, and $R$
+is the distance between the two interacting electrons.
+
+Even though the model system contains five parameters $(N, m, \omega,
+e, \epsilon)$, many of them are redundant.  With an appropriate choice
+of units, the number of parameters in the system can be reduced to
+just two.  For rest of this paper, we shall use atomic units where
+$\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.  The unit
+Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr
+radius $a$ becomes the unit of length:
+\begin{align*}
+  E_{\mathrm{h}} &\equiv m \left(\frac{e^2}{4 \pi \epsilon \hbar}\right)^2, &
   a &\equiv \frac{4 \pi \epsilon \hbar^2}{m e^2}.
@@
 \end{align*}
-Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is its position relative to the center of the trap.
-The pairwise interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$ is simply the Coulomb interaction:
+Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is
+its position relative to the center of the trap.  The pairwise
+interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$
+is simply the Coulomb interaction:
 \begin{align*}
@@
 \end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th
+particle,\footnote{The ordering of the particle labels $j$ is
+unimportant as they exist only for the purpose of bookkeeping.} and
+$\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its
+momentum operator.
 
@@
   \includegraphics{figures/fig-shell-structure-v2.pdf}
-  \caption{The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
+  \caption{(Color online) The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
 Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.
@@
 
-The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
+The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$
+can be reduced to $N$ independent single-particle Hamiltonians each of
+the form:
 \begin{align*}
@@
 \end{align*}
-where $p$ is an unknown tuple of quantum numbers.
-In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
-However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
+where $p$ is an unknown tuple of quantum numbers.  In Cartesian
+coordinates, the two-dimensional harmonic oscillator is trivially
+reducible to the well-known one-dimensional problem.  However, to
+exploit the circular symmetry, we prefer to use Fock-Darwin states,
+which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+Such states have the computationally useful property of conserving
+orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv
+-\mathrm{i} \frac{\partial}{\partial \varphi}$.
 
@@
 \end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
-For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
-
-Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy either of the two possible spin states $\chi_{-\frac{1}{2}}$ or $\chi_{+\frac{1}{2}}$.
-Thus, every single-particle basis state $|n m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+The states are labeled by two quantum numbers: the principal quantum
+number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum
+projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
+For a wave function, $n$ indicates the degree of the Laguerre
+polynomial, whereas $m_\ell$ is simply the eigenvalue of
+$\hat{L}_{\mathrm{z}}$.
+
+Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy
+either of the two possible spin states $\chi_{-\frac{1}{2}}$ or
+$\chi_{+\frac{1}{2}}$.  Thus, every single-particle basis state $|n
+m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial
+component \eqref{eq:fockdarwin} and a spin component,
 \begin{align} \label{eq:singleparticlestate}
@@
 \end{align}
-Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the third quantum number and $\delta_{p q}$ to denote the Kronecker delta..
+Here we have introduced spin projection
+$m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the
+third quantum number and $\delta_{p q}$ to denote the Kronecker
+delta.
 
@@
 \end{align}
-which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
-
-Returning to the one-body part of the many-body Hamiltonian, $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
-Note that a Slater determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
+which we conveniently call the \textit{shell index} as it labels each
+shell starting from zero.  The shells are equidistant with an energy
+spacing equal to the frequency $\omega$.
+
+Returning to the one-body part of the many-body Hamiltonian,
+$\hat{H}^{[1]}$, we can use the Slater determinant construction to
+build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the
+many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$
+single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$
+from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for
+the triplet $(n, m_\ell, m_{\mathrm{s}})$.  Note that a Slater
+determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the
+single-particle states, but an antisymmetrized sum over all possible
+products,
 \begin{align*}
@@
 \end{align*}
-The Slater determinant $|p_1 \ldots p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
-By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
+The Slater determinant $|p_1 \ldots p_N\rangle$ is said
+to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.  By
+construction, Slater determinants satisfy the Pauli exclusion
+principle, ensuring that the exchange of any two particles is
+equivalent to a reversal in the sign of the many-body wave function.
 
@@
 \begin{align*}
-  \hat{H}^{[1]} | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle
-\end{align*}
-It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
-This is possible even for ground states of $\hat{H}^{[1]}$.
-However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
-The values of $N$ at which this occurs are said to be \textit{magic numbers}.
-We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
-In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
-
-In this paper, we use the letters $p, q, r, s, \ldots$ to label arbitrary \textit{single-particle states} in the basis.
-In the discussion of many-body methods that rely a single, distinguished Slater determinant $\Phi$, known as the \textit{reference state}, we use the letters $i, j, k, l, \ldots$ as placeholders for the occupied states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
-A summation such as $\sum_p$ is understood as a summation over every single-particle basis state $p$.
-In contrast, $\sum_i$ only sums over those that are occupied and $\sum_a$ only sums over those that are unoccupied.
-
-We will describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
-To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
-These operators must satisfy the anticommutation relations that encode the Pauli principle, namely
+  \hat{H}^{[1]} | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle.
+\end{align*}
+It is possible for Slater determinants occupying different sets of
+single-particle states to be degenerate in energy.  This is possible
+even for ground states of $\hat{H}^{[1]}$.  However, if the number of
+particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for
+some nonnegative integer $K_{\mathrm{F}}$, there would be just enough
+particles to form a closed-shell Slater determinant, leading to a
+unique, well-isolated ground state.  The values of $N$ at which this
+occurs are said to be \textit{magic numbers}.  We call
+$K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi
+level'').  In particular, a single-particle state is occupied in the
+ground state Slater determinant if and only $k < K_{\mathrm{F}}$,
+where $k$ is the shell index of the single-particle state as defined
+in \eqref{eq:shell_index}.
+
+In this paper, we use the letters $p, q, r, s, \ldots$ to label
+arbitrary \textit{single-particle states} in the basis.  In the
+discussion of many-body methods that rely a single, distinguished
+Slater determinant $\Phi$, known as the \textit{reference state}, we
+use the letters $i, j, k, l, \ldots$ as placeholders for the occupied
+states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
+A summation such as $\sum_p$ is understood as a summation over every
+single-particle basis state $p$.  In contrast, $\sum_i$ only sums over
+those that are occupied and $\sum_a$ only sums over those that are
+unoccupied.
+
+We will describe many-body methods within the formalism of second
+quantization; see for example Ref.\ \cite{shavitt2009many}.  To
+properly describe fermions, we introduce the annihilation and creation
+operators $\hat a_p$ and $\hat a_p^\dagger$. These operators must
+satisfy the anticommutation relations that encode the Pauli principle,
+namely
 \begin{align*}
@@
   \hat H^{[1]} &= \sum_{p q} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{}, &
-  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{}.
+  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{},
 \end{align}
@@
 \end{align}
-Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a 4-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
-For this reason, the two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the (non-antisymmetric) interaction integral,
+Due to the antisymmetry of Slater determinants, we have the property
+that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign
+of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a four-fold
+symmetry that must be canceled out by the $1/4$ factor in front of the
+summation in \eqref{eq:vacuumhamiltonian}.  For this reason, the
+two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is
+commonly referred to as the \emph{antisymmetrized} matrix element.
+This is not to be confused with the (non-antisymmetric) interaction
+integral,
 \begin{align} \label{eq:interactionintegral}
@@
 \begin{align} \label{eq:antisymmetricmatrixelement}
-  \langle p q | \hat{H}^{[2]} | r s \rangle = v_{p q r s} - v_{p q s r}
-\end{align}
-
-With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
-The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
-Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
-
-However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
-This is a general strategy for many of the many-body methods that we shall describe.
+  \langle p q | \hat{H}^{[2]} | r s \rangle = v_{p q r s} - v_{p q s r}.
+\end{align}
+
+With the basic formalism and notation established along with the
+system of interest, we may begin to discuss the various techniques to
+solve the full many-body problem.  The principal difficulty stems from
+the fact that, due to the presence of interactions, the exact solution
+is in general \emph{not} a single Slater determinant built from the
+single-particle states.  Hence, it is not possible to trivially reduce
+the problem to that of a single particle as we had done previously.
+
+However, if we assume the interaction alters the behavior of the
+system only mildly, we can use a Slater determinant of the
+noninteracting system as a starting point and then apply various
+methods to improve the accuracy of the solution.  This is a general
+strategy for many of the many-body methods that we shall describe.
 
@@
 
-One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
-Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value
+One of the simplest numerical corrections that could be applied to the
+initial guess is that of the Hartree--Fock (HF) method.  Using the
+variational principle, one can compute an approximate ground state
+$\Phi$ by minimizing the energy expectation value
 \begin{align} \label{eq:hfexpectation}
-  E_{\Phi} \equiv \langle \Phi | \hat H | \Phi \rangle
-\end{align}
-with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
-The restriction is what enables the simplicity and efficiency of this method.
-We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
+  E_{\Phi} \equiv \langle \Phi | \hat H | \Phi \rangle,
+\end{align}
+with respect to $|\Phi\rangle$, subject to the restriction that
+$|\Phi\rangle$ remains a single Slater determinant constructed from an
+unknown single-particle basis.  The restriction is what enables the
+simplicity and efficiency of this method.  We shall denote each
+unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To perform numerical calculations, we further assume that each unknown
+state $|q'\rangle$ is built from a linear combination of known states
+$|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined
+via the transformation equation
 \begin{align*}
@@
 \end{align*}
-This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
-The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
-
-If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
-
-To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
-These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
-At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
+This allows the problem to be reduced from an abstract minimization
+problem \eqref{eq:hfexpectation} to a concrete numerical problem.  The
+caveat is that the set of known functions be large enough to capture
+the relevant behavior of the system.
+
+If the interaction is not too strong, it is common to use the
+single-particle states of the noninteracting Hamiltonian
+$\hat{H}^{[1]}$ as the set of known states.
+
+To ensure orthonormality of the states, we require there to be as many
+unknown states $|q'\rangle$ as known states $|p\rangle$, and the
+coefficient matrix $\bm C$ must be unitary.  These conditions are more
+strict than necessary, but they greatly simplify the calculations and
+allow the states $|q'\rangle$ to act as \textit{optimized} inputs for
+methods beyond HF.  At the end of the calculation, of the set of
+states $|q'\rangle$ there would exactly $N$ \textit{occupied} states
+that participate in the optimized Slater determinant $|\Phi\rangle$.
+The remaining \textit{unoccupied} states serve as the complementary
+space into which particles can be excited by the interaction
+$\hat{H}^{[2]}$ during the post-HF calculation.
 
@@
 \begin{align}
-  H^{[1] \prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s q}^{} \label{eq:hftransform1} \\
+  H^{[1] \prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s q}^{}, \label{eq:hftransform1} \\
   H^{[2] \prime}_{p q r s} &\equiv \sum_{t u v w} C_{t p}^* C_{u q}^* \langle t u | \hat{H}^{[2]} | v w \rangle C_{v r}^{} C_{w s}^{}, \label{eq:hftransform2}
@@
 
-The power of SRG methods lies in the flexibility of the generator $\hat{\eta}$, which is usually chosen in an $s$-dependent manner.
-In particular, it is often dependent on the evolving Hamiltonian $\hat{H}(s)$.
-The operator $\hat{\eta}$ determines which parts of the Hamiltonian matrix would become suppressed by the evolution, which are usually considered ``off-diagonal'' in an abstract sense.
-The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
-Or, the ``off-diagonal'' parts could be elements that couple the ground state from the excited state, in which case the evolution drives the matrix towards a block-diagonal form that isolates the ground state.
-Or, the ``off-diagonal'' could be literally the elements that do not lie on the diagonal, in which case the evolution would simply diagonalize the Hamiltonian.
-Through different choices of $\hat{\eta}$, the SRG evolution can be controlled and adapted to the features of a particular problem.
+The power of SRG methods lies in the flexibility of the generator
+$\hat{\eta}$, which is usually chosen in an $s$-dependent manner.  In
+particular, it is often dependent on the evolving Hamiltonian
+$\hat{H}(s)$.  The operator $\hat{\eta}$ determines which parts of the
+Hamiltonian matrix would become suppressed by the evolution, which are
+usually considered ``off-diagonal'' in an abstract sense.  The
+``off-diagonal'' parts could be elements far away from the matrix
+diagonal, in which case the evolution drives the matrix towards a
+band-diagonal form.  Or, the ``off-diagonal'' parts could be elements
+that couple the ground state from the excited state, in which case the
+evolution drives the matrix towards a block-diagonal form that
+isolates the ground state.  Or, the ``off-diagonal'' could be
+literally the elements that do not lie on the diagonal, in which case
+the evolution would simply diagonalize the Hamiltonian.  Through
+different choices of $\hat{\eta}$, the SRG evolution can be controlled
+and adapted to the features of a particular problem.
 
@@
 
-The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
-However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
-A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
-This gives rise to the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
+The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the
+second quantization formalism described in
+Section \ref{subsec:modelHamiltonian}, where field operators are
+defined with respect to the physical vacuum state.  However, since the
+basis of a many-body problem grows factorially with the number of
+particles and the size of the model space, the applicability of the
+naive (free-space) SRG method is restricted to comparatively small
+systems.  A more practical approach is to perform the
+evolution \textit{in medium}, i.e.\ using a many-body Slater
+determinant as a reference \cite{kehrein2006flow}.  This gives rise to
+the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
 
@@
 \end{align*}
-where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label the occupied states.
-One can define a set of \textit{quasiparticle field operators} $\hat b$ and $\hat b^\dagger$ that obey the same anticommutation relations as the $\hat a$ operators.
-The normal ordering of the quasiparticle field operators is straightforward to compute.
-What is more interesting is the normal ordering of the physical field operators $\hat a$ and $\hat a^\dagger$ with respect to $|\Phi\rangle$:
+where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label
+the occupied states.  We define then the normal ordering of the
+physical field operators $\hat a$ and $\hat a^\dagger$ with respect to
+$|\Phi\rangle$, that is
 \begin{align*}
@@
 \end{align*}
-and $n_p$ is the \textit{occupancy} of the single-particle state $p$, defined as
+where $n_p$ is the \textit{occupancy} of the single-particle state $p$, defined as
 \begin{align}
@@
 \end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix $F_{p q}$.
-The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
-The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
-Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
-Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
-
-Higher-body operators arise from integrating the flow equations (\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
-With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
-Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy (zero-body component) is of interest.
-
-Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
-Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
-Thus, to make the method tractable, the IM-SRG flow equations must be closed by truncating the equations to a finite order.
-
-In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
-This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
-
-Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
-The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
-The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
-In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
-For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
+If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is
+simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix
+$F_{p q}$.  The operator $\hat H$ in
+Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat
+H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.  The only difference is that
+the meaning of a ``$k$-body operator'' has been redefined with respect
+to the reference state $\Phi$ rather than the vacuum state $\ket{}$,
+causing matrix elements to be reshuffled among the $k$-body operators.
+Where this makes a critical difference is when the operator
+expressions are \emph{truncated}, i.e.\ some $k$-body operators may be
+discarded from the computation for efficiency reasons.
+Normal-ordering can drastically alter the importance of the $k$-body
+operators with respect to each other.
+
+Higher-body operators arise from integrating the flow equations of Eq.~(\ref{eq:imsrgode}), 
+which is one of the major challenges of the SRG
+method.  With each evaluation of the commutator, the Hamiltonian gains
+terms of higher order, and these induced contributions will in
+subsequent integration steps feed back into terms of lower order.
+Thus, the higher-body contributions are not irrelevant to the final
+solution even if only the ground state energy (zero-body component) is
+of interest.
+
+Computationally, higher-body terms rapidly become unfeasible to
+handle: the amount of memory required to store a $k$-body operator is
+grows exponentially with $k$.  Moreover, the flow equations are
+capable of generating an infinite number of higher-body terms as the
+Hamiltonian evolves.  Thus, to make the method tractable, the IM-SRG
+flow equations must be closed by truncating the equations to a finite
+order.
+
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the
+two-body level, leading to an approach known as IM-SRG(2).  This
+normal-ordered two-body approximation appears to be sufficient in many
+cases and has yielded excellent results for several
+nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+Note that the loss of three- and higher-body terms (\textit{operator
+truncation}) is only one out of the two sources of error in this
+method.  The other source of error is due to the \textit{basis
+truncation}, a concern for any method that relies on a finite
+single-particle basis such as IM-SRG.  The latter can be reduced by
+increasing the size of the basis at the expense of greater
+computational effort, albeit the cost increases much less rapidly in
+this direction.  In IM-SRG the CPU cost is polynomial with respect to
+$N_{\mathrm{b}}$, the number of states in the single-particle basis.
+For IM-SRG(2) in particular, the CPU cost scales roughly as
+$\mathcal{O}(N_{\mathrm{b}}^6)$.
 
@@
 \begin{align}
-    \frac{\D H^{[k]}}{\D s} = C^{[k]}(\eta, H) \label{eq:flowmxe}
+    \frac{\D H^{[k]}}{\D s} = C^{[k]}(\eta, H), \label{eq:flowmxe}
 \end{align}
@@
 \includegraphics{fig-diagrams-imsrg.pdf}
-\caption{Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
+\caption{(Color online) Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
 The two-body vertices are implicitly antisymmetric (i.e.\ \textit{Hugenholtz diagrams} \cite{HUGENHOLTZ1957481}, as described in \cite{shavitt2009many} \S 4.4.3).
@@
 
-Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian operators, it is antihermitian as required for a generator.
-Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
-Matrix elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian couples states with large energy differences -- are suppressed much faster than those ``close'' to the diagonal.
-
-Apart from Wegner's generator, there exist several other ones in literature.
-One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
-The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
-Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
-This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
-
-The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
-Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
-This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
-Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
-This ensures that the affected elements decay at approximately the same rate, reducing the stiffness of the flow equations.
+Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian
+operators, it is antihermitian as required for a generator.
+Additionally, it can be shown that the commutator has the property of
+suppressing off-diagonal matrix elements as the state evolves via the
+flow equation \cite{kehrein2006flow}, as we would like.  Matrix
+elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian
+couples states with large energy differences -- are suppressed much
+faster than those ``close'' to the diagonal.
+
+Apart from Wegner's generator, there exist several other ones in
+literature. One choice, proposed by
+White \cite{White:cond-mat0201346}, makes numerical approaches much
+more efficient.  The problem with the Wegner generator is the widely
+varying decaying speeds of the Hamiltonian matrix elements.  Terms
+with large energy separations from the ground state are suppressed
+initially, followed by those with smaller energy separations.  This
+leads to stiffness in the flow equation, leading to numerical
+difficulties in solving the set of coupled differential equations.
+
+The White generator takes an alternative approach, which is well
+suited for problems where one is mainly interested in the ground state
+of a system.  Firstly, instead of driving all off-diagonal elements of
+the Hamiltonian to zero, the generator focuses exclusively on those
+ones that are coupled to the reference state $\Phi$ so as to decouple
+the reference state from the remaining Hamiltonian.  This reduces the
+amount of change done to the Hamiltonian, reducing the accuracy lost
+from the operator truncation.  Secondly, the rate of decay in
+Hamiltonian matrix elements are approximately normalized by dividing
+the generator matrix elements by an appropriate factor.  This ensures
+that the affected elements decay at approximately the same rate,
+reducing the stiffness of the flow equations.
 
@@
 \begin{align*}
-\eta^{\prime [1]}_{a i} &\equiv \frac{H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}} &
-\eta^{\prime [2]}_{a b i j} &\equiv \frac{H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}}
+\eta^{\prime [1]}_{a i} &\equiv \frac{H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}}, &
+\eta^{\prime [2]}_{a b i j} &\equiv \frac{H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}},
 \end{align*}
@@
   \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
 As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
@@
 \includegraphics{fig-diagrams-sfe.pdf}
-\caption{Diagrammatic form of the second- and third-order QDPT corrections.
+\caption{(Color online) Diagrammatic form of the second- and third-order QDPT corrections.
 The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.
@@
   \includegraphics{figures/fig-methods.pdf}
-  \caption{A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
+  \caption{(Color online) A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
   \label{fig:methods}
@@
 
-The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
-This is due to the presence of multiple states with near-degenerate energies.
-For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
-This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for the modulo operation) where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+The addition and removal energies are similar, but they require an
+additional parameter: the total orbital angular momentum $M_\ell$,
+defined as the sum of the $m_\ell$ of each particle.  This is due to
+the presence of multiple states with near-degenerate energies.  For
+this paper, we will consider exclusively the addition/removal energies
+with the lowest $|M_\ell|$ subject to the constraint that the particle
+added/removed lies within the next/last shell.  This means the $N + 1$
+states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$
+(where $\bmod$ stands for the modulo operation) where $K_{\mathrm{F}}$
+is the number of occupied shells, while the $N - 1$ states of interest
+are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
 
@@
 This also affects the extrapolation results in Section \ref{subsec:extrapolation}, as for consistency reasons we chose to extrapolate only when all five points were available.
-Some extrapolations resulted in unphysical parameters ($\beta \le 0$); these are marked ``n.f.''.
-
-Numerical calculations in this paper are performed with a relative precision of about $10^{-5}$ or lower.
-This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate over the multiple steps of the calculation, thus the precision of the final results is expected to be roughly $10^{-4}$.
+
+Numerical calculations in this paper are performed with a relative
+precision of about $10^{-5}$ or lower.  This does not necessarily mean
+the results are as precise as $10^{-5}$, since numerical errors tend
+to accumulate over the multiple steps of the calculation, thus the
+precision of the final results is expected to be roughly $10^{-4}$.
 
@@
   \includegraphics{fig-gs2.pdf}
-  \caption{Plots of ground state energy of quantum dots with $N$ particles and an oscillatory frequency of $\omega$ against the number of shells $K$.
+  \caption{(Color online) Plots of ground state energy of quantum dots with $N$ particles and an oscillatory frequency of $\omega$ against the number of shells $K$.
 Since DMC does not utilize a finite basis, the horizontal axis is irrelevant and DMC results are plotted as horizontal lines.}
@@
   \includegraphics{fig-add2.pdf}
-  \caption{Addition energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:gs} for details.}
+  \caption{(Color online) Addition energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:gs} for details.}
   \label{fig:add}
@@
   \includegraphics{fig-rm2.pdf}
-  \caption{Removal energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:add} for details.}
+  \caption{(Color online) Removal energies for a selection of quantum dot parameters.  See Fig.\ \ref{fig:add} for details.}
   \label{fig:rm}
@@
   \includegraphics{fig-by-freq-10-6-normal.pdf}
-  \caption{The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
+  \caption{(Color online) The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
 The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
@@
   \includegraphics{fig-rel-slopes2.pdf}
-  \caption{The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
+  \caption{(Color online) The impact of the interaction on convergence of addition and removal energies using IM-SRG(2) + QDPT3.
 For clarity, the plot does not distinguish between addition and removal energies.
@@
   \includegraphics{fig-fit-2-1p0-add.pdf}
-  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.
+  \caption{(Color online) A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system with $K_{\text{stop}} = 15$.
 The grey shaded region contains the masked data points, which are ignored by the fitting procedure.
@@
 \begin{align*}
-  \Delta E \propto K^{-\beta}
+  \Delta E \propto K^{-\beta},
 \end{align*}
@@
 \begin{align} \label{eq:power_law_model}
-  E = \alpha K^{-\beta} + \gamma
+  E = \alpha K^{-\beta} + \gamma.
 \end{align}
@@
 \begin{align*}
-  \log \left|\frac{\partial E}{\partial K}\right| = - (\beta + 1) \log K + \log|\alpha \beta|
+  \log \left|\frac{\partial E}{\partial K}\right| = - (\beta + 1) \log K + \log|\alpha \beta|.
 \end{align*}
@@
 \end{align*}
-The process of numerically calculating the derivative can amplify the noise in the data and distorts the weights of the data points.
-Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
-Thus a second accurate nonlinear curve fit is necessary.
-
-The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
-It is necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting Eq.\ \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
-The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
-Afterward, we do a final fit with all three parameters free to vary.
-All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm \cite{10.2307/43633451,doi:10.1137/0111030} as implemented in \texttt{Minpack} \cite{More1978,More:126569}, with equal weighting of all data points.
-
-There is still one additional tuning knob for this model that is not explicitly part of Eq.\ \eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
-Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
-To account for this, we only fit the last few data points within some chosen range.
-If the range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, there would be more noise and less confidence in whether the trend is legitimate rather than accidental.
+The process of numerically calculating the derivative can amplify the
+noise in the data and distorts the weights of the data points.
+Moreover, it does not provide a means to compute $\gamma$, the
+extrapolated energy.  Thus a second accurate nonlinear curve fit is
+necessary.
+
+The parameters $\alpha$ and $\beta$ are extracted from the linear fit
+and used as inputs for a power-law fit of $E$ against $K$.  It is
+necessary to estimate the infinite-basis energy $\gamma$ as well,
+which is done by fitting Eq.\ \eqref{eq:power_law_model} while the
+parameters $\alpha$ and $\beta$ are fixed to the initial guesses.  The
+fixing ensures that the fit is still linear in nature and thus highly
+likely to converge.  Afterward, we do a final fit with all three
+parameters free to vary.  All fits are done using the traditional
+Levenberg--Marquardt (LM) optimization
+algorithm \cite{10.2307/43633451,doi:10.1137/0111030} as implemented
+in \texttt{Minpack} \cite{More1978,More:126569}, with equal weighting
+of all data points.
+
+There is still one additional tuning knob for this model that is not
+explicitly part of Eq.\ \eqref{eq:power_law_model}: the range of data
+points taken into consideration (\textit{fit range}).  Since the model
+describes the \emph{asymptotic} behavior, we do not expect the fit to
+produce good results when the energy is still very far from
+convergence.  To account for this, we only fit the last few data
+points within some chosen range.  If the range is too large, then the
+non-asymptotic behavior would perturb the result too much, whereas if
+the range is too small, there would be more noise and less confidence
+in whether the trend is legitimate rather than accidental.
 Empirically, we chose to fit the last 5 points of our available data.
-The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
-A specific example of the fit is shown in Fig.\ \ref{fig:by-fit-2-1p0-add}
-
-The LM fitting procedure also computes uncertainties for the parameters from an approximate Hessian of the model function.
-It is therefore tempting to use the uncertainty of the fit to quantify the uncertainty of the extrapolated energy.
-We certainly would not expect this to account for the error due to the operator truncation, but how accurately does it quantify the discrepancy of our extrapolated result from the true infinite-basis energy?
-
-We investigated this idea by performing a fit over \emph{all possible} 5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.
-By comparing the extrapolated results at varying values of $K_{\text{stop}}$ with the extrapolated result at the highest possible $K_{\text{stop}}$ and treating the latter as the ``true'' infinite-basis result, we can statistically assess whether the fit uncertainties are a good measure of the discrepancy from the true infinite-basis result.
-Our results show a somewhat bimodal distribution: when the relative fit uncertainty is higher than $10^{-3.5}$, the fit uncertainty quantifies the discrepancy well; otherwise, the fit uncertainty underestimates the discrepancy by a factor of 10 or less.
-
-Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
-In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
-It is likely that HF is insensitive to the Coulomb cusp.
-
-Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
-This is likely due to its rapid convergence, which leaves very little degree of freedom even for a poorly chosen model.
-Moreover, we found that the fit uncertainties of the energy are fairly good measures of the true discrepancy.
-
-Not all fits yield a positive value of $\beta$ for addition and removal energies, which suggests that the data points do not converge, or require a very high number of shells to converge.
-These cases are marked ``n.f.'' in the tables.
-This affects exclusively IM-SRG(2) + QDPT3 for systems with few particles and low frequencies, indicating that perturbation theory is inadequate for such systems.
+The results are shown in
+Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated},
+and \ref{tab:rm-extrapolated}.  A specific example of the fit is shown
+in Fig.\ \ref{fig:by-fit-2-1p0-add}
+
+The LM fitting procedure also computes uncertainties for the
+parameters from an approximate Hessian of the model function.  It is
+therefore tempting to use the uncertainty of the fit to quantify the
+uncertainty of the extrapolated energy.  We certainly would not expect
+this to account for the error due to the operator truncation, but how
+accurately does it quantify the discrepancy of our extrapolated result
+from the true infinite-basis energy?
+
+We investigated this idea by performing a fit over \emph{all possible}
+5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.  By
+comparing the extrapolated results at varying values of
+$K_{\text{stop}}$ with the extrapolated result at the highest possible
+$K_{\text{stop}}$ and treating the latter as the ``true''
+infinite-basis result, we can statistically assess whether the fit
+uncertainties are a good measure of the discrepancy from the true
+infinite-basis result.  Our results show a somewhat bimodal
+distribution: when the relative fit uncertainty is higher than
+$10^{-3.5}$, the fit uncertainty quantifies the discrepancy well;
+otherwise, the fit uncertainty underestimates the discrepancy by a
+factor of 10 or less.
+
+Unlike the other methods, Hartree--Fock energies are somewhat unusual
+in that they generally do not conform to the power-law model.  In
+fact, the results and plots seem to indicate an \emph{exponential}
+convergence with respect to the number of shells.  It is likely that
+HF is insensitive to the Coulomb cusp.
+
+Nonetheless, despite the poor fits that often arise, the extrapolated
+energies are often quite good for HF.  This is likely due to its rapid
+convergence, which leaves very little degree of freedom even for a
+poorly chosen model.  Moreover, we found that the fit uncertainties of
+the energy are fairly good measures of the true discrepancy.
+
+Not all fits yield a positive value of $\beta$ for addition and
+removal energies, which suggests that the data points do not converge,
+or require a very high number of shells to converge.  This affects
+exclusively IM-SRG(2) + QDPT3 for systems with few particles and low
+frequencies, indicating that perturbation theory is inadequate for
+such systems.
 
@@
 
-We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
-Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
+We have demonstrated calculations of ground state, addition, and
+removal energies of two-dimensional circular quantum dots using a
+variety of many-body methods: ranging from the basic Hartree-Fock
+method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or
+EOM.  Many closed-shell quantum dot systems have been explored,
+ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
 All such results show good agreement with one another.
 
-We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.
-Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
-EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
-
-There are several directions in which the calculations may be improved.
-One can attempt to improve the IM-SRG approximation by incorporating some of the missing higher-body terms in the commutator.
-This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
-While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
-
-The application of IM-SRG eliminates a large number of the QDPT diagrams of Fig.\ \ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
-Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
-Moreover, the remaining diagrams at third order can be eliminated through infinite resummation techniques, which would incorporate higher order terms and therefore further increase the accuracy of the result.
-
-We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by T.
-D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
-Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
-
-The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).
-This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.
-
-By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.
-Such interactions can be used to lower the cost of other methods such as full configuration interaction theory.
-
-Implementation-wise, our current code constructs the two-particle states as simple Slater determinants of their one-particle states.
-This approach is often referred to as \textit{m-scheme} in nuclear physics.
-It is straightforward to implement and works well for general systems, but it fails to exploit all the symmetries in the quantum dot system: not only is spin projection $\hat S_z$ conserved, the Casimir operator $\hat S^2$ is as well.
-A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
-A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
-
-We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
+We note that the HF + IM-SRG + QDPT combination provides a reasonable
+moderate-cost approach to the calculation of addition and removal
+energies for many systems in comparison to the somewhat more expensive
+and complicated EOM calculations.  Both IM-SRG and CC are reasonably
+accurate compared to the near-exact but factorial-cost FCI method,
+allowing exploration of much higher number of particles than would
+otherwise be possible.  EOM-IM-SRG does have more flexibility over
+perturbative approaches: in particular, it could be more readily used
+to construct excited states \cite{2016arXiv161100661P}, which is more
+difficult for methods such as DMC.
+
+There are several directions in which the calculations may be
+improved.  One can attempt to improve the IM-SRG approximation by
+incorporating some of the missing higher-body terms in the commutator.
+This would also provide some insight into the rate of convergence with
+respect to the operator truncation, providing a sense of how large the
+truncation error is.  While a full 3-body treatment of IM-SRG would be
+extremely costly, it is possible implicitly track for a portion of the
+induced 3-body forces by computing certain diagrams that are either
+lower cost or could be approximated at lower cost \cite{IMSRG}.
+
+The application of IM-SRG eliminates a large number of the QDPT
+diagrams of Fig.\ \ref{fig:diagrams-sfe}, which is beneficial as it
+increases the efficiency of the QDPT calculations.  Thus it may be
+more feasible to perform higher orders of QDPT on IM-SRG evolved
+Hamiltonians.  Moreover, the remaining diagrams at third order can be
+eliminated through infinite resummation techniques, which would
+incorporate higher order terms and therefore further increase the
+accuracy of the result.
+
+We note that this calculation was done entirely using the traditional
+approach of using a high-order ODE solver to solve the flow equation.
+A new technique developed by T. D. Morris \cite{PhysRevC.92.034331}
+uses an alternative approach that obviates the need for a high-order
+ODE solver, leading to much more efficient computations and also
+allowing operators of other observables to be evolved at lower cost,
+which poses a significant advantage over coupled cluster methods.
+Implementing this approach would allows us to study the accuracy and
+convergence of other possibly more sensitive observables.
+
+The IM-SRG method can be extended to support multiple reference states
+(multi-reference IM-SRG or simply
+MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through
+the generalized normal ordering
+formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of
+calculating quantum systems that are far from the magic numbers
+(open-shell systems).  This is a territory that few many-body methods
+can tackle and is one of the major strengths of the IM-SRG approach.
+
+By transforming of the operator-SRG rather than the wave function,
+IM-SRG is more amenable to the construction of
+softened \textit{effective interactions} than
+CC \cite{Hergert2016165}.  Such interactions can be used to lower the
+cost of other methods such as full configuration interaction theory.
+
+Implementation-wise, our current code constructs the two-particle
+states as simple Slater determinants of their one-particle states.
+This approach is often referred to as \textit{m-scheme} in nuclear
+physics.  It is straightforward to implement and works well for
+general systems, but it fails to exploit all the symmetries in the
+quantum dot system: not only is spin projection $\hat S_z$ conserved,
+the Casimir operator $\hat S^2$ is as well.  A more efficient approach
+is to couple the spins of the single-particle states to form
+two-particle states with good $\hat S^2$, an approach analogous
+to \textit{j-scheme} in nuclear physics.  A combination of this with
+the Eckart-Wigner theorem could reduce the computational cost
+significantly, albeit at the cost of increased implementation
+complexity.
+
+We hope to apply these theoretical and technical enhancements not only
+to the study of quantum dots, but to studies of nuclear and atomic
+systems, opening up an even greater range of applications.
 
 \begin{acknowledgments}
-  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University).
+  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University). Discussions with Simen Kvaal are highly appreciated.
 \end{acknowledgments}

### 2017-06-14 Manuscript/paper.tex
Unwrap paragraphs
Remove reference to b-hat

@@
 \begin{abstract}
-  We present and compare several many-body methods as applied to
-  two-dimensional quantum dots with circular symmetry.  We calculate
-  the approximate ground state energy using a harmonic oscillator
-  basis optimized by Hartree--Fock (HF) theory and further improve the
-  ground state energy using two post-HF methods: in-medium similarity
-  renormalization group (IM-SRG) and coupled cluster
-  singles-and-doubles (CCSD).  With the application of quasidegenerate
-  perturbation theory (QDPT) or the equation-of-motion (EOM) method,
-  we obtain addition and removal energies as well.  Our results are
-  benchmarked against full configuration interaction (FCI) and
-  diffusion Monte Carlo (DMC) where available.  We examine the rate of
-  convergence and perform extrapolations to the infinite basis limit
-  using a power-law model.
+  We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
+We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
+With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
+Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
+We examine the rate of convergence and perform extrapolations to the infinite basis limit using a power-law model.
 \end{abstract}
@@
 
-The behavior of strongly confined electrons is of fundamental concern
-to many-body theory.  The prototypical system is that of quantum dots,
-also known as ``artificial atoms'', in which electrons are confined
-within artificially constructed semiconducting heterostructures.  Such
-nanoscale systems are highly relevant as they lie at a critical point
-where both theoretical models and experimental observations can
-readily probe quantum phenomena such as tunneling, entanglement, and
-magnetization \cite{reimann2002,engel1993}.  Moreover, unlike many
-physical systems, quantum dots enjoy the benefit of being highly
-tunable through changes in the external field or the structure of the
-confining material.  This allows experiments to quantify the impact of
-quantum effects at different levels of correlation.
-
-The ground states of quantum dots exhibit shell structures and magic
-numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, they provide a rare opportunity to study electronic systems
-without the influence of the atomic nuclei.  They also provide a
-testbed for the development of many-body methods for other systems
-with similar geometry, such as nuclei or neutrons
-drops \cite{PhysRevC.84.044306}.
-
-Beyond their theoretical relevance, there are numerous potential
-applications of quantum dots.  The electrical and optical properties
-of quantum dots are particularly useful for solar
-cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser
-technology \cite{strauf2010,5075760}.  They have potential medical
-applications in diagnosis and treatment \cite{Ben-Ari02042003}.  And
-of course, quantum dots are also promising candidates for the physical
-realization of quantum computing \cite{PhysRevA.57.120}.
-
-In general, quantum dot systems are not analytically solvable, with
-the exception of two-electron systems or systems with specific
-strengths of the external field \cite{PhysRevA.48.3561}.  Hence, in
-practical applications one can only hope for a numerical solution
-through some \textit{many-body method} or a combination thereof.
-
-One of the most accurate techniques for solving many-body systems is
-that of exact diagonalization, also known as the full configuration
-interaction method.  Unlike most methods, it is assured to converge to
-the exact answer as the size of the finite basis is increased to
-infinity (the so-called \textit{infinite-basis limit}).  Despite this
-significant advantage, it is often not possible to perform exact
-diagonalization due to its factorially increasing cost with respect to
-the basis size and the number of particles.  This led to the
-development of more cost-effective methods that trade varying amounts
-of accuracy for varying amounts of speed.
-
-In this paper, we analyze the application of several methods to the
-quantum dot systems, including the Hartree--Fock (HF) method, M\o
-ller-Plesset perturbation theory (MP), the in-medium similarity
-renormalization group (IM-SRG) method, coupled cluster (CC)
-theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302},
-quasidegenerate perturbation theory (QDPT), and equation-of-motion
-(EOM) methods.  We compare them against variational and diffusion
-Monte Carlo (VMC and
-DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780}
-and full configuration interaction (FCI)
-theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102}
-results, where available, from the existing literature.
-
-Of these methods, IM-SRG is a recently developed technique that has
-shown significant promises.  Similarity renormalization group (SRG)
-methods are a family of methods that transform the Hamiltonian into a
-band- or block-diagonal form through a continuous sequence of unitary
-transformations.  The goal of such a transformation is to reduce the
-coupling between a subspace of interest -- such as the ground state or
-a set of low-lying states -- and the remaining Hilbert space.  It has
-successfully been applied to systems with various underlying
-potentials to calculate their binding energy and other observables,
-especially in nuclear
-theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
-The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method
-to evolve Hamiltonians in a truncated Fock space, which avoids the
-prohibitive cost of constructing a full many-body Hamiltonian.  The
-effect of the truncation is minimized through the normal-ordering
-technique, which re-expands the operators with respect to a nearby
-many-body reference state rather than the far-away vacuum state.
-
-The article is organized as follows: Section \ref{sec:formalism}
-introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we
-use to model circular quantum dots, and gives afterwards an overview
-of the \textit{ab initio} many-body methods used in this paper:
-Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.  Our results are presented in
-Section \ref{sec:results}.  We analyze and compare the differences
-between the various methods and also between different quantum dot
-systems.  We examine the usefulness of extrapolation techniques in
-improving the precision of the results.  Section \ref{sec:conclusions}
-concludes our work and gives perspectives for future work.
+The behavior of strongly confined electrons is of fundamental concern to many-body theory.
+The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
+Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
+Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
+This allows experiments to quantify the impact of quantum effects at different levels of correlation.
+
+The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
+Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
+They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{PhysRevC.84.044306}.
+
+Beyond their theoretical relevance, there are numerous potential applications of quantum dots.
+The electrical and optical properties of quantum dots are particularly useful for solar cells \cite{jenks:013111,doi:10.1021/cr900289f} and laser technology \cite{strauf2010,5075760}.
+They have potential medical applications in diagnosis and treatment \cite{Ben-Ari02042003}.
+And of course, quantum dots are also promising candidates for the physical realization of quantum computing \cite{PhysRevA.57.120}.
+
+In general, quantum dot systems are not analytically solvable, with the exception of two-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
+Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
+
+One of the most accurate techniques for solving many-body systems is that of exact diagonalization, also known as the full configuration interaction method.
+Unlike most methods, it is assured to converge to the exact answer as the size of the finite basis is increased to infinity (the so-called \textit{infinite-basis limit}).
+Despite this significant advantage, it is often not possible to perform exact diagonalization due to its factorially increasing cost with respect to the basis size and the number of particles.
+This led to the development of more cost-effective methods that trade varying amounts of accuracy for varying amounts of speed.
+
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
+We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
+
+Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
+Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
+The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
+It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
+The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
+The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
+
+The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
+Our results are presented in Section \ref{sec:results}.
+We analyze and compare the differences between the various methods and also between different quantum dot systems.
+We examine the usefulness of extrapolation techniques in improving the precision of the results.
+Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
 
@@
 
-We shall model the circular quantum dot system as a collection of $N$
-nonrelativistic electrons of mass $m$ in two-dimensional space,
-trapped by an external harmonic-oscillator potential of the form
-$m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the
-oscillator trap and $r$ is the distance from the center of the trap.
-The electrons interact with each other through the standard Coulomb
-interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of
-each electron, $\epsilon$ is the permittivity of the medium, and $R$
-is the distance between the two interacting electrons.
-
-Even though the model system contains five parameters $(N, m, \omega,
-e, \epsilon)$, many of them are redundant.  With an appropriate choice
-of units, the number of parameters in the system can be reduced to
-just two.  For rest of this paper, we shall use atomic units where
-$\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.  The unit
-Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr
-radius $a$ becomes the unit of length:
+We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
+The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
+
+Even though the model system contains five parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
+With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
+For rest of this paper, we shall use atomic units where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
+The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
 \begin{align*}
@@
 \end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th
-particle,\footnote{The ordering of the particle labels $j$ is
-unimportant as they exist only for the purpose of bookkeeping.} and
-$\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its
-momentum operator.
+The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
 
@@
 
-The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$
-can be reduced to $N$ independent single-particle Hamiltonians each of
-the form:
+The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
 \begin{align*}
@@
 \end{align*}
-where $p$ is an unknown tuple of quantum numbers.  In Cartesian
-coordinates, the two-dimensional harmonic oscillator is trivially
-reducible to the well-known one-dimensional problem.  However, to
-exploit the circular symmetry, we prefer to use Fock-Darwin states,
-which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving
-orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv
--\mathrm{i} \frac{\partial}{\partial \varphi}$.
+where $p$ is an unknown tuple of quantum numbers.
+In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
+However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
 
@@
 \end{align*}
-The states are labeled by two quantum numbers: the principal quantum
-number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum
-projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
-For a wave function, $n$ indicates the degree of the Laguerre
-polynomial, whereas $m_\ell$ is simply the eigenvalue of
-$\hat{L}_{\mathrm{z}}$.
-
-Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy
-either of the two possible spin states $\chi_{-\frac{1}{2}}$ or
-$\chi_{+\frac{1}{2}}$.  Thus, every single-particle basis state $|n
-m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial
-component \eqref{eq:fockdarwin} and a spin component,
+The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
+For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
+
+Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy either of the two possible spin states $\chi_{-\frac{1}{2}}$ or $\chi_{+\frac{1}{2}}$.
+Thus, every single-particle basis state $|n m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
 \begin{align} \label{eq:singleparticlestate}
@@
 \end{align}
-Here we have introduced spin projection
-$m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the
-third quantum number and $\delta_{p q}$ to denote the Kronecker
-delta.
+Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the third quantum number and $\delta_{p q}$ to denote the Kronecker delta.
 
@@
 \end{align}
-which we conveniently call the \textit{shell index} as it labels each
-shell starting from zero.  The shells are equidistant with an energy
-spacing equal to the frequency $\omega$.
-
-Returning to the one-body part of the many-body Hamiltonian,
-$\hat{H}^{[1]}$, we can use the Slater determinant construction to
-build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the
-many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$
-single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$
-from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for
-the triplet $(n, m_\ell, m_{\mathrm{s}})$.  Note that a Slater
-determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the
-single-particle states, but an antisymmetrized sum over all possible
-products,
+which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
+
+Returning to the one-body part of the many-body Hamiltonian, $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
+Note that a Slater determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
 \begin{align*}
@@
 \end{align*}
-The Slater determinant $|p_1 \ldots p_N\rangle$ is said
-to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.  By
-construction, Slater determinants satisfy the Pauli exclusion
-principle, ensuring that the exchange of any two particles is
-equivalent to a reversal in the sign of the many-body wave function.
+The Slater determinant $|p_1 \ldots p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
+By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
 
@@
 \end{align*}
-It is possible for Slater determinants occupying different sets of
-single-particle states to be degenerate in energy.  This is possible
-even for ground states of $\hat{H}^{[1]}$.  However, if the number of
-particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for
-some nonnegative integer $K_{\mathrm{F}}$, there would be just enough
-particles to form a closed-shell Slater determinant, leading to a
-unique, well-isolated ground state.  The values of $N$ at which this
-occurs are said to be \textit{magic numbers}.  We call
-$K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi
-level'').  In particular, a single-particle state is occupied in the
-ground state Slater determinant if and only $k < K_{\mathrm{F}}$,
-where $k$ is the shell index of the single-particle state as defined
-in \eqref{eq:shell_index}.
-
-In this paper, we use the letters $p, q, r, s, \ldots$ to label
-arbitrary \textit{single-particle states} in the basis.  In the
-discussion of many-body methods that rely a single, distinguished
-Slater determinant $\Phi$, known as the \textit{reference state}, we
-use the letters $i, j, k, l, \ldots$ as placeholders for the occupied
-states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
-A summation such as $\sum_p$ is understood as a summation over every
-single-particle basis state $p$.  In contrast, $\sum_i$ only sums over
-those that are occupied and $\sum_a$ only sums over those that are
-unoccupied.
-
-We will describe many-body methods within the formalism of second
-quantization; see for example Ref.\ \cite{shavitt2009many}.  To
-properly describe fermions, we introduce the annihilation and creation
-operators $\hat a_p$ and $\hat a_p^\dagger$. These operators must
-satisfy the anticommutation relations that encode the Pauli principle,
-namely
+It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
+This is possible even for ground states of $\hat{H}^{[1]}$.
+However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
+The values of $N$ at which this occurs are said to be \textit{magic numbers}.
+We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
+In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
+
+In this paper, we use the letters $p, q, r, s, \ldots$ to label arbitrary \textit{single-particle states} in the basis.
+In the discussion of many-body methods that rely a single, distinguished Slater determinant $\Phi$, known as the \textit{reference state}, we use the letters $i, j, k, l, \ldots$ as placeholders for the occupied states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
+A summation such as $\sum_p$ is understood as a summation over every single-particle basis state $p$.
+In contrast, $\sum_i$ only sums over those that are occupied and $\sum_a$ only sums over those that are unoccupied.
+
+We will describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
+To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
+These operators must satisfy the anticommutation relations that encode the Pauli principle, namely
 \begin{align*}
@@
 \end{align}
-Due to the antisymmetry of Slater determinants, we have the property
-that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign
-of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a four-fold
-symmetry that must be canceled out by the $1/4$ factor in front of the
-summation in \eqref{eq:vacuumhamiltonian}.  For this reason, the
-two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is
-commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the (non-antisymmetric) interaction
-integral,
+Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a four-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
+For this reason, the two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
+This is not to be confused with the (non-antisymmetric) interaction integral,
 \begin{align} \label{eq:interactionintegral}
@@
 
-With the basic formalism and notation established along with the
-system of interest, we may begin to discuss the various techniques to
-solve the full many-body problem.  The principal difficulty stems from
-the fact that, due to the presence of interactions, the exact solution
-is in general \emph{not} a single Slater determinant built from the
-single-particle states.  Hence, it is not possible to trivially reduce
-the problem to that of a single particle as we had done previously.
-
-However, if we assume the interaction alters the behavior of the
-system only mildly, we can use a Slater determinant of the
-noninteracting system as a starting point and then apply various
-methods to improve the accuracy of the solution.  This is a general
-strategy for many of the many-body methods that we shall describe.
+With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
+The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
+Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
+
+However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
+This is a general strategy for many of the many-body methods that we shall describe.
 
@@
 \end{align}
-with respect to $|\Phi\rangle$, subject to the restriction that
-$|\Phi\rangle$ remains a single Slater determinant constructed from an
-unknown single-particle basis.  The restriction is what enables the
-simplicity and efficiency of this method.  We shall denote each
-unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To perform numerical calculations, we further assume that each unknown
-state $|q'\rangle$ is built from a linear combination of known states
-$|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined
-via the transformation equation
+with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
+The restriction is what enables the simplicity and efficiency of this method.
+We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
+
+To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
 \begin{align*}
@@
 \end{align*}
-This allows the problem to be reduced from an abstract minimization
-problem \eqref{eq:hfexpectation} to a concrete numerical problem.  The
-caveat is that the set of known functions be large enough to capture
-the relevant behavior of the system.
-
-If the interaction is not too strong, it is common to use the
-single-particle states of the noninteracting Hamiltonian
-$\hat{H}^{[1]}$ as the set of known states.
-
-To ensure orthonormality of the states, we require there to be as many
-unknown states $|q'\rangle$ as known states $|p\rangle$, and the
-coefficient matrix $\bm C$ must be unitary.  These conditions are more
-strict than necessary, but they greatly simplify the calculations and
-allow the states $|q'\rangle$ to act as \textit{optimized} inputs for
-methods beyond HF.  At the end of the calculation, of the set of
-states $|q'\rangle$ there would exactly $N$ \textit{occupied} states
-that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary
-space into which particles can be excited by the interaction
-$\hat{H}^{[2]}$ during the post-HF calculation.
+This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
+The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
+
+If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
+
+To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
+These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
+At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
+The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
 
@@
 
-The power of SRG methods lies in the flexibility of the generator
-$\hat{\eta}$, which is usually chosen in an $s$-dependent manner.  In
-particular, it is often dependent on the evolving Hamiltonian
-$\hat{H}(s)$.  The operator $\hat{\eta}$ determines which parts of the
-Hamiltonian matrix would become suppressed by the evolution, which are
-usually considered ``off-diagonal'' in an abstract sense.  The
-``off-diagonal'' parts could be elements far away from the matrix
-diagonal, in which case the evolution drives the matrix towards a
-band-diagonal form.  Or, the ``off-diagonal'' parts could be elements
-that couple the ground state from the excited state, in which case the
-evolution drives the matrix towards a block-diagonal form that
-isolates the ground state.  Or, the ``off-diagonal'' could be
-literally the elements that do not lie on the diagonal, in which case
-the evolution would simply diagonalize the Hamiltonian.  Through
-different choices of $\hat{\eta}$, the SRG evolution can be controlled
-and adapted to the features of a particular problem.
+The power of SRG methods lies in the flexibility of the generator $\hat{\eta}$, which is usually chosen in an $s$-dependent manner.
+In particular, it is often dependent on the evolving Hamiltonian $\hat{H}(s)$.
+The operator $\hat{\eta}$ determines which parts of the Hamiltonian matrix would become suppressed by the evolution, which are usually considered ``off-diagonal'' in an abstract sense.
+The ``off-diagonal'' parts could be elements far away from the matrix diagonal, in which case the evolution drives the matrix towards a band-diagonal form.
+Or, the ``off-diagonal'' parts could be elements that couple the ground state from the excited state, in which case the evolution drives the matrix towards a block-diagonal form that isolates the ground state.
+Or, the ``off-diagonal'' could be literally the elements that do not lie on the diagonal, in which case the evolution would simply diagonalize the Hamiltonian.
+Through different choices of $\hat{\eta}$, the SRG evolution can be controlled and adapted to the features of a particular problem.
 
@@
 
-The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the
-second quantization formalism described in
-Section \ref{subsec:modelHamiltonian}, where field operators are
-defined with respect to the physical vacuum state.  However, since the
-basis of a many-body problem grows factorially with the number of
-particles and the size of the model space, the applicability of the
-naive (free-space) SRG method is restricted to comparatively small
-systems.  A more practical approach is to perform the
-evolution \textit{in medium}, i.e.\ using a many-body Slater
-determinant as a reference \cite{kehrein2006flow}.  This gives rise to
-the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
+The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
+However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
+A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.
+This gives rise to the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
 
@@
 \end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is
-simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix
-$F_{p q}$.  The operator $\hat H$ in
-Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat
-H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.  The only difference is that
-the meaning of a ``$k$-body operator'' has been redefined with respect
-to the reference state $\Phi$ rather than the vacuum state $\ket{}$,
-causing matrix elements to be reshuffled among the $k$-body operators.
-Where this makes a critical difference is when the operator
-expressions are \emph{truncated}, i.e.\ some $k$-body operators may be
-discarded from the computation for efficiency reasons.
-Normal-ordering can drastically alter the importance of the $k$-body
-operators with respect to each other.
-
-Higher-body operators arise from integrating the flow equations of Eq.~(\ref{eq:imsrgode}), 
-which is one of the major challenges of the SRG
-method.  With each evaluation of the commutator, the Hamiltonian gains
-terms of higher order, and these induced contributions will in
-subsequent integration steps feed back into terms of lower order.
-Thus, the higher-body contributions are not irrelevant to the final
-solution even if only the ground state energy (zero-body component) is
-of interest.
-
-Computationally, higher-body terms rapidly become unfeasible to
-handle: the amount of memory required to store a $k$-body operator is
-grows exponentially with $k$.  Moreover, the flow equations are
-capable of generating an infinite number of higher-body terms as the
-Hamiltonian evolves.  Thus, to make the method tractable, the IM-SRG
-flow equations must be closed by truncating the equations to a finite
-order.
-
-In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the
-two-body level, leading to an approach known as IM-SRG(2).  This
-normal-ordered two-body approximation appears to be sufficient in many
-cases and has yielded excellent results for several
-nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
-
-Note that the loss of three- and higher-body terms (\textit{operator
-truncation}) is only one out of the two sources of error in this
-method.  The other source of error is due to the \textit{basis
-truncation}, a concern for any method that relies on a finite
-single-particle basis such as IM-SRG.  The latter can be reduced by
-increasing the size of the basis at the expense of greater
-computational effort, albeit the cost increases much less rapidly in
-this direction.  In IM-SRG the CPU cost is polynomial with respect to
-$N_{\mathrm{b}}$, the number of states in the single-particle basis.
-For IM-SRG(2) in particular, the CPU cost scales roughly as
-$\mathcal{O}(N_{\mathrm{b}}^6)$.
+If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix $F_{p q}$.
+The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
+The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than the vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
+Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
+Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
+
+Higher-body operators arise from integrating the flow equations of Eq.~(\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
+With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
+Thus, the higher-body contributions are not irrelevant to the final solution even if only the ground state energy (zero-body component) is of interest.
+
+Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
+Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
+Thus, to make the method tractable, the IM-SRG flow equations must be closed by truncating the equations to a finite order.
+
+In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
+This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+
+Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
+The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
+The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
+In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
+For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
 
@@
 
-Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian
-operators, it is antihermitian as required for a generator.
-Additionally, it can be shown that the commutator has the property of
-suppressing off-diagonal matrix elements as the state evolves via the
-flow equation \cite{kehrein2006flow}, as we would like.  Matrix
-elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian
-couples states with large energy differences -- are suppressed much
-faster than those ``close'' to the diagonal.
-
-Apart from Wegner's generator, there exist several other ones in
-literature. One choice, proposed by
-White \cite{White:cond-mat0201346}, makes numerical approaches much
-more efficient.  The problem with the Wegner generator is the widely
-varying decaying speeds of the Hamiltonian matrix elements.  Terms
-with large energy separations from the ground state are suppressed
-initially, followed by those with smaller energy separations.  This
-leads to stiffness in the flow equation, leading to numerical
-difficulties in solving the set of coupled differential equations.
-
-The White generator takes an alternative approach, which is well
-suited for problems where one is mainly interested in the ground state
-of a system.  Firstly, instead of driving all off-diagonal elements of
-the Hamiltonian to zero, the generator focuses exclusively on those
-ones that are coupled to the reference state $\Phi$ so as to decouple
-the reference state from the remaining Hamiltonian.  This reduces the
-amount of change done to the Hamiltonian, reducing the accuracy lost
-from the operator truncation.  Secondly, the rate of decay in
-Hamiltonian matrix elements are approximately normalized by dividing
-the generator matrix elements by an appropriate factor.  This ensures
-that the affected elements decay at approximately the same rate,
-reducing the stiffness of the flow equations.
+Since $\hat{\eta}^{\text{Wg}}$ is a commutator between two Hermitian operators, it is antihermitian as required for a generator.
+Additionally, it can be shown that the commutator has the property of suppressing off-diagonal matrix elements as the state evolves via the flow equation \cite{kehrein2006flow}, as we would like.
+Matrix elements ``far'' from the diagonal -- i.e.\ where the Hamiltonian couples states with large energy differences -- are suppressed much faster than those ``close'' to the diagonal.
+
+Apart from Wegner's generator, there exist several other ones in literature.
+One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
+The problem with the Wegner generator is the widely varying decaying speeds of the Hamiltonian matrix elements.
+Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
+This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
+
+The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
+Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
+This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
+Secondly, the rate of decay in Hamiltonian matrix elements are approximately normalized by dividing the generator matrix elements by an appropriate factor.
+This ensures that the affected elements decay at approximately the same rate, reducing the stiffness of the flow equations.
 
@@
 \end{align}
-where $i$ is restricted to labels of occupied states, $a$ is restricted to labels of unoccupied states, and $|\Phi_p\rangle \equiv \hat b_p |\Phi\rangle$.
+where $i$ is restricted to labels of occupied states, $a$ is restricted to labels of unoccupied states, $|\Phi_i\rangle \equiv \hat{a}_i^{} |\Phi\rangle$, and $|\Phi_a\rangle \equiv \hat{a}_a^\dagger |\Phi\rangle$.
 
@@
 
-The addition and removal energies are similar, but they require an
-additional parameter: the total orbital angular momentum $M_\ell$,
-defined as the sum of the $m_\ell$ of each particle.  This is due to
-the presence of multiple states with near-degenerate energies.  For
-this paper, we will consider exclusively the addition/removal energies
-with the lowest $|M_\ell|$ subject to the constraint that the particle
-added/removed lies within the next/last shell.  This means the $N + 1$
-states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$
-(where $\bmod$ stands for the modulo operation) where $K_{\mathrm{F}}$
-is the number of occupied shells, while the $N - 1$ states of interest
-are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
+The addition and removal energies are similar, but they require an additional parameter: the total orbital angular momentum $M_\ell$, defined as the sum of the $m_\ell$ of each particle.
+This is due to the presence of multiple states with near-degenerate energies.
+For this paper, we will consider exclusively the addition/removal energies with the lowest $|M_\ell|$ subject to the constraint that the particle added/removed lies within the next/last shell.
+This means the $N + 1$ states of interest are those with $|M_\ell| = K_{\mathrm{F}} \bmod 2$ (where $\bmod$ stands for the modulo operation) where $K_{\mathrm{F}}$ is the number of occupied shells, while the $N - 1$ states of interest are those with $|M_\ell| = 1 - (K_{\mathrm{F}} \bmod 2)$.
 
@@
 
-Numerical calculations in this paper are performed with a relative
-precision of about $10^{-5}$ or lower.  This does not necessarily mean
-the results are as precise as $10^{-5}$, since numerical errors tend
-to accumulate over the multiple steps of the calculation, thus the
-precision of the final results is expected to be roughly $10^{-4}$.
+Numerical calculations in this paper are performed with a relative precision of about $10^{-5}$ or lower.
+This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate over the multiple steps of the calculation, thus the precision of the final results is expected to be roughly $10^{-4}$.
 
@@
 \end{align*}
-The process of numerically calculating the derivative can amplify the
-noise in the data and distorts the weights of the data points.
-Moreover, it does not provide a means to compute $\gamma$, the
-extrapolated energy.  Thus a second accurate nonlinear curve fit is
-necessary.
-
-The parameters $\alpha$ and $\beta$ are extracted from the linear fit
-and used as inputs for a power-law fit of $E$ against $K$.  It is
-necessary to estimate the infinite-basis energy $\gamma$ as well,
-which is done by fitting Eq.\ \eqref{eq:power_law_model} while the
-parameters $\alpha$ and $\beta$ are fixed to the initial guesses.  The
-fixing ensures that the fit is still linear in nature and thus highly
-likely to converge.  Afterward, we do a final fit with all three
-parameters free to vary.  All fits are done using the traditional
-Levenberg--Marquardt (LM) optimization
-algorithm \cite{10.2307/43633451,doi:10.1137/0111030} as implemented
-in \texttt{Minpack} \cite{More1978,More:126569}, with equal weighting
-of all data points.
-
-There is still one additional tuning knob for this model that is not
-explicitly part of Eq.\ \eqref{eq:power_law_model}: the range of data
-points taken into consideration (\textit{fit range}).  Since the model
-describes the \emph{asymptotic} behavior, we do not expect the fit to
-produce good results when the energy is still very far from
-convergence.  To account for this, we only fit the last few data
-points within some chosen range.  If the range is too large, then the
-non-asymptotic behavior would perturb the result too much, whereas if
-the range is too small, there would be more noise and less confidence
-in whether the trend is legitimate rather than accidental.
+The process of numerically calculating the derivative can amplify the noise in the data and distorts the weights of the data points.
+Moreover, it does not provide a means to compute $\gamma$, the extrapolated energy.
+Thus a second accurate nonlinear curve fit is necessary.
+
+The parameters $\alpha$ and $\beta$ are extracted from the linear fit and used as inputs for a power-law fit of $E$ against $K$.
+It is necessary to estimate the infinite-basis energy $\gamma$ as well, which is done by fitting Eq.\ \eqref{eq:power_law_model} while the parameters $\alpha$ and $\beta$ are fixed to the initial guesses.
+The fixing ensures that the fit is still linear in nature and thus highly likely to converge.
+Afterward, we do a final fit with all three parameters free to vary.
+All fits are done using the traditional Levenberg--Marquardt (LM) optimization algorithm \cite{10.2307/43633451,doi:10.1137/0111030} as implemented in \texttt{Minpack} \cite{More1978,More:126569}, with equal weighting of all data points.
+
+There is still one additional tuning knob for this model that is not explicitly part of Eq.\ \eqref{eq:power_law_model}: the range of data points taken into consideration (\textit{fit range}).
+Since the model describes the \emph{asymptotic} behavior, we do not expect the fit to produce good results when the energy is still very far from convergence.
+To account for this, we only fit the last few data points within some chosen range.
+If the range is too large, then the non-asymptotic behavior would perturb the result too much, whereas if the range is too small, there would be more noise and less confidence in whether the trend is legitimate rather than accidental.
 Empirically, we chose to fit the last 5 points of our available data.
-The results are shown in
-Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated},
-and \ref{tab:rm-extrapolated}.  A specific example of the fit is shown
-in Fig.\ \ref{fig:by-fit-2-1p0-add}
-
-The LM fitting procedure also computes uncertainties for the
-parameters from an approximate Hessian of the model function.  It is
-therefore tempting to use the uncertainty of the fit to quantify the
-uncertainty of the extrapolated energy.  We certainly would not expect
-this to account for the error due to the operator truncation, but how
-accurately does it quantify the discrepancy of our extrapolated result
-from the true infinite-basis energy?
-
-We investigated this idea by performing a fit over \emph{all possible}
-5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.  By
-comparing the extrapolated results at varying values of
-$K_{\text{stop}}$ with the extrapolated result at the highest possible
-$K_{\text{stop}}$ and treating the latter as the ``true''
-infinite-basis result, we can statistically assess whether the fit
-uncertainties are a good measure of the discrepancy from the true
-infinite-basis result.  Our results show a somewhat bimodal
-distribution: when the relative fit uncertainty is higher than
-$10^{-3.5}$, the fit uncertainty quantifies the discrepancy well;
-otherwise, the fit uncertainty underestimates the discrepancy by a
-factor of 10 or less.
-
-Unlike the other methods, Hartree--Fock energies are somewhat unusual
-in that they generally do not conform to the power-law model.  In
-fact, the results and plots seem to indicate an \emph{exponential}
-convergence with respect to the number of shells.  It is likely that
-HF is insensitive to the Coulomb cusp.
-
-Nonetheless, despite the poor fits that often arise, the extrapolated
-energies are often quite good for HF.  This is likely due to its rapid
-convergence, which leaves very little degree of freedom even for a
-poorly chosen model.  Moreover, we found that the fit uncertainties of
-the energy are fairly good measures of the true discrepancy.
-
-Not all fits yield a positive value of $\beta$ for addition and
-removal energies, which suggests that the data points do not converge,
-or require a very high number of shells to converge.  This affects
-exclusively IM-SRG(2) + QDPT3 for systems with few particles and low
-frequencies, indicating that perturbation theory is inadequate for
-such systems.
+The results are shown in Tables \ref{tab:ground-extrapolated}, \ref{tab:add-extrapolated}, and \ref{tab:rm-extrapolated}.
+A specific example of the fit is shown in Fig.\ \ref{fig:by-fit-2-1p0-add}
+
+The LM fitting procedure also computes uncertainties for the parameters from an approximate Hessian of the model function.
+It is therefore tempting to use the uncertainty of the fit to quantify the uncertainty of the extrapolated energy.
+We certainly would not expect this to account for the error due to the operator truncation, but how accurately does it quantify the discrepancy of our extrapolated result from the true infinite-basis energy?
+
+We investigated this idea by performing a fit over \emph{all possible} 5-point fit ranges $[K_{\text{stop}} - 4, K_{\text{stop}}]$.
+By comparing the extrapolated results at varying values of $K_{\text{stop}}$ with the extrapolated result at the highest possible $K_{\text{stop}}$ and treating the latter as the ``true'' infinite-basis result, we can statistically assess whether the fit uncertainties are a good measure of the discrepancy from the true infinite-basis result.
+Our results show a somewhat bimodal distribution: when the relative fit uncertainty is higher than $10^{-3.5}$, the fit uncertainty quantifies the discrepancy well; otherwise, the fit uncertainty underestimates the discrepancy by a factor of 10 or less.
+
+Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
+In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
+It is likely that HF is insensitive to the Coulomb cusp.
+
+Nonetheless, despite the poor fits that often arise, the extrapolated energies are often quite good for HF.
+This is likely due to its rapid convergence, which leaves very little degree of freedom even for a poorly chosen model.
+Moreover, we found that the fit uncertainties of the energy are fairly good measures of the true discrepancy.
+
+Not all fits yield a positive value of $\beta$ for addition and removal energies, which suggests that the data points do not converge, or require a very high number of shells to converge.
+This affects exclusively IM-SRG(2) + QDPT3 for systems with few particles and low frequencies, indicating that perturbation theory is inadequate for such systems.
 
@@
 
-We have demonstrated calculations of ground state, addition, and
-removal energies of two-dimensional circular quantum dots using a
-variety of many-body methods: ranging from the basic Hartree-Fock
-method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or
-EOM.  Many closed-shell quantum dot systems have been explored,
-ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
+We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
+Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
 All such results show good agreement with one another.
 
-We note that the HF + IM-SRG + QDPT combination provides a reasonable
-moderate-cost approach to the calculation of addition and removal
-energies for many systems in comparison to the somewhat more expensive
-and complicated EOM calculations.  Both IM-SRG and CC are reasonably
-accurate compared to the near-exact but factorial-cost FCI method,
-allowing exploration of much higher number of particles than would
-otherwise be possible.  EOM-IM-SRG does have more flexibility over
-perturbative approaches: in particular, it could be more readily used
-to construct excited states \cite{2016arXiv161100661P}, which is more
-difficult for methods such as DMC.
-
-There are several directions in which the calculations may be
-improved.  One can attempt to improve the IM-SRG approximation by
-incorporating some of the missing higher-body terms in the commutator.
-This would also provide some insight into the rate of convergence with
-respect to the operator truncation, providing a sense of how large the
-truncation error is.  While a full 3-body treatment of IM-SRG would be
-extremely costly, it is possible implicitly track for a portion of the
-induced 3-body forces by computing certain diagrams that are either
-lower cost or could be approximated at lower cost \cite{IMSRG}.
-
-The application of IM-SRG eliminates a large number of the QDPT
-diagrams of Fig.\ \ref{fig:diagrams-sfe}, which is beneficial as it
-increases the efficiency of the QDPT calculations.  Thus it may be
-more feasible to perform higher orders of QDPT on IM-SRG evolved
-Hamiltonians.  Moreover, the remaining diagrams at third order can be
-eliminated through infinite resummation techniques, which would
-incorporate higher order terms and therefore further increase the
-accuracy of the result.
-
-We note that this calculation was done entirely using the traditional
-approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by T. D. Morris \cite{PhysRevC.92.034331}
-uses an alternative approach that obviates the need for a high-order
-ODE solver, leading to much more efficient computations and also
-allowing operators of other observables to be evolved at lower cost,
-which poses a significant advantage over coupled cluster methods.
-Implementing this approach would allows us to study the accuracy and
-convergence of other possibly more sensitive observables.
-
-The IM-SRG method can be extended to support multiple reference states
-(multi-reference IM-SRG or simply
-MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through
-the generalized normal ordering
-formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of
-calculating quantum systems that are far from the magic numbers
-(open-shell systems).  This is a territory that few many-body methods
-can tackle and is one of the major strengths of the IM-SRG approach.
-
-By transforming of the operator-SRG rather than the wave function,
-IM-SRG is more amenable to the construction of
-softened \textit{effective interactions} than
-CC \cite{Hergert2016165}.  Such interactions can be used to lower the
-cost of other methods such as full configuration interaction theory.
-
-Implementation-wise, our current code constructs the two-particle
-states as simple Slater determinants of their one-particle states.
-This approach is often referred to as \textit{m-scheme} in nuclear
-physics.  It is straightforward to implement and works well for
-general systems, but it fails to exploit all the symmetries in the
-quantum dot system: not only is spin projection $\hat S_z$ conserved,
-the Casimir operator $\hat S^2$ is as well.  A more efficient approach
-is to couple the spins of the single-particle states to form
-two-particle states with good $\hat S^2$, an approach analogous
-to \textit{j-scheme} in nuclear physics.  A combination of this with
-the Eckart-Wigner theorem could reduce the computational cost
-significantly, albeit at the cost of increased implementation
-complexity.
-
-We hope to apply these theoretical and technical enhancements not only
-to the study of quantum dots, but to studies of nuclear and atomic
-systems, opening up an even greater range of applications.
+We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.
+Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
+EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
+
+There are several directions in which the calculations may be improved.
+One can attempt to improve the IM-SRG approximation by incorporating some of the missing higher-body terms in the commutator.
+This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
+While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
+
+The application of IM-SRG eliminates a large number of the QDPT diagrams of Fig.\ \ref{fig:diagrams-sfe}, which is beneficial as it increases the efficiency of the QDPT calculations.
+Thus it may be more feasible to perform higher orders of QDPT on IM-SRG evolved Hamiltonians.
+Moreover, the remaining diagrams at third order can be eliminated through infinite resummation techniques, which would incorporate higher order terms and therefore further increase the accuracy of the result.
+
+We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
+A new technique developed by T.
+D.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
+Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
+
+The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).
+This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.
+
+By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.
+Such interactions can be used to lower the cost of other methods such as full configuration interaction theory.
+
+Implementation-wise, our current code constructs the two-particle states as simple Slater determinants of their one-particle states.
+This approach is often referred to as \textit{m-scheme} in nuclear physics.
+It is straightforward to implement and works well for general systems, but it fails to exploit all the symmetries in the quantum dot system: not only is spin projection $\hat S_z$ conserved, the Casimir operator $\hat S^2$ is as well.
+A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
+A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
+
+We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
 

### 2017-06-14 Manuscript/paper.tex
Simplify ^{[k]} notation

@@
 \begin{align*}
-  \hat H \equiv \hat H^{[1]} + \hat H^{[2]},
-\end{align*}
-where $\hat{H}^{[1]}$ and $\hat{H}^{[2]}$ are respectively the one- and two-body parts of the Hamiltonian, namely
+  \hat H \equiv \hat H_1 + \hat H_2,
+\end{align*}
+where $\hat{H}_1$ and $\hat{H}_2$ are respectively the one- and two-body parts of the Hamiltonian, namely
 \begin{align} \label{eq:onetwobodyhamiltonian}
-\hat{H}^{[1]} &\equiv \sum_{j = 1}^N h(\hat{\bm p}_j, \hat{\bm r}_j), &
-\hat{H}^{[2]} &\equiv \sum_{j_1 = 1}^N \sum_{j_2 = 1}^{j_1 - 1} v(\hat{\bm r}_{j_1}, \hat{\bm r}_{j_2}).
-\end{align}
-The operator $\hat{\bm r}_j$ is the position operator of the $j$-th particle,\footnote{The ordering of the particle labels $j$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_j \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_j}$ is its momentum operator.
+\hat{H}_1 &\equiv \sum_{\alpha = 1}^N h(\hat{\bm p}_\alpha, \hat{\bm r}_\alpha), &
+\hat{H}_2 &\equiv \sum_{\alpha = 1}^N \sum_{\beta = 1}^{\alpha - 1} v(\hat{\bm r}_\alpha, \hat{\bm r}_\beta).
+\end{align}
+The operator $\hat{\bm r}_\alpha$ is the position operator of the $\alpha$-th particle,\footnote{The ordering of the particle labels $\alpha$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_\alpha \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_\alpha}$ is its momentum operator.
 
@@
 
-The noninteracting part of the many-body Hamiltonian $\hat{H}^{[1]}$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
+The noninteracting part of the many-body Hamiltonian $\hat{H}_1$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
 \begin{align*}
@@
 
-Returning to the one-body part of the many-body Hamiltonian, $\hat{H}^{[1]}$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}^{[1]}$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
+Returning to the one-body part of the many-body Hamiltonian, $\hat{H}_1$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}_1$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
 Note that a Slater determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
@@
 \begin{align*}
-  \hat{H}^{[1]} | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle.
+  \hat{H}_1 | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle.
 \end{align*}
 It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
-This is possible even for ground states of $\hat{H}^{[1]}$.
+This is possible even for ground states of $\hat{H}_1$.
 However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
@@
 
-In second quantization, the one- and two-body Hamiltonian operators $H^{[1]}$ and $\hat{H}^{[2]}$ from Eq.\ \eqref{eq:onetwobodyhamiltonian} can be rewritten as
+In second quantization, the one- and two-body Hamiltonian operators $\hat{H}_1$ and $\hat{H}_2$ from Eq.\ \eqref{eq:onetwobodyhamiltonian} can be rewritten as
 \begin{align} \label{eq:second_quantized_hamiltonian}
-  \hat H^{[1]} &= \sum_{p q} \langle p | \hat{H}^{[1]} | q \rangle \hat a_p^\dagger \hat a_q^{}, &
-  \hat{H}^{[2]} &= \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{},
-\end{align}
-where the quantities $\langle p | \hat{H}^{[1]} | q \rangle$ and $\langle p q | \hat{H}^{[2]} | r s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
+  \hat{H}_1 &= \sum_{p q} \langle p | \hat{H}_1 | q \rangle \hat a_p^\dagger \hat a_q^{}, &
+  \hat{H}_2 &= \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}_2 | r s \rangle \hat a_p^\dagger \hat a_q^\dagger \hat a_s^{} \hat a_r^{},
+\end{align}
+where the quantities $\langle p | \hat{H}_1 | q \rangle$ and $\langle p q | \hat{H}_2 | r s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
 
@@
 \begin{align}
-  \hat{H} = \sum_{p q} \langle p | \hat{H}^{[1]} | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}^{[2]} | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
+  \hat{H} = \sum_{p q} \langle p | \hat{H}_1 | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}_2 | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
 \label{eq:vacuumhamiltonian}
 \end{align}
-Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}^{[2]} | r s \rangle$, leading to a four-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
-For this reason, the two-body matrix element $\langle p q | \hat{H}^{[2]} | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
+Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}_2 | r s \rangle$, leading to a four-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
+For this reason, the two-body matrix element $\langle p q | \hat{H}_2 | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
 This is not to be confused with the (non-antisymmetric) interaction integral,
@@
 \begin{align} \label{eq:antisymmetricmatrixelement}
-  \langle p q | \hat{H}^{[2]} | r s \rangle = v_{p q r s} - v_{p q s r}.
+  \langle p q | \hat{H}_2 | r s \rangle = v_{p q r s} - v_{p q s r}.
 \end{align}
@@
 
-If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}^{[1]}$ as the set of known states.
+If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}_1$ as the set of known states.
 
@@
 At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}^{[2]}$ during the post-HF calculation.
+The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}_2$ during the post-HF calculation.
 
@@
 \begin{align}
-  E_{\Phi} &= \sum_i H^{[1] \prime}_{i i} + \sum_{i j} H^{[2] \prime}_{i j i j} \label{eq:hfenergy},
+  E_{\Phi} &= \sum_i H^{\prime}_{i i} + \sum_{i j} H^{\prime}_{i j i j} \label{eq:hfenergy},
 \end{align}
@@
 \begin{align}
-  H^{[1] \prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}^{[1]} | s \rangle C_{s q}^{}, \label{eq:hftransform1} \\
-  H^{[2] \prime}_{p q r s} &\equiv \sum_{t u v w} C_{t p}^* C_{u q}^* \langle t u | \hat{H}^{[2]} | v w \rangle C_{v r}^{} C_{w s}^{}, \label{eq:hftransform2}
+  H^{\prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}_1 | s \rangle C_{s q}^{}, \label{eq:hftransform1} \\
+  H^{\prime}_{p q r s} &\equiv \sum_{t u v w} C_{t p}^* C_{u q}^* \langle t u | \hat{H}_2 | v w \rangle C_{v r}^{} C_{w s}^{}, \label{eq:hftransform2}
 \end{align}
@@
 \begin{align} \label{eq:fock}
-  F_{p q} \equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_{r s i} C_{r i}^* \langle p r | \hat{H}^{[2]} | q s \rangle C_{s i}^{},
+  F_{p q} \equiv \langle p | \hat{H}_1 | q \rangle + \sum_{r s i} C_{r i}^* \langle p r | \hat{H}_2 | q s \rangle C_{s i}^{},
 \end{align}
@@
 
-To make use of the HF solution as the reference state for future calculations, we transform the operators via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
-Therefore, the post-HF methods described in the next few sections generally use the transformed operators $\hat{H}^{[1] \prime}$ and $\hat{H}^{[2] \prime}$ as inputs.
-However, we will not annotate them with the prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
+To make use of the HF solution as the reference state for future calculations, we transform the matrix elements via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
+Therefore, the post-HF methods described in the next few sections generally use the transformed matrix elements $\hat{H}'_{pq}$ and $\hat{H}'_{pqrs}$ as inputs.
+However, we will omit prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
 
@@
 The normal ordering notation thus provides a concise way of expressing the right-hand side.
-In this new notation, we can rewrite the Hamiltonian $\hat H = \hat{H}^{[1]} + \hat{H}^{[2]}$ in its \emph{normal-ordered representation}:
-\begin{align}
-  \hat{H} = H^{[0]} + \sum_{p q} H^{[1]}_{p q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p q r s} H^{[2]}_{p q r s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}},
+In this new notation, we can rewrite the Hamiltonian $\hat H = \hat{H}_1 + \hat{H}_2$ in its \emph{normal-ordered representation}:
+\begin{align}
+  \hat{H} = H_\varnothing + \sum_{p q} H_{p q} \normord{\hat{a}_p^\dagger \hat{a}_q^{}} + \frac{1}{4} \sum_{p q r s} H_{p q r s} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}},
   \label{eq:normordhamiltonian}
@@
 \begin{align*}
-  H^{[0]} &\equiv \sum_i \langle i | \hat{H}^{[1]} | i \rangle + \frac{1}{2} \sum_{i j} \langle i j | \hat{H}^{[2]} | i j \rangle, \\
-  H^{[1]}_{p q} &\equiv \langle p | \hat{H}^{[1]} | q \rangle + \sum_i \langle p i | \hat{H}^{[2]} | q i \rangle, \\
-  H^{[2]}_{p q r s} &\equiv \langle p q | \hat{H}^{[2]} | r s \rangle. \\
-\end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H^{[0]}$ is simply the HF energy $E_\Phi$ and $H^{[1]}_{p q}$ is the Fock matrix $F_{p q}$.
+  H_\varnothing &\equiv \sum_i \langle i | \hat{H}_1 | i \rangle + \frac{1}{2} \sum_{i j} \langle i j | \hat{H}_2 | i j \rangle, \\
+  H_{p q} &\equiv \langle p | \hat{H}_1 | q \rangle + \sum_i \langle p i | \hat{H}_2 | q i \rangle, \\
+  H_{p q r s} &\equiv \langle p q | \hat{H}_2 | r s \rangle. \\
+\end{align*}
+If $\Phi$ is a state optimized by the HF method, then $H_\varnothing$ is simply the HF energy $E_\Phi$ and $H_{p q}$ is the Fock matrix $F_{p q}$.
 The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
@@
 \begin{align*}
-\hat{\eta} = \sum_{p q} \eta_{p q}^{[1]} \normord{\hat a_p^\dagger \hat a_q} +
-\frac{1}{4} \sum_{p q r s}\eta_{p q r s}^{[2]} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r},
-\end{align*}
-where $\eta_{p q}^{[1]}$ and $ \eta_{p q r s}^{[2]}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$, subject to the antihermittivity constraint.
+\hat{\eta} = \sum_{p q} \eta_{p q} \normord{\hat a_p^\dagger \hat a_q} +
+\frac{1}{4} \sum_{p q r s}\eta_{p q r s} \normord{\hat a_p^\dagger \hat a_q^\dagger \hat a_s \hat a_r},
+\end{align*}
+where $\eta_{p q}$ and $ \eta_{p q r s}$ respectively are its one- and two-body matrix elements normal ordered with respect to $\Phi$, subject to the antihermittivity constraint.
 
@@
 \begin{align}
-    \frac{\D H^{[k]}}{\D s} = C^{[k]}(\eta, H), \label{eq:flowmxe}
+    \frac{\D H}{\D s} = C(\eta, H), \label{eq:flowmxe}
 \end{align}
@@
 \begin{align}
-  C^{[k]}(A, B) &\equiv 2 \antisymm_{A B} D^{[k]}(A, B), \label{eq:commutmxe} \\
+  C(A, B) &\equiv 2 \antisymm_{A B} D(A, B), \label{eq:commutmxe} \\
   \antisymm_{x y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr),
@@
 \begin{align}
-  D^{[0]}(A, B)
+  D_\varnothing(A, B)
   &\equiv
-    \sum_{i a} A^{[1]}_{i a} B^{[1]}_{a i}
-    + \frac{1}{4} \sum_{i j a b} A^{[2]}_{i j a b} B^{[2]}_{a b i j},
+    \sum_{i a} A_{i a} B_{a i}
+    + \frac{1}{4} \sum_{i j a b} A_{i j a b} B_{a b i j},
     \label{eq:flow0} \\
-  D^{[1]}_{p q}(A, B)
+  D_{p q}(A, B)
   &\equiv
-    \sum_r A^{[1]}_{p r} B^{[1]}_{r q}
-    - \frac{1}{2} \sum_{i j a} A^{[2]}_{i j a q} B^{[2]}_{a p i j}
-    + \frac{1}{2} \sum_{i a b} A^{[2]}_{i p a b} B^{[2]}_{a b i q}
+    \sum_r A_{p r} B_{r q}
+    - \frac{1}{2} \sum_{i j a} A_{i j a q} B_{a p i j}
+    + \frac{1}{2} \sum_{i a b} A_{i p a b} B_{a b i q}
     \notag \\
@@
     + \sum_{i a} \left(
-    A^{[1]}_{i a} B^{[2]}_{a p i q}
-    + A^{[2]}_{i p a q} B^{[1]}_{a i}
+    A_{i a} B_{a p i q}
+    + A_{i p a q} B_{a i}
     \right),
     \label{eq:flow1} \\
-  D^{[2]}_{p q r s}(A, B)
+  D_{p q r s}(A, B)
   &\equiv
-    4 \antisymm_{p q} \antisymm_{r s} \sum_{i a} A^{[2]}_{i p a r} B^{[2]}_{a q i s}
-    + \frac{1}{2} \sum_{i j} A^{[2]}_{i j r s} B^{[2]}_{p q i j}
-    + \frac{1}{2} \sum_{a b} A^{[2]}_{p q a b} B^{[2]}_{a b r s}
+    4 \antisymm_{p q} \antisymm_{r s} \sum_{i a} A_{i p a r} B_{a q i s}
+    + \frac{1}{2} \sum_{i j} A_{i j r s} B_{p q i j}
+    + \frac{1}{2} \sum_{a b} A_{p q a b} B_{a b r s}
     \notag \\
@@
     + 2 \sum_t \left(
-    \antisymm_{p q} A^{[1]}_{q t} B^{[2]}_{p t r s}
-    + \antisymm_{r s} A^{[2]}_{p q r t} B^{[1]}_{t s}
+    \antisymm_{p q} A_{q t} B_{p t r s}
+    + \antisymm_{r s} A_{p q r t} B_{t s}
     \right).
@@
 \includegraphics{fig-diagrams-imsrg.pdf}
-\caption{(Color online) Diagrammatic representation of $D^{[k]}(\circ, \bullet)$ of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
+\caption{(Color online) Diagrammatic representation of $D(\circ, \bullet)$ of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}, where open circles represent $A$ and filled circles represent $B$.
 The two-body vertices are implicitly antisymmetric (i.e.\ \textit{Hugenholtz diagrams} \cite{HUGENHOLTZ1957481}, as described in \cite{shavitt2009many} \S 4.4.3).
@@
 If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
-In particular, $H^{[0]}(\infty)$ would be the exact ground state energy.
+In particular, $H_\varnothing(\infty)$ would be the exact ground state energy.
 
@@
 \begin{align*}
-\eta^{\prime [1]}_{a i} &\equiv \frac{H^{[1]}_{a i}}{\tilde{\Delta}^{[1]}_{a i}}, &
-\eta^{\prime [2]}_{a b i j} &\equiv \frac{H^{[2]}_{a b i j}}{\tilde{\Delta}^{[2]}_{a b i j}},
+\eta'_{a i} &\equiv \frac{H_{a i}}{\tilde{\Delta}_{a i}}, &
+\eta'_{a b i j} &\equiv \frac{H_{a b i j}}{\tilde{\Delta}_{a b i j}},
 \end{align*}
@@
 \begin{align}
-\tilde{\Delta}^{[1]}_{a i} &\equiv \Delta_{a i} - H^{[2]}_{a i a i}, \notag \\
-\tilde{\Delta}^{[2]}_{a b i j} &\equiv \Delta_{a b i j} + w_{a b i j}, \notag \\
-\Delta_{p_1 \ldots p_k q_1 \ldots q_k} &\equiv \sum_{i = 1}^k (H^{[1]}_{p_i p_i} -  H^{[1]}_{q_i q_i}), \label{eq:moellerplessetdenominator} \\
+\tilde{\Delta}_{a i} &\equiv \Delta_{a i} - H_{a i a i}, \notag \\
+\tilde{\Delta}_{a b i j} &\equiv \Delta_{a b i j} + w_{a b i j}, \notag \\
+\Delta_{p_1 \ldots p_k q_1 \ldots q_k} &\equiv \sum_{i = 1}^k (H_{p_i p_i} -  H_{q_i q_i}), \label{eq:moellerplessetdenominator} \\
 w_{a b i j}
-  &\equiv H^{[2]}_{a b a b} - H^{[2]}_{a i a i} - H^{[2]}_{b i b i} \notag \\
-  &\qquad + H^{[2]}_{i j i j} - H^{[2]}_{a j a j} - H^{[2]}_{b j b j}. \notag
+  &\equiv H_{a b a b} - H_{a i a i} - H_{b i b i} \notag \\
+  &\qquad + H_{i j i j} - H_{a j a j} - H_{b j b j}. \notag
 \end{align}
@@
 \begin{align} \label{eq:cc_amps}
-  \hat{T}_k \equiv \left(\frac{1}{k!}\right)^2 \sum_{\substack{a_1 \ldots a_k \\ i_1 \ldots i_k}} t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k} \normord{\hat{a}_{a_1}^\dagger \ldots \hat{a}_{a_k}^\dagger \hat a_{i_k}^{} \ldots \hat{a}_{i_1}^{}},
-\end{align}
-where the unknown matrix elements, $t^{[k]}_{a_1 \ldots a_k i_1 \ldots i_k}$, are known as \textit{cluster amplitudes} \cite{shavitt2009many}.
+  \hat{T}_k \equiv \left(\frac{1}{k!}\right)^2 \sum_{\substack{a_1 \ldots a_k \\ i_1 \ldots i_k}} t_{a_1 \ldots a_k i_1 \ldots i_k} \normord{\hat{a}_{a_1}^\dagger \ldots \hat{a}_{a_k}^\dagger \hat a_{i_k}^{} \ldots \hat{a}_{i_1}^{}},
+\end{align}
+where the unknown matrix elements, $t_{a_1 \ldots a_k i_1 \ldots i_k}$, are known as \textit{cluster amplitudes} \cite{shavitt2009many}.
 
@@
   \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}^{[2]}$.
+  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}_2$.
 As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
-Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}^{[2]}$ are unconstrained.}
+Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}_2$ are unconstrained.}
   \label{fig:diagrams-ccsd}
@@
 
-The unknown cluster amplitudes in CCSD, $t_{a i}^{[1]}$ and $t_{a b i j}^{[2]}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \E^{-\hat{T}}$, respectively,
+The unknown cluster amplitudes in CCSD, $t_{a i}$ and $t_{a b i j}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \E^{-\hat{T}}$, respectively,
 \begin{align} \label{eq:ccsd1}
@@
 \begin{gather} \label{eq:ccsd2}
-  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \hat{H}^{[2]} \bigl\{\hat{T}_1 + \hat{T}_2 + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_1^{2} + \frac{1}{3!} \hat{T}_1^{3}\}_{\mathrm{c}} \ket{\Phi} = \Delta_{i a} t_{a i}^{[1]} \\
-  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \hat{H}^{[2]} \bigl\{1 + \hat{T}_1 + \hat{T}_2 + \frac{1}{2} \hat{T}_1^{2} + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_2^{2} + \frac{1}{3!} \hat{T}_1^{3} + \frac{1}{2!} \hat{T}_1^{2} \hat{T}_2 + \frac{1}{4!} \hat{T}_1^{4}\bigr\}_{\mathrm{c}} \ket{\Phi} \notag \\
-= \Delta_{i j a b} t_{a b i j}^{[2]} \notag
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \hat{H}_2 \bigl\{\hat{T}_1 + \hat{T}_2 + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_1^{2} + \frac{1}{3!} \hat{T}_1^{3}\}_{\mathrm{c}} \ket{\Phi} = \Delta_{i a} t_{a i} \\
+  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \hat{H}_2 \bigl\{1 + \hat{T}_1 + \hat{T}_2 + \frac{1}{2} \hat{T}_1^{2} + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_2^{2} + \frac{1}{3!} \hat{T}_1^{3} + \frac{1}{2!} \hat{T}_1^{2} \hat{T}_2 + \frac{1}{4!} \hat{T}_1^{4}\bigr\}_{\mathrm{c}} \ket{\Phi} \notag \\
+= \Delta_{i j a b} t_{a b i j} \notag
 \end{gather}
@@
 
-In QDPT, solutions of an approximate one-body Hamiltonian $\hat{H}^{[1]}$ form the basis of the model space.
+In QDPT, solutions of an approximate one-body Hamiltonian $\hat{H}_1$ form the basis of the model space.
 One begins by assuming the existence of an operator $\hat{\Omega}$, known as the \textit{wave operator}, that maps some set of states $\tilde \Psi^{\mathrm{o}}_u$ within the model space to the exact ground state $\Psi_u$:
@@
 \end{align}
-The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}^{[1]}$.
+The states $\tilde \Psi^{\mathrm{o}}_u$ consist of some mixture of the eigenstates $\Psi^{\mathrm{o}}_{u'}$ of the approximate Hamiltonian $\hat{H}_1$.
 
@@
 \begin{gather*}
-  [\hat \Omega, \hat{H}^{[1]}] =
+  [\hat \Omega, \hat{H}_1] =
   (1 - \hat \Omega) \hat V \Omega,
 \end{gather*}
-where $\hat V \equiv \hat H - \hat{H}^{[1]}$ is the perturbation.  The commutator on the left may be ``inverted'' using the resolvent approach (\cite{shavitt2009many}, p.\ 50), resulting in:
+where $\hat V \equiv \hat H - \hat{H}_1$ is the perturbation.  The commutator on the left may be ``inverted'' using the resolvent approach (\cite{shavitt2009many}, p.\ 50), resulting in:
 \begin{align*}
@@
 \end{align*}
-where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}^{[1]} \hat Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
+where $\hat R_u \equiv \hat Q (E_u - \hat Q \hat{H}_1 \hat Q)^{-1} \hat Q$ defines the resolvent and $\hat P_u$ is the projection operator that projects any state onto $\Psi^{\mathrm{o}}_u$.
 As is standard in perturbation theory, we now assume $\hat \Omega$ can be expanded as a series of terms of increasing order, as quantified by the power of the perturbation $\hat V$:
@@
   &=
-    \sum_{i a b} \frac{|H^{[2]}_{p i a b}|^2}{2 \Delta_{p i a b}}
-    - \sum_{i j a} \frac{|H^{[2]}_{i j p a}|^2}{2 \Delta_{i j p a}},
+    \sum_{i a b} \frac{|H_{p i a b}|^2}{2 \Delta_{p i a b}}
+    - \sum_{i j a} \frac{|H_{i j p a}|^2}{2 \Delta_{i j p a}},
 \end{align*}
@@
 \begin{align*}
-  \varepsilon_p = H^{[1]}_{p p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}.
+  \varepsilon_p = H_{p p} + \varepsilon_p^{(2)} + \varepsilon_p^{(3)}.
 \end{align*}
@@
   \label{eq:gen_attached}
-  \hat{X}^{(N + 1)}_u &= \sum_a x^{[1, 0]}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{[2, 1]}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
+  \hat{X}^{(N + 1)}_u &= \sum_a x^{(+)}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{(+)}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{[0, 1]} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{[1, 2]}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
+  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{(-)} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{(-)}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
 \end{align}
@@
   \label{eq:partial_norms_p}
-  n_{\text{1-particle}} &= \sqrt{\sum_a | \bar{x}^{[1,0]}_a |^2},\\
+  n_{\text{1-particle}} &= \sqrt{\sum_a | \bar{x}^{(+)}_a |^2},\\
   \label{eq:partial_norms_h}
-  n_{\text{1-hole}} &= \sqrt{\sum_i | \bar{x}^{[0,1]}_i |^2}.
+  n_{\text{1-hole}} &= \sqrt{\sum_i | \bar{x}^{(-)}_i |^2}.
 \end{align}
@@
 \begin{align*}
-    \hat{L}^{(N + 1)}_w &= \sum_a l^{[1, 0]}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{[2, 1]}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
-    \hat{L}^{(N - 1)}_w &= \sum_i l_i^{[0, 1]} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{[1, 2]}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
+    \hat{L}^{(N + 1)}_w &= \sum_a l^{(+)}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{(+)}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
+    \hat{L}^{(N - 1)}_w &= \sum_i l_i^{(-)} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{(-)}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
 \end{align*}

### 2017-06-14 Manuscript/paper.tex
Use more consistent notation for HF
To avoid confusion, the H_{pqrs} notation should be exclusively reserved
for normal-ordered matrix elements.

@@
 The restriction is what enables the simplicity and efficiency of this method.
-We shall denote each unknown single-particle state $|q'\rangle$ by a primed label $q'$.
-
-To perform numerical calculations, we further assume that each unknown state $|q'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
-\begin{align*}
-  |q'\rangle \equiv \sum_p |p\rangle C_{p q'}.
+We shall denote each unknown single-particle state $|p'\rangle$ by a primed label $p'$.
+
+To perform numerical calculations, we further assume that each unknown state $|p'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
+\begin{align*}
+  |p'\rangle \equiv \sum_p |p\rangle C_{p p'}.
 \end{align*}
@@
 
-To ensure orthonormality of the states, we require there to be as many unknown states $|q'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
-These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|q'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
-At the end of the calculation, of the set of states $|q'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
+To ensure orthonormality of the states, we require there to be as many unknown states $|p'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
+These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|p'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
+At the end of the calculation, of the set of states $|p'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
 The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}_2$ during the post-HF calculation.
 
-The goal then is to find the coefficients $\bm C$ that minimize the energy $E_{\Phi}$, now given by
-\begin{align}
-  E_{\Phi} &= \sum_i H^{\prime}_{i i} + \sum_{i j} H^{\prime}_{i j i j} \label{eq:hfenergy},
-\end{align}
-where the transformed operators are defined as
-\begin{align}
-  H^{\prime}_{p q} &\equiv \sum_{r s} C_{r p}^* \langle r | \hat{H}_1 | s \rangle C_{s q}^{}, \label{eq:hftransform1} \\
-  H^{\prime}_{p q r s} &\equiv \sum_{t u v w} C_{t p}^* C_{u q}^* \langle t u | \hat{H}_2 | v w \rangle C_{v r}^{} C_{w s}^{}, \label{eq:hftransform2}
+The goal then is to find the coefficients $\bm C$ that minimize the energy $E_{\Phi}$,
+\begin{align}
+  E_{\Phi} &= \sum_{i'} \langle i' | \hat{H}_1 | i' \rangle + \sum_{i' j'} \langle i' j' | \hat{H}_2 | i' j' \rangle \label{eq:hfenergy},
+\end{align}
+where
+\begin{align}
+  \langle p' | \hat{H}_1 | q' \rangle &= \sum_{p q} C_{p p'}^* \langle p | \hat{H}_1 | q \rangle C_{q q'}^{}, \label{eq:hftransform1} \\
+  \langle p' q' | \hat{H}_2 | r' s' \rangle &= \sum_{p q r s} C_{p p'}^* C_{q q'}^* \langle p q | \hat{H}_2 | r s \rangle C_{r r'}^{} C_{s s'}^{}, \label{eq:hftransform2}
 \end{align}
@@
 \begin{align} \label{eq:fock}
-  F_{p q} \equiv \langle p | \hat{H}_1 | q \rangle + \sum_{r s i} C_{r i}^* \langle p r | \hat{H}_2 | q s \rangle C_{s i}^{},
-\end{align}
-and $\bm{\varepsilon}$ is a vector of Lagrange multipliers: each element $\varepsilon_{q'}$ is associated with a specific single-particle state $|q'\rangle$.
+  F_{p q} \equiv \langle p | \hat{H}_1 | q \rangle + \sum_{r s i'} C_{r i'}^* \langle p r | \hat{H}_2 | q s \rangle C_{s i'}^{},
+\end{align}
+and $\bm{\varepsilon}$ is a vector of Lagrange multipliers: each element $\varepsilon_{p'}$ is associated with a specific single-particle state $|p'\rangle$.
 
 Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
-We begin with an initial guess $\bm{C}^{(i)}$, which is fed into Eq.\ \eqref{eq:fock} to produce the Fock matrix.
-This is then used in Eq.\ \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(i + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(i + 1)}$ as the vector of eigenvalues.
+We begin with an initial guess $\bm{C}^{(j)}$ on the $j$-th iteration, which is fed into Eq.\ \eqref{eq:fock} to produce the Fock matrix.
+This is then used in Eq.\ \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(j + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(j + 1)}$ as the vector of eigenvalues.
 This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
@@
 
-To make use of the HF solution as the reference state for future calculations, we transform the matrix elements via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
-Therefore, the post-HF methods described in the next few sections generally use the transformed matrix elements $\hat{H}'_{pq}$ and $\hat{H}'_{pqrs}$ as inputs.
-However, we will omit prime symbols as the methods are generic and can be applied to any reference state, whether optimized by HF or not.
+To make use of the HF solution as the reference state for post-HF calculations, we transform the matrix elements via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
+In effect, this means we are no longer operating within the harmonic oscillator single-particle basis, but a HF-optimized single-particle basis.
+However, we will omit the prime symbols as the post-HF methods are generic and can be used in any basis, whether optimized by HF or not.
 

### 2017-06-14 Manuscript/paper.tex
Clarify EOM notation

@@
   \label{eq:gen_attached}
-  \hat{X}^{(N + 1)}_u &= \sum_a x^{(+)}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{(+)}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
+  \hat{X}^{(N + 1)}_u &= \sum_a x^{(u, +)}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{(u, +)}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{(-)} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{(-)}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
+  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{(u, -)} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{(u, -)}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
 \end{align}
@@
 \begin{align*}
-    \hat{L}^{(N + 1)}_w &= \sum_a l^{(+)}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{(+)}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
-    \hat{L}^{(N - 1)}_w &= \sum_i l_i^{(-)} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{(-)}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
-\end{align*}
-These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_w$, analogous to Eq.\ \eqref{eq:EOMIMSRG},
-\begin{align*}
-  \bra{\Phi^{(N)}_0} [\bar{H}, \bar{L}^{(N \pm 1)}_w] = \pm \varepsilon^{(\pm)}_w \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_w
-\end{align*}
-and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_w}{\bar{X}^{(N \pm 1)}_u} = \delta_{w u}$.
+    \hat{L}^{(N + 1)}_u &= \sum_a l^{(u, +)}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{(u, +)}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
+    \hat{L}^{(N - 1)}_u &= \sum_i l_i^{(u, -)} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{(u, -)}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
+\end{align*}
+These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_u$, analogous to Eq.\ \eqref{eq:EOMIMSRG},
+\begin{align*}
+  \bra{\Phi^{(N)}_0} [\bar{H}, \bar{L}^{(N \pm 1)}_u] = \pm \varepsilon^{(\pm)}_u \bra{\Phi^{(N)}_0} \bar{L}^{(N \pm 1)}_u
+\end{align*}
+and form a bi-orthogonal set with the right-eigenvectors, $\braket{\bar{L}^{(N \pm 1)}_u}{\bar{X}^{(N \pm 1)}_v} = \delta_{u v}$.
 

### 2017-06-19 Manuscript/paper.tex
fixed ladder operator indices

@@
 We will describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
-To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$.
+To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$, collectively known as \textit{field operators}.
 These operators must satisfy the anticommutation relations that encode the Pauli principle, namely
@@
 
-The second-quantized operators in Eq.\ \eqref{eq:second_quantized_hamiltonian} are constructed with respect to the vacuum state in the sense that their operator strings $\hat{a}_p^\dagger \hat{a}_q$ and $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ both have expectation values of zero in vacuum:
-\begin{align*}
-&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0, &
-&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0.
-\end{align*}
-They are said to be \emph{normal-ordered} with respect to the vacuum state $\ket{}$.
-It is possible to be normal-ordered with respect to a different state, however.
-Suppose we have a Slater determinant $\Phi$ with $N$ occupied states:
-\begin{align*}
-  \ket{\Phi} \equiv \ket{i_1 i_2 \ldots i_N}
-\end{align*}
-where $\{i_1, i_2, \ldots, i_N\}$ is a set of $N$ indices that label
-the occupied states.  We define then the normal ordering of the
-physical field operators $\hat a$ and $\hat a^\dagger$ with respect to
-$|\Phi\rangle$, that is
-\begin{align*}
-  \normord{\hat{a}_p^\dagger \hat{a}_q^{}} &= \hat{a}_p^\dagger \hat{a}_q^{} - n_p^{} \delta_{p q}^{}.
-\end{align*}
-where $n_p$ is the \textit{occupancy} of the single-particle state $p$, defined as
-\begin{align}
-  n_p \equiv \begin{cases}
-    1 & \text{if $p$ is an occupied state of $\Phi$}, \\
-    0 & \text{if $p$ is an unoccupied state of $\Phi$}.
-  \end{cases}
-\end{align}
-
-The normal ordering notation thus provides a concise way of expressing the right-hand side.
-In this new notation, we can rewrite the Hamiltonian $\hat H = \hat{H}_1 + \hat{H}_2$ in its \emph{normal-ordered representation}:
+In the Hamiltonian representation of Eq.\ \eqref{eq:second_quantized_hamiltonian}, the one-body operator string $\hat{a}_p^\dagger \hat{a}_q$  has an expectation value of zero in vacuum:
+\begin{align}
+&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0, \label{eq:vacuum-zero1}
+\end{align}
+and the two-body string $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ does not couple states with one or fewer particles:
+\begin{align}
+&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0, &
+&\bra{t} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{u} = 0. \label{eq:vacuum-zero2}
+\end{align}
+These properties arise from the fact that the creation operators always appear to the left of the annihilation operators, the defining property of a pure $k$-body operator in vacuum.
+Such strings are said to be \textit{normal-ordered with respect to the vacuum state $\ket{}$}.
+
+It is also possible to be normal-ordered with respect to a different state.
+Suppose our reference state is a Slater determinant $\ket{\Phi} \equiv \ket{i_1 i_2 \ldots i_N}$ containing $N$ occupied states $I \equiv \{i_1, i_2, \ldots, i_N\}$.
+Let $s$ be a string of fermionic field operators.
+We define the \textit{normal ordering of $s$ with respect to $|\Phi\rangle$}, denoted $\normord{s}$, to be a syntactic transformation that (a) permutes field operators belonging to $L \equiv \{\hat{a}_i^{} \mid i \in I\} \cup \{\hat{a}_a^\dagger \mid a \notin I\}$ to the left of those not belonging to $L$, and (b) attaches a negative sign to the resulting string if the permutation is odd.
+The permutation in (a) is only defined up to reordering among the $L$ and non-$L$ operators, but this ambiguity has no effect on the semantics of the result due to the sign compensation in (b).
+For example,
+\begin{align*}
+  \normord{\hat{a}_i \hat{a}^\dagger_j \hat{a}_a \hat{a}_b^\dagger}
+  &= \hat{a}_i \hat{a}_b^\dagger \hat{a}^\dagger_j \hat{a}_a \\
+  &= -\hat{a}_b^\dagger \hat{a}_i \hat{a}^\dagger_j \hat{a}_a.
+\end{align*}
+Here, both of the RHS expressions are valid and equivalent interpretations of the normal ordering  of $\hat{a}_i \hat{a}^\dagger_j \hat{a}_a \hat{a}_b^\dagger$.
+
+With normal-ordering, we obtain analogs of Eqs.\ \eqref{eq:vacuum-zero1} and \eqref{eq:vacuum-zero2} for the reference state $\ket{\Phi}$:
+\begin{align*}
+&\bra{\Phi} \normord{\hat{a}_p^\dagger \hat{a}_q} \ket{\Phi} = 0, &
+&\bra{\Phi} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r} \ket{\Phi} = 0,
+&\bra{\Phi_t} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r} \ket{\Phi_u} = 0.
+\end{align*}
+where $|\Phi_i\rangle \equiv \hat{a}_i^{} |\Phi\rangle$, and $|\Phi_a\rangle \equiv \hat{a}_a^\dagger |\Phi\rangle$.
+
+Likewise, we can rewrite the Hamiltonian $\hat H = \hat{H}_1 + \hat{H}_2$ in its \emph{normal-ordered representation}:
 \begin{align}
@@
 The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
-The only difference is that the meaning of a ``$k$-body operator'' has been redefined with respect to the reference state $\Phi$ rather than the vacuum state $\ket{}$, causing matrix elements to be reshuffled among the $k$-body operators.
-Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ some $k$-body operators may be discarded from the computation for efficiency reasons.
-Normal-ordering can drastically alter the importance of the $k$-body operators with respect to each other.
-
-Higher-body operators arise from integrating the flow equations of Eq.~(\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
+The only difference is that the meaning of a pure $k$-body operator has been redefined with respect to the reference state $\ket{\Phi}$ rather than the vacuum state $\ket{}$, causing matrix elements to be reshuffled among the themselves.
+Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ higher-body operators discarded from the computation for efficiency reasons.
+By normal-ordering with respect to an approximate state $\ket{\Phi}$, we reshuffle higher-body contributions into the lower-body terms, significantly reducing the importance of the higher-body operators.
+
+Higher-body operators arise from integrating the flow equations of Eq.\ (\ref{eq:imsrgode}), which is one of the major challenges of the SRG method.
 With each evaluation of the commutator, the Hamiltonian gains terms of higher order, and these induced contributions will in subsequent integration steps feed back into terms of lower order.
@@
 
-Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator is grows exponentially with $k$.
+Computationally, higher-body terms rapidly become unfeasible to handle: the amount of memory required to store a $k$-body operator grows exponentially with $k$.
 Moreover, the flow equations are capable of generating an infinite number of higher-body terms as the Hamiltonian evolves.
@@
 \end{equation}
-where $\hat{X}$ is in principle a linear combination of excitation and de-excitation operators that change particle number by one,
+where $\hat{X}$ is in principle a linear combination of excitation $(+)$ and de-excitation $(-)$ operators that change particle number by one,
 \begin{align}
   \label{eq:gen_attached}
-  \hat{X}^{(N + 1)}_u &= \sum_a x^{(u, +)}_a  \hat{a}^\dagger_a + \frac{1}{2} \sum_{a b i} x^{(u, +)}_{a b i} \hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{} + \cdots,  \\
+  \hat{X}^{(N + 1)}_u &= \sum_a x^{(u, +)}_a  \normord{\hat{a}^\dagger_a} + \frac{1}{2} \sum_{a b i} x^{(u, +)}_{a b i} \normord{\hat{a}^\dagger_a \hat{a}^\dagger_b \hat{a}_i^{}} + \cdots,  \\
   \label{eq:gen_removed}
-  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{(u, -)} \hat{a}_i^{} + \frac{1}{2} \sum_{i j a} x^{(u, -)}_{i j a} \hat{a}^\dagger_i \hat{a}_j^{} \hat{a}_a^{}  + \cdots.
-\end{align}
+  \hat{X}^{(N - 1)}_u &= \sum_i x_i^{(u, -)} \normord{\hat{a}_i^{}} + \frac{1}{2} \sum_{i j a} x^{(u, -)}_{a i j} \normord{\hat{a}^\dagger_a \hat{a}_j^{} \hat{a}_i^{}}  + \cdots.
+\end{align}
+Here, $x^{(u, \pm)}_p$ and $x^{(u, \pm)}_{p q r}$ are the normal-ordered matrix elements of $\hat{X}_u^{(N \pm 1)}$, defined analogously to Eq.\ \eqref{eq:normordhamiltonian}.
+
 Substitution of Eq.\ \eqref{eq:ladder_def} into the energy eigenvalue problem
@@
 \begin{align*}
-    \hat{L}^{(N + 1)}_u &= \sum_a l^{(u, +)}_a \hat{a}_a^{} + \frac{1}{2} \sum_{i a b} l^{(u, +)}_{a b i} \hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{} + \cdots, \\
-    \hat{L}^{(N - 1)}_u &= \sum_i l_i^{(u, -)} \hat{a}^\dagger_i + \frac{1}{2} \sum_{i j a} l^{(u, -)}_{i j a} \hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{} + \cdots
-\end{align*}
+    \hat{L}^{(N + 1)}_u &= \sum_a l^{(u, +)}_a \normord{\hat{a}_a^{}} + \frac{1}{2} \sum_{i a b} l^{(u, +)}_{i a b} \normord{\hat{a}^\dagger_i \hat{a}_b^{} \hat{a}_a^{}} + \cdots, \\
+    \hat{L}^{(N - 1)}_u &= \sum_i l_i^{(u, -)} \normord{\hat{a}^\dagger_i} + \frac{1}{2} \sum_{i j a} l^{(u, -)}_{i j a} \normord{\hat{a}^\dagger_i \hat{a}^\dagger_j \hat{a}_a^{}} + \cdots,
+\end{align*}
+where $l^{(u, \pm)}_p$ and $l^{(u, \pm)}_{p q r}$ are likewise the normal-ordered matrix elements of $\hat{L}^{(N \pm 1)}_u$.
 These left-eigenvectors satisfy the left-eigenvalue problem, with left-eigenvalues $\varepsilon^{(\pm)}_u$, analogous to Eq.\ \eqref{eq:EOMIMSRG},
@@
 Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
-In the tables, ``n.c.'' marks the cases where IM-SRG or CCSD either diverged or converged extremely slowly.
+In the tables, ``n.c.'' marks the cases where IM-SRG(2) or CCSD either diverged or converged extremely slowly.
 This also affects the extrapolation results in Section \ref{subsec:extrapolation}, as for consistency reasons we chose to extrapolate only when all five points were available.
@@
   \caption{Ground state energy of quantum dots with $N$ particles and an oscillator frequency of $\omega$.
-For every row, the calculations performed in a harmonic oscillator basis size with $K$ shells.}
+For every row, the calculations are performed in a harmonic oscillator basis with $K$ shells.
+The abbreviation ``n.c.'' stands for ``no convergence'': these are cases where IM-SRG(2) or CCSD either diverged or converged extremely slowly.}
   \label{tab:ground}
@@
   \centering
-  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.
-The uncertainties are computed from the approximate Hessian constructed by Levenberg-Marquardt fitting algorithm.
-Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
+  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties, computed from the approximate Hessian in the Levenberg--Marquardt fitting algorithm.
+These uncertainties also determine the number of significant figures presented.
+Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).
+The abbreviation ``n.c.'' stands for ``no convergence'': these are extrapolations where, out of the 5 points, at least one of them was unavailable because IM-SRG(2) or CCSD either diverged or converged extremely slowly.}
   \label{tab:ground-extrapolated}
@@
   \centering
-  \caption{Extrapolated addition energies for quantum dots with fit uncertainties.  See Table \ref{tab:ground-extrapolated} for details.}
+  \caption{Extrapolated addition energies for quantum dots with fit uncertainties.
+The abbreviation ``n.c.'' has the same meaning as in Table \ref{tab:ground-extrapolated}.
+The abbreviation``n.f.'' stands for ``no fit'': this particular extrapolation resulted in unphysical parameters ($\beta \le 0$).
+See Table \ref{tab:ground-extrapolated} for other details.}
   \label{tab:add-extrapolated}

### 2017-06-19 Manuscript/paper.tex
Made Morten and Nathan changes to CC sections

@@
 in which the wave operator, $\E^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.
-An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\bar{H}$ is not Hermitian.
+An important difference, however, is that the coupled cluster wave operator, which contains no de-excitations, is not unitary, and thus $\bar{H}$ is not Hermitian.
 
@@
 
-In practice, the cluster operator $\hat{T}$ must be truncated to be computationally feasible.  In this paper, we truncate it to only single and double excitations,
+In practice, the cluster operator $\hat{T}$ must be truncated for calculations to be computationally feasible.  In this work, we use only single and double excitations,
 \begin{align*}
@@
   \includegraphics{fig-diagrams-ccsd.pdf}
-  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}_2$.
+  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, excluding terms involving the one-body interaction $\hat{H}_1$ and first-order terms involving only the bare Hamiltonian.
+Open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}_2$.
 As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).
-Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}_2$ are unconstrained.}
+Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}_2$ are unconstrained.
+}
   \label{fig:diagrams-ccsd}

### 2017-06-20 Manuscript/paper.tex
Fixes in response to Nathan's review

@@
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
+\affiliation{The Ohio State University, Columbus, OH 43210, USA}
 \author{Sarah Reimann}
 \affiliation{Department of Chemistry and Center for Theoretical and Computational Chemistry, University of Oslo, N-0316 Oslo, Norway}
-\author{Scott Bogner}
+\author{Scott K. Bogner}
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
@@
   We present and compare several many-body methods as applied to two-dimensional quantum dots with circular symmetry.
-We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster singles-and-doubles (CCSD).
-With the application of quasidegenerate perturbation theory (QDPT) or the equation-of-motion (EOM) method, we obtain addition and removal energies as well.
+We calculate the approximate ground state energy using a harmonic oscillator basis optimized by Hartree--Fock (HF) theory and further improve the ground state energy using two post-HF methods: in-medium similarity renormalization group (IM-SRG) and coupled cluster with singles and doubles (CCSD).
+With the application of quasidegenerate perturbation theory (QDPT) or the equations-of-motion (EOM) method to the results of the previous two methods, we obtain addition and removal energies as well.
 Our results are benchmarked against full configuration interaction (FCI) and diffusion Monte Carlo (DMC) where available.
@@
 
-The behavior of strongly confined electrons is of fundamental concern to many-body theory.
+The behavior of strongly confined electrons is a major problem for many-body theory.
 The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equation-of-motion (EOM) methods.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equations-of-motion (EOM) methods.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
@@
 It has successfully been applied to systems with various underlying potentials to calculate their binding energy and other observables, especially in nuclear theory \cite{ScottSRG,PhysRevC.75.061001,SRGThreeDim}.
-The \emph{in-medium} SRG (IM-SRG) is an adaptation of the SRG method to evolve Hamiltonians in a truncated Fock space, which avoids the prohibitive cost of constructing a full many-body Hamiltonian.
-The effect of the truncation is minimized through the normal-ordering technique, which re-expands the operators with respect to a nearby many-body reference state rather than the far-away vacuum state.
-
-The article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: Hartree--Fock, IM-SRG, CCSD, QDPT, EOM.
+The \emph{in-medium} SRG (IM-SRG) method adapts the SRG approach to evolve Hamiltonians in a truncated Fock space that is centered around an approximate reference state rather than the physical vacuum, which substantially reduces the importance of the computationally costly higher-body operators.
+
+This article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: HF, IM-SRG, CCSD, QDPT, EOM.
 Our results are presented in Section \ref{sec:results}.
 We analyze and compare the differences between the various methods and also between different quantum dot systems.
-We examine the usefulness of extrapolation techniques in improving the precision of the results.
+We examine the utility of extrapolation techniques in improving the precision of our results.
 Section \ref{sec:conclusions} concludes our work and gives perspectives for future work.
@@
 We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
-The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the charge of each electron, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
+The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the electron charge, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
 
@@
 \end{align*}
-Then, the full many-body problem is described by the Hamiltonian
+The full many-body problem is described by the Hamiltonian
 \begin{align*}
@@
 \end{align*}
-Therefore, solving the noninteracting many-body problem amounts to solving the single-particle Schr\"odinger equation
+Therefore, solving the noninteracting many-body problem amounts to solving the single-particle time-independent Schr\"odinger equation
 \begin{align*}
@@
 We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
-In particular, a single-particle state is occupied in the ground state Slater determinant if and only $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
+In particular, a single-particle state is occupied in the ground state Slater determinant if and only if $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
 
@@
 This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
-The caveat is that the set of known functions be large enough to capture the relevant behavior of the system.
+The caveat is that the set of known functions must be large enough to capture the relevant behavior of the system.
 
@@
 
-The goal then is to find the coefficients $\bm C$ that minimize the energy $E_{\Phi}$,
+The goal then is to find the coefficients $\bm C$ that minimize the \textit{Hartree--Fock energy} $E_{\Phi}$,
 \begin{align}
@@
 
-With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the \textit{Hartree--Fock equation}:
+With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the self-consistent \textit{Hartree--Fock equations}:
 \begin{align} \label{eq:hartreefock}
@@
 \end{align}
-and $\bm{\varepsilon}$ is a vector of Lagrange multipliers: each element $\varepsilon_{p'}$ is associated with a specific single-particle state $|p'\rangle$.
-
-Aside from trivial cases, the HF equation is generally solved using an iterative algorithm.
+and $\bm{\varepsilon}$ is a vector of Lagrange multipliers, which serve to constrain the orthonormality of the single-particle basis.
+Each multiplier $\varepsilon_{p'}$ is associated with a specific single-particle state $|p'\rangle$.
+
+Aside from trivial cases that are analytically solvable, the HF equation is generally solved numerically using an iterative algorithm.
 We begin with an initial guess $\bm{C}^{(j)}$ on the $j$-th iteration, which is fed into Eq.\ \eqref{eq:fock} to produce the Fock matrix.
 This is then used in Eq.\ \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(j + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(j + 1)}$ as the vector of eigenvalues.
-This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point.
+This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point (self-consistency).
 While in theory it is possible for the solution to never reach a fixed point, or that it may require a unfeasibly large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
-In other cases where it is insufficient, methods such as DIIS, Broyden's method, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
+In other cases where it is insufficient, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
 Therefore, the possibility of slow or non-convergence is generally not a concern in practice.
@@
 Since HF restricts the ground state to merely a single Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
-The discrepancy between the Hartree--Fock energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
-The focus of post-HF methods such as IM-SRG or coupled cluster is to add corrections beyond mean-field approximations such as HF.
+The discrepancy between the HF energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
+The focus of post-HF methods such as IM-SRG or CC is to add corrections beyond mean-field approximations such as HF.
 
 To make use of the HF solution as the reference state for post-HF calculations, we transform the matrix elements via Eqs.\ \eqref{eq:hftransform1} and \eqref{eq:hftransform2}.
-In effect, this means we are no longer operating within the harmonic oscillator single-particle basis, but a HF-optimized single-particle basis.
+In effect, this means we are no longer operating within the harmonic oscillator single-particle basis, but rather a HF-optimized single-particle basis.
 However, we will omit the prime symbols as the post-HF methods are generic and can be used in any basis, whether optimized by HF or not.
@@
 Note that the loss of three- and higher-body terms (\textit{operator truncation}) is only one out of the two sources of error in this method.
-The other source of error is due to the \textit{basis truncation}, a concern for any method that relies on a finite single-particle basis such as IM-SRG.
-The latter can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
-In IM-SRG the CPU cost is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
+The other source of error is due to the \textit{basis truncation}, a concern for any approach that relies on a finite single-particle basis, including HF, IM-SRG, CC, and many others.
+This second source of error can be reduced by increasing the size of the basis at the expense of greater computational effort, albeit the cost increases much less rapidly in this direction.
+The CPU cost of IM-SRG methods is polynomial with respect to $N_{\mathrm{b}}$, the number of states in the single-particle basis.
 For IM-SRG(2) in particular, the CPU cost scales roughly as $\mathcal{O}(N_{\mathrm{b}}^6)$.
@@
 
-Through the flow equation and with an appropriate choice of the generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will gradually approach a more ``diagonal'' form.
+With an appropriate choice of the generator $\hat{\eta}$, the evolved state $\hat U(s) \ket{\Phi}$ will gradually approach a more ``diagonal'' form.
 If the ``diagonal'' form decouples the ground state from the excited states, then $\hat U(\infty) \ket{\Phi}$ would yield the exact ground state solution of the problem if no operator or basis truncations are made.
@@
 
-Apart from Wegner's generator, there exist several other ones in literature.
+There exist several other generators in literature.
 One choice, proposed by White \cite{White:cond-mat0201346}, makes numerical approaches much more efficient.
@@
 Terms with large energy separations from the ground state are suppressed initially, followed by those with smaller energy separations.
-This leads to stiffness in the flow equation, leading to numerical difficulties in solving the set of coupled differential equations.
+This leads to stiffness in the flow equation, which in turn causes numerical difficulties when solving the set of coupled differential equations.
 
 The White generator takes an alternative approach, which is well suited for problems where one is mainly interested in the ground state of a system.
-Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those ones that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
+Firstly, instead of driving all off-diagonal elements of the Hamiltonian to zero, the generator focuses exclusively on those that are coupled to the reference state $\Phi$ so as to decouple the reference state from the remaining Hamiltonian.
 This reduces the amount of change done to the Hamiltonian, reducing the accuracy lost from the operator truncation.
@@
 
-The White generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}.  Let
+The White generator is explicitly constructed in the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}.  Let
 \begin{align*}
@@
 
-\subsection{Coupled-cluster theory}
+\subsection{Coupled cluster theory}
 \label{subsec:cctheory}
 
-Coupled-cluster theory is based on expressing the $N$-particle correlated wave function $\ket{\Psi}$ using the exponential ansatz,
+Coupled cluster (CC) theory is based on expressing the $N$-particle correlated wave function $\ket{\Psi}$ using the exponential ansatz,
 \begin{align*}
@@
 
-Using the coupled cluster wave function, the Schr\"odinger equation,
+Using the CC ansatz, the Schr\"odinger equation,
 \begin{align} \label{eq:cc_schrodeq}
@@
 \end{align*}
-where we define a coupled-cluster effective Hamiltonian,
+where we define a \textit{coupled cluster effective Hamiltonian},
 \begin{align} \label{eq:cc_heff0}
@@
 in which the wave operator, $\E^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.
-An important difference, however, is that the coupled cluster wave operator, which contains no de-excitations, is not unitary, and thus $\bar{H}$ is not Hermitian.
+An important difference, however, is that the wave operator in CC, which contains no de-excitations, is not unitary, and thus $\bar{H}$ is not Hermitian.
 
@@
 which terminates at four-nested commutators due to the two-body nature of the interaction.
-Like with IM-SRG, this commutator expression ensures that coupled cluster is size-extensive and contains only connected terms.
+Like with IM-SRG, this commutator expression ensures that CC is size-extensive and contains only connected terms.
 In addition, because $\hat{T}$ is an excitation operator, terms of the form $\hat{T} \hat{H}$ are disconnected and thus vanish \cite{shavitt2009many}.
-Therefore the coupled cluster effective Hamiltonian can be further reduced to
+Therefore the CC effective Hamiltonian can be further reduced to
 \begin{align} \label{eq:cc_heff1}
@@
 \end{align*}
-This is known as coupled cluster singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).
+This is known as coupled cluster with singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).
 This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
@@
 This process is repeated until the amplitudes reach a fixed point.
-Like the Hartree--Fock iterative procedure, employing convergence acceleration techniques can reduce the number of coupled cluster iterations required.
+Like the HF iterative procedure, employing convergence acceleration techniques can reduce the number of CC iterations required.
 
@@
 
-The in-medium SRG, in the approach described, provides a means to calculate the ground state energy of any system that is reasonably approximated by a single Slater determinant.
+The IM-SRG method provides a means to calculate the ground state energy of any system that is reasonably approximated by a single Slater determinant.
 This works well for closed-shell systems, but it does not provide a direct means to obtain the ground state energy of open-shell systems.
-While there exist more complicated multi-reference approaches to IM-SRG that can tackle the general problem \cite{Hergert2016165}, we opted to use a perturbative approach, which is simple, inexpensive, and as we shall see in the results, quite effective for many problems.
+While there exist more complicated multi-reference approaches to IM-SRG that seek to tackle the general problem \cite{Hergert2016165}, we opted to use a perturbative approach, which is simple, inexpensive, and as we shall see from the results, quite effective for many problems.
 
@@
 where $\hat P$ projects any state into the model space and $\hat Q$ is the complement of $\hat P$.
-This entails that the exact states $\Psi_u$ is no longer normalized but instead satisfies the so-called intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
+This entails that the exact states $\Psi_u$ are no longer normalized but instead satisfy the so-called intermediate normalization: $\langle \Psi_u | \tilde \Psi^{\mathrm{o}}_u \rangle = 1$.
 
@@
 
-\subsection{Equations of motion methods}
-
-Particle attached and particle removed equations of motion (EOM) methods can be coupled with either IM-SRG or coupled cluster calculations.
+\subsection{Equations-of-motion methods}
+
+Particle attached and particle removed equations-of-motion (EOM) methods can be coupled with either IM-SRG or CC calculations.
 The principal idea is that one may construct a ladder operator $\hat{X}$ that promotes the $N$-particle ground state to any state in the $N + 1$ or $N - 1$ spectrum,
@@
 
-\subsubsection*{Equation of motion IM-SRG}
+\subsubsection*{Equations-of-motion IM-SRG}
 
@@
 We expect $N + 1$ (or $N - 1$) states to be described appropriately by EOM-IM-SRG if their wavefunctions are dominated by 1-particle-0-hole (or 0-particle-1-hole) contributions in the rotated frame.
-We use partial norms of the EOM ladder operators to make this determination:
+We use partial norms of the EOM ladder operators to estimate these contributions:
 \begin{align}
@@
 \end{align}
-Large single particle partial norms indicate that the EOM truncation is valid for the relevant state.
+Large single particle partial norms indicate that the EOM truncation is reasonable for the relevant state.
 States with lower single particle norms should be treated with a higher EOM approximation, which can be accomplished directly or perturbatively \cite{PhysRevC.95.044304}.
 
-\subsubsection*{Equation of motion coupled-cluster theory}
-
-Like EOM-IM-SRG, the equation-of-motion technique can be applied after a coupled-cluster ground-state calculation, by using the coupled-cluster effective Hamiltonian.
+\subsubsection*{Equations-of-motion coupled cluster theory}
+
+Like EOM-IM-SRG, the equations-of-motion technique can be applied after a CC ground-state calculation, by using the CC effective Hamiltonian.
 Here, the non-Hermitian nature of $\bar{H}_{\mathrm{CC}}$ becomes apparent.
@@
 There is great amount of flexibility in the application of many-body methods.
-The approaches we use is shown in Fig.\ \ref{fig:methods}.
-Such an ordering maximizes the benefits of each method: Hartree--Fock acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+The approaches we use are shown in Fig.\ \ref{fig:methods}.
+Applying the methods in this order maximizes the benefits of each method: HF acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
 
@@
 For example, one can omit HF, but continue with the remaining two steps.
-While this is doable, from our experience Hartree--Fock significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
+While this is doable, from our experience HF significantly improves the results of the later post-HF methods at very low cost compared to the post-HF methods.
 Therefore, in practice there is little reason to omit HF.
@@
 
-Since every calculation in this paper begins with the Hartree--Fock stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
+Since every calculation in this paper begins with the HF stage, we will not explicitly state ``HF'' unless there is no post-HF method used at all, in which case we write ``HF only''.
 
@@
 There are a few cases where the IM-SRG over-corrects the result, leading to an energy lower than the quasi-exact DMC results.
-This is not unexpected given that, unlike the Hartree--Fock results, the IM-SRG method is non-variational in the presence of operator truncations, which in turn results in small unitarity violations.
+This is not unexpected given that, unlike the HF results, the IM-SRG method is non-variational in the presence of operator truncations, which in turn results in small unitarity violations.
 This over-correction tends to occur when the frequency is low (high correlation), or when \emph{few} particles are involved.
@@
   \caption{(Color online) The behavior of ground state, addition, and removal energies as a function of the oscillator frequency $\omega$, with $K = 10$ shells in the basis.
-The energy is normalized with respect to the Hartree--Fock values to magnify the differences.
+The energy is normalized with respect to the HF values to magnify the differences.
 Lower frequency leads to stronger correlations and thereby a more difficult problem.}
@@
 
-Unlike the other methods, Hartree--Fock energies are somewhat unusual in that they generally do not conform to the power-law model.
+Unlike the other methods, HF energies are somewhat unusual in that they generally do not conform to the power-law model.
 In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
@@
 
-We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
+We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic HF method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.
 Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.
@@
 D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.
+Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over CC methods.
 Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.

### 2017-06-20 Manuscript/paper.tex
Prune older refs and restore some too

@@
 
-In general, quantum dot systems are not analytically solvable, with the exception of two-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561}.
+In general, quantum dot systems are not analytically solvable, with the exception of two-electron systems or systems with specific strengths of the external field \cite{PhysRevA.48.3561,10.1088/0305-4470/27/3/040}.
 Hence, in practical applications one can only hope for a numerical solution through some \textit{many-body method} or a combination thereof.
@@
 Of these methods, IM-SRG is a recently developed technique that has shown significant promises.
-Similarity renormalization group (SRG) methods are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
+Similarity renormalization group (SRG) methods \cite{PhysRevD.48.5863,PhysRevD.49.4214} are a family of methods that transform the Hamiltonian into a band- or block-diagonal form through a continuous sequence of unitary transformations.
 The goal of such a transformation is to reduce the coupling between a subspace of interest -- such as the ground state or a set of low-lying states -- and the remaining Hilbert space.
@@
 This is known as coupled cluster with singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).
-This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.
+This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{2014RPPh...77i6302H}.
 In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
@@
 Internally, \texttt{OpenFCI} calculates the interaction integrals in the center-of-mass frame using Gauss--Hermite quadrature and transforms them back into the laboratory frame to produce matrix elements suitable for use in our many-body methods.
+In principle, one could also compute Eq.\ \eqref{eq:interactionintegral} analytically \cite{0953-8984-10-3-013}, but the computational cost of the analytic expression grows much more rapidly than \texttt{OpenFCI}'s quadrature-based approach.
 
@@
 Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.
-EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.
+EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{PhysRevC.95.044304}, which is more difficult for methods such as DMC.
 

### 2017-07-01 Manuscript/paper.tex
Forgot factorial in Slater det
Tweak and simplify style

@@
 \usepackage{bm}
-\usepackage{booktabs}
 \usepackage{color}
@@
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
-\author{Nathan Parzuchowski}
+\author{Nathan M. Parzuchowski}
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
@@
 \affiliation{Department of Chemistry and Center for Theoretical and Computational Chemistry, University of Oslo, N-0316 Oslo, Norway}
-\author{Scott K. Bogner}
+\author{S. K. Bogner}
 \affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
@@
 The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
-Such nanoscale systems are highly relevant as they lie at a critical point where both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
+Such nanoscale systems are highly relevant as both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
 Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.
@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method, M\o ller-Plesset perturbation theory (MP), the in-medium similarity renormalization group (IM-SRG) method, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT), and equations-of-motion (EOM) methods.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
@@
 \begin{figure}
-  \includegraphics{figures/fig-shell-structure-v2.pdf}
+  \includegraphics{fig-shell-structure-v2.pdf}
   \caption{(Color online) The 42 lowest single-particle states (the first 5 shells) in the 2D harmonic oscillator basis.
@@
 In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
-However, to exploit the circular symmetry, we prefer to use Fock-Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
+However, to exploit the circular symmetry, we prefer to use Fock--Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
 Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
 
-The Fock-Darwin wave functions can be decomposed into radial and angular components,\cite{lohne2010coupled}
+The Fock--Darwin wave functions can be decomposed into radial and angular components,\cite{lohne2010coupled}
 \begin{align}
   F_{n m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\
-  R_{n m}(\varrho) &\equiv \sqrt{\frac{2 \cdot n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
+  R_{n m}(\varrho) &\equiv \sqrt{\frac{2 \times n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
   A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi}, \notag
@@
   \langle \bm{r}_1 \ldots \bm{r}_N | p_1 \ldots p_N \rangle \equiv
-  \frac{1}{\sqrt{N}} \left|
+  \frac{1}{\sqrt{N!}} \left|
   \begin{matrix}
@@
   \centering
-  \includegraphics{figures/fig-methods.pdf}
+  \includegraphics{fig-methods.pdf}
   \caption{(Color online) A schematic view of the various ways in which many-body methods in this paper could be combined to calculate ground state, addition, and removal energies.}
@@
   \label{tab:ground}
-  \input{tab-ground}
+  \input{tab-ground}\unskip
 \end{table}
@@
   \label{tab:add}
-  \input{tab-add}
+  \input{tab-add}\unskip
 \end{table}
@@
   \label{tab:rm}
-  \input{tab-rm}
+  \input{tab-rm}\unskip
 \end{table}
@@
   \label{tab:ground-extrapolated}
-  \input{tab-ground-extrapolated}
+  \input{tab-ground-extrapolated}\unskip
 \end{table}
@@
   \label{tab:add-extrapolated}
-  \input{tab-add-extrapolated}
+  \input{tab-add-extrapolated}\unskip
 \end{table}
@@
   \label{tab:rm-extrapolated}
-  \input{tab-rm-extrapolated}
+  \input{tab-rm-extrapolated}\unskip
 \end{table}
@@
 We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by T.
-D.
-Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over CC methods.
+A new technique developed by Morris et al.\ \cite{PhysRevC.92.034331} uses an alternative approach based on the Magnus expansion that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over CC methods.
 Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
@@
 A more efficient approach is to couple the spins of the single-particle states to form two-particle states with good $\hat S^2$, an approach analogous to \textit{j-scheme} in nuclear physics.
-A combination of this with the Eckart-Wigner theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
+A combination of this with the Wigner--Eckart theorem could reduce the computational cost significantly, albeit at the cost of increased implementation complexity.
 
@@
 
-\bibliographystyle{\mybibstyle}
 \bibliography{paper}

### 2017-07-01 Datafiles/tabulate.py

@@ -59,24 +59,24 @@ def save_table(path, label,
     if label == "ground":
         methods = ["hf", "mp2", "imsrg", "ccsd"]
         header = r"""
-        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
-        \toprule
-        {$N$} & {$\omega$} & {$K$} & {HF} & {MP2} & {IM-SRG(2)} & {CCSD} \\
-        """
+\begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
+\hline\hline
+{$N$} & {$\omega$} & {$K$} & {HF} & {MP2} & {IM-SRG(2)} & {CCSD} \\
+"""[1:]
     else:
         methods = ["hf+qdpt3", "imsrg+qdpt3", "imsrg+eom", "ccsd+eom"]
         header = r"""
-        \begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
-        \toprule
-        {$N$} & {$\omega$} & {$K$} & {HF} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
-        {} & {} & {} & {+QDPT3} & {+QDPT3} & {+EOM} & {+EOM} \\
-        """
+\begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
+\hline\hline
+{$N$} & {$\omega$} & {$K$} & {HF} & {IM-SRG(2)} & {IMSRG(2)} & {CCSD} \\
+{} & {} & {} & {+QDPT3} & {+QDPT3} & {+EOM} & {+EOM} \\
+"""[1:]
     c = d["energy"]
 
     s = []
     s.append(header)
     for num_shells, num_particles in zip(num_shells, num_particles):
-        s.append("\\midrule\n")
+        s.append("\\hline\n")
         for freq in freqs:
             row = [num_particles, freq, num_shells]
             for method in methods:
@@ -96,7 +96,7 @@ def save_table(path, label,
                         value = "n.c."
                 row.append(render_entry(value))
[…]

### 2017-07-12 Manuscript/paper.tex
Add citation

@@
 The prototypical system is that of quantum dots, also known as ``artificial atoms'', in which electrons are confined within artificially constructed semiconducting heterostructures.
-Such nanoscale systems are highly relevant as both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, and magnetization \cite{reimann2002,engel1993}.
+Such nanoscale systems are highly relevant as both theoretical models and experimental observations can readily probe quantum phenomena such as tunneling, entanglement, magnetization, and symmetry breaking \cite{reimann2002,engel1993,BIRMAN20131}.
 Moreover, unlike many physical systems, quantum dots enjoy the benefit of being highly tunable through changes in the external field or the structure of the confining material.

### 2017-08-25 Manuscript/paper.tex
Shorten pages 4-11 and 13

@@
 Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
-They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{PhysRevC.84.044306}.
+They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutron drops \cite{PhysRevC.84.044306}.
 
@@
 
-We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is the angular frequency of the oscillator trap and $r$ is the distance from the center of the trap.
+We shall model the circular quantum dot system as a collection of $N$ nonrelativistic electrons of mass $m$ in two-dimensional space, trapped by an external harmonic-oscillator potential of the form $m \omega^2r^2 / 2$, where $\omega$ is its angular frequency and $r$ is the radial distance from the center.
 The electrons interact with each other through the standard Coulomb interaction $e^2 / (4 \pi \epsilon R)$, where $e$ is the electron charge, $\epsilon$ is the permittivity of the medium, and $R$ is the distance between the two interacting electrons.
 
-Even though the model system contains five parameters $(N, m, \omega, e, \epsilon)$, many of them are redundant.
-With an appropriate choice of units, the number of parameters in the system can be reduced to just two.
-For rest of this paper, we shall use atomic units where $\hbar$, $m$, $e$ and $4 \pi \epsilon$ are all set to one.
-The unit Hartree $E_{\mathrm{h}}$ becomes the unit of energy and the Bohr radius $a$ becomes the unit of length:
-\begin{align*}
-  E_{\mathrm{h}} &\equiv m \left(\frac{e^2}{4 \pi \epsilon \hbar}\right)^2, &
-  a &\equiv \frac{4 \pi \epsilon \hbar^2}{m e^2}.
-\end{align*}
-This leaves us with $(N, \omega)$ as the only parameters necessary to specify the quantum dot system, with $\omega$ in units of $E_{\mathrm{h}} / \hbar$.
-
-The behavior of each electron in isolation is described by the nonrelativistic kinetic energy $t(\bm{r})$ and the potential energy due to the trap $u(\bm{r})$, which combine to form the standard harmonic oscillator Hamiltonian $h(\bm{p}, \bm{r})$:
-\begin{align*}
-  t(\bm{p}) &\equiv \frac{1}{2} \bm{p}^2, &
-  u(\bm{r}) &\equiv \frac{1}{2} \omega^2 \bm{r}^2, &
-  h(\bm{p}, \bm{r}) &\equiv t(\bm{p}) + t(\bm{r}).
-\end{align*}
-Here, $\bm{p}$ is the linear momentum of the electron and $\bm{r}$ is its position relative to the center of the trap.
-The pairwise interaction between two electrons at positions $\bm{r}$ and $\bm{r}'$ is simply the Coulomb interaction:
-\begin{align*}
-  v(\bm{r}, \bm{r}') \equiv \frac{1}{|\bm{r} - \bm{r}'|}.
-\end{align*}
-The full many-body problem is described by the Hamiltonian
-\begin{align*}
-  \hat H \equiv \hat H_1 + \hat H_2,
-\end{align*}
-where $\hat{H}_1$ and $\hat{H}_2$ are respectively the one- and two-body parts of the Hamiltonian, namely
-\begin{align} \label{eq:onetwobodyhamiltonian}
-\hat{H}_1 &\equiv \sum_{\alpha = 1}^N h(\hat{\bm p}_\alpha, \hat{\bm r}_\alpha), &
-\hat{H}_2 &\equiv \sum_{\alpha = 1}^N \sum_{\beta = 1}^{\alpha - 1} v(\hat{\bm r}_\alpha, \hat{\bm r}_\beta).
-\end{align}
-The operator $\hat{\bm r}_\alpha$ is the position operator of the $\alpha$-th particle,\footnote{The ordering of the particle labels $\alpha$ is unimportant as they exist only for the purpose of bookkeeping.} and $\hat{\bm p}_\alpha \equiv -\mathrm{i} \hat{\bm{\nabla}}_{\bm{r}_\alpha}$ is its momentum operator.
+For simplicity, we will use atomic units, choosen such that $\hbar \equiv m \equiv e \equiv 4 \pi \epsilon \equiv 1$, reducing the parameters of the system from $(N, m, \omega, e, \epsilon)$ to just $(N, \omega)$.
+Hence, all energies and frequencies are presented in hartrees and hartrees per $\hbar$ respectively.
+
+In these units, the many-body problem is described by the Hamiltonian
+\begin{align} \label{eq:fullhamiltonian}
+  \hat H &\equiv \hat{H}_1 + \hat{H}_2 & \hat{H}_1 &\equiv \sum_{\alpha = 1}^N \hat{h}_\alpha & \hat{H}_2 &\equiv \sum_{\alpha = 1}^N \sum_{\beta = 1}^{\alpha - 1} \frac{1}{\hat{\bm r}_\alpha - \hat{\bm r}_\beta},
+\end{align}
+where, $\hat{H}_1$ and $\hat{H}_2$ are its one- and two-body parts respecitvely, and for the $\alpha$-th particle, $\hat{\bm r}_\alpha$ is its position operator and  $\hat{h}_\alpha$ is its single-particle harmonic-oscillator Hamiltonian, defined as
+\begin{align*}
+  \hat{h} \equiv -\frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2.
+\end{align*}
+
+The noninteracting Hamiltonian $\hat{H}_1$ can be solved as $N$ independent single-particle problems involving $\hat{h}$ with easy analytic solutions in Cartesian form.
+However, to exploit circular symmetry, we use instead the Fock--Darwin states $F_{n m_\ell}$, which favor polar coordinates $\bm{r} = (\rho, \varphi)$ and conserve orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
+They are defined as\cite{lohne2010coupled}
+\begin{align}
+  F_{n m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n |m_\ell|}(\sqrt \omega \rho) \times \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi} \label{eq:fockdarwin}, \\
+  R_{n m}(\varrho) &\equiv \sqrt{\frac{2 \times n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag
+\end{align}
+where $L_n^{(\alpha)}$ denotes the generalized Laguerre polynomial \cite{NIST:DLMF} of degree $n$ and parameter $\alpha$,
+\begin{align*}
+  L_n^{(\alpha)}(u) \equiv \frac{1}{n!} u^{-\alpha} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{\alpha + n}).
+\end{align*}
+The states are distinguished by two quantum numbers: the principal quantum number $n$, a nonnegative integer related to the degree of the Laguerre polynomial, and the orbital angular momentum projection $m_\ell$, the integer eigenvalue of $\hat{L}_{\mathrm{z}}$.
 
@@
 
-The noninteracting part of the many-body Hamiltonian $\hat{H}_1$ can be reduced to $N$ independent single-particle Hamiltonians each of the form:
-\begin{align*}
-  \hat{h} = \frac{1}{2} \hat{\bm{\nabla}}^2 + \frac{1}{2} \omega^2 \hat{\bm{r}}^2.
-\end{align*}
-Therefore, solving the noninteracting many-body problem amounts to solving the single-particle time-independent Schr\"odinger equation
-\begin{align*}
-  \hat{h} |p\rangle = \varepsilon_p |p\rangle,
-\end{align*}
-where $p$ is an unknown tuple of quantum numbers.
-In Cartesian coordinates, the two-dimensional harmonic oscillator is trivially reducible to the well-known one-dimensional problem.
-However, to exploit the circular symmetry, we prefer to use Fock--Darwin states, which are written in polar coordinates $\bm{r} = (\rho, \varphi)$.
-Such states have the computationally useful property of conserving orbital angular momentum $\hat{L}_{\mathrm{z}} \equiv -\mathrm{i} \frac{\partial}{\partial \varphi}$.
-
-The Fock--Darwin wave functions can be decomposed into radial and angular components,\cite{lohne2010coupled}
-\begin{align}
-  F_{n m_\ell}(\rho, \varphi) &\equiv \sqrt\omega R_{n |m_\ell|}(\sqrt \omega \rho) A_{m_\ell}(\varphi) \label{eq:fockdarwin}, \\
-  R_{n m}(\varrho) &\equiv \sqrt{\frac{2 \times n!}{(n + m)!}} \mathrm{e}^{-\varrho^2 / 2} \varrho^m L_n^{(m)}(\varrho^2), \notag \\
-  A_{m_\ell}(\varphi) &\equiv \frac{1}{\sqrt{2 \pi}} \mathrm{e}^{\mathrm{i} m_\ell \varphi}, \notag
-\end{align}
-where $L_n^{(\alpha)}$ denotes the (generalized) Laguerre polynomial \cite{NIST:DLMF} of degree $n$ and parameter $\alpha$,
-\begin{align*}
-  L_n^{(\alpha)}(u) = \frac{1}{n!} u^{-\alpha} \mathrm{e}^u \frac{\mathrm{d}^n}{\mathrm{d} u^n} (\mathrm{e}^{-u} u^{\alpha + n}).
-\end{align*}
-The states are labeled by two quantum numbers: the principal quantum number $n \in \{0, 1, 2, \ldots\}$ and orbital angular momentum projection $m_\ell \in \mathbb \{\ldots, -2, -1, 0, +1, +2, \ldots\}$.
-For a wave function, $n$ indicates the degree of the Laguerre polynomial, whereas $m_\ell$ is simply the eigenvalue of $\hat{L}_{\mathrm{z}}$.
-
-Since electrons are spin-$\frac{1}{2}$ fermions, they can occupy either of the two possible spin states $\chi_{-\frac{1}{2}}$ or $\chi_{+\frac{1}{2}}$.
-Thus, every single-particle basis state $|n m_\ell m_{\mathrm{s}}\rangle$ contains both a spatial component \eqref{eq:fockdarwin} and a spin component,
+Single-particle states of spin-$\frac{1}{2}$ electrons also contain a spin component,
 \begin{align} \label{eq:singleparticlestate}
-  \langle \rho \varphi m_{\mathrm{s}}' |n m_\ell m_{\mathrm{s}}\rangle \equiv F_{n m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{} m_{\mathrm{s}}'}.
-\end{align}
-Here we have introduced spin projection $m_{\mathrm{s}} \in \bigl\{-\frac{1}{2}, +\frac{1}{2}\bigr\}$ as the third quantum number and $\delta_{p q}$ to denote the Kronecker delta.
-
-The energy of the single-particle state $|n m_\ell m_{\mathrm{s}}\rangle$ is given by
+  \langle \rho \varphi m_{\mathrm{s}}' |n m_\ell m_{\mathrm{s}}\rangle \equiv F_{n m_\ell}(\rho, \varphi) \delta_{m_{\mathrm{s}}^{} m_{\mathrm{s}}'},
+\end{align}
+where $m_{\mathrm{s}} = \pm\frac{1}{2}$ is the spin projection quantum number and $\delta$ is the Kronecker delta.
+
+The energy of each single-particle state $|n m_\ell m_{\mathrm{s}}\rangle$ is given by
 \begin{align} \label{eq:energysingleparticlestate}
@@
 \end{align}
-The energies are degenerate with respect to the spin projection $m_{\mathrm{s}}$ as our Hamiltonian $\hat{h}$ does not distinguish between them.
-Additionally, they are degenerate with respect to the nonnegative integer
+They are degenerate with respect to both spin projection $m_{\mathrm{s}}$ and \textit{shell index} $k$, defined as
 \begin{align} \label{eq:shell_index}
@@
 \end{align}
-which we conveniently call the \textit{shell index} as it labels each shell starting from zero.  The shells are equidistant with an energy spacing equal to the frequency $\omega$.
-
-Returning to the one-body part of the many-body Hamiltonian, $\hat{H}_1$, we can use the Slater determinant construction to build an $N$-particle eigenstate $|p_1, \ldots, p_N\rangle$ of the many-body Hamiltonian $\hat{H}_1$ from an arbitrary choice of $N$ single-particle eigenstates $|p_1\rangle, \ldots, |p_N\rangle$ from \eqref{eq:singleparticlestate}, where $p$ is an abbreviation for the triplet $(n, m_\ell, m_{\mathrm{s}})$.
-Note that a Slater determinant $|p_1 \ldots p_N\rangle$ is not merely a product of the single-particle states, but an antisymmetrized sum over all possible products,
-\begin{align*}
-  \langle \bm{r}_1 \ldots \bm{r}_N | p_1 \ldots p_N \rangle \equiv
-  \frac{1}{\sqrt{N!}} \left|
-  \begin{matrix}
-    \langle \bm{r}_1 | p_1 \rangle & \cdots & \langle \bm{r}_1 | p_N \rangle \\
-    \vdots & \ddots & \vdots \\
-    \langle \bm{r}_N | p_1 \rangle & \cdots & \langle \bm{r}_N | p_N \rangle \\
-  \end{matrix}
-  \right|.
-\end{align*}
-The Slater determinant $|p_1 \ldots p_N\rangle$ is said to \textit{occupy} the states $|p_1\rangle, \ldots, |p_N\rangle$.
-By construction, Slater determinants satisfy the Pauli exclusion principle, ensuring that the exchange of any two particles is equivalent to a reversal in the sign of the many-body wave function.
-
-The energy of a Slater determinant is given by a sum over the occupied single-particle energies,
-\begin{align*}
-  \hat{H}_1 | p_1 \ldots p_N \rangle = (\varepsilon_{p_1} + \cdots + \varepsilon_{p_N}) | p_1 \ldots p_N \rangle.
-\end{align*}
-It is possible for Slater determinants occupying different sets of single-particle states to be degenerate in energy.
-This is possible even for ground states of $\hat{H}_1$.
-However, if the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a unique, well-isolated ground state.
-The values of $N$ at which this occurs are said to be \textit{magic numbers}.
-We call $K_{\mathrm{F}}$ the \textit{number of filled shells} (or ``Fermi level'').
-In particular, a single-particle state is occupied in the ground state Slater determinant if and only if $k < K_{\mathrm{F}}$, where $k$ is the shell index of the single-particle state as defined in \eqref{eq:shell_index}.
+which labels each shell from zero.  The shell structure is illustrated in Figure \ref{fig:shell-structure}.
+
+Fermionic $N$-particle eigenstates of the one-body Hamiltonian $\hat{H}_1$ can be explicitly constructed as Slater determinants $|p_1 \ldots p_N\rangle$ of the single-particle states $|p_1\rangle, \ldots, |p_N\rangle$ from Eq.\ \eqref{eq:singleparticlestate}, where $|p\rangle$ is an abbreviation of $|n m_\ell m_{\mathrm{s}}\rangle$.
+The Slater determinant $|p_1 \ldots p_N\rangle$ is said to \textit{occupy} the single-particle states $|p_1\rangle, \ldots, |p_N\rangle$.
+
+When the number of particles $N$ satisfies $N = K_{\mathrm{F}} (K_{\mathrm{F}} + 1)$ for some nonnegative integer $K_{\mathrm{F}}$, there would be just enough particles to form a closed-shell Slater determinant, leading to a nondegenerate, well-isolated ground state.
+The values of $N$ at which this occurs are often termed \textit{magic numbers}, and $K_{\mathrm{F}}$ is the \textit{number of filled shells} (or more abstractly the ``Fermi level'').
+A single-particle state is occupied in the ground state Slater determinant if and only if $k < K_{\mathrm{F}}$, where $k$ is its shell index as defined in Eq.\ \eqref{eq:shell_index}.
 
 In this paper, we use the letters $p, q, r, s, \ldots$ to label arbitrary \textit{single-particle states} in the basis.
-In the discussion of many-body methods that rely a single, distinguished Slater determinant $\Phi$, known as the \textit{reference state}, we use the letters $i, j, k, l, \ldots$ as placeholders for the occupied states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
+In the discussion of many-body methods that rely a single, distinguished Slater determinant $\Phi$, known as the \textit{reference state}, we use the $i, j, k, l, \ldots$ as placeholders for the occupied states of $\Phi$, and $a, b, c, d, \ldots$ for the unoccupied states.
 A summation such as $\sum_p$ is understood as a summation over every single-particle basis state $p$.
-In contrast, $\sum_i$ only sums over those that are occupied and $\sum_a$ only sums over those that are unoccupied.
-
-We will describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many}.
-To properly describe fermions, we introduce the annihilation and creation operators $\hat a_p$ and $\hat a_p^\dagger$, collectively known as \textit{field operators}.
-These operators must satisfy the anticommutation relations that encode the Pauli principle, namely
-\begin{align*}
-  &\{\hat a_p, \hat a_q\} = \{\hat a_p^\dagger, \hat a_q^\dagger\} = 0, &
-  &\{\hat a_p, \hat a_q^\dagger\} = \delta_{p q}.
-\end{align*}
-
-In second quantization, the one- and two-body Hamiltonian operators $\hat{H}_1$ and $\hat{H}_2$ from Eq.\ \eqref{eq:onetwobodyhamiltonian} can be rewritten as
+In contrast, $\sum_i$ only sums over occupied states and $\sum_a$ over unoccupied ones.
+
+It is generally more convenient to describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many} for details.
+For fermions, this involves annihilation operators $\hat a_p$ and creation operators $\hat a_p^\dagger$.
+By construction, they satisfy anticommutation relations that encode the antisymmetry of the wave functions.
+The one- and two-body Hamiltonian operators $\hat{H}_1$ and $\hat{H}_2$ are rewritten as
 \begin{align} \label{eq:second_quantized_hamiltonian}
@@
 \end{align}
-where the quantities $\langle p | \hat{H}_1 | q \rangle$ and $\langle p q | \hat{H}_2 | r s \rangle$ are known as \textit{matrix elements} and fully characterize the two operators in the basis.
-
-The complete Hamiltonian is given by the sum
-\begin{align}
-  \hat{H} = \sum_{p q} \langle p | \hat{H}_1 | q \rangle \hat{a}_p^\dagger \hat{a}_q + \frac{1}{4} \sum_{p q r s} \langle p q | \hat{H}_2 | r s \rangle \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r.
-\label{eq:vacuumhamiltonian}
-\end{align}
-Due to the antisymmetry of Slater determinants, we have the property that exchanging either $p$ with $q$ or $r$ with $s$ reverses the sign of $\langle p q | \hat{H}_2 | r s \rangle$, leading to a four-fold symmetry that must be canceled out by the $1/4$ factor in front of the summation in \eqref{eq:vacuumhamiltonian}.
-For this reason, the two-body matrix element $\langle p q | \hat{H}_2 | r s \rangle$ is commonly referred to as the \emph{antisymmetrized} matrix element.
-This is not to be confused with the (non-antisymmetric) interaction integral,
+where the quantities $\langle p | \hat{H}_1 | q \rangle$ and $\langle p q | \hat{H}_2 | r s \rangle$ are referred to as \textit{matrix elements} and fully characterize the two operators in the basis.
+Specifically, $\langle p q | \hat{H}_2 | r s \rangle$ are \emph{antisymmetrized} matrix elements, which should not to be confused with the (non-antisymmetric) interaction integral,
 \begin{align} \label{eq:interactionintegral}
-  v_{p_1 p_2 p_3 p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}' \rangle v(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'.
-\end{align}
-This object only has a two-fold symmetry: $v_{p_1 p_2 p_3 p_4} = v_{p_2 p_1 p_4 p_3}$.  The antisymmetrized matrix elements are related to the interaction integral via
-\begin{align} \label{eq:antisymmetricmatrixelement}
-  \langle p q | \hat{H}_2 | r s \rangle = v_{p q r s} - v_{p q s r}.
-\end{align}
+  v_{p_1 p_2 p_3 p_4} \equiv \int \langle p_1 | \bm{r} \rangle \langle p_2 | \bm{r}'\rangle V(\bm r, \bm r') \langle \bm{r} | p_3 \rangle \langle \bm{r}' | p_4 \rangle \D \bm{r} \D \bm{r}'.
+\end{align}
+where for the standard Coulomb interaction we would have $V(\bm r, \bm r') = 1 / |\bm r - \bm r'|$.
+In practice, antisymmetrized matrix elements are often computed from interaction integrals by antisymmetrization, $\langle p q | \hat{H}_2 | r s \rangle = v_{p q r s} - v_{p q s r}$.
 
@@
 However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
-This is a general strategy for many of the many-body methods that we shall describe.
+The single-particle states of the noninteracting Hamiltonian $\hat{H}_1$ thus forms the \textit{single-particle basis} of the many-body methods that we shall describe.
 
@@
 One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
-Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value
-\begin{align} \label{eq:hfexpectation}
-  E_{\Phi} \equiv \langle \Phi | \hat H | \Phi \rangle,
-\end{align}
-with respect to $|\Phi\rangle$, subject to the restriction that $|\Phi\rangle$ remains a single Slater determinant constructed from an unknown single-particle basis.
-The restriction is what enables the simplicity and efficiency of this method.
-We shall denote each unknown single-particle state $|p'\rangle$ by a primed label $p'$.
-
-To perform numerical calculations, we further assume that each unknown state $|p'\rangle$ is built from a linear combination of known states $|p\rangle$, with an unknown matrix of coefficients $\bm C$ defined via the transformation equation
-\begin{align*}
-  |p'\rangle \equiv \sum_p |p\rangle C_{p p'}.
-\end{align*}
-This allows the problem to be reduced from an abstract minimization problem \eqref{eq:hfexpectation} to a concrete numerical problem.
-The caveat is that the set of known functions must be large enough to capture the relevant behavior of the system.
-
-If the interaction is not too strong, it is common to use the single-particle states of the noninteracting Hamiltonian $\hat{H}_1$ as the set of known states.
-
-To ensure orthonormality of the states, we require there to be as many unknown states $|p'\rangle$ as known states $|p\rangle$, and the coefficient matrix $\bm C$ must be unitary.
-These conditions are more strict than necessary, but they greatly simplify the calculations and allow the states $|p'\rangle$ to act as \textit{optimized} inputs for methods beyond HF.
-At the end of the calculation, of the set of states $|p'\rangle$ there would exactly $N$ \textit{occupied} states that participate in the optimized Slater determinant $|\Phi\rangle$.
-The remaining \textit{unoccupied} states serve as the complementary space into which particles can be excited by the interaction $\hat{H}_2$ during the post-HF calculation.
-
-The goal then is to find the coefficients $\bm C$ that minimize the \textit{Hartree--Fock energy} $E_{\Phi}$,
-\begin{align}
-  E_{\Phi} &= \sum_{i'} \langle i' | \hat{H}_1 | i' \rangle + \sum_{i' j'} \langle i' j' | \hat{H}_2 | i' j' \rangle \label{eq:hfenergy},
+Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value $E_{\Phi}$ with respect to some Slater determinant $|\Phi\rangle$ in an unknown single-particle basis.
+We shall denote each state $|p'\rangle$ in this unknown basis by a primed label $p'$.
+We assume each unknown state $|p'\rangle$ is built from a linear combination of known basis states $|p\rangle$ with an unknown unitary matrix of coefficients $C_{p p'}$.
+
+The goal is to find the coefficients $C_{p p'}$ that minimize the \textit{Hartree--Fock energy} $E_{\Phi}$,
+\begin{align}
+  E_{\Phi} &= \sum_{i'} \langle i' | \hat{H}_1 | i' \rangle + \frac{1}{2} \sum_{i' j'} \langle i' j' | \hat{H}_2 | i' j' \rangle \label{eq:hfenergy},
 \end{align}
@@
 \end{align}
-
-With the method of Lagrange multipliers, the minimization problem can be reduced to the solving of a nonlinear equation -- the self-consistent \textit{Hartree--Fock equations}:
+Using the method of Lagrange multipliers, the minimization problem reduces to a nonlinear equation -- the self-consistent \textit{Hartree--Fock equations}:
 \begin{align} \label{eq:hartreefock}
-  \bm{F} \bm{C} = \bm{C} \bm{\varepsilon},
-\end{align}
-where the \textit{Fock matrix} $\bm F$ is defined as
+  \sum_q F_{p q} C_{q p'} = C_{p p'} \varepsilon_{p'},
+\end{align}
+where the \textit{Fock matrix} $F_{p q}$ is defined as
 \begin{align} \label{eq:fock}
@@
 \end{align}
-and $\bm{\varepsilon}$ is a vector of Lagrange multipliers, which serve to constrain the orthonormality of the single-particle basis.
-Each multiplier $\varepsilon_{p'}$ is associated with a specific single-particle state $|p'\rangle$.
-
-Aside from trivial cases that are analytically solvable, the HF equation is generally solved numerically using an iterative algorithm.
-We begin with an initial guess $\bm{C}^{(j)}$ on the $j$-th iteration, which is fed into Eq.\ \eqref{eq:fock} to produce the Fock matrix.
-This is then used in Eq.\ \eqref{eq:hartreefock}, which leads to a standard eigenvalue problem from which $\bm{C}^{(j + 1)}$ arise as the matrix of eigenvectors and $\bm{\varepsilon}^{(j + 1)}$ as the vector of eigenvalues.
-This process can be repeated indefinitely until $\bm{C}$ approaches a fixed point (self-consistency).
-While in theory it is possible for the solution to never reach a fixed point, or that it may require a unfeasibly large number of iterations, in practice this naive approach can adequately provide solutions for many cases.
-In other cases where it is insufficient, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
-Therefore, the possibility of slow or non-convergence is generally not a concern in practice.
-
-For the initial guess, we simply use the ground state of our noninteracting Hamiltonian, thus $\bm{C}^{(0)} = \bm{1}$, the identity matrix.
-At each iteration, we calculate the sum of the Lagrange multipliers $\bm{\varepsilon}$ as a diagnostic for convergence: as the iteration approaches convergence, the change in the sum per iteration should decrease rapidly.
-
-Since HF restricts the ground state to merely a single Slater determinant of single-particle states, it cannot provide an exact solution to a problem where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
-The discrepancy between the HF energy and the exact ground state energy is often referred to as the \textit{correlation energy}, by definition.
-The focus of post-HF methods such as IM-SRG or CC is to add corrections beyond mean-field approximations such as HF.
+and $\varepsilon_{p'}$ is a vector of Lagrange multipliers.
+
+Besides trivial cases, the HF equation is generally solved numerically using an iterative algorithm the alternates between the use of Eq.\ \eqref{eq:fock} and Eq.\ \eqref{eq:hartreefock} to successively refine an initial guess for $C_{p p'}$ until a fixed point (self-consistency) is reached.
+For our calculations, we use the identity matrix as the initial guess.
+When convergence is too slow, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
+
+HF does not provide an exact solution to problems where multi-particle correlations are present even if the single-particle basis is not truncated (infinite in size).
+The discrepancy between the HF energy and the exact ground state energy is often referred to as the \textit{correlation energy}.
+The focus of post-HF methods such as IM-SRG or CC is to add corrections that recover parts of the correlation energy.
 
@@
 In effect, this means we are no longer operating within the harmonic oscillator single-particle basis, but rather a HF-optimized single-particle basis.
-However, we will omit the prime symbols as the post-HF methods are generic and can be used in any basis, whether optimized by HF or not.
+However, we will omit the prime symbols as the post-HF methods are generally basis-agnostic.
 
@@
 
-The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.
+The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where creation and annihilation operators are defined with respect to the physical vacuum state.
 However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.
@@
 
-In the Hamiltonian representation of Eq.\ \eqref{eq:second_quantized_hamiltonian}, the one-body operator string $\hat{a}_p^\dagger \hat{a}_q$  has an expectation value of zero in vacuum:
-\begin{align}
-&\bra{} \hat{a}_p^\dagger \hat{a}_q \ket{} = 0, \label{eq:vacuum-zero1}
-\end{align}
-and the two-body string $\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r$ does not couple states with one or fewer particles:
-\begin{align}
-&\bra{} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{} = 0, &
-&\bra{t} \hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r \ket{u} = 0. \label{eq:vacuum-zero2}
-\end{align}
-These properties arise from the fact that the creation operators always appear to the left of the annihilation operators, the defining property of a pure $k$-body operator in vacuum.
-Such strings are said to be \textit{normal-ordered with respect to the vacuum state $\ket{}$}.
-
-It is also possible to be normal-ordered with respect to a different state.
-Suppose our reference state is a Slater determinant $\ket{\Phi} \equiv \ket{i_1 i_2 \ldots i_N}$ containing $N$ occupied states $I \equiv \{i_1, i_2, \ldots, i_N\}$.
-Let $s$ be a string of fermionic field operators.
-We define the \textit{normal ordering of $s$ with respect to $|\Phi\rangle$}, denoted $\normord{s}$, to be a syntactic transformation that (a) permutes field operators belonging to $L \equiv \{\hat{a}_i^{} \mid i \in I\} \cup \{\hat{a}_a^\dagger \mid a \notin I\}$ to the left of those not belonging to $L$, and (b) attaches a negative sign to the resulting string if the permutation is odd.
-The permutation in (a) is only defined up to reordering among the $L$ and non-$L$ operators, but this ambiguity has no effect on the semantics of the result due to the sign compensation in (b).
-For example,
-\begin{align*}
-  \normord{\hat{a}_i \hat{a}^\dagger_j \hat{a}_a \hat{a}_b^\dagger}
-  &= \hat{a}_i \hat{a}_b^\dagger \hat{a}^\dagger_j \hat{a}_a \\
-  &= -\hat{a}_b^\dagger \hat{a}_i \hat{a}^\dagger_j \hat{a}_a.
-\end{align*}
-Here, both of the RHS expressions are valid and equivalent interpretations of the normal ordering  of $\hat{a}_i \hat{a}^\dagger_j \hat{a}_a \hat{a}_b^\dagger$.
-
-With normal-ordering, we obtain analogs of Eqs.\ \eqref{eq:vacuum-zero1} and \eqref{eq:vacuum-zero2} for the reference state $\ket{\Phi}$:
-\begin{align*}
-&\bra{\Phi} \normord{\hat{a}_p^\dagger \hat{a}_q} \ket{\Phi} = 0, &
-&\bra{\Phi} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r} \ket{\Phi} = 0,
-&\bra{\Phi_t} \normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s \hat{a}_r} \ket{\Phi_u} = 0.
-\end{align*}
-where $|\Phi_i\rangle \equiv \hat{a}_i^{} |\Phi\rangle$, and $|\Phi_a\rangle \equiv \hat{a}_a^\dagger |\Phi\rangle$.
-
-Likewise, we can rewrite the Hamiltonian $\hat H = \hat{H}_1 + \hat{H}_2$ in its \emph{normal-ordered representation}:
+The Hamiltonian representation in Eq.\ \eqref{eq:second_quantized_hamiltonian} is said to be \textit{normal-ordered}\cite{shavitt2009many} with respect to the (true) vacuum, meaning that for any $k$-body operator, its matrix elements vanish unless the bra and ket states have at least $k$ particles.
+It is also possible to normal order with respect to a different state, in which case matrix elements of $k$-body operators vanish unless the bra and ket states have at least $k$ \emph{quasiparticles}, as defined with respect to the reference state.
+In single-reference IM-SRG, we assume the reference state to be an $N$-particle Slater determinant $\ket{\Phi} \equiv \ket{i_1 i_2 \ldots i_N}$.
+We may then rewrite the Hamiltonian $\hat H$ in a representation normal-ordered with respect to the reference state (``Fermi vacuum'') $\ket{\Phi}$:
 \begin{align}
@@
   H_{p q} &\equiv \langle p | \hat{H}_1 | q \rangle + \sum_i \langle p i | \hat{H}_2 | q i \rangle, \\
-  H_{p q r s} &\equiv \langle p q | \hat{H}_2 | r s \rangle. \\
-\end{align*}
-If $\Phi$ is a state optimized by the HF method, then $H_\varnothing$ is simply the HF energy $E_\Phi$ and $H_{p q}$ is the Fock matrix $F_{p q}$.
-The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:vacuumhamiltonian}.
-The only difference is that the meaning of a pure $k$-body operator has been redefined with respect to the reference state $\ket{\Phi}$ rather than the vacuum state $\ket{}$, causing matrix elements to be reshuffled among the themselves.
-Where this makes a critical difference is when the operator expressions are \emph{truncated}, i.e.\ higher-body operators discarded from the computation for efficiency reasons.
+  H_{p q r s} &\equiv \langle p q | \hat{H}_2 | r s \rangle.
+\end{align*}
+The colons in $\normord{\hat{a}_p^\dagger \hat{a}_q^{}}$ and $\normord{\hat{a}_p^\dagger \hat{a}_q^\dagger \hat{a}_s^{} \hat{a}_r^{}}$ denote strings of creation and annihilation operators normal-ordered with respect to $\ket{\Phi}$.
+
+If $\Phi$ is a state optimized by the HF method, then $H_\varnothing$ is simply the HF energy $E_\Phi$ in Eq.\ \eqref{eq:hfenergy} and $H_{p q}$ is the Fock matrix $F_{p q}$ in Eq.\ \eqref{eq:fock}.
+The operator $\hat H$ in Eq.\ \eqref{eq:normordhamiltonian} is completely equivalent to $\hat H$ in Eq.\ \eqref{eq:second_quantized_hamiltonian}.
+The only difference is that the meaning of a ``$k$-body'' operator has been redefined with respect to $\ket{\Phi}$ rather than the vacuum state $\ket{}$, causing matrix elements to be reshuffled among the the $k$-body components.
+This makes a critical difference when operator expressions are \emph{truncated}, i.e.\ higher-body operators discarded from the computation for efficiency reasons.
 By normal-ordering with respect to an approximate state $\ket{\Phi}$, we reshuffle higher-body contributions into the lower-body terms, significantly reducing the importance of the higher-body operators.
@@
 
-The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
+The equations can be derived directly from the anticommutation relations of the creation and annihilation operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
 In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.

### 2017-08-25 Manuscript/paper.tex
Minor fixups to theory sections

@@
 The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.
-Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.
+Thus, they provide a rare opportunity to study electronic systems without the influence of atomic nuclei.
 They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutron drops \cite{PhysRevC.84.044306}.
@@
 In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.
-We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from the existing literature.
+We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.
 
@@
 
-This article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: HF, IM-SRG, CCSD, QDPT, EOM.
+This article is organized as follows: Section \ref{sec:formalism} introduces first (\ref{subsec:modelHamiltonian}) the Hamiltonian and basis we use to model circular quantum dots, and gives afterwards an overview of the \textit{ab initio} many-body methods used in this paper: HF, IM-SRG, CCSD, QDPT, EOM.
 Our results are presented in Section \ref{sec:results}.
@@
 \end{align}
-where, $\hat{H}_1$ and $\hat{H}_2$ are its one- and two-body parts respecitvely, and for the $\alpha$-th particle, $\hat{\bm r}_\alpha$ is its position operator and  $\hat{h}_\alpha$ is its single-particle harmonic-oscillator Hamiltonian, defined as
+where $\hat{H}_1$ and $\hat{H}_2$ are its one- and two-body parts respectively and, for the $\alpha$-th particle, $\hat{\bm r}_\alpha$ is its position operator and  $\hat{h}_\alpha$ is its single-particle harmonic-oscillator Hamiltonian,
 \begin{align*}
@@
 \end{align}
-They are degenerate with respect to both spin projection $m_{\mathrm{s}}$ and \textit{shell index} $k$, defined as
+They are degenerate with respect to both spin projection $m_{\mathrm{s}}$ and \textit{shell index} $k$,
 \begin{align} \label{eq:shell_index}
@@
 It is generally more convenient to describe many-body methods within the formalism of second quantization; see for example Ref.\ \cite{shavitt2009many} for details.
-For fermions, this involves annihilation operators $\hat a_p$ and creation operators $\hat a_p^\dagger$.
-By construction, they satisfy anticommutation relations that encode the antisymmetry of the wave functions.
+For fermions, this involves annihilation operators $\hat a_p$ and creation operators $\hat a_p^\dagger$ that, by construction, satisfy the canonical anticommutation relations.
 The one- and two-body Hamiltonian operators $\hat{H}_1$ and $\hat{H}_2$ are rewritten as
@@
 
-With the basic formalism and notation established along with the system of interest, we may begin to discuss the various techniques to solve the full many-body problem.
+We now discuss the various techniques we use to solve the interacting many-body problem.
 The principal difficulty stems from the fact that, due to the presence of interactions, the exact solution is in general \emph{not} a single Slater determinant built from the single-particle states.
-Hence, it is not possible to trivially reduce the problem to that of a single particle as we had done previously.
-
-However, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and then apply various methods to improve the accuracy of the solution.
-The single-particle states of the noninteracting Hamiltonian $\hat{H}_1$ thus forms the \textit{single-particle basis} of the many-body methods that we shall describe.
+However, for closed-shell systems, if we assume the interaction alters the behavior of the system only mildly, we can use a Slater determinant of the noninteracting system as a starting point and apply various methods to improve the accuracy of the solution.
+The single-particle states of $\hat{H}_1$ serve as the \textit{single-particle basis} of the many-body methods that we shall describe.
 
@@
 
-One of the simplest numerical corrections that could be applied to the initial guess is that of the Hartree--Fock (HF) method.
-Using the variational principle, one can compute an approximate ground state $\Phi$ by minimizing the energy expectation value $E_{\Phi}$ with respect to some Slater determinant $|\Phi\rangle$ in an unknown single-particle basis.
+One of the simplest corrections is that of the Hartree--Fock (HF) method, also known as the self-consistent field (SCF) method.
+Using the variational principle, one can obtain an approximate ground state of a closed-shell system by minimizing the energy expectation value $E_{\Phi}$ with respect to some Slater determinant $|\Phi\rangle$ in an unknown single-particle basis.
 We shall denote each state $|p'\rangle$ in this unknown basis by a primed label $p'$.
@@
 and $\varepsilon_{p'}$ is a vector of Lagrange multipliers.
+The Coulomb and exchange terms are both contained in the second term of Eq.\ \eqref{eq:fock} due to the use of antisymmetrized matrix elements.
 
@@
 When convergence is too slow, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.
+For our quantum dot cases, linear mixing was more than adequate.
 

### 2017-08-26 Manuscript/paper.tex
Add table for comparing against FCI

@@
 \end{align}
-which labels each shell from zero.  The shell structure is illustrated in Figure \ref{fig:shell-structure}.
+which labels each shell from zero.  The shell structure is illustrated in Fig.\ \ref{fig:shell-structure}.
 
@@
 The equations can be derived directly from the anticommutation relations of the creation and annihilation operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.
-In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.
+In particular, Fig.\ \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.
 
@@
 In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.
-Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.
+Fig.\ \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.
 
@@
 where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.\ \eqref{eq:moellerplessetdenominator}.
-The above expression is depicted in Figure \ref{fig:diagrams-sfe}.
-Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.
+The above expression is depicted in Fig.\ \ref{fig:diagrams-sfe}.
+Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Fig.\ \ref{fig:diagrams-sfe}.
 We will refer to QDPT to third order as ``QDPT3''.
@@
 
-Afterward, there are several paths through which one can traverse Figure \ref{fig:methods} to obtain output observables.
+Afterward, there are several paths through which one can traverse Fig.\ \ref{fig:methods} to obtain output observables.
 We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.
@@
 
-All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).
+All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Fig.\ \ref{fig:shell-structure} for an illustration of the shell structure).
 This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).
@@
 
-In Fig.\ \ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
-We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.
+\begin{table}
+  \centering
+  \caption{Similar to Table \ref{tab:ground}, this table compares the ground state energies of quantum dots calculated using IM-SRG(2), CCSD, and FCI \cite{olsen2013thesis}.}
+  \label{tab:ground-fci}
+  \input{tab-ground-fci}\unskip
+\end{table}
+
+Fig.\ \ref{fig:gs} and Table \ref{tab:ground} display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.
+We include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} (see Table \ref{tab:ground-fci}) for comparison where available.
 

### 2017-08-26 Datafiles/tabulate.py

@@ -9,7 +9,9 @@ NUM_SHELLS = [14, 16, 16, 16, 20, 20]
 # known cases of IM-SRG(2) that don't converge
 KNOWN_NC_IMSRG = set((k, kf * (kf + 1), f) for (k, kf, f) in [
     # diverged (no hope of convergence)
+    (5, 1, 0.1),
     (8, 3, 0.1),
+    (10, 1, 0.1),
     (11, 4, 0.1),
 
     # took more than 500 steps to reach s = 2.0
@@ -41,6 +43,56 @@ def render_entry(value, err=None, default_precision=4):
     if np.isnan(err):
         return "{{:.{}f}}{{{{(?)}}}}".format(default_precision).format(value)
     return utils.render_with_err(value, err)
+
+def save_fci_table(path,
+                   cases=[(2, [(0.1, 5), (0.28, 5), (1.0, 5),
+                               (0.1, 10), (0.28, 10), (1.0, 10)]),
+                          (6, [(0.1, 8), (0.28, 8), (1.0, 8)])]):
+    d = utils.load_all()
+    del d["ml"]
+    d = d[d["interaction"] == "normal"]
+    del d["interaction"]
+    d = d[d["label"] == "ground"]
+    del d["label"]
+    del d["num_filled"]
+    d = d.set_index(["num_shells", "num_particles", "freq", "method"])
+
+    methods = ["imsrg", "ccsd", "fci"]
+    header = r"""
+\begin{tabular}{S[table-format=2.0]SS[table-format=2.0]S[table-format=3.5]S[table-format=3.5]S[table-format=3.5]}%
+\hline\hline
+{$N$} & {$\omega$} & {$K$} & {IM-SRG(2)} & {CCSD} & {FCI} \\
+"""[1:]
+    c = d["energy"]
+
+    s = []
+    s.append(header)
+    for num_particles, case in cases:
+        s.append("\\hline\n")
+        for freq, num_shells in case:
+            row = [num_particles, freq, num_shells]
+            for method in methods:
+                def get(): # to allow early returns
+                    try:
+                        r = d.loc[(num_shells, num_particles, freq, method)]
+                    except KeyError:
+                        return None
+                    return r["energy"]
+                value = get()
+                if value is None:
+                    if ("imsrg" in method and
+                        (num_shells, num_particles, freq) in KNOWN_NC_IMSRG):
+                        value = "n.c."
+                    if ("ccsd" in method and
[…]

### 2017-08-26 Datafiles/utils.py

@@ -644,6 +644,7 @@ def load_ground_dmc():
 def load_ground(with_priority=False, toler=6e-4,
                 files=FileDeps(
                     "ground-sarah.txt",
+                    "ground-veronica.txt",
                     "imsrg-qdpt/ground.txt",
                     "EOM_IMSRG_qd_attached.dat",
                     "EOMIMSRG_up_to_16_attached.dat",
@@ -685,6 +686,14 @@ def load_ground(with_priority=False, toler=6e-4,
             (d["num_shells"] == 11) &
             (d["method"] == "imsrg"))]
     d["num_filled"] = get_num_filled(d["num_particles"])
+    del d["num_particles"]
+    d["priority"] = -2
+    d = d.dropna()
+    ds.append(d)
+
+    d = load_table(files["ground-veronica.txt"])
+    d["num_filled"] = get_num_filled(d["num_particles"])
+    d["method"] = "fci"
     del d["num_particles"]
     d["priority"] = -2
     d = d.dropna()

### 2017-08-29 Manuscript/paper.tex
Shortened description of CC algo and left/right eigen

@@
 where $\Delta$ are the M\o ller--Plesset denominators from Eq.\ \eqref{eq:moellerplessetdenominator}.
-As usual, these non-linear equations are solved using an iterative procedure.
-One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of Eq.\ \eqref{eq:ccsd2}.
-Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side.
-This process is repeated until the amplitudes reach a fixed point.
+As usual, these non-linear equations are solved using an iterative procedure where the cluster amplitudes on the right-hand side of Eq.\ \eqref{eq:ccsd2} are updated by calculating the terms on the left-hand side until a fixed point is reached.
 Like the HF iterative procedure, employing convergence acceleration techniques can reduce the number of CC iterations required.
@@
 
-In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent.
-In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle Eq.\ \eqref{eq:partial_norms_p} or single-hole Eq.\ \eqref{eq:partial_norms_h} natures are, in practice, not significant.
+In this paper, because the effective Hamiltonian is real, the corresponding left- and right-eigenvalues are equal.
+In addition, while the the left- and right-eigenvectors are generally not equivalent, the differences in their single-particle Eq.\ \eqref{eq:partial_norms_p} or single-hole Eq.\ \eqref{eq:partial_norms_h} natures are, in practice, not significant.
 Therefore, only the right-eigenvectors are used in this paper.

### 2017-08-30 Manuscript/paper.tex
Explain how commutator truncation in IM-SRG affects final results

@@
 This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+The IM-SRG(2) ground state energy is third-order exact, with the most prominent error terms corresponding to fourth order energy diagrams with intermediate triples, and asymmetric intermediate quadruples.
+For a wide variety of systems across nuclear physics and quantum chemistry, reincorporation of the triples adds attraction to the system, while that of the asymmetric quadruples adds repulsion.
+Because of this cancellation of errors, the IM-SRG(2) tends to track with higher-order methods such as CCSD(T).
+
+Despite the fortuitous result, the cancellation is nonetheless accidental.
+A more controlled restoration of the missing error terms can be performed perturbatively.
+In Ref.\ \cite{morris2016thesis}, the difference between IM-SRG(2) and perturbative approximations to IM-SRG(3) was investigated in nuclei, the homogeneous electron gas, and several molecules.
+In nuclei, differences in binding energies were typically on the order of hundreds of \si{keV}, whereas the binding energies themselves are on the order of \SI{8}{MeV} per nucleon.
+This is within the tolerances prescribed by the accuracy of contemporary inter-nucleon interactions.
+For electronic systems, the differences were typically less than a few millihartrees.
 

### 2017-09-05 Manuscript/paper.tex
Add more bibliographic references

@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.
@@
 
+Lastly, we note that from the above discussion it is clear that the IMSRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.
+We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of the similarities and differences from these approaches.
+
 \subsection{Coupled cluster theory}
@@
 \end{align*}
-The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge.
+The denominator allows the quantity to be meaningfully compared between different systems.
+We expect this quantity to become increasingly small as the calculations converge towards the complete basis set limit.
 
@@
 
+To minimize basis set truncation errors, one can either use explicitly correlated R12/F12 methods that account for the correct cusp behavior in many-electron wave functions\cite{Kutzelnigg1985,KLOPPER198717,explicitcorrelationreview}, or one can use basis extrapolation techniques.
+In the present work, we focus on the latter.
 As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:

### 2017-09-05 Manuscript/paper.tex
Minor fixes

--- 2017-08-30 Manuscript/paper.tex
@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset (MP) perturbation theory \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.
@@
 
+Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.
+We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of similarities with and differences from these approaches.
+
 \subsection{Coupled cluster theory}

### 2017-09-06 Manuscript/paper.tex
Inline head_revtex.tex
Comment on HF exponential convergence

@@
-\input{head_revtex.tex}
+\documentclass[aip, jcp, 12pt]{revtex4-1}
 \usepackage{amsmath}
@@
 
-To minimize basis set truncation errors, one can either use explicitly correlated R12/F12 methods that account for the correct cusp behavior in many-electron wave functions\cite{Kutzelnigg1985,KLOPPER198717,explicitcorrelationreview}, or one can use basis extrapolation techniques.
+To reduce errors from the basis set truncation, one can either use explicitly correlated R12/F12 methods that account for the correct cusp behavior in many-electron wave functions\cite{Kutzelnigg1985,KLOPPER198717,explicitcorrelationreview}, or one can use basis extrapolation techniques.
 In the present work, we focus on the latter.
-As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
+As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
 \begin{align*}
@@
 
-It is difficult to ascertain what $\beta$ is \textit{a priori}, thus we will empirically compute $\beta$ by fitting the following model through our data:
+We note that this model was derived under the assumption that all correlations are included in the calculation (i.e.\ FCI), thus we are making an assumption that our selection of methods approximately obey the same behavior.
+The validity of this assumption will be assessed at the end of this section.
+
+In general, the exponent $\beta$ cannot be determined \textit{a priori}, thus we will empirically compute $\beta$ by fitting the following model through our data:
 \begin{align} \label{eq:power_law_model}
@@
 Unlike the other methods, HF energies are somewhat unusual in that they generally do not conform to the power-law model.
-In fact, the results and plots seem to indicate an \emph{exponential} convergence with respect to the number of shells.
-It is likely that HF is insensitive to the Coulomb cusp.
+In fact, the plots indicate an \emph{exponential} convergence with respect to the number of shells, which has also been observed in molecular systems.\cite{HALKIER1999437}  We surmise that HF is insensitive to the Coulomb cusp.
 

### 2017-09-06 Manuscript/paper.tex
Minor fix

@@
 We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.
-A new technique developed by Morris et al.\ \cite{PhysRevC.92.034331} uses an alternative approach based on the Magnus expansion that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over CC methods.
+A new technique developed by Morris et al.\ \cite{PhysRevC.92.034331} uses an alternative approach based on the Magnus expansion that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which presents a significant advantage over CC methods.
 Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.

### 2017-09-06 Manuscript/paper.tex
Mention dynamical and static correlations

@@
 
-There is great amount of flexibility in the application of many-body methods.
+There is significant flexibility in the application of many-body methods.
 The approaches we use are shown in Fig.\ \ref{fig:methods}.
 Applying the methods in this order maximizes the benefits of each method: HF acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.
+We expect single-reference IM-SRG and CC to recover a substantial part of the dynamical correlations, while QDPT and EOM help account for static correlations.
 

### 2017-09-07 Manuscript/paper.tex
Fix typo

@@
 
-Besides trivial cases, the HF equation is generally solved numerically using an iterative algorithm the alternates between the use of Eq.\ \eqref{eq:fock} and Eq.\ \eqref{eq:hartreefock} to successively refine an initial guess for $C_{p p'}$ until a fixed point (self-consistency) is reached.
+Besides trivial cases, the HF equation is generally solved numerically using an iterative algorithm that alternates between the use of Eq.\ \eqref{eq:fock} and Eq.\ \eqref{eq:hartreefock} to successively refine an initial guess for $C_{p p'}$ until a fixed point (self-consistency) is reached.
 For our calculations, we use the identity matrix as the initial guess.
@@
 
-Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.
+Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazziotti1,Mazziotti2}, and the driven similarity renormalization group method \cite{Evangelista}.
 We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of similarities with and differences from these approaches.

### 2017-10-16 Manuscript/paper.tex
Fix formatting, affiliation, and references

@@
 \author{Sarah Reimann}
-\affiliation{Department of Chemistry and Center for Theoretical and Computational Chemistry, University of Oslo, N-0316 Oslo, Norway}
+\affiliation{Department of Chemistry, Hylleraas Centre for Quantum Molecular Sciences, University of Oslo, N-0316 Oslo, Norway}
 \author{S. K. Bogner}
@@
 
-In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset (MP) perturbation theory \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.
+In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset (MP) perturbation theory \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{Hergert2016165}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.
 We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.
@@
 In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).
-This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.
+This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,Hergert2016165}.
 The IM-SRG(2) ground state energy is third-order exact, with the most prominent error terms corresponding to fourth order energy diagrams with intermediate triples, and asymmetric intermediate quadruples.
@@
 \end{align}
-It is also possible \cite{IMSRG} to use $\Delta$ (also defined above), the same energy denominators from M\o ller--Plesset perturbation theory, which leads to a slightly different variant of the White generator.
+It is also possible \cite{Hergert2016165} to use $\Delta$ (also defined above), the same energy denominators from M\o ller--Plesset perturbation theory, which leads to a slightly different variant of the White generator.
 For our calculations, we use exclusively Epstein--Nesbet denominators.
@@
 \begin{align*}
-  \ket{\Psi} = e^{\hat{T}} \ket{\Phi},
+  \ket{\Psi} = \E^{\hat{T}} \ket{\Phi},
 \end{align*}
@@
 \end{align}
-can be rewritten by left-multiplying by $\bra{\Phi}e^{-T}$ as,
+can be rewritten by left-multiplying by $\bra{\Phi} \E^{-T}$ as,
 \begin{align*}
@@
 \begin{align} \label{eq:cc_heff1}
-  \bar{H}_{\mathrm{CC}} = \bigl\{\hat{H}e^{\hat{T}}\bigr\}_{\mathrm{c}},
+  \bar{H}_{\mathrm{CC}} = \bigl\{\hat{H} \E^{\hat{T}}\bigr\}_{\mathrm{c}},
 \end{align}
@@
 This would also provide some insight into the rate of convergence with respect to the operator truncation, providing a sense of how large the truncation error is.
-While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{IMSRG}.
+While a full 3-body treatment of IM-SRG would be extremely costly, it is possible implicitly track for a portion of the induced 3-body forces by computing certain diagrams that are either lower cost or could be approximated at lower cost \cite{Hergert2016165}.
 

### 2018-01-12 Manuscript/paper.tex
Fix more typos

@@
 
-Not all cases are solvable with our selection many-body methods.
+Not all cases are solvable with our selection of many-body methods.
 Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.
@@
 The results of our addition and removal energy calculations are summarized in Fig.\ \ref{fig:add} and Fig.\ \ref{fig:rm} respectively.
-The figures show the the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
+The figures show the addition/removal energies for using the approaches mentioned in Section \ref{subsec:methodology}.
 Where available, results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line.
@@
 The abbreviation ``n.c.'' has the same meaning as in Table \ref{tab:ground-extrapolated}.
-The abbreviation``n.f.'' stands for ``no fit'': this particular extrapolation resulted in unphysical parameters ($\beta \le 0$).
+The abbreviation ``n.f.'' stands for ``no fit'': this particular extrapolation resulted in unphysical parameters ($\beta \le 0$).
 See Table \ref{tab:ground-extrapolated} for other details.}
